### 2018-09-18 pilots/pilot1/vacc_manyBelief_pilot1.Rmd
added files

---
title: "Vaccines: Many Beliefs"
author: "Derek Powell"
date: "June 15, 2017"
output: 
  html_notebook: 
    code_folding: hide
---

```{r}
df <- read.csv("data/vb_pilot1.csv")
df <- df[which(df$check_3==3 & df$check_5==5),]

# first need to do some data cleaning
all_items <- c("hb_1",
            "hb_2",
            "hb_3",
            "hb_4",
            "nat_1",
            "nat_2r",
            "nat_3",
            "nat_4",
            "nat_5",
            "diseaseLikeli_1",
            "diseaseLikeli_2",
            "diseaseLikeli_3",
            "diseaseSevere_1",
            "diseaseSevere_2",
            "diseaseSevere_3",
            "diseaseSevere_4",
            "diseaseSevere_5r",
            "vaccEff_1",
            "vaccEff_2r",
            "vaccEff_3r",
            "vaccEff_4",
            "vaccDanger_1",
            "vaccDanger_2",
            "vaccDanger_3",
            "vaccDanger_4r",
            "medSkept_1",
            "medSkept_2r",
            "medSkept_3",
            "medSkept_4",
            "medSkept_5",
            "medSkept_6",
            "vaccIntent_1r",
            "vaccIntent_2",
            "vaccIntent_3r",
            "vaccIntent_4",
            "vaccIntent_5r",
            "parDuty_1",
            "parDuty_2",
            "parDuty_3",
            "parDuty_4",
            "parExpert_1",
            "parExpert_2",
            "parExpert_3",
            "parExpert_4",
            "parExpert_5",
            "immCap_1",
            "immCap_2",
            "immCap_3r",
            "immCap_4",
            "immSymptoms_1",
            "immSymptoms_2",
            "immSympt_3r",
            "immSympt_4r",
            "immWeak_1",
            "immWeak_2",
            "immWeak_3r",
            "immWeak_4r",
            "immWeak_5",
            "immStrain_1",
            "immStrain_2r",
            "immPassive_1",
            "immPassive_2r",
            "immPassive_3")

reverse_items <- c("nat_2r",
                   "diseaseSevere_5r",
                   "vaccEff_2r", 
                   "vaccEff_3r",
                   "medSkept_2r",
                   "vaccDanger_4r",
                   "vaccIntent_1r",
                   "vaccIntent_3r",
                   "vaccIntent_5r",
                   "immCap_3r",
                   "immSympt_3r",
                   "immSympt_4r",
                   "immWeak_3r",
                   "immWeak_4r",
                   "immStrain_2r",
                   "immPassive_2r")

df[,all_items] <- lapply(df[,all_items], function(x) {
  8-x
})

df[,reverse_items] <- lapply(df[,reverse_items], function(x) {
  8-x
})

df_main <- df[,all_items]
```
# Introduction

This is a notebook for the first pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures. We recruited 100 participants and lost 5 to comprehension checks, leaving 95.

# Item Correlations

Here's a correlation matrix for all individual items. It appears items of some scales are intercorrelating well, though others are weaker. There is also considerable correlation among items across scales--as we might expect.

```{r,fig.height=9,fig.width=9}
library(corrplot)
library(viridis)

corrplot(cor(df_main),
         tl.cex=.75,
         tl.col="black",
         method="color",
         col=viridis(128))
```

Here's another matrix, this time sorted according to a hierarchical clustering algorithm, with bounding rectangles identifying clusters. Whereas we treated these as 15 different scales, this finds just 3 separate clusters. I don't think this is a problem--we expected and even hoped these scales would be correlated with one another.

```{r,fig.height=9,fig.width=9}
corrplot(cor(df_main[,all_items]),
         order="hclust",
         # addrect=3,
         tl.cex=.75,
         tl.col="black",
         method="color",
         col=viridis(128))
```

# Scale Internal Consistency Reliability

Below are computed chronbach's alpha for all scales along with more detailed analyses of scales that are problematic.

## Holistic Balance

```{r}
hb <- c("hb_1",
        "hb_2",
        "hb_3",
        "hb_4")

hb.alpha <- psych::alpha(df[,hb])
hb.alpha$total$raw_alpha
```

## Naturalism

```{r}
nat <- c("nat_1",
"nat_2r",
"nat_3",
"nat_4",
"nat_5")

naturalism.alpha <- psych::alpha(df[,nat])
naturalism.alpha$total$raw_alpha
```

## Disease Likelihood

```{r}
diseaseLikeli <- c("diseaseLikeli_1",
"diseaseLikeli_2",
"diseaseLikeli_3")

diseaseLikeli.alpha <- psych::alpha(df[,diseaseLikeli])
diseaseLikeli.alpha$total$raw_alpha
```

## Disease Severity

**NOTE**: we scored this one kind of strangely, high scores mean you believe diseases are unlikely. So should really be labled "Diseases Unlikely" (as it is below) or in the future could be reversed.

```{r}
diseaseSevere <- c("diseaseSevere_1",
"diseaseSevere_2",
"diseaseSevere_3",
"diseaseSevere_4",
"diseaseSevere_5r")

diseaseSevere.alpha <- psych::alpha(df[,diseaseSevere])
diseaseSevere.alpha$total$raw_alpha
```

## Vaccine Effectiveness

```{r}
vaccEff <- c("vaccEff_1",
"vaccEff_2r",
"vaccEff_3r",
"vaccEff_4")

vaccEff.alpha <- psych::alpha(df[,vaccEff])
vaccEff.alpha$total$raw_alpha
```

## Vaccine Danger

```{r}
vaccDanger <- c("vaccDanger_1",
"vaccDanger_2",
"vaccDanger_3",
"vaccDanger_4r")

vaccDanger.alpha <- psych::alpha(df[,vaccDanger])
vaccDanger.alpha$total$raw_alpha
```

## Medical Skepticism

```{r}
medSkept <- c("medSkept_1",
"medSkept_2r",
"medSkept_3",
"medSkept_4",
"medSkept_5",
"medSkept_6")

medSkept.alpha <- psych::alpha(df[,medSkept])
medSkept.alpha$total$raw_alpha
```

## Vaccination Intentions

```{r}
vaccIntent <- c("vaccIntent_1r",
"vaccIntent_2",
"vaccIntent_3r",
"vaccIntent_4",
"vaccIntent_5r")

vaccIntent.alpha <- psych::alpha(df[,vaccIntent])
vaccIntent.alpha$total$raw_alpha
```

## Parental Duty

```{r}
parDuty <- c("parDuty_1",
"parDuty_2",
"parDuty_3",
"parDuty_4")

parDuty.alpha <- psych::alpha(df[,parDuty])
parDuty.alpha$total$raw_alpha
# parDuty.alpha
```

## Parental Expertise (and patient individualism)

```{r}
parExpert <- c("parExpert_1",
"parExpert_2",
"parExpert_3",
"parExpert_4",
"parExpert_5")

parExpert.alpha <- psych::alpha(df[,parExpert])
parExpert.alpha$total$raw_alpha
```

## Immune system has limited capacity

Reliability is low here with no obvious way to fix it.

```{r}
immCap <- c("immCap_1",
"immCap_2",
"immCap_3r",
"immCap_4")

immCap.alpha <- psych::alpha(df[,immCap])
immCap.alpha$total$raw_alpha
immCap.alpha

```

## Immune system produces cold symptoms

Reliability is somewhat middling here.

```{r}
immSympt <- c("immSymptoms_1",
"immSymptoms_2",
"immSympt_3r",
"immSympt_4r")

immSympt.alpha <- psych::alpha(df[,immSympt])
immSympt.alpha$total$raw_alpha
immSympt.alpha

```

## Children's immune systems are weak

Some problems here. The second item, "Babies should be sheltered from exposure to germs as much as possible" is essentially uncorrelated with the rest of the scale.

```{r}
immWeak <- c("immWeak_1",
"immWeak_2",
"immWeak_3r",
"immWeak_4r",
"immWeak_5")

immWeak.alpha <- psych::alpha(df[,immWeak])
immWeak.alpha$total$raw_alpha
immWeak.alpha

```

Dropping that item as well as the other "germ" item (#3, "Even infants immune systems are able to fight germs"), raises the reliability closer to acceptable levels.

```{r}
psych::alpha(df[,c("immWeak_1",
"immWeak_4r",
"immWeak_5")])
```

## vaccines strain the immune system

Probably not really right to calculate reliability here -- there are only two items in this scale.

```{r}
immStrain <- c("immStrain_1",
"immStrain_2r")

# cor(df$immStrain_1,df$immStrain_2r)

immStrain.alpha <- psych::alpha(df[,immStrain])

immStrain.alpha

```

## Immune system can operate passively

This scale is a complete mess. The items are all essentially uncorrelated. Based on face validity I think the third item is the least related, so perhaps it should be dropped.

```{r}
immPassive <- c("immPassive_1",
"immPassive_2r",
"immPassive_3")

immPassive.alpha <- psych::alpha(df[,immPassive])

immPassive.alpha

```

```{r}
cor(df[,immPassive])
```

# Scale Distributions

Here I'm computing the scale average for all scales but the "children's weak immune system" scale and the "passive immune system" scale, where I'm making the changes suggested from the reliability analysis. *UPDATE*: Now also changing the "immune system and cold symptoms" scale to remove a bad item.

```{r}
df_scales<-df_main
df_scales$holBalance <- rowMeans(df[,hb])
df_scales$naturalism <- rowMeans(df[,nat])
df_scales$diseaseUnlikely <- rowMeans(df[,diseaseLikeli])
df_scales$diseaseSevere <- rowMeans(df[,diseaseSevere])
df_scales$vaccEff <- rowMeans(df[,vaccEff])
df_scales$vaccDanger <- rowMeans(df[,vaccDanger])
df_scales$medSkept <- rowMeans(df[,medSkept])
df_scales$vaccIntent <- rowMeans(df[,vaccIntent])
df_scales$parDuty <- rowMeans(df[,parDuty])
df_scales$parExpert <- rowMeans(df[,parExpert])
df_scales$immCap <- rowMeans(df[,immCap])
df_scales$immSympt <- rowMeans(df[,c("immSymptoms_1","immSympt_3r","immSympt_4r")])
df_scales$immWeak <- rowMeans(df[,c("immWeak_1","immWeak_4r","immWeak_5")])
df_scales$immStrain <- rowMeans(df[,immStrain])
df_scales$immPassive <- rowMeans(df[,c("immPassive_1","immPassive_2r")])

```

```{r,fig.height=9,fig.width=9}
library(ggplot2)
library(reshape2)

scale_vars <- c("holBalance",
                "naturalism",
                "diseaseUnlikely",
                "diseaseSevere",
                "vaccEff",
                "vaccDanger",
                "medSkept",
                "vaccIntent", 
                "parDuty",
                "parExpert",
                "immCap",
                "immSympt",
                "immWeak",
                "immStrain",
                "immPassive")

# df_hist <- df_scales[,scale_vars]
ggplot(data = melt(df_scales[,scale_vars]), mapping = aes(x = value)) + 
    geom_histogram(bins = 10) + facet_wrap(~variable, scales = 'free_x')
```

# Scale correlations

Here are intercorrelations among the scales (ordered by angular order of eigenvectors). I think we should use a big grain of salt interpreting any of these because this is all based on just `r nrow(df_scales)` paricipants' data. Nevertheless, let's take a look.

Some of this is expected and some is a bit surprising. Of course once we start taking into account other conditional dependencies, some of these correlations could change, or even reverse sign.

```{r,fig.height=9,fig.width=9}
corrplot(cor(df_scales[,scale_vars]),
         order="AOE",
         tl.cex=1,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))
```

### Linear model predicting vaccine intentions

This is just goofing around, throwing some of our topic predictors in terms of pairwise correlations into a linear model together.

First have to find an appropriate distribution because the distribution of vaccine intentions is extremely non-normal.

```{r}
library(fitdistrplus)
descdist(df_scales$vaccIntent)
# fit.gamma <- fitdist(df_scales$vaccIntent,"gamma")
# plot(fit.gamma)
# 
# fit.weibull <- fitdist(df_scales$vaccIntent,"weibull")
# plot(fit.weibull)

df_scales$scaledIntent <- (df_scales$vaccIntent - 1)/7
fit.beta <- fitdist(df_scales$scaledIntent,"beta")
plot(fit.beta)
```

Beta distribution does a decent job of capturing it. Let's do beta regression using BRMS.

```{r}
library(brms)

fit <- brm(scaledIntent ~ vaccEff + vaccDanger + diseaseUnlikely + diseaseSevere + naturalism + medSkept, family="Beta", data=df_scales)
summary(fit)
```

Beta regression model predicted values account for `r round(cor(predict(fit)[,1],df_scales$scaledIntent)**2*100,1)`% of the variance (and a standard normal linear model performed just a few percent worse in an earlier test). So, what you think matters!

```{r}

df_scales$predicted <- predict(fit)[,1]*6+1
ggplot(df_scales,aes(x=predicted,y=vaccIntent)) + 
  geom_jitter(shape=1) + 
  geom_smooth() + 
  labs(x="Predicted Values", y="Observed Vaccination Intention")

```

### 2018-09-18 pilots/pilot2/vacc_manyBelief_pilot2.Rmd
added files

---
title: "Vaccines: Many Beliefs Pilot 2"
author: "Derek Powell"
date: "June 21, 2017"
output: 
  html_notebook: 
    code_folding: hide
---

```{r}
library(ggplot2)
df <- read.csv("data/vb_pilot2.csv")
df <- df[which(df$parentDuty_check_3==3 & df$diseaseRare_check_5==5),]

# first need to do some data cleaning
all_items <- c("hb_hb_1",
"hb_hb_2",
"hb_hb_3",
"hb_hb_4",
"nat_nat_1",
"nat_nat_2r",
"nat_nat_3",
"nat_nat_4",
"nat_nat_5",
"medSkept_medSkept_1",
"medSkept_medSkept_2r",
"medSkept_medSkept_3",
"medSkept_medSkept_4",
"medSkept_medSkept_5",
"medSkept_medSkept_6",
"diseaseRare_diseaseRare_1",
"diseaseRare_diseaseRare_2",
"diseaseRare_diseaseRare_3",
"diseaseSevere_diseaseSevere_1",
"diseaseSevere_diseaseSevere_2",
"diseaseSevere_diseaseSevere_3",
"diseaseSevere_diseaseSevere_4",
"diseaseSevere_diseaseSevere_5r",
"vaccEff_vaccEff_1",
"vaccEff_vaccEff_2r",
"vaccEff_vaccEff_3r",
"vaccEff_vaccEff_4",
"vaccDanger_vaccDanger_1",
"vaccDanger_vaccDanger_2",
"vaccDanger_vaccDanger_3",
"vaccDanger_vaccDanger_4r",
"vaccTox_vaccTox_1",
"vaccTox_vaccTox_2",
"vaccTox_vaccTox_3",
"vaccTox_vaccTox_4r",
"vaccStrain_vaccStrain_1",
"vaccStrain_vaccStrain_2r",
"vaccStrain_vaccStrain_3",
"vaccIntent_vaccIntent_1r",
"vaccIntent_vaccIntent_2",
"vaccIntent_vaccIntent_3r",
"vaccIntent_vaccIntent_4",
"vaccIntent_vaccIntent_5r",
"infantVuln_infantVuln_1r",
"infantVuln_infantVuln_2",
"infantVuln_infantVuln_3",
"parentDuty_parentDuty_1",
"parentDuty_parentDuty_2",
"parentDuty_parentDuty_3",
"parentDuty_parentDuty_4",
"parentExpert_parentExpert_1",
"parentExpert_parentExpert_2",
"parentExpert_parentExpert_3",
"parentExpert_parentExpert_4",
"parentExpert_parentExpert_5",
"infantImmLimCap_infantImmLimCap_1",
"infantImmLimCap_infantImmLimCap_2r",
"infantImmLimCap_infantImmLimCap_3",
"infantImmLimCap_infantImmLimCap_4",
"immSympt_immSympt_1",
"immSympt_immSympt_2r",
"immSympt_immSympt_3r",
"infantImmWeak_infantImmWeak_1",
"infantImmWeak_infantImmWeak_2",
"infantImmWeak_infantImmWeak_3",
"infantImmWeak_infantImmWeak_4r"

)

reverse_items <- c("nat_nat_2r",
                  "vaccEff_vaccEff_2r",
                  "vaccEff_vaccEff_3r",
                  "vaccTox_vaccTox_4r",
                  "medSkept_medSkept_2r",
                  "immSympt_immSympt_2r",
                  "immSympt_immSympt_3r",
                  "vaccDanger_vaccDanger_4r",
                  "vaccStrain_vaccStrain_2r",
                  "vaccIntent_vaccIntent_1r",
                  "vaccIntent_vaccIntent_3r",
                  "vaccIntent_vaccIntent_5r",
                  "infantVuln_infantVuln_1r",
                  "diseaseSevere_diseaseSevere_5r",
                  "infantImmWeak_infantImmWeak_4r",
                  "infantImmLimCap_infantImmLimCap_2r")

# df[,all_items] <- lapply(df[,all_items], function(x) {
#   8-x
# })

df[,reverse_items] <- lapply(df[,reverse_items], function(x) {
  8-x
})

df_main <- df[,all_items]
```
# Introduction

This is a notebook for the first pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures. We recruited 100 participants and lost 6 to comprehension checks, leaving 94.

# Item Correlations

Here's a correlation matrix for all individual items. It appears items of some scales are intercorrelating well, though others are weaker. There is also considerable correlation among items across scales--as we might expect.

```{r,fig.height=9,fig.width=9}
library(corrplot)
library(viridis)

corrplot(cor(df_main),
         tl.cex=.65,
         tl.col="black",
         method="color",
         col=viridis(128))
```

Here's another matrix, this time sorted according to a hierarchical clustering algorithm, with bounding rectangles identifying clusters. Whereas we treated these as 15 different scales, this finds just 3 separate clusters. I don't think this is a problem--we expected and even hoped these scales would be correlated with one another.

```{r,fig.height=9,fig.width=9}
corrplot(cor(df_main[,all_items]),
         order="hclust",
         # addrect=3,
         tl.cex=.65,
         tl.col="black",
         method="color",
         col=viridis(128))
```

# Scale Internal Consistency Reliability

Below are computed chronbach's alpha for all scales along with more detailed analyses of scales that are problematic.

## Holistic Balance

```{r}
hb <- c("hb_hb_1",
"hb_hb_2",
"hb_hb_3",
"hb_hb_4")

hb.alpha <- psych::alpha(df[,hb])
hb.alpha$total$raw_alpha
```

## Naturalism

```{r}
nat <- c("nat_nat_1",
"nat_nat_2r",
"nat_nat_3",
"nat_nat_4",
"nat_nat_5")

naturalism.alpha <- psych::alpha(df[,nat])
naturalism.alpha$total$raw_alpha

```

## Disease Rarity

**NOTE**: we previously scored this one kind of strangely, so it's now been relabeld as "diseaseRare" to indicate that it reflects participants' belief the diseases are extremely rare.

```{r}
diseaseRare <- c("diseaseRare_diseaseRare_1",
"diseaseRare_diseaseRare_2",
"diseaseRare_diseaseRare_3")

diseaseRare.alpha <- psych::alpha(df[,diseaseRare])
diseaseRare.alpha$total$raw_alpha

```

## Disease Severity

```{r}
diseaseSevere <- c("diseaseSevere_diseaseSevere_1",
"diseaseSevere_diseaseSevere_2",
"diseaseSevere_diseaseSevere_3",
"diseaseSevere_diseaseSevere_4",
"diseaseSevere_diseaseSevere_5r")

diseaseSevere.alpha <- psych::alpha(df[,diseaseSevere])
diseaseSevere.alpha$total$raw_alpha
diseaseSevere.alpha

```
### Diagnosing

Here are histograms of each item

```{r}
library(ggplot2)
library(reshape2)

ggplot(data = melt(df[,diseaseSevere]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
corrplot(cor(df[,diseaseSevere]),
         type="lower",
         order="alpha",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

```

Now try McDonald's Omega (which might be better for all--though some problem with scales with only 3 items?). The robust estimates mostly seem higher than the normal estimates.

```{r}
library(coefficientalpha)

omega(df[,diseaseSevere])
```

## Vaccine Effectiveness

```{r}
vaccEff <- c("vaccEff_vaccEff_1",
"vaccEff_vaccEff_2r",
"vaccEff_vaccEff_3r",
"vaccEff_vaccEff_4")

vaccEff.alpha <- psych::alpha(df[,vaccEff])
vaccEff.alpha$total$raw_alpha
```

## Vaccine Danger

```{r}
vaccDanger <- c("vaccDanger_vaccDanger_1",
"vaccDanger_vaccDanger_2",
"vaccDanger_vaccDanger_3",
"vaccDanger_vaccDanger_4r")

vaccDanger.alpha <- psych::alpha(df[,vaccDanger])
vaccDanger.alpha$total$raw_alpha
```

## Vaccines are toxic

```{r}
vaccTox <- c("vaccTox_vaccTox_1",
"vaccTox_vaccTox_2",
"vaccTox_vaccTox_3",
"vaccTox_vaccTox_4r")

vaccTox.alpha <- psych::alpha(df[,vaccTox])
vaccTox.alpha$total$raw
```

## Medical Skepticism

```{r}
medSkept <- c("medSkept_medSkept_1",
"medSkept_medSkept_2r",
"medSkept_medSkept_3",
"medSkept_medSkept_4",
"medSkept_medSkept_5",
"medSkept_medSkept_6")

medSkept.alpha <- psych::alpha(df[,medSkept])
medSkept.alpha$total$raw_alpha
```

## Vaccination Intentions

```{r}
vaccIntent <- c("vaccIntent_vaccIntent_1r",
"vaccIntent_vaccIntent_2",
"vaccIntent_vaccIntent_3r",
"vaccIntent_vaccIntent_4",
"vaccIntent_vaccIntent_5r")

vaccIntent.alpha <- psych::alpha(df[,vaccIntent])
vaccIntent.alpha$total$raw_alpha
```

## Infant vulnerability (general)

Reliabilty here is somewhat low.

```{r}
infantVuln <- c("infantVuln_infantVuln_1r",
"infantVuln_infantVuln_2",
"infantVuln_infantVuln_3")

infantVuln.alpha <- psych::alpha(df[,infantVuln])

infantVuln.alpha$total$raw_alpha
infantVuln.alpha
```

## Parental Duty

This remains middling.

```{r}
parDuty <- c("parentDuty_parentDuty_1",
"parentDuty_parentDuty_2",
"parentDuty_parentDuty_3",
"parentDuty_parentDuty_4")

parDuty.alpha <- psych::alpha(df[,parDuty])
parDuty.alpha$total$raw_alpha
parDuty.alpha
```

## Parental Expertise (and patient individualism)

As does this.

```{r}
parExpert <- c("parentExpert_parentExpert_1",
"parentExpert_parentExpert_2",
"parentExpert_parentExpert_3",
"parentExpert_parentExpert_4",
"parentExpert_parentExpert_5")

parExpert.alpha <- psych::alpha(df[,parExpert])
parExpert.alpha$total$raw_alpha
parExpert.alpha
```
```{r}
library(ggplot2)
library(reshape2)

ggplot(data = melt(df[,parExpert]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

corrplot(cor(df[,parExpert]),
         type="lower",
         order="AOE",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

psych::alpha(df[, c("parentExpert_parentExpert_1",
"parentExpert_parentExpert_2",

"parentExpert_parentExpert_5")])
```

## Infant immune system has limited capacity

Reliability much better now. Perhaps still not as high as we'd like but seriously improved.

```{r}
immCap <- c("infantImmLimCap_infantImmLimCap_1",
"infantImmLimCap_infantImmLimCap_2r",
"infantImmLimCap_infantImmLimCap_3",
"infantImmLimCap_infantImmLimCap_4")

immCap.alpha <- psych::alpha(df[,immCap])
immCap.alpha$total$raw_alpha
immCap.alpha

```

```{r}

library(ggplot2)
library(reshape2)

ggplot(data = melt(df[,immCap]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

corrplot(cor(df[,c(immCap,immWeak)]),
         order="AOE",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

psych::alpha(df[,c(immCap,immWeak)])
```

## Immune system produces cold symptoms

Reliability better but still somewhat middling here.

```{r}
immSympt <- c("immSympt_immSympt_1",
"immSympt_immSympt_2r",
"immSympt_immSympt_3r")

immSympt.alpha <- psych::alpha(df[,immSympt])
immSympt.alpha$total$raw_alpha
immSympt.alpha

```

## Infants' immune systems are weak

This looks much better!

```{r}
immWeak <- c("infantImmWeak_infantImmWeak_1",
"infantImmWeak_infantImmWeak_2",
"infantImmWeak_infantImmWeak_3",
"infantImmWeak_infantImmWeak_4r")

immWeak.alpha <- psych::alpha(df[,immWeak])
immWeak.alpha$total$raw_alpha
immWeak.alpha

```

## Vaccines strain the immune system

Now with three items this makes for a pretty reliable scale.

```{r}
vaccStrain <- c("vaccStrain_vaccStrain_1",
"vaccStrain_vaccStrain_2r",
"vaccStrain_vaccStrain_3")

# cor(df$immStrain_1,df$immStrain_2r)

vaccStrain.alpha <- psych::alpha(df[,vaccStrain])

vaccStrain.alpha

```

# Scale Distributions

Here I'm computing the scale average for all scales but the "children's weak immune system" scale and the "passive immune system" scale, where I'm making the changes suggested from the reliability analysis. *UPDATE*: Now also changing the "immune system and cold symptoms" scale to remove a bad item.

```{r}
df_scales<-df_main
df_scales$holBalance <- rowMeans(df[,hb])
df_scales$naturalism <- rowMeans(df[,nat])
df_scales$diseaseRare <- rowMeans(df[,diseaseRare])
df_scales$diseaseSevere <- rowMeans(df[,diseaseSevere])
df_scales$vaccEff <- rowMeans(df[,vaccEff])
df_scales$vaccDanger <- rowMeans(df[,vaccDanger])
df_scales$medSkept <- rowMeans(df[,medSkept])
df_scales$vaccIntent <- rowMeans(df[,vaccIntent])
df_scales$parDuty <- rowMeans(df[,parDuty])
df_scales$parExpert <- rowMeans(df[,parExpert])
df_scales$immCap <- rowMeans(df[,immCap])
df_scales$immSympt <- rowMeans(df[,immSympt])
df_scales$immWeak <- rowMeans(df[,immWeak])
df_scales$vaccStrain <- rowMeans(df[,vaccStrain])
df_scales$vaccTox <- rowMeans(df[,vaccTox])
df_scales$infantVuln <- rowMeans(df[,infantVuln])
```

```{r,fig.height=9,fig.width=9}
library(ggplot2)
library(reshape2)

scale_vars <- c("holBalance",
                "naturalism",
                "diseaseRare",
                "diseaseSevere",
                "vaccEff",
                "vaccDanger",
                "medSkept",
                "vaccIntent", 
                "parDuty",
                "parExpert",
                "immCap",
                "immSympt",
                "immWeak",
                "vaccStrain",
                "vaccTox",
                "infantVuln")

# df_hist <- df_scales[,scale_vars]
ggplot(data = melt(df_scales[,scale_vars]), mapping = aes(x = value)) + 
    geom_histogram(bins = 10) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
```

# Scale correlations

Here are intercorrelations among the scales (ordered by angular order of eigenvectors). I think we should use a big grain of salt interpreting any of these because this is all based on just `r nrow(df_scales)` paricipants' data. Nevertheless, let's take a look.

Some of this is expected and some is a bit surprising. Of course once we start taking into account other conditional dependencies, some of these correlations could change, or even reverse sign.

```{r,fig.height=9,fig.width=9}
corrplot(cor(df_scales[,scale_vars]),
         order="hclust",
         tl.cex=1.25,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))
```

### 2018-09-18 pilots/pilot3/vacc_manyBelief_pilot3.Rmd
added files

---
title: "Vaccines: Many Beliefs Pilot 3"
author: "Derek Powell"
date: "June 26, 2017"
output: 
  html_notebook: 
    code_folding: hide
---

```{r}

filename <- "data/vb_pilot3.csv"

headers <- as.matrix(read.csv(filename, skip = 0, header = F, nrows = 1, as.is = T ))
df <- read.csv(filename, skip = 3, header = F)
colnames(df) <- headers

df <- df[which(df$Status==0),] # remove survey previews

# remove unused qualtrics variables
remove_cols <- c("RecipientLastName",
                 "RecipientFirstName",
                 "RecipientEmail",
                 "Finished",
                 "ResponseId",
                 "ExternalReference",
                 "DistributionChannel",
                 "UserLanguage",
                 "Status")

df <- df[ , -which(names(df) %in% remove_cols)]
```

```{r}
all_items <- c("hb_hb_1",
"hb_hb_2",
"hb_hb_3",
"hb_hb_4",
"nat_nat_1",
"nat_nat_2r",
"nat_nat_3",
"nat_nat_4",
"nat_nat_5",
"medSkept_medSkept_1",
"medSkept_medSkept_2r",
"medSkept_medSkept_3",
"medSkept_medSkept_4",
"medSkept_medSkept_5",
"medSkept_medSkept_6",
"diseaseRare_diseaseRare_1",
"diseaseRare_diseaseRare_2",
"diseaseRare_diseaseRare_3",
"diseaseRare_diseaseRare_4",
"diseaseSevere_diseaseSevere_1",
"diseaseSevere_diseaseSevere_2",
"diseaseSevere_diseaseSevere_3",
"diseaseSevere_diseaseSevere_4r",
"diseaseSevere_diseaseSevere_5",
"diseaseSevere_diseaseSevere_6",
"vaccEff_vaccEff_1",
"vaccEff_vaccEff_2r",
"vaccEff_vaccEff_3r",
"vaccEff_vaccEff_4",
"vaccDanger_vaccDanger_1",
"vaccDanger_vaccDanger_2",
"vaccDanger_vaccDanger_3",
"vaccDanger_vaccDanger_4r",
"vaccTox_vaccTox_1",
"vaccTox_vaccTox_2",
"vaccTox_vaccTox_3",
"vaccTox_vaccTox_4r",
"vaccStrain_vaccStrain_1",
"vaccStrain_vaccStrain_2r",
"vaccStrain_vaccStrain_3",
"vaccStrain_vaccStrain_4",
"vaccStrain_vaccStrain_5",
"vaccIntent_vaccIntent_1r",
"vaccIntent_vaccIntent_2",
"vaccIntent_vaccIntent_3r",
"vaccIntent_vaccIntent_4",
"vaccIntent_vaccIntent_5r",
"parentExpert_parentExpert_1",
"parentExpert_parentExpert_2",
"parentExpert_parentExpert_3",
"parentExpert_parentExpert_4r",
"infantImmLimCap_infantImmLimCap_1",
"infantImmLimCap_infantImmLimCap_2r",
"infantImmLimCap_infantImmLimCap_3",
"infantImmLimCap_infantImmLimCap_4",
"infantImmLimCap_infantImmLimCap_5",
"immSympt_immSympt_1",
"immSympt_immSympt_2r",
"immSympt_immSympt_3r",
"immSympt_immSympt_4",
"immSympt_immSympt_5r",
"immSympt_immSympt_6",
"immSympt_immSympt_7r",
"infantImmWeak_infantImmWeak_1",
"infantImmWeak_infantImmWeak_2",
"infantImmWeak_infantImmWeak_3",
"infantImmWeak_infantImmWeak_4r",
"overpar_overpar_1r",
"overpar_overpar_2r",
"overpar_overpar_3",
"overpar_overpar_4",
"overpar_overpar_5")

```

```{r}
library(ggplot2)
# df <- read.csv("vb_pilot2.csv")
df <- df[which(df$diseaseRare_check_5==5),]

reverse_items <- all_items[!sapply(
  lapply(all_items, function (x) {
  if (substr(x,nchar(x),nchar(x))=="r") {
    return(x)
  }
}), is.null)]

df[,reverse_items] <- lapply(df[,reverse_items], function(x) {
  8-x
})

df_main <- df[,all_items]
```

# Introduction

This is a notebook for the first pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures. We recruited 100 participants and lost 6 to comprehension checks, leaving 94.

# Item Correlations

Here's a correlation matrix for all individual items. It appears items of some scales are intercorrelating well, though others are weaker. There is also considerable correlation among items across scales--as we might expect.

```{r,fig.height=9,fig.width=9}
library(corrplot)
library(viridis)

corrplot(cor(df_main),
         tl.cex=.65,
         tl.col="black",
         method="color",
         col=viridis(128))
```

Here's another matrix, this time sorted according to a hierarchical clustering algorithm, with bounding rectangles identifying clusters. Whereas we treated these as 15 different scales, this finds just 3 separate clusters. I don't think this is a problem--we expected and even hoped these scales would be correlated with one another.

```{r,fig.height=9,fig.width=9}
corrplot(cor(df_main[,all_items]),
         order="hclust",
         # addrect=3,
         tl.cex=.65,
         tl.col="black",
         method="color",
         col=viridis(128))
```

# Scale Internal Consistency Reliability

Below are computed chronbach's alpha for all scales along with more detailed analyses of scales that are problematic.

## Holistic Balance

```{r}
hb <- c("hb_hb_1",
"hb_hb_2",
"hb_hb_3",
"hb_hb_4")

hb.alpha <- psych::alpha(df[,hb])
hb.alpha$total$raw_alpha
```

## Naturalism

```{r}
nat <- c("nat_nat_1",
"nat_nat_2r",
"nat_nat_3",
"nat_nat_4",
"nat_nat_5")

naturalism.alpha <- psych::alpha(df[,nat])
naturalism.alpha$total$raw_alpha

corrplot(cor(df[,nat]),
         order="alpha",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

```

## Disease Rarity

**NOTE**: we previously scored this one kind of strangely, so it's now been relabeld as "diseaseRare" to indicate that it reflects participants' belief the diseases are extremely rare.

```{r}
diseaseRare <- c("diseaseRare_diseaseRare_1",
"diseaseRare_diseaseRare_2",
"diseaseRare_diseaseRare_3",
"diseaseRare_diseaseRare_4")

diseaseRare.alpha <- psych::alpha(df[,diseaseRare])
diseaseRare.alpha$total$raw_alpha

```

## Disease Severity

Disease severe is now a highly reliable scale (and could even remove an item.)

```{r}
diseaseSevere <- c("diseaseSevere_diseaseSevere_1",
"diseaseSevere_diseaseSevere_2",
"diseaseSevere_diseaseSevere_3",
"diseaseSevere_diseaseSevere_4r",
"diseaseSevere_diseaseSevere_5",
"diseaseSevere_diseaseSevere_6")

diseaseSevere.alpha <- psych::alpha(df[,diseaseSevere])
diseaseSevere.alpha$total$raw_alpha
diseaseSevere.alpha

```
### Diagnosing

Here are histograms of each item

```{r}
library(ggplot2)
library(reshape2)

ggplot(data = melt(df[,diseaseSevere]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
corrplot(cor(df[,diseaseSevere]),
         order="alpha",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

```

## Vaccine Effectiveness

```{r}
vaccEff <- c("vaccEff_vaccEff_1",
"vaccEff_vaccEff_2r",
"vaccEff_vaccEff_3r",
"vaccEff_vaccEff_4")

vaccEff.alpha <- psych::alpha(df[,vaccEff])
vaccEff.alpha$total$raw_alpha
```

## Vaccine Danger

```{r}
vaccDanger <- c("vaccDanger_vaccDanger_1",
"vaccDanger_vaccDanger_2",
"vaccDanger_vaccDanger_3",
"vaccDanger_vaccDanger_4r")

vaccDanger.alpha <- psych::alpha(df[,vaccDanger])
vaccDanger.alpha$total$raw_alpha
```

## Vaccines are toxic

```{r}
vaccTox <- c("vaccTox_vaccTox_1",
"vaccTox_vaccTox_2",
"vaccTox_vaccTox_3",
"vaccTox_vaccTox_4r")

vaccTox.alpha <- psych::alpha(df[,vaccTox])
vaccTox.alpha$total$raw
```

## Medical Skepticism

```{r}
medSkept <- c("medSkept_medSkept_1",
"medSkept_medSkept_2r",
#"medSkept_medSkept_3", # planned to remove
"medSkept_medSkept_4",
"medSkept_medSkept_5",
"medSkept_medSkept_6")

medSkept.alpha <- psych::alpha(df[,medSkept])
medSkept.alpha$total$raw_alpha
medSkept.alpha
```

## Vaccination Intentions

```{r}
vaccIntent <- c("vaccIntent_vaccIntent_1r",
"vaccIntent_vaccIntent_2",
"vaccIntent_vaccIntent_3r",
"vaccIntent_vaccIntent_4",
"vaccIntent_vaccIntent_5r")

vaccIntent.alpha <- psych::alpha(df[,vaccIntent])
vaccIntent.alpha$total$raw_alpha
```

## Parental Expertise

Success!

```{r}
parExpert <- c("parentExpert_parentExpert_1",
"parentExpert_parentExpert_2",
"parentExpert_parentExpert_3",
"parentExpert_parentExpert_4r")

parExpert.alpha <- psych::alpha(df[,parExpert])
parExpert.alpha$total$raw_alpha
parExpert.alpha
```
```{r}
library(ggplot2)
library(reshape2)

ggplot(data = melt(df[,parExpert]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

corrplot(cor(df[,parExpert]),
         order="AOE",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

```

## Infant immune system has limited capacity

Reliability is still weak Might improve if we ditch my new item #5

```{r}
immCap <- c(
  "infantImmLimCap_infantImmLimCap_1",
"infantImmLimCap_infantImmLimCap_2r",
"infantImmLimCap_infantImmLimCap_3",
"infantImmLimCap_infantImmLimCap_4",
"infantImmLimCap_infantImmLimCap_5")

immCap.alpha <- psych::alpha(df[,immCap])
immCap.alpha$total$raw_alpha
immCap.alpha

```

```{r}

library(ggplot2)
library(reshape2)

ggplot(data = melt(df[,immCap]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

corrplot(cor(df[,immCap]),
         order="AOE",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))
```

## Immune system produces cold symptoms

Reliability actually got worse!

```{r}
immSympt <- c("immSympt_immSympt_1",
"immSympt_immSympt_2r",
"immSympt_immSympt_3r",
"immSympt_immSympt_4",
"immSympt_immSympt_5r",
"immSympt_immSympt_6",
"immSympt_immSympt_7r")

immSympt.alpha <- psych::alpha(df[,immSympt])
immSympt.alpha$total$raw_alpha
immSympt.alpha

```

No obvious fixes here -- just a mess.

```{r}
# library(ggplot2)
# library(reshape2)
# 
# ggplot(data = melt(df[,immSympt]), mapping = aes(x = value)) + 
#     geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
# 
# corrplot(cor(df[,immSympt]),
#          order="AOE",
#          tl.cex=.65,
#          tl.col="black",
#          method="color",
#          addCoef.col="black",
#          col=viridis(128))
```

```{r}
library(ggplot2)
library(reshape2)

# ggplot(data = melt(df[,immSympt]), mapping = aes(x = value)) + 
#     geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

corrplot(cor(df[,c(immCap,immWeak)]),
         order="AOE",
         tl.cex=.5,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))
```

## Infants' immune systems are weak

Looks pretty good.

```{r}
immWeak <- c("infantImmWeak_infantImmWeak_1",
"infantImmWeak_infantImmWeak_2",
"infantImmWeak_infantImmWeak_3",
"infantImmWeak_infantImmWeak_4r")

immWeak.alpha <- psych::alpha(df[,immWeak])
immWeak.alpha$total$raw_alpha
immWeak.alpha

```

## Vaccines strain the immune system

Now with five items this makes for a very reliable scale.

```{r}
vaccStrain <- c("vaccStrain_vaccStrain_1",
"vaccStrain_vaccStrain_2r",
"vaccStrain_vaccStrain_3",
"vaccStrain_vaccStrain_4",
"vaccStrain_vaccStrain_5")

# cor(df$immStrain_1,df$immStrain_2r)

vaccStrain.alpha <- psych::alpha(df[,vaccStrain])

vaccStrain.alpha

```

## Overparenting with babies (new scale)

This is a brand new scale so these numbers are ok but probably want this improved. Could be improved slightly by removing item #2.

```{r}
overPar <- c("overpar_overpar_1r",
"overpar_overpar_2r",
"overpar_overpar_3",
"overpar_overpar_4",
"overpar_overpar_5")

# cor(df$immStrain_1,df$immStrain_2r)

overPar.alpha <- psych::alpha(df[,overPar])

overPar.alpha
```

```{r}
ggplot(data = melt(df[,overPar]), mapping = aes(x = value)) + 
    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

corrplot(cor(df[,overPar]),
         order="AOE",
         tl.cex=.65,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))
```

# Scale Distributions

Here I'm computing the scale average for all scales but the "children's weak immune system" scale and the "passive immune system" scale, where I'm making the changes suggested from the reliability analysis. *UPDATE*: Now also changing the "immune system and cold symptoms" scale to remove a bad item.

```{r}
df_scales<-df_main
df_scales$holBalance <- rowMeans(df[,hb])
df_scales$naturalism <- rowMeans(df[,nat])
df_scales$diseaseRare <- rowMeans(df[,diseaseRare])
df_scales$diseaseSevere <- rowMeans(df[,diseaseSevere])
df_scales$vaccEff <- rowMeans(df[,vaccEff])
df_scales$vaccDanger <- rowMeans(df[,vaccDanger])
df_scales$medSkept <- rowMeans(df[,medSkept])
df_scales$vaccIntent <- rowMeans(df[,vaccIntent])
# df_scales$parDuty <- rowMeans(df[,parDuty])
df_scales$parExpert <- rowMeans(df[,parExpert])
df_scales$immCap <- rowMeans(df[,immCap])
df_scales$immSympt <- rowMeans(df[,immSympt])
df_scales$immWeak <- rowMeans(df[,immWeak])
df_scales$vaccStrain <- rowMeans(df[,vaccStrain])
df_scales$vaccTox <- rowMeans(df[,vaccTox])
df_scales$overParenting <- rowMeans(df[,overPar])
```

```{r,fig.height=9,fig.width=9}
library(ggplot2)
library(reshape2)

scale_vars <- c("holBalance",
                "naturalism",
                "diseaseRare",
                "diseaseSevere",
                "vaccEff",
                "vaccDanger",
                "medSkept",
                "vaccIntent", 
                "parExpert",
                "immCap",
                "immSympt",
                "immWeak",
                "vaccStrain",
                "vaccTox",
                "overParenting")

# df_hist <- df_scales[,scale_vars]
plt.hist <- ggplot(data = melt(df_scales[,scale_vars]), mapping = aes(x = value)) + 
    geom_histogram(bins = 14) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)

# ggsave("scale_hists.png",plt.hist)

plt.hist
```

# Scale correlations

Here are intercorrelations among the scales (ordered by angular order of eigenvectors). I think we should use a big grain of salt interpreting any of these because this is all based on just `r nrow(df_scales)` paricipants' data. Nevertheless, let's take a look.

Some of this is expected and some is a bit surprising. Of course once we start taking into account other conditional dependencies, some of these correlations could change, or even reverse sign.

```{r,fig.height=9,fig.width=9}
corrplot(cor(df_scales[,scale_vars]),
         order="hclust",
         tl.cex=1.25,
         tl.col="black",
         method="color",
         addCoef.col="black",
         col=viridis(128))

```

```{r,fig.height=9,fig.width=9}
corrplot(cor(df_scales)[73:87,1:72],
         tl.cex=.65,
         tl.col="black",
         method="color",
         col=viridis(128))
```

```{r}
df_long <- df_scales
df_long$y_val <- df_long$vaccIntent
df_long <- reshape(df_long, idvar="workerId", timevar = "item", direction="long", 
             varying=list(x_val = scale_vars[-8]),
             v.names = c("x_val"))
df_long$item <- factor(df_long$item,
                       levels = seq(1,14,1),
                       labels=scale_vars[-8])

plt.scatter <- ggplot(data = df_long, mapping = aes(x = x_val, y=y_val)) + 
    geom_point(shape=1) + 
  geom_smooth(method="lm", se=FALSE, col=viridis_pal()(5)[3]) + 
  facet_wrap(~item) + 
  xlim(1,7) + ylim(1,7) + labs(y="Vaccine Intent", x="")

ggsave("scale_scatter.png",plt.scatter)
```

### 2018-09-18 pilots/pilot4/vacc_manyBelief_pilot4.Rmd
added files

--- 2018-09-18 pilots/pilot3/vacc_manyBelief_pilot3.Rmd
@@
 ---
-title: "Vaccines: Many Beliefs Pilot 3"
+title: "Vaccines: Many Beliefs Pilot 4"
 author: "Derek Powell"
-date: "June 26, 2017"
+date: "June 30, 2017"
 output: 
@@
 
-filename <- "data/vb_pilot3.csv"
+filename <- "data/vb_pilot4.csv"
 
@@
 df <- df[ , -which(names(df) %in% remove_cols)]
+df <- df[which(df$vaccDanger_check_3==3 & df$hb_check_5==5),]
 ```
@@
 ```{r}
-all_items <- c("hb_hb_1",
-"hb_hb_2",
-"hb_hb_3",
-"hb_hb_4",
-"nat_nat_1",
-"nat_nat_2r",
-"nat_nat_3",
-"nat_nat_4",
-"nat_nat_5",
-"medSkept_medSkept_1",
-"medSkept_medSkept_2r",
-"medSkept_medSkept_3",
-"medSkept_medSkept_4",
-"medSkept_medSkept_5",
-"medSkept_medSkept_6",
-"diseaseRare_diseaseRare_1",
-"diseaseRare_diseaseRare_2",
-"diseaseRare_diseaseRare_3",
-"diseaseRare_diseaseRare_4",
-"diseaseSevere_diseaseSevere_1",
-"diseaseSevere_diseaseSevere_2",
-"diseaseSevere_diseaseSevere_3",
-"diseaseSevere_diseaseSevere_4r",
-"diseaseSevere_diseaseSevere_5",
-"diseaseSevere_diseaseSevere_6",
-"vaccEff_vaccEff_1",
-"vaccEff_vaccEff_2r",
-"vaccEff_vaccEff_3r",
-"vaccEff_vaccEff_4",
-"vaccDanger_vaccDanger_1",
-"vaccDanger_vaccDanger_2",
-"vaccDanger_vaccDanger_3",
-"vaccDanger_vaccDanger_4r",
-"vaccTox_vaccTox_1",
-"vaccTox_vaccTox_2",
-"vaccTox_vaccTox_3",
-"vaccTox_vaccTox_4r",
-"vaccStrain_vaccStrain_1",
-"vaccStrain_vaccStrain_2r",
-"vaccStrain_vaccStrain_3",
-"vaccStrain_vaccStrain_4",
-"vaccStrain_vaccStrain_5",
-"vaccIntent_vaccIntent_1r",
-"vaccIntent_vaccIntent_2",
-"vaccIntent_vaccIntent_3r",
-"vaccIntent_vaccIntent_4",
-"vaccIntent_vaccIntent_5r",
-"parentExpert_parentExpert_1",
-"parentExpert_parentExpert_2",
-"parentExpert_parentExpert_3",
-"parentExpert_parentExpert_4r",
-"infantImmLimCap_infantImmLimCap_1",
-"infantImmLimCap_infantImmLimCap_2r",
-"infantImmLimCap_infantImmLimCap_3",
-"infantImmLimCap_infantImmLimCap_4",
-"infantImmLimCap_infantImmLimCap_5",
-"immSympt_immSympt_1",
-"immSympt_immSympt_2r",
-"immSympt_immSympt_3r",
-"immSympt_immSympt_4",
-"immSympt_immSympt_5r",
-"immSympt_immSympt_6",
-"immSympt_immSympt_7r",
-"infantImmWeak_infantImmWeak_1",
-"infantImmWeak_infantImmWeak_2",
-"infantImmWeak_infantImmWeak_3",
-"infantImmWeak_infantImmWeak_4r",
-"overpar_overpar_1r",
-"overpar_overpar_2r",
-"overpar_overpar_3",
-"overpar_overpar_4",
-"overpar_overpar_5")
+all_items <- c("hb_1",
+"hb_2",
+"hb_3",
+"hb_4",
+"nat_1",
+"nat_2r",
+"nat_3",
+"nat_4",
+"nat_5r",
+"medSkept_1",
+"medSkept_2r",
+"medSkept_3",
+"medSkept_4",
+"medSkept_5r",
+"diseaseRare_1",
+"diseaseRare_2",
+"diseaseRare_3r",
+"diseaseRare_4",
+"diseaseRare_5r",
+"diseaseSevere_1",
+"diseaseSevere_2",
+"diseaseSevere_3r",
+"diseaseSevere_4",
+"diseaseSevere_5r",
+"vaccEff_1",
+"vaccEff_2r",
+"vaccEff_3r",
+"vaccEff_4",
+"vaccDanger_1",
+"vaccDanger_2r",
+"vaccDanger_3",
+"vaccDanger_4r",
+"vaccTox_1r",
+"vaccTox_2",
+"vaccTox_3",
+"vaccTox_4r",
+"vaccStrain_1",
+"vaccStrain_2r",
+"vaccStrain_3",
+"vaccStrain_4r",
+"vaccStrain_5",
+"vaccIntent_1r",
+"vaccIntent_2",
+"vaccIntent_3r",
+"vaccIntent_4",
+"vaccIntent_5r",
+"parentExpert_1",
+"parentExpert_2",
+"parentExpert_3",
+"parentExpert_4r",
+"parentExpert_5r",
+"infantImmLimCap_1",
+"infantImmLimCap_2r",
+"infantImmLimCap_3",
+"infantImmLimCap_4",
+"infantImmLimCap_5r",
+"infantImmWeak_1",
+"infantImmWeak_2",
+"infantImmWeak_3",
+"infantImmWeak_4r",
+"infantImmWeak_5r",
+"overpar_1r",
+"overpar_2",
+"overpar_3",
+"overpar_4",
+"overpar_5r",
+"overpar_6r")
 
@@
 # df <- read.csv("vb_pilot2.csv")
-df <- df[which(df$diseaseRare_check_5==5),]
 
@@
 
-This is a notebook for the first pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures.
-We recruited 100 participants and lost 6 to comprehension checks, leaving 94.
+This is a notebook for the fourth pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures.
+We recruited 100 participants and lost 1 to comprehension checks, leaving 99.
 
@@
 Here's another matrix, this time sorted according to a hierarchical clustering algorithm, with bounding rectangles identifying clusters.
-Whereas we treated these as 15 different scales, this finds just 3 separate clusters.
-I don't think this is a problem--we expected and even hoped these scales would be correlated with one another.
 
@@
 
+# Problem scales
+
 Below are computed chronbach's alpha for all scales along with more detailed analyses of scales that are problematic.
 
-## Holistic Balance
+## Disease Severity
+
+Disease severe is now a weaker scale. I'd wager this is due to our changes, as this used to be highly reliable at $\alpha$  = .86.
 
 ```{r}
-hb <- c("hb_hb_1",
-"hb_hb_2",
-"hb_hb_3",
-"hb_hb_4")
+diseaseSevere <- all_items[20:24]
 
-hb.alpha <- psych::alpha(df[,hb])
-hb.alpha$total$raw_alpha
+diseaseSevere.alpha <- psych::alpha(df[,diseaseSevere])
+diseaseSevere.alpha$total$raw_alpha
+diseaseSevere.alpha
+
 ```
 
-## Naturalism
+### Diagnosing
 
 ```{r}
-nat <- c("nat_nat_1",
-"nat_nat_2r",
-"nat_nat_3",
-"nat_nat_4",
-"nat_nat_5")
+library(ggplot2)
+library(reshape2)
 
-naturalism.alpha <- psych::alpha(df[,nat])
-naturalism.alpha$total$raw_alpha
-
-corrplot(cor(df[,nat]),
-         order="alpha",
+ggplot(data = melt(df[,diseaseSevere]), mapping = aes(x = value)) + 
+    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
+corrplot(cor(df[,diseaseSevere]),
+         order="AOE",
          tl.cex=.65,
@@
 
+## Naturalism
+
+This scale took a hit -- possibly due to the reverse coding? possibly just random variation. It went down from .825 so random variation is possible but seems on the extreme end.
+
+```{r}
+nat <- all_items[5:9]
+
+naturalism.alpha <- psych::alpha(df[,nat])
+naturalism.alpha$total$raw_alpha
+naturalism.alpha
+
+```
+
+## Overparenting with babies (new scale)
+
+This got worse!
+
+```{r}
+# overPar <- all_items[62:67]
+overPar <- c(
+"overpar_2",
+"overpar_3",
+"overpar_4",
+"overpar_5r")
+
+overPar.alpha <- psych::alpha(df[,overPar])
+
+overPar.alpha
+```
+
+### Diagnosing
+
+No clear fixes here, just not doing very well.
+
+```{r}
+ggplot(data = melt(df[,overPar]), mapping = aes(x = value)) + 
+    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
+
+corrplot(cor(df[,overPar]),
+         order="AOE",
+         tl.cex=.65,
+         tl.col="black",
+         method="color",
+         addCoef.col="black",
+         col=viridis(128))
+```
+
+# Acceptable scales
+
+The remaining scales are (within rounding) in the acceptable reliabiltiy range.
+
+## Holistic Balance
+
+This reliability is lower but this scale is unchanged (and a pre-existing scale, so we should leave it alone).
+
+```{r}
+hb <- all_items[1:4]
+
+hb.alpha <- psych::alpha(df[,hb])
+hb.alpha$total$raw_alpha
+```
+
 ## Disease Rarity
 
-**NOTE**: we previously scored this one kind of strangely, so it's now been relabeld as "diseaseRare" to indicate that it reflects participants' belief the diseases are extremely rare.
-
 ```{r}
-diseaseRare <- c("diseaseRare_diseaseRare_1",
-"diseaseRare_diseaseRare_2",
-"diseaseRare_diseaseRare_3",
-"diseaseRare_diseaseRare_4")
+diseaseRare <- all_items[15:19]
 
@@
 
-## Disease Severity
-
-Disease severe is now a highly reliable scale (and could even remove an item.)
-
-```{r}
-diseaseSevere <- c("diseaseSevere_diseaseSevere_1",
-"diseaseSevere_diseaseSevere_2",
-"diseaseSevere_diseaseSevere_3",
-"diseaseSevere_diseaseSevere_4r",
-"diseaseSevere_diseaseSevere_5",
-"diseaseSevere_diseaseSevere_6")
-
-diseaseSevere.alpha <- psych::alpha(df[,diseaseSevere])
-diseaseSevere.alpha$total$raw_alpha
-diseaseSevere.alpha
-
-```
-### Diagnosing
-
-Here are histograms of each item
-
-```{r}
-library(ggplot2)
-library(reshape2)
-
-ggplot(data = melt(df[,diseaseSevere]), mapping = aes(x = value)) + 
-    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
-corrplot(cor(df[,diseaseSevere]),
-         order="alpha",
-         tl.cex=.65,
-         tl.col="black",
-         method="color",
-         addCoef.col="black",
-         col=viridis(128))
-
-```
-
 ## Vaccine Effectiveness
@@
 ```{r}
-vaccEff <- c("vaccEff_vaccEff_1",
-"vaccEff_vaccEff_2r",
-"vaccEff_vaccEff_3r",
-"vaccEff_vaccEff_4")
+vaccEff <- all_items[25:28]
 
@@
 ```{r}
-vaccDanger <- c("vaccDanger_vaccDanger_1",
-"vaccDanger_vaccDanger_2",
-"vaccDanger_vaccDanger_3",
-"vaccDanger_vaccDanger_4r")
+vaccDanger <- all_items[29:32]
 
@@
 ```{r}
-vaccTox <- c("vaccTox_vaccTox_1",
-"vaccTox_vaccTox_2",
-"vaccTox_vaccTox_3",
-"vaccTox_vaccTox_4r")
+vaccTox <- all_items[33:36]
 
@@
 
+This is just barely making the grade now. Removing 5r would improve the reliability. I thought the phrasing of that item was a bit awkward after reverse coding, so maybe it can be fixed.
+
 ```{r}
-medSkept <- c("medSkept_medSkept_1",
-"medSkept_medSkept_2r",
-#"medSkept_medSkept_3", # planned to remove
-"medSkept_medSkept_4",
-"medSkept_medSkept_5",
-"medSkept_medSkept_6")
+medSkept <- all_items[10:14]
 
@@
 medSkept.alpha
+
+corrplot(cor(df[,medSkept]),
+         order="alpha",
+         tl.cex=.65,
+         tl.col="black",
+         method="color",
+         addCoef.col="black",
+         col=viridis(128))
 ```
@@
 ```{r}
-vaccIntent <- c("vaccIntent_vaccIntent_1r",
-"vaccIntent_vaccIntent_2",
-"vaccIntent_vaccIntent_3r",
-"vaccIntent_vaccIntent_4",
-"vaccIntent_vaccIntent_5r")
+vaccIntent <- all_items[42:46]
 
@@
 
-Success!
+Success! Reliability is very solid.
 
 ```{r}
-parExpert <- c("parentExpert_parentExpert_1",
-"parentExpert_parentExpert_2",
-"parentExpert_parentExpert_3",
-"parentExpert_parentExpert_4r")
+parExpert <- all_items[47:51]
 
@@
 ```
+
+Looks a little two-dimensional though. Items 4 and 5 are both about trusing doctors' advice, so I suppose it's not surprising they hang together even more strongly.
+
 ```{r}
@@
 
-Reliability is still weak Might improve if we ditch my new item #5
+Reliability is now very good.
 
 ```{r}
-immCap <- c(
-  "infantImmLimCap_infantImmLimCap_1",
-"infantImmLimCap_infantImmLimCap_2r",
-"infantImmLimCap_infantImmLimCap_3",
-"infantImmLimCap_infantImmLimCap_4",
-"infantImmLimCap_infantImmLimCap_5")
+immCap <- all_items[52:56]
 
@@
 
-```{r}
+## Infants' immune systems are weak
 
-library(ggplot2)
-library(reshape2)
-
-ggplot(data = melt(df[,immCap]), mapping = aes(x = value)) + 
-    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
-
-corrplot(cor(df[,immCap]),
-         order="AOE",
-         tl.cex=.65,
-         tl.col="black",
-         method="color",
-         addCoef.col="black",
-         col=viridis(128))
-```
-
-## Immune system produces cold symptoms
-
-Reliability actually got worse!
+Looks good!
 
 ```{r}
-immSympt <- c("immSympt_immSympt_1",
-"immSympt_immSympt_2r",
-"immSympt_immSympt_3r",
-"immSympt_immSympt_4",
-"immSympt_immSympt_5r",
-"immSympt_immSympt_6",
-"immSympt_immSympt_7r")
-
-immSympt.alpha <- psych::alpha(df[,immSympt])
-immSympt.alpha$total$raw_alpha
-immSympt.alpha
-
-```
-
-No obvious fixes here -- just a mess.
-
-```{r}
-# library(ggplot2)
-# library(reshape2)
-# 
-# ggplot(data = melt(df[,immSympt]), mapping = aes(x = value)) + 
-#     geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
-# 
-# corrplot(cor(df[,immSympt]),
-#          order="AOE",
-#          tl.cex=.65,
-#          tl.col="black",
-#          method="color",
-#          addCoef.col="black",
-#          col=viridis(128))
-```
-
-```{r}
-library(ggplot2)
-library(reshape2)
-
-# ggplot(data = melt(df[,immSympt]), mapping = aes(x = value)) + 
-#     geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
-
-corrplot(cor(df[,c(immCap,immWeak)]),
-         order="AOE",
-         tl.cex=.5,
-         tl.col="black",
-         method="color",
-         addCoef.col="black",
-         col=viridis(128))
-```
-
-## Infants' immune systems are weak
-
-Looks pretty good.
-
-```{r}
-immWeak <- c("infantImmWeak_infantImmWeak_1",
-"infantImmWeak_infantImmWeak_2",
-"infantImmWeak_infantImmWeak_3",
-"infantImmWeak_infantImmWeak_4r")
+immWeak <- all_items[57:61]
 
@@
 ```{r}
-vaccStrain <- c("vaccStrain_vaccStrain_1",
-"vaccStrain_vaccStrain_2r",
-"vaccStrain_vaccStrain_3",
-"vaccStrain_vaccStrain_4",
-"vaccStrain_vaccStrain_5")
+vaccStrain <- all_items[37:41]
 
@@
 
-```
-
-## Overparenting with babies (new scale)
-
-This is a brand new scale so these numbers are ok but probably want this improved. Could be improved slightly by removing item #2.
-
-```{r}
-overPar <- c("overpar_overpar_1r",
-"overpar_overpar_2r",
-"overpar_overpar_3",
-"overpar_overpar_4",
-"overpar_overpar_5")
-
-# cor(df$immStrain_1,df$immStrain_2r)
-
-overPar.alpha <- psych::alpha(df[,overPar])
-
-overPar.alpha
-```
-
-```{r}
-ggplot(data = melt(df[,overPar]), mapping = aes(x = value)) + 
-    geom_histogram(bins = 7) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
-
-corrplot(cor(df[,overPar]),
-         order="AOE",
-         tl.cex=.65,
-         tl.col="black",
-         method="color",
-         addCoef.col="black",
-         col=viridis(128))
 ```
@@
 df_scales$immCap <- rowMeans(df[,immCap])
-df_scales$immSympt <- rowMeans(df[,immSympt])
+# df_scales$immSympt <- rowMeans(df[,immSympt])
 df_scales$immWeak <- rowMeans(df[,immWeak])
@@
                 "immCap",
-                "immSympt",
                 "immWeak",
@@
 plt.hist <- ggplot(data = melt(df_scales[,scale_vars]), mapping = aes(x = value)) + 
-    geom_histogram(bins = 14) + facet_wrap(~variable, scales = 'free_x') + xlim(1,7)
+    geom_histogram(bins = 14) + facet_wrap(~variable) + xlim(1,7)
 
@@
 
-```{r,fig.height=9,fig.width=9}
-corrplot(cor(df_scales)[73:87,1:72],
-         tl.cex=.65,
-         tl.col="black",
-         method="color",
-         col=viridis(128))
-```
-
 ```{r}
@@
 df_long$item <- factor(df_long$item,
-                       levels = seq(1,14,1),
+                       levels = seq(1,13,1),
                        labels=scale_vars[-8])
@@
 
-ggsave("scale_scatter.png",plt.scatter)
+# ggsave("scale_scatter.png",plt.scatter)
+plt.scatter
 ```
+
+# Coefficient $\omega$ reliability
+
+Coefficient $\alpha$ has a number of well-known problems, not the least of which it is often biased (either under or over-estimating).
+Most people who know now recommend the use of coeffiicent $\omega$, because it is unbiased and also readily interpretable: $\omega$ represents the proportion of variance in scale scores accounted for by the latent factor.
+
+Here I'm calculating robust $\omega$ using the coefficientalpha package. A (non-robust?) implementation is also available in the psych package that relies on an SEM package.
+
+If $\omega$ is to be trusted it looks like the bias in $\alpha$ is leading to an underestimate of the reliability of most scales.
+
+## Naturalism
+
+```{r}
+coefficientalpha::omega(df[,nat])
+```
+
+## DiseaseSeverity
+
+```{r}
+coefficientalpha::omega(df[,diseaseSevere])
+```
+
+## Over-parenting
+
+Still poor.
+
+```{r}
+coefficientalpha::omega(df[,overPar])
+```
+
+## Medical skepticism
+
+```{r}
+coefficientalpha::omega(df[,medSkept])
+```
+
+## Disease Rarity
+
+```{r}
+coefficientalpha::omega(df[,diseaseRare])
+```

### 2018-09-18 pilots/pilot5/vacc_manyBelief_pilot5.Rmd
added files

--- 2018-09-18 pilots/pilot4/vacc_manyBelief_pilot4.Rmd
@@
 ---
-title: "Vaccines: Many Beliefs Pilot 4"
+title: "Vaccines: Many Beliefs Pilot 5"
 author: "Derek Powell"
-date: "June 30, 2017"
+date: "July 14, 2017"
 output: 
@@
 
-filename <- "data/vb_pilot4.csv"
+filename <- "data/vb_pilot5.csv"
 
@@
 "nat_4",
-"nat_5r",
+"nat_5",
+"nat_6r",
 "medSkept_1",
@@
 "medSkept_5r",
+"medSkept_6r",
 "diseaseRare_1",
@@
 "diseaseSevere_5r",
+"diseaseSevere_6",
 "vaccEff_1",
@@
 "infantImmWeak_5r",
-"overpar_1r",
+"overpar_1",
 "overpar_2",
 "overpar_3",
-"overpar_4",
-"overpar_5r",
-"overpar_6r")
+"overpar_4r",
+"overpar_5r")
 
@@
 
-This is a notebook for the fourth pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures.
-We recruited 100 participants and lost 1 to comprehension checks, leaving 99.
+This is a notebook for the fifth pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures.
+We recruited 100 participants and lost 4 to comprehension checks, leaving 96.
 
@@
 
-Disease severe is now a weaker scale. I'd wager this is due to our changes, as this used to be highly reliable at $\alpha$  = .86.
+Our changes to disease severity did not help at all and in fact hurt the reliability of the scale even with an additional item.
+I think we really need to iron out the issues in this scale, whether that means returning to the original or making new changes.
 
 ```{r}
-diseaseSevere <- all_items[20:24]
+diseaseSevere <- all_items[22:27]
+diseaseSevere <- c("diseaseSevere_1",
+"diseaseSevere_2",
+"diseaseSevere_3r",
+"diseaseSevere_4",
+"diseaseSevere_5r",
+"diseaseSevere_6")
 
@@
 
-This scale took a hit -- possibly due to the reverse coding? possibly just random variation. It went down from .825 so random variation is possible but seems on the extreme end.
+This scale improved very slightly, looks like we can remove either 5 or 6r and retain an alpha of .78.
+Since removing 6r makes this basically the original scale I think we can say that the difference between that score (.78) and the .825 it scored earlier is essentially just noise.
+As a spoiler, I looked at the consistency in the alpha scores for the unchanged scales (n=10) across pilot 4 and 5.
+The average absolute difference was .021 and the SD of the differences was .025.
+So I guess that makes me less interested in reading into changes or differences smaller than those values, and we should only really be struck by changes greater than .049 or so.
 
 ```{r}
-nat <- all_items[5:9]
+nat <- all_items[5:10]
 
@@
 
-This got worse!
+This improved considerably, though it's still a tad low. Looks like item 4r is weak.
 
 ```{r}
-# overPar <- all_items[62:67]
-overPar <- c(
-"overpar_2",
-"overpar_3",
-"overpar_4",
-"overpar_5r")
+overPar <- all_items[65:69]
 
@@
 
-No clear fixes here, just not doing very well.
+Items 3 and 4r really don't correlate.
 
@@
 
-This reliability is lower but this scale is unchanged (and a pre-existing scale, so we should leave it alone).
+In pilot 4 the reliability of this was just below threshold, here it's just above.
 
@@
 ```{r}
-diseaseRare <- all_items[15:19]
+diseaseRare <- all_items[17:21]
 
@@
 ```{r}
-vaccEff <- all_items[25:28]
+vaccEff <- all_items[28:31]
 
@@
 ```{r}
-vaccDanger <- all_items[29:32]
+vaccDanger <- all_items[32:35]
 
@@
 ```{r}
-vaccTox <- all_items[33:36]
+vaccTox <- all_items[36:39]
 
@@
 
-This is just barely making the grade now. Removing 5r would improve the reliability. I thought the phrasing of that item was a bit awkward after reverse coding, so maybe it can be fixed.
+This is just making the grade now and looks like we are safe to remove 5r without harming reliability, though I think it's kind of an important part of the idea.
+So maybe we are left to choose between a 5 item scale and a scale with that item included.
 
 ```{r}
-medSkept <- all_items[10:14]
+medSkept <- all_items[11:16]
 
@@
 ```{r}
-vaccIntent <- all_items[42:46]
+vaccIntent <- all_items[45:49]
 
@@
 ```{r}
-parExpert <- all_items[47:51]
+parExpert <- all_items[50:54]
 
@@
 ```{r}
-immCap <- all_items[52:56]
+immCap <- all_items[55:59]
 
@@
 ```{r}
-immWeak <- all_items[57:61]
+immWeak <- all_items[60:64]
 
@@
 ```{r}
-vaccStrain <- all_items[37:41]
+vaccStrain <- all_items[40:44]
 
@@
 
+Still doesn't make the grade according to omega
 ```{r}
@@
 
-Still poor.
+Makes the grade according to omega
 
@@
 ```
+
+# Comparing studies
+
+As mentioned in the naturalism scale section, I looked at the consistency in the alpha scores for the unchanged scales (n=10) across pilot 4 and 5.
+The average absolute difference was .021 and the SD of the differences was .025.
+So I guess that makes me less interested in reading into changes or differences smaller than those values, and we should only really be struck by changes greater than .049 or so.
+The alpha values correlate at *r* = .89 across studies.

### 2018-09-18 pilots/pilot6/vacc_manyBelief_pilot6.Rmd
added files

---
title: "Vaccines: Many Beliefs Pilot 5"
author: "Derek Powell"
date: "July 14, 2017"
output: 
  html_notebook: 
    code_folding: hide
---

```{r}

filename <- "data/vb_pilot6.csv"

headers <- as.matrix(read.csv(filename, skip = 0, header = F, nrows = 1, as.is = T ))
df <- read.csv(filename, skip = 3, header = F)
colnames(df) <- headers

df <- df[which(df$Status==0),] # remove survey previews

# remove unused qualtrics variables
remove_cols <- c("RecipientLastName",
                 "RecipientFirstName",
                 "RecipientEmail",
                 "Finished",
                 "ResponseId",
                 "ExternalReference",
                 "DistributionChannel",
                 "UserLanguage",
                 "Status")

df <- df[ , -which(names(df) %in% remove_cols)]
df <- df[which(df$diseaseRarity_check_3==3),]
```

```{r}
all_items <- c("diseaseSevere_1",
"diseaseSevere_2",
"diseaseSevere_3r",
"diseaseSevere_4",
"diseaseSevere_5r",
"diseaseSevere_6",
"diseaseSevere_7",
"diseaseSevere_8r",
"diseaseSevere_9r",
"diseaseSevere_10",
"diseaseSevere_11",
"diseaseSevere_12r",
"diseaseSevere_13r",
"diseaseSevere_14r",
"diseaseSevere_15r",
"diseaseSevere_16r",
"diseaseSevere_17",
"diseaseRarity_1",
"diseaseRarity_2",
"diseaseRarity_3r",
"diseaseRarity_4",
"diseaseRarity_5r",
"vaccIntent_1r",
"vaccIntent_2",
"vaccIntent_3r",
"vaccIntent_4",
"vaccIntent_5r")

```

```{r}
library(ggplot2)
# df <- read.csv("vb_pilot2.csv")

reverse_items <- all_items[!sapply(
  lapply(all_items, function (x) {
  if (substr(x,nchar(x),nchar(x))=="r") {
    return(x)
  }
}), is.null)]

df[,reverse_items] <- lapply(df[,reverse_items], function(x) {
  8-x
})

df_main <- df[,c("workerId",all_items)]

```

# Introduction

This is a notebook for the 6th pilot experiment of our (Kara, Ellen, and Derek) first pilot experiment examining vaccine theories using multiple attitude measures. We recruited 120 and are left with 113.

This pilot is specifically targetted at fixing our issues with reliability for disease severity scale.

I'm splitting this data evenly into training and validation sets. The plan is to pick several candidate scales based on the "training" data and then ensure it remains reliable when tested on the validation set.

```{r}

library(dplyr)
train <- df_main %>% sample_frac(.5)
test  <- dplyr::anti_join(df_main, train, by = 'workerId')

# train <- train[, all_items]
```

## Disease Severity

Here's a correlation plot of all items sorted by hierarchical clustering.

Looks like 2,4,7 are closely tied together. ALso, 15r, 8r, 16r and 17, 1, 11

```{r}
diseaseSevere <- all_items[1:17]
# diseaseSevere <-

# diseaseSevere.alpha <- psych::alpha(df[,diseaseSevere])
# diseaseSevere.alpha$total$raw_alpha
# diseaseSevere.alpha \

corrplot(cor(train[,diseaseSevere]),
         order="hclust",
         # addrect=3,
         tl.cex=.65,
         tl.col="black",
         method="color",
         col=viridis(128))

```

## proposed scales

1. Items 2, 4, 7, 8r, 16r.
2. Items 1, 4, 7, 8r, 3r.
3. Items 4, 8r, 16r, 15r,  11
5. Items 3r, 4, 7, 8r, 11 
4. Items 1, 3r, 4, 9r, 11, 17 (6 items)

### Scale 1

1. Whooping cough often makes you sick for months. 
1. Childhood diseases are serious diseases.
1. Diseases like measles, mumps, and whooping cough can cause permanent damage to a child who contracts them.
1. Childhood diseases are not that big a deal.*
1. Measles, mumps, and whooping cough are mild enough that they don’t really deserve to be called “diseases.”*

```{r}
s1 <- all_items[c(2,4,7,8,16)]

s1.alpha <- psych::alpha(train[,s1])
s1.alpha$total$raw_alpha
s1.alpha
```

### Scale 2

1.  Measles can be life-threatening.
1. Childhood diseases are serious diseases.
1. Diseases like measles, mumps, and whooping cough can cause permanent damage to a child who contracts them.
1. Childhood diseases are not that big a deal.*
1. Measles, mumps, and whooping cough are no more severe than the flu.*

```{r}
s2 <- all_items[c(1,4,7,8,3)]

s2.alpha <- psych::alpha(train[,s2])
s2.alpha$total$raw_alpha
s2.alpha
```

### Scale 3

1. Childhood diseases are serious diseases.
1. Childhood diseases are not that big a deal.*
1.Whooping cough is much like any other cough.*
1. Measles, mumps, and whooping cough are mild enough that they don’t really deserve to be called “diseases.”*
1. Diseases like measles and whooping cough are extremely dangerous for young children.

```{r}
s3 <- all_items[c(4,8,16,15,11)]

s3.alpha <- psych::alpha(train[,s3])
s3.alpha$total$raw_alpha
s3.alpha
```

### Scale 4

1. Measles, mumps, and whooping cough are no more severe than the flu.*
4. Childhood diseases are serious diseases.
7. Diseases like measles, mumps, and whooping cough can cause permanent damage to a child who contracts them.
8. Childhood diseases are not that big a deal.*
11. Diseases like measles and whooping cough are extremely dangerous for young children.

```{r}
s4 <- all_items[c(3,4,7,8,11)]

s4.alpha <- psych::alpha(train[,s4])
s4.alpha$total$raw_alpha
s4.alpha
```

###  Scale 5

1. Measles can be life-threatening.
3. Measles, mumps, and whooping cough are no more severe than the flu.*
4. Childhood diseases are serious diseases.
9. A child getting measles might be a hassle, but it would not be a cause for serious concern.*
11. Diseases like measles and whooping cough are extremely dangerous for young children.
17. Measles and whooping cough can be just as deadly as Polio.

```{r}
s5 <- all_items[c(1, 3, 4, 9, 11, 17)]

s5.alpha <- psych::alpha(train[,s5])
s5.alpha$total$raw_alpha
s5.alpha
```

# Validation

Now we'll test all 5 on the validation set and see how great the loss of reliability is.

```{r}
s1 <- all_items[c(2,4,7,8,16)]

s1.alpha <- psych::alpha(test[,s1])
s1.alpha$total$raw_alpha
s1.alpha
```

```{r}
s2 <- all_items[c(1,4,7,8,3)]

s2.alpha <- psych::alpha(test[,s2])
s2.alpha$total$raw_alpha
# s2.alpha
```

```{r}
s3 <- all_items[c(4,8,16,15,11)]

s3.alpha <- psych::alpha(test[,s3])
s3.alpha$total$raw_alpha
s3.alpha
```

```{r}
s4 <- all_items[c(3,4,7,8,11)]

s4.alpha <- psych::alpha(test[,s4])
s4.alpha$total$raw_alpha
s4.alpha
```

```{r}
s5 <- all_items[c(1, 3, 4, 9, 11, 17)]

s5.alpha <- psych::alpha(test[,s5])
s5.alpha$total$raw_alpha
s5.alpha
```

## Result

All are acceptably reliable! Scale 3 has the highest reliability at validation (and 95% confidence intervals don't go below .80), but I think we can feel reasonably safe picking from among these scales (and possibly recombining items).

### 2018-09-18 study1/custom-structure-learning-vaccData.Rmd
added files

---
title: "Vaccine data modeling: Custom MCMC solution"
output: 
  html_notebook: 
    code_folding: hide
---

In this notebook I'll do all the modeling for study 1. I will use my custom scoring method with BiDAG to do MCMC search for a structure across the space of DAGs. I'll do a few searches, imposing different top-down theory/constraints. In each case, we'll inspect the MAP dag and the posterior probability of edges.

My approach will be to searching for an underlying cognitive model. For each family, the responses are treated as generated from a cognitive model, as reports of the credence in the states of affairs represented by each variable.

Unpacking that a bit more, the idea is that participants share a mental model of some set of states of affairs (SOAs), that is, how the states of affairs relate or go together. The relations between SOAs can be represented by conditional probability table. To estimate this CPT, I further assume these CPTS can themselves be captured by a canonical distribution--in this case, something I'm calling noisy-or-nor (needs a better name). Noisy-or-nor assumes that each parent has an __independent__ generating or preventing influence on the child node. The probability of the child is the probability that it is generated (either by one of its generating parents, or a implied "leak" variable) and that none of its preventers prevent it. This is based on work by Lu & Yuille, and draws on a common set of assumptions in causal learning literature. The essential feature of this CPD is that __it assumes independent influences of each parent on the child__--this is necessary in order to estimate the parameters of the CPD from reports of the marginal probability of each SOA.

```{r}
source("vacc_import_data.R", chdir = TRUE)
```

```{r}
# detach("package:BiDAG", unload=TRUE)

library(tidyverse)
library(BiDAG)
# BiDAG depends on 'graph' package, source: http://www.bioconductor.org/packages/release/bioc/html/graph.html
# BiDAG depends on 'RBGL' package, source: https://bioconductor.org/packages/release/bioc/html/RBGL.html
library(bnlearn)
library(HydeNet)
library(gtools)

# source("cog-model-graph-tools.R")
source("../scripts/custom-structure-learning/cog-model-main.R")
source("../scripts/gmod_tools.R")
source("../scripts/bnTheoryBlacklist.R")

# # customize BiDAG functions
# orig_DAGcorescore <- BiDAG:::DAGcorescore # save to switch back if desired
# orig_TableDAGscore.alias <- BiDAG:::TableDAGscore.alias # save to switch back if desired

```

# Set up data

Participants responses were scaled from a 1 to 7 rating scale onto the open interval (0,1). We scaled these responses as recommended by [cite beta regression paper]. After scaling, we interpret these responses as indicating participants' credence in each belief--that is, the marginal probability they assign to the state of affairs described by the scale.

```{r}
# rescale beta

rescale_beta <- function(x, lower, upper) {
  # rescales onto the open interval (0,1)
  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"

  N <- length(x)
  res <- (x - lower) / (upper - lower)
  res <- (res * (N - 1) + .5) / N

  return(as.vector(res))
}

d_bn_scaled <- d_bn %>%
 mutate_all(function(x){rescale_beta(x,-3,3)})

## set the seed to make your partition reproductible
set.seed(123)
trainInd <- sample(seq_len(nrow(d_bn_scaled)), size = floor(nrow(d_bn_scaled)*.80))

train <- d_bn_scaled[trainInd, ]
test <- d_bn_scaled[-trainInd, ]
```

## Define search spaces

Initialize search space. Perform initial pruning of search space using PC algorithm. This step does not respect cognitive model assumptions. Generally, this is a heuristic step needed to get the process off the ground.

In addition to the basic level of streamlining needed, we also impose different "blacklists" to constrain the search according to theory. These different blacklists apply our "generative model" assumption with different degrees of specificity. This can (might?) help us probe where our assumptions are driving findings, versus the kinds of findings that are emerging directly out of the data.

```{r}
# run to compute scoretables
# takes a few minutes if not computing scoretables ...
# takes a long time (10 hours ish) if scoretables must be computed ...

compute_scoretables <- FALSE # uncomment to recompute scoretables
source("fit-cog-models.R")

```

```{r}
nCores <- parallel::detectCores(logical=TRUE)

# load scoretables computed by fit-cog-models.R

scoretables <- list(
  readRDS("scoretable-unconstrained.rds"),
  readRDS("scoretable-intent_is_dv.rds"),
  readRDS("scoretable-abstract_are_parents.rds"),
  readRDS("scoretable-abstract_are_parents_intent_dv.rds"),
  readRDS("scoretable-theoryBasedHierarchy.rds")
  )

# # DO MCMC - comment to skip and load saved results
# all_results <- list(list(), list(), list(), list(), list())
# 
# customize_BiDAG() # customize bidag!
# 
# for (i in 1:length(startspaces)) {
#   all_results[[i]] <- parallel_orderMCMC(train,
#                                        startspaces[[i]],
#                                        scoretables[[i]],
#                                        MAP = FALSE, # might error
#                                        1e6,
#                                        100,
#                                        blacklist = blacklists[[i]],
#                                        chains = 4,
#                                        cores = 4
#                                        )
# 
# }
# 
# reinit_BiDAG() # set it back!

# saveRDS(all_results, "allresults.rds")

all_results <- readRDS("allresults.rds")
```

## For all four

Now let's do this for all five models ...

```{r}

plots <- list()
all_edge_df <- data.frame()

for (i in 1:5) {
  chains <- all_results[[i]]
  merged_chain <- merge_chains(chains)
  map_dag <- extract_mapdag(merged_chain)

  h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(map_dag)))
  plots[[i]] <- plot(h)

  edge_posterior <- edges.posterior(merged_chain$incidence, pdag=FALSE)
  rownames(edge_posterior) <- nodes
  colnames(edge_posterior) <- nodes

  edge_df <- reshape::melt(edge_posterior) %>%
    rename(x = X1, y = X2) %>%
    mutate(constraints = i)
  all_edge_df <- bind_rows(all_edge_df, edge_df)
}

```

NOTE: chains did not converge for #2, intent as DV ...

```{r}
print("unconstrained")
plots[[1]] # intent is dv
print("intent is dv")
plots[[2]] # intent is dv
print("hb + naturalism are parents")
plots[[3]] # hb + naturalism are parents
print("hb + naturalism are parents, intent is dv")
plots[[4]] # hb + naturalism are parents, intent is dv
print("full abstraction hierarchy")
plots[[5]] # full abstraction hierarchy
```

```{r, fig.align="center", fig.width=8, fig.height=8}
all_edge_df %>%
  mutate(constraints = factor(constraints, 
                              levels = c(1,2,3,4,5), 
                              labels = c("unconstrained",
                                "intent is dv", 
                                         "hb + nat are abstract", 
                                         "intent is dv\nand hb+nat are parents", 
                                         "theory based"))
         ) %>%
  ggplot(aes(x=x, y=y, fill=value)) +
  geom_tile() +
  facet_wrap(~constraints) +
  scale_fill_viridis_c(option="C") +
  theme_minimal() +
  theme(aspect.ratio=1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=.5)) +
  labs(x = "From", y = "To", title="Edge posterior probabilities", fill="p(edge)") 
```

Comparing posteriors ...

The code below can be used to compare the posterior edge probabilities under different constraints. It's still a bit tricky to get a sense of, but this gives the answer more or less ...

```{r}
all_edge_df %>%
  spread(constraints, value) %>%
  mutate(diff = `2`-`1`) %>% # which to compare ...
  ggplot(aes(x=x, y=y, fill=diff)) +
  geom_tile() +
  # facet_wrap(~constraints) +
  scale_fill_viridis_c(option="C") +
  theme_minimal() +
  theme(aspect.ratio=1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=.5)) +
  labs(x = "From", y = "To", title="Edge posterior prob. diffs", fill="prob. diff") 
```

## Impressions

workign?

# Focusing in ...

Using theory-based model ...

Extract results and plot a traceplot. For unconstrained search, chains did not all converge

```{r}

BiDAG_traceplot(all_results[[1]], hide = 1, show_chains=c(1,2,3,4))
# BiDAG_traceplot(all_results[[3]], hide = 100, show_chains=c(3,4))
```

plot map dag

```{r}
merged_chains <- merge_chains(all_results[[1]][2:4])
map_dag <- extract_mapdag(merged_chains)

h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(map_dag)))
plot(h)
```

plot posterior

```{r}
edge_posterior <- edges.posterior(merged_chains$incidence, pdag=FALSE)
rownames(edge_posterior) <- nodes
colnames(edge_posterior) <- nodes

edge_df <- reshape::melt(edge_posterior) %>%
  rename(x = X1, y = X2)

edge_df %>%
  ggplot(aes(x=x, y=y, fill=value)) +
  geom_tile() +
  scale_fill_viridis_c(option="C") +
  theme_minimal() +
  theme(aspect.ratio=1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=.5)) +
  labs(x = "From", y = "To", title="Edge posterior probabilities", fill="p(edge)") 
```

## Predictions

Now we do one-node held-out prediction as I have in the past.

```{r}
# this now takes ~20 minutes or so
model_string <- suppressWarnings(write_jags_model(map_dag, train))
cat(model_string)
```

```{r}
# takes about 20-30 min
start_time <- Sys.time()

# test2 <- test
predictions <- test %>% mutate_all(function(x){NA}) %>% mutate_all(as.numeric)
# net.fit <- bn.fit(map_dag, train)

for (targVar in names(test)) {
  tempDF <- test
  tempDF[[targVar]] <- NA
  tempDF[[targVar]] <- as.numeric(tempDF[[targVar]])

  # imputed <- impute(net.fit, tempDF, method="bayes-lw")
  imputed <- make_predictions(model_string, test, nodes_to_predict = targVar)
  predictions[[targVar]] <- imputed[[targVar]]
}

predictions <- predictions %>% gather(varName, predValue)
test_analyze <- test %>% gather(varName, value) %>% bind_cols(predictions) %>% select(varName, value, predValue)

print(Sys.time() - start_time)
```

```{r}
library(ggthemes)

predObsCor <- cor(test_analyze$value,test_analyze$predValue)

corrDF <- test_analyze %>%
  group_by(varName) %>%
  summarize(cor = cor(value,predValue)) %>%
  mutate(cor = format(round(cor,2),nsmall=2))

plt.valid <- test_analyze %>%
  ggplot(aes(x=predValue, y=value)) + 
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha=.33) +
  geom_point(shape=1, size=.5, color="darkturquoise") + 
  geom_text(data=corrDF, aes(label=paste("r =", cor)),
            x=-Inf, y=Inf, hjust=-0.12, vjust=1.4,
            size = 10*.352777778,
            color="grey25") +
  # geom_smooth(method="lm") +
  theme_bw(base_size = 10) +
  theme(strip.background = element_rect(fill="grey90"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  coord_fixed() + 
  facet_wrap(~varName, nrow=2) + 
  scale_x_continuous("Predicted values", limits = c(0, 1)) +
  scale_y_continuous("Observed values", limits = c(0, 1))

plt.valid
```

### 2018-09-18 study1/vacc-manybelief-bidag.Rmd
added files

---
title: "Vaccine Manybeliefs - bidag"
date: August 6, 2018
output:
  html_notebook: 
    code_folding: hide
---

This notebook examines the use of Bayesian graphical model structure learning using the new R package `BiDAG` ( [CRAN LINK](https://cran.r-project.org/web/packages/BiDAG/index.html) ). This package implements two MCMC algorithms for searching the space of DAGs, "partition mcmc" and "order mcmc". Partition MCMC is a more recent development, and reportedly performs slightly better. Both methods require decomposable scoring functions and both can also get too complex with large numbers of variables. To avoid this, before sampling the package seeks to constrain the search space using the pc algorithm (by default). Our networks are relatively small, so we don't have to be very aggressive in constraining the search space.

First, I load in data and split into training and testing splits

```{r, include=FALSE}
source("vacc_import_data.R", chdir = TRUE)

# library(BDgraph)
library(bnlearn)
library(tidyverse)
# library(modelr)
# library(stringr)
library(viridis)
library(multidplyr) # source: https://github.com/hadley/multidplyr
library(parallel)
library(BiDAG) 
# BiDAG depends on 'graph' package, source: http://www.bioconductor.org/packages/release/bioc/html/graph.html
# BiDAG depends on 'RBGL' package, source: https://bioconductor.org/packages/release/bioc/html/RBGL.html
```

```{r}
# Here we'll split our d_bn data into a training and test split

## set the seed to make your partition reproductible
set.seed(123)
trainInd <- sample(seq_len(nrow(d_bn)), size = floor(nrow(d_bn)*.80))

train <- d_bn[trainInd, ]
test <- d_bn[-trainInd, ]
```

## Bayesian structure search with MCMC

Here we'll do bayesian structure search with MCMC. Here's a run with more-or-less `BiDAG` defaults, except a higher alpha value in the pc stage, to allow exploration of more of the space.

```{r}
mcmc_samples <- 1e5

scoreparam <- scoreparameters(ncol(train), scoretype = "bge", data = train)

# I think the default search space restriction is too severe, at least when we have so few variables
searchSpace <- iterativeMCMCsearch(
  ncol(train),
  scoreparam = scoreparam,
  scoreout = TRUE,
  alpha = .4
)

res <- orderMCMC(
  ncol(train), 
  startspace = searchSpace$space$adjacency,
  plus1 = FALSE,
  scoreparam = scoreparam, 
  iterations = mcmc_samples,
  chainout = TRUE, # orderMCMC only
  scoreout = TRUE, # orderMCMC only
  # MAP = FALSE, # this breaks iterations/stepsave arguments for some reason?
  stepsave = 10
  )
```

Do a traceplot of DAG scores ...

```{r}
scoreChain <- unlist(res$chain$DAGscores)
plot(scoreChain,  type = "l" )

# res_uc <- res # save for later
```

From this sample of the posterior, we can identify the Maximum A-Posteriori (MAP) graph.

```{r}
map_score <- max(scoreChain)
map_index <- match(map_score, scoreChain)

map_adj <- res$chain$incidence[map_index]
```

And we can turn that object into a `bnlearn` object. I first check on the undirected edges in the _cpdag_. Then plot the MAP dag using HydeNet/graphviz.

```{r}
library(bnlearn)
library(HydeNet)
source("../Scripts/gmod_tools.R")

map_dag <- adjacency2dag(map_adj[[1]], nodes = colnames(train))
map_dag <- as.bn(map_dag)

map_dag_uc <- map_dag # save for later

# which edge directions are known and which can be set?
map_cpdag <- cpdag(map_dag)
undirected.arcs(map_cpdag)

h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(map_dag)))
plot(h)
```

So here with no constraints we get a kind of weird outcome where an edge goes FROM vaccIntent TO vaccDanger. And this isn't one of the arbitrary/undirected edges! It certainly hurts intelligibility to imagine that's the true relationship, even though it improves fit on the training data. (spoiler, looks better on transfer to testing data too). Does it make sense conceptually to do CV to test the fit? Or, since there aren't that many alternatives, should I just do actual validation, maybe doing bootstrapping and re-assessing fit to assess? Then, choose-the-best or choose-the-preferred for the next step of predicting brand new data in exp2?

### (How does bidag work?)

It's a bit unclear exactly how bidag chooses to give a specific DAG when sampling the orders. It says it gives the MAP dag, so that part's clear, but how often are those dags unique? Here's a couple tests:

```{r}
# how many unique dags?
res$chain$incidence %>% unique() %>% length()

# how many unique scores (different dags could be score equivalent, or could be rounding issues)
res$chain$DAGscores %>% unique() %>% length()

# how many unique cpdags? 
res$chain$incidence %>% map(function(x){cpdag(as.bn(adjacency2dag(x)))}) %>% unique() %>% length() 
```

On one run of 10,000 MCMC samples, got 5738 unique dags, 2559 unique scores, and 2014 unique cpdags.

## Applying blacklist

In cogsci paper we imposed a fair amount of structure by demanding the ordering of nodes reflect the "abstract-ness" of each of the beliefs. We assumed that abstract beliefs influence more concrete beliefs (i.e., set expectations for, etc), so that edges would go from abstract --> concrete. We arranged the beliefs into "tiers" of abstractness to impose this constraint, while not imposing constraints on beliefs we thought were equally abstract/concrete.

Another approach would be to impose even less structure, maybe just stipuating that vaccIntent must be the "outcome" DV, so that it has no children (`intent_is_dv`), or that `nat` and `hb` must be parents without parents themselves (`abstract_are_parents`). That's what I'm currently doing here (toggle-able by (un)commenting in code below)

```{r define_theory}
# theory based stuff
nodes <- c(
  "diseaseRare",
  "diseaseSevere",
  "hb",
  "infantImmLimCap",
  "infantImmWeak",
  "medSkept",
  "nat",
  "overpar",
  "parentExpert",
  "vaccDanger",
  "vaccEff",
  "vaccIntent",
  "vaccStrain",
  "vaccTox"
)

theoryBasedHierarchy <- data.frame(
  node = nodes,
  order = c(
    3,
    3,
    1,
    3,
    3,
    2,
    1,
    2,
    2,
    3,
    3,
    4,
    3,
    3
  )
)

intent_is_dv <- data.frame(
  node = nodes,
  order = c(
    1,
    1,
    1,
    1,
    1,
    1,
    1,
    1,
    1,
    1,
    1,
    2,
    1,
    1
  )
)

abstract_are_parents <- data.frame(
  node = nodes,
  order = c(
    2,
    2,
    1,
    2,
    2,
    2,
    1,
    2,
    2,
    2,
    2,
    2,
    2,
    2
  )
)

source("../Scripts/bnTheoryBlacklist.R")

# theoryBlacklist <- make_theory_blacklist(theoryBasedHierarchy) # something is wrong here?
# theoryBlacklist <- make_theory_blacklist(intent_is_dv)
theoryBlacklist <- make_theory_blacklist(abstract_are_parents)
theoryBlacklist <- bind_rows(theoryBlacklist, data.frame(from = nodes, to = nodes)) %>% arrange(from)
adjBlacklist <- igraph::graph.data.frame(theoryBlacklist)
adjBlacklist <- igraph::get.adjacency(adjBlacklist,sparse=FALSE)

bl_modifier <- abs(1-adjBlacklist)
```

MCMC inference and diagnostics with minimal imposed structure ...

```{r}

# search_space_bl <- searchSpace$space$adjacency * bl_modifier

searchSpace_bl <- iterativeMCMCsearch(
  ncol(train),
  scoreparam = scoreparam,
  blacklist = abs(1-bl_modifier),
  scoreout = TRUE,
  alpha = .4
)

res_bl <- orderMCMC(
  ncol(train), 
  startspace = searchSpace_bl$space$adjacency, # DP 8/14/18, 12:22 PM: Fixed this w/ blcaklist in prior step
  blacklist = abs(1-bl_modifier),
  scoreparam = scoreparam, 
  iterations = mcmc_samples,
  chainout = TRUE, # orderMCMC only
  scoreout = TRUE, # orderMCMC only
  stepsave = 10
  )

saveRDS(res_bl, file = "mcmc-result-blacklist.rds")

scoreChain_bl <- unlist(res_bl$chain$DAGscores)
plot(scoreChain_bl[1000:mcmc_samples/10+1],  type = "l" )
```

Plotting the Maximum A-Posteriori (MAP) DAG and checking undirected edges (13, so a fair number of decisions to make there ...)

```{r}
map_score_bl <- max(scoreChain_bl)
map_index_bl <- match(map_score_bl, scoreChain_bl)

map_adj_bl <- res_bl$chain$incidence[map_index_bl]

map_dag_bl <- adjacency2dag(map_adj_bl[[1]], nodes = colnames(train))
map_dag_bl <- as.bn(map_dag_bl)

map_cpdag_bl <- cpdag(map_dag_bl)
undirected.arcs(map_cpdag_bl)

h_bl <- HydeNetwork(as.formula(bnlearn_to_hyde_string(map_dag_bl)))
plot(h_bl)

```

### Comparing map dags

Let's compare the map dag we get with no constraints to the map dag we get with our theory-based constraints.

```{r}
# compare dag scores on out of sample preds 
# (but this is refitting  pars to test data so not perfect)
exp(score(map_dag, test) - score(map_dag_bl, test))

```

It's a pretty big difference in performance between the dags fitting in terms of raw score. However, when we compare the actual predictive performance below, they are pretty much equivalent. The unconstrained dag does trivially better but it's within the error of the estimation process. (e.g., r = .830 vs r = .832)

### Plotting posterior over edges

In addition to examining the MAP graph, we can also ask about the posterior probability of each potential edge. This can let us assess our confidence in components of the graph, and may provide more qualitative insights.

```{r}
# choose which dag is being used in code below
# chosen_dag <- "unconstrained"
chosen_dag <- "theory-based"

if (chosen_dag == "theory-based") {
  map_dag <- map_dag_bl
  res <- res_bl
} else {
  map_dag <- map_dag_uc # to examine unconstrained dag
  res <- res_uc
}

```

```{r fig.height=5, fig.width=5, fig.align="center"}
library(viridis)

edge_posterior <- edges.posterior(res$chain$incidence, pdag=TRUE)
rownames(edge_posterior) <- colnames(search_space_bl) # KW modified, added _bl
colnames(edge_posterior) <- colnames(search_space_bl) # KW modified, added _bl

cor_df <- cor(train) %>%
  reshape::melt() %>%
  rename(x = X1, y = X2, correlation = value) %>%
  left_join(
    map_adj_bl %>% 
      reshape::melt() %>% 
      rename(x = X1, y=X2, map_edge = value) %>% 
      mutate(x = factor(x, labels=nodes), 
             y = factor(y, labels=nodes), 
             map_edge = factor(map_edge)) %>%
      select(-L1)
  )

edge_df <- reshape::melt(edge_posterior) %>%
  rename(x = X1, y = X2) %>%
  left_join(cor_df) %>%
  # mutate(value = correlation*value) %>%
  mutate(correlation = abs(correlation))

edge_df %>%
  ggplot(aes(x=reorder(x, -correlation), y=reorder(y, -correlation), fill=value)) +
  geom_tile() +
  geom_point(aes(alpha = map_edge), shape = 16) +
  scale_alpha_discrete(range=c(0,1)) +
  guides(alpha="none") +
  scale_fill_viridis(option="C") +
  # scale_fill_distiller(palette =  "RdBu") +
  theme_bw() +
  theme(aspect.ratio=1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=.5)) +
  labs(x = "From", y = "To", title="Edge posterior probabilities", fill="p(edge)") 
```

This plot shows the posterior edge probabilities, and marks the edges in the MAP DAG with dots. Looking at this, it's pretty peak-y. So for each edge in the MAP dag, we're pretty sure it should be there. And there are only two edges with any meaningful probability that aren't in the MAP dag.

Here's another plot where edge probabilities are weighted by the edge correlation between the variables. As a statistical quantity this is kinda murky, but it's maybe a useful visualization? The average edge coefficients plot below this is probably better.

```{r}
edge_df <- reshape::melt(edge_posterior) %>%
  rename(x = X1, y = X2) %>%
  left_join(cor_df) %>%
  mutate(value = correlation*value) %>%
  mutate(correlation = abs(correlation))

edge_df %>%
  ggplot(aes(x=reorder(x, -correlation), y=reorder(y, -correlation), fill=value)) +
  geom_tile() +
  geom_point(aes(alpha = map_edge), shape = 16) +
  scale_alpha_discrete(range=c(0,1)) +
  guides(alpha="none") +
  # scale_fill_viridis(option="C") +
  scale_fill_distiller(palette =  "RdBu") +
  theme_bw() +
  theme(aspect.ratio=1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=.5)) +
  labs(x = "From", y = "To", title="Edge posterior probabilities", fill="p*w") 
```

A potentially better way of examining the posterior of strength of direct relationships is to take the expected beta weight over all graphs. So here we're computing the betas for all graphs, then taking the average beta connecting each variable. If there's no edge, then beta is zero.

```{r}
# make function to get edge weights out of fitted network
get_weights <- function(bnFitted) {
  arcDf <- arcs(bnFitted)

  apply(arcDf, 1, function(x){
    from <- x[1]
    to <- x[2]

    val <- bnFitted[[to]][["coefficients"]][[from]]
  })

}

adj_to_bnlearn <- function(adjmat, data) {
  bnlearn::as.bn(BiDAG::adjacency2dag(adjmat[[1]], nodes = colnames(data)))
}

adj_fit_weights <- function(adjmat, data) {
  bn <- adj_to_bnlearn(adjmat, data)
  w <- data.frame(arcs(bn)) %>%
    mutate(w = get_weights(bn.fit(bn, data))) %>%
    mutate(X1 = as.character(X1), X2 = as.character(X2)) %>%
    bind_rows(data.frame(X1=as.character(nodes), X2=as.character(nodes), w = as.numeric(0))) %>%
    spread(X2, w) %>%
    replace(is.na(.), 0) %>%
    select(-X1) %>%
    mutate_all(as.numeric) %>%
    as.matrix()
  rownames(w) <- colnames(w)
  return(w)
}

# adj_fit_weights(map_adj, train)

incidence_chain <- res$chain$incidence[9001:10001] # just using last 1k b/c this is slow

for (i in 1:length(incidence_chain)) {
  suppressWarnings( incidence_chain[i][[1]] <- adj_fit_weights(incidence_chain[i], train) )
  # this isn't accounting for other dags in the equivalence class
}

avg_weights <- Reduce("+", incidence_chain)/length(incidence_chain)

```

```{r fig.height=5, fig.width=5}

coolwarm_hcl <- colorspace::diverge_hcl(11,
  h = c(250, 10), c = 100, l = c(37, 88), power = c(0.7, 1.7))

weights_df <- reshape::melt(avg_weights) %>%
  rename(x = X1, y = X2) %>%
  left_join(cor_df)

weights_df %>%
  ggplot(aes(x=reorder(x, -abs(correlation)),
             y= reorder(y,-abs(correlation)), 
             fill=value)) +
  geom_tile() +
  scale_alpha_discrete(range=c(0,1)) +
  # scale_fill_viridis(option="C") +
  scale_fill_distiller(palette =  "RdBu") +
  # scale_fill_gradientn(colours = coolwarm_hcl) +
  geom_point(aes(alpha = map_edge), shape = 16) +
  guides(alpha="none") +
  theme_minimal() +
  theme(aspect.ratio=1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "From", y = "To", title="Avg. Edge Coefficients", fill="Avg. Beta")
```

Here are the edges with average weights stronger than .1, sorted by strength of edge weight. Interpreting this can be tricky. For instance, `vaccDanger --> vaccTox` and `vaccTox --> vaccDanger` are both represented. We can interpret that either way that edge is set, there's a strong relationship. However, `infantImmWeak --> infantImmLimCap` actually comes out the strongest, which could be partially attributable to the fact that it only seems to appear in that direction. So the betas are biased by the tendency for the model to be confident about the edge directions. Maybe I could do something to not count those "zeros" against an edge direction?

__NOTE__: ordering of variables in both of these plots could be improved. Could also improve the continuity between the color palettes.

```{r}
weights_df %>% 
  rename(from = x, to = y) %>%
  filter(abs(value) > .1) %>%
  arrange(desc(abs(value)))
```

### Thresholded DAG

```{r}
thresh_dag <- dag.threshold(14, res_bl$chain$incidence, .90) # posterior is less peak-y
x <- as.bn(adjacency2dag(thresh_dag, nodes = colnames(train)))
plot(HydeNetwork(as.formula(bnlearn_to_hyde_string(x))))

# DAGscore(14, scoreparameters(14, scoretype = "bge", data=test), thresh_dag) # scores much worse
```

## Some thoughts

Some things we might think about:

1. What about the ORDER of each variable? Are more abstract beliefs more likely to come BEFORE concrete beliefs in the topological ordering of the graphs? That doesn't really seem true based on the map graph, but might come out of the posterior _NOPE_
2. Are abstract beliefs more highly connected than concrete beliefs? Could measure as # of children and parents, or as markov blanket size. _NOPE_
3. If these things don't pan out, may suggest more emphasis of the importance of a priori verbal theories. E.g., theory of node orderings.
4. To test the argument re interventions as conditioning, will need to explore prediction performance for whole posterior over dags (and all dags in each equivalence class). But really, maybe this just isn't the sort of thing you test? It's really a theoretical point.

## parents and children

```{r}
count_parents_and_children <- function(x, id){
  # x <- x[[1]]
  rowSums(x)[id] + colSums(x)[id]
}

get_counts <- function(adj, nodes) {
  counts <- map(nodes, function(x){count_parents_and_children(adj, x)})
  result <- unlist(counts)
  names(result) <- colnames(train)
  return(result)
}

all_counts <- map(res$chain$incidence, function(z){get_counts(z, 1:14)})

all_counts <- do.call(rbind, all_counts)

count_df <- data.frame(all_counts)

count_df %>%
  gather(scale, edges) %>%
  ggplot(aes(x=reorder(scale,edges), y = edges)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Looking at ordering. There's a pattern but not clear if it's coherent. If anything though, it looks bad for the idea that abstract = lower order. Abstract stuff is showing up downstream more than other things. So is vaccIntent, which is good, and in contrast to the MAP graph. So all in all confusing.

```{r}
get_node_order <- function(adj, nodes){
  dag <- as.bn(adjacency2dag(adj, nodes))
  ordering <- bnlearn::node.ordering(dag)

  node_orders <- sapply(nodes, function(x){match(x, ordering)})
  return(node_orders)
}

mcmc_named <- map(res$chain$incidence, function(z){colnames(z) <- nodes; return(z)})
all_orders <- map(mcmc_named, function(z){get_node_order(z, nodes)})

all_orders <- do.call(rbind, all_orders)

all_orders <- data.frame(all_orders)

all_orders %>%
  gather(scale, edges) %>%
  ggplot(aes(x=reorder(scale,edges), y = edges)) +
  # geom_violin() +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## MAP model predictions

Below I've made some code to generate predictions from the model using what I'll call a "leave-out-one-node" approach. We predict each node from the network conditional on all other nodes using `bnlearn::impute()` function to impute the target "missing" values using `method="bayes-lw"`.

8/6/18, 11:53 AM: iirc this was not perfectly accurate b/c the bnlearn inference tools are a bit crap. I think it was better to use my own implementation of MCMC with jags.

```{r}
predictions <- test %>% mutate_all(function(x){NA}) %>% mutate_all(as.numeric)
net.fit <- bn.fit(map_dag, train)

for (targVar in names(test)) {
  tempDF <- test
  tempDF[[targVar]] <- NA
  tempDF[[targVar]] <- as.numeric(tempDF[[targVar]])

  imputed <- impute(net.fit, tempDF, method="bayes-lw")
  predictions[[targVar]] <- imputed[[targVar]]
}

predictions <- predictions %>% gather(varName, predValue)
test_analyze <- test %>% gather(varName, value) %>% bind_cols(predictions) %>% select(varName, value, predValue)

```

Doing this, the average correlation between predicted and observed is `r cor(test_analyze$predValue, test_analyze$value) %>% round(4)` for an $R^2 =$ `r (cor(test_analyze$predValue, test_analyze$value)^2) %>% round(4)`, which seems pretty good considering this is an out-of-sample prediction.

We can also think about the proportion of total variance accounted for, and compute an $R^2$ equivalent for that. Doing that below, we find it's a bit lower than suggested by the average correlation. Not sure which of these is more meaningful to use ...

```{r}
# and weight by variance
test_analyze %>%
  group_by(varName) %>%
  summarize(cor = cor(value,predValue), variance=var(value)*n()) %>%
  mutate(varAccounted = (cor^2)*(variance)) %>%
  summarize(meanWeightedR2 = sum(varAccounted)/sum(variance)) %>% 
  as.numeric()
```

Finally, below is a plot of the predicted versus actual values for each variable in our test set (20% of data).

```{r fig.height=3, fig.width=7, fig.align="center"}

library(ggthemes)

predObsCor <- cor(test_analyze$value,test_analyze$predValue)

recode_nodesCV <- function(x){
  recode(x,
         "diseaseRare" = "disease\nrarity",
         "diseaseSevere" = "disease\nseverity",
         "hb" = "holistic\nbalance",
         "infantImmLimCap" = "limited\ncapacity",
         "infantImmWeak" = "weakness",
         "medSkept" = "medical\nskepticism",
         "nat" = "naturalism",
         "overpar" = "parental\nprotectiveness",
         "parentExpert" = "parental\nexpertise",
         "vaccDanger" = "vaccine\ndanger",
         "vaccEff" = "vaccine\neffectivenness",
         "vaccIntent" = "vaccination\nintentions",
         "vaccStrain" = "vaccines\nstrain",
         "vaccTox" = "vacc. toxic\naddititves")}

corrDF <- test_analyze %>%
  mutate(varName = gsub("IIS:\n", "", recode_nodesCV(varName))) %>%
  group_by(varName) %>%
  summarize(cor = cor(value,predValue)) %>%
  mutate(cor = format(round(cor,2),nsmall=2))

plt.valid <- test_analyze %>%
  mutate(varName = gsub("IIS:\n", "", recode_nodesCV(varName))) %>%
  ggplot(aes(x=predValue, y=value)) + 
  geom_point(shape=1, size=.5, color="darkturquoise") + 
  geom_text(data=corrDF, aes(label=paste("r =", cor)), 
            x=-Inf, y=Inf, hjust=-0.12, vjust=1.4, 
            size = 10*.352777778,
            color="grey25") +
  # geom_smooth(method="lm") +
  theme_bw(base_size = 10) +
  theme(strip.background =element_rect(fill="grey90")) +
  coord_fixed() + 
  facet_wrap(~varName, nrow=2) + 
  scale_x_continuous("Predicted values", limits = c(-3.5, 3.5), breaks = c(-3, 0, 3)) +
  scale_y_continuous("Observed values", limits = c(-3.5, 3.5), breaks = c(-3, 0, 3))

plt.valid
```

In any case, nothing radically different here from the cogsci paper (maybe a tiny improvement). But that's ok, we were pretty happy with it as-is.

### 2018-09-18 study1/vacc_manyBelief_study1.Rmd
added files

---
title: 'Vaccines: Many Beliefs Study 1'
author: "Derek Powell, Kara Weisman"
date: "September 7, 2017"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(stringr)
library(corrplot)
library(viridis)
library(psych)
library(glmpath)
library(bnlearn)
```

```{r}
# moved all data import/munging to a separate file 
# so we can have multiple workbooks working withthe same data

source("vacc_import_data.R", chdir = TRUE)
```

# Introduction

This is a notebook for the first experiment of our (Kara, Ellen, and Derek) study examining vaccine theories using multiple attitude measures. We recruited 1200 and are left with `r length(d_demo$ResponseId)` after excluding any participants who failed at least 1 of the 2 attention checks.

# Demographics

A quick look at demographics variables...

## Study duration

```{r duration}
ggplot(d_demo, aes(x = Duration/60)) +
  geom_histogram() +
  geom_vline(xintercept = median(d_demo$Duration/60), color = "blue") +
  annotate("label", x = 0, y = 350, color = "blue", hjust = 0,
           label = paste0("median: ", round(median(d_demo$Duration/60)), "min")) +
  labs(x = "duration (min)") +
  theme_bw()
```

## Gender

```{r sex}
ggplot(d_demo, aes(x = sex)) +
  geom_bar() +
  labs(x = "gender") +
  theme_bw() +
  coord_flip()
```

## Age

```{r age}
ggplot(d_demo, aes(x = age)) +
  geom_histogram() +
  geom_vline(xintercept = median(d_demo$age), color = "blue") +
  annotate("label", x = 0, y = 150, color = "blue", hjust = 0,
           label = paste0("median: ", round(median(d_demo$age)), "y")) +
  labs(x = "age (y)") +
  theme_bw()
```

## Race

```{r race}
ggplot(d_demo, aes(x = race)) +
  geom_bar() +
  labs(x = "race") +
  theme_bw() +
  coord_flip()
```

## Religion

```{r religion}
ggplot(d_demo, aes(x = religion)) +
  geom_bar() +
  labs(x = "religion") +
  theme_bw() +
  coord_flip()
```

## Education

```{r education}
ggplot(d_demo, aes(x = educ)) +
  geom_bar() +
  labs(x = "educ") +
  theme_bw() +
  coord_flip()
```

## Income

```{r income}
ggplot(d_demo, aes(x = income)) +
  geom_bar() +
  labs(x = "income") +
  theme_bw() +
  coord_flip()
```

## Parent

```{r parent}
ggplot(d_demo, aes(x = parent)) +
  geom_bar() +
  labs(x = "parent") +
  theme_bw() +
  coord_flip()
```

## Expecting

```{r expecting}
ggplot(d_demo, aes(x = expecting)) +
  geom_bar() +
  labs(x = "expecting") +
  theme_bw() +
  coord_flip()
```

## Number of children

```{r children}
ggplot(d_demo, aes(x = factor(children))) +
  geom_bar() +
  labs(x = "number of children") +
  theme_bw() +
  coord_flip()
```

## Age of youngest child

```{r youngest_child}
ggplot(d_demo, aes(x = factor(youngest_child))) +
  geom_bar() +
  labs(x = "age of youngest child") +
  theme_bw() +
  coord_flip()
```

## Comments on study experience

```{r comments}
d_demo %>% select(comments)
```

# Heatmap

```{r heatmap, fig.width = 5, fig.height = 5}
# make dataframe for heatmpa, efa, etc.
d_efa <- d_wide %>% select(-c(StartDate, Duration, sex:comments)) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId")

# make correlation plot heatmap
# corrplot(cor(d_efa),
#          tl.cex=.75,
#          tl.col="black",
#          method="color",
#          col=viridis(128))

# with clustering
corrplot(cor(d_efa),
         order="hclust",
         # addrect=3,
         tl.cex=.75,
         tl.col="black",
         method="color",
         col=viridis(128))
```

# Exploratory factor analysis

Just for fun, let's do exploratory factor analysis!

```{r efa}
# NEED TO AUTOMATE THIS: do maximal unrotated efa, retain factors with SS loadings > 1 and Prop Explained > 0.05
fa_maximal <- fa(d_efa, nfactors = floor(length(levels(factor(d_long$question)))/3), rotate = "none")
nfactors_efa <- 4

# small rotated efa (oblimin rotation, doesn't have to be orthogonal)
fa_small <- fa(d_efa, nfactors = nfactors_efa, rotate = "oblimin")
fa.sort(fa_small$loadings)
```

By my typical factor retention criteria, we observe for 4 factors here:

1. Beliefs/attitudes about vaccines and medical skepticism
2. Beliefs/attitudes about infants
3. Beliefs/attitudes about holistic balance and naturalism
4. Beliefs/attitudes about childhood diseases

```{r parallel analysis}
# extract number of factors recommended by fa.parallel
fa_parallel <- fa(d_efa, nfactors = fa.parallel(d_efa, plot = F)$nfact, rotate = "oblimin")
fa.sort(fa_parallel$loadings)
```

By anoother criterion (parallel analysis) we observe 12ish factors. For the most part, these correspond to the 14 intended scales, with a little bit of combination in the factors related to vaccines per se:

1. Vaccine intentions + some other beliefs/attitudes about vaccines (*vaccIntent* + *vaccEff* + some of *vaccDanger*)
2. Disease severity (*diseaseSevere*)
3. Vaccines strain the immune system + some other beliefs/attitudes about vaccines (*vaccStrain* + some of *vaccDanger*)
4. Infant immune system is weak (*infantImmWeak*)
5. Infant immune system has limited capacity (*infantImmLimCap*)
6. Disease rarity (*diseaseRare*)
7. Holistic balance (*hb*)
8. Parent expertise (*parentExpert*)
9. Overparenting (*overpar*)
10. Vaccines are toxic (*vaccTox* + some of *vaccDanger*)
11. Naturalism (*nat*)
12. Medical skepticism (*medSkept*)

Now let's leave the vaccIntent scale out of this (holding it out as our DV) and do traditional-style EFA for all the rest of the items:

```{r efa without vaccIntent}
# NEED TO AUTOMATE THIS: do maximal unrotated efa, retain factors with SS loadings > 1 and Prop Explained > 0.05
fa_maximal2 <- fa(d_efa %>% select(-starts_with("vaccIntent")), 
                 nfactors = floor(length(levels(factor(d_long$question)))/3), 
                 rotate = "none")
nfactors_efa2 <- 4

# small rotated efa (oblimin rotation, doesn't have to be orthogonal)
fa_small2 <- fa(d_efa %>% select(-starts_with("vaccIntent")), 
                                 nfactors = nfactors_efa2, 
                                 rotate = "oblimin")
fa.sort(fa_small2$loadings)
```

By my typical factor retention criteria, we again observe for 4 factors here - very similar to the 4 factors we observed when we left the vaccIntent scale in:

1. Beliefs/attitudes about vaccines, medical skepticism, parental expertise, and naturalism
2. Beliefs/attitudes about infants' immune systems (and a little overparenting)
3. Beliefs/attitudes about childhood diseases
4. Beliefs/attitudes about holistic balance and overparenting (and a little naturalism)

# Scale reliability analyses

As a reminder, our goal was $\alpha$ >= 0.80 for each scale individually.

## Alpha for each scale

### Disease rarity (*diseaseRare*)

```{r reliability diseaseRare}
alpha_diseaseRare <- d_long %>%
  filter(question_block == "diseaseRare") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_diseaseRare
```

For *diseaseRare*, $\alpha$ = `r round(alpha_diseaseRare$total$raw_alpha, 2)`. This is *just* under our cutoff (ok).

### Disease severity (*diseaseSevere*)

```{r reliability diseaseSevere}
alpha_diseaseSevere <- d_long %>%
  filter(question_block == "diseaseSevere") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_diseaseSevere
```

For *diseaseSevere*, $\alpha$ = `r round(alpha_diseaseSevere$total$raw_alpha, 2)`. This is well over our cutoff (good).

### Holistic balance (*hb*)

```{r reliability hb}
alpha_hb <- d_long %>%
  filter(question_block == "hb") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_hb
```

For *hb*, $\alpha$ = `r round(alpha_hb$total$raw_alpha, 2)`. This is a little over our cutoff (good).

### Infant immune system has limited capacity (*infantImmLimCap*)

```{r reliability infantImmLimCap}
alpha_infantImmLimCap <- d_long %>%
  filter(question_block == "infantImmLimCap") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_infantImmLimCap
```

For *infantImmLimCap*, $\alpha$ = `r round(alpha_infantImmLimCap$total$raw_alpha, 2)`. This is well over our cutoff (good).

### Infant immune system is weak (*infantImmWeak*)

```{r reliability infantImmWeak}
alpha_infantImmWeak <- d_long %>%
  filter(question_block == "infantImmWeak") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_infantImmWeak
```

For *infantImmWeak*, $\alpha$ = `r round(alpha_infantImmWeak$total$raw_alpha, 2)`. This is well over our cutoff (good).

### Medical skepticism (*medSkept*)

```{r reliability medSkept}
alpha_medSkept <- d_long %>%
  filter(question_block == "medSkept") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_medSkept
```

For *medSkept*, $\alpha$ = `r round(alpha_medSkept$total$raw_alpha, 2)`. This is just under our cutoff (ok).

### Naturalism (*nat*)

```{r reliability nat}
alpha_nat <- d_long %>%
  filter(question_block == "nat") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_nat
```

For *nat*, $\alpha$ = `r round(alpha_nat$total$raw_alpha, 2)`. This is just under our cutoff (ok).

### Overparenting (*overpar*)

```{r reliability overpar}
alpha_overpar <- d_long %>%
  filter(question_block == "overpar") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_overpar
```

For *overpar*, $\alpha$ = `r round(alpha_overpar$total$raw_alpha, 2)`. This is quite a bit under our cutoff (not great).

### Parental expertise (*parentExpert*)

```{r reliability parentExpert}
alpha_parentExpert <- d_long %>%
  filter(question_block == "parentExpert") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_parentExpert
```

For *parentExpert*, $\alpha$ = `r round(alpha_parentExpert$total$raw_alpha, 2)`. This is just over our cutoff (good).

### Vaccines are dangerous (*vaccDanger*)

```{r reliability vaccDanger}
alpha_vaccDanger <- d_long %>%
  filter(question_block == "vaccDanger") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_vaccDanger
```

For *vaccDanger*, $\alpha$ = `r round(alpha_vaccDanger$total$raw_alpha, 2)`. This is well over our cutoff (good).

### Vaccines are effective (*vaccEff*)

```{r reliability vaccEff}
alpha_vaccEff <- d_long %>%
  filter(question_block == "vaccEff") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_vaccEff
```

For *vaccEff*, $\alpha$ = `r round(alpha_vaccEff$total$raw_alpha, 2)`. This is well over our cutoff (good).

### Vaccine intentions (*vaccIntent*)

```{r reliability vaccIntent}
alpha_vaccIntent <- d_long %>%
  filter(question_block == "vaccIntent") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_vaccIntent
```

For *vaccIntent*, $\alpha$ = `r round(alpha_vaccIntent$total$raw_alpha, 2)`. This is just over our cutoff (good).

### Vaccines strain the immune system (*vaccStrain*)

```{r reliability vaccStrain}
alpha_vaccStrain <- d_long %>%
  filter(question_block == "vaccStrain") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_vaccStrain
```

For *vaccStrain*, $\alpha$ = `r round(alpha_vaccStrain$total$raw_alpha, 2)`. This is well over our cutoff (good).

### Vaccines are toxic (*vaccTox*)

```{r reliability vaccTox}
alpha_vaccTox <- d_long %>%
  filter(question_block == "vaccTox") %>%
  select(ResponseId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  alpha()

alpha_vaccTox
```

For *vaccTox*, $\alpha$ = `r round(alpha_vaccTox$total$raw_alpha, 2)`. This is well over our cutoff (good).

## Scale reliability summary

Things worked out pretty well:

- 10 scales were above the $\alpha$ = 0.80 cutoff (*diseaseSevere*, *hb*,*infantImmLimCap*, *infantImmWeak*, *parentExpert*, *vaccDanger*, *vaccEff*, *vaccIntent*, *vaccStrain*, *vaccTox*)
- 3 scales were just under the cutoff (*diseaseRare*: $\alpha$ = `r round(alpha_diseaseRare$total$raw_alpha, 2)`; *medSkept*: $\alpha$ = `r round(alpha_medSkept$total$raw_alpha, 2)`; *nat*: $\alpha$ = `r round(alpha_nat$total$raw_alpha, 2)`)
- 1 scale was pretty well below the cutoff (*overpar*: $\alpha$ = `r round(alpha_overpar$total$raw_alpha, 2)`)

So, we should probably be a little cautious in interpreting results related to overparenting (*overpar*) (though note that even that reliability is not terrible relative to what other research groups use!).

# Scale score distributions

Let's look at the distributions of scores on each scale. I scored each scale by taking the average of the participant's responses to items on that scale - so for each scale, scores could theoretically range from -3 (participant said "Strongly disagree" to all items after reverse-coding) to +3 (participant said "Strongly agree" to all items after reverse-coding).

```{r score distributions, fig.width = 5, fig.asp = 0.67}
score_medians <- d_sum %>%
  mutate(scale = recode_factor(
    question_block,
    "vaccIntent" = "Vaccination Intentions",
    "nat" = "Naturalism",
    "hb" = "Holistic Balance",
    "overpar" = "Protective Parenting",
    "parentExpert" = "Parental Expertise",
    "medSkept" = "Medical Skepticism",
    "vaccDanger" = "Vaccine Danger",
    "vaccTox" = "Toxic Additives in Vaccines",
    "vaccEff" = "Vaccine Efficacy",
    "diseaseRare" = "Disease Rarity",
    "diseaseSevere" = "Disease Severity",
    "infantImmWeak" = "Infant Immune System:\nWeakness",
    "infantImmLimCap" = "Infant Immune System:\nLimited Capacity",
    "vaccStrain" = "Infant Immune System:\nVaccines Strain")) %>%
  group_by(scale) %>%
  summarise(median_score = median(score))

d_sum %>%
  mutate(scale = recode_factor(
    question_block,
    "vaccIntent" = "Vaccination Intentions",
    "nat" = "Naturalism",
    "hb" = "Holistic Balance",
    "overpar" = "Protective Parenting",
    "parentExpert" = "Parental Expertise",
    "medSkept" = "Medical Skepticism",
    "vaccDanger" = "Vaccine Danger",
    "vaccTox" = "Toxic Additives in Vaccines",
    "vaccEff" = "Vaccine Efficacy",
    "diseaseRare" = "Disease Rarity",
    "diseaseSevere" = "Disease Severity",
    "infantImmWeak" = "Infant Immune System:\nWeakness",
    "infantImmLimCap" = "Infant Immune System:\nLimited Capacity",
    "vaccStrain" = "Infant Immune System:\nVaccines Strain")) %>%
  ggplot(aes(x = score)) +
  facet_wrap(~ scale, ncol = 5) +
  geom_histogram(binwidth = 0.25) +
  scale_x_continuous(limits = c(-3, 3), breaks = seq(-3, 3, 1)) +
  geom_vline(data = score_medians, aes(xintercept = median_score), 
             color = "blue") +
  geom_label(data = score_medians,
             aes(x = -3, y = 200, 
                 label = paste0("median: ", round(median_score, 2))),
             color = "blue", hjust = 0) +
  labs(x = "Score", y = "Number of participants") +
  theme_bw()
```

Most of these scales are pretty normally distributed, with the major exceptions of *diseaseSevere* and *vaccIntent*, which are both severely skewed, and a few other more minor ceiling/floor issues (e.g., *vaccDanger*, *vaccEff*, *vaccTox*).

# First-order correlations

```{r}
# with clustering
corrplot(cor(d_bn),
         order="hclust",
         # addrect=3,
         tl.cex=.75,
         tl.col="black",
         method="color",
         col=viridis(128))
```

```{r, fig.width = 4, fig.asp = 0.8}
temp_order <- corrMatOrder(cor(d_bn))

temp_cor <- cor(d_bn)[temp_order, temp_order] %>%
  data.frame() %>%
  rownames_to_column("scale1") %>%
  mutate(order1 = 1:14) %>%
  gather(scale2, cor, -c(scale1, order1))

temp_cor_df <- temp_cor %>%
  full_join(temp_cor %>% 
              distinct(scale1, order1) %>%
              rename(scale2 = scale1, order2 = order1)) %>%
  mutate_at(vars(scale1, scale2),
            funs(recode(.,
                        "diseaseRare" = "Disease Rarity",
                        "diseaseSevere" = "Disease Severity",
                        "hb" = "Holistic Balance",
                        "infantImmLimCap" = "Infant Immune System: Limited Capacity",
                        "infantImmWeak" = "Infant Immune System: Weakness",
                        "medSkept" = "Medical Skepticism",
                        "nat" = "Naturalism",
                        "overpar" = "Protective Parenting",
                        "parentExpert" = "Parental Expertise",
                        "vaccDanger" = "Vaccine Danger",
                        "vaccEff" = "Vaccine Efficacy",
                        "vaccIntent" = "Vaccination Intentions",
                        "vaccStrain" = "Infant Immune System: Vaccines Strain",
                        "vaccTox" = "Toxic Additives in Vaccines")))

ggplot(temp_cor_df,
       aes(x = reorder(scale1, desc(order1)), 
           y = reorder(scale2, order2), 
           fill = cor)) +
  geom_tile(color = "black") +
  geom_text(aes(label = format(round(cor, 2), digits = 2)), size = 3) +
  scale_fill_viridis("R", limits = c(-1, 1),
                     guide = guide_colorbar(barheight = 15)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title = element_blank())
```

# Regularized regression

Here's another thing I know how to do, so why not try it...

```{r glmpath}
# make a matrix for predictors
predictors <- d_sum %>% 
  select(ResponseId, question_block, score) %>%
  arrange(ResponseId, question_block) %>%
  filter(question_block != "vaccIntent") %>%
  spread(question_block, score) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  as.matrix()

# make a matrix for outcome
outcome <- d_sum %>%
  select(ResponseId, question_block, score) %>%
  arrange(ResponseId, question_block) %>%
  filter(question_block == "vaccIntent") %>%
  spread(question_block, score) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId") %>%
  as.matrix()

glm_fit <- glmpath(predictors, outcome, family = "gaussian"); glm_fit
# plot(glm_fit, xvar = "lambda")

d_glm <- glm_fit$b.predictor %>% # extract the coefficient estimates
  data.frame() %>% # turn them into a dataframe
  rownames_to_column(var = "step") %>% # add the rownames as a "step" variable
  mutate(lambda = glm_fit$lambda, # add the lambda values for each step
         aic = glm_fit$aic, # add AIC for each step
         bic = glm_fit$bic) %>% # add BIC for each step
  gather(scale, coeff, diseaseRare:vaccTox) %>% # turn into longform
  arrange(step, scale) # arrange by step number and scale

d_glm_labs <- d_glm %>% filter(lambda == 0) %>% select(scale, coeff)

ggplot(data = d_glm, aes(x = lambda, y = coeff, color = scale)) +
  geom_point() +
  geom_line() + 
  scale_x_reverse(limits = c(1200, -300)) +
  geom_text(data = d_glm_labs, aes(x = -10, y = coeff, label = scale), hjust = 0) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(title = "Order of predictors based on regularized regression",
       subtitle = "Most important predictors' coefficients become non-zero first (when lambda is large)")
```

Regularized regression suggests that, in the aggregate, beliefs that vaccines are *not* dangerous (opposite of *vaccDanger*) and that vaccines are effective (*vaccEff*) are particularly strong predictors of intentions to vaccinate.

The next most important predictors is a belief that vaccines are *not* toxic (opposite of *vaccTox*), followed by a belief that do *not* strain the immune system (opposite of *vaccStrain*), a belief that childhood diseases are severe (*diseaseSevere*), and a *lack* of medical skepticism (opposite of *medSkept*).

Other predictors seem less important, according to this analysis.

**Important**: This does *not* take into account all the causal relationships among the different scales that we are primarily interested in - it just examines each scale and its direct relationship to our outcome variable (*vaccIntent*). (Perhaps these will end up being the most proximal causal relationships...?)

# Bayesian network structure learning

A first attempt!

Resources used:

- [package guide](https://cran.r-project.org/web/packages/bnlearn/bnlearn.pdf)
- [hameddaily.blogspot.com](http://hameddaily.blogspot.com/2015/02/bayesian-network-in-r-introduction.html)
- [UC Denver Biostatistics dept.](http://www.ucdenver.edu/academics/colleges/PublicHealth/Academics/departments/Biostatistics/WorkingGroups/Documents/Networks%20Presentation%20With%20Sachs%20-%20032317.pdf)

```{r bn dataframe}
d_bn <- d_sum %>%
  select(ResponseId, question_block, score) %>%
  spread(question_block, score) %>%
  remove_rownames() %>%
  column_to_rownames("ResponseId")
```

## Learning the structure

There are lots of different methods... still figuring out what they mean.

### Method 1: Grow-shrink

From the package info: "Based on the Grow-Shrink Markov Blanket, the first (and simplest) Markov
blanket detection algorithm used in a structure learning algorithm."

```{r bn grow-shrink, fig.width = 6, fig.height = 6}
res_bn_gs <- gs(d_bn)
plot(res_bn_gs)
```

### Method 2: Incremental association

From the package info: "based on the Markov blanket detection algorithm of the same name, which is based on a two-phase selection scheme (a forward selection followed by an attempt to remove false positives)."

```{r bn iamb, fig.width = 6, fig.height = 6}
res_bn_iamb <- iamb(d_bn)
plot(res_bn_iamb)
```

### Method 3: Fast incremental association

From the package info: "a variant of IAMB which uses speculative stepwise forward selection to reduce the number of conditional independence tests."

```{r bn fast.iamb, fig.width = 6, fig.height = 6}
res_bn_fast.iamb <- fast.iamb(d_bn)
plot(res_bn_fast.iamb)
```

### Method 4: Interleaved incremental association

From the package info: "another variant of IAMB which uses forward stepwise selection to avoid false positives in the Markov blanket detection phase."

```{r bn inter.iamb, fig.width = 6, fig.height = 6}
res_bn_inter.iamb <- inter.iamb(d_bn)
plot(res_bn_inter.iamb)
```

### Method 5: Hill-climbing

From the package info: "a hill climbing greedy search on the space of the directed graphs. The optimized implementation uses score caching, score decomposability and score equivalence to reduce the number of duplicated tests."

```{r bn hc, fig.width = 6, fig.height = 6}
res_bn_hc <- hc(d_bn)
plot(res_bn_hc)
```

### Method 6: Tabu search

From the package info: "a modified hill-climbing able to escape local optima by selecting a network
that minimally decreases the score function."

```{r bn tabu, fig.width = 6, fig.height = 6}
res_bn_tabu <- tabu(d_bn)
plot(res_bn_tabu)
```

### Method 7: Max-min hill-climbing

From the package info: "a hybrid algorithm which combines the Max-Min Parents and Children algorithm (to restrict the search space) and the Hill-Climbing algorithm (to find the optimal network structure in the restricted space)."

```{r bn mmhc, fig.width = 6, fig.height = 6}
res_bn_mmhc <- mmhc(d_bn)
plot(res_bn_mmhc)
```

### Method 8: Restricted maximization

From the package info: "a more general implementation of the Max-Min Hill-Climbing, which can use any combination of constraint-based and score-based algorithms."

```{r bn rsmax2, fig.width = 6, fig.height = 6}
res_bn_rsmax2 <- rsmax2(d_bn)
plot(res_bn_rsmax2)
```

Let's go with MMHC (Method #7) for now (for no real reason other than the fact that I've heard of it before).

## Parameter learning

```{r bn parameter learning}
res_bn_mmhc_fitted <- bn.fit(res_bn_mmhc, data = d_bn); res_bn_mmhc_fitted
```

## Limit to just parents?

```{r bn just parents, fig.width = 6, fig.height = 6}
d_bn_parents <- d_bn %>%
  rownames_to_column("ResponseId") %>%
  left_join(d_demo %>% select(ResponseId, parent)) %>%
  filter(parent == "Yes") %>%
  select(-parent) %>%
  column_to_rownames("ResponseId")

res_bn_parents_mmhc <- mmhc(d_bn_parents)
plot(res_bn_parents_mmhc)
```

### 2018-09-18 study2/cog-model-discrete-predictions.Rmd
added files

---
title: "R Notebook"
output: 
  html_notebook: 
    code_folding: hide
    toc: true
    toc_float: true
---

```{r load in existing objects, message=FALSE, warning=FALSE}
# net.struct <- readRDS("net-struct-cogsci2018.rds")

source("../../study1/vacc_import_data.R")
source("../../Scripts/gmod_tools.R")
# source("../../Scripts/virtualEvidence.R")

library(bnlearn)
library(rjags)
library(patchwork)
library(BiDAG)
library(HydeNet)
library(bnlearn)

source("cog-model-main.R")
```

```{r set up training split}
# rescale beta

rescale_beta <- function(x, lower, upper) {
  # rescales onto the open interval (0,1)
  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"

  N <- length(x)
  res <- (x - lower) / (upper - lower)
  res <- (res * (N - 1) + .5) / N

  return(as.vector(res))
}

d_bn_scaled <- d_bn %>%
 mutate_all(function(x){rescale_beta(x,-3,3)})

## set the seed to make your partition reproductible
set.seed(123)
trainInd <- sample(seq_len(nrow(d_bn_scaled)), size = floor(nrow(d_bn_scaled)*.80))

train <- d_bn_scaled[trainInd, ]
test <- d_bn_scaled[-trainInd, ]
```

# loading in data model

```{r}
# first load in mcmc results
all_results <- readRDS("allresults.rds")
nodes <- colnames(train)
# then grab map dag for theory-based constraints
merged_chains <- merge_chains(all_results[[5]])
map_dag <- extract_mapdag(merged_chains)

h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(map_dag)))
plot(h)
```

## creating cognitive model

```{r}
# parse bn into list of parents and children

arcs_df <- bnlearn_to_df(map_dag)

df_to_list <- function(arcs_df, as.strings=FALSE) {
  # take arcs_df and make list of formulas
  arcs_df$to <- as.character(arcs_df$to)
  arcs_df$from <- as.character(arcs_df$from)

  nodes <- unique(unlist(arcs_df))
  output <- lapply(nodes, function(node) {
    edges <- arcs_df[which(arcs_df$to == node), "from"]
    if (length(edges) < 1) {
      edges <- NULL
    }
    list(child=node, parents=edges)

  })
  names(output) <- nodes
  return(output)
}

graph_list <- df_to_list(arcs_df)

bagOfModels <- lapply(graph_list, function(x){fit_node_cpt(x, train)})

# bagNet <- HydeNetwork(bagOfModels)
# writeNetworkModel(bagNet, pretty=TRUE)

```

```{r}
# add evidence node with cpt defined 
evid_ratio <- exp(0.4566215)

evid_cpt <- make_custom_cpt(c(.5*evid_ratio,.5, (1-.5*evid_ratio), (1-.5)), c(2,2), list(diseaseSevere=c("Yes","No"), evid = c("Yes","No") ), NULL)
# evid_cpt <- make_custom_cpt(c(.83,.5, .17, .5), c(2,2), list(diseaseSevere=c("yes","No"), evid = c("yes","no") ), NULL)
bagOfModels$evid <- evid_cpt

bagNet <- HydeNetwork(bagOfModels)
plot(bagNet)
writeNetworkModel(bagNet, pretty=TRUE)
## In the future (soon), make a function to create this node cpt

```

__Translating hydenet model to bnlearn__

below is some code to get things into the right format. Later I'll break this out into a function I guess.

```{r}
hyde_to_bn_cpt <- function(hyde_cpt) {
  ndims <- length(dim(hyde_cpt))

  if ("xtabs" %in% class(hyde_cpt)) {
    output <- hyde_cpt/1e5
  } else {

    output <- aperm(hyde_cpt, ndims:1)
  }
 return (output) 
}

# hyde_to_bn_cpt(bagOfModels$evid)

bnlearn_models <- lapply(bagOfModels, hyde_to_bn_cpt)

model_string <- as.character(map_dag)
model_string <- paste0(model_string,"[evid|diseaseSevere]")
model_network <- model2network(model_string)

predModel <- custom.fit(model_network, dist = bnlearn_models)
```

__Generating predictions__

Now I can use this model to generate predictions.

```{r}
# cpquery(predModel, event = (eval(parse(text="diseaseSevere"))=="Yes"), evidence = TRUE)
# cpquery(predModel, event = (eval(parse(text="diseaseSevere == 'Yes'"))), evidence = TRUE)
# cpquery(predModel, event = (eval(parse(text="diseaseSevere"))=="Yes"), evidence = (evid == "Yes"))

set.seed(12345)

pred0 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence=TRUE, n = 5e5)")
  eval(parse(text=statement))
})

pred1 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 5e5)")
  eval(parse(text=statement))
})

pred_changes <- pred1 - pred0

pred_changes <- as.data.frame(pred_changes)

pred_changes <- pred_changes %>%
  mutate(scale = nodes) %>%
  rename(Mean = pred_changes) %>%
  mutate(type = "predicted")

```

```{r}
source("../../study3/load-study3-data.R", chdir = TRUE)

obs_changes <- d_scored %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase,mean) %>%
  mutate(changeScore = post-pre) %>%
  filter(condition == "diseaseRisk") %>%
  group_by(scale) %>%
  summarise(
    Mean = mean(changeScore),
    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()), # replace with bootstrapping
    ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
    ) %>%
  mutate(type = "observed")

obs_pred <- bind_rows(pred_changes, obs_changes) %>%
  spread(type, Mean) %>%
  group_by(scale) %>%
  summarize_all(mean, na.rm=TRUE)

cor(obs_pred$predicted, obs_pred$observed)

obs_pred %>% # a bit of a hack
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point() +
  geom_errorbar() +
  coord_cartesian(xlim=c(-.06,.08), ylim=c(-.06,.08)) +
  theme_bw() +
  theme(aspect.ratio = 1)

obs_pred %>%
  gather(type, Mean, observed, predicted) %>%
  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
  geom_point() +
  geom_errorbarh(height=0)
```

----------------------------------------------

HydeNet prediction failures below ...

```{r}
set.seed(456)
model0 <- compileJagsModel(bagNet)
model1 <- compileJagsModel(bagNet, data= data.frame(evid=2))

post0 <- HydeSim(model0,
                       variable.names = nodes,
                       n.iter = 1e5
                       )

post1 <- HydeSim(model1,
                       variable.names = nodes,
                       n.iter = 1e5
                       )

post0 <- post0 %>%
  mutate(nat = ifelse(nat=="Yes",2,1)) %>%
  mutate_all(~ . -1) %>%
  summarize_all(mean) %>%
  select(-chain_index, -obs_index)

post1 <- post1 %>%
  mutate(nat = ifelse(nat=="Yes",2,1)) %>%
  mutate_all(~ . -1) %>%
  summarize_all(mean) %>%
  select(-evid, -chain_index, -obs_index)

pred_changes <- (post1 - post0)  %>%
  gather(scale, Mean) %>%
  mutate(type = "predicted")
```

```{r}
source("../../study3/load-study3-data.R", chdir = TRUE)

obs_changes <- d_scored %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase,mean) %>%
  mutate(changeScore = post-pre) %>%
  filter(condition == "diseaseRisk") %>%
  group_by(scale) %>%
  summarise(
    Mean = mean(changeScore),
    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()),
    ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
    ) %>%
  mutate(type = "observed")

bind_rows(pred_changes, obs_changes) %>%
  spread(type, Mean) %>%
  group_by(scale) %>%
  summarize_all(mean, na.rm=TRUE) %>% # a bit of a hack
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point() +
  geom_errorbar() +
  # coord_cartesian(xlim=c(-.1,.1), ylim=c(-.1,.1)) +
  theme_bw() +
  theme(aspect.ratio = 1)
```

Strong correlation, and pretty good numerically. But for some reason it's getting disease severity wrong! I really can't wrap my head around it, it's not predicting what I would expect based on the evidence ratio (when I do it manually, the predictions are more in line with observed). So something strange is going wrong. I should try making a really simple little test case.

```{r}
bind_rows(pred_changes, obs_changes) %>%
  spread(type, Mean) %>%
  group_by(scale) %>%
  summarize_all(mean, na.rm=TRUE) %>%
  mutate(abs_resid = abs(predicted - observed)) %>%
  arrange(-abs_resid)
```

So for some reason this is not working quite right with hydenet. I'm going to translate things over to bnlearn and try taht.
# JUNK BELOW
----------------------------------------

```{r}

make_predictions_hyde <- function(hyde_model, orig_data, nodes_to_predict, nodes_held_out=c(), iter=1e3) {
  # takes a model and dataframe and generates model predictions for variables listed in 
  # nodes_to_predict. By default, uses all remaining nodes in orig_data. Hold out nodes from
  # prediction with nodes_held_out. iter sets mcmc samples

  pred_df <- orig_data
  pred_df[,nodes_to_predict] <- NA

  for (i in 1:nrow(pred_df)) {
    row <- pred_df[i,]
    row[nodes_held_out] <- NA
    pred <- do_jags_inference(hyde_model, nodes_to_predict, data = row, iter = iter)
    point_preds <- rowMeans(t(pred[[1]][(iter/2+1):iter,nodes_to_predict]))
    pred_df[i,nodes_to_predict] <- point_preds
  }

  return(pred_df)
}

predict_change_scores_cog <- function(model, nodes_to_predict, iter){

  preds_mean1 <- make_predictions(model, 
                                data.frame(evid=1), 
                                nodes_to_predict, 
                                c(),
                                iter = iter)

  preds_mean0 <- make_predictions(model, 
                                  data.frame(), 
                                  nodes_to_predict, 
                                  c("evid"),
                                  iter = iter)

  preds_mean <- preds_mean1 - preds_mean0
}

predict_change_scores_cog(bagNet, nodes, 1e4)
```

```{r}
# define some functions for doing and processing predictions

predict_change_scores <- function(model, data0, data1, nodes_to_predict, held_out_nodes=c(), iter=1e4) {
  # note: intervention must be named "interv"

  require(dplyr)

  preds_mean1 <- make_predictions(model, 
                                data1, 
                                nodes_to_predict, 
                                held_out_nodes,
                                iter = iter)

  preds_mean0 <- make_predictions(model, 
                                  data0, 
                                  nodes_to_predict, 
                                  held_out_nodes,
                                  iter = iter)

  preds_mean <- preds_mean1 - preds_mean0

}

process_predictions <- function(predictions, obs_data) {
  require(dplyr)
  predictions <- predictions %>% 
  select(-interv) %>%
  gather(scale, predicted) %>%
  left_join(obs_data, by = "scale") 
}

plot_processed_predictions <- function(processed_predictions) {
  require(dplyr)
  require(ggplot2)
  plt1 <- processed_predictions %>%
    mutate(
           UL = observed + std_error*1.96,
           LL = observed - std_error*1.96
           ) %>%
    ggplot(aes(x=predicted, y = observed, ymin = LL, ymax=UL)) +
    geom_errorbar(color="grey", width=0) +
    geom_point() +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color="grey") +
    theme_bw() +
    theme(aspect.ratio = 1)

  plt2 <- processed_predictions %>% 
    # left_join(obs_error, by = "scale") %>%
    group_by(scale) %>%
    gather(type, change_score, observed, predicted) %>%
    mutate(std_error = ifelse(type == "observed", std_error, NA )) %>%
    mutate(
           UL = change_score + std_error*1.96,
           LL = change_score - std_error*1.96
           ) %>%
    ggplot(aes(y = reorder(scale, change_score),
               x = change_score,
               xmax = UL, 
               xmin = LL, 
               color = type)) +
    geom_point(shape=17, size=3) +
    geom_errorbarh(height=0) +
    theme_bw()
    # theme(axis.text.x = element_text(angle = 90, hjust = 1))

  return(list(corr_plot = plt1, means_plot = plt2))
}

score_predictions <- function(processed_predictions) {
  list(
  r = cor(processed_predictions$observed, processed_predictions$predicted),
  r_squared = cor(processed_predictions$observed, processed_predictions$predicted)^2,
  mae = mean(abs(processed_predictions$observed - processed_predictions$predicted)),
  rmse = sqrt(mean((processed_predictions$observed - processed_predictions$predicted)^2))
  )
}

score_predictions_boot <- function(processed_predictions) {

  samps <- 1:1000

  preds <- lapply(samps, function(x){
    pp <-  processed_predictions %>% 
      mutate(resamp_observed = rnorm(14, observed, std_error))
    list(
    r = cor(pp$resamp_observed, pp$predicted),
    r_squared = cor(pp$resamp_observed, pp$predicted)^2,
    mae = mean(abs(pp$resamp_observed - pp$predicted)),
    rmse = sqrt(mean((pp$resamp_observed - pp$predicted)^2))
    )
  })

}

```

# conceptual illustration

```{r}
p_x <- rbeta(100, 2, 2)
p_y_x0 = .4
p_y_x1 = .8

p_y = rethinking::rbeta2(100, p_x*p_y_x1 + (1-p_x)*p_y_x0, 100)

plot(p_x, p_y)

df <- data.frame(x=p_x, y=p_y)
df %>%
  rename(`p(fire)` = x,
         `p(smoke)` = y) %>%
  ggplot(aes(x=`p(fire)`, y = `p(smoke)`)) +
  geom_point() +
  theme_bw(base_size = 24)
```

# correlation matrix

```{r}
# borrowing code from
# http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization

reorder_cormat <- function(cormat){
  # Use correlation between variables as distance
  dd <- as.dist((1-cormat)/2)
  hc <- hclust(dd)
  cormat <-cormat[hc$order, hc$order]
}

# Get lower triangle of the correlation matrix
get_lower_tri<-function(cormat){
  cormat[upper.tri(cormat)] <- NA
  return(cormat)
}
# Get upper triangle of the correlation matrix
get_upper_tri <- function(cormat){
  cormat[lower.tri(cormat)]<- NA
  return(cormat)
}

corr_plot <- d_bn %>%
  cor() %>%
  reorder_cormat() %>%
  # get_lower_tri() %>%
  reshape2::melt(na.rm=TRUE) %>%
  ggplot(aes(x=Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_tile() +
  geom_text(aes(label=round(value,2)), size=6*.35) +
  scale_fill_distiller(type="div", palette = "RdYlBu") +
  # scale_fill_viridis_c(limit = c(-1,1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust=.85)) +
  theme(aspect.ratio = 1) +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(fill="corr.")

ggsave("corrplot.png", corr_plot, dpi=320, height=5,width=5)
```

# Aggregate predictions

This notebook aims to examine/address the issue of predicting out-of-sample data using our model. In a previous notebook, `vacc_manyBelief_study3_modelsim.RMD`, I predicted average scale responses from study 3 using the previously learned model by conditioning on the Disease Severe node.

In this notebook, I'll ...

1. Explicitly model the intervention, rather than just conditioning disease severe.
2. Examine model as "causal model"
3. Explore model predictions under different assumptions about what beliefs are "targetted" by the intervention.
4. Similarly, explore whether we should model the intervention as providing direct evidence for multiple beliefs.
5. Consider naïve models ...

## cognitive model

First, let's examine the predictions of our cognitive model, where we treat the graphical model as a cognitive model, and reading the intervention materials as observing or conditioning on some evidence relevant to beliefs about disease severity.

To recap, we have ...

1. The cognitive network model (from study 1, n=1130 (data = `d_bn`))
2. A model of the relationship between disease severity and the intervention, modeled from study 2.

And we're predicting the average change scores observed in each condition following the disease risk manipulation in Study 2. So, for the most part this is an out-of-sample prediction task -- predicting change scores for new participants on the basis of a model generated from correlations observed among different participants, along with a bit of info about the intervention's effects on disease severity from the same participants.

```{r, message=FALSE, warning=FALSE}

nodes_to_predict <- bnlearn::nodes(net.struct)

cog_model <- write_jags_model(bnlearn_to_df(net.struct), d_bn)

# can modify this to test assumptions about direct effects of intervention ...
interv_fit <- glm(interv ~ diseaseSevere, 
                  data = interv_df,
                  family = "binomial"
                  )

cog_model <- add_node(cog_model, glm_to_jags_eq(interv_fit))

# can also just use "model" here so long as you include held_out_nodes

preds_cog <- predict_change_scores(cog_model,
                                           data.frame(interv = 0),
                                           data.frame(interv = 1),
                                           nodes_to_predict,
                                           iter = 1e5*2.5
                                           )

# preds_cog$interv <- 0

preds_cog <- process_predictions(preds_cog, obs_data)

plots_cog <- plot_processed_predictions(preds_cog)

scores_cog <- score_predictions(preds_cog)

plt1 <- plots_cog$corr_plot +
  geom_text(
    aes(
      label = ifelse(observed == preds_cog[which(preds_cog$scale == "diseaseSevere"), "observed"],
        as.character(scale), ""
      )
    ),
    hjust = 1.1, vjust = 0
  ) +
  geom_text(aes(label = ifelse(observed == preds_cog[which(preds_cog$scale == "overpar"), "observed"],
    as.character(scale), ""
  )), hjust = 1.1, vjust = 0) +
  theme(aspect.ratio = 1) +
  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
  annotate("text", 
           x = .25, 
           y = -.2, 
           label = paste("italic(R)^2 == ", round(scores_cog$r_squared,3)), 
           parse = TRUE,
           size=18*.35
          ) +
  theme_bw(base_size=18)

plt2 <- plots_cog$means_plot +
  labs(x="Change score", y="Belief Scale") +
  theme_bw(base_size=18) +
  theme(legend.position = "bottom")

ggsave("plot.png", plot = plt1, dpi=320, width=4, height=4)
ggsave("plot2.png", plot = plt2, dpi=320, width=6, height=4)

```

So it's a pretty good fit, as we expected. Note that the r = `r score_predictions(preds_cog)$r %>% round(3)` is higher than the correlation in `...modelsims.Rmd` notebook, because I'm here also including disease severity in calculating the fit.

## "Non-mental" model

Next we can rule out the (perhaps not-all-that tempting) argument that we haven't developed a cognitive model at all, instead perhaps a causal model describing how holding different beliefs _causes_ a person to hold other beliefs. verbally that might not sound all that different, but the difference comes in how we conceive of evidence affecting participants' beliefs. Instead of an edge directed from the belief to the evidence, it'd be an edge directed from the evidence to the belief.

(Here I'm fudging things a bit in a way that should be fine considering these are linear models. I'm keeping the edge directed from disease severity to intervention, but then doing "graph surgery" to prune the disease severity node's parents when we predict the effects of the intervention. Since we're predicting changes, I'm about 99% confident this should work.)

```{r, message=FALSE, warning=FALSE}
library(bnlearn)
surgery_graph <- net.struct %>%
  drop.arc("vaccEff", "diseaseSevere") %>%
  drop.arc("infantImmLimCap", "diseaseSevere")

causal_arcs <- bnlearn_to_df(surgery_graph)

causal_model <- write_jags_model(causal_arcs, d_bn) %>% suppressWarnings()

interv_fit <- glm(interv ~ diseaseSevere, 
                  data = interv_df,
                  family = "binomial"
                  )

causal_model <- add_node(causal_model, glm_to_jags_eq(interv_fit)) # this is a cheat but it's ok ...

preds_causal <- predict_change_scores(causal_model,
                                           data.frame(interv = 0),
                                           data.frame(interv = 1),
                                           nodes_to_predict,
                                           iter = 1e5
                                           )

preds_causal <- process_predictions(preds_causal, obs_data)

plots_causal <- plot_processed_predictions(preds_causal)

scores_causal <- score_predictions(preds_causal)

plt3 <- plots_causal$corr_plot +
  geom_text(
    aes(
      label = ifelse(observed == preds_causal[which(preds_causal$scale == "diseaseSevere"), "observed"],
        as.character(scale), ""
      )
    ),
    hjust = 1.1, vjust = 0
  ) +
  # geom_text(aes(label = ifelse(observed == preds_cog[which(preds_cog$scale == "overpar"), "observed"],
  #   as.character(scale), ""
  # )), hjust = 1.1, vjust = 0) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  theme(aspect.ratio = 1) +
  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
  annotate("text", 
           x = .25, 
           y = -.2, 
           label = paste("italic(R)^2 == ", round(scores_causal$r_squared,3)), 
           parse=TRUE,
           size=14*.35
          ) +
  theme_bw(base_size=18)

# plots_causal$means_plot +
#   labs(x="Change score", y="Belief Scale") +
#   theme_bw(base_size=18)

ggsave("plot3.png", plot = plt3, dpi=320, width=4, height=4)
```

Treating things as a causal model makes very poor predictions.

# What beliefs are targetted by the intervention?

Here we can pretend that expectations for the intervention materials are set by each of the 14 beliefs, and compare the accuracy of the resulting models' predictions. We should also ask whether the differences among models are substantial and reliable enough for us to prefer any one model over another.

```{r}
predict_change_scores_pipe <- partial(predict_change_scores,
                                      data0 = data.frame(interv = 0),
                                      data1 = data.frame(interv = 1),
                                      nodes_to_predict = nodes_to_predict,
                                      iter = 1e5
                                      )

all_beliefs <- nodes(net.struct)

cog_model <- write_jags_model(bnlearn_to_df(net.struct), d_bn) %>% suppressWarnings()

belief_targets_models <- lapply(all_beliefs, function(b){

  f <- paste0("interv ~ ", b)

  # can modify this to test assumptions about direct effects of intervention ...
  interv_fit <- glm(as.formula(f), 
                    data = interv_df,
                    family = "binomial"
                    )

  model <- add_node(cog_model, glm_to_jags_eq(interv_fit))

  }
)

model_compare <- tibble(
  model_name = all_beliefs,
  model = unlist(belief_targets_models)
  ) %>%
    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
    mutate(proc_preds = map(predictions, process_predictions, obs_data = obs_data)) %>%
    mutate(scores = map(proc_preds, score_predictions_boot))

model_compare2 <- model_compare %>%
    mutate(
      rmse = map(scores, ~ sapply(.x, function(z){z$rmse})),
      r_squared = map(scores, ~ sapply(.x, function(z){z$r_squared}))
      ) %>%
  gather(metric, value, rmse, r_squared) %>%
  mutate(
    mean_value = map_dbl(value, mean),
    se_value = map_dbl(value, sd)
    )

plt_models <- model_compare2 %>%
  mutate(
    UL = mean_value + se_value,
    LL = mean_value - se_value
  ) %>%
  ggplot(aes(x = reorder(model_name, -mean_value), y = mean_value, ymin = LL, ymax = UL)) +
  geom_pointrange() +
  theme_bw(base_size=18) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~metric, scales="free") +
  labs(x="Targetted belief", y = "Score")

ggsave("plot_models.png", plot = plt_models, dpi=320, width=12, height=6)
```

# Modeling multiple targetted beliefs

The biggest outlier point for our cognitive model is the "parental protectiveness" (`overpar`) belief. Considering the evocative content of the intervention, it's possible that it directly bears on this belief.

Here we can model our intervention targetting both disease severity and overparenting ...

```{r, message=FALSE, warning=FALSE}

cog_model2 <- write_jags_model(bnlearn_to_df(net.struct), d_bn) %>% suppressWarnings()

# can modify this to test assumptions about direct effects of intervention ...
interv_fit <- glm(interv ~ diseaseSevere + overpar, 
                  data = interv_df,
                  family = "binomial"
                  )

cog_model2 <- add_node(cog_model2, glm_to_jags_eq(interv_fit))

# can also just use "model" here so long as you include held_out_nodes

preds_cog2 <- predict_change_scores(cog_model2,
                                           data.frame(interv = 0),
                                           data.frame(interv = 1),
                                           nodes_to_predict,
                                           iter = 1e5*2.5
                                           )

preds_cog2 <- process_predictions(preds_cog2, obs_data)

plots_cog2 <- plot_processed_predictions(preds_cog2)

scores_cog2 <- score_predictions(preds_cog2)

plt4 <- plots_cog2$corr_plot +
  geom_text(
    aes(
      label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "diseaseSevere"), "observed"],
        as.character(scale), ""
      )
    ),
    hjust = 1.1, vjust = 0
  ) +
  geom_text(aes(label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "overpar"), "observed"],
    as.character(scale), ""
  )), hjust = 1.1, vjust = 0) +
    geom_text(aes(label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "infantImmWeak"), "observed"],
    as.character(scale), ""
  )), hjust = 1.1, vjust = 0) +
  # geom_abline(intercept = 0, slope = 1, linetype = "dashed", color="grey") +
  # geom_errorbar(aes(ymin = LL, ymax=UL)) +
  theme(aspect.ratio = 1) +
  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
  annotate("text", 
           x = .25, 
           y = -.2, 
           label = paste("italic(R)^2 == ", round(scores_cog2$r_squared,3)), 
           parse=TRUE,
           size=14*.35
          )

plots_cog2$means_plot +
  labs(x="Change score", y="Belief Scale")

ggsave("plot4.png", plot = plt4, dpi=320, width=4, height=4)
```

## Comparing models

This code is a bit hacky, should write some better bootstrapping code. But here is a quick comparison, with somewhat unclear results. Previously this looked more clear cut, to me suggesting there may be more volatility in the mcmc sampling than I had thought. I should maybe give them more burn-in.

```{r}
boot_scores_cog <- score_predictions_boot(preds_cog)
boot_scores_cog2 <- score_predictions_boot(preds_cog2)

tibble(cog = sapply(boot_scores_cog, function(x){x$rmse}), 
           cog2 = sapply(boot_scores_cog2, function(x){x$rmse})) %>%
  gather(model, rmse, cog, cog2) %>%
  ggplot(aes(x=model, y = rmse)) +
  geom_boxplot() +
  theme_bw()
```

# Naïve Models

Once we see that we have a cognitive model, I'll say the _cognitive model assumption_ is met. And when it's met, it actually has some interesting consequences.

Because observations in a cognitive model (as in, exposure to educational materials) are conditioning events rather than causal interventions, we can actually do a good job predicting their effects using naïve models. What I mean by naïve models are models that naïvely assume all beliefs are connected to some central, focal belief(s)--specifically, whichever beliefs are targetted by educational interventions.

This works because all we need to predict the expected change is a model of the marginal conditional distribution of each variable. To put it in some math, our model approximates the joint distribution over all the variables $x_1$ through $x_n$:

$$P(x_1, x_2, x_3, ..., x_n)$$

But to ask how some other belief, $y$ will change on average, given some change in another belief $x$, that's something like this:

$$E[P(y|x=1) - P(y|x=0)]$$

And for that we only need to know the conditional probability, $P(y|x)$, which we can approximate in this naïve model. So here we have a model that naïvely assumes that disease severity beliefs influence all other beliefs.

```{r, message=FALSE, warning=FALSE}

vars <- d_scored %>% select(scale) %>% filter(scale!="diseaseSevere") %>% distinct()

# naïve causal model, diseaseSevere--> all (equivalent change score prediction)
nb_arcs <- data.frame(from = rep("diseaseSevere", 13), to = vars$scale)

nb_model <- write_jags_model(nb_arcs, d_bn) %>% suppressWarnings()

# can modify this to test assumptions about direct effects of intervention ...
interv_fit <- glm(interv ~ diseaseSevere, 
                  data = interv_df,
                  family = "binomial"
                  )

nb_model <- add_node(nb_model, glm_to_jags_eq(interv_fit))

# can also just use "model" here so long as you include held_out_nodes

preds_nb <- predict_change_scores(nb_model,
                                           data.frame(interv = 0),
                                           data.frame(interv = 1),
                                           nodes_to_predict,
                                           iter = 1e5
                                           )

preds_nb <- process_predictions(preds_nb, obs_data)

plots_nb <- plot_processed_predictions(preds_nb)

plots_nb$corr_plot
plots_nb$means_plot

score_predictions(preds_nb)

```

The naïve model is comparable to the more complex cognitive model, at least when it comes to predicting the changes in beliefs following the interventions. Of course, as a model of the actual relationships among beliefs, it's terrible (see `...modelSims.Rmd` notebook for a brief exploration of that).

### Naïvely modeling multiple targetted beliefs

We can also model multiple direct evidence relations by extending the naïve model. There are probably multiple ways to extend it. What I've come up with here is to just assume that both disease severity and parental protectiveness are the two focal beliefs, and that they both influene all other beliefs. I suppose I could also add a connection between them one way or another.

```{r, message=FALSE, warning=FALSE}

vars2 <- d_scored %>% select(scale) %>% filter(scale!="diseaseSevere", scale!="overpar") %>% distinct()

# naïve causal model, diseaseSevere--> all (equivalent change score prediction)

nb_arcs2 <- data.frame(
  from = c(
    rep("diseaseSevere", 12),
    rep("overpar", 12)
  ),
  to = rep(vars2$scale, 2)
)

nb_model2 <- write_jags_model(nb_arcs2, d_bn) %>% suppressWarnings()

# can modify this to test assumptions about direct effects of intervention ...
interv_fit <- glm(interv ~ diseaseSevere + overpar, 
                  data = interv_df,
                  family = "binomial"
                  )

nb_model2 <- add_node(nb_model2, glm_to_jags_eq(interv_fit))

# can also just use "model" here so long as you include held_out_nodes

preds_nb2 <- predict_change_scores(nb_model2,
                                           data.frame(interv = 0),
                                           data.frame(interv = 1),
                                           nodes_to_predict,
                                           iter = 1e5*2.5
                                           )

preds_nb2 <- process_predictions(preds_nb2, obs_data)

plots_nb2 <- plot_processed_predictions(preds_nb2)

plots_nb2$corr_plot
plots_nb2$means_plot

score_predictions(preds_nb2)

```

This model is the best of all!, getting a whopping `r score_predictions(preds_nb2)$r^2 %>% round(3) * 100`% of the variance! Not only that, RMSE and MAE also look somewhat lower than the other models.

So, from a purely predictive standpoint, if the cognitive model assumption holds, then the naïve model might actually be the best approach to predicting belief changes. However I don't think there are any guarantees that this sort of thing will always work when thinking about multiple targetted beliefs, for one. Quickly comparing all four models, it really does look like the naïve model with both disease severity and overparenting targetted does best, for what it's worth.

```{r}
boot_scores_cog <- score_predictions_boot(preds_cog)
boot_scores_cog2 <- score_predictions_boot(preds_cog2)
boot_scores_nb <- score_predictions_boot(preds_nb)
boot_scores_nb2 <- score_predictions_boot(preds_nb2)

tibble(
  cog = sapply(boot_scores_cog, function(x){x$rmse}), 
  cog2 = sapply(boot_scores_cog2, function(x){x$rmse}),
  nb = sapply(boot_scores_nb, function(x){x$rmse}),
  nb2 = sapply(boot_scores_nb2, function(x){x$rmse}),
       ) %>%
  gather(model, rmse, cog, cog2, nb, nb2) %>%
  ggplot(aes(x=model, y = rmse)) +
  geom_boxplot() +
  theme_bw()
```

### 2018-09-18 study2/lab_pres_nb_2018-6-11.Rmd
added files

--- 2018-09-18 study2/cog-model-discrete-predictions.Rmd
@@
 ```{r load in existing objects, message=FALSE, warning=FALSE}
-# net.struct <- readRDS("net-struct-cogsci2018.rds")
+net.struct <- readRDS("net-struct-cogsci2018.rds")
 
-source("../../study1/vacc_import_data.R")
-source("../../Scripts/gmod_tools.R")
-# source("../../Scripts/virtualEvidence.R")
+source("../study1/vacc_import_data.R")
+source("../Scripts/gmod_tools.R")
+source("../Scripts/virtualEvidence.R")
 
@@
 library(patchwork)
-library(BiDAG)
-library(HydeNet)
-library(bnlearn)
-
-source("cog-model-main.R")
 ```
 
-```{r set up training split}
-# rescale beta
+```{r load and tidy study 3 data, include = F}
+# load data
+d_all <- read.csv("data/study3_data.csv")
 
-rescale_beta <- function(x, lower, upper) {
-  # rescales onto the open interval (0,1)
-  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
+# reformat to match previous analyses (i.e., 2 rows per participant)
+d_demo <- d_all %>% 
+  select(workerId, condition, gender, age, ethnicity, education, job, income,
+         political_party, political_beliefs, eligible_pretest, 
+         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
+         children_youngest_posttest, plan_parent_posttest,
+         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
+         starts_with("comments"), starts_with("duration"))
+d_pre <- d_all %>% 
+  select(workerId, ends_with("_pretest")) %>%
+  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
+            starts_with("attention_"), starts_with("comments"), 
+            starts_with("duration"))) %>%
+  rename_all(funs(gsub("_pretest", "", .))) %>%
+  mutate(phase = "pre")
+d_post <- d_all %>% 
+  select(workerId, ends_with("_posttest")) %>%
+  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
+            children_youngest_posttest, plan_parent_posttest,
+            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
+            starts_with("comments"), starts_with("duration"))) %>%
+  rename_all(funs(gsub("_posttest", "", .))) %>%
+  mutate(phase = "post")
 
-  N <- length(x)
-  res <- (x - lower) / (upper - lower)
-  res <- (res * (N - 1) + .5) / N
+d <- bind_rows(d_pre, d_post) %>% 
+  gather(question, response, -c(workerId, phase)) %>%
+  mutate(phase = factor(phase,
+                        levels = c("pre", "post")),
+         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
+         # NOTE: "response" has already been reverse coded!
+         question = factor(question),
+         scale = factor(gsub("_.*$", "", question),
+                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
+                                   "vaccStrain", "vaccTox", 
+                                   "diseaseSevere", "diseaseRare", 
+                                   "infantImmLimCap", "infantImmWeak", 
+                                   "medSkept", "hb", "nat", 
+                                   "overpar", "parentExpert"))) %>%
+  full_join(d_demo) %>%
+  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
+  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
+  distinct()
 
-  return(as.vector(res))
+# how many left?
+d %>% distinct(workerId, condition) %>% count(condition)
+
+# score all scales
+d_scored <- d %>%
+  select(workerId, condition, phase, scale, response,
+         gender:duration_posttest) %>%
+  group_by(workerId, condition, phase, scale) %>%
+  mutate(response = as.numeric(response)) %>%
+  summarise(Mean = mean(response, na.rm = TRUE)) %>%
+  ungroup() %>%
+  distinct()
+
+stderr <- function(x) {
+          sqrt(var(x[!is.na(x)]) / length(x[!is.na(x)]))
 }
 
-d_bn_scaled <- d_bn %>%
- mutate_all(function(x){rescale_beta(x,-3,3)})
+interv_df <- d_scored %>% 
+              filter(condition=="diseaseRisk") %>%
+              mutate(interv = ifelse(phase=="pre",0,1)) %>%
+              group_by(workerId) %>%
+              spread(scale, Mean)
 
-## set the seed to make your partition reproductible
-set.seed(123)
-trainInd <- sample(seq_len(nrow(d_bn_scaled)), size = floor(nrow(d_bn_scaled)*.80))
-
-train <- d_bn_scaled[trainInd, ]
-test <- d_bn_scaled[-trainInd, ]
-```
-
-# loading in data model
-
-```{r}
-# first load in mcmc results
-all_results <- readRDS("allresults.rds")
-nodes <- colnames(train)
-# then grab map dag for theory-based constraints
-merged_chains <- merge_chains(all_results[[5]])
-map_dag <- extract_mapdag(merged_chains)
-
-h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(map_dag)))
-plot(h)
-```
-
-## creating cognitive model
-
-```{r}
-# parse bn into list of parents and children
-
-arcs_df <- bnlearn_to_df(map_dag)
-
-df_to_list <- function(arcs_df, as.strings=FALSE) {
-  # take arcs_df and make list of formulas
-  arcs_df$to <- as.character(arcs_df$to)
-  arcs_df$from <- as.character(arcs_df$from)
-
-  nodes <- unique(unlist(arcs_df))
-  output <- lapply(nodes, function(node) {
-    edges <- arcs_df[which(arcs_df$to == node), "from"]
-    if (length(edges) < 1) {
-      edges <- NULL
-    }
-    list(child=node, parents=edges)
-
-  })
-  names(output) <- nodes
-  return(output)
-}
-
-graph_list <- df_to_list(arcs_df)
-
-bagOfModels <- lapply(graph_list, function(x){fit_node_cpt(x, train)})
-
-# bagNet <- HydeNetwork(bagOfModels)
-# writeNetworkModel(bagNet, pretty=TRUE)
-
-```
-
-```{r}
-# add evidence node with cpt defined 
-evid_ratio <- exp(0.4566215)
-
-evid_cpt <- make_custom_cpt(c(.5*evid_ratio,.5, (1-.5*evid_ratio), (1-.5)), c(2,2), list(diseaseSevere=c("Yes","No"), evid = c("Yes","No") ), NULL)
-# evid_cpt <- make_custom_cpt(c(.83,.5, .17, .5), c(2,2), list(diseaseSevere=c("yes","No"), evid = c("yes","no") ), NULL)
-bagOfModels$evid <- evid_cpt
-
-bagNet <- HydeNetwork(bagOfModels)
-plot(bagNet)
-writeNetworkModel(bagNet, pretty=TRUE)
-## In the future (soon), make a function to create this node cpt
-
-```
-
-__Translating hydenet model to bnlearn__
-
-below is some code to get things into the right format. Later I'll break this out into a function I guess.
-
-```{r}
-hyde_to_bn_cpt <- function(hyde_cpt) {
-  ndims <- length(dim(hyde_cpt))
-
-  if ("xtabs" %in% class(hyde_cpt)) {
-    output <- hyde_cpt/1e5
-  } else {
-
-    output <- aperm(hyde_cpt, ndims:1)
-  }
- return (output) 
-}
-
-# hyde_to_bn_cpt(bagOfModels$evid)
-
-bnlearn_models <- lapply(bagOfModels, hyde_to_bn_cpt)
-
-model_string <- as.character(map_dag)
-model_string <- paste0(model_string,"[evid|diseaseSevere]")
-model_network <- model2network(model_string)
-
-predModel <- custom.fit(model_network, dist = bnlearn_models)
-```
-
-__Generating predictions__
-
-Now I can use this model to generate predictions.
-
-```{r}
-# cpquery(predModel, event = (eval(parse(text="diseaseSevere"))=="Yes"), evidence = TRUE)
-# cpquery(predModel, event = (eval(parse(text="diseaseSevere == 'Yes'"))), evidence = TRUE)
-# cpquery(predModel, event = (eval(parse(text="diseaseSevere"))=="Yes"), evidence = (evid == "Yes"))
-
-set.seed(12345)
-
-pred0 <- sapply(nodes, function(x){
-  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence=TRUE, n = 5e5)")
-  eval(parse(text=statement))
-})
-
-pred1 <- sapply(nodes, function(x){
-  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 5e5)")
-  eval(parse(text=statement))
-})
-
-pred_changes <- pred1 - pred0
-
-pred_changes <- as.data.frame(pred_changes)
-
-pred_changes <- pred_changes %>%
-  mutate(scale = nodes) %>%
-  rename(Mean = pred_changes) %>%
-  mutate(type = "predicted")
-
-```
-
-```{r}
-source("../../study3/load-study3-data.R", chdir = TRUE)
-
-obs_changes <- d_scored %>%
-  mutate(mean = rescale_beta(mean, -3, 3)) %>%
-  spread(phase,mean) %>%
-  mutate(changeScore = post-pre) %>%
+obs_data <- d_scored %>% 
   filter(condition == "diseaseRisk") %>% 
+  spread(phase, Mean) %>%
+  mutate(score = post - pre) %>%
   group_by(scale) %>%
-  summarise(
-    Mean = mean(changeScore),
-    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()), # replace with bootstrapping
-    ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
-    ) %>%
-  mutate(type = "observed")
-
-obs_pred <- bind_rows(pred_changes, obs_changes) %>%
-  spread(type, Mean) %>%
-  group_by(scale) %>%
-  summarize_all(mean, na.rm=TRUE)
-
-cor(obs_pred$predicted, obs_pred$observed)
-
-obs_pred %>% # a bit of a hack
-  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
-  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
-  geom_point() +
-  geom_errorbar() +
-  coord_cartesian(xlim=c(-.06,.08), ylim=c(-.06,.08)) +
-  theme_bw() +
-  theme(aspect.ratio = 1)
-
-obs_pred %>%
-  gather(type, Mean, observed, predicted) %>%
-  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
-  geom_point() +
-  geom_errorbarh(height=0)
-```
-
-----------------------------------------------
-
-HydeNet prediction failures below ...
-
-```{r}
-set.seed(456)
-model0 <- compileJagsModel(bagNet)
-model1 <- compileJagsModel(bagNet, data= data.frame(evid=2))
-
-post0 <- HydeSim(model0,
-                       variable.names = nodes,
-                       n.iter = 1e5
-                       )
-
-post1 <- HydeSim(model1,
-                       variable.names = nodes,
-                       n.iter = 1e5
-                       )
-
-post0 <- post0 %>%
-  mutate(nat = ifelse(nat=="Yes",2,1)) %>%
-  mutate_all(~ . -1) %>%
-  summarize_all(mean) %>%
-  select(-chain_index, -obs_index)
-
-post1 <- post1 %>%
-  mutate(nat = ifelse(nat=="Yes",2,1)) %>%
-  mutate_all(~ . -1) %>%
-  summarize_all(mean) %>%
-  select(-evid, -chain_index, -obs_index)
-
-pred_changes <- (post1 - post0)  %>%
-  gather(scale, Mean) %>%
-  mutate(type = "predicted")
-```
-
-```{r}
-source("../../study3/load-study3-data.R", chdir = TRUE)
-
-obs_changes <- d_scored %>%
-  mutate(mean = rescale_beta(mean, -3, 3)) %>%
-  spread(phase,mean) %>%
-  mutate(changeScore = post-pre) %>%
-  filter(condition == "diseaseRisk") %>%
-  group_by(scale) %>%
-  summarise(
-    Mean = mean(changeScore),
-    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()),
-    ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
-    ) %>%
-  mutate(type = "observed")
-
-bind_rows(pred_changes, obs_changes) %>%
-  spread(type, Mean) %>%
-  group_by(scale) %>%
-  summarize_all(mean, na.rm=TRUE) %>% # a bit of a hack
-  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
-  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
-  geom_point() +
-  geom_errorbar() +
-  # coord_cartesian(xlim=c(-.1,.1), ylim=c(-.1,.1)) +
-  theme_bw() +
-  theme(aspect.ratio = 1)
-```
-
-Strong correlation, and pretty good numerically.
-But for some reason it's getting disease severity wrong!
-I really can't wrap my head around it, it's not predicting what I would expect based on the evidence ratio (when I do it manually, the predictions are more in line with observed).
-So something strange is going wrong.
-I should try making a really simple little test case.
-
-```{r}
-bind_rows(pred_changes, obs_changes) %>%
-  spread(type, Mean) %>%
-  group_by(scale) %>%
-  summarize_all(mean, na.rm=TRUE) %>%
-  mutate(abs_resid = abs(predicted - observed)) %>%
-  arrange(-abs_resid)
-```
-
-So for some reason this is not working quite right with hydenet. I'm going to translate things over to bnlearn and try taht.
-# JUNK BELOW
-----------------------------------------
-
-```{r}
-
-make_predictions_hyde <- function(hyde_model, orig_data, nodes_to_predict, nodes_held_out=c(), iter=1e3) {
-  # takes a model and dataframe and generates model predictions for variables listed in 
-  # nodes_to_predict. By default, uses all remaining nodes in orig_data. Hold out nodes from
-  # prediction with nodes_held_out. iter sets mcmc samples
-
-  pred_df <- orig_data
-  pred_df[,nodes_to_predict] <- NA
-
-  for (i in 1:nrow(pred_df)) {
-    row <- pred_df[i,]
-    row[nodes_held_out] <- NA
-    pred <- do_jags_inference(hyde_model, nodes_to_predict, data = row, iter = iter)
-    point_preds <- rowMeans(t(pred[[1]][(iter/2+1):iter,nodes_to_predict]))
-    pred_df[i,nodes_to_predict] <- point_preds
-  }
-
-  return(pred_df)
-}
-
-predict_change_scores_cog <- function(model, nodes_to_predict, iter){
-
-  preds_mean1 <- make_predictions(model, 
-                                data.frame(evid=1), 
-                                nodes_to_predict, 
-                                c(),
-                                iter = iter)
-
-  preds_mean0 <- make_predictions(model, 
-                                  data.frame(), 
-                                  nodes_to_predict, 
-                                  c("evid"),
-                                  iter = iter)
-
-  preds_mean <- preds_mean1 - preds_mean0
-}
-
-predict_change_scores_cog(bagNet, nodes, 1e4)
+  summarize(
+    observed = mean(score),
+    std_error = stderr(score))
 ```

### 2018-09-18 study2/study2-evid-ratio.Rmd
added files

---
title: "R Notebook"
output: html_notebook
---

```{r setup, include = F}
library(tidyverse)
library(psych)
# library(ggcorrplot)
library(lme4)
library(brms)
library(rms)
```

# Data prep

```{r tidy, include = F}
source("load-study2-data.R", chdir = TRUE)
```

# doing it

```{r}
rescale_beta <- function(x, lower, upper) {
  # rescales onto the open interval (0,1)
  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
  # based on Smithson & Verkuilen (2006), though this is not as principled as you might think
  # see http://dx.doi.org/10.1037/1082-989X.11.1.54.supp

  N <- length(x)
  res <- (x-lower)/(upper - lower)
  res <- (res*(N-1) + .5)/N

  return(as.vector(res))
}

d <- d_scored %>%
  filter(scale == "diseaseSevere") %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase, mean) %>% 
  mutate(condition = relevel(condition, ref="noInterv")) %>%
  mutate(evid = ifelse(condition=="noInterv",0,1))
```

```{r}
brm_fitodds <- brm(
  bf(
    post ~ log(pre/(1-pre)) + evid*logER1 + logER0,
    logER1 + logER0 ~ 1,
    nl = TRUE,
    family = Beta("logit")
     ),
  prior = prior("normal(0,3)", nlpar = "logER1") +
          prior("normal(0,3)", nlpar = "logER0"),
    # prior("uniform(0,1)", lb = 0, ub = 1, nlpar = "p0"),
  data = d,
  iter = 4000,
  warmup = 2000,
  chains = 2,
  cores = 2,
  control = list(adapt_delta=.95)
)

# brm_fitodds <- brm(
#   bf(
#     post ~ logit(pre) + evid*logER1,
#     logER1 ~ 1,
#     nl = TRUE,
#     family = Beta("logit")
#      ),
#   prior = prior("normal(0,3)", nlpar = "logER1"), 
#     # prior("uniform(0,1)", lb = 0, ub = 1, nlpar = "p0"),
#   data = d,
#   iter = 4000,
#   warmup = 2000,
#   chains = 2,
#   cores = 2,
#   control = list(adapt_delta=.95)
# )

summary(brm_fitodds)
```

```{r}
pred_data <- expand.grid(
  list(
    pre = seq(.01,.99,.01),
    evid = c(0,1)
  )
)

predict(brm_fitodds, 
        pred_data, probs=c(.05,.95)) %>%
  as_tibble() %>%
  bind_cols(pred_data) %>%
  ggplot(aes(x=pre, y=Estimate, color = factor(evid), fill = factor(evid))) +
    geom_line() +
  geom_ribbon(aes(ymin = `5%ile`, ymax = `95%ile`, color=NULL), alpha=.2) +
  geom_jitter(data=d, aes(x=pre, y=post, color=factor(evid))) +
  theme_bw()
```

```{r}
evid_ratio <- exp(fixef(brm_fitodds)[1,1])
broom::tidy(brm_fitodds) %>%
  filter(grepl("b_", term)) %>%
  mutate(evid_ratio = exp(estimate))
```

The resulting evidence ratio is `r evid_ratio`. Reasonable CPT values would be .5 and `r .5*evid_ratio` That's not that huge really ...

### 2018-09-18 study2/vacc_manyBelief_study2_analysis.Rmd
added files

---
title: 'Vaccines: Many Beliefs Study 3: Analysis'
author: "Derek Powell, Kara Weisman"
date: "2018-05-01"
output: html_notebook
---

```{r, include = F}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r setup, include = F}
library(tidyverse)
library(psych)
# library(ggcorrplot)
library(lme4)
library(brms)
library(rms)
```

# Data prep

```{r tidy, include = F}
# load data
d_all <- read.csv("../study3/data/study3_data.csv")[-1]

# reformat to match previous analyses (i.e., 2 rows per participant)
d_demo <- d_all %>% 
  select(workerId, condition, gender, age, ethnicity, education, job, income,
         political_party, political_beliefs, eligible_pretest, 
         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
         children_youngest_posttest, plan_parent_posttest,
         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
         starts_with("comments"), starts_with("duration"))
d_pre <- d_all %>% 
  select(workerId, ends_with("_pretest")) %>%
  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
            starts_with("attention_"), starts_with("comments"), 
            starts_with("duration"))) %>%
  rename_all(funs(gsub("_pretest", "", .))) %>%
  mutate(phase = "pre")
d_post <- d_all %>% 
  select(workerId, ends_with("_posttest")) %>%
  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
            children_youngest_posttest, plan_parent_posttest,
            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
            starts_with("comments"), starts_with("duration"))) %>%
  rename_all(funs(gsub("_posttest", "", .))) %>%
  mutate(phase = "post")

d <- bind_rows(d_pre, d_post) %>% 
  gather(question, response, -c(workerId, phase)) %>%
  mutate(phase = factor(phase,
                        levels = c("pre", "post")),
         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
         # NOTE: "response" has already been reverse coded!
         question = factor(question),
         scale = factor(gsub("_.*$", "", question),
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert"))) %>%
  full_join(d_demo) %>%
  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
  distinct()

# how many left?
d %>% distinct(workerId, condition) %>% count(condition)
```

```{r scores, include = F}
# score all scales
d_scored <- d %>%
  select(workerId, condition, phase, scale, response,
         gender:duration_posttest) %>%
  group_by(workerId, condition, phase, scale) %>%
  mutate(response = as.numeric(response)) %>%
  summarise(mean = mean(response, na.rm = TRUE)) %>%
  ungroup() %>%
  distinct()
```

# Score distributions

First, let's look at the distributions of scores for all scales, pre- and post-test:

```{r scores histo, fig.width = 7, fig.height = 2}
ggplot(d_scored, 
       aes(x = mean, fill = phase)) +
  # facet_wrap(~ scale, ncol = 5) +
  facet_grid(condition ~ scale) +
  geom_histogram(bins = 14, position = "identity", alpha = 0.6) +
  scale_x_continuous(breaks = seq(-3, 3, 1)) + 
  theme_bw() +
  labs(title = "distributions of scores by scale, condition, and phase (pre/post)")
```

```{r scores density plot, fig.width = 7, fig.height = 2, include = F}
# ggplot(d_scored, 
#        aes(x = mean, fill = phase, color = phase)) +
#   # facet_wrap(~ scale, ncol = 5) +
#   facet_grid(condition ~ scale) +
#   geom_density(alpha = 0.5) +
#   scale_x_continuous(breaks = seq(-3, 3, 1)) + 
#   theme_bw() +
#   labs(title = "distributions of scores by scale, condition, and phase (pre/post)")
```

It looks like there's a lot of overlap in the pre- and post-test distrubtions for all scales - though a few hints of subtle shifts (e.g., in `diseaseRare`, `vaccIntent`).

# Visual comparison of pre- vs. post-intervention

Let's compare participants' responses pre- vs. post-intervention on all scales. I'll plot both mean pre- and post-intervention scores, as well as mean difference scores (note separate axes):

```{r plot means, fig.width = 3, fig.asp = 3}
d_means <- d_scored %>%
  distinct(workerId, condition, phase, scale, mean) %>%
  group_by(condition, phase, scale) %>%
  # summarise(Mean = mean(mean, na.rm = T),
  #           Lower = Mean - 2 * sd(mean, na.rm = T)/sqrt(n()),
  #           Upper = Mean + 2 * sd(mean, na.rm = T)/sqrt(n())) %>%
  do(data.frame(rbind(smean.cl.boot(.$mean)))) %>% # bootstrapped 95% CI
  ungroup() %>%
  distinct() %>%
  mutate(scale = factor(scale,
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert")),
         condition = factor(condition,
                            levels = c("diseaseRisk", "autismCorr", "noInterv")))

g_means <- ggplot(d_means,
                  aes(x = phase, y = Mean,
                      color = condition, group = condition)) +
  facet_wrap(~ scale, ncol = 3) +
  geom_path(position = position_dodge(width = 0.1)) +
  geom_linerange(aes(ymin = Lower, ymax = Upper),
                 position = position_dodge(width = 0.1)) +
  geom_point(size = 3,
             position = position_dodge(width = 0.1)) +
  scale_y_continuous("mean score", 
                     # limits = c(-3, 3),
                     breaks = seq(-3, 3, 1)) +
  scale_color_brewer(palette = "Set1", direction = -1) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(title = "mean scores by phase and condition",
       subtitle = "error bars are bootstrapped 95% CIs")

g_means
```

```{r plot diffs, fig.width = 3, fig.asp = 3}
d_diffs <- d_scored %>%
  spread(phase, mean) %>%
  mutate(post_pre_diff = post - pre) %>%
  group_by(condition, scale) %>%
  do(data.frame(rbind(smean.cl.boot(.$post_pre_diff)))) %>%
  ungroup() %>%
  mutate(scale = factor(scale,
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert")),
         condition = factor(condition,
                            levels = c("diseaseRisk", "autismCorr", "noInterv")))

g_diffs <- ggplot(d_diffs,
                  aes(x = condition, y = Mean, 
                      color = condition, group = condition)) +
  facet_wrap(~ scale, ncol = 3) +
  geom_hline(yintercept = 0, lty = 2, size = 0.5) +
  geom_linerange(aes(ymin = Lower, ymax = Upper)) +
  geom_point(size = 3) +
  scale_y_continuous("mean diff") + #, 
                     # limits = c(-3, 3), 
                     # breaks = seq(-3, 3, 1)) +
  scale_color_brewer(palette = "Set1", direction = -1) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "mean difference scores by scale and condition",
       subtitle = "error bars are 95% bootstrapped CIs")

g_diffs
```

```{r plot means and diffs, fig.width = 3, fig.asp = 3}
multiplicand <- 6
multi_fun <- function(x, multi = multiplicand){return(x * multi)}
g_means +
  geom_segment(aes(x = 2.5, xend = 3.5, y = 0, yend = 0), 
               color = "black", lty = "dashed", size = 0.3) +
  geom_linerange(data = d_diffs %>% 
                   mutate_at(vars(Mean, Lower, Upper), funs(multi_fun)) %>%
                   mutate(phase = "diff"),
                 aes(x = phase, ymin = Lower, ymax = Upper),
                 position = position_dodge(width = 0.5)) +
  geom_point(data = d_diffs %>%
               mutate_at(vars(Mean, Lower, Upper), funs(multi_fun)) %>%
               mutate(phase = "diff"),
             aes(x = phase, y = Mean),
             position = position_dodge(width = 0.5),
             size = 2, shape = 17) +
  scale_x_discrete(limits = c("pre", "post", "diff")) +
  scale_y_continuous("mean score", breaks = seq(-3, 3, 1),
                     sec.axis = sec_axis(~./multiplicand, 
                                         name = "mean diff")) +
  scale_color_brewer(palette = "Set1", direction = -1) +
  theme(legend.position = "top", 
        panel.grid.minor.y = element_blank()) +
  labs(title = "means and mean difference scores by scale and condition",
       subtitle = "error bars are 95% bootstrapped CIs\nNOTE:use left y-axis for pre and post phases, right y-axis for difference scores")
```

Some interesting things might be going on here! Probably most useful paired with some actual stats...

# Regression analyses

First, let's choose how to code our data - I've set up contrast coding, effect coding and dummy coding options here, and I'll go with dummy-coding for now (with `noInterv` and `pre` as the baselines for comparison for condition and phase, respectively).

```{r contrasts, include = F}
# # orthogonal contrast coding
# contrasts(d_scored$condition) <- cbind(interv_none = c(1, 1, -2),
#                                        DR_AC = c(1, -1, 0))
# contrasts(d_scored$phase) <- cbind(post_GM = c(-1, 1))

# # effect coding
# contrasts(d_scored$condition) <- cbind(DR_GM = c(1, 0, -1),
#                                        AC_GM = c(0, 1, -1))
# contrasts(d_scored$phase) <- cbind(post_GM = c(-1, 1))

# dummy coding
contrasts(d_scored$condition) <- cbind(DR_none = c(0, 1))
contrasts(d_scored$phase) <- cbind(post_pre = c(0, 1))
```

```{r print contrasts}
# print out contrasts
contrasts(d_scored$condition)
contrasts(d_scored$phase)
```

## By scale

This is rather crazy (and of course exploratory) endeavor, and very vulnerable to multiple comparisons... but let's look at the effects on all scales individually.

### Beliefs about vaccines

#### Intentions to vaccinate (`vaccIntent`)

<span style="color:blue">**NOTE**: This is our main DV of interest.</span>

```{r regression vaccIntent}
# vaccIntent
r1_vaccIntent <- lmer(mean ~ phase * condition + (1 | workerId),
                      data = d_scored %>% filter(scale == "vaccIntent"))
summary(r1_vaccIntent)
```

Success! In the form of a significant interaction between phase and condition  (`phasepost_pre:conditionDR_none`: change from pre- to post-intervention in the Disease Risk vs. No Intervention conditions).

An analysis with change scores (a la Horne, Powell, et al. (2015, *PNAS*)):

```{r regression change scores vaccIntent}
# vaccIntent
r2_vaccIntent <- lm(diff ~ condition,
                    data = d_scored %>% 
                      filter(scale == "vaccIntent") %>%
                      spread(phase, mean) %>%
                      mutate(diff = post - pre))
summary(r2_vaccIntent)

# # in case you want to check equivalence to ANOVA
# r3_vaccIntent <- oneway.test(diff ~ condition,
#                              data = d_scored %>%
#                                filter(scale == "vaccIntent") %>%
#                                spread(phase, mean) %>%
#                                mutate(diff = post - pre),
#                              var.equal = TRUE)
# r3_vaccIntent
```

Again, success!

Here's the relevant plot from the *PNAS* paper:

```{r plot change scores vaccIntent, fig.width = 2, fig.height = 2}
ggplot(d_diffs %>% filter(scale == "vaccIntent"),
       aes(x = condition, y = Mean, fill = condition)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.1) +
  scale_y_continuous("vaccIntent change score", limits = c(-.25, .5)) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(subtitle = "error bars are 95% bootstrapped CIs")
```

#### Vaccine danger (`vaccDanger`)

```{r regression vaccDanger}
# vaccDanger
r1_vaccDanger <- lmer(mean ~ phase * condition + (1 | workerId),
                      data = d_scored %>% filter(scale == "vaccDanger"))
summary(r1_vaccDanger)
```

#### Vaccine efficacy (`vaccEff`)

```{r regression vaccEff}
# vaccEff
r1_vaccEff <- lmer(mean ~ phase * condition + (1 | workerId),
                   data = d_scored %>% filter(scale == "vaccEff"))
summary(r1_vaccEff)
```

#### Vaccines' tendency to strain the infant immune system (`vaccStrain`)

```{r regression vaccStrain}
# vaccStrain
r1_vaccStrain <- lmer(mean ~ phase * condition + (1 | workerId),
                      data = d_scored %>% filter(scale == "vaccStrain"))
summary(r1_vaccStrain)
```

#### Vaccine toxicity (`vaccTox`)

```{r regression vaccTox}
# vaccTox
r1_vaccTox <- lmer(mean ~ phase * condition + (1 | workerId),
                   data = d_scored %>% filter(scale == "vaccTox"))
summary(r1_vaccTox)
```

### Beliefs about diseases

#### Disease severity (`diseaseSevere`)

<span style="color:blue">**NOTE**: This is the scale that we thought the Disease Risk intervention should affect most directly.</span>

```{r regression diseaseSevere}
# diseaseSevere
r1_diseaseSevere <- lmer(mean ~ phase * condition + (1 | workerId),
                         data = d_scored %>% filter(scale == "diseaseSevere"))
summary(r1_diseaseSevere)
```

#### Disease rarity (`diseaseRare`)

```{r regression diseaseRare}
# diseaseRare
r1_diseaseRare <- lmer(mean ~ phase * condition + (1 | workerId),
                       data = d_scored %>% filter(scale == "diseaseRare"))
summary(r1_diseaseRare)
```

### Beliefs about infants' immune systems

#### Limited capacity of infants' immune systems (`infantImmLimCap`)

```{r regression infantImmLimCap}
# infantImmLimCap
r1_infantImmLimCap <- lmer(mean ~ phase * condition + (1 | workerId),
                           data = d_scored %>% filter(scale == "infantImmLimCap"))
summary(r1_infantImmLimCap)
```

#### Weakness of infants' immune systems (`infantImmWeak`)

```{r regression infantImmWeak}
# infantImmWeak
r1_infantImmWeak <- lmer(mean ~ phase * condition + (1 | workerId),
                         data = d_scored %>% filter(scale == "infantImmWeak"))
summary(r1_infantImmWeak)
```

### Other beliefs, attitudes, and worldviews

#### Medical skepticism (`medSkept`)

```{r regression medSkept}
# medSkept
r1_medSkept <- lmer(mean ~ phase * condition + (1 | workerId),
                    data = d_scored %>% filter(scale == "medSkept"))
summary(r1_medSkept)
```

#### Holistic balance (`hb`)

```{r regression hb}
# hb
r1_hb <- lmer(mean ~ phase * condition + (1 | workerId),
              data = d_scored %>% filter(scale == "hb"))
summary(r1_hb)
```

#### Naturalism (`nat`)

```{r regression nat}
# nat
r1_nat <- lmer(mean ~ phase * condition + (1 | workerId),
               data = d_scored %>% filter(scale == "nat"))
summary(r1_nat)
```

#### Overparenting (`overpar`)

```{r regression overpar}
# overpar
r1_overpar <- lmer(mean ~ phase * condition + (1 | workerId),
                   data = d_scored %>% filter(scale == "overpar"))
summary(r1_overpar)
```

#### Parental Expertise (`parentExpert`)

```{r regression parentExpert}
# parentExpert
r1_parentExpert <- lmer(mean ~ phase * condition + (1 | workerId),
                        data = d_scored %>% filter(scale == "parentExpert"))
summary(r1_parentExpert)
```

# Other stuff

## Violin plots

With violin plots, we can see the full distribution of scores at each time point in each condition:

```{r plot violin, fig.width = 3, fig.height = 5}
ggplot(d_scored,
       aes(x = interaction(phase, condition), y = mean, # fill = condition, 
           group = interaction(phase, condition))) +
  facet_wrap(~ scale, ncol = 3) +
  geom_point(aes(color = condition),
             position = position_jitter(width = 0.3, height = 0), 
             alpha = 0.5) +
  # geom_boxplot(alpha = 0) +
  geom_violin(alpha = 0,
              draw_quantiles = c(0.25, 0.5, 0.75)) +
  scale_y_continuous("mean score", 
                     limits = c(-3, 3), 
                     breaks = seq(-3, 3, 1)) +
  scale_x_discrete("phase by condition",
                   labels = rep(c("pre", "post"), 3)) +
  theme_bw() +
  theme(legend.position = "bottom") + #,
        # axis.text.x = element_text(angle = 90, hjust = 1))
  labs(title = "violin plot of pre- and post-intervention scores by scale and condition",
       subtitle = "horizontal lines correspond to 25th, 50th, and 75th percentiles")
```

# Derek's analyses

_DATE_: March 13, 2018 3:52 PM

I'm going to pick up here and do some further regression analyses. I'll look at this data in the way I *wish* we'd looked at the original PNAS data.

That is, (1) using an ordinal HLM regression over the five separate scale items (conceptually, I think, similar to SEM-style approaches), and (2) using beta regression.

There are two general model forms that I think are reasonable for looking at this. First:

```
response ~ phase * condition
```

Kara already tried this general approach, saving the model as `r1_vaccIntent`. So the only difference here will be the distributions I use. In this case, the interaction term is required, and the real thing to test is the phase*condition interaction.

And second:

```
post_response ~ pre_response * condition
```

Here pre_response could be the response on the overall pre-test scale, or the individual items. In addition, the interaction terms are optional, as warranted by the data. I'd wager this is the more familiar approach for most psychologists.

## Ordinal HLM

### Predicting "response"

```{r}
devtools::source_gist(id = "f1994c0f8325abbc5d300600744af39d", filename="cbrm.R")

library(brms)
fit_ord <- cbrm(response ~ condition * phase + (1|workerId) + (1|question),
               data = d %>%
                    filter(scale=="vaccIntent") %>%
                    mutate(
                      condition = relevel(condition, ref="noInterv"),
                      response = response + 4),
               family=cumulative(),
               control = list(adapt_delta = .85),
               cores = parallel::detectCores(),
               iter = 2000,
               cached_file = "fit_ord.rds")
summary(fit_ord)
```

### Predicting post-test

Here `pre` is the specific item pre-test score and `preMean` is the mean of the scale at pretest.

```{r}
d1 <- d %>%
  filter(scale=="vaccIntent") %>%
  mutate(condition = relevel(condition, ref="noInterv")) %>%
  spread(phase,response) %>%
  select(pre, post, condition, workerId, question) %>%
  {
    {. -> tmp} %>%
      group_by(workerId) %>%
      summarise(preMean = mean(pre)) %>%
      mutate(preMean = scale(preMean)) %>%
      left_join(tmp, by = "workerId")
  } %>%
  mutate(post = post + 4)
```

```{r}
fit_ord2 <- cbrm(post ~ condition + preMean + (1|workerId) + (1|question),
               data=d1,
               family=cumulative(),
               control = list(adapt_delta = .85),
               cores = parallel::detectCores(),
               iter = 2000,
               cached_file = "fit_ord2.rds")
summary(fit_ord2)
```

## Regression on scale averages

Recall, Kara already looked at a normal regression on responses with `r1_vaccIntent` model.

### Normal regression: predicting post-test

```{r}
d2 <- d_scored %>% filter(scale=="vaccIntent") %>% spread(phase,mean) %>% mutate(condition = relevel(condition, ref="noInterv"))

contrasts(d2$condition) <- cbind(diseaseRisk = c(0, 1))

fit.lm <- lm(post ~ scale(pre) * condition,
                    data=d2)
summary(fit.lm)
```

### Beta regression: response

A beta regression on the responses accords with the linear regression on responses--slight positive effect of diseaseRisk, slight negative effect of autism correction, but too much uncertainty overall.

But, our response variable isn't really all that appropriate for a linear regression, even if many researchers would be happy with that results and move on. Instead, vaccIntent is bounded and highly skewed. That makes it suitable for beta regression.

```{r}
rescale_beta <- function(x, lower, upper) {
  # rescales onto the open interval (0,1)
  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
  # based on Smithson & Verkuilen (2006), though this is not as principled as you might think
  # see http://dx.doi.org/10.1037/1082-989X.11.1.54.supp

  N <- length(x)
  res <- (x-lower)/(upper - lower)
  res <- (res*(N-1) + .5)/N

  return(as.vector(res))
}
# 
# fit.betaR<- brm(mean ~ condition * phase + (1|workerId), 
#                data=d_scored %>% mutate(mean = rescale_beta(mean,-3,3)),
#                family=Beta(),
#                control = list(adapt_delta = .85),
#                cores = parallel::detectCores(),
#                iter = 2000)
# 
# summary(fit.betaR)
```

### Beta regresstion: posttest

```{r}
library(betareg)

contrasts(d2$condition) <- cbind(diseaseRisk = c(0, 1))

fit.betaInt <- betareg(post ~ scale(pre) * condition,
                    data=d2 %>% mutate(post=rescale_beta(post,-3,3)))

summary(fit.betaInt)
```

A plot ...

```{r}

fit.olsScaled <- lm(post ~ scale(pre) * condition, data=d2 %>% mutate(post=rescale_beta(post,-3,3)))

d2 %>% 
  mutate(post=rescale_beta(post,-3,3)) %>%
  select(condition, pre, post) %>%
  bind_cols(predict(fit.betaInt) %>% as_tibble()) %>%
  rename(predictionBeta=value) %>%
  bind_cols(predict(fit.olsScaled) %>% as_tibble()) %>%
  rename(predictionOLS=value) %>%

ggplot(aes(x = pre, y = post, color=condition)) +
  geom_jitter(height=.1, width=.05, alpha=.8, shape=1) +
  geom_line(aes(y = predictionBeta, linetype="Beta")) +
  geom_line(aes(y = predictionOLS, linetype="OLS")) +
  # geom_line(aes(y = predict(fit.ols, vaccW),
  #               colour = "OLS", linetype = "OLS")) +
  # scale_colour_manual("", values = c("red", "blue")) +
  scale_linetype_manual("", values = c("solid", "dashed")) +
  theme_bw()
```

### 2018-09-18 study2/vacc_manyBelief_study2_modelsims.Rmd
added files

---
title: 'Vaccines: Many Beliefs Study 3 - Simulations'
author: "Kara Weisman, Derek Powell"
date: "May 2, 2018"
output: 
  html_notebook: 
    code_folding: hide
---

```{r setup, include = F}
library(tidyverse)

```

__As of May 2, 2018 all text in this notebook is just copy/pasted from the study2 notebook, so should largely be disregarded. will fill this in later__

# A few initial thoughts

Fundamentally, there are two major questions we want to ask/answer:

1. How well can we predict the effect of the intervention on other beliefs using a previously-learned network (or by averaging over networks)?
2. Given what we know about the intervention effect, what is the best model of the belief system?

The first is an out-of-sample prediction question, the second is more a model fit question. The first can be answered by generating predictions from hydenet, or possibly even by generating predictions with BRMS and using rejection sampling (since just conditioning on the assigned condition variable). The second can be addressed with either a cross validation and prediction scheme, or with WAIC via BRMS, either using imputed data or using a two-stage fitting process where posteriors from stage 1 are passed in as priors in stage 2.

In this notebook, I'm going to focus on the first issue: predicting effects of interventions from learned networks.

```{r tidy, include = F}
# load data
d_all <- read.csv("data/study3_data.csv")

# reformat to match previous analyses (i.e., 2 rows per participant)
d_demo <- d_all %>% 
  select(workerId, condition, gender, age, ethnicity, education, job, income,
         political_party, political_beliefs, eligible_pretest, 
         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
         children_youngest_posttest, plan_parent_posttest,
         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
         starts_with("comments"), starts_with("duration"))
d_pre <- d_all %>% 
  select(workerId, ends_with("_pretest")) %>%
  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
            starts_with("attention_"), starts_with("comments"), 
            starts_with("duration"))) %>%
  rename_all(funs(gsub("_pretest", "", .))) %>%
  mutate(phase = "pre")
d_post <- d_all %>% 
  select(workerId, ends_with("_posttest")) %>%
  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
            children_youngest_posttest, plan_parent_posttest,
            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
            starts_with("comments"), starts_with("duration"))) %>%
  rename_all(funs(gsub("_posttest", "", .))) %>%
  mutate(phase = "post")

d <- bind_rows(d_pre, d_post) %>% 
  gather(question, response, -c(workerId, phase)) %>%
  mutate(phase = factor(phase,
                        levels = c("pre", "post")),
         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
         # NOTE: "response" has already been reverse coded!
         question = factor(question),
         scale = factor(gsub("_.*$", "", question),
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert"))) %>%
  full_join(d_demo) %>%
  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
  distinct()

# how many left?
d %>% distinct(workerId, condition) %>% count(condition)
```

```{r scores, include = F}
# score all scales
d_scored <- d %>%
  select(workerId, condition, phase, scale, response,
         gender:duration_posttest) %>%
  group_by(workerId, condition, phase, scale) %>%
  mutate(response = as.numeric(response)) %>%
  summarise(Mean = mean(response, na.rm = TRUE)) %>%
  ungroup() %>%
  distinct()
```

# Predicting scale averages

Let's see what the model predicts based on the change in the scale averages from pre-test to post-test. To transform this into something more like a real "fit", one approach is to predict a distribution of change scores and then compare the predicted and observed distributions.

### Disease Risk Condition

I'll generate predictions for each of the 13 other nodes with _diseaseSevere_ = pre-test mean and _diseaseSevere_ = post-test mean, and see how those other nodes change. This is like imagining that all that's changed between pre- and post-test is the information affecting diseaseSevere beliefs. So, conditioned only on what we know about how that changed, what should we expect would also change?

```{r}

summarize <- summarise
diseaseSevereMean0 <- d_scored %>% 
  filter(condition=="diseaseRisk", scale=="diseaseSevere", phase=="pre") %>% 
  summarize(mean = mean(Mean)) %>%
  as.numeric()

diseaseSevereMean1 <- d_scored %>% 
  filter(condition=="diseaseRisk", scale=="diseaseSevere", phase=="post") %>% 
  summarize(mean = mean(Mean)) %>%
  as.numeric()

```

Once we start visualizing the error inherent in the data and estimates, only the prediction for "diseaseRare", "overpar", and "vaxtox" lie more than 1 standard error away from the observed mean. The all-important "vaxIntent" prediction is right about 1 SE away from the observed mean.

That's part win for the model and part failure of the data to provide enough precision to really assess it strongly.

Below I do the actual inference with mcmc in jags, sampling from the multivariate distribution defined by the model graph.

```{r}
set.seed(123)
library(HydeNet)
library(rjags)
library(bnlearn)

# load in model from cogsci paper
# net.fit <- readRDS("net-fit-cogsci2018.rds")
net.struct <- readRDS("net-struct-cogsci2018.rds")

# load in data from cogsci paper
source("../study1/vacc_import_data.R")
source("../Scripts/gmod_tools.R")
# get model out of HYDE network

# # HERE WE CAN TEST DIFFERENT MODELS! THIS IS A QUICK HACK JUST TO SEE IF THINGS ARE SIMILAR
# net.struct <- mmhc(d_bn)

my_hyde_network <- bnlearn_to_hyde_string(net.struct)
my_hyde_network <- HydeNetwork(as.formula(my_hyde_network), data=as.data.frame(d_bn))

jags_model <- writeNetworkModel(my_hyde_network)

do_jags_inference <- function(model, variable.names, data = NULL, iter = 1e4, silent=TRUE) {
  if (silent) {
    pbar <- "none"
  } else {
    pbar <- "text"
  }

  jags <- jags.model(textConnection(model), data = data, quiet=silent)
  model_samples <- coda.samples(jags, variable.names, iter*2, progress.bar="none")
  return(model_samples)
}

make_predictions <- function(model, orig_data, nodes_to_predict, nodes_held_out=c(), iter=1e4) {
  # takes a model and dataframe and generates model predictions for variables listed in 
  # nodes_to_predict. By default, uses all remaining nodes in orig_data. Hold out nodes from
  # prediction with nodes_held_out. iter sets mcmc samples

  pred_df <- orig_data
  pred_df[,nodes_to_predict] <- NA

  for (i in 1:nrow(pred_df)) {
    row <- pred_df[i,]
    row[nodes_held_out] <- NA
    pred <- do_jags_inference(model, nodes_to_predict, data = row, iter = iter)
    point_preds <- rowMeans(t(pred[[1]][(iter/2+1):iter,nodes_to_predict]))
    pred_df[i,nodes_to_predict] <- point_preds
  }

  return(pred_df)
}

x1 <- as.data.frame(t(colMeans(d_bn)))
x2 <- as.data.frame(t(colMeans(d_bn)))

x1[,"diseaseSevere"] <- diseaseSevereMean0
x2[,"diseaseSevere"] <- diseaseSevereMean1

vars <- d_scored %>% select(scale) %>% filter(scale!="diseaseSevere") %>% distinct()
pred0 <- make_predictions(jags_model, x1, as.character(vars$scale),iter=1e5)
pred1 <- make_predictions(jags_model, x2, as.character(vars$scale),iter=1e5)

pred0 <- pred0 %>% as_tibble() %>% gather(scale, value) %>% mutate(phase = "pre")
pred1 <- pred1 %>% as_tibble() %>% gather(scale, value) %>% mutate(phase = "post")

predictions <- pred0 %>% 
  bind_rows(pred1)

```

Recall, here's the network ...

```{r}
plot(my_hyde_network)
```

Predicted change scores against observed change scores (error bars = 95% CI) ...

```{r}
# make change score df with error info
# standard error function
stderr <- function(x) {
          sqrt(var(x[!is.na(x)]) / length(x[!is.na(x)]))
}

obsMeans <- d_scored %>% 
  filter(condition == "diseaseRisk") %>% 
  spread(phase, Mean) %>%
  mutate(score = post - pre) %>%
  group_by(scale) %>%
  summarize(change_score = mean(score),
            std_error = stderr(score)) %>%
  filter(scale!="diseaseSevere") %>%
  mutate(type="observed")

# %>% 
#   summarize(mean_resp = mean(Mean),
#             std_error = stderr(Mean)) %>%

predMeans <- predictions %>% 
  group_by(scale,phase) %>% 
  summarize(mean_resp = mean(value)) %>%
  mutate(type="predicted") %>%
  spread(phase, mean_resp) %>%
  # group_by(scale) %>%
  mutate(change_score = post - pre,
            std_error = 0)

d_sim <- obsMeans %>% bind_rows(predMeans)

d_sim %>%
  mutate(
         UL = change_score + std_error*1.96,
         LL = change_score - std_error*1.96
         ) %>%
  ggplot(aes(y = reorder(scale, change_score),
             x = change_score,
             xmax = UL, 
             xmin = LL, 
             color = type)) +
  geom_point(shape=17, size=3) +
  geom_errorbarh(height=0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
simMean <- d_sim %>% 
  select(-post,-pre, -std_error) %>%
  filter(scale!="diseaseSevere") %>%
  group_by(type,scale) %>%
  spread(type, change_score)

simMeanCor <- cor(simMean$predicted, simMean$observed) %>% round(3)

simMean %>%
  ggplot(aes(x=predicted, y=observed)) +
  geom_point() +
  geom_text(aes(x=-.1, y= .2, label=paste("r =",simMeanCor))) +
  geom_smooth(method="lm") +
  labs(title="Average difference scores") +
  theme(aspect.ratio = 1)
```

# bootstrapping CI

Here I'm going to bootstrap a confidence interval for the correlation between model predictions and observations for aggregated change scores across the 13 predicted scales.

I was thinking that it's not quite right to do your standard "significance" test on this correlation, as these predicted/observed change scores aren't values sampled from a population of variables. Instead, they represent their own population, but their measurement is uncertain, with that uncertainty coming from the participant-level data.

As I reflect on this I'm potentially a bit out of my depth, statistically. But the idea was I would take bootstrap samples of the data, make model predictions for each, then calculate the correlation with obtained values.

The results give a bit more confidence about the estimate than you'd have from the CI you'd get just treating the 13 points as a sample from a population (.303 to .914).

```{r}
# watch out! this takes a good 20 min to run ...

vars <- d_scored %>% select(scale) %>% filter(scale!="diseaseSevere") %>% distinct()

boot_n <- 500
iters <- 1:boot_n
cors <- rep(NA,boot_n)

d_scored_wide <- d_scored %>%
  filter(condition=="diseaseRisk") %>%
  unite(all, scale, phase) %>%
  spread(all, Mean)

for (i in iters) {

  # resample d_scored as d_boot
  d_boot <- sample_n(d_scored_wide, size = nrow(d_scored_wide), replace=TRUE)

  x1 <- as.data.frame(t(colMeans(d_bn)))
  x2 <- x1

  # calculate mean from d_boot
  diseaseSevereMean0 <- d_boot %>% 
    summarize(mean=mean(diseaseSevere_pre)) %>%
    as.numeric()

  diseaseSevereMean1 <- d_boot %>% 
    summarize(mean=mean(diseaseSevere_post)) %>%
    as.numeric()

  x1[,"diseaseSevere"] <- diseaseSevereMean0
  x2[,"diseaseSevere"] <- diseaseSevereMean1

  # make predictions
  pred0 <- make_predictions(jags_model, x1, as.character(vars$scale), iter = 5*1e4)
  pred1 <- make_predictions(jags_model, x2, as.character(vars$scale), iter = 5*1e4)

  pred0 <- pred0 %>% as_tibble() %>% gather(scale, value) %>% mutate(phase="pre")
  pred1 <- pred1 %>% as_tibble() %>% gather(scale, value) %>% mutate(phase="post")

  predictions <- pred0 %>% 
    bind_rows(pred1)

  # calculate observed change scores
  obsMeans <- d_boot %>%
    mutate(id = row_number()) %>% # all this to get a unique ID for each "participant"
    gather(scale, Mean,diseaseRare_post:vaccTox_pre) %>% 
    mutate(phase = ifelse(grepl("_post", scale),"post","pre")) %>%
    mutate(scale = gsub("_.*","",scale)) %>%
    spread(phase,Mean) %>%
    mutate(change = post-pre) %>%
    group_by(scale) %>%
    summarize(change_score = mean(change),
          std_error = stderr(change)) %>%
    filter(scale!="diseaseSevere") %>%
    mutate(type="observed")

  predMeans <- predictions %>% 
    group_by(scale,phase) %>% 
    summarize(mean_resp = mean(value)) %>%
    mutate(type="predicted") %>%
    spread(phase, mean_resp) %>%
    # group_by(scale) %>%
    mutate(change_score = post - pre,
              std_error = 0)
  # combine with predictions
  d_sim <- obsMeans %>% bind_rows(predMeans)

  simMean <- d_sim %>% 
    select(-post,-pre, -std_error) %>%
    filter(scale!="diseaseSevere") %>%
    group_by(type,scale) %>%
    spread(type, change_score)

  cors[i] <- cor(simMean$predicted, simMean$observed)
}

```

The mean correlation value is `r round(mean(cors),3)` and the bootstrapped 95% CI does not include zero. So, minimally, the model is picking up on _something_. Below is a histogram of correlation values, with a line marking the observed correlation in the original sample.

```{r}
mean(cors)
quantile(cors, c(.025,.975))

hist(cors, breaks = 20)
abline(v = .776, col="red")
```

# Modeling mean changes as causal model ...

```{r}
surgery_graph <- net.struct %>%
  drop.arc("vaccEff", "diseaseSevere") %>%
  drop.arc("infantImmLimCap", "diseaseSevere")

causal_network <- bnlearn_to_hyde_string(surgery_graph)
causal_network <- HydeNetwork(as.formula(causal_network), data=as.data.frame(d_bn))

jags_causal_model <- writeNetworkModel(causal_network)

x1 <- as.data.frame(t(colMeans(d_bn)))
x2 <- as.data.frame(t(colMeans(d_bn)))

x1[,"diseaseSevere"] <- diseaseSevereMean0
x2[,"diseaseSevere"] <- diseaseSevereMean1

vars <- d_scored %>% select(scale) %>% filter(scale!="diseaseSevere") %>% distinct()
pred0 <- make_predictions(jags_causal_model, x1, as.character(vars$scale),iter=1e5)
pred1 <- make_predictions(jags_causal_model, x2, as.character(vars$scale),iter=1e5)

pred0 <- pred0 %>% as_tibble() %>% gather(scale, value) %>% mutate(phase = "pre")
pred1 <- pred1 %>% as_tibble() %>% gather(scale, value) %>% mutate(phase = "post")

predictions <- pred0 %>% 
  bind_rows(pred1)

obsMeans <- d_scored %>% 
  filter(condition == "diseaseRisk") %>% 
  spread(phase, Mean) %>%
  mutate(score = post - pre) %>%
  group_by(scale) %>%
  summarize(change_score = mean(score),
            std_error = stderr(score)) %>%
  filter(scale!="diseaseSevere") %>%
  mutate(type="observed")

predMeans <- predictions %>% 
  group_by(scale,phase) %>% 
  summarize(mean_resp = mean(value)) %>%
  mutate(type="predicted") %>%
  spread(phase, mean_resp) %>%
  # group_by(scale) %>%
  mutate(change_score = post - pre,
            std_error = 0)

d_sim <- obsMeans %>% bind_rows(predMeans)

d_sim %>%
  mutate(
         UL = change_score + std_error*1.96,
         LL = change_score - std_error*1.96
         ) %>%
  ggplot(aes(y = reorder(scale, change_score),
             x = change_score,
             xmax = UL, 
             xmin = LL, 
             color = type)) +
  geom_point(shape=17, size=3) +
  geom_errorbarh(height=0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
simMean <- d_sim %>% 
  select(-post,-pre, -std_error) %>%
  filter(scale!="diseaseSevere") %>%
  group_by(type,scale) %>%
  spread(type, change_score)

simMeanCor <- cor(simMean$predicted, simMean$observed) %>% round(3)

simMean %>%
  ggplot(aes(x=predicted, y=observed)) +
  geom_point() +
  geom_text(aes(x=-.1, y= .2, label=paste("r =",simMeanCor))) +
  geom_smooth(method="lm") +
  labs(title="Average difference scores") +
  theme(aspect.ratio = 1)
```

The model does a very poor job of predicting change in attitudes if we treat it as a causal model.

# Baseline model (naïve bayes)

To evaluate the performance of our model, we should compare it to something else. I think a good baseline candidate is a "naïve bayes" or naïve causal model--where diseaseSevere predicts all other beliefs. This could be simulated by a series of linear regressions, but I think it will actually be easier to put it into hydenet.

Visually ...

```{r}
vars <- d_scored %>% select(scale) %>% filter(scale!="diseaseSevere", scale!="overpar") %>% distinct()

# naïve causal model, diseaseSevere--> all (equivalent change score prediction)
# nb_arcs <- data.frame(from = rep("diseaseSevere", 13), to = vars$scale)
nb_arcs <- data.frame(from = c(
  rep("diseaseSevere", 12),
  rep("overpar", 12)
  ), 
                      to = rep(vars$scale,2))

# # regression predicting vaccIntent (poor change score prediction)
# nb_arcs <- data.frame(from = names(d_bn), to = rep("vaccIntent", 14)) %>% filter(from!="vaccIntent")

# # naïve bayes, vacc intent "classifier" (slightly weaker change score prediction)
# nb_arcs <- data.frame(to = names(d_bn), from = rep("vaccIntent", 14)) %>% filter(to!="vaccIntent")

hyde_nb <- df_to_hyde_string(nb_arcs)
nb_hyde_network <- HydeNetwork(as.formula(hyde_nb), data=as.data.frame(d_bn))

nb_jags_model <- writeNetworkModel(nb_hyde_network)

plot(nb_hyde_network)
```

```{r}

x1 <- as.data.frame(t(colMeans(d_bn)))
x2 <- as.data.frame(t(colMeans(d_bn)))

x1[,"diseaseSevere"] <- diseaseSevereMean0
x2[,"diseaseSevere"] <- diseaseSevereMean1

pred0_nb <- make_predictions(nb_jags_model, x1, as.character(vars$scale),iter=1e5)
pred1_nb <- make_predictions(nb_jags_model, x2, as.character(vars$scale),iter=1e5)

pred0_nb <- pred0_nb %>% as_tibble() %>% gather(scale, value) %>% mutate(phase = "pre")
pred1_nb <- pred1_nb %>% as_tibble() %>% gather(scale, value) %>% mutate(phase = "post")

predictions_nb <- pred0_nb %>% 
  bind_rows(pred1_nb)

obsMeans <- d_scored %>% 
  filter(condition == "diseaseRisk") %>% 
  spread(phase, Mean) %>%
  mutate(score = post - pre) %>%
  group_by(scale) %>%
  summarize(change_score = mean(score),
            std_error = stderr(score)) %>%
  filter(scale!="diseaseSevere") %>%
  mutate(type="observed")

predMeans_nb <- predictions_nb %>% 
  group_by(scale,phase) %>% 
  summarize(mean_resp = mean(value)) %>%
  mutate(type="predicted") %>%
  spread(phase, mean_resp) %>%
  # group_by(scale) %>%
  mutate(change_score = post - pre,
            std_error = 0)

d_sim_nb <- obsMeans %>% bind_rows(predMeans_nb)

d_sim_nb %>%
  mutate(
         UL = change_score + std_error*1.96,
         LL = change_score - std_error*1.96
         ) %>%
  ggplot(aes(y = reorder(scale, change_score),
             x = change_score,
             xmax = UL, 
             xmin = LL, 
             color = type)) +
  geom_point(shape=17, size=3) +
  geom_errorbarh(height=0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
simMean_nb <- d_sim_nb %>% 
  select(-post,-pre, -std_error) %>%
  filter(scale!="diseaseSevere") %>%
  group_by(type,scale) %>%
  spread(type, change_score)

simMeanCor <- cor(simMean_nb$predicted, simMean_nb$observed) %>% round(3)

simMean_nb %>%
  ggplot(aes(x=predicted, y=observed)) +
  geom_point() +
  geom_text(aes(x=-.1, y= .2, label=paste("r =",simMeanCor))) +
  geom_smooth(method="lm") +
  labs(title="Average difference scores") +
  theme(aspect.ratio = 1)
```

And performance is essentially identical. That is, __if we just naïvely assume disease severity drives all beliefs and we get just about as good a prediction as our more sophisticated model.__

Of course, our learned structure accounts for the original correlational data far (infinitely?) better. As revealed by a $\Delta AIC$ in the thousands.

```{r}
# comparing models on the original data
# maddeningly, bnlearn's AIC values are rescaled by -2, so that greater values are better!

nb_struct <- df_to_bnlearn_string(nb_arcs)
nb_struct <- model2network(nb_struct)

print(paste0("naïve structure AIC = ", round(AIC(nb_struct, d_bn)),2))
print(paste0("learned structure AIC = ", round(AIC(net.struct, d_bn),2)))
```

# Preliminary conclusions

On some reflection, these results shoudln't have been so shocking. Since the structure learning algorithm is working to find a graph that preserves the correlations among variables, it's not so surprising that conditioning on disease severity in the graph produces roughly the same predictions as a set of regression models predicting all other node from disease severity (or equivalently, the "naïve" network I used here). However, the fact that those predictions map reasonably well onto what we observe is still important!

__What's better about the network structure models compared with naïve or univariate models?__

1. Fit both correlations between all scales and predict change scores on all scales
2. Predict effects of educational interventions on any node or multiple nodes, all in one model
3. Give ways to help diagnose which nodes were directly affected by interventions
4. (Arguably) better allow interpretation of overall structure of belief system, better provide insights, etc
5. Serve as a cognitive model of the belief system in important ways

If we have three models, one that lets us do prediction in one domain, another that lets us to do prediction in another domain, and one that does both -- we should prefer the one that does both. Likewise, if we have three models, one that lets us do prediction, one that provides an intelligible cognitive theory, and one that does both--we should prefer the one that does both. So it would have been (or would be) a lot more exciting if the theory models could outperform the naïve models on both tasks, but it's still interesting/cool if they do at least as well on multiple tasks as the other models each do on their one task.

That final point is important too. The (presumed) fact that the model will do better prediction treated as a cognitive model than as a causal model is very informative. In a sense, it's actually supported by the naïve models too. A naïve model where disease severity predicts all beliefs is a very poor model of the overall system. But, it is a decent model of how the beliefs change. This would be _very unlikely_ if what we were modeling was a simple causal system.

This also suggests a more general lesson: If beliefs are sufficiently interconnected and there are few v-structures, then the directions of each edge may matter very little in terms of prediction. Of course, this also means that setting those edge directions (if we care to do so), is going to be difficult. It might also mean it's not the right way of concieving of the relationships among beliefs.

### 2018-09-18 study2/vacc_manyBelief_study2_overpar.Rmd
added files

---
title: 'Vaccines: Many Beliefs Study 3: Overparenting deep dive'
author: "Kara Weisman, Derek Powell"
date: "2018-05-18"
output:
  html_notebook:
    toc: true
    toc_float: true
---

```{r, include = F}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

<script type="text/javascript">
  // When the document is fully rendered...
  $(document).ready(function() {
    // ...select all header elements...
    $('h1, h2, h3, h4, h5').each(function() {
      // ...and add an id to them corresponding to their 'titles'
      $(this).attr('id', $(this).html());
    });
  });
</script>

```{r setup, include = F}
library(tidyverse)
library(psych)
library(lme4)
# library(brms)
library(rms)
```

This is a document where we do a "deep dive" on the "Overparenting" scale, which is one of the scales we are least able to predict movement in after the Disease Risk intervention - and a case that we think might be involved meaningful interactions with other scales (e.g., Disease Severity, Medical Skepticism).

```{r tidy, include = F}
# load data
d_all <- read.csv("data/study3_data.csv")[-1]

# reformat to match previous analyses (i.e., 2 rows per participant)
d_demo <- d_all %>% 
  select(workerId, condition, gender, age, ethnicity, education, job, income,
         political_party, political_beliefs, eligible_pretest, 
         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
         children_youngest_posttest, plan_parent_posttest,
         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
         starts_with("comments"), starts_with("duration"))
d_pre <- d_all %>% 
  select(workerId, ends_with("_pretest")) %>%
  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
            starts_with("attention_"), starts_with("comments"), 
            starts_with("duration"))) %>%
  rename_all(funs(gsub("_pretest", "", .))) %>%
  mutate(phase = "pre")
d_post <- d_all %>% 
  select(workerId, ends_with("_posttest")) %>%
  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
            children_youngest_posttest, plan_parent_posttest,
            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
            starts_with("comments"), starts_with("duration"))) %>%
  rename_all(funs(gsub("_posttest", "", .))) %>%
  mutate(phase = "post")

d <- bind_rows(d_pre, d_post) %>% 
  gather(question, response, -c(workerId, phase)) %>%
  mutate(phase = factor(phase,
                        levels = c("pre", "post")),
         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
         # NOTE: "response" has already been reverse coded!
         question = factor(question),
         scale = factor(gsub("_.*$", "", question),
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert"))) %>%
  full_join(d_demo) %>%
  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
  distinct()

# how many left?
# d %>% distinct(workerId, condition) %>% count(condition)
```

```{r scores, include = F}
# score all scales
d_scored <- d %>%
  select(workerId, condition, phase, scale, response,
         gender:duration_posttest) %>%
  group_by(workerId, condition, phase, scale) %>%
  mutate(response = as.numeric(response)) %>%
  summarise(mean = mean(response, na.rm = TRUE)) %>%
  ungroup() %>%
  distinct()
```

# Reliability

Let's look at the observed reliability of the Overparenting scale at pre-test:

```{r}
d_pre %>% select(starts_with("overpar_")) %>% alpha()
```

Not spectacular, but there don't appear to be items that would dramatically improve it.

Let's look at the observed reliability of the Overparenting scale at post-test:

```{r}
d_post %>% select(starts_with("overpar_")) %>% alpha()
```

Again, not spectacular, though perhaps slightly better than at pre-test; no obvious items that should be dropped.

It's possible that the lower-than-average reliability for this scale is one of the reasons it's harder to predict - it's the lowest reliability of all 14 scales at both pre- and post-test (though not dramatically lower than the Disease Rarity scale at pre-test, $\alpha$ = 0.75, or the Naturalism scale at post-test, $\alpha$ = 0.76).

```{r, include = F}
d_pre %>% select(starts_with("hb_")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("nat_")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("medSkept_")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("diseaseRare_")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("diseaseSevere")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("vaccEff_")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("vaccDanger")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("vaccTox_")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("vaccStrain_")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("vaccIntent_")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("parentExpert_")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("infantImmLimCap_")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("infantImmWeak")) %>% select(-contains("check")) %>% alpha()
d_pre %>% select(starts_with("overpar_")) %>% select(-contains("check")) %>% alpha()

d_post %>% select(starts_with("hb_")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("nat_")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("medSkept_")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("diseaseRare_")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("diseaseSevere")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("vaccEff_")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("vaccDanger")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("vaccTox_")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("vaccStrain_")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("vaccIntent_")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("parentExpert_")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("infantImmLimCap_")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("infantImmWeak")) %>% select(-contains("check")) %>% alpha()
d_post %>% select(starts_with("overpar_")) %>% select(-contains("check")) %>% alpha()
```

# Distributions of scores

Let's look at the overall distribution of scores on the Overparenting scale, by condition and phase:

```{r, fig.width = 4, fig.asp = 0.67}
d_scored %>%
  filter(scale == "overpar") %>%
  ggplot(aes(x = mean, fill = condition)) +
  facet_grid(phase ~ condition) +
  geom_bar(stat = "count", position = "identity") +
  scale_x_continuous(limits = c(-3, 3), breaks = seq(-100, 100, 1)) +
  theme_minimal() +
  labs(title = "Distribution of Overparenting scores by phase and condition",
       x = "Overparenting score (range: -3 to +3)",
       y = "Number of participants",
       fill = "Condition")

# d_scored %>%
#   filter(scale == "overpar") %>%
#   ggplot(aes(x = phase, color = condition, y = mean)) +
#   facet_grid(~ condition) +
#   geom_point(position = position_jitter(width = 0.4, height = 0), alpha = 0.5) +
#   scale_y_continuous(limits = c(-3, 3), breaks = seq(-100, 100, 1)) +
#   theme_minimal() +
#   theme(legend.position = "none") +
#   labs(title = "Distribution of Overparenting scores by phase and condition",
#        x = "Phase",
#        y = "Overparenting score (range: -3 to +3)", 
#        fill = "Condition")

d_scored %>%
  filter(scale == "overpar") %>%
  group_by(condition, phase) %>%
  do(data.frame(rbind(smean.cl.boot(.$mean)))) %>% # bootstrapped 95% CI
  ggplot(aes(x = phase, y = Mean)) +
  facet_grid(~ condition) +
  geom_point(data = d_scored %>% 
               filter(scale == "overpar") %>% 
               distinct(workerId, condition, phase, mean),
             aes(x = phase, y = mean, color = condition),
             position = position_jitter(width = 0.4, height = 0), 
             alpha = 0.5, size = 0.8) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper)) +
  scale_y_continuous(limits = c(-3, 3), breaks = seq(-100, 100, 1)) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Distribution of Overparenting scores by phase and condition",
       subtitle = "Error bars are 95% bootstrapped CIs",
       x = "Phase",
       y = "Overparenting score (range: -3 to +3)", 
       fill = "Condition")
```

And at the difference scores:

```{r, fig.width = 4, fig.asp = 0.67}
d_scored %>%
  filter(scale == "overpar") %>%
  spread(phase, mean) %>%
  mutate(diff = post - pre) %>%
  ggplot(aes(x = diff, fill = condition)) +
  facet_grid(~ condition) +
  geom_histogram(binwidth = 0.2) +
  geom_vline(xintercept = 0, lty = 2) +
  scale_x_continuous(breaks = seq(-100, 100, 1)) +
  theme_minimal() +
  labs(title = "Distribution of Overparenting difference scores by condition",
       x = "Difference score",
       y = "Number of participants",
       fill = "Condition")

d_scored %>% 
  filter(scale == "overpar") %>%
  spread(phase, mean) %>%
  mutate(diff = post - pre) %>%
  group_by(condition) %>%
  do(data.frame(rbind(smean.cl.boot(.$diff)))) %>%
  ggplot(aes(x = condition, y = Mean)) +
  geom_point(data = d_scored %>% 
               filter(scale == "overpar") %>%
               spread(phase, mean) %>%
               mutate(diff = post - pre) %>%
               distinct(workerId, condition, diff),
             aes(x = condition, y = diff, color = condition),
             position = position_jitter(width = 0.4, height = 0), 
             alpha = 0.5, size = 0.8) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper)) +
  geom_hline(yintercept = 0, lty = 2) +
  scale_y_continuous(limits = c(-3, 3), breaks = seq(-100, 100, 1)) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Distribution of Overparenting difference scores by condition",
       subtitle = "Error bars are 95% bootstrapped CIs (on difference scores)",
       x = "Phase",
       y = "Difference score", 
       fill = "Condition")  
```

Looks like mean scores were around the midpoint (0) at pre-test in both conditions, and increased at post-test among participants in the Disease Risk condition (but not the No Intervention condition). This increase in the Disease Risk condition seems to be on the order of 0.25 pts on our 7-point scale.

# Correlations with other scales

Let's look at the observed correlations between the Overparenting scale and other scales:

```{r, fig.width = 8, fig.asp = 1}
d_scored %>%
  filter(phase == "pre", condition == "noInterv") %>%
  distinct(workerId, scale, mean) %>%
  spread(scale, mean) %>%
  select(-workerId) %>%
  cor() %>%
  data.frame() %>%
  rownames_to_column("scaleA") %>%
  gather(scaleB, noInterv_pre_cor, -scaleA) %>%
  full_join(d_scored %>%
              filter(phase == "post", condition == "noInterv") %>%
              distinct(workerId, scale, mean) %>%
              spread(scale, mean) %>%
              select(-workerId) %>%
              cor() %>%
              data.frame() %>%
              rownames_to_column("scaleA") %>%
              gather(scaleB, noInterv_post_cor, -scaleA)) %>%
  full_join(d_scored %>%
              filter(phase == "pre", condition == "diseaseRisk") %>%
              distinct(workerId, scale, mean) %>%
              spread(scale, mean) %>%
              select(-workerId) %>%
              cor() %>%
              data.frame() %>%
              rownames_to_column("scaleA") %>%
              gather(scaleB, diseaseRisk_pre_cor, -scaleA)) %>%
  full_join(d_scored %>%
              filter(phase == "post", condition == "diseaseRisk") %>%
              distinct(workerId, scale, mean) %>%
              spread(scale, mean) %>%
              select(-workerId) %>%
              cor() %>%
              data.frame() %>%
              rownames_to_column("scaleA") %>%
              gather(scaleB, diseaseRisk_post_cor, -scaleA)) %>%
  gather(group, cor, -c(scaleA, scaleB)) %>%
  mutate(condition = gsub("_.*$", "", group),
         phase = gsub("^.*_p", "p", gsub("_cor", "", group))) %>%
  select(-group) %>%
  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk")),
         phase = factor(phase, levels = c("pre", "post"))) %>%
  ggplot(aes(x = scaleA, y = scaleB, fill = cor,
             label = format(round(cor, 2), digits = 2))) +
  facet_grid(phase ~ condition) +
  geom_tile() +
  geom_text() +
  annotate("rect", xmin = 0.5, xmax = 14.5, ymin = 7.5, ymax = 8.5,
           alpha = 0, size = 1, color = "black") +
  annotate("rect", ymin = 0.5, ymax = 14.5, xmin = 7.5, xmax = 8.5,
           alpha = 0, size = 1, color = "black") +
  scale_fill_distiller(palette = "RdYlBu", limits = c(-1, 1),
                       guide = guide_colorbar(barheight = 30)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  coord_equal() +
  labs(title = "Correlations between scales, by phase and condition",
       x = "", y = "", fill = "R")
```

```{r, fig.width = 4, fig.asp = 0.67}
d_scored %>%
  filter(phase == "pre", condition == "noInterv") %>%
  distinct(workerId, scale, mean) %>%
  spread(scale, mean) %>%
  select(-workerId) %>%
  cor() %>%
  data.frame() %>%
  rownames_to_column("scaleA") %>%
  gather(scaleB, noInterv_pre_cor, -scaleA) %>%
  full_join(d_scored %>%
              filter(phase == "post", condition == "noInterv") %>%
              distinct(workerId, scale, mean) %>%
              spread(scale, mean) %>%
              select(-workerId) %>%
              cor() %>%
              data.frame() %>%
              rownames_to_column("scaleA") %>%
              gather(scaleB, noInterv_post_cor, -scaleA)) %>%
  full_join(d_scored %>%
              filter(phase == "pre", condition == "diseaseRisk") %>%
              distinct(workerId, scale, mean) %>%
              spread(scale, mean) %>%
              select(-workerId) %>%
              cor() %>%
              data.frame() %>%
              rownames_to_column("scaleA") %>%
              gather(scaleB, diseaseRisk_pre_cor, -scaleA)) %>%
  full_join(d_scored %>%
              filter(phase == "post", condition == "diseaseRisk") %>%
              distinct(workerId, scale, mean) %>%
              spread(scale, mean) %>%
              select(-workerId) %>%
              cor() %>%
              data.frame() %>%
              rownames_to_column("scaleA") %>%
              gather(scaleB, diseaseRisk_post_cor, -scaleA)) %>%
  gather(group, cor, -c(scaleA, scaleB)) %>%
  mutate(condition = gsub("_.*$", "", group),
         phase = gsub("^.*_p", "p", gsub("_cor", "", group)),
         scale_pair = paste(scaleA, scaleB, sep = "_")) %>%
  select(-group) %>%
  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk")),
         phase = factor(phase, levels = c("pre", "post"))) %>%
  filter(scaleA == "overpar", scaleB != "overpar") %>%
  ggplot(aes(x = phase, y = cor, color = scale_pair, group = scale_pair)) +
  facet_grid(. ~ condition) +
  geom_line() +
  geom_point() +
  directlabels::geom_dl(aes(label = scale_pair),
                        method = list("last.qp")) + #, cex = 0.8)) +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Changes in correlations between scales, by condition",
       x = "Phase", y = "R", color = "Pair of scales")
```

At pre-test, none of the other scales was strongy correlated with Overparenting among participants in either condition; the strongest were the two infant immune system beliefs scales (IIS: Limited Capacity and IIS: Weak).

In the No Intevention condition, these correlations seem to have increased at post-test relative to pre-test; this didn't happen in the Disease Risk condition. The correlation between Overparenting and Medical Skepticism also seems to have increased in this condition from pre- to post-test in the No Intervention condition.

In the Disease Risk condition, a handful of correlations seem to have *decreased* from pre- to post-test, most notably all the correlations with vaccine beliefs, as well as the correlation with Medical Skepticism. Meanwhile, a different set of correlations seem to have *increased* from pre- to post-test, including correlations with Disease Severity (the target of the intervention), Vaccine Intention (the outcome of interest), and Vaccine Efficacy.

So it seems like just filling out these scales twice might have made participants align their beliefs about infant immune systems with their attitudes toward protective parenting (at least in the No Intervention condition) - but in addition to this, the intervention might have changed the relationship between participants' beliefs about vaccines and their attitudes toward protective partenting. In particular, at pre-test, participants who more strongly endorsed what we're calling "overparenting" also tended to think vaccines were more dangerous, less effective, more of a strain on the infant immune system, and more likely to contain toxins, and were generally lower on our Vaccine Intent scale. But at post-test, these relationships no longer held - all of these correlations were pretty close to 0.

(Note that this way of thinking about things is at odds with our use of the same cognitive model connecting all of these beliefs - I need to think harder about this.)

# Quantile splits

Let's split people into groups by their scores on the Overparenting, Medical Skepticism, and Disease Severity scores, since these were possible interactions that we identified in person. (Note that we could also use our investigations of the changing correlations among scales to do further investigations like this...)

```{r, include = F}
split <- d_scored %>%
  filter(scale %in% c("overpar", "medSkept", "diseaseSevere"), phase == "pre") %>%
  group_by(scale) %>%
  mutate(split = ntile(mean, 3),
         split = factor(split, labels = c("low", "mid", "high"))) %>%
  ungroup() %>%
  select(workerId, condition, scale, split) %>%
  spread(scale, split) %>%
  full_join(d_scored %>% 
              filter(scale == "vaccIntent") %>% 
              distinct(workerId, phase, mean)) %>%
  mutate(overpar = factor(paste("Overparenting:", 
                                as.character(overpar)),
                          levels = c("Overparenting: low",
                                     "Overparenting: mid",
                                     "Overparenting: high")),
         diseaseSevere = factor(paste("Disease Severity:", 
                                      as.character(diseaseSevere)),
                                levels = c("Disease Severity: low",
                                           "Disease Severity: mid",
                                           "Disease Severity: high")),
         medSkept = factor(paste("Medical Skepticism:",
                                 as.character(medSkept)),
                           levels = c("Medical Skepticism: low",
                                      "Medical Skepticism: mid",
                                      "Medical Skepticism: high"))) %>%
  spread(phase, mean) %>%
  mutate(diff = post - pre)
```

## Overparenting and Disease Severity

```{r, fig.width = 4, fig.asp = 1}
split %>%
  group_by(condition, overpar, diseaseSevere) %>%
  do(data.frame(rbind(smean.cl.boot(.$diff)))) %>% # bootstrapped 95% CI
  ggplot(aes(x = condition, y = Mean, color = condition)) +
  # facet_grid(overpar ~ diseaseSevere ~ medSkept) +
  facet_grid(diseaseSevere ~ overpar) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = split, aes(y = diff),
             alpha = 0.5, position = position_jitter(width = 0.4, height = 0)) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper), color = "black") +
  theme_minimal() +
  theme(legend.position = "none",
        panel.border = element_rect(fill = NA, color = "black")) +
  labs(title = "Changes in Vaccine Intentions",
       subtitle = "By condition, Overparenting quantile at pre-test, and Disease Severity quantile at pre-test\nError bars are 95% bootstrapped CIs",
       x = "Condition", y = "Vaccine Intentions difference score", 
       color = "Condition")
```

What I had written down in our notes from our meeting on 2018-05-15 was that the Disease Risk intervention might be most effective for participants who were high in Overparenting and low or moderate on Disease Severity. This does seem to be the case - these are the top and middle rows for the right-most column.

Interestingly, this plot reveals that the intervention generally didn't work for participants who started out as low in Overparenting (left-most column) - this is good to know... not sure yet what to make of it!

As we'd predict, the intervention didn't do much for participants who started out as high in Disease Severity (bottom row).

## Overparenting and Medical Skepticism

```{r, fig.width = 4, fig.asp = 1}
split %>%
  group_by(condition, overpar, medSkept) %>%
  do(data.frame(rbind(smean.cl.boot(.$diff)))) %>% # bootstrapped 95% CI
  ggplot(aes(x = condition, y = Mean, color = condition)) +
  # facet_grid(overpar ~ diseaseSevere ~ medSkept) +
  facet_grid(medSkept ~ overpar) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = split, aes(y = diff),
             alpha = 0.5, position = position_jitter(width = 0.4, height = 0)) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper), color = "black") +
  theme_minimal() +
  theme(legend.position = "none",
        panel.border = element_rect(fill = NA, color = "black")) +
  labs(title = "Changes in Vaccine Intentions",
       subtitle = "By condition, Overparenting quantile at pre-test, and Medical Skepticism quantile at pre-test\nError bars are 95% bootstrapped CIs",
       x = "Condition", y = "Vaccine Intentions difference score", 
       color = "Condition")
```

I also had written down in our notes that the Disease Risk intervention might be most effective for participants who were high in Overparenting and high in Medicial Skepticism. Again, this does seem to be the case - this would be the bottom right panel.

Note, however, that this might just be a main effect of Medical Skepticism: Participants who started out high in Medical Skepticism (bottom row) seem to have been particularly sensitive to the intervention, perhaps regardless of their Overparenting scores.

Interestingly, this plot reveals that the intervention generally didn't work for participants who started out as low in Medical Skepticism (top row) - again, this is good to know, though again not sure yet what to make of it!

# Modeling interactions via regression

Let's model these potential interactions via regression. (Again, we could also do this for any of the additional relationships of interest revealed by the changes in correlations, above).

I started off with my go-to model of the intervention, `score ~ phase * condition + (1|subject)` (with phase and condition effect-coded), because it's the one that always makes sense to me, but we should consider doing this with other models as well.

On the idea that we were interested in possible interactions involving Overparenting, Medicial Skepticism, and Disease Severity in particular, I created a new dataframe with pre-test scores for Overparenting, Medicial Skepticism, and Disease Severity (all mean-centered and standardized), and both pre- and post-test scores for Vaccine Intentions (also mean-centered and standardized). I think proceeded through a series of models of increasing complexity (though I know this isn't a very sophisticated approach) - see the code for everything I did.

Somewhat surprisingly, the "best-fitting" model according to model comparison is the one with all of the interactions (I've marked parameters with $t$ > 2 with an asterisk in the table below):

```{r, include = F}
d_scored_wide <- d_scored %>%
  filter(scale == "vaccIntent") %>%
  mutate_at(vars(mean), funs(scale(., scale = T))) %>% 
  spread(scale, mean) %>%
  full_join(d_scored %>%
              filter(phase == "pre", scale != "vaccIntent") %>%
              distinct(workerId, scale, mean) %>%
              group_by(scale) %>%
              mutate_at(vars(mean), funs(scale(., scale = T))) %>% # mean-center & standardize
              spread(scale, mean) %>%
              ungroup())

contrasts(d_scored_wide$phase) <- cbind(post = c(-1, 1))
contrasts(d_scored_wide$condition) <- cbind(DR = c(-1, 1))

r1 <- lmer(vaccIntent ~ phase * condition + (1|workerId), d_scored_wide)
# summary(r1)

r2a <- lmer(vaccIntent ~ phase * condition * overpar + 
              (1|workerId), d_scored_wide)
# summary(r2a)

r2b <- lmer(vaccIntent ~ phase * condition * medSkept + 
              (1|workerId), d_scored_wide)
# summary(r2b)

r2c <- lmer(vaccIntent ~ phase * condition * diseaseSevere + 
              (1|workerId), d_scored_wide)
# summary(r2c)

r3a <- lmer(vaccIntent ~ phase * condition * overpar * medSkept + 
              (1|workerId), d_scored_wide)
# summary(r3a)

r3b <- lmer(vaccIntent ~ phase * condition * overpar * diseaseSevere + 
              (1|workerId), d_scored_wide)
# summary(r3b)

r4 <- lmer(vaccIntent ~ phase * condition * overpar * medSkept * diseaseSevere + 
              (1|workerId), d_scored_wide)
# summary(r4)

anova(r1, r2a, r3a, r4)
anova(r1, r2a, r3b, r4)
```

```{r, as.is = T}
summary(r4)$coefficients %>%
  data.frame() %>%
  rownames_to_column("Parameter") %>%
  mutate(` ` = ifelse(abs(t.value) >= 2, "*", "")) %>%
  knitr::kable(digits = 2)
```

I think the most interesting "significant" parameter here is:

- __`phasepost:conditionDR:overpar:medSkept`: A 4-way interaction betwen phase, condition, Overparenting at pre-test, and Medicial Skepticism at pre-test__. Without thinking too deeply about this yet, I think this means that the intervention effect (the interaction between phase and condition) depended on pre-test scores for Overparenting and Medicial Skepticism. This is consistent with the observations we made looking at the second set of quantile splits, <a href="#Overparenting and Medical Skepticism">above</a>.

Also interesting to think about (later):

- `conditionDR:medSkept:diseaseSevere`: A 3-way interaction between condition, Medical Skepticism at pre-test, and Disease Severity at pre-test.
- `conditionDR:overpar:medSkept:diseaseSevere`: A 4-way interaction between condition, Overparenting at pre-test, Medicial Skepticism at pre-test, and Disease Severity at pre-test.

# Take-aways

This all suggests to me that it would be worth it to try including a node for the interaction between Overparenting and Medical Skepticism (and perhaps a node for the interaction between Overparenting and Disease Severity) in our cognitive model. We've come up with many (post-hoc) reasons why this might be important, and our data suggest that it was.

### 2018-09-18 study2/vmb_model_preds.Rmd
added files

--- 2018-09-18 study2/lab_pres_nb_2018-6-11.Rmd
@@
   plt1 <- processed_predictions %>%
-    mutate(
-           UL = observed + std_error*1.96,
-           LL = observed - std_error*1.96
-           ) %>%
-    ggplot(aes(x=predicted, y = observed, ymin = LL, ymax=UL)) +
-    geom_errorbar(color="grey", width=0) +
+    ggplot(aes(x=predicted, y = observed)) +
     geom_point() +
-    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color="grey") +
     theme_bw() +
@@
     geom_errorbarh(height=0) +
-    theme_bw()
-    # theme(axis.text.x = element_text(angle = 90, hjust = 1))
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 90, hjust = 1))
 
@@
 
-```
-
-# conceptual illustration
-
-```{r}
-p_x <- rbeta(100, 2, 2)
-p_y_x0 = .4
-p_y_x1 = .8
-
-p_y = rethinking::rbeta2(100, p_x*p_y_x1 + (1-p_x)*p_y_x0, 100)
-
-plot(p_x, p_y)
-
-df <- data.frame(x=p_x, y=p_y)
-df %>%
-  rename(`p(fire)` = x,
-         `p(smoke)` = y) %>%
-  ggplot(aes(x=`p(fire)`, y = `p(smoke)`)) +
-  geom_point() +
-  theme_bw(base_size = 24)
-```
-
-# correlation matrix
-
-```{r}
-# borrowing code from
-# http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization
-
-reorder_cormat <- function(cormat){
-  # Use correlation between variables as distance
-  dd <- as.dist((1-cormat)/2)
-  hc <- hclust(dd)
-  cormat <-cormat[hc$order, hc$order]
-}
-
-# Get lower triangle of the correlation matrix
-get_lower_tri<-function(cormat){
-  cormat[upper.tri(cormat)] <- NA
-  return(cormat)
-}
-# Get upper triangle of the correlation matrix
-get_upper_tri <- function(cormat){
-  cormat[lower.tri(cormat)]<- NA
-  return(cormat)
-}
-
-corr_plot <- d_bn %>%
-  cor() %>%
-  reorder_cormat() %>%
-  # get_lower_tri() %>%
-  reshape2::melt(na.rm=TRUE) %>%
-  ggplot(aes(x=Var1, y = Var2, fill = value)) +
-  geom_tile(color = "white") +
-  geom_tile() +
-  geom_text(aes(label=round(value,2)), size=6*.35) +
-  scale_fill_distiller(type="div", palette = "RdYlBu") +
-  # scale_fill_viridis_c(limit = c(-1,1)) +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust=.85)) +
-  theme(aspect.ratio = 1) +
-  theme(
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    panel.grid.major = element_blank(),
-    panel.border = element_blank(),
-    panel.background = element_blank(),
-    axis.ticks = element_blank()
-  ) +
-  labs(fill="corr.")
-
-ggsave("corrplot.png", corr_plot, dpi=320, height=5,width=5)
 ```
@@
                                            nodes_to_predict,
-                                           iter = 1e5*2.5
+                                           iter = 1e5
                                            )
@@
 
-scores_cog <- score_predictions(preds_cog)
+plots_cog$corr_plot
+plots_cog$means_plot
 
-plt1 <- plots_cog$corr_plot +
-  geom_text(
-    aes(
-      label = ifelse(observed == preds_cog[which(preds_cog$scale == "diseaseSevere"), "observed"],
-        as.character(scale), ""
-      )
-    ),
-    hjust = 1.1, vjust = 0
-  ) +
-  geom_text(aes(label = ifelse(observed == preds_cog[which(preds_cog$scale == "overpar"), "observed"],
-    as.character(scale), ""
-  )), hjust = 1.1, vjust = 0) +
-  theme(aspect.ratio = 1) +
-  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
-  annotate("text", 
-           x = .25, 
-           y = -.2, 
-           label = paste("italic(R)^2 == ", round(scores_cog$r_squared,3)), 
-           parse = TRUE,
-           size=18*.35
-          ) +
-  theme_bw(base_size=18)
-
-plt2 <- plots_cog$means_plot +
-  labs(x="Change score", y="Belief Scale") +
-  theme_bw(base_size=18) +
-  theme(legend.position = "bottom")
-
-ggsave("plot.png", plot = plt1, dpi=320, width=4, height=4)
-ggsave("plot2.png", plot = plt2, dpi=320, width=6, height=4)
+score_predictions(preds_cog)
 
@@
 
-## "Non-mental" model
+## "Causal" model
 
@@
 
-scores_causal <- score_predictions(preds_causal)
+plots_causal$corr_plot
+plots_causal$means_plot
 
-plt3 <- plots_causal$corr_plot +
-  geom_text(
-    aes(
-      label = ifelse(observed == preds_causal[which(preds_causal$scale == "diseaseSevere"), "observed"],
-        as.character(scale), ""
-      )
-    ),
-    hjust = 1.1, vjust = 0
-  ) +
-  # geom_text(aes(label = ifelse(observed == preds_cog[which(preds_cog$scale == "overpar"), "observed"],
-  #   as.character(scale), ""
-  # )), hjust = 1.1, vjust = 0) +
-  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
-  theme(aspect.ratio = 1) +
-  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
-  annotate("text", 
-           x = .25, 
-           y = -.2, 
-           label = paste("italic(R)^2 == ", round(scores_causal$r_squared,3)), 
-           parse=TRUE,
-           size=14*.35
-          ) +
-  theme_bw(base_size=18)
-
-# plots_causal$means_plot +
-#   labs(x="Change score", y="Belief Scale") +
-#   theme_bw(base_size=18)
-
-ggsave("plot3.png", plot = plt3, dpi=320, width=4, height=4)
+score_predictions(preds_causal)
 ```
@@
 Here we can pretend that expectations for the intervention materials are set by each of the 14 beliefs, and compare the accuracy of the resulting models' predictions.
-We should also ask whether the differences among models are substantial and reliable enough for us to prefer any one model over another.
 
-```{r}
-predict_change_scores_pipe <- partial(predict_change_scores,
-                                      data0 = data.frame(interv = 0),
-                                      data1 = data.frame(interv = 1),
-                                      nodes_to_predict = nodes_to_predict,
-                                      iter = 1e5
-                                      )
+```{r, message=FALSE, warning=FALSE}
 
@@
 
-belief_targets_models <- lapply(all_beliefs, function(b){
+r_belief_targets <- lapply(all_beliefs, function(b){
 
@@
 
-  model <- add_node(cog_model, glm_to_jags_eq(interv_fit))
+  cog_model <- add_node(cog_model, glm_to_jags_eq(interv_fit))
 
+  # can also just use "model" here so long as you include held_out_nodes
+
+  preds <- predict_change_scores(cog_model,
+                                             data.frame(interv = 0),
+                                           data.frame(interv = 1),
+                                             nodes_to_predict,
+                                             iter = 1e5
+                                             )
+
+  preds <- process_predictions(preds, obs_data)
+  score_predictions(preds)
   }
@@
 
-model_compare <- tibble(
-  model_name = all_beliefs,
-  model = unlist(belief_targets_models)
+names(r_belief_targets) <- all_beliefs
+
+r_belief_targets %>% 
+  data.frame() %>%
+  gather(id, value) %>% 
+  mutate(
+    belief = gsub("\\.(.*)","",id), 
+    metric = gsub("(.*)\\.","",id)
     ) %>%
-    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
-    mutate(proc_preds = map(predictions, process_predictions, obs_data = obs_data)) %>%
-    mutate(scores = map(proc_preds, score_predictions_boot))
+  select(-id) %>%
+  ggplot(aes(x = belief, y = value)) +
+  geom_point() +
+  facet_wrap(~ metric, scales = "free") +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
 
-model_compare2 <- model_compare %>%
-    mutate(
-      rmse = map(scores, ~ sapply(.x, function(z){z$rmse})),
-      r_squared = map(scores, ~ sapply(.x, function(z){z$r_squared}))
-      ) %>%
-  gather(metric, value, rmse, r_squared) %>%
-  mutate(
-    mean_value = map_dbl(value, mean),
-    se_value = map_dbl(value, sd)
+By all metrics disease severity gives the best fit, with disease rarity in second place. Both seem highly plausible as targets of the intervention. None of the other beliefs come close.
+
+# Playing with edge directions
+
+The direction of three edges were set arbitrarily in our original cogsci model.
+Here I examine what happens if we change their directions (comparing the original model with the 6 other possible models).
+
+```{r, message=FALSE, warning=FALSE}
+# here I can swap things around
+mynet <- net.struct
+
+mynet1 <- reverse.arc(mynet, "hb","nat") # this might be the best
+mynet2 <- reverse.arc(mynet, "vaccStrain","vaccDanger") 
+mynet3 <- reverse.arc(mynet1, "vaccStrain","vaccDanger")
+mynet4 <- reverse.arc(mynet2, "vaccTox","vaccDanger")
+mynet5 <- reverse.arc(mynet3, "vaccTox","vaccDanger")
+
+possible_dags <- list(
+  mynet,
+  mynet1,
+  mynet2,
+  mynet3,
+  mynet4,
+  mynet5
   )
 
-plt_models <- model_compare2 %>%
+r_dag_comparisons <- lapply(possible_dags, function(dag){
+
+  dag_model <- write_jags_model(bnlearn_to_df(dag), d_bn) %>% suppressWarnings()
+
+  # can modify this to test assumptions about direct effects of intervention ...
+  interv_fit <- glm(interv ~ diseaseSevere, 
+                    data = interv_df,
+                    family = "binomial"
+                    )
+
+  dag_model <- add_node(dag_model, glm_to_jags_eq(interv_fit))
+
+  # can also just use "model" here so long as you include held_out_nodes
+
+  preds <- predict_change_scores(dag_model,
+                                             data.frame(interv = 0),
+                                           data.frame(interv = 1),
+                                             nodes_to_predict,
+                                             iter = 1e5*2.5
+                                             )
+
+  preds <- process_predictions(preds, obs_data)
+  score_predictions(preds)
+  }
+)
+
+names(r_dag_comparisons) <- c(
+  "original",
+  "swap_hb_nat",
+  "swap_vs_vd",
+  "swap_hb_nat_vs_vd",
+  "swap_vs_vd_vt_vd",
+  "swap_hb_nat_vs_vd_vt_vd"
+)
+
+r_dag_comparisons %>% 
+  data.frame() %>%
+  gather(id, value) %>% 
   mutate(
-    UL = mean_value + se_value,
-    LL = mean_value - se_value
+    dag = gsub("\\.(.*)","",id), 
+    metric = gsub("(.*)\\.","",id)
     ) %>%
-  ggplot(aes(x = reorder(model_name, -mean_value), y = mean_value, ymin = LL, ymax = UL)) +
-  geom_pointrange() +
-  theme_bw(base_size=18) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-  facet_wrap(~metric, scales="free") +
-  labs(x="Targetted belief", y = "Score")
+  select(-id) %>%
+  ggplot(aes(x = dag, y = value)) +
+  geom_point() +
+  facet_wrap(~ metric, scales = "free") +
+  theme(axis.text.x = element_text(angle = 30, hjust = 1))
+```
 
-ggsave("plot_models.png", plot = plt_models, dpi=320, width=12, height=6)
-```
+This analysis doesn't hugely favor any of the models, and even seems sensitive to error in the predictions, so I've ramped mcmc sampels up to 250k.
 
@@
 
-scores_cog2 <- score_predictions(preds_cog2)
+plots_cog2$corr_plot
+plots_cog2$means_plot
 
-plt4 <- plots_cog2$corr_plot +
-  geom_text(
-    aes(
-      label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "diseaseSevere"), "observed"],
-        as.character(scale), ""
-      )
-    ),
-    hjust = 1.1, vjust = 0
-  ) +
-  geom_text(aes(label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "overpar"), "observed"],
-    as.character(scale), ""
-  )), hjust = 1.1, vjust = 0) +
-    geom_text(aes(label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "infantImmWeak"), "observed"],
-    as.character(scale), ""
-  )), hjust = 1.1, vjust = 0) +
-  # geom_abline(intercept = 0, slope = 1, linetype = "dashed", color="grey") +
-  # geom_errorbar(aes(ymin = LL, ymax=UL)) +
-  theme(aspect.ratio = 1) +
-  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
-  annotate("text", 
-           x = .25, 
-           y = -.2, 
-           label = paste("italic(R)^2 == ", round(scores_cog2$r_squared,3)), 
-           parse=TRUE,
-           size=14*.35
-          )
-
-plots_cog2$means_plot +
-  labs(x="Change score", y="Belief Scale")
-
-ggsave("plot4.png", plot = plt4, dpi=320, width=4, height=4)
+score_predictions(preds_cog2)
 ```
@@
 ```
+
+# Binning participants
+
+One idea we had was to predict change scores for different bins of participants.
+The obvious binning variable to me is disease severity.
+Here I'm binning participants by disease severity quartile (4 bins), generating predictions within each bin, and plotting the performance individually.
+
+I used the same intervention node formula for each bin, so this is consistently the same model.
+So, all we're looking at here is whether the model's predictions hold for different groups of participants.
+In contrast, I could also refit the intervention node for each bin, but it's less clear what's being modeled in that case.
+
+```{r, message=FALSE, warning=FALSE}
+# let's try creating 4 bins of participants
+
+cutpoints <- c(.25, .5, .75, 1)
+q <- quantile(interv_df %>%
+                        filter(phase=="pre") %>%
+                        .$diseaseSevere, cutpoints)
+
+interv_df_binned <- interv_df %>%
+  ungroup() %>%
+  mutate(workerId = as.character(workerId)) %>%
+  mutate(bin = ifelse(diseaseSevere <= q[1], 1,
+                      ifelse( diseaseSevere <= q[2], 2,
+                              ifelse(diseaseSevere <= q[3],3,
+                                     4))))
+
+bin_ids <- list(
+  interv_df_binned %>% filter(phase=="pre", bin==1) %>% .$workerId,
+  interv_df_binned %>% filter(phase=="pre", bin==2) %>% .$workerId,
+  interv_df_binned %>% filter(phase=="pre", bin==3) %>% .$workerId,
+  interv_df_binned %>% filter(phase=="pre", bin==4) %>% .$workerId
+)
+
+data_bins <- lapply(bin_ids, function(x){
+  interv_df %>%
+    filter(workerId %in% x)
+})
+
+bin_preds <- lapply(data_bins, function(data){
+
+  obs_data <- d_scored %>% 
+    filter(condition == "diseaseRisk") %>% 
+    mutate(workerId = as.character(workerId)) %>%
+    filter(workerId %in% data$workerId) %>%
+    spread(phase, Mean) %>%
+    mutate(score = post - pre) %>%
+    group_by(scale) %>%
+    summarize(
+      observed = mean(score),
+      std_error = stderr(score)
+      )
+
+  model <- write_jags_model(bnlearn_to_df(net.struct), d_bn)
+  # model <- write_jags_model(nb_arcs, d_bn) # produces similar predictions
+
+  # # # can modify this to test assumptions about direct effects of intervention ...
+  # interv_fit <- glm(interv ~ diseaseSevere + overpar,
+  #                   data = data,
+  #                   family = "binomial"
+  #                   )
+
+  model <- add_node(model, glm_to_jags_eq(interv_fit))
+
+  # can also just use "model" here so long as you include held_out_nodes
+  m0 <- data %>%
+    filter(phase=="pre") %>%
+    .$diseaseSevere %>%
+    mean()
+
+  m1 <- data %>%
+    filter(phase=="post") %>%
+    .$diseaseSevere %>%
+    mean()
+
+  preds <- predict_change_scores(model,
+    data.frame(interv = 0),
+    data.frame(interv = 1),
+    # data.frame(diseaseSevere = m0),
+    # data.frame(diseaseSevere = m1),
+    nodes_to_predict,
+    iter = 1e5
+  ) %>% mutate(interv = 0)
+
+  preds <- process_predictions(preds, obs_data)
+  }
+)
+
+```
+
+```{r}
+# man this is hackey ...
+
+all_bin_preds <- bin_preds[[1]] %>%
+  mutate(bin = 1) %>%
+  bind_rows(
+    bin_preds[[2]] %>%
+      mutate(bin = 2)
+      ) %>%
+  bind_rows(
+    bin_preds[[3]] %>%
+      mutate(bin = 3)
+  ) %>%
+  bind_rows(
+    bin_preds[[4]] %>%
+  mutate(bin = 4)
+  )
+
+all_bin_preds %>%
+  # filter(scale!="diseaseSevere") %>%
+  ggplot(aes(x=predicted, y = observed)) +
+  geom_point() +
+  geom_smooth(method="lm") +
+  facet_wrap(~bin, scales="fixed", ncol = 2) +
+  theme_bw() +
+  coord_fixed(xlim = c(-.35,.8), ylim = c(-.35,.8)) +
+  theme(aspect.ratio = 1) +
+  labs(title = "Predictions by quartile bin (binned on disease severity)")
+```
+
+Correlations are strongly positive in the the first 3 quartiles, and less strong in the upper-most quartile.
+Of course that's where we have the most restriction of range.
+Though the correlations are similar, note the differences in the scales, with bigger changes observed in the 1st quartile especially.
+The model makes essentially (exactly?) the same predictions for all four bins, so it misses in different ways across the bins.
+
+In case it helps, here it all is together in one plot ...
+
+```{r}
+all_bin_preds %>%
+  # filter(scale!="diseaseSevere") %>%
+  mutate(bin = as.factor(bin)) %>%
+  ggplot(aes(x=predicted, y = observed, color = bin)) +
+  geom_point() +
+  # facet_wrap(~bin, scales="fixed", ncol = 2) +
+  theme_bw() +
+  coord_fixed(xlim = c(-.35,.8), ylim = c(-.35,.8)) +
+  theme(aspect.ratio = 1) +
+  labs(title = "Predictions by quartile bin\n(binned on disease severity)")
+```
+
+Overall, I think this is somewhat encouraging, but it's not quite as clear or revealing as I had hoped.
+
+# More serious model comparison
+
+Now it's time to ask whether the differences among models are substantial and reliable enough for us to prefer any one model over another.
+
+```{r}
+all_beliefs <- nodes(net.struct)
+
+cog_model <- write_jags_model(bnlearn_to_df(net.struct), d_bn) %>% suppressWarnings()
+
+belief_targets_models <- lapply(all_beliefs, function(b){
+
+  f <- paste0("interv ~ ", b)
+
+  # can modify this to test assumptions about direct effects of intervention ...
+  interv_fit <- glm(as.formula(f), 
+                    data = interv_df,
+                    family = "binomial"
+                    )
+
+  model <- add_node(cog_model, glm_to_jags_eq(interv_fit))
+
+  }
+)
+
+model_compare <- tibble(
+  model_name = all_beliefs,
+  model = belief_targets_models
+  ) %>%
+    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
+    mutate(proc_preds = map(predictions, process_predictions, obs_data = obs_data)) %>%
+    mutate(scores = map(proc_preds, score_predictions_boot)) %>%
+    mutate(rmse = map(scores, ~ sapply(.x, function(z){z$rmse}))) %>%
+  mutate(
+    mean_rmse = map_dbl(rmse, mean),
+    se_rmse = map_dbl(rmse, sd)
+    )
+
+model_compare %>%
+  mutate(
+    UL = mean_rmse + se_rmse,
+    LL = mean_rmse - se_rmse
+  ) %>%
+  ggplot(aes(x = model_name, y = mean_rmse, ymin = LL, ymax = UL)) +
+  geom_pointrange() +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+```
+
+## comparing alternate structures
+
+```{r}
+# here I can swap things around
+mynet <- net.struct
+
+mynet1 <- reverse.arc(mynet, "hb","nat") # this might be the best
+mynet2 <- reverse.arc(mynet, "vaccStrain","vaccDanger") 
+mynet3 <- reverse.arc(mynet1, "vaccStrain","vaccDanger")
+mynet4 <- reverse.arc(mynet2, "vaccTox","vaccDanger")
+mynet5 <- reverse.arc(mynet3, "vaccTox","vaccDanger")
+
+possible_dags <- list(
+  mynet,
+  mynet1,
+  mynet2,
+  mynet3,
+  mynet4,
+  mynet5
+  )
+
+dag_comparison_models <- lapply(possible_dags, function(dag){
+
+  dag_model <- write_jags_model(bnlearn_to_df(dag), d_bn) %>% suppressWarnings()
+
+  # can modify this to test assumptions about direct effects of intervention ...
+  interv_fit <- glm(interv ~ diseaseSevere, 
+                    data = interv_df,
+                    family = "binomial"
+                    )
+
+  dag_model <- add_node(dag_model, glm_to_jags_eq(interv_fit))
+
+  }
+)
+
+model_names <- c(
+  "original",
+  "swap_hb_nat",
+  "swap_vs_vd",
+  "swap_hb_nat_vs_vd",
+  "swap_vs_vd_vt_vd",
+  "swap_hb_nat_vs_vd_vt_vd"
+)
+
+model_compare_dags <- tibble(
+  model_name = model_names,
+  model = dag_comparison_models
+  ) %>%
+    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
+    mutate(proc_preds = map(predictions, process_predictions, obs_data = obs_data)) %>%
+    mutate(scores = map(proc_preds, score_predictions_boot)) %>%
+    mutate(rmse = map(scores, ~ sapply(.x, function(z){z$rmse}))) %>%
+  mutate(
+    mean_rmse = map_dbl(rmse, mean),
+    se_rmse = map_dbl(rmse, sd)
+    )
+
+model_compare_dags %>%
+  mutate(
+    UL = mean_rmse + se_rmse,
+    LL = mean_rmse - se_rmse
+  ) %>%
+  ggplot(aes(x = model_name, y = mean_rmse, ymin = LL, ymax = UL)) +
+  geom_pointrange() +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
+
+----------------------------------------
+
+# Broken?
+
+Here I wrote some code to compute mse and mae across all individual subjects.
+I treated the resulting statistisc as means and calculated their standard error.
+I thought that would help clarify things, but actually it doesn't seem quite right as a model of the model predictions for average change scores.
+For instance, the disease severity targetting model isn't strongly preferred, despite getting like 20% more variance among average change scores.
+
+```{r}
+
+interv_df_wide <- interv_df %>%
+  gather(scale, response, vaccIntent:parentExpert) %>%
+  mutate(scale_id = paste0(scale,"_",phase)) %>%
+  select(-phase, -scale, -condition, -interv) %>%
+  spread(scale_id, response)
+
+predict_change_scores_pipe <- partial(predict_change_scores,
+                                      data0 = data.frame(interv=0),
+                                      data1 = data.frame(interv=1),
+                                      nodes_to_predict = nodes_to_predict,
+                                      iter = 1e5
+                                      )
+
+compute_residuals <- function(predictions, observed){
+  observed <- observed %>%
+    as.matrix()
+
+  predictions <- predictions %>% 
+    select(-interv) %>%
+      as.matrix()
+
+  resids <- sweep(observed, 2, predictions)
+
+}
+
+compute_ms_residuals <- function(predictions, observed) {
+  resids <- compute_residuals(predictions, observed)
+  resids2 <- resids^2
+  rowMeans(resids2)
+}
+
+compute_mabs_residuals <- function(predictions, observed) {
+  resids <- compute_residuals(predictions, observed)
+  # mae <- colMeans(abs(resids))
+  rowMeans(abs(resids))
+}
+
+obs_data_indiv <- interv_df_wide %>%
+            gather(scale_id, response, -workerId) %>%
+          mutate(
+            scale = gsub("_.*", "", scale_id),
+            phase = gsub(".*_", "", scale_id)
+          ) %>%
+  select(-scale_id) %>%
+  spread(phase, response) %>%
+  mutate(change_score = post - pre) %>%
+  select(-post, -pre) %>%
+  spread(scale, change_score) %>%
+  ungroup() %>%
+  select(-workerId)
+
+model_name_list <- c("cognitive model", "cognitive model\n(overpar)", "causal model")
+model_list <- c(cog_model, cog_model2, causal_model)
+
+model_compare <- tibble(
+  model_name = model_name_list,
+  model = model_list
+  ) %>%
+    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
+    mutate(
+      abs_resids = map(predictions, compute_mabs_residuals, observed = obs_data_indiv),
+      resids_squared = map(predictions, compute_ms_residuals, observed = obs_data_indiv)
+           ) %>%
+  gather(err_type, errs, abs_resids, resids_squared) %>%
+  mutate(
+    mean = map_dbl(errs, mean), 
+    se = map_dbl(errs, ~ sd(.x)/sqrt(length(.x)-1))
+    )
+
+```
+
+```{r}
+model_compare %>%
+  mutate(UL = mean + se,
+         LL = mean - se) %>%
+  ggplot(aes(x = model_name, y = mean, ymin = LL, ymax = UL)) +
+  geom_pointrange() +
+  facet_wrap(~ err_type)
+```
+
+```{r}
+# by individuals, not working great
+all_beliefs <- nodes(net.struct)
+
+cog_model <- write_jags_model(bnlearn_to_df(net.struct), d_bn) %>% suppressWarnings()
+
+belief_targets_models <- lapply(all_beliefs, function(b){
+
+  f <- paste0("interv ~ ", b)
+
+  # can modify this to test assumptions about direct effects of intervention ...
+  interv_fit <- glm(as.formula(f), 
+                    data = interv_df,
+                    family = "binomial"
+                    )
+
+  model <- add_node(cog_model, glm_to_jags_eq(interv_fit))
+
+  }
+)
+
+model_compare <- tibble(
+  model_name = all_beliefs,
+  model = belief_targets_models
+  ) %>%
+    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
+    mutate(
+      abs_resids = map(predictions, compute_mabs_residuals, observed = obs_data_indiv),
+      resids_squared = map(predictions, compute_ms_residuals, observed = obs_data_indiv)
+           ) %>%
+  gather(err_type, errs, abs_resids, resids_squared) %>%
+  mutate(
+    mean = map_dbl(errs, mean), 
+    se = map_dbl(errs, ~ sd(.x)/sqrt(259))
+    )
+```
+
+```{r}
+model_compare %>%
+  mutate(UL = mean + se,
+         LL = mean - se) %>%
+  ggplot(aes(x = model_name, y = mean, ymin = LL, ymax = UL)) +
+  geom_pointrange() +
+  facet_wrap(~ err_type) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
+
+To be completed ...

### 2018-09-18 scripts/bdToBn.R

@@ -1,0 +1,68 @@
+# author: Kara Weisman
+# created: 11/10/17, 2:28 PM
+# last updated: 11/10/17, 2:28 PM
+
+# script for translating BDgraph posterior probabilities to bnlearn
+
+library(tidyverse)
+library(bnlearn)
+library(BDgraph)
+library(tidygraph)
+
+# make model with BDgraph -----
+fit.bd.ggm <- bdgraph(d_bn, method = "ggm")
+plot(fit.bd.ggm)
+
+# approach #1: from last graph -----
+
+## get links
+links.bd.ggm <- fit.bd.ggm$last_graph
+
+# ## format as arcs for bnlearn
+# arcs.whitelist <- links.bd.ggm %>%
+#   data.frame() %>%
+#   rownames_to_column("from") %>%
+#   gather(to, yes_no, -from) %>%
+#   filter(yes_no == 1) %>%
+#   data.frame() %>%
+#   dplyr::select(from, to)
+
+## make the blacklist for bnlearn
+arcs.blacklist <- links.bd.ggm %>%
+  data.frame() %>%
+  rownames_to_column("from") %>%
+  gather(to, yes_no, -from) %>%
+  filter(yes_no == 0) %>%
+  data.frame() %>%
+  dplyr::select(from, to)
+
+## make model with bnlearn
+fit.mmhc.blacklist <- mmhc(d_bn, blacklist = arcs.blacklist)
+plot(fit.mmhc.blacklist)
+
+# approach #2: from posterior probabilities -----
+
+## format as arcs for bnlearn
+arcs.whitelist995 <- fit.bd.ggm$p_links %>%
+  data.frame() %>%
+  rownames_to_column("from") %>%
+  gather(to, posterior, -from) %>%
+  filter(posterior >= 0.995) %>%
+  data.frame() %>%
+  dplyr::select(from, to)
+
+## make the blacklist for bnlearn
+arcs.blacklist995 <- fit.bd.ggm$p_links %>%
+  data.frame() %>%
+  rownames_to_column("from") %>%
+  gather(to, posterior, -from) %>%
+  filter(posterior < 0.995) %>%
+  data.frame() %>%
+  dplyr::select(from, to)
+
+## make model with bnlearn
+fit.mmhc.blacklist995 <- mmhc(d_bn, blacklist = arcs.blacklist995)
+plot(fit.mmhc.blacklist995)
+
+# convert to tidy -----
+tidy_graph <- as_tbl_graph(fit.mmhc.blacklist995$arcs)

### 2018-09-18 scripts/bnLavaan.R

@@ -1,0 +1,164 @@
+# author: Derek Powell
+# created: 11/3/17, 10:28 AM
+# last updated: 11/3/17, 1:44 PM
+
+# script for translating bnlearn arcs to lavaan
+
+library(tidyverse)
+library(stringr)
+
+cat_string_list <- function(listOfStrings) {
+  paste(listOfStrings, collapse="")
+}
+
+
+cat_plus <- function(x) {
+  return(paste(x,"+ "))
+}
+
+
+cat_weight <- function(x,wVal) {
+  wVal <- round(wVal,4) # to keep human-readable
+  paste0(wVal,"*",x)
+}
+
+
+cat_weight_list <- function(x,wVals) {
+  mapply(cat_weight,x,wVals)
+}
+
+
+write_sum <- function(toBeSummed) {
+  firstPart <- sapply(toBeSummed[1:length(toBeSummed)-1],cat_plus)
+  cat_string_list(c(firstPart,toBeSummed[length(toBeSummed)]))
+}
+
+
+cat_and_sort <- function(x,y) {
+  sort(c(x,y)) %>% as.character(collapse="") %>% paste(collapse="")
+}
+
+
+tag_arcs <- function(graphStruct) {
+  g <- graphStruct %>% 
+    mutate(from =  as.character(from)) %>%
+    mutate(to = as.character(to)) %>%
+    mutate(id = map2_chr(from, to, cat_and_sort))
+  return(as_tibble(g))
+}
+
+get_graphStruct <- function(bnObject) {
+  # Returns the graph structure ($arcs) from a bn object
+  # bnObject: any object of class bn
+  
+  graphStruct <- bnObject$arcs %>% as_tibble()
+  return(graphStruct)
+}
+
+make_weighted_lavaan_paths <- function(graphStruct, pathParams, residParams) {
+  # Translates bnlearn graph into lavaan syntax with randomly sampled weights
+  # for simulating data from graphical models
+  # Note: this function requires fully directed graph
+  # ---
+  # baseGraph: DAG from bnlearn
+  # pathParams: c(a,b) for Beta(a, b) for path coefficients 
+  # residParams: c(a,b) for Beta(a, b) for variances
+  
+  graphStruct <- graphStruct %>% mutate(from = as.character(from),
+                                        to = as.character(to))
+  allNodes <- unique(c(graphStruct$from, graphStruct$to)) %>% as.character()
+  
+  modelStr <- ""
[…]

### 2018-09-18 scripts/cextend_all.R

@@ -1,0 +1,53 @@
+# Author: Derek Powell
+# Created: 12/20/17, 3:34 PM
+# Last updated: 12/20/17, 3:34 PM
+
+tag_arcs <- function(graphStruct) {
+  g <- graphStruct %>% 
+    mutate(from =  as.character(from)) %>%
+    mutate(to = as.character(to)) %>%
+    mutate(id = map2_chr(from, to, cat_and_sort))
+  return(as_tibble(g))
+}
+
+cextend_all <- function(cpDAG) {
+  # Generate all consistent extensions of equivalence class
+  # cpDAG: complete partially directed graph (cpdag(bnobject))
+  # returns: a list of bn objects
+  library(gtools)
+  undirected <- undirected.arcs(cpDAG) %>% as_tibble() %>% tag_arcs()
+  uniqueArcs <- unique(undirected$id)
+  
+  arcDF <- undirected %>% distinct(id, .keep_all=TRUE)
+  arcNum <- nrow(arcDF)
+  
+  # m <- as.data.frame(matrix(rbinom(arcNum*2, 1, 0.5),ncol=arcNum))
+  
+  grid <- gtools::permutations(2,arcNum,v=c(0,1),repeats.allowed=TRUE)
+  # permutations(2,i,v=c(0,1),repeats.allowed=TRUE)
+  # grid <- expand.grid(m)
+  
+  graphList <- list()
+  for (i in 1:dim(grid)[1]) {
+    # for (i in 1:50) {
+    gDF <- arcDF %>% mutate(direction = as.numeric(grid[i,]))
+    g <- cpDAG
+    for (j in 1:nrow(gDF)) {
+      arc <- gDF[j,]
+      if (arc$direction==1){
+        g <- set.arc(g,arc$from,arc$to, check.cycles=FALSE, check.illegal=FALSE)
+        
+      } else if (arc$direction==0) {
+        g <- set.arc(g, arc$to, arc$from, check.cycles=FALSE, check.illegal=FALSE)
+      }
+    }
+    checkDag <- acyclic(g)
+    
+    if (checkDag==TRUE) {
+      # graphList <- c(graphList, g)
+      graphList[[length(graphList)+1]] <- g
+    }
+    
+  }
+  return(graphList)
+}

### 2018-09-18 scripts/custom-structure-learning/cog-model-bidag-functions.R

@@ -1,0 +1,333 @@
+
+## ----------------------------------------
+## Generating BiDAG scoretable 
+## -------------------------------------------
+## Code below is modified from BiDAG package v1.2 under GPL 2/3 license 
+## 8/21/18, 1:11 PM
+library(parallel)
+
+c_definestartspace <- function(alpha, param, cpdag = FALSE, n, algo = "pc") {
+  # condense, just error out for other score types 
+  if (is.null(alpha)) {
+    if (n < 50) {
+      alpha <- 0.4
+    }
+    else {
+      alpha <- max(20/n, 0.01)
+    }
+  }
+  if (param$type == "bde") {
+    if (cpdag) {
+      pc.skel <- pc(suffStat = list(d1 = param$d1, d0 = param$d0, 
+                                    data = param$data), indepTest = weightedbinCItest, 
+                    alpha = alpha, labels = colnames(param$data), 
+                    verbose = FALSE)
+    }
+    else {
+      pc.skel <- pcalg::skeleton(suffStat = list(d1 = param$d1, 
+                                                 d0 = param$d0, data = param$data), indepTest = weightedbinCItest, 
+                                 alpha = alpha, labels = colnames(param$data), 
+                                 verbose = FALSE)
+    }
+  }
+  else if (param$type != "bde") {
+    if (is.null(param$weightvector)) {
+      cormat <- cor(param$data)
+      N <- nrow(param$data)
+    }
+    else {
+      N <- sum(param$weightvector)
+      cormat <- cov.wt(param$data, wt = param$weightvector, 
+                       cor = TRUE)$cor
+    }
+    if (cpdag) {
+      pc.skel <- pcalg::pc(suffStat = list(C = cormat, 
+                                           n = N), indepTest = pcalg::gaussCItest, alpha = alpha, 
+                           labels = colnames(param$data), skel.method = "stable", 
+                           verbose = FALSE)
+    }
+    else {
+      pc.skel <- pcalg::skeleton(suffStat = list(C = cormat, 
+                                                 n = N), indepTest = pcalg::gaussCItest, alpha = alpha, 
[…]

### 2018-09-18 scripts/custom-structure-learning/cog-model-discrete-funcs.R

@@ -1,0 +1,92 @@
+make_custom_cpt <- function(ps, dims, dim_names, data) {
+  # makes custom cpt in HydeNet format
+  output <- array(ps, dim=dims, dimnames=dim_names)
+  attr(output, "model") <- data
+  attr(output, "class") <- c("cpt","array")
+  
+  return(output)
+}
+
+
+result_to_cpt <- function(result, child, predictors, data) {
+  # compute cpt for child node given optim result and predictor variables
+  # result: optim result
+  # child: name of child node (string)
+  # data: dataframe
+  # return: array
+  states <- lapply(c(predictors,child), function(x){c(0,1)})
+  names(states) <- c(predictors,child)
+  states_labeled <- lapply(c(predictors,child), function(x){c("No","Yes")}) # not working 8/17/18, 9:44 AM
+  names(states_labeled) <- c(predictors,child)
+  ds <- ifelse(result > 0,1,0)
+  names(ds) <- sapply(names(result), function(x){paste0("d_",substr(x,3,100))})
+  result <- abs(c(result, ds[-(1:2)]))
+  
+  z <- expand.grid(states) %>%
+    mutate(
+      p = with(
+        as.data.frame(t(result)),
+        eval(parse(text=create_equation_expression(predictors)))
+      )
+    )
+  z[which(z[child]==0),"p"] <- 1-z[which(z[child]==0),"p"] # unnecessary to preserve child name oh well
+  
+  output <- make_custom_cpt(z$p, rep(2,length(predictors)+1), states_labeled, data)
+  return(output)
+}
+
+
+fake_xtabs <- function(node, data, trueval = 1, falseval = 0){
+  data <- as.data.frame(data)
+  probs <- data[, node]
+  p1 <- mean(probs)
+  count1 <- round(p1*1e5)
+  count0 <- 1e5 - count1
+  counts <- matrix(c(rep(trueval,count1), rep(falseval,count0)), ncol=1)
+  colnames(counts) <- c(node)
+  f <- paste0("~",node)
+  output <- xtabs(as.formula(f), data = counts)
+  attr(output, "call") <- list(formula = as.formula(f) )
+  
+  return(output)
+}
+
+
+fit_node_cpt <- function(node, data) {
+  child <- node$child # specific to format above ,could be imrpoved
+  predictors <- node$parents # specific to format above ,could be imrpoved
+  data <- as.data.frame(data)
+  if (is.null(predictors)) {
[…]

### 2018-09-18 scripts/custom-structure-learning/cog-model-jags-tools.R

@@ -1,0 +1,142 @@
+# # Doing inference on beta DAGs through rjags
+# # ----
+
+do_jags_inference <- function(model, variable.names, data = NULL, iter = 1e4, silent=TRUE) {
+  if (silent) {
+    pbar <- "none"
+  } else {
+    pbar <- "text"
+  }
+  tc <- textConnection(model)
+  jags <- rjags::jags.model(tc, data = data, quiet=silent)
+  close(tc)
+  
+  model_samples <- rjags::coda.samples(jags, variable.names, iter*2, progress.bar="none")
+  return(model_samples)
+}
+
+
+make_predictions <- function(model, orig_data, nodes_to_predict, nodes_held_out=c(), iter=1e3) {
+  # takes a model and dataframe and generates model predictions for variables listed in 
+  # nodes_to_predict. By default, uses all remaining nodes in orig_data. Hold out nodes from
+  # prediction with nodes_held_out. iter sets mcmc samples
+  
+  pred_df <- orig_data
+  pred_df[,nodes_to_predict] <- NA
+  
+  for (i in 1:nrow(pred_df)) {
+    row <- pred_df[i,]
+    row[nodes_held_out] <- NA
+    pred <- do_jags_inference(model, nodes_to_predict, data = row, iter = iter)
+    point_preds <- rowMeans(t(pred[[1]][(iter/2+1):iter,nodes_to_predict]))
+    pred_df[i,nodes_to_predict] <- point_preds
+  }
+  
+  return(pred_df)
+}
+
+assemble_fitted_equation <- function(w_leak, prevterms, genterms) {
+  # assembles the noisy-or-and-nor equation
+  # prevterms: probability of non-prevention (p(fail prevent))
+  # genterms: probability of non-generation (p(fail generate))
+  # return: equation string
+  
+  gen <- paste0("(1-",w_leak, ")*",terms_product(genterms))
+  prev <- terms_product(prevterms)
+  paste0(wrap_paren(paste0("1-",gen)), " * ", terms_product(prevterms))
+}
+
+
+create_fitted_equation_expression <- function(predictors, coefs, digits = 5){
+  # creates equation string
+  # predictors: list of names of predictor variables (parents)
+  # return: equation string (expression to evaluate)
+  
+  coefs <- as.list(coefs)
+  
[…]

### 2018-09-18 scripts/custom-structure-learning/cog-model-main.R

@@ -1,0 +1,9 @@
+## Inferring Discrete Cognitive Models from Continuous Belief Reports 
+## Beta regression of belief reports
+
+## initialize ...
+
+source("cog-model-scoring.R")
+source("cog-model-jags-tools.R")
+source("cog-model-bidag-functions.R")
+source("cog-model-discrete-funcs.R")

### 2018-09-18 scripts/custom-structure-learning/cog-model-scoring.R

@@ -1,0 +1,519 @@
+## Inferring Discrete Cognitive Models from Continuous Belief Reports 
+## Beta regression of belief reports
+
+## ----------------------------------------
+## functions to assemble model-fitting expressions 
+## ----------------------------------------
+ 
+wrap_paren <- function(string){
+  # wrap string in parentheses
+  paste0("(",string,")")
+}
+
+
+terms_product <- function(termlist){
+  # writes formula for product of terms in termlist
+  # termlist: list of strings
+  # return: string
+  
+  output <- ""
+  for (i in 1:length(termlist)) {
+    output <- paste0(termlist[i],"*",output)
+  }
+  output <- substr(output, 1, nchar(output)-1)
+  return(output)
+}
+
+
+assemble_equation <- function(prevterms, genterms) {
+  # assembles the noisy-or-and-nor equation
+  # prevterms: probability of non-prevention (p(fail prevent))
+  # genterms: probability of non-generation (p(fail generate))
+  # return: equation string
+  
+  gen <- paste0("(1-w_leak)*",terms_product(genterms))
+  prev <- terms_product(prevterms)
+  paste0(wrap_paren(paste0("1-",gen)), " * ", terms_product(prevterms))
+}
+
+
+assign_pars_exp <- function(pars){
+  # creates expressions to initialize named weight parameters from par
+  # input: par_weights vector
+  # return: list of strings (to be evaluated as expressions)
+  
+  Map(function(x, i) paste0(x," <- abs(par[",i+2,"])"), pars, seq_along(pars))
+}
+
+
+assign_dpars_exp <- function(predictors){
+  # creates expressions to initialize named direction parameters from predictors
+  # input: predictors vector
+  # return: list of strings (to be evaluated as expressions)
+  
+  Map(function(x, i) paste0("d_",x," <- ifelse(par[",i+2,"] > 0,1,0)"), predictors, seq_along(predictors))
+}
+
+
+create_init_expression <- function(child, predictors){
+  # assembles initialization expressions
+  # child: name of predicted variable
+  # predictors: list of names of predictor variables (parents)
+  # return: list of strings (expressions to evaluate)
+  
+  par_weights <- sapply(predictors, function(x){paste0("w_",x)})
+  par_directions <- sapply(predictors, function(x){paste0("d_",x)})
[…]

### 2018-09-18 scripts/custom-structure-learning/fit-cog-models.R

@@ -1,0 +1,236 @@
+
+# load data
+# -----------------------------------------
+source("../../study1/vacc_import_data.R")
+
+
+# load packages
+# ----------------------------------------
+library(tidyverse)
+library(BiDAG)
+# BiDAG depends on 'graph' package, source: http://www.bioconductor.org/packages/release/bioc/html/graph.html
+# BiDAG depends on 'RBGL' package, source: https://bioconductor.org/packages/release/bioc/html/RBGL.html
+library(bnlearn)
+library(HydeNet)
+library(gtools)
+
+# source("cog-model-graph-tools.R")
+source("cog-model-main.R")
+source("../../Scripts/gmod_tools.R")
+source("../../Scripts/bnTheoryBlacklist.R")
+
+
+# transform data
+# ----------------------------------------
+
+rescale_beta <- function(x, lower, upper) {
+  # rescales onto the open interval (0,1)
+  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
+  
+  N <- length(x)
+  res <- (x - lower) / (upper - lower)
+  res <- (res * (N - 1) + .5) / N
+  
+  return(as.vector(res))
+}
+
+d_bn_scaled <- d_bn %>%
+  mutate_all(function(x){rescale_beta(x,-3,3)})
+
+## set the seed to make your partition reproductible
+set.seed(123)
+trainInd <- sample(seq_len(nrow(d_bn_scaled)), size = floor(nrow(d_bn_scaled)*.80))
+
+train <- d_bn_scaled[trainInd, ]
+test <- d_bn_scaled[-trainInd, ]
+
+
+# generate blacklists
+# ----------------------------------------
+nodes <- c(
+  "diseaseRare",
+  "diseaseSevere",
+  "hb",
+  "infantImmLimCap",
+  "infantImmWeak",
+  "medSkept",
+  "nat",
+  "overpar",
+  "parentExpert",
+  "vaccDanger",
+  "vaccEff",
+  "vaccIntent",
+  "vaccStrain",
+  "vaccTox"
+)
+
+theoryBasedHierarchy <- data.frame(
+  node = nodes,
+  order = c(
+    3,
+    3,
+    1,
+    3,
+    3,
+    2,
+    1,
+    2,
+    2,
+    3,
+    3,
+    4,
+    3,
+    3
+  )
+)
+
+intent_is_dv <- data.frame(
+  node = nodes,
[…]

### 2018-09-18 scripts/gmod_tools.R

@@ -1,0 +1,425 @@
+# gmod_tools.R
+# Author: Derek Powell
+# Created: 4/24/18
+# Updated: 5/10/18, 4:04 PM
+#
+# Tools for working with graphical models. Gathering functions created across notebooks/scripts into a single set of tools
+# for the project. May split them back out again if this gets too unweildy
+#
+# 1. Translating graphs/networks among existing R packages
+# 2. Doing MCMC inference on DAGs
+# 3. Creating pseudo-dbn networks
+
+# todo: 
+# 1. document functions
+# 2. refactor and possibly rename funcs/arguments
+# 3. explicitly map package functions with :: (done?)
+# 4. reduce dependencies(?)
+
+library(tidyverse)
+library(stringr)
+
+### ----------------------------------------
+# Translation functions
+# bnlearn, bdgraph, lavaan, and HydeNet
+
+
+# basic string functions
+cat_string_list <- function(listOfStrings) {
+  paste(listOfStrings, collapse = "")
+}
+
+
+cat_plus <- function(x) {
+  return(paste(x, "+ "))
+}
+
+
+cat_weight <- function(x, wVal) {
+  wVal <- round(wVal, 4) # to keep human-readable
+  paste0(wVal, "*", x)
+}
+
+
+cat_weight_list <- function(x, wVals) {
+  mapply(cat_weight, x, wVals)
+}
+
+
+write_sum <- function(toBeSummed) {
+  firstPart <- sapply(toBeSummed[1:length(toBeSummed) - 1], cat_plus)
+  cat_string_list(c(firstPart, toBeSummed[length(toBeSummed)]))
+}
+
+cat_and_sort <- function(x, y) {
+  sort(c(x, y)) %>% as.character(collapse = "") %>% paste(collapse = "")
+}
+
+wrap_brackets <- function(string) {
+  return(paste0("[", string, "]"))
+}
+
+wrap_space <- function(string) {
+  return(paste0(" ", string, " "))
+}
+
+get_left_of <- function(pattern, string) {
+  trimws(strsplit(string, pattern)[[1]][1])
+}
+
+# bnlearn --> arcs_df
+
+bnlearn_to_df <- function(bn.net) {
+  arcs <- data.frame(from = bnlearn::arcs(bn.net)[,1],
+                     to = bnlearn::arcs(bn.net)[,2])
+  return(arcs)
+}
+
+# arcs_df --> bnlearn
+
[…]

### 2018-09-18 scripts/loss.R

@@ -1,0 +1,140 @@
+# this is from bnlearn package
+# available at:
+# https://github.com/cran/bnlearn/blob/1100114a7e14b447b80f95ae2790c1bb18198c57/R/loss.R
+# copy/pasted 1/4/18, 10:32 AM
+
+loss.function = function(fitted, data, loss, extra.args, debug = FALSE) {
+
+  if (loss %in% c("logl", "logl-g", "logl-cg")) {
+
+    result = entropy.loss(fitted = fitted, data = data, debug = debug)
+
+  }#THEN
+  else if (loss %in% c("pred", "pred-lw", "pred-lw-cg")) {
+
+    result = classification.error(node = extra.args$target, fitted = fitted,
+               prior = extra.args$prior, n = extra.args$n,
+               from = extra.args$from, data = data, loss = loss, debug = debug)
+
+  }#THEN
+  else if (loss %in% c("cor", "cor-lw", "cor-lw-cg")) {
+
+    result = predictive.correlation(node = extra.args$target, fitted = fitted,
+               n = extra.args$n, from = extra.args$from, data = data,
+               loss = loss, debug = debug)
+
+  }#THEN
+  else if (loss %in% c("mse", "mse-lw", "mse-lw-cg")) {
+
+    result = mean.square.error(node = extra.args$target, fitted = fitted,
+               n = extra.args$n, from = extra.args$from, data = data,
+               loss = loss, debug = debug)
+
+  }#THEN
+
+  if (debug)
+    cat("  @ total loss is", result$loss, ".\n")
+
+  return(result)
+
+}#LOSS.FUNCTION
+
+# how to aggregate loss functions across the folds of cross-validation.
+kfold.loss.postprocess = function(kcv, kcv.length, loss, extra.args, data) {
+
+  if (loss %in% c("cor", "cor-lw")) {
+
+    if (all(is.na(unlist(sapply(kcv, "[", "loss"))))) {
+
+      # this happens for root nodes, whose predictions are just the mean of
+      # the response over the test set; propagate the NAs to the CV estimate.
+      mean = NA
+
+    }#THEN
+    else {
+
+      # match predicted and observed values.
+      pred = unlist(lapply(kcv, "[[", "predicted"))
+      obs = unlist(lapply(kcv, "[[", "observed"))
+      # compute the predictive correlation.
+      mean = cor(obs, pred)
+
+    }#ELSE
+
+  }#THEN
+  else {
+
[…]

### 2018-09-18 scripts/modelstringFuncs.R

@@ -1,0 +1,96 @@
+# Functions for translating network objects across packages via model strings / formulas
+# Author: Derek Powell
+# Created: 3/8/18, 3:46 PM
+# Updated: 3/8/18, 4:24 PM
+
+wrap_brackets <- function(string) {
+  return(paste0("[",string,"]"))
+}
+
+wrap_space <- function(string) {
+  return(paste0(" ",string," "))
+}
+
+make_bnlearn_node_string <- function(node, children) {
+  output <- as.character(node)
+  
+  if (length(children) > 0) {
+    output <- paste0(output,"|")
+    for (c in children) {
+      output <- paste0(output,c,":") 
+      
+    }
+    output <- substr(output,1,nchar(output)-1)
+  }
+  
+  return(wrap_brackets(output))
+}
+
+make_hyde_node_string <- function(node, children) {
+  output <- as.character(node)
+  
+  if (length(children) > 0) {
+    output <- paste0(output,"|")
+    for (c in children) {
+      output <- paste0(output,c,"*") 
+      
+    }
+    output <- substr(output,1,nchar(output)-1)
+  }
+  
+  return(wrap_space(output))
+}
+
+df_to_hyde_string <- function(df) {
+  output <- ""
+  for (node in unique(unlist(df))) {
+    edges <- df[which(df$to==node),"from"]
+    edges <- edges$from
+    nodeString <- make_hyde_node_string(node, edges)
+    output <- paste0(output,"+",nodeString)
+    
+  }
+  output <- paste0("~",substr(output, 2, nchar(output)))
+  
+  return(output)
+}
+
+
+df_to_bnlearn_string <- function(df) {
+  output <- ""
+  for (node in unique(unlist(df))) {
+    edges <- df[which(df$to==node),"from"]
+    edges <- edges$from
+    nodeString <- make_node_string(node, edges)
+    output <- paste0(output,nodeString)
+    
+  }
+  return(output)
+}
+
+bnlearn_to_hyde <- function(bn.net) {
+  arcs <- as.data.frame(bnlearn::arcs(bn.net))
+  return(df_to_hyde_string(arcs))
+}
+
+bn_to_dbn <- function(model) {
+  # takes a bnlearn bn, bn.fit, or modelstring and transforms it into a dynamic bayes net
+  # with a second mirrored stage (could later be generalized to add a timestep)
[…]

### 2018-09-18 scripts/transformation.R

@@ -1,0 +1,18 @@
+boxcox_transform <- function(x, lambda2=NULL) {
+	# finds optimal boxcox transformation parameters and performs transformation
+  	# (requires AID and car packages)
+  	# returns box-cox transformed variable
+  minval <- min(x)
+  
+  if(minval <= 0) {lambda2 <- abs(minval) + .01}
+  if(!is.null(lambda2)) {x <- x + lambda2}
+  
+  bc <- AID::boxcoxnc(x, lambda = seq(-10,10,.01), lambda2=lambda2, plot=FALSE, verbose=FALSE)
+    
+  return(car::bcPower(x, bc$lambda.hat))
+}
+
+normalize <- function(x) {
+	# rescale variable to (0,1) range
+    return ((x - min(x)) / (max(x) - min(x)))
+  }

### 2018-09-18 scripts/virtualEvidence.R

@@ -1,0 +1,216 @@
+# # Author: Derek Powell
+# # Updated: 5/14/18, 2:57 PM
+
+# # code for applying virtual evidence to cognitive model
+
+# functions for creating virtual evidence formula links
+
+make_ve_formula_strings <- function(nodes, suffix = "_v") {
+  lapply(nodes, function(x){paste0(x, suffix, " ~ ", x)})
+}
+
+# functions for fitting the weights of those links
+fit_formulas <- function(formula_strings, data, family="gaussian") {
+  # take a list of formulas as strings and return fit glm objects
+  # formula_strings: strings specifying formulas
+  # data: data for analyses
+  # family: glm family string or function object
+  
+  if (family %in% c("gaussian","binomial","gamma")) {# etc, finish later
+    lapply(formula_strings, function(x) {
+      glm(as.formula(x), data = data, family = family)
+    })
+  } else if (family=="beta") {
+    require(betareg)
+    lapply(formula_strings, function(x) {
+      betareg::betareg(as.formula(x), data = data)
+    })
+  }
+}
+
+# A function to assemble the results with the original model
+# 1. get lm coefficients and make jags code (modify make_jags_eq for lm())
+
+glm_to_jags_eq <- function(fit, digits=5) {
+  # fit: glm fit object
+  # returns jags code
+  
+  if (class(fit) == "glm") {
+    response_node <- as.character(formula(fit))[2]
+    coefs <- round(fit$coefficients, digits)
+    linear_eq <- paste0(coefs[1])
+    
+    if (length(coefs) > 1) {
+      
+      for (i in 2:length(coefs)) {
+        
+        coef_name <- names(coefs)[i]
+        coef <- coefs[i]
+        linear_eq <- paste0(linear_eq, " + ", coef, "*", coef_name)
+      }
+    }
+    if (fit$family$family == "gaussian") {
+      precision <- 1/stats::sigma(fit)^2
+      paste0(response_node," ~ ", "dnorm(", linear_eq,", ", round(precision,5),")")
+    } else if (fit$family$family == "binomial") {
+      paste0(response_node, " ~ ", "dbern(ilogit(", linear_eq, "))")
+    }
+  } else if (class(fit) == "betareg") {
+    
[…]

### 2018-09-18 study1/vacc_import_data.R

@@ -1,0 +1,118 @@
+
+# set wd (user-specific)
+# setwd("/Users/kweisman/Documents/Research (Stanford)/Projects/Vaccines/vaccineBeliefs/study1/")
+library(tidyverse)
+library(stringr)
+
+# working_dir <- getwd()
+# this.dir <- dirname(parent.frame(2)$ofile)
+# setwd(this.dir)
+
+# load in raw data
+d_raw <- read.csv("../data/study1_data.csv", header = T)
+
+# filter rows and select columns
+d1 <- d_raw %>%
+  filter(grepl("2017", StartDate)) %>% # remove extra headers
+  filter(Status == "IP Address") %>% # remove survey previews (?)
+  filter(Progress == 100) %>% # only get people who made it all the way through (?)
+  filter(as.numeric(as.character(age)) >= 18) %>% # exclude people who said they were <18 yo (could be more stringent)
+  select(StartDate, Duration..in.seconds., ResponseId, hb_1:comments) # include only selected columns
+
+# reformat variables
+d2 <- d1 %>% 
+  mutate_at(vars(StartDate), funs(parse_datetime)) %>% # parse dates
+  mutate_at(vars(Duration..in.seconds., age, children), funs(as.character)) %>% # parse numbers step 1
+  mutate_at(vars(Duration..in.seconds., age, children), funs(as.numeric)) %>% # parse numbers step 2
+  mutate(educ = factor(educ, # recode ordinal variables
+                       levels = c("No Diploma", "High School or Equivalent",
+                                  "Some Undergraduate Education", "Undergraduate Degree",
+                                  "Some Graduate or Professional Education",
+                                  "Graduate or Professional Degree", "Doctorate")),
+         income = factor(income, 
+                         levels = c("Less than $20,000", "$20,000 - $30,0000",
+                                    "$30,001 - $50,000", "$50,001 - $70,000",
+                                    "$70,001 - $100,000", "More than $100,000")),
+         parent = factor(parent, levels = c("No", "Yes")),
+         expecting = factor(expecting, levels =c ("No", "Yes")),
+         youngest_child = factor(youngest_child, 
+                                 levels = c("Less than 1 year old", "1 year old", "2 years old", 
+                                            "3 years old", "4 years old", "5 years old", "6 years old",
+                                            "7 years old", "8 years old", "9 years old", "10 years old",
+                                            "11 years old", "12 years old", "13 years old", "14 years old",
+                                            "15 years old", "16 years old", "17 years old", "18 years old",
[…]

### 2018-09-18 study2/interim_sample_size_check.R

@@ -1,0 +1,46 @@
+setwd("~/Projects/Vaccines/Repos/vaccineBeliefs/study3/")
+
+read_qualtrics_csv <- function(fname) {
+  df <- read.csv(fname, skip = 3, header = F)
+  headers <- as.matrix(read.csv(fname, skip = 0, header = F, nrows = 1, as.is = T))
+  colnames(df) <- headers
+  df <- df[which(df[, "DistributionChannel", ] == "anonymous"), ] # remove survey previews
+  total_n <- nrow(df)
+  
+  remove_cols <- c(
+    "RecipientLastdata",
+    "RecipientFirstdata",
+    "RecipientEmail",
+    "Finished",
+    "ResponseId",
+    "ExternalReference",
+    "DistributionChannel",
+    "UserLanguage",
+    "Status"
+  )
+  
+  df <- df[, -which(colnames(df) %in% remove_cols)]
+  
+  return(df)
+}
+
+pre <- read_qualtrics_csv("./data/vaccine+many+beliefs+-+interv+1+pre+-+APRIL_April+24%2C+2018_10.54.csv")
+post1 <- read_qualtrics_csv("./data/vaccine+many+beliefs+-+interv+1+post+g1+-+APRIL_April+24%2C+2018_10.55.csv") %>%
+  select(Progress, hb_check_5, vaccEff_check_1,vaccTox_check_6, vaccDanger_check_3)
+post2 <- read_qualtrics_csv("./data/vaccine+many+beliefs+-+interv+1+post+g2+-+APRIL_April+24%2C+2018_10.55.csv") %>%
+  select(Progress, hb_check_5, vaccEff_check_1,vaccTox_check_6, vaccDanger_check_3)
+post3 <- read_qualtrics_csv("./data/vaccine+many+beliefs+-+interv+1+post+g3+-+APRIL_April+24%2C+2018_10.56.csv") %>%
+  select(Progress, hb_check_5, vaccEff_check_1,vaccTox_check_6, vaccDanger_check_3)
+
+df_post <- post1 %>%
+  bind_rows(post2) %>%
+  bind_rows(post3) %>%
+  as_tibble() %>%
+  filter(Progress==100) %>%
+  filter(hb_check_5==5,
+         vaccEff_check_1==1,
+         vaccTox_check_6==6,
+         vaccDanger_check_3==3) 
+
+# started with 667, invited 574 to return, got 450 to return and complete, 405 of them passed all checks
+# so lost 14%, 22%, and 10% at each step.

### 2018-09-18 study2/load-study2-data.R

@@ -1,0 +1,59 @@
+# load data for study 3
+# Kara's code
+
+library(tidyverse)
+d_all <- read.csv("../data/study2_data.csv")[-1]
+
+# reformat to match previous analyses (i.e., 2 rows per participant)
+d_demo <- d_all %>% 
+  select(workerId, condition, gender, age, ethnicity, education, job, income,
+         political_party, political_beliefs, eligible_pretest, 
+         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
+         children_youngest_posttest, plan_parent_posttest,
+         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
+         starts_with("comments"), starts_with("duration"))
+d_pre <- d_all %>% 
+  select(workerId, ends_with("_pretest")) %>%
+  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
+            starts_with("attention_"), starts_with("comments"), 
+            starts_with("duration"))) %>%
+  rename_all(funs(gsub("_pretest", "", .))) %>%
+  mutate(phase = "pre")
+d_post <- d_all %>% 
+  select(workerId, ends_with("_posttest")) %>%
+  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
+            children_youngest_posttest, plan_parent_posttest,
+            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
+            starts_with("comments"), starts_with("duration"))) %>%
+  rename_all(funs(gsub("_posttest", "", .))) %>%
+  mutate(phase = "post")
+
+d <- bind_rows(d_pre, d_post) %>% 
+  gather(question, response, -c(workerId, phase)) %>%
+  mutate(phase = factor(phase,
+                        levels = c("pre", "post")),
+         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
+         # NOTE: "response" has already been reverse coded!
+         question = factor(question),
+         scale = factor(gsub("_.*$", "", question),
+                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
+                                   "vaccStrain", "vaccTox", 
+                                   "diseaseSevere", "diseaseRare", 
+                                   "infantImmLimCap", "infantImmWeak", 
+                                   "medSkept", "hb", "nat", 
[…]

### 2018-09-18 study2/cog-model-discrete-predictions.Rmd
refactored, working

@@
 
-source("../../study1/vacc_import_data.R")
-source("../../Scripts/gmod_tools.R")
+source("../study1/vacc_import_data.R", chdir = TRUE)
+source("../scripts/gmod_tools.R")
 # source("../../Scripts/virtualEvidence.R")
@@
 
-source("cog-model-main.R")
+source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)
 ```

### 2018-09-18 study2/lab_pres_nb_2018-6-11.Rmd
refactored, working

@@
 ```{r load in existing objects, message=FALSE, warning=FALSE}
-net.struct <- readRDS("net-struct-cogsci2018.rds")
+# net.struct <- readRDS("net-struct-cogsci2018.rds")
 
 source("../study1/vacc_import_data.R")
-source("../Scripts/gmod_tools.R")
-source("../Scripts/virtualEvidence.R")
+source("../scripts/gmod_tools.R")
+source("../scripts/virtualEvidence.R")
 
@@
 # load data
-d_all <- read.csv("data/study3_data.csv")
+d_all <- read.csv("../data/study2_data.csv")
 

### 2018-09-18 study2/study2-evid-ratio.Rmd
refactored, working

@@
 The resulting evidence ratio is `r evid_ratio`. Reasonable CPT values would be .5 and `r .5*evid_ratio` That's not that huge really ...
+
+# maximum likelihood estimate with optim()
+
+WE can do this with optim too, which will work better when we go to do it 14 times.
+
+```{r}
+inv_logit <- plogis
+logit <- qlogis
+
+evid_score_func <- function(data, par) {
+  pred_y <- with(data,
+                 {
+                   inv_logit(logit(pre) + evid*par[2] + par[1])
+                 }
+       )
+  pred_beta_A <- pred_y * par[3]
+  pred_beta_B <- (1-pred_y) * par[3]
+
+  ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
+  return(ll)
+}
+
+result <- optim(par = c(0, 0, 5), fn = evid_score_func, data = d, method="BFGS")
+
+result
+```

### 2018-09-18 study1/vacc_import_data.R

@@ -115,4 +115,4 @@ d_bn <- d_sum %>%
   remove_rownames() %>%
   column_to_rownames("ResponseId")
 
-setwd(working_dir) # reset working directory
+# setwd(working_dir) # reset working directory

### 2018-09-18 study2/interim_sample_size_check.R

@@ -1,46 +1,0 @@
-setwd("~/Projects/Vaccines/Repos/vaccineBeliefs/study3/")
-
-read_qualtrics_csv <- function(fname) {
-  df <- read.csv(fname, skip = 3, header = F)
-  headers <- as.matrix(read.csv(fname, skip = 0, header = F, nrows = 1, as.is = T))
-  colnames(df) <- headers
-  df <- df[which(df[, "DistributionChannel", ] == "anonymous"), ] # remove survey previews
-  total_n <- nrow(df)
-  
-  remove_cols <- c(
-    "RecipientLastdata",
-    "RecipientFirstdata",
-    "RecipientEmail",
-    "Finished",
-    "ResponseId",
-    "ExternalReference",
-    "DistributionChannel",
-    "UserLanguage",
-    "Status"
-  )
-  
-  df <- df[, -which(colnames(df) %in% remove_cols)]
-  
-  return(df)
-}
-
-pre <- read_qualtrics_csv("./data/vaccine+many+beliefs+-+interv+1+pre+-+APRIL_April+24%2C+2018_10.54.csv")
-post1 <- read_qualtrics_csv("./data/vaccine+many+beliefs+-+interv+1+post+g1+-+APRIL_April+24%2C+2018_10.55.csv") %>%
-  select(Progress, hb_check_5, vaccEff_check_1,vaccTox_check_6, vaccDanger_check_3)
-post2 <- read_qualtrics_csv("./data/vaccine+many+beliefs+-+interv+1+post+g2+-+APRIL_April+24%2C+2018_10.55.csv") %>%
-  select(Progress, hb_check_5, vaccEff_check_1,vaccTox_check_6, vaccDanger_check_3)
-post3 <- read_qualtrics_csv("./data/vaccine+many+beliefs+-+interv+1+post+g3+-+APRIL_April+24%2C+2018_10.56.csv") %>%
-  select(Progress, hb_check_5, vaccEff_check_1,vaccTox_check_6, vaccDanger_check_3)
-
-df_post <- post1 %>%
-  bind_rows(post2) %>%
-  bind_rows(post3) %>%
-  as_tibble() %>%
-  filter(Progress==100) %>%
-  filter(hb_check_5==5,
-         vaccEff_check_1==1,
-         vaccTox_check_6==6,
-         vaccDanger_check_3==3) 
-
-# started with 667, invited 574 to return, got 450 to return and complete, 405 of them passed all checks
-# so lost 14%, 22%, and 10% at each step.

### 2018-09-20 study2/cog-model-discrete-predictions.Rmd
updated study2 modeling

@@
 ---
-title: "R Notebook"
+title: "int-theory-vacc: Study 2 modeling"
 output: 
@@
     code_folding: hide
-    toc: true
-    toc_float: true
+    # toc: true
+    # toc_float: true
 ---
@@
 library(bnlearn)
+
+library(rsample)
 
@@
 # first load in mcmc results
-all_results <- readRDS("allresults.rds")
+all_results <- readRDS("../local/allresults.rds")
 nodes <- colnames(train)
@@
 
-## creating cognitive model
+## Translate into cognitive model
 
@@
 
+Compute and add evidence cpt
+
 ```{r}
-# add evidence node with cpt defined 
-evid_ratio <- exp(0.4566215)
+inv_logit <- plogis
+logit <- qlogis
 
-evid_cpt <- make_custom_cpt(c(.5*evid_ratio,.5, (1-.5*evid_ratio), (1-.5)), c(2,2), list(diseaseSevere=c("Yes","No"), evid = c("Yes","No") ), NULL)
-# evid_cpt <- make_custom_cpt(c(.83,.5, .17, .5), c(2,2), list(diseaseSevere=c("yes","No"), evid = c("yes","no") ), NULL)
+evid_score_func <- function(data, par) {
+
+  inv_logit <- plogis
+  logit <- qlogis
+
+  pred_y <- with(data,
+                 {
+                   inv_logit(logit(pre) + evid*par[2] + par[1])
+                 }
+       )
+  pred_beta_A <- pred_y * par[3]
+  pred_beta_B <- (1-pred_y) * par[3]
+
+  ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
+  return(ll)
+}
+
+get_evid_probs <- function(result){
+  # this is a heuristic/hack, could be made better but probably doesn't matter
+  evid_ratio <- exp(result$par[1] + result$par[2])
+  if (evid_ratio < 1) {
+    p0 <- .90
+  } else {
+    p0 <- .50
+  }
+
+  if (p0*evid_ratio > 1) {
+    p0 <- p0*.9/(p0*evid_ratio)
+  }
+
+  p1 <- p0*evid_ratio
+
+  c(p0,p1)
+}
+
+evid_probs_to_cpt <- function(probs, var_name){
+  p0 <- probs[1]
+  p1 <- probs[2]
+
+  full_list <- paste0("list(",var_name,"=c('Yes','No'), evid = c('Yes', 'No'))")
+  make_custom_cpt(c(p1, p0, (1-p1), (1-p0)), c(2,2), eval(parse(text=full_list)), NULL)
+}
+
+find_evid_ratio <- function(data){
+  optim(par = c(0, 0, 5), fn = evid_score_func, data = data, method="BFGS")
+}
+
+make_evid_cpt <- function(data, var_name){
+  result <- find_evid_ratio(data)
+  probs <- get_evid_probs(result)
+  cpt <- evid_probs_to_cpt(probs, var_name)
+
+  return(cpt)
+}
+
+```
+
+```{r}
+source("../study2/load-study2-data.R", chdir = TRUE)
+
+d <- d_scored %>%
+  filter(scale == "diseaseSevere") %>%
+  mutate(mean = rescale_beta(mean, -3, 3)) %>%
+  spread(phase, mean) %>% 
+  mutate(condition = relevel(condition, ref="noInterv")) %>%
+  mutate(evid = ifelse(condition=="noInterv",0,1))
+
+evid_cpt <- make_evid_cpt(d, "diseaseSevere")
+
 bagOfModels$evid <- evid_cpt
@@
 ```
+
+Generate predictions ...
 
@@
 predModel <- custom.fit(model_network, dist = bnlearn_models)
+
 ```
@@
 ```{r}
-# cpquery(predModel, event = (eval(parse(text="diseaseSevere"))=="Yes"), evidence = TRUE)
-# cpquery(predModel, event = (eval(parse(text="diseaseSevere == 'Yes'"))), evidence = TRUE)
-# cpquery(predModel, event = (eval(parse(text="diseaseSevere"))=="Yes"), evidence = (evid == "Yes"))
-
 set.seed(12345)
@@
 
+Compare predicted and observed changes ...
+
 ```{r}
-source("../../study3/load-study3-data.R", chdir = TRUE)
 
@@
 
-----------------------------------------------
+# What beliefs are targetted by the intervention?
 
-HydeNet prediction failures below ...
+Here we can pretend that expectations for the intervention materials are set by each of the 14 beliefs, and compare the accuracy of the resulting models' predictions.
+We should also ask whether the differences among models are substantial and reliable enough for us to prefer any one model over another.
 
 ```{r}
-set.seed(456)
-model0 <- compileJagsModel(bagNet)
-model1 <- compileJagsModel(bagNet, data= data.frame(evid=2))
+create_bnlearn_cog_model <- function(dag, data, evid_cpt = NULL, targetted_belief = NULL) {
+  arcs_df <- bnlearn_to_df(dag)
+  graph_list <- df_to_list(arcs_df)
+  bagOfModels <- lapply(graph_list, function(x){fit_node_cpt(x, data)})
+  model_string <- as.character(dag)
 
-post0 <- HydeSim(model0,
-                       variable.names = nodes,
-                       n.iter = 1e5
-                       )
+  if (!(is.null(evid_cpt))) {
+    bagOfModels$evid <- evid_cpt
+    model_string <- paste0(model_string,"[evid|", targetted_belief, "]")
+  }
+  model_network <- model2network(model_string)
+  bnlearn_models <- lapply(bagOfModels, hyde_to_bn_cpt)
+  predModel <- custom.fit(model_network, dist = bnlearn_models)
 
-post1 <- HydeSim(model1,
-                       variable.names = nodes,
-                       n.iter = 1e5
-                       )
+  return(predModel)
+}
 
-post0 <- post0 %>%
-  mutate(nat = ifelse(nat=="Yes",2,1)) %>%
-  mutate_all(~ . -1) %>%
-  summarize_all(mean) %>%
-  select(-chain_index, -obs_index)
+add_evid_node <- function(data, bnlearn_model, targetted_belief) {
 
-post1 <- post1 %>%
-  mutate(nat = ifelse(nat=="Yes",2,1)) %>%
-  mutate_all(~ . -1) %>%
-  summarize_all(mean) %>%
-  select(-evid, -chain_index, -obs_index)
+  evid_cpt <- make_evid_cpt(data, targetted_belief)
+  model_list <- lapply(bnlearn_model, function(x){x$prob})
+  model_list$evid <- hyde_to_bn_cpt(evid_cpt)
 
-pred_changes <- (post1 - post0)  %>%
-  gather(scale, Mean) %>%
-  mutate(type = "predicted")
+  model_string <- modelstring(bnlearn_model)
+  model_string <- paste0(model_string,"[evid|", targetted_belief, "]")
+  model_network <- model2network(model_string)
+  predModel <- custom.fit(model_network, dist = model_list)
+
+  return(predModel)
+}
+
 ```
@@
 ```{r}
-source("../../study3/load-study3-data.R", chdir = TRUE)
+filter_dscored <- function(data, scale_name){
 
-obs_changes <- d_scored %>%
+  data %>%
+  filter(scale == scale_name) %>%
+  mutate(mean = rescale_beta(mean, -3, 3)) %>%
+  spread(phase, mean) %>% 
+  mutate(condition = relevel(condition, ref="noInterv")) %>%
+  mutate(evid = ifelse(condition=="noInterv",0,1))
+}
+
+cogModel_predictions <- function(model){
+  pred0 <- sapply(nodes, function(x){
+  statement <- paste0("cpquery(model, event = (", x, " == 'Yes'), evidence=TRUE, n = 1e5)")
+  eval(parse(text=statement))
+  })
+
+  pred1 <- sapply(nodes, function(x){
+    statement <- paste0("cpquery(model, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 1e5)")
+    eval(parse(text=statement))
+  })
+
+  pred_changes <- pred1 - pred0
+
+  pred_changes <- as.data.frame(pred_changes)
+
+  pred_changes <- pred_changes %>%
+    mutate(scale = nodes) %>%
+    rename(Mean = pred_changes) %>%
+    mutate(type = "predicted")
+
+  return(pred_changes)
+}
+
+compare_pred_obs_r <- function(predicted, observed){
+
+  obs_pred <- suppressWarnings(bind_rows(predicted, observed)) %>%
+    spread(type, Mean) %>%
+    group_by(scale) %>%
+    summarize_all(mean, na.rm=TRUE)
+
+  cor(obs_pred$predicted, obs_pred$observed)
+}
+
+compare_pred_obs_rmse <- function(predicted, observed){
+
+  obs_pred <- suppressWarnings(bind_rows(predicted, observed)) %>%
+    spread(type, Mean) %>%
+    group_by(scale) %>%
+    summarize_all(mean, na.rm=TRUE)
+
+  sqrt(mean((obs_pred$observed-obs_pred$predicted)^2))
+
+}
+
+extract_obs_changes <- function(observed){
+  obs_changes <- observed %>%
   mutate(mean = rescale_beta(mean, -3, 3)) %>%
@@
     Mean = mean(changeScore),
-    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()),
+    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()), # replace with bootstrapping
     ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
@@
   mutate(type = "observed")
-
-bind_rows(pred_changes, obs_changes) %>%
-  spread(type, Mean) %>%
-  group_by(scale) %>%
-  summarize_all(mean, na.rm=TRUE) %>% # a bit of a hack
-  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
-  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
-  geom_point() +
-  geom_errorbar() +
-  # coord_cartesian(xlim=c(-.1,.1), ylim=c(-.1,.1)) +
-  theme_bw() +
-  theme(aspect.ratio = 1)
-```
-
-Strong correlation, and pretty good numerically.
-But for some reason it's getting disease severity wrong!
-I really can't wrap my head around it, it's not predicting what I would expect based on the evidence ratio (when I do it manually, the predictions are more in line with observed).
-So something strange is going wrong.
-I should try making a really simple little test case.
-
-```{r}
-bind_rows(pred_changes, obs_changes) %>%
-  spread(type, Mean) %>%
-  group_by(scale) %>%
-  summarize_all(mean, na.rm=TRUE) %>%
-  mutate(abs_resid = abs(predicted - observed)) %>%
-  arrange(-abs_resid)
-```
-
-So for some reason this is not working quite right with hydenet. I'm going to translate things over to bnlearn and try taht.
-# JUNK BELOW
-----------------------------------------
-
-```{r}
-
-make_predictions_hyde <- function(hyde_model, orig_data, nodes_to_predict, nodes_held_out=c(), iter=1e3) {
-  # takes a model and dataframe and generates model predictions for variables listed in 
-  # nodes_to_predict. By default, uses all remaining nodes in orig_data. Hold out nodes from
-  # prediction with nodes_held_out. iter sets mcmc samples
-
-  pred_df <- orig_data
-  pred_df[,nodes_to_predict] <- NA
-
-  for (i in 1:nrow(pred_df)) {
-    row <- pred_df[i,]
-    row[nodes_held_out] <- NA
-    pred <- do_jags_inference(hyde_model, nodes_to_predict, data = row, iter = iter)
-    point_preds <- rowMeans(t(pred[[1]][(iter/2+1):iter,nodes_to_predict]))
-    pred_df[i,nodes_to_predict] <- point_preds
-  }
-
-  return(pred_df)
-}
-
-predict_change_scores_cog <- function(model, nodes_to_predict, iter){
-
-  preds_mean1 <- make_predictions(model, 
-                                data.frame(evid=1), 
-                                nodes_to_predict, 
-                                c(),
-                                iter = iter)
-
-  preds_mean0 <- make_predictions(model, 
-                                  data.frame(), 
-                                  nodes_to_predict, 
-                                  c("evid"),
-                                  iter = iter)
-
-  preds_mean <- preds_mean1 - preds_mean0
-}
-
-predict_change_scores_cog(bagNet, nodes, 1e4)
-```
-
-```{r}
-# define some functions for doing and processing predictions
-
-predict_change_scores <- function(model, data0, data1, nodes_to_predict, held_out_nodes=c(), iter=1e4) {
-  # note: intervention must be named "interv"
-
-  require(dplyr)
-
-  preds_mean1 <- make_predictions(model, 
-                                data1, 
-                                nodes_to_predict, 
-                                held_out_nodes,
-                                iter = iter)
-
-  preds_mean0 <- make_predictions(model, 
-                                  data0, 
-                                  nodes_to_predict, 
-                                  held_out_nodes,
-                                  iter = iter)
-
-  preds_mean <- preds_mean1 - preds_mean0
-
-}
-
-process_predictions <- function(predictions, obs_data) {
-  require(dplyr)
-  predictions <- predictions %>% 
-  select(-interv) %>%
-  gather(scale, predicted) %>%
-  left_join(obs_data, by = "scale") 
-}
-
-plot_processed_predictions <- function(processed_predictions) {
-  require(dplyr)
-  require(ggplot2)
-  plt1 <- processed_predictions %>%
-    mutate(
-           UL = observed + std_error*1.96,
-           LL = observed - std_error*1.96
-           ) %>%
-    ggplot(aes(x=predicted, y = observed, ymin = LL, ymax=UL)) +
-    geom_errorbar(color="grey", width=0) +
-    geom_point() +
-    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color="grey") +
-    theme_bw() +
-    theme(aspect.ratio = 1)
-
-  plt2 <- processed_predictions %>% 
-    # left_join(obs_error, by = "scale") %>%
-    group_by(scale) %>%
-    gather(type, change_score, observed, predicted) %>%
-    mutate(std_error = ifelse(type == "observed", std_error, NA )) %>%
-    mutate(
-           UL = change_score + std_error*1.96,
-           LL = change_score - std_error*1.96
-           ) %>%
-    ggplot(aes(y = reorder(scale, change_score),
-               x = change_score,
-               xmax = UL, 
-               xmin = LL, 
-               color = type)) +
-    geom_point(shape=17, size=3) +
-    geom_errorbarh(height=0) +
-    theme_bw()
-    # theme(axis.text.x = element_text(angle = 90, hjust = 1))
-
-  return(list(corr_plot = plt1, means_plot = plt2))
-}
-
-score_predictions <- function(processed_predictions) {
-  list(
-  r = cor(processed_predictions$observed, processed_predictions$predicted),
-  r_squared = cor(processed_predictions$observed, processed_predictions$predicted)^2,
-  mae = mean(abs(processed_predictions$observed - processed_predictions$predicted)),
-  rmse = sqrt(mean((processed_predictions$observed - processed_predictions$predicted)^2))
-  )
-}
-
-score_predictions_boot <- function(processed_predictions) {
-
-  samps <- 1:1000
-
-  preds <- lapply(samps, function(x){
-    pp <-  processed_predictions %>% 
-      mutate(resamp_observed = rnorm(14, observed, std_error))
-    list(
-    r = cor(pp$resamp_observed, pp$predicted),
-    r_squared = cor(pp$resamp_observed, pp$predicted)^2,
-    mae = mean(abs(pp$resamp_observed - pp$predicted)),
-    rmse = sqrt(mean((pp$resamp_observed - pp$predicted)^2))
-    )
-  })
-
 }
@@
 
-# conceptual illustration
+```{r}
+# -- takes about 20 min
+base_model <- create_bnlearn_cog_model(map_dag, train)
+
+# do bootstrap comparison
+set.seed(1234)
+t1 <- Sys.time()
+
+boot_fits <- as_tibble(expand.grid(
+  list(
+    replicate = 1:100, scale = nodes
+  )
+)) %>%
+  nest(-replicate, .key="scales") %>%
+  mutate(boot_d_scored = map(replicate, function(x) {
+    totaln <- length(unique(d_scored$workerId))
+    d_scored %>%
+      nest(-workerId) %>%
+      sample_n(totaln, replace = TRUE) %>%
+      mutate(uniqueId = 1:totaln) %>%
+      unnest()
+  })) %>%
+  unnest(scales, .drop=FALSE) %>%
+  mutate(
+      boot_d = map2(boot_d_scored, scale, function(x,y){filter_dscored(x, y)}),
+      obs_changes = map(boot_d_scored, extract_obs_changes)
+      ) %>%
+  select(-boot_d_scored) %>%
+  mutate(
+    models = map2(boot_d, scale, function(x,y){add_evid_node(x, base_model, y)}),
+    pred_changes = map(models, cogModel_predictions),
+    r = map2_dbl(pred_changes, obs_changes, compare_pred_obs_r),
+    rmse = map2_dbl(pred_changes, obs_changes, compare_pred_obs_rmse)
+    )
+
+print(Sys.time() - t1)
+```
 
 ```{r}
-p_x <- rbeta(100, 2, 2)
-p_y_x0 = .4
-p_y_x1 = .8
+boot_fits %>%
+  mutate(r2 = r^2) %>%
+  ggplot(aes(x=reorder(scale,-r2), y = r2)) +
+  geom_boxplot(fill="lightgray") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
 
-p_y = rethinking::rbeta2(100, p_x*p_y_x1 + (1-p_x)*p_y_x0, 100)
-
-plot(p_x, p_y)
-
-df <- data.frame(x=p_x, y=p_y)
-df %>%
-  rename(`p(fire)` = x,
-         `p(smoke)` = y) %>%
-  ggplot(aes(x=`p(fire)`, y = `p(smoke)`)) +
-  geom_point() +
-  theme_bw(base_size = 24)
+boot_fits %>%
+  ggplot(aes(x=reorder(scale,-r), y = rmse)) +
+  # geom_violin(fill="gray", alpha=.5) +
+  geom_boxplot(fill = "lightgray") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
 ```
 
-# correlation matrix
-
 ```{r}
-# borrowing code from
-# http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization
-
-reorder_cormat <- function(cormat){
-  # Use correlation between variables as distance
-  dd <- as.dist((1-cormat)/2)
-  hc <- hclust(dd)
-  cormat <-cormat[hc$order, hc$order]
-}
-
-# Get lower triangle of the correlation matrix
-get_lower_tri<-function(cormat){
-  cormat[upper.tri(cormat)] <- NA
-  return(cormat)
-}
-# Get upper triangle of the correlation matrix
-get_upper_tri <- function(cormat){
-  cormat[lower.tri(cormat)]<- NA
-  return(cormat)
-}
-
-corr_plot <- d_bn %>%
-  cor() %>%
-  reorder_cormat() %>%
-  # get_lower_tri() %>%
-  reshape2::melt(na.rm=TRUE) %>%
-  ggplot(aes(x=Var1, y = Var2, fill = value)) +
-  geom_tile(color = "white") +
-  geom_tile() +
-  geom_text(aes(label=round(value,2)), size=6*.35) +
-  scale_fill_distiller(type="div", palette = "RdYlBu") +
-  # scale_fill_viridis_c(limit = c(-1,1)) +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust=.85)) +
-  theme(aspect.ratio = 1) +
-  theme(
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    panel.grid.major = element_blank(),
-    panel.border = element_blank(),
-    panel.background = element_blank(),
-    axis.ticks = element_blank()
-  ) +
-  labs(fill="corr.")
-
-ggsave("corrplot.png", corr_plot, dpi=320, height=5,width=5)
+boot_fits %>% 
+  filter(scale=="diseaseSevere") %>%
+  summarize(
+    estimate = mean(r),
+    ul = quantile(r,.975),
+    ll = quantile(r, .025)
+    )
 ```
-
-# Aggregate predictions
-
-This notebook aims to examine/address the issue of predicting out-of-sample data using our model.
-In a previous notebook, `vacc_manyBelief_study3_modelsim.RMD`, I predicted average scale responses from study 3 using the previously learned model by conditioning on the Disease Severe node.
-
-In this notebook, I'll ...
-
-1. Explicitly model the intervention, rather than just conditioning disease severe.
-2. Examine model as "causal model"
-3. Explore model predictions under different assumptions about what beliefs are "targetted" by the intervention.
-4. Similarly, explore whether we should model the intervention as providing direct evidence for multiple beliefs.
-5. Consider naïve models ...
-
-## cognitive model
-
-First, let's examine the predictions of our cognitive model, where we treat the graphical model as a cognitive model, and reading the intervention materials as observing or conditioning on some evidence relevant to beliefs about disease severity.
-
-To recap, we have ...
-
-1. The cognitive network model (from study 1, n=1130 (data = `d_bn`))
-2. A model of the relationship between disease severity and the intervention, modeled from study 2.
-
-And we're predicting the average change scores observed in each condition following the disease risk manipulation in Study 2.
-So, for the most part this is an out-of-sample prediction task -- predicting change scores for new participants on the basis of a model generated from correlations observed among different participants, along with a bit of info about the intervention's effects on disease severity from the same participants.
-
-```{r, message=FALSE, warning=FALSE}
-
-nodes_to_predict <- bnlearn::nodes(net.struct)
-
-cog_model <- write_jags_model(bnlearn_to_df(net.struct), d_bn)
-
-# can modify this to test assumptions about direct effects of intervention ...
-interv_fit <- glm(interv ~ diseaseSevere, 
-                  data = interv_df,
-                  family = "binomial"
-                  )
-
-cog_model <- add_node(cog_model, glm_to_jags_eq(interv_fit))
-
-# can also just use "model" here so long as you include held_out_nodes
-
-preds_cog <- predict_change_scores(cog_model,
-                                           data.frame(interv = 0),
-                                           data.frame(interv = 1),
-                                           nodes_to_predict,
-                                           iter = 1e5*2.5
-                                           )
-
-# preds_cog$interv <- 0
-
-preds_cog <- process_predictions(preds_cog, obs_data)
-
-plots_cog <- plot_processed_predictions(preds_cog)
-
-scores_cog <- score_predictions(preds_cog)
-
-plt1 <- plots_cog$corr_plot +
-  geom_text(
-    aes(
-      label = ifelse(observed == preds_cog[which(preds_cog$scale == "diseaseSevere"), "observed"],
-        as.character(scale), ""
-      )
-    ),
-    hjust = 1.1, vjust = 0
-  ) +
-  geom_text(aes(label = ifelse(observed == preds_cog[which(preds_cog$scale == "overpar"), "observed"],
-    as.character(scale), ""
-  )), hjust = 1.1, vjust = 0) +
-  theme(aspect.ratio = 1) +
-  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
-  annotate("text", 
-           x = .25, 
-           y = -.2, 
-           label = paste("italic(R)^2 == ", round(scores_cog$r_squared,3)), 
-           parse = TRUE,
-           size=18*.35
-          ) +
-  theme_bw(base_size=18)
-
-plt2 <- plots_cog$means_plot +
-  labs(x="Change score", y="Belief Scale") +
-  theme_bw(base_size=18) +
-  theme(legend.position = "bottom")
-
-ggsave("plot.png", plot = plt1, dpi=320, width=4, height=4)
-ggsave("plot2.png", plot = plt2, dpi=320, width=6, height=4)
-
-```
-
-So it's a pretty good fit, as we expected.
-Note that the r = `r score_predictions(preds_cog)$r %>% round(3)` is higher than the correlation in `...modelsims.Rmd` notebook, because I'm here also including disease severity in calculating the fit.
-
-## "Non-mental" model
-
-Next we can rule out the (perhaps not-all-that tempting) argument that we haven't developed a cognitive model at all, instead perhaps a causal model describing how holding different beliefs _causes_ a person to hold other beliefs.
-verbally that might not sound all that different, but the difference comes in how we conceive of evidence affecting participants' beliefs.
-Instead of an edge directed from the belief to the evidence, it'd be an edge directed from the evidence to the belief.
-
-(Here I'm fudging things a bit in a way that should be fine considering these are linear models.
-I'm keeping the edge directed from disease severity to intervention, but then doing "graph surgery" to prune the disease severity node's parents when we predict the effects of the intervention.
-Since we're predicting changes, I'm about 99% confident this should work.)
-
-```{r, message=FALSE, warning=FALSE}
-library(bnlearn)
-surgery_graph <- net.struct %>%
-  drop.arc("vaccEff", "diseaseSevere") %>%
-  drop.arc("infantImmLimCap", "diseaseSevere")
-
-causal_arcs <- bnlearn_to_df(surgery_graph)
-
-causal_model <- write_jags_model(causal_arcs, d_bn) %>% suppressWarnings()
-
-interv_fit <- glm(interv ~ diseaseSevere, 
-                  data = interv_df,
-                  family = "binomial"
-                  )
-
-causal_model <- add_node(causal_model, glm_to_jags_eq(interv_fit)) # this is a cheat but it's ok ...
-
-preds_causal <- predict_change_scores(causal_model,
-                                           data.frame(interv = 0),
-                                           data.frame(interv = 1),
-                                           nodes_to_predict,
-                                           iter = 1e5
-                                           )
-
-preds_causal <- process_predictions(preds_causal, obs_data)
-
-plots_causal <- plot_processed_predictions(preds_causal)
-
-scores_causal <- score_predictions(preds_causal)
-
-plt3 <- plots_causal$corr_plot +
-  geom_text(
-    aes(
-      label = ifelse(observed == preds_causal[which(preds_causal$scale == "diseaseSevere"), "observed"],
-        as.character(scale), ""
-      )
-    ),
-    hjust = 1.1, vjust = 0
-  ) +
-  # geom_text(aes(label = ifelse(observed == preds_cog[which(preds_cog$scale == "overpar"), "observed"],
-  #   as.character(scale), ""
-  # )), hjust = 1.1, vjust = 0) +
-  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
-  theme(aspect.ratio = 1) +
-  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
-  annotate("text", 
-           x = .25, 
-           y = -.2, 
-           label = paste("italic(R)^2 == ", round(scores_causal$r_squared,3)), 
-           parse=TRUE,
-           size=14*.35
-          ) +
-  theme_bw(base_size=18)
-
-# plots_causal$means_plot +
-#   labs(x="Change score", y="Belief Scale") +
-#   theme_bw(base_size=18)
-
-ggsave("plot3.png", plot = plt3, dpi=320, width=4, height=4)
-```
-
-Treating things as a causal model makes very poor predictions.
-
-# What beliefs are targetted by the intervention?
-
-Here we can pretend that expectations for the intervention materials are set by each of the 14 beliefs, and compare the accuracy of the resulting models' predictions.
-We should also ask whether the differences among models are substantial and reliable enough for us to prefer any one model over another.
-
-```{r}
-predict_change_scores_pipe <- partial(predict_change_scores,
-                                      data0 = data.frame(interv = 0),
-                                      data1 = data.frame(interv = 1),
-                                      nodes_to_predict = nodes_to_predict,
-                                      iter = 1e5
-                                      )
-
-all_beliefs <- nodes(net.struct)
-
-cog_model <- write_jags_model(bnlearn_to_df(net.struct), d_bn) %>% suppressWarnings()
-
-belief_targets_models <- lapply(all_beliefs, function(b){
-
-  f <- paste0("interv ~ ", b)
-
-  # can modify this to test assumptions about direct effects of intervention ...
-  interv_fit <- glm(as.formula(f), 
-                    data = interv_df,
-                    family = "binomial"
-                    )
-
-  model <- add_node(cog_model, glm_to_jags_eq(interv_fit))
-
-  }
-)
-
-model_compare <- tibble(
-  model_name = all_beliefs,
-  model = unlist(belief_targets_models)
-  ) %>%
-    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
-    mutate(proc_preds = map(predictions, process_predictions, obs_data = obs_data)) %>%
-    mutate(scores = map(proc_preds, score_predictions_boot))
-
-model_compare2 <- model_compare %>%
-    mutate(
-      rmse = map(scores, ~ sapply(.x, function(z){z$rmse})),
-      r_squared = map(scores, ~ sapply(.x, function(z){z$r_squared}))
-      ) %>%
-  gather(metric, value, rmse, r_squared) %>%
-  mutate(
-    mean_value = map_dbl(value, mean),
-    se_value = map_dbl(value, sd)
-    )
-
-plt_models <- model_compare2 %>%
-  mutate(
-    UL = mean_value + se_value,
-    LL = mean_value - se_value
-  ) %>%
-  ggplot(aes(x = reorder(model_name, -mean_value), y = mean_value, ymin = LL, ymax = UL)) +
-  geom_pointrange() +
-  theme_bw(base_size=18) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-  facet_wrap(~metric, scales="free") +
-  labs(x="Targetted belief", y = "Score")
-
-ggsave("plot_models.png", plot = plt_models, dpi=320, width=12, height=6)
-```
-
-# Modeling multiple targetted beliefs
-
-The biggest outlier point for our cognitive model is the "parental protectiveness" (`overpar`) belief.
-Considering the evocative content of the intervention, it's possible that it directly bears on this belief.
-
-Here we can model our intervention targetting both disease severity and overparenting ...
-
-```{r, message=FALSE, warning=FALSE}
-
-cog_model2 <- write_jags_model(bnlearn_to_df(net.struct), d_bn) %>% suppressWarnings()
-
-# can modify this to test assumptions about direct effects of intervention ...
-interv_fit <- glm(interv ~ diseaseSevere + overpar, 
-                  data = interv_df,
-                  family = "binomial"
-                  )
-
-cog_model2 <- add_node(cog_model2, glm_to_jags_eq(interv_fit))
-
-# can also just use "model" here so long as you include held_out_nodes
-
-preds_cog2 <- predict_change_scores(cog_model2,
-                                           data.frame(interv = 0),
-                                           data.frame(interv = 1),
-                                           nodes_to_predict,
-                                           iter = 1e5*2.5
-                                           )
-
-preds_cog2 <- process_predictions(preds_cog2, obs_data)
-
-plots_cog2 <- plot_processed_predictions(preds_cog2)
-
-scores_cog2 <- score_predictions(preds_cog2)
-
-plt4 <- plots_cog2$corr_plot +
-  geom_text(
-    aes(
-      label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "diseaseSevere"), "observed"],
-        as.character(scale), ""
-      )
-    ),
-    hjust = 1.1, vjust = 0
-  ) +
-  geom_text(aes(label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "overpar"), "observed"],
-    as.character(scale), ""
-  )), hjust = 1.1, vjust = 0) +
-    geom_text(aes(label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "infantImmWeak"), "observed"],
-    as.character(scale), ""
-  )), hjust = 1.1, vjust = 0) +
-  # geom_abline(intercept = 0, slope = 1, linetype = "dashed", color="grey") +
-  # geom_errorbar(aes(ymin = LL, ymax=UL)) +
-  theme(aspect.ratio = 1) +
-  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
-  annotate("text", 
-           x = .25, 
-           y = -.2, 
-           label = paste("italic(R)^2 == ", round(scores_cog2$r_squared,3)), 
-           parse=TRUE,
-           size=14*.35
-          )
-
-plots_cog2$means_plot +
-  labs(x="Change score", y="Belief Scale")
-
-ggsave("plot4.png", plot = plt4, dpi=320, width=4, height=4)
-```
-
-## Comparing models
-
-This code is a bit hacky, should write some better bootstrapping code.
-But here is a quick comparison, with somewhat unclear results.
-Previously this looked more clear cut, to me suggesting there may be more volatility in the mcmc sampling than I had thought.
-I should maybe give them more burn-in.
-
-```{r}
-boot_scores_cog <- score_predictions_boot(preds_cog)
-boot_scores_cog2 <- score_predictions_boot(preds_cog2)
-
-tibble(cog = sapply(boot_scores_cog, function(x){x$rmse}), 
-           cog2 = sapply(boot_scores_cog2, function(x){x$rmse})) %>%
-  gather(model, rmse, cog, cog2) %>%
-  ggplot(aes(x=model, y = rmse)) +
-  geom_boxplot() +
-  theme_bw()
-```
-
-# Naïve Models
-
-Once we see that we have a cognitive model, I'll say the _cognitive model assumption_ is met. And when it's met, it actually has some interesting consequences.
-
-Because observations in a cognitive model (as in, exposure to educational materials) are conditioning events rather than causal interventions, we can actually do a good job predicting their effects using naïve models.
-What I mean by naïve models are models that naïvely assume all beliefs are connected to some central, focal belief(s)--specifically, whichever beliefs are targetted by educational interventions.
-
-This works because all we need to predict the expected change is a model of the marginal conditional distribution of each variable.
-To put it in some math, our model approximates the joint distribution over all the variables $x_1$ through $x_n$:
-
-$$P(x_1, x_2, x_3, ..., x_n)$$
-
-But to ask how some other belief, $y$ will change on average, given some change in another belief $x$, that's something like this:
-
-$$E[P(y|x=1) - P(y|x=0)]$$
-
-And for that we only need to know the conditional probability, $P(y|x)$, which we can approximate in this naïve model.
-So here we have a model that naïvely assumes that disease severity beliefs influence all other beliefs.
-
-```{r, message=FALSE, warning=FALSE}
-
-vars <- d_scored %>% select(scale) %>% filter(scale!="diseaseSevere") %>% distinct()
-
-# naïve causal model, diseaseSevere--> all (equivalent change score prediction)
-nb_arcs <- data.frame(from = rep("diseaseSevere", 13), to = vars$scale)
-
-nb_model <- write_jags_model(nb_arcs, d_bn) %>% suppressWarnings()
-
-# can modify this to test assumptions about direct effects of intervention ...
-interv_fit <- glm(interv ~ diseaseSevere, 
-                  data = interv_df,
-                  family = "binomial"
-                  )
-
-nb_model <- add_node(nb_model, glm_to_jags_eq(interv_fit))
-
-# can also just use "model" here so long as you include held_out_nodes
-
-preds_nb <- predict_change_scores(nb_model,
-                                           data.frame(interv = 0),
-                                           data.frame(interv = 1),
-                                           nodes_to_predict,
-                                           iter = 1e5
-                                           )
-
-preds_nb <- process_predictions(preds_nb, obs_data)
-
-plots_nb <- plot_processed_predictions(preds_nb)
-
-plots_nb$corr_plot
-plots_nb$means_plot
-
-score_predictions(preds_nb)
-
-```
-
-The naïve model is comparable to the more complex cognitive model, at least when it comes to predicting the changes in beliefs following the interventions.
-Of course, as a model of the actual relationships among beliefs, it's terrible (see `...modelSims.Rmd` notebook for a brief exploration of that).
-
-### Naïvely modeling multiple targetted beliefs
-
-We can also model multiple direct evidence relations by extending the naïve model.
-There are probably multiple ways to extend it.
-What I've come up with here is to just assume that both disease severity and parental protectiveness are the two focal beliefs, and that they both influene all other beliefs.
-I suppose I could also add a connection between them one way or another.
-
-```{r, message=FALSE, warning=FALSE}
-
-vars2 <- d_scored %>% select(scale) %>% filter(scale!="diseaseSevere", scale!="overpar") %>% distinct()
-
-# naïve causal model, diseaseSevere--> all (equivalent change score prediction)
-
-nb_arcs2 <- data.frame(
-  from = c(
-    rep("diseaseSevere", 12),
-    rep("overpar", 12)
-  ),
-  to = rep(vars2$scale, 2)
-)
-
-nb_model2 <- write_jags_model(nb_arcs2, d_bn) %>% suppressWarnings()
-
-# can modify this to test assumptions about direct effects of intervention ...
-interv_fit <- glm(interv ~ diseaseSevere + overpar, 
-                  data = interv_df,
-                  family = "binomial"
-                  )
-
-nb_model2 <- add_node(nb_model2, glm_to_jags_eq(interv_fit))
-
-# can also just use "model" here so long as you include held_out_nodes
-
-preds_nb2 <- predict_change_scores(nb_model2,
-                                           data.frame(interv = 0),
-                                           data.frame(interv = 1),
-                                           nodes_to_predict,
-                                           iter = 1e5*2.5
-                                           )
-
-preds_nb2 <- process_predictions(preds_nb2, obs_data)
-
-plots_nb2 <- plot_processed_predictions(preds_nb2)
-
-plots_nb2$corr_plot
-plots_nb2$means_plot
-
-score_predictions(preds_nb2)
-
-```
-
-This model is the best of all!, getting a whopping `r score_predictions(preds_nb2)$r^2 %>% round(3) * 100`% of the variance! Not only that, RMSE and MAE also look somewhat lower than the other models.
-
-So, from a purely predictive standpoint, if the cognitive model assumption holds, then the naïve model might actually be the best approach to predicting belief changes.
-However I don't think there are any guarantees that this sort of thing will always work when thinking about multiple targetted beliefs, for one.
-Quickly comparing all four models, it really does look like the naïve model with both disease severity and overparenting targetted does best, for what it's worth.
-
-```{r}
-boot_scores_cog <- score_predictions_boot(preds_cog)
-boot_scores_cog2 <- score_predictions_boot(preds_cog2)
-boot_scores_nb <- score_predictions_boot(preds_nb)
-boot_scores_nb2 <- score_predictions_boot(preds_nb2)
-
-tibble(
-  cog = sapply(boot_scores_cog, function(x){x$rmse}), 
-  cog2 = sapply(boot_scores_cog2, function(x){x$rmse}),
-  nb = sapply(boot_scores_nb, function(x){x$rmse}),
-  nb2 = sapply(boot_scores_nb2, function(x){x$rmse}),
-       ) %>%
-  gather(model, rmse, cog, cog2, nb, nb2) %>%
-  ggplot(aes(x=model, y = rmse)) +
-  geom_boxplot() +
-  theme_bw()
-```

### 2018-09-20 study2/study2-evid-ratio.Rmd
updated study2 modeling

--- 2018-09-18 study2/study2-evid-ratio.Rmd
@@
 The resulting evidence ratio is `r evid_ratio`. Reasonable CPT values would be .5 and `r .5*evid_ratio` That's not that huge really ...
+
+# maximum likelihood estimate with optim()
+
+WE can do this with optim too, which will work better when we go to do it 14 times.
+
+```{r}
+inv_logit <- plogis
+logit <- qlogis
+
+evid_score_func <- function(data, par) {
+
+  inv_logit <- plogis
+  logit <- qlogis
+
+  pred_y <- with(data,
+                 {
+                   inv_logit(logit(pre) + evid*par[2] + par[1])
+                 }
+       )
+  pred_beta_A <- pred_y * par[3]
+  pred_beta_B <- (1-pred_y) * par[3]
+
+  ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
+  return(ll)
+}
+
+get_evid_probs <- function(result){
+  # this is a heuristic/hack, could be made better but probably doesn't matter
+  evid_ratio <- exp(result$par[1] + result$par[2])
+  if (evid_ratio < 1) {
+    p0 <- .90
+  } else {
+    p0 <- .50
+  }
+
+  if (p0*evid_ratio > 1) {
+    p0 <- p0*.9/(p0*evid_ratio)
+  }
+
+  p1 <- p0*evid_ratio
+
+  c(p0,p1)
+}
+
+evid_probs_to_cpt <- function(probs, var_name){
+  p0 <- probs[1]
+  p1 <- probs[2]
+
+  full_list <- paste0("list(",var_name,"=c('Yes','No'), evid = c('Yes', 'No'))")
+  make_custom_cpt(c(p1, p0, (1-p1), (1-p0)), c(2,2), eval(parse(text=full_list)), NULL)
+}
+
+find_evid_ratio <- function(data){
+  optim(par = c(0, 0, 5), fn = evid_score_func, data = data, method="BFGS")
+}
+
+make_evid_cpt <- function(data, var_name){
+  result <- find_evid_ratio(data)
+  probs <- get_evid_probs(result)
+  cpt <- evid_probs_to_cpt(probs, var_name)
+
+  return(cpt)
+}
+
+evid_cpt <- make_evid_cpt(d, "diseaseSevere")
+
+```

### 2018-09-20 study2/cog-model-discrete-predictions.Rmd
minor readme update

@@
 print(Sys.time() - t1)
+
+saveRDS(object = boot_fits, file = "boot_fits.rds")
 ```
@@
 ```
+
+# two beliefs at the same time
+
+```{r}
+res_overpar <- find_evid_ratio(filter_dscored(d_scored, "overpar"))
+res_ds <- find_evid_ratio(filter_dscored(d_scored, "diseaseSevere"))
+
+overpar_ratio <- exp(res_overpar$par[1] + res_overpar$par[2])
+ds_ratio <- exp(res_ds$par[1] + res_ds$par[2])
+
+p0p0 <- .3
+p1p0 <- p0p0*ds_ratio
+p0p1 <- p0p0*overpar_ratio
+p1p1 <- p0p0*overpar_ratio*ds_ratio
+
+overpar_ds_evid_cpt <- make_custom_cpt(
+  # c(p1p0, p0p0, (1-p1p0), (1-p0p0), p1p1, p0p1, (1-p1p1), (1-p0p1)),   
+  c(p1p1, (1-p1p1), p1p0, (1-p1p0), p0p1, (1-p0p1), p0p0, (1-p0p0) ),
+                c(2,2,2),
+                list(evid=c("Yes","No"), overpar = c("Yes","No"), diseaseSevere = c("Yes","No")), 
+                NULL)
+
+```
+
+```{r}
+add_evid_node_custom <- function(bnlearn_model, parents_string, evid_cpt) {
+
+  # evid_cpt <- make_evid_cpt(data, targetted_belief)
+  model_list <- lapply(bnlearn_model, function(x){x$prob})
+  # model_list$evid <- hyde_to_bn_cpt(evid_cpt)
+  model_list$evid <- evid_cpt
+
+  model_string <- modelstring(bnlearn_model)
+  model_string <- paste0(model_string,"[evid|", parents_string, "]")
+  model_network <- model2network(model_string)
+  predModel <- custom.fit(model_network, dist = model_list)
+
+  return(predModel)
+
+}
+
+ds_overpar_model <- add_evid_node_custom(base_model, "overpar:diseaseSevere", overpar_ds_evid_cpt)
+
+# ----------------------------------------
+
+set.seed(12345)
+
+pred0_ds_overpar <- sapply(nodes, function(x){
+  statement <- paste0("cpquery(ds_overpar_model, event = (", x, " == 'Yes'), evidence=TRUE, n = 5e5)")
+  eval(parse(text=statement))
+})
+
+pred1_ds_overpar <- sapply(nodes, function(x){
+  statement <- paste0("cpquery(ds_overpar_model, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 5e5)")
+  eval(parse(text=statement))
+})
+
+pred_changes2 <- pred1_ds_overpar - pred0_ds_overpar
+
+pred_changes2 <- as.data.frame(pred_changes2)
+
+pred_changes2 <- pred_changes2 %>%
+  mutate(scale = nodes) %>%
+  rename(Mean = pred_changes2) %>%
+  mutate(type = "predicted")
+
+# ----------------------------------------
+
+obs_pred2 <- bind_rows(pred_changes2, obs_changes) %>%
+  spread(type, Mean) %>%
+  group_by(scale) %>%
+  summarize_all(mean, na.rm=TRUE)
+
+cor(obs_pred2$predicted, obs_pred2$observed)
+
+obs_pred2 %>% # a bit of a hack
+  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
+  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+  geom_point() +
+  geom_errorbar() +
+  coord_cartesian(xlim=c(-.06,.08), ylim=c(-.06,.08)) +
+  theme_bw() +
+  theme(aspect.ratio = 1)
+
+obs_pred2 %>%
+  gather(type, Mean, observed, predicted) %>%
+  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
+  geom_point() +
+  geom_errorbarh(height=0)
+```
+
+```{r}
+# obs,pred correlation excluding nodes fit
+obs_pred_excl <- bind_rows(pred_changes, obs_changes) %>%
+  spread(type, Mean) %>%
+  filter(scale!="diseaseSevere", scale!="overpar") %>%
+  group_by(scale) %>%
+  summarize_all(mean, na.rm=TRUE)
+
+cor(obs_pred_excl$predicted, obs_pred_excl$observed)
+sqrt(mean((obs_pred_excl$observed-obs_pred_excl$predicted)^2))
+```
+
+```{r}
+# obs,pred correlation excluding nodes fit
+obs_pred_excl2 <- bind_rows(pred_changes2, obs_changes) %>%
+  spread(type, Mean) %>%
+  filter(scale!="diseaseSevere",scale!="overpar") %>%
+  group_by(scale) %>%
+  summarize_all(mean, na.rm=TRUE)
+
+cor(obs_pred_excl2$predicted, obs_pred_excl2$observed)
+sqrt(mean((obs_pred_excl2$observed-obs_pred_excl2$predicted)^2))
+```
+
+Adding edge from overparenting hurts prediction for the 12 nodes other than disease severity and overparenting, goes from r = .90 to r = .818.
+RMSE just about doubled.
+To be sure I'd have to do the bootstrap on these estimates, but I think this is a signal that the fit is worse modeling it as a direct effect.
+If so that indicates to me that something is wrong in the model wrt overparenting beliefs.

### 2018-10-22 study1/custom-structure-learning-vaccData.Rmd
updates ahead of talk

@@
 # source("cog-model-graph-tools.R")
-source("../scripts/custom-structure-learning/cog-model-main.R")
+source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)
 source("../scripts/gmod_tools.R")
@@
 compute_scoretables <- FALSE # uncomment to recompute scoretables
-source("fit-cog-models.R")
+source("../scripts/custom-structure-learning/fit-cog-models.R", chdir=TRUE)
 
@@
 
-all_results <- readRDS("allresults.rds")
+all_results <- readRDS("../local/allresults.rds")
 ```
@@
 
-BiDAG_traceplot(all_results[[1]], hide = 1, show_chains=c(1,2,3,4))
+BiDAG_traceplot(all_results[[5]], hide = 1, show_chains=c(1,2,3,4))
 # BiDAG_traceplot(all_results[[3]], hide = 100, show_chains=c(3,4))
@@
 ```{r}
-merged_chains <- merge_chains(all_results[[1]][2:4])
+merged_chains <- merge_chains(all_results[[5]][1:4])
 map_dag <- extract_mapdag(merged_chains)
@@
   # geom_smooth(method="lm") +
+  coord_fixed() + 
+  facet_wrap(~varName, nrow=2) + 
+  scale_x_continuous("Predicted values", limits = c(0, 1)) +
+  scale_y_continuous("Observed values", limits = c(0, 1)) +
   theme_bw(base_size = 10) +
@@
         panel.grid.minor = element_blank()) +
-  coord_fixed() + 
-  facet_wrap(~varName, nrow=2) + 
-  scale_x_continuous("Predicted values", limits = c(0, 1)) +
-  scale_y_continuous("Observed values", limits = c(0, 1))
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
 

### 2018-10-22 study2/vacc_manyBelief_study2_overpar.Rmd
refactored, working
updates ahead of talk

@@
 # load data
-d_all <- read.csv("data/study3_data.csv")[-1]
+d_all <- read.csv("../data/study2_data.csv")[-1]
 
@@
 We've come up with many (post-hoc) reasons why this might be important, and our data suggest that it was.
+
+# Bayesian regularized regression
+
+This is interesting and a great setup, but I'm having a bit of trouble interpreting 3-4 way interactions ...
+
+```{r}
+library(brms)
+
+rescale_beta <- function(x, lower, upper) {
+  # rescales onto the open interval (0,1)
+  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
+
+  N <- length(x)
+  res <- (x - lower) / (upper - lower)
+  res <- (res * (N - 1) + .5) / N
+
+  return(as.vector(res))
+}
+
+fit <- brm(
+  vaccIntent ~ phase * condition * overpar * medSkept * diseaseSevere + (1|workerId),
+  prior = set_prior("normal(0,.5)", class = "b"),
+  family = Beta(),
+  data = d_scored_wide %>% 
+    mutate(vaccIntent = rescale_beta(vaccIntent, 
+                                     min(d_scored_wide$vaccIntent), 
+                                     max(d_scored_wide$vaccIntent)
+                                     )),
+  control = list(adapt_delta = .90, max_treedepth = 15),
+  chains = 2,
+  cores = 2
+)
+```
+
+```{r}
+summary(fit)
+```
+
+I don't think any of these interaction terms are coming out "significant." Certainly all the phasepost:conditionDR involved ones are not. Closest looks like phasepost:conditionDR:overpar:medskept.
+
+```{r}
+fit_pre <- brm(
+  vaccIntent ~ overpar * medSkept * diseaseSevere + (1|workerId),
+  prior = set_prior("normal(0,.5)", class = "b"),
+  family = Beta(),
+  data = d_bn %>% 
+    mutate(vaccIntent = rescale_beta(vaccIntent, -3, 3), workerId = 1:nrow(d_bn)),
+  control = list(adapt_delta = .90, max_treedepth = 15),
+  chains = 2,
+  cores = 2
+)
+```
+
+```{r}
+summary(fit_pre)
+```

### 2018-10-22 scripts/custom-structure-learning/fit-cog-models.R

@@ -1,7 +1,7 @@
 
 # load data
 # -----------------------------------------
-source("../../study1/vacc_import_data.R")
+# source("../../study1/vacc_import_data.R", chd)
 
 
 # load packages
@@ -15,9 +15,9 @@ library(HydeNet)
 library(gtools)
 
 # source("cog-model-graph-tools.R")
-source("cog-model-main.R")
-source("../../Scripts/gmod_tools.R")
-source("../../Scripts/bnTheoryBlacklist.R")
+# source("cog-model-main.R")
+# source("../../Scripts/gmod_tools.R")
+# source("../../Scripts/bnTheoryBlacklist.R")
 
 
 # transform data

### 2018-11-29 study1/custom-structure-learning-vaccData.Rmd
before yale visit

@@
 source("../scripts/bnTheoryBlacklist.R")
+source("../scripts/custom-structure-learning/cog-model-jags-tools.R")
 
@@
 ```{r}
-# takes about 20-30 min
-start_time <- Sys.time()
+# #  takes about 20-30 min to run
 
-# test2 <- test
-predictions <- test %>% mutate_all(function(x){NA}) %>% mutate_all(as.numeric)
-# net.fit <- bn.fit(map_dag, train)
+# start_time <- Sys.time()
+# 
+# # test2 <- test
+# predictions <- test %>% mutate_all(function(x){NA}) %>% mutate_all(as.numeric)
+# # net.fit <- bn.fit(map_dag, train)
+# 
+# for (targVar in names(test)) {
+#   tempDF <- test
+#   tempDF[[targVar]] <- NA
+#   tempDF[[targVar]] <- as.numeric(tempDF[[targVar]])
+#   
+#   # imputed <- impute(net.fit, tempDF, method="bayes-lw")
+#   imputed <- make_predictions(model_string, test, nodes_to_predict = targVar)
+#   predictions[[targVar]] <- imputed[[targVar]]
+# }
+# 
+# predictions <- predictions %>% gather(varName, predValue)
+# test_analyze <- test %>% gather(varName, value) %>% bind_cols(predictions) %>% select(varName, value, predValue)
+# 
+# print(Sys.time() - start_time)
 
-for (targVar in names(test)) {
-  tempDF <- test
-  tempDF[[targVar]] <- NA
-  tempDF[[targVar]] <- as.numeric(tempDF[[targVar]])
+# saveRDS(object = test_analyze, file = "../local/s1_model_predictions.rds")
 
-  # imputed <- impute(net.fit, tempDF, method="bayes-lw")
-  imputed <- make_predictions(model_string, test, nodes_to_predict = targVar)
-  predictions[[targVar]] <- imputed[[targVar]]
-}
+test_analyze <- readRDS("../local/s1_model_predictions.rds")
+```
 
-predictions <- predictions %>% gather(varName, predValue)
-test_analyze <- test %>% gather(varName, value) %>% bind_cols(predictions) %>% select(varName, value, predValue)
+# job talk plots
 
-print(Sys.time() - start_time)
-```
+November 16, 2018
+
+## predicted vs observed across scales
 
@@
 
+recode_nodes <- function(x){
+  recode(x,
+         "diseaseRare" = "Disease Rarity",
+         "diseaseSevere" = "Disease Severity",
+         "hb" = "Holistic Balance",
+         "infantImmLimCap" = "IIS: Limited\nCapacity",
+         "infantImmWeak" = "IIS: Weakness",
+         "medSkept" = "Medical\nSkepticism",
+         "nat" = "Naturalism",
+         "overpar" = "Parental\nProtectiveness",
+         "parentExpert" = "Parental\nExpertise",
+         "vaccDanger" = "Vaccine\nDanger",
+         "vaccEff" = "Vaccine\nEffectiveness",
+         "vaccIntent" = "Vaccination\nIntentions",
+         "vaccStrain" = "IIS: Vaccines\nStrain",
+         "vaccTox" = "Vaccines\nToxicity")}
+
 predObsCor <- cor(test_analyze$value,test_analyze$predValue)
@@
 corrDF <- test_analyze %>%
+  # mutate(varName = recode_nodes(varName)) %>%
   group_by(varName) %>%
@@
 plt.valid <- test_analyze %>%
+  mutate(varName = recode_nodes(varName)) %>%
   ggplot(aes(x=predValue, y=value)) + 
@@
 
-plt.valid
+ggsave(plot = plt.valid, filename = "../local/s1_predobs_plot.png", width=8.5, height=4)
 ```
+
+## network structure (beautified)
+
+```{r}
+# do network structure plotting here ...
+library(DiagrammeR)
+
+custom_plot.HydeNetwork <- function(x, 
+                             customNodes = NULL,
+                             customEdges = NULL,
+                             ..., 
+                             removeDeterm = FALSE,
+                             useHydeDefaults = TRUE)
+{
+  if (removeDeterm) x <- plot_nondeterm_only(x)
+
+  node_df <- 
+    DiagrammeR::create_node_df(n = length(x[["nodes"]]),
+                               label = x[["nodes"]])
+  # 
+  # node_df <- data.frame(nodes = x[["nodes"]],
+  #                       stringsAsFactors = FALSE)
+  if (useHydeDefaults) node_df <- HydeNet:::mergeDefaultPlotOpts(x, node_df)
+
+  if (!is.null(customNodes)) node_df <- HydeNet::mergeCustomNodes(node_df, customNodes)
+
+  edge_table <- do.call("rbind", 
+                        mapply(FUN = HydeNet:::mapEdges, 
+                               x[["nodes"]], 
+                               x[["parents"]],
+                               MoreArgs = list(node_df = node_df)))
+
+  edge_df <- DiagrammeR::create_edge_df(from = edge_table[, 2], 
+                                        to = edge_table[, 1])
+
+  if (!is.null(customEdges)) HydeNet::mergeCustomEdges(edge_df, customEdges)
+
+  DiagrammeR::create_graph(nodes_df = node_df,
+                           edges_df = edge_df,
+                           attr_theme = NULL)
+
+}
+
+## ----------------------------------------
+
+# code to demo. For some reason set_edge_attrs() isn't working right, so have to do it manually
+
+map_to_viridis <- function(vec, bins=64, option="D"){
+
+  binned <- cut(vec, bins)
+  levels(binned) <- viridis::viridis(bins, option=option)
+
+  return(as.character(binned))
+}
+
+map_to_brewer <- function(vec, bins=11, option="RdYlBu"){
+  binned <- cut(vec, bins)
+  levels(binned) <- RColorBrewer::brewer.pal(bins, name=option)
+
+  return(as.character(binned))
+}
+
+```
+
+```{r}
+z <- custom_plot.HydeNetwork(h)
+
+c <- find_dag_coefs(map_dag, train)
+
+coefs <- tidy_coefs(c)
+
+coefs %>%
+  filter(parameter!="phi",parameter!="w_leak") %>%
+  rename(from = parameter) %>%
+  mutate(from = gsub("w_","",from)) %>%
+  select(to, from, value) %>%
+  merge(z$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
+  mutate(from = id) %>%
+  select(-id) %>%
+  merge(z$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
+  mutate(to = id) %>%
+  arrange(to,from) -> edge_df_mod
+  # select(value, id.x, id.y) %>%
+  # mutate(from = id.x, to = id.y)
+
+# z$nodes_df
+z$nodes_df <- z$nodes_df %>% mutate(label = recode_nodes(label))
+z$nodes_df$fontname <- "Helvetica"
+z$nodes_df$shape <- "ellipse"
+z$nodes_df$fillcolor <- ifelse(z$nodes_df$id==13, "grey","white")
+z$nodes_df$fixedsize <- FALSE
+z$edges_df$penwidth <- abs(edge_df_mod$value)*2
+z$edges_df$penwidth <- 1.5
+# z$edges_df$label <- round(edge_df_mod$value,2)
+# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
+z$edges_df$color <- map_to_brewer(edge_df_mod$value)
+render_graph(z)
+
+```
+
+# save relevant outputs!
+
+```{r}
+# save model as bn
+saveRDS(map_dag, "../local/map_dag_bn_theorybased.rds")
+# and as hydnet
+saveRDS(h, "../local/map_dag_hydenet_theorybased.rds")
+# save model string
+saveRDS(model_string, "../local/map_dag_modelstring_theorybased.rds")
+
+```

### 2018-11-29 study2/study2_modeling.Rmd
before yale visit

---
title: "int-theory-vacc: Study 2 modeling"
output: 
  html_notebook: 
    code_folding: hide
    # toc: true
    # toc_float: true
---

```{r load in existing objects, message=FALSE, warning=FALSE}
# net.struct <- readRDS("net-struct-cogsci2018.rds")

source("../study1/vacc_import_data.R", chdir = TRUE)
source("../scripts/gmod_tools.R")
# source("../../Scripts/virtualEvidence.R")

library(bnlearn)
library(rjags)
library(patchwork)
library(BiDAG)
library(HydeNet)
library(bnlearn)

library(rsample)

source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)
```

```{r set up training split}
# rescale beta

rescale_beta <- function(x, lower, upper) {
  # rescales onto the open interval (0,1)
  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"

  N <- length(x)
  res <- (x - lower) / (upper - lower)
  res <- (res * (N - 1) + .5) / N

  return(as.vector(res))
}

d_bn_scaled <- d_bn %>%
 mutate_all(function(x){rescale_beta(x,-3,3)})

## set the seed to make your partition reproductible
set.seed(123)
trainInd <- sample(seq_len(nrow(d_bn_scaled)), size = floor(nrow(d_bn_scaled)*.80))

train <- d_bn_scaled[trainInd, ]
test <- d_bn_scaled[-trainInd, ]
```

# loading in data model

```{r}
# first load in mcmc results
all_results <- readRDS("../local/allresults.rds")
nodes <- colnames(train)
# then grab map dag for theory-based constraints
merged_chains <- merge_chains(all_results[[5]])
map_dag <- extract_mapdag(merged_chains)

h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(map_dag)))
plot(h)
```

## Translate into cognitive model

```{r}
# parse bn into list of parents and children

arcs_df <- bnlearn_to_df(map_dag)

df_to_list <- function(arcs_df, as.strings=FALSE) {
  # take arcs_df and make list of formulas
  arcs_df$to <- as.character(arcs_df$to)
  arcs_df$from <- as.character(arcs_df$from)

  nodes <- unique(unlist(arcs_df))
  output <- lapply(nodes, function(node) {
    edges <- arcs_df[which(arcs_df$to == node), "from"]
    if (length(edges) < 1) {
      edges <- NULL
    }
    list(child=node, parents=edges)

  })
  names(output) <- nodes
  return(output)
}

graph_list <- df_to_list(arcs_df)

bagOfModels <- lapply(graph_list, function(x){fit_node_cpt(x, train)})

# bagNet <- HydeNetwork(bagOfModels)
# writeNetworkModel(bagNet, pretty=TRUE)

```

Compute and add evidence cpt

```{r}
inv_logit <- plogis
logit <- qlogis

evid_score_func <- function(data, par) {

  inv_logit <- plogis
  logit <- qlogis

  pred_y <- with(data,
                 {
                   inv_logit(logit(pre) + evid*par[2] + par[1])
                 }
       )
  pred_beta_A <- pred_y * par[3]
  pred_beta_B <- (1-pred_y) * par[3]

  ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
  return(ll)
}

get_evid_probs <- function(result){
  # this is a heuristic/hack, could be made better but probably doesn't matter
  evid_ratio <- exp(result$par[1] + result$par[2])
  if (evid_ratio < 1) {
    p0 <- .90
  } else {
    p0 <- .50
  }

  if (p0*evid_ratio >= 1) {
    p0 <- p0*.9/(p0*evid_ratio)
  }

  p1 <- p0*evid_ratio

  c(p0,p1)
}

evid_probs_to_cpt <- function(probs, var_name, evid_name = "evid"){
  p0 <- probs[1]
  p1 <- probs[2]

  full_list <- paste0("list(",var_name,"=c('Yes','No'),", evid_name, " = c('Yes', 'No'))")
  make_custom_cpt(c(p1, p0, (1-p1), (1-p0)), c(2,2), eval(parse(text=full_list)), NULL)
}

find_evid_ratio <- function(data){
  optim(par = c(0, 0, 5), fn = evid_score_func, data = data, method="BFGS")
}

make_evid_cpt <- function(data, var_name, evid_name = "evid"){
  result <- find_evid_ratio(data)
  probs <- get_evid_probs(result)
  cpt <- evid_probs_to_cpt(probs, var_name, evid_name)

  return(cpt)
}

make_evid_cpt_custom <- function(var_name, evid_ratio, evid_name = "evid"){
  # result <- find_evid_ratio(data)
  result <<- list(par = c(0, log(evid_ratio)) )
  probs <- get_evid_probs(result)
  cpt <- evid_probs_to_cpt(probs, var_name, evid_name)

  return(cpt)
}

```

Generate predictions ...

__Translating hydenet model to bnlearn__

below is some code to get things into the right format. Later I'll break this out into a function I guess.

```{r}
hyde_to_bn_cpt <- function(hyde_cpt) {
  ndims <- length(dim(hyde_cpt))

  if ("xtabs" %in% class(hyde_cpt)) {
    output <- hyde_cpt/1e5
  } else {

    output <- aperm(hyde_cpt, ndims:1)
  }
 return (output) 
}

# # This is old?

# # hyde_to_bn_cpt(bagOfModels$evid)
# bagOfModels[[15]] <- make_evid_cpt(d,"diseaseSevere") # don't have data loaded in yet?
# 
# bnlearn_models <- lapply(bagOfModels, hyde_to_bn_cpt)
# model_string <- as.character(map_dag)
# model_string <- paste0(model_string,"[evid|diseaseSevere]")
# model_network <- model2network(model_string)
# 
# predModel <- custom.fit(model_network, dist = bnlearn_models)

```

__Generating predictions__

Now I can use this model to generate predictions.

## Predicting effect on vaccintent of hypothetical interventions

```{r}

# this is some code to genrate predictions of vacc intent change based on
# hypothetical interventions

create_bnlearn_cog_model <- function(dag, data, evid_cpt = NULL, targetted_belief = NULL) {
  arcs_df <- bnlearn_to_df(dag)
  graph_list <- df_to_list(arcs_df)
  bagOfModels <- lapply(graph_list, function(x){fit_node_cpt(x, data)})
  model_string <- as.character(dag)

  if (!(is.null(evid_cpt))) {
    bagOfModels$evid <- evid_cpt
    model_string <- paste0(model_string,"[evid|", targetted_belief, "]")
  }
  model_network <- model2network(model_string)
  bnlearn_models <- lapply(bagOfModels, hyde_to_bn_cpt)
  predModel <- custom.fit(model_network, dist = bnlearn_models)

  return(predModel)
}

add_evid_node <- function(data, bnlearn_model, targetted_belief, evid_id = NULL) {

  if (!is.null(evid_id)) {
    evid <- paste0("evid",evid_id)
  } else {
    evid <- "evid"
  }

  evid_cpt <- make_evid_cpt(data, targetted_belief, evid)
  model_list <- lapply(bnlearn_model, function(x){x$prob})
  model_list[[evid]] <- hyde_to_bn_cpt(evid_cpt)

  model_string <- modelstring(bnlearn_model)
  model_string <- paste0(model_string,"[", evid,"|", targetted_belief, "]")

  model_network <- model2network(model_string)
  predModel <- custom.fit(model_network, dist = model_list)

  return(predModel)
}

add_evid_node_custom <- function(bnlearn_model, parents_string, evid_cpt) {

  model_list <- lapply(bnlearn_model, function(x){x$prob})
  model_list$evid <- evid_cpt

  model_string <- modelstring(bnlearn_model)
  model_string <- paste0(model_string,"[evid|", parents_string, "]")
  model_network <- model2network(model_string)
  predModel <- custom.fit(model_network, dist = model_list)

  return(predModel)
}

cogModel_predictions <- function(model){
  pred0 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(model, event = (", x, " == 'Yes'), evidence=TRUE, n = 1e5)")
  eval(parse(text=statement))
  })

  pred1 <- sapply(nodes, function(x){
    statement <- paste0("cpquery(model, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 1e5)")
    eval(parse(text=statement))
  })

  pred_changes <- pred1 - pred0

  pred_changes <- as.data.frame(pred_changes)

  pred_changes <- pred_changes %>%
    mutate(scale = nodes) %>%
    rename(Mean = pred_changes) %>%
    mutate(type = "predicted")

  return(pred_changes)
}

base_model <- create_bnlearn_cog_model(map_dag, train)

source("../study2/load-study2-data.R", chdir = TRUE)

vaccIntent_pred_results <- data.frame(scale=nodes, value = NA)

for (i in 1:length(nodes)) {
  if (cor(d_bn[,"vaccIntent"], d_bn[,nodes[i]]) >= 0) {
    evid_ratio <- 2
  } else {
    evid_ratio <- .5
  }
  evid_cpt <- hyde_to_bn_cpt(make_evid_cpt_custom(nodes[i], evid_ratio))
  vaccIntent_predNet <- add_evid_node_custom(base_model, nodes[i], evid_cpt)

  preds <- cogModel_predictions(vaccIntent_predNet) %>%
    filter(scale=="vaccIntent")

  vaccIntent_pred_results[i,"value"] <- preds[1,"Mean"]

}

## combine this with observed correlations from study 1

corrmat <- cor(d_bn)

interv_sim <- corrmat["vaccIntent",] %>%
  tibble(scale = names(.), value = ., type="correlation") %>%
  bind_rows(vaccIntent_pred_results %>% mutate(type="model_pred")) %>%
  spread(type,value)

interv_sim %>%
  ggplot(aes(x=abs(correlation), y = model_pred)) +
  geom_point()

(pred_change_plot <- interv_sim %>% 
  filter(scale!="vaccIntent") %>%
  ggplot(aes(x=reorder(scale, model_pred), y = model_pred)) + 
  geom_bar(stat="identity") + 
  coord_flip() +
  labs(x="Targeted belief", y = "Predicted change in intentions") +
  theme_bw(base_size=22) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1.5))

ggsave("../local/predicted_changes.png", pred_change_plot)
```

The correlation between model predicted change and first-order correlation with vaccIntent is essentially 1. This is to be expected, the model is based on the correlation structure of these data. So, if you're just looking to figure out what to intervene on, first-order correlations can give you a good starting place.

## predicting effect of disease risk intervention on network

```{r}
set.seed(12345)

filter_dscored <- function(data, scale_name){

  data %>%
  filter(scale == scale_name) %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase, mean) %>% 
  mutate(condition = relevel(condition, ref="noInterv")) %>%
  mutate(evid = ifelse(condition=="noInterv",0,1))
}

# d <- d_scored %>%
#   filter(scale == "diseaseSevere") %>%
#   mutate(mean = rescale_beta(mean, -3, 3)) %>%
#   spread(phase, mean) %>% 
#   mutate(condition = relevel(condition, ref="noInterv")) %>%
#   mutate(evid = ifelse(condition=="noInterv",0,1))

predModel <- add_evid_node(filter_dscored(d_scored, "diseaseSevere"), base_model, "diseaseSevere")

pred0 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence=TRUE, n = 5e5)")
  eval(parse(text=statement))
})

pred1 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 5e5)")
  eval(parse(text=statement))
})

pred_changes <- pred1 - pred0

pred_changes <- as.data.frame(pred_changes)

pred_changes <- pred_changes %>%
  mutate(scale = nodes) %>%
  rename(Mean = pred_changes) %>%
  mutate(type = "predicted")

```

Compare predicted and observed changes ...

```{r}

obs_changes <- d_scored %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase,mean) %>%
  mutate(changeScore = post-pre) %>%
  filter(condition == "diseaseRisk") %>%
  group_by(scale) %>%
  summarise(
    Mean = mean(changeScore),
    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()), # replace with bootstrapping
    ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
    ) %>%
  mutate(type = "observed")

obs_pred <- bind_rows(pred_changes, obs_changes) %>%
  spread(type, Mean) %>%
  group_by(scale) %>%
  summarize_all(mean, na.rm=TRUE)

cor(obs_pred$predicted, obs_pred$observed)

(obs_pred_plot <- obs_pred %>% # a bit of a hack
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point(size=2.5) +
  geom_errorbar(alpha=.5, width=0) +
  coord_cartesian(xlim=c(-.06,.08), ylim=c(-.06,.08)) +
  theme_bw(base_size=22) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1))

obs_pred %>%
  gather(type, Mean, observed, predicted) %>%
  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
  geom_point() +
  geom_errorbarh(height=0)

ggsave("../local/obs_pred_plot.png",obs_pred_plot)
```

# What beliefs are targetted by the intervention?

Here we can pretend that expectations for the intervention materials are set by each of the 14 beliefs, and compare the accuracy of the resulting models' predictions. We should also ask whether the differences among models are substantial and reliable enough for us to prefer any one model over another.

```{r}

compare_pred_obs_r <- function(predicted, observed){

  obs_pred <- suppressWarnings(bind_rows(predicted, observed)) %>%
    spread(type, Mean) %>%
    group_by(scale) %>%
    summarize_all(mean, na.rm=TRUE)

  cor(obs_pred$predicted, obs_pred$observed)
}

compare_pred_obs_rmse <- function(predicted, observed){

  obs_pred <- suppressWarnings(bind_rows(predicted, observed)) %>%
    spread(type, Mean) %>%
    group_by(scale) %>%
    summarize_all(mean, na.rm=TRUE)

  sqrt(mean((obs_pred$observed-obs_pred$predicted)^2))

}

extract_obs_changes <- function(observed){
  obs_changes <- observed %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase,mean) %>%
  mutate(changeScore = post-pre) %>%
  filter(condition == "diseaseRisk") %>%
  group_by(scale) %>%
  summarise(
    Mean = mean(changeScore),
    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()), # replace with bootstrapping
    ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
    ) %>%
  mutate(type = "observed")
}

```

```{r}
# -- takes about 1.5 hrs for 500 bootstrap samples
# base_model <- create_bnlearn_cog_model(map_dag, train)
# 
# # do bootstrap comparison
# set.seed(1234)
# t1 <- Sys.time()
# 
# boot_fits <- as_tibble(expand.grid(
#   list(
#     replicate = 1:500, scale = nodes
#   )
# )) %>%
#   nest(-replicate, .key="scales") %>%
#   mutate(boot_d_scored = map(replicate, function(x) {
#     totaln <- length(unique(d_scored$workerId))
#     d_scored %>%
#       nest(-workerId) %>%
#       sample_n(totaln, replace = TRUE) %>%
#       mutate(uniqueId = 1:totaln) %>%
#       unnest()
#   })) %>%
#   unnest(scales, .drop=FALSE) %>%
#   mutate(
#       boot_d = map2(boot_d_scored, scale, function(x,y){filter_dscored(x, y)}),
#       obs_changes = map(boot_d_scored, extract_obs_changes)
#       ) %>%
#   select(-boot_d_scored) %>%
#   mutate(
#     models = map2(boot_d, scale, function(x,y){add_evid_node(x, base_model, y)}),
#     pred_changes = map(models, cogModel_predictions),
#     r = map2_dbl(pred_changes, obs_changes, compare_pred_obs_r),
#     rmse = map2_dbl(pred_changes, obs_changes, compare_pred_obs_rmse)
#     )
# 
# print(Sys.time() - t1)
# 
# saveRDS(object = boot_fits, file = "../local/boot_fits.rds")

boot_fits <- readRDS("../local/boot_fits.rds")
```

```{r}
boot_fits %>%
  mutate(r2 = r^2) %>%
  ggplot(aes(x=reorder(scale,-r2), y = r2)) +
  geom_boxplot(fill="lightgray") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  coord_flip()
  # theme(axis.text.x = element_text(angle = 90, hjust = 1))

diagnose_plot <- boot_fits %>%
  select(replicate, scale,r,rmse) %>%
  mutate(scale_order = r) %>%
  gather(meas, value, r, rmse) %>%
  mutate(meas = ifelse(meas=="rmse", "RMSE (lower is better)", "Correlation")) %>%
  mutate(meas = factor(meas, levels=c("RMSE (lower is better)", "Correlation"))) %>%
  ggplot(aes(x=reorder(scale, scale_order), y = value)) +
  # geom_violin(fill="gray", alpha=.5) +
  geom_boxplot(fill = "lightgray") +
  facet_wrap(~meas, scales="free_x" ) +
  labs(x = "Belief", y = "Value") +
  theme_bw(base_size=14) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  coord_flip()

ggsave("../local/diagnose_plot.png", diagnose_plot, width = 7.5, height=5)
```

```{r}
boot_fits %>% 
  filter(scale=="diseaseSevere") %>%
  summarize(
    estimate = mean(r),
    ul = quantile(r,.975),
    ll = quantile(r, .025)
    )
```

# two beliefs at the same time

```{r}
# res_overpar <- find_evid_ratio(filter_dscored(d_scored, "overpar"))
# res_ds <- find_evid_ratio(filter_dscored(d_scored, "diseaseSevere"))
# 
# overpar_ratio <- exp(res_overpar$par[1] + res_overpar$par[2])
# ds_ratio <- exp(res_ds$par[1] + res_ds$par[2])
# # 
# # p0p0 <- .08
# # p1p0 <- p0p0*ds_ratio
# # p0p1 <- p0p0*overpar_ratio
# # # p1p1 <- p0p0*overpar_ratio*ds_ratio
# # 
# # # p1p1 is noisy-or integration of p1p0 and p0p1
# # # so have to back-out failure prob of overpar and disease severe, then integrate
# # # p1p1 <- 1-(1-p0p0)*(1-(p1p0-p0p0)/(1-p0p0))*(1-(p0p1-p0p0)/(1-p0p0))
# # 
# # p_ds <- (p1p0-p0p0)/(1-p0p0)
# # p_overpar <- (p0p1-p0p0)/(1-p0p0)
# # p1p1 <- 1-(1-p0p0)*(1-p_ds)*(1-p_overpar)
# 
# overpar_ds_evid_cpt <- make_custom_cpt(
#   # c(p1p0, p0p0, (1-p1p0), (1-p0p0), p1p1, p0p1, (1-p1p1), (1-p0p1)),   
#   c(p1p1, (1-p1p1), p1p0, (1-p1p0), p0p1, (1-p0p1), p0p0, (1-p0p0) ),
#                 c(2,2,2),
#                 list(evid=c("Yes","No"), overpar = c("Yes","No"), diseaseSevere = c("Yes","No")), 
#                 NULL)

```

These solutions to calculating joint cpt are making me nervous, I'm clearly missing something since it's not invariant to the base probability. I'm going to try using brms and doing things a bit differently ... Ok so apparently this is a disaster and I should definitely not do it this way.

```{r}
# # this is the old way I was thinking of doing things and it is apparently a disaster ...
# library(brms)
# 
# d_brm <- d_scored %>%
#   filter(scale %in% c("overpar","diseaseSevere")) %>%
#   filter(condition=="diseaseRisk") %>%
#   mutate(evid = ifelse(phase=="pre",0,1)) %>%
#   select(workerId, condition, evid, scale, mean) %>%
#   mutate(mean = rescale_beta(mean, -3, 3)) %>%
#   spread(scale,mean) %>%
#   rename(op = overpar, ds=diseaseSevere)
# 
# 
# brm_fit<- brm(
#   bf(
#     evid ~ p0p0*(1-ds)*(1-op) + p1p0*ds*(1-op) + p0p1*(1-ds)*op + p1p1*ds*op,
#     p0p0 + p1p0 + p0p1 + p1p1 ~ 1,
#     nl = TRUE,
#     family = bernoulli()
#      ),
#   prior = prior("uniform(0,1)", lb =0, ub=1, nlpar = "p0p0") +
#           prior("uniform(0,1)", lb =0, ub=1, nlpar = "p1p0") +
#           prior("uniform(0,1)", lb =0, ub=1, nlpar = "p0p1") +
#           prior("uniform(0,1)", lb =0, ub=1, nlpar = "p1p1"),
#     # prior("uniform(0,1)", lb = 0, ub = 1, nlpar = "p0"),
#   data = d_brm,
#   iter = 4000,
#   warmup = 2000,
#   chains = 2,
#   cores = 2,
#   control = list(adapt_delta=.95)
# )
```

```{r}
# add_evid_node_custom <- function(bnlearn_model, parents_string, evid_cpt) {
#   
#   # evid_cpt <- make_evid_cpt(data, targetted_belief)
#   model_list <- lapply(bnlearn_model, function(x){x$prob})
#   # model_list$evid <- hyde_to_bn_cpt(evid_cpt)
#   model_list$evid <- evid_cpt
#   
#   model_string <- modelstring(bnlearn_model)
#   model_string <- paste0(model_string,"[evidk|", parents_string, "]")
#   model_network <- model2network(model_string)
#   predModel <- custom.fit(model_network, dist = model_list)
# 
#   return(predModel)
#   
# }

# ds_overpar_model <- add_evid_node_custom(base_model, "overpar:diseaseSevere", overpar_ds_evid_cpt)
# ds_overpar_model <- add_evid_node_custom(base_model, "overpar:diseaseSevere", overpar_ds_evid_cpt)

# ds_overpar_model <- add_evid_node(filter_dscored(d_scored, "diseaseSevere"), 
#                                   base_model, 
#                                   "diseaseSevere", "_1")

ds_overpar_model <- add_evid_node(filter_dscored(d_scored, "diseaseSevere"), 
                                  base_model, 
                                  "diseaseSevere", "_1")

ds_overpar_model <- add_evid_node(filter_dscored(d_scored, "overpar"), 
                                  ds_overpar_model, 
                                  "overpar", "_2")

# ----------------------------------------

set.seed(12345)

pred0_ds_overpar <- sapply(nodes, function(x){
  statement <- paste0("cpquery(ds_overpar_model, event = (", x, " == 'Yes'), evidence=TRUE, n = 1e6)")
  eval(parse(text=statement))
})

pred1_ds_overpar <- sapply(nodes, function(x){
  statement <- paste0("cpquery(ds_overpar_model, event = (", 
                      x,
                      " == 'Yes'), evidence= (evid_1 == 'Yes' & evid_2== 'Yes'), n = 1e6)")
  eval(parse(text=statement))
})

pred_changes2 <- pred1_ds_overpar - pred0_ds_overpar

pred_changes2 <- as.data.frame(pred_changes2)

pred_changes2 <- pred_changes2 %>%
  mutate(scale = nodes) %>%
  rename(Mean = pred_changes2) %>%
  mutate(type = "predicted")

# ----------------------------------------

obs_pred2 <- bind_rows(pred_changes2, obs_changes) %>%
  spread(type, Mean) %>%
  group_by(scale) %>%
  summarize_all(mean, na.rm=TRUE)

cor(obs_pred2$predicted, obs_pred2$observed)

obs_pred2 %>% # a bit of a hack
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point() +
  geom_errorbar() +
  coord_cartesian(xlim=c(-.06,.08), ylim=c(-.06,.08)) +
  theme_bw() +
  theme(aspect.ratio = 1)

obs_pred2 %>%
  gather(type, Mean, observed, predicted) %>%
  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
  geom_point() +
  geom_errorbarh(height=0)
```

Pretty confident the issue predicting overpar is coming from slightly different pre-test scores for study 2 compared with study 1 (an issue that also applies for disease severity too, but apparently not having as large an effect.)

```{r}
# obs,pred correlation excluding nodes fit
obs_pred_excl <- bind_rows(pred_changes, obs_changes) %>%
  spread(type, Mean) %>%
  filter(scale!="diseaseSevere", scale!="overpar") %>%
  group_by(scale) %>%
  summarize_all(mean, na.rm=TRUE)

cor(obs_pred_excl$predicted, obs_pred_excl$observed)
sqrt(mean((obs_pred_excl$observed-obs_pred_excl$predicted)^2))
```

```{r}
# obs,pred correlation excluding nodes fit
obs_pred_excl2 <- bind_rows(pred_changes2, obs_changes) %>%
  spread(type, Mean) %>%
  filter(scale!="diseaseSevere",scale!="overpar") %>%
  group_by(scale) %>%
  summarize_all(mean, na.rm=TRUE)

cor(obs_pred_excl2$predicted, obs_pred_excl2$observed)
sqrt(mean((obs_pred_excl2$observed-obs_pred_excl2$predicted)^2))
```

Adding edge from overparenting hurts prediction for the 12 nodes other than disease severity and overparenting, goes from r = .90 to r = .818. RMSE just about doubled. To be sure I'd have to do the bootstrap on these estimates, but I think this is a signal that the fit is worse modeling it as a direct effect. If so that indicates to me that something is wrong in the model wrt overparenting beliefs.

```{r}
# make_evid_cpt_custom <- function(data){
#   res_overpar <- find_evid_ratio(filter_dscored(data, "overpar"))
#   res_ds <- find_evid_ratio(filter_dscored(data, "diseaseSevere"))
# 
#   overpar_ratio <- exp(res_overpar$par[1] + res_overpar$par[2])
#   ds_ratio <- exp(res_ds$par[1] + res_ds$par[2])
#   
#   p0p0 <- .1
#   p1p0 <- p0p0*ds_ratio
#   p0p1 <- p0p0*overpar_ratio
#   # p1p1 <- p0p0*overpar_ratio*ds_ratio
#   p1p1 <- 1-(1-p0p0)*(1-(p1p0-p0p0)/(1-p0p0))*(1-(p0p1-p0p0)/(1-p0p0))
#   
#   overpar_ds_evid_cpt <- make_custom_cpt(
#     # c(p1p0, p0p0, (1-p1p0), (1-p0p0), p1p1, p0p1, (1-p1p1), (1-p0p1)),   
#     c(p1p1, (1-p1p1), p1p0, (1-p1p0), p0p1, (1-p0p1), p0p0, (1-p0p0) ),
#                   c(2,2,2),
#                   list(evid=c("Yes","No"), overpar = c("Yes","No"), diseaseSevere = c("Yes","No")), 
#                   NULL)
# }

```

```{r}
cogModel_predictions2 <- function(model){

  if (length(model)==15) {
      pred0 <- sapply(nodes, function(x){
    statement <- paste0("cpquery(model, event = (", x, " == 'Yes'), evidence=TRUE, n = 1e5)")
    eval(parse(text=statement))
    })

    pred1 <- sapply(nodes, function(x){
      statement <- paste0("cpquery(model, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 1e5)")
      eval(parse(text=statement))
  })
  } else {
    pred0 <- sapply(nodes, function(x){
    statement <- paste0("cpquery(model, event = (", x, " == 'Yes'), evidence=TRUE, n = 1e5)")
    eval(parse(text=statement))
    })

    pred1 <- sapply(nodes, function(x){
      statement <- paste0("cpquery(model, event = (", x,
                          " == 'Yes'), evidence=(evid_1 == 'Yes' & evid_2 == 'Yes'), n = 1e5)")
      eval(parse(text=statement))
    })
  }

  pred_changes <- pred1 - pred0

  pred_changes <- as.data.frame(pred_changes)

  pred_changes <- pred_changes %>%
    mutate(scale = nodes) %>%
    rename(Mean = pred_changes) %>%
    mutate(type = "predicted")

  return(pred_changes)
}
```

```{r}
set.seed(1234)
t1 <- Sys.time()

boot_fits2 <- as_tibble(expand.grid(
  list(
    replicate = 1:100, parents = c("diseaseSevere","overpar:diseaseSevere")
  )
)) %>%
  nest(-replicate, .key="scales") %>%
  mutate(boot_d_scored = map(replicate, function(x) {
    totaln <- length(unique(d_scored$workerId))
    d_scored %>%
      nest(-workerId) %>%
      sample_n(totaln, replace = TRUE) %>%
      mutate(uniqueId = 1:totaln) %>%
      unnest()
  })) %>%
  unnest(scales, .drop=FALSE) %>%
  mutate(
      # boot_d = map2(boot_d_scored, scale, function(x,y){filter_dscored(x, y)}),
      obs_changes = map(boot_d_scored, extract_obs_changes),
      models = ifelse(parents=="diseaseSevere",
                 map(boot_d_scored, 
                     function(x){
                       add_evid_node(filter_dscored(x,"diseaseSevere"), base_model, "diseaseSevere")
                     }
                     ),
                 map(boot_d_scored, 
                     function(x){
                       m <- add_evid_node(filter_dscored(x,"diseaseSevere"), base_model, "diseaseSevere","_1")
                       m <- add_evid_node(filter_dscored(x,"overpar"), m, "overpar", "_2")
                     }))
      ) %>%
  select(-boot_d_scored) %>%
  mutate(
    pred_changes = map(models, cogModel_predictions2)
    # r = map2_dbl(pred_changes, obs_changes, compare_pred_obs_r),
    # rmse = map2_dbl(pred_changes, obs_changes, compare_pred_obs_rmse)
    )

print(Sys.time() - t1)
```

```{r}
boot_fits2 %>%
  mutate(
    pred_changes = map(pred_changes, filter, scale!="diseaseSevere", scale!="overpar"),
    obs_changes = map(obs_changes, filter, scale!="diseaseSevere", scale!="overpar"),
    r = map2_dbl(pred_changes, obs_changes, compare_pred_obs_r),
    rmse = map2_dbl(pred_changes, obs_changes, compare_pred_obs_rmse)#,
    # r2 = r^2
  ) %>%
  gather(measure, value, rmse, r) %>%
  ggplot(aes(x=parents, y = value)) +
  geom_boxplot() +
  facet_wrap(~measure, scales="free")
```

# Comparison with Naive models
*this should all get moved into study 1, or I should combine the studies ...*
After visiting UCLA (on 10/26), Hongjing suggested that the fit of the model needs to be situated or given context by some kind of model comparison. It's not clear what the real competing models are exactly, but one approach might be to build the best possible model for each node (14 models), and a model for the intervention effect. Then compare the fit of our one model against those. If it's achieving similar performance, all within one model, then that seems like the superior approach. Another thing to do might be to examine the test-retest reliability of the scales, based on the control condition in Study 2. This would set a bar for the maximum expected predictive power.

[ looks like several will be at test-retest, suggesting no possibility of improvement. A full set of naïve models will basically predict all the scores in study 1, without overfitting it seems. But, those models will totally fail to predict changes. ]

As Kara suggested, in presenting this I should make it clear that model selection (via model comparison) has already occurred--we've compared a huge space of possible models during structure learning. Thus, the real question we're seeking to answer here is how _good_ that best model is. Comparison against test-retest helps answer this, by giving context for what could be considered as good as possible. A potential second question could be to consider how things work compared with "naïve" models, which is like asking, "was it worth all that effort to find this model?", maybe seeing how well we can predict by just naïvely throwing all other measures at the problem. We'll find that doing so can work, but only for one of the tasks at a time. And for that reason, it can't help guide the design of interventions in the same way.

```{r}
# code to play with this

library(betareg)

build_formula <- function(node, all_nodes){

  lhs_nodes <- all_nodes[all_nodes != node]

  f <- paste(node, "~ ")
  for (n in lhs_nodes){
    f <- paste0(f, n, " + ")
  }

  f <- substr(f,1,nchar(f)-3)

  return(f)
}

make_model <- function(node){
  betareg(as.formula(build_formula(node, nodes)), 
        data = train)
}

calc_oos_fit <- function(model, node){ # break this up

  p <- predict(model, test)

  cor(p, test[,node])
}

calc_change <- function(model,node){
  df <- d_scored %>%
    filter(condition=="diseaseRisk") %>%
    group_by(scale, phase) %>%
    summarize(mean = mean(mean)) %>%
    spread(phase, mean)

  df1 <- df %>%
    select(scale, pre) %>%
    spread(scale, pre)

  # df2 <- df %>%
  #   select(scale,post) %>%
  #   spread(scale, post)

  df1[2,] <- df1[1,]  # can swap to have all changing ...
  df1[2,"diseaseSevere"] <- df[6, "post"]

  p <- predict(model, df1)

  p[2] - p[1]
}

oos_fits <- tibble(node=as.character(nodes)) %>%
  mutate(model = map(node, make_model)) %>%
  mutate(fit = map2_dbl(model, node, calc_oos_fit)) %>%
  mutate(pred_change = map2_dbl(model, node, calc_change))

```

```{r}
# compute test-retest reliability for each scale
test_retest_cor <- function(node){
    df <- d_scored %>%
    filter(condition == "noInterv", scale == node) %>%
    spread(phase, mean)
  return( cor(df$pre,df$post) )
}

test_retest <- tibble(node=as.character(nodes)) %>%
  mutate(fit = map_dbl(node, test_retest_cor))

```

Full models do just as well at predicting relationships as the cognitive model does ...

```{r}

r_lower <- function(r,n){
  map2_dbl(r, n, function(r,n){psych::r.con(r,n)[1]})
}

r_upper <- function(r,n){
  map2_dbl(r, n, function(r,n){psych::r.con(r,n)[2]})
}

model_fits <- tibble(
  node = as.character(nodes),
  model_fit = c(.50, .66, .48, .63, .64, .56, .71, .35, .63, .90, .83, .86, .81, .87),
  test_retest = test_retest$fit,
  full_fit = oos_fits$fit
  ) %>%
  gather(model, fit, model_fit, test_retest, full_fit) %>%
  mutate(n = ifelse(model=="test_retest", 233, 226)) %>%
  mutate(ul = r_upper(fit,n), ll= r_lower(fit,n))

model_fits %>%
  filter(model!="full_fit") %>%
  mutate(model = ifelse(model=="model_fit", "model", "test-retest")) %>%
  ggplot(aes(x=reorder(node, -fit), y = fit, color=model, ymin = ll, ymax =ul)) +
  # geom_errorbar(position = position_dodge(width=.25)) +
  geom_pointrange(size =.25, position = position_dodge(width=.25)) +
  ylim(0,1) +
  theme_bw(base_size = 14) +
  labs(x="Belief", y = "Correlation") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

(could we do also do proportion of non-error variance captured?)

... but full models cannot predict change scores. (they are also more complex, inelegant, etc.)

```{r}
obs_pred$full_model_pred <- oos_fits$pred_change

cor(obs_pred$observed, obs_pred$full_model_pred)

obs_pred %>% # a bit of a hack
  ggplot(aes(x=full_model_pred, y = observed)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point() +
  # geom_errorbar() +
  coord_cartesian(xlim=c(-.06,.08), ylim=c(-.06,.08)) +
  theme_bw() +
  theme(aspect.ratio = 1)

```

### 2018-11-29 study2/vacc_manyBelief_study2_analysis.Rmd
refactored, working
before yale visit

@@
 # load data
-d_all <- read.csv("../study3/data/study3_data.csv")[-1]
+d_all <- read.csv("../data/study2_data.csv")[-1]
 
@@
 
-```{r plot diffs, fig.width = 3, fig.asp = 3}
+```{r plot diffs}
 d_diffs <- d_scored %>%
@@
 g_diffs <- ggplot(d_diffs,
-                  aes(x = condition, y = Mean, 
+                  aes(x = scale, y = Mean, 
                       color = condition, group = condition)) +
-  facet_wrap(~ scale, ncol = 3) +
+  # facet_wrap(~ scale, ncol = 3) +
   geom_hline(yintercept = 0, lty = 2, size = 0.5) +
@@
   theme_bw() +
-  theme(legend.position = "none",
+  theme(
+    # legend.position = "none",
         axis.text.x = element_text(angle = 90, hjust = 1)) +

### 2018-11-29 scripts/custom-structure-learning/cog-model-discrete-funcs.R

@@ -68,6 +68,112 @@ fit_node_cpt <- function(node, data) {
   return(node_cpt)
 }
 
+# 11/21/18, 4:26 PM
+# adding this frm study2_modeling.Rmd b/c seems to be missing
+
+df_to_list <- function(arcs_df, as.strings=FALSE) {
+  # take arcs_df and make list of formulas
+  arcs_df$to <- as.character(arcs_df$to)
+  arcs_df$from <- as.character(arcs_df$from)
+  
+  nodes <- unique(unlist(arcs_df))
+  output <- lapply(nodes, function(node) {
+    edges <- arcs_df[which(arcs_df$to == node), "from"]
+    if (length(edges) < 1) {
+      edges <- NULL
+    }
+    list(child=node, parents=edges)
+    
+  })
+  names(output) <- nodes
+  return(output)
+}
+
+
+inv_logit <- plogis
+logit <- qlogis
+
+evid_score_func <- function(data, par) {
+  
+  inv_logit <- plogis
+  logit <- qlogis
+  
+  pred_y <- with(data,
+                 {
+                   inv_logit(logit(pre) + evid*par[2] + par[1])
+                 }
+  )
+  pred_beta_A <- pred_y * par[3]
+  pred_beta_B <- (1-pred_y) * par[3]
+  
+  ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
+  return(ll)
+}
+
+get_evid_probs <- function(result){
+  # this is a heuristic/hack, could be made better but probably doesn't matter
+  evid_ratio <- exp(result$par[1] + result$par[2])
+  if (evid_ratio < 1) {
+    p0 <- .90
+  } else {
+    p0 <- .50
+  }
+  
+  if (p0*evid_ratio >= 1) {
+    p0 <- p0*.9/(p0*evid_ratio)
+  }
+  
+  p1 <- p0*evid_ratio
+  
+  c(p0,p1)
+}
+
+
+evid_probs_to_cpt <- function(probs, var_name, evid_name = "evid"){
+  p0 <- probs[1]
+  p1 <- probs[2]
+  
+  full_list <- paste0("list(",var_name,"=c('Yes','No'),", evid_name, " = c('Yes', 'No'))")
+  make_custom_cpt(c(p1, p0, (1-p1), (1-p0)), c(2,2), eval(parse(text=full_list)), NULL)
+}
+
+
+find_evid_ratio <- function(data){
[…]

### 2018-11-29 scripts/custom-structure-learning/cog-model-jags-tools.R

@@ -140,3 +140,30 @@ write_jags_model <- function(bn.dag, obs_df) {
   model <- paste(model,"}")
   return(model)
 }
+
+
+find_dag_coefs <- function(bn.dag, obs_df) {
+  # bn.dag: bnlearn dag object
+  # obs_df: observed values for variables in bn_df
+  # coefs: coefficients from fitting bn in BRMS
+  
+  ordered_nodes <- bnlearn::node.ordering(bn.dag)
+  
+  coefs <- lapply(ordered_nodes, function(node){
+    node_parents <- parents(bn.dag, node)
+    find_node_coefs(node, node_parents, obs_df)
+  })
+  
+  names(coefs) <- ordered_nodes
+  return(coefs)
+}
+
+tidy_coefs <- function(coefs) {
+  
+  c2 <- lapply(coefs, as.list)
+  c3 <- lapply(c2, function(x){as_tibble(x) %>% gather(parameter, value)})
+  c4 <- imap(c3,function(x,y){x$to <- y; x})
+  coefs <- bind_rows(c4)
+  
+  return(coefs)
+}

### 2018-11-29 scripts/custom_plotting.R

@@ -1,0 +1,45 @@
+custom_plot.HydeNetwork <- function(x, 
+                             customNodes = NULL,
+                             customEdges = NULL,
+                             ..., 
+                             removeDeterm = FALSE,
+                             useHydeDefaults = TRUE)
+{
+  if (removeDeterm) x <- plot_nondeterm_only(x)
+  
+  node_df <- 
+    DiagrammeR::create_node_df(n = length(x[["nodes"]]),
+                               label = x[["nodes"]])
+  # 
+  # node_df <- data.frame(nodes = x[["nodes"]],
+  #                       stringsAsFactors = FALSE)
+  if (useHydeDefaults) node_df <- HydeNet:::mergeDefaultPlotOpts(x, node_df)
+  
+  if (!is.null(customNodes)) node_df <- HydeNet::mergeCustomNodes(node_df, customNodes)
+  
+  edge_table <- do.call("rbind", 
+                        mapply(FUN = HydeNet:::mapEdges, 
+                               x[["nodes"]], 
+                               x[["parents"]],
+                               MoreArgs = list(node_df = node_df)))
+  
+  edge_df <- DiagrammeR::create_edge_df(from = edge_table[, 2], 
+                                        to = edge_table[, 1])
+  
+  if (!is.null(customEdges)) HydeNet::mergeCustomEdges(edge_df, customEdges)
+  
+  
+  
+  DiagrammeR::create_graph(nodes_df = node_df,
+                           edges_df = edge_df,
+                           attr_theme = NULL)
+  
+}
+
+
+## ----------------------------------------
+
+# code to demo. For some reason set_edge_attrs() isn't working right, so have to do it manually
+z <- custom_plot.HydeNetwork(h)
+z$edges_df <- z$edges_df %>% mutate(color = "blue", penwidth=rep(c(1,2,3),10))
+render_graph(z)

### 2019-01-14 study2/job-talk-s2.Rmd
added notebook related to job talk

---
title: 'Vaccines: Many Beliefs Study 2: jobtalk'
author: "Derek Powell"
date: "November 16, 2018"
output: html_notebook
---

```{r, include = F}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r setup, include = F}
library(tidyverse)
library(psych)
# library(ggcorrplot)
library(lme4)
library(brms)
library(rms)
```

# model

```{r}
# detach("package:BiDAG", unload=TRUE)

library(tidyverse)
library(BiDAG)
# BiDAG depends on 'graph' package, source: http://www.bioconductor.org/packages/release/bioc/html/graph.html
# BiDAG depends on 'RBGL' package, source: https://bioconductor.org/packages/release/bioc/html/RBGL.html
library(bnlearn)
library(HydeNet)
library(gtools)

# source("cog-model-graph-tools.R")
source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)
source("../scripts/gmod_tools.R")
source("../scripts/bnTheoryBlacklist.R")
source("../scripts/custom-structure-learning/cog-model-jags-tools.R")

# # customize BiDAG functions
# orig_DAGcorescore <- BiDAG:::DAGcorescore # save to switch back if desired
# orig_TableDAGscore.alias <- BiDAG:::TableDAGscore.alias # save to switch back if desired

source("../study1/vacc_import_data.R", chdir = TRUE)
```

# Set up data

Participants responses were scaled from a 1 to 7 rating scale onto the open interval (0,1). We scaled these responses as recommended by [cite beta regression paper]. After scaling, we interpret these responses as indicating participants' credence in each belief--that is, the marginal probability they assign to the state of affairs described by the scale.

```{r}
# rescale beta

rescale_beta <- function(x, lower, upper) {
  # rescales onto the open interval (0,1)
  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"

  N <- length(x)
  res <- (x - lower) / (upper - lower)
  res <- (res * (N - 1) + .5) / N

  return(as.vector(res))
}

d_bn_scaled <- d_bn %>%
 mutate_all(function(x){rescale_beta(x,-3,3)})

## set the seed to make your partition reproductible
set.seed(123)
trainInd <- sample(seq_len(nrow(d_bn_scaled)), size = floor(nrow(d_bn_scaled)*.80))

train <- d_bn_scaled[trainInd, ]
test <- d_bn_scaled[-trainInd, ]
```

```{r}
map_dag <- readRDS("../local/map_dag_bn_theorybased.rds")
h <- readRDS("../local/map_dag_hydenet_theorybased.rds")
model_string <- readRDS("../local/map_dag_modelstring_theorybased.rds")
test_analyze <- readRDS("../local/s1_model_predictions.rds")

```

# job talk plots

November 16, 2018

## predicted vs observed across scales

```{r}
# library(ggthemes)

recode_nodes <- function(x){
  recode(x,
         "diseaseRare" = "Disease Rarity",
         "diseaseSevere" = "Disease Severity",
         "hb" = "Holistic Balance",
         "infantImmLimCap" = "IIS: Limited\nCapacity",
         "infantImmWeak" = "IIS: Weakness",
         "medSkept" = "Medical\nSkepticism",
         "nat" = "Naturalism",
         "overpar" = "Parental\nProtectiveness",
         "parentExpert" = "Parental\nExpertise",
         "vaccDanger" = "Vaccine\nDanger",
         "vaccEff" = "Vaccine\nEffectiveness",
         "vaccIntent" = "Vaccination\nIntentions",
         "vaccStrain" = "IIS: Vaccines\nStrain",
         "vaccTox" = "Vaccines\nToxicity")}

predObsCor <- cor(test_analyze$value,test_analyze$predValue)

corrDF <- test_analyze %>%
  mutate(varName = recode_nodes(varName)) %>%
  group_by(varName) %>%
  summarise(cor = cor(value,predValue)) %>%
  mutate(cor = format(round(cor,2),nsmall=2))

(
plt.valid <- test_analyze %>%
  mutate(varName = recode_nodes(varName)) %>%
  ggplot(aes(x=predValue, y=value)) + 
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha=.33) +
  geom_point(shape=1, size=.5, color=ibm_palette[3]) + 
  geom_text(data=corrDF, aes(label=paste("r =", cor)),
            x=-Inf, y=Inf, hjust=-0.12, vjust=1.4,
            size = 10*.352777778,
            color="grey25") +
  # geom_smooth(method="lm") +
  coord_fixed() + 
  facet_wrap(~varName, nrow=2) + 
  scale_x_continuous("Predicted values", limits = c(0, 1)) +
  scale_y_continuous("Observed values", limits = c(0, 1)) +
  theme_bw(base_size = 10) +
  theme(strip.background = element_rect(fill="grey90"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
)

ggsave(plot = plt.valid, filename = "../local/s1_predobs_plot.png", width=8.5, height=4)
```

## network structure (beautified)

```{r}
# do network structure plotting here ...
library(DiagrammeR)

custom_plot.HydeNetwork <- function(x, 
                             customNodes = NULL,
                             customEdges = NULL,
                             ..., 
                             removeDeterm = FALSE,
                             useHydeDefaults = TRUE)
{
  if (removeDeterm) x <- plot_nondeterm_only(x)

  node_df <- 
    DiagrammeR::create_node_df(n = length(x[["nodes"]]),
                               label = x[["nodes"]])
  # 
  # node_df <- data.frame(nodes = x[["nodes"]],
  #                       stringsAsFactors = FALSE)
  if (useHydeDefaults) node_df <- HydeNet:::mergeDefaultPlotOpts(x, node_df)

  if (!is.null(customNodes)) node_df <- HydeNet::mergeCustomNodes(node_df, customNodes)

  edge_table <- do.call("rbind", 
                        mapply(FUN = HydeNet:::mapEdges, 
                               x[["nodes"]], 
                               x[["parents"]],
                               MoreArgs = list(node_df = node_df)))

  edge_df <- DiagrammeR::create_edge_df(from = edge_table[, 2], 
                                        to = edge_table[, 1])

  if (!is.null(customEdges)) HydeNet::mergeCustomEdges(edge_df, customEdges)

  DiagrammeR::create_graph(nodes_df = node_df,
                           edges_df = edge_df,
                           attr_theme = NULL)

}

## ----------------------------------------

# code to demo. For some reason set_edge_attrs() isn't working right, so have to do it manually

map_to_viridis <- function(vec, bins=64, option="D"){

  binned <- cut(vec, bins)
  levels(binned) <- viridis::viridis(bins, option=option)

  return(as.character(binned))
}

map_to_brewer <- function(vec, bins=11, mid=NULL, option="RdYlBu"){

  Min <- min(vec)
  Max <- max(vec)
  if (is.null(mid)){
    breaks <- seq(Min,Max, length.out=bins)
  } else {
    breaks <- c(seq(Min,mid,length.out=bins/2), seq(mid,Max, length.out=bins/2)[-1]) 
  }

  binned <- cut(vec, breaks=breaks, include.lowest = TRUE)
  levels(binned) <- RColorBrewer::brewer.pal(bins, name=option)

  return(as.character(binned))
}

```

```{r}
z <- custom_plot.HydeNetwork(h)

c <- find_dag_coefs(map_dag, train)

coefs <- tidy_coefs(c)

coefs %>%
  filter(parameter!="phi",parameter!="w_leak") %>%
  rename(from = parameter) %>%
  mutate(from = gsub("w_","",from)) %>%
  select(to, from, value) %>%
  merge(z$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
  mutate(from = id) %>%
  select(-id) %>%
  merge(z$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
  mutate(to = id) %>%
  arrange(to,from) -> edge_df_mod

z$nodes_df <- z$nodes_df %>% mutate(label = recode_nodes(label))
z <- z %>% 
  set_node_attrs(node_attr = fontname, values="Helvetica") %>%
  set_node_attrs(node_attr = fillcolor, 
                 values = ifelse(z$nodes_df$id==13, "lightgrey","white")) %>%
  set_node_attrs(node_attr = fontsize, values = 10) %>%
  set_edge_attrs(edge_attr=color, values = map_to_brewer(edge_df_mod$value)) %>%
  set_edge_attrs(edge_attr=penwidth, values=1.5) %>%
  set_edge_attrs(edge_attr=arrowsize, values=1)

z$edges_df$color <- map_to_brewer(edge_df_mod$value, mid=0,option="RdBu")
render_graph(z)

```

## Color legend

```{r}
legend_plot <- tibble(values = edge_df_mod$value, colors = map_to_brewer(edge_df_mod$value,mid = 0)) %>%
  mutate(x = 1) %>%
  ggplot(aes(x=x, y=values, color=values)) +
  geom_point() +
  scale_color_distiller(palette="RdYlBu", direction=1) +
  labs(color="Weight")

# extract Legend 
g_legend <- function(a.gplot){ 
  tmp <- ggplot_gtable(ggplot_build(a.gplot)) 
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box") 
  legend <- tmp$grobs[[leg]] 
  return(legend)
  }

legend <- g_legend(legend_plot)

ggsave(plot = legend, filename = "../local/legend.png")
```

# Data prep

```{r tidy, include = F}
# load data
d_all <- read.csv("../data/study2_data.csv")[-1]

# reformat to match previous analyses (i.e., 2 rows per participant)
d_demo <- d_all %>% 
  select(workerId, condition, gender, age, ethnicity, education, job, income,
         political_party, political_beliefs, eligible_pretest, 
         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
         children_youngest_posttest, plan_parent_posttest,
         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
         starts_with("comments"), starts_with("duration"))
d_pre <- d_all %>% 
  select(workerId, ends_with("_pretest")) %>%
  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
            starts_with("attention_"), starts_with("comments"), 
            starts_with("duration"))) %>%
  rename_all(funs(gsub("_pretest", "", .))) %>%
  mutate(phase = "pre")
d_post <- d_all %>% 
  select(workerId, ends_with("_posttest")) %>%
  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
            children_youngest_posttest, plan_parent_posttest,
            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
            starts_with("comments"), starts_with("duration"))) %>%
  rename_all(funs(gsub("_posttest", "", .))) %>%
  mutate(phase = "post")

d <- bind_rows(d_pre, d_post) %>% 
  gather(question, response, -c(workerId, phase)) %>%
  mutate(phase = factor(phase,
                        levels = c("pre", "post")),
         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
         # NOTE: "response" has already been reverse coded!
         question = factor(question),
         scale = factor(gsub("_.*$", "", question),
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert"))) %>%
  full_join(d_demo) %>%
  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
  distinct()

# how many left?
d %>% distinct(workerId, condition) %>% count(condition)
```

```{r scores, include = F}
# score all scales
d_scored <- d %>%
  select(workerId, condition, phase, scale, response,
         gender:duration_posttest) %>%
  group_by(workerId, condition, phase, scale) %>%
  mutate(response = as.numeric(response)) %>%
  summarise(mean = mean(response, na.rm = TRUE)) %>%
  ungroup() %>%
  distinct()
```

It looks like there's a lot of overlap in the pre- and post-test distrubtions for all scales - though a few hints of subtle shifts (e.g., in `diseaseRare`, `vaccIntent`).

# Visual comparison of pre- vs. post-intervention

Let's compare participants' responses pre- vs. post-intervention on all scales. I'll plot both mean pre- and post-intervention scores, as well as mean difference scores (note separate axes):

```{r plot means}
d_means <- d_scored %>%
  distinct(workerId, condition, phase, scale, mean) %>%
  group_by(condition, phase, scale) %>%
  # summarise(Mean = mean(mean, na.rm = T),
  #           Lower = Mean - 2 * sd(mean, na.rm = T)/sqrt(n()),
  #           Upper = Mean + 2 * sd(mean, na.rm = T)/sqrt(n())) %>%
  do(data.frame(rbind(smean.cl.boot(.$mean)))) %>% # bootstrapped 95% CI
  ungroup() %>%
  distinct() %>%
  mutate(scale = factor(scale,
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert")),
         condition = factor(condition,
                            levels = c("diseaseRisk", "autismCorr", "noInterv")))
# 
# g_means <- ggplot(d_means,
#                   aes(x = phase, y = Mean,
#                       color = condition, group = condition)) +
#   facet_wrap(~ scale, ncol = 3) +
#   geom_path(position = position_dodge(width = 0.1)) +
#   geom_linerange(aes(ymin = Lower, ymax = Upper),
#                  position = position_dodge(width = 0.1)) +
#   geom_point(size = 3,
#              position = position_dodge(width = 0.1)) +
#   scale_y_continuous("mean score", 
#                      # limits = c(-3, 3),
#                      breaks = seq(-3, 3, 1)) +
#   scale_color_brewer(palette = "Set1", direction = -1) +
#   theme_bw() +
#   theme(legend.position = "bottom") +
#   labs(title = "mean scores by phase and condition",
#        subtitle = "error bars are bootstrapped 95% CIs")
# 
# g_means
```

```{r plot diffs}

recode_nodes2 <- function(x){
  recode(x,
         "diseaseRare" = "Disease\nRarity",
         "diseaseSevere" = "Disease\nSeverity",
         "hb" = "Holistic\nBalance",
         "infantImmLimCap" = "IIS:\nLimited\nCapacity",
         "infantImmWeak" = "IIS:\nWeakness",
         "medSkept" = "Medical\nSkepticism",
         "nat" = "Naturalism",
         "overpar" = "Parental\nProtect-\nivenness",
         "parentExpert" = "Parental\nExpertise",
         "vaccDanger" = "Vaccine\nDanger",
         "vaccEff" = "Vaccine\nEffect-\niveness",
         "vaccIntent" = "Vaccine\nIntentions",
         "vaccStrain" = "IIS:\nVaccines\nStrain",
         "vaccTox" = "Vaccines\nToxicity")}

boot_ci_upper <- function(x){
  Hmisc::smean.cl.boot(x)[3]
}

boot_ci_lower <- function(x){
  Hmisc::smean.cl.boot(x)[2]
}

# standard error function
std_err <- function(x) {
          sqrt(var(x[!is.na(x)]) / length(x[!is.na(x)]))
}

d_diffs <- d_scored %>%
  mutate(mean = rescale_beta(mean,-3,3)) %>%
  spread(phase, mean) %>%
  mutate(post_pre_diff = post - pre) %>%
  group_by(condition, scale) %>%
  summarise(
    Mean = mean(post_pre_diff),
    Upper95 = boot_ci_upper(post_pre_diff),
    Lower95 = boot_ci_lower(post_pre_diff),
    UpperSD = mean(post_pre_diff) + std_err(post_pre_diff),
    LowerSD = mean(post_pre_diff) - std_err(post_pre_diff),
    ) %>%
  # do(data.frame(rbind(smean.cl.boot(.$post_pre_diff)))) %>%
  ungroup() %>%
  mutate(scale = factor(scale,
                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
                                   "vaccStrain", "vaccTox", 
                                   "diseaseSevere", "diseaseRare", 
                                   "infantImmLimCap", "infantImmWeak", 
                                   "medSkept", "hb", "nat", 
                                   "overpar", "parentExpert")),
         condition = factor(condition,
                            levels = c("diseaseRisk", "autismCorr", "noInterv"),
                            labels = c("Disease Risk", "autismCorr", "No-intervention"))) %>%
  mutate(scale = recode_nodes2(scale))

(
g_diffs <- ggplot(d_diffs,
                  aes(x = reorder(scale, -Mean), y = Mean, 
                      color = condition, group = condition)) +
  # facet_wrap(~ scale, ncol = 3) +
  geom_hline(yintercept = 0, lty = 2, size = 0.5) +
  geom_linerange(aes(ymin = Lower95, ymax = Upper95), position = position_dodge(.25)) +
  geom_linerange(aes(ymin = LowerSD, ymax = UpperSD), 
                 position = position_dodge(.25), size=1.5) +
  geom_point(size = 3, position = position_dodge(.25)) +
  # scale_y_continuous("mean diff") + #, 
                     # limits = c(-3, 3), 
                     # breaks = seq(-3, 3, 1)) +
  # scale_color_brewer(palette = "Set1", direction = -1) +
  scale_color_manual(values=ibm_palette[c(1,3)]) +
  theme_bw(base_size=14) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size=8),
    panel.grid = element_blank()
        ) +
  labs(
    # title = "mean difference scores by scale and condition",
       # subtitle = "error bars are 95% bootstrapped CIs",
       x = "Belief",
       y = "Mean Change Score",
       color = "Condition") 
)

ggsave(plot = g_diffs, filename = "../local/s2_diffs.png", height=5, width=8.5)

```

```{r}
 # standard error function
stderr <- function(x) {
          sqrt(var(x[!is.na(x)]) / length(x[!is.na(x)]))
}

(
  vacc_intent_change_plot <- d_diffs %>%
  filter(scale=="Vaccine\nIntentions") %>%
  mutate(condition = factor(condition, levels = c("No-intervention", "Disease Risk"))) %>%
  ggplot(aes(x = condition, fill=condition, y = Mean, ymin = LowerSD, ymax=UpperSD)) +
    geom_bar(stat="identity") +
    geom_errorbar(width=.1) +
  theme_bw(base_size=14) +
  # scale_fill_brewer(palette = "Set1", direction = 1) +
  scale_fill_manual(values=ibm_palette[c(1,3)]) +
  geom_hline(yintercept = 0, linetype="dashed") +
  theme(panel.grid = element_blank(), legend.position = "none") +
  labs(
    x = "Condition",
    y = "Mean Change Score"
  )
)

ggsave(plot = vacc_intent_change_plot, filename = "../local/s2_vacc_intent.png", height=4, width=5)
```

```{r plot means and diffs, fig.width = 3, fig.asp = 3}
multiplicand <- 6
multi_fun <- function(x, multi = multiplicand){return(x * multi)}
g_means +
  geom_segment(aes(x = 2.5, xend = 3.5, y = 0, yend = 0), 
               color = "black", lty = "dashed", size = 0.3) +
  geom_linerange(data = d_diffs %>% 
                   mutate_at(vars(Mean, Lower, Upper), funs(multi_fun)) %>%
                   mutate(phase = "diff"),
                 aes(x = phase, ymin = Lower, ymax = Upper),
                 position = position_dodge(width = 0.5)) +
  geom_point(data = d_diffs %>%
               mutate_at(vars(Mean, Lower, Upper), funs(multi_fun)) %>%
               mutate(phase = "diff"),
             aes(x = phase, y = Mean),
             position = position_dodge(width = 0.5),
             size = 2, shape = 17) +
  scale_x_discrete(limits = c("pre", "post", "diff")) +
  scale_y_continuous("mean score", breaks = seq(-3, 3, 1),
                     sec.axis = sec_axis(~./multiplicand, 
                                         name = "mean diff")) +
  scale_color_brewer(palette = "Set1", direction = -1) +
  theme(legend.position = "top", 
        panel.grid.minor.y = element_blank()) +
  labs(title = "means and mean difference scores by scale and condition",
       subtitle = "error bars are 95% bootstrapped CIs\nNOTE:use left y-axis for pre and post phases, right y-axis for difference scores")
```

# modeling

```{r}
# load in model components

map_dag <- readRDS("../local/map_dag_bn_theorybased.rds")
h <- readRDS("../local/map_dag_hydenet_theorybased.rds")
model_string <- readRDS("../local/map_dag_modelstring_theorybased.rds")
test_analyze <- readRDS("../local/s1_model_predictions.rds")
```

s1 model predictions ...

```{r}
# library(ggthemes)

summarize <- dplyr::summarise

recode_nodes <- function(x){
  recode(x,
         "diseaseRare" = "Disease Rarity",
         "diseaseSevere" = "Disease Severity",
         "hb" = "Holistic Balance",
         "infantImmLimCap" = "IIS: Limited\nCapacity",
         "infantImmWeak" = "IIS: Weakness",
         "medSkept" = "Medical\nSkepticism",
         "nat" = "Naturalism",
         "overpar" = "Parental\nProtectiveness",
         "parentExpert" = "Parental\nExpertise",
         "vaccDanger" = "Vaccine\nDanger",
         "vaccEff" = "Vaccine\nEffectiveness",
         "vaccIntent" = "Vaccination\nIntentions",
         "vaccStrain" = "IIS: Vaccines\nStrain",
         "vaccTox" = "Vaccines\nToxicity")}

predObsCor <- cor(test_analyze$value,test_analyze$predValue)

corrDF <- test_analyze %>%
  # mutate(varName = recode_nodes(varName)) %>%
  group_by(varName) %>%
  summarize(cor = cor(value,predValue)) %>%
  mutate(cor = format(round(cor,2),nsmall=2))

plt.valid <- test_analyze %>%
  mutate(varName = recode_nodes(varName)) %>%
  ggplot(aes(x=predValue, y=value)) + 
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha=.33) +
  geom_point(shape=1, size=.5, color="darkturquoise") + 
  geom_text(data=(corrDF %>% mutate(varName = recode_nodes(varName))), 
            aes(label=paste("r =", cor)),
            x=-Inf, y=Inf, hjust=-0.12, vjust=1.4,
            size = 10*.352777778,
            color="grey25") +
  # geom_smooth(method="lm") +
  coord_fixed() + 
  facet_wrap(~varName, nrow=2) + 
  scale_x_continuous("Predicted values", limits = c(0, 1)) +
  scale_y_continuous("Observed values", limits = c(0, 1)) +
  theme_bw(base_size = 10) +
  theme(strip.background = element_rect(fill="grey90"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggsave(plot = plt.valid, filename = "../local/s1_predobs_plot.png", width=8.5, height=4)
```

# simulating hypothetical interventions

```{r}

# this is some code to genrate predictions of vacc intent change based on
# hypothetical interventions

source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)

create_bnlearn_cog_model <- function(dag, data, evid_cpt = NULL, targetted_belief = NULL) {
  arcs_df <- bnlearn_to_df(dag)
  graph_list <- df_to_list(arcs_df)
  bagOfModels <- lapply(graph_list, function(x){fit_node_cpt(x, data)})
  model_string <- as.character(dag)

  if (!(is.null(evid_cpt))) {
    bagOfModels$evid <- evid_cpt
    model_string <- paste0(model_string,"[evid|", targetted_belief, "]")
  }
  model_network <- model2network(model_string)
  bnlearn_models <- lapply(bagOfModels, hyde_to_bn_cpt)
  predModel <- custom.fit(model_network, dist = bnlearn_models)

  return(predModel)
}

add_evid_node <- function(data, bnlearn_model, targetted_belief, evid_id = NULL) {

  if (!is.null(evid_id)) {
    evid <- paste0("evid",evid_id)
  } else {
    evid <- "evid"
  }

  evid_cpt <- make_evid_cpt(data, targetted_belief, evid)
  model_list <- lapply(bnlearn_model, function(x){x$prob})
  model_list[[evid]] <- hyde_to_bn_cpt(evid_cpt)

  model_string <- modelstring(bnlearn_model)
  model_string <- paste0(model_string,"[", evid,"|", targetted_belief, "]")

  model_network <- model2network(model_string)
  predModel <- custom.fit(model_network, dist = model_list)

  return(predModel)
}

add_evid_node_custom <- function(bnlearn_model, parents_string, evid_cpt) {

  model_list <- lapply(bnlearn_model, function(x){x$prob})
  model_list$evid <- evid_cpt

  model_string <- modelstring(bnlearn_model)
  model_string <- paste0(model_string,"[evid|", parents_string, "]")
  model_network <- model2network(model_string)
  predModel <- custom.fit(model_network, dist = model_list)

  return(predModel)
}

cogModel_predictions <- function(model){
  pred0 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(model, event = (", x, " == 'Yes'), evidence=TRUE, n = 1e5)")
  eval(parse(text=statement))
  })

  pred1 <- sapply(nodes, function(x){
    statement <- paste0("cpquery(model, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 1e5)")
    eval(parse(text=statement))
  })

  pred_changes <- pred1 - pred0

  pred_changes <- as.data.frame(pred_changes)

  pred_changes <- pred_changes %>%
    mutate(scale = nodes) %>%
    rename(Mean = pred_changes) %>%
    mutate(type = "predicted")

  return(pred_changes)
}

base_model <- create_bnlearn_cog_model(map_dag, train)

# source("../study2/load-study2-data.R", chdir = TRUE)

dag_nodes <- nodes(map_dag)

vaccIntent_pred_results <- data.frame(scale=dag_nodes, value = NA)

for (i in 1:length(dag_nodes)) {
  if (cor(d_bn[,"vaccIntent"], d_bn[,dag_nodes[i]]) >= 0) {
    evid_ratio <- 2
  } else {
    evid_ratio <- .5
  }
  evid_cpt <- hyde_to_bn_cpt(make_evid_cpt_custom(dag_nodes[i], evid_ratio))
  vaccIntent_predNet <- add_evid_node_custom(base_model, dag_nodes[i], evid_cpt)

  preds <- cogModel_predictions(vaccIntent_predNet) %>%
    filter(scale=="vaccIntent")

  vaccIntent_pred_results[i,"value"] <- preds[1,"Mean"]

}

## combine this with observed correlations from study 1

corrmat <- cor(d_bn)

interv_sim <- corrmat["vaccIntent",] %>%
  tibble(scale = names(.), value = ., type="correlation") %>%
  bind_rows(vaccIntent_pred_results %>% mutate(type="model_pred")) %>%
  spread(type,value)

interv_sim %>%
  ggplot(aes(x=abs(correlation), y = model_pred)) +
  geom_point()

(pred_change_plot <- interv_sim %>% 
  filter(scale!="vaccIntent") %>%
    mutate(scale = recode_nodes(scale)) %>%
  ggplot(aes(x=reorder(scale, model_pred), y = model_pred)) + 
  geom_bar(stat="identity", fill=ibm_palette[3], width=.5) + 
  coord_flip() +
  labs(x="Targeted belief", y = "Predicted change in intentions") +
  theme_bw(base_size=12) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1.5))

ggsave("../local/predicted_changes.png", pred_change_plot, height=5, width=5)
```

Compare predicted and observed changes ...

```{r}
set.seed(12345)

filter_dscored <- function(data, scale_name){

  data %>%
  filter(scale == scale_name) %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase, mean) %>% 
  mutate(condition = relevel(condition, ref="noInterv")) %>%
  mutate(evid = ifelse(condition=="noInterv",0,1))
}

# d <- d_scored %>%
#   filter(scale == "diseaseSevere") %>%
#   mutate(mean = rescale_beta(mean, -3, 3)) %>%
#   spread(phase, mean) %>% 
#   mutate(condition = relevel(condition, ref="noInterv")) %>%
#   mutate(evid = ifelse(condition=="noInterv",0,1))

predModel <- add_evid_node(filter_dscored(d_scored, "diseaseSevere"), base_model, "diseaseSevere")

pred0 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence=TRUE, n = 5e5)")
  eval(parse(text=statement))
})

pred1 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 5e5)")
  eval(parse(text=statement))
})

pred_changes <- pred1 - pred0

pred_changes <- as.data.frame(pred_changes)

pred_changes <- pred_changes %>%
  mutate(scale = nodes) %>%
  rename(Mean = pred_changes) %>%
  mutate(type = "predicted")

```

```{r}

obs_changes <- d_scored %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase,mean) %>%
  mutate(changeScore = post-pre) %>%
  filter(condition == "diseaseRisk") %>%
  group_by(scale) %>%
  summarise(
    Mean = mean(changeScore),
    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()), # replace with bootstrapping
    ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
    ) %>%
  mutate(type = "observed")

obs_pred <- bind_rows(pred_changes, obs_changes) %>%
  spread(type, Mean) %>%
  group_by(scale) %>%
  summarize_all(mean, na.rm=TRUE)

cor(obs_pred$predicted, obs_pred$observed)

(obs_pred_plot <- obs_pred %>% # a bit of a hack
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point(size=2) +
  geom_errorbar(alpha=.5, width=0) +
  coord_cartesian(xlim=c(-.06,.08), ylim=c(-.06,.08)) +
  labs(x="Predicted", y="Observed") +
  theme_bw(base_size=16) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1))

obs_pred %>%
  gather(type, Mean, observed, predicted) %>%
  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
  geom_point() +
  geom_errorbarh(height=0)

ggsave("../local/obs_pred_plot.png",obs_pred_plot, height=5, width=5)
```

# backslides stuff

## model comparison

```{r}
# compute test-retest reliability for each scale
test_retest_cor <- function(node){
    df <- d_scored %>%
    filter(condition == "noInterv", scale == node) %>%
    spread(phase, mean)
  return( cor(df$pre,df$post) )
}

test_retest <- tibble(node=as.character(nodes(map_dag))) %>%
  mutate(fit = map_dbl(node, test_retest_cor))

build_formula <- function(node, all_nodes){

  lhs_nodes <- all_nodes[all_nodes != node]

  f <- paste(node, "~ ")
  for (n in lhs_nodes){
    f <- paste0(f, n, " + ")
  }

  f <- substr(f,1,nchar(f)-3)

  return(f)
}

make_model <- function(node){
  betareg(as.formula(build_formula(node, nodes)), 
        data = train)
}

calc_oos_fit <- function(model, node){ # break this up

  p <- predict(model, test)

  cor(p, test[,node])
}

calc_change <- function(model,node){
  df <- d_scored %>%
    filter(condition=="diseaseRisk") %>%
    group_by(scale, phase) %>%
    summarize(mean = mean(mean)) %>%
    spread(phase, mean)

  df1 <- df %>%
    select(scale, pre) %>%
    spread(scale, pre)

  # df2 <- df %>%
  #   select(scale,post) %>%
  #   spread(scale, post)

  df1[2,] <- df1[1,]  # can swap to have all changing ...
  df1[2,"diseaseSevere"] <- df[6, "post"]

  p <- predict(model, df1)

  p[2] - p[1]
}

oos_fits <- tibble(node=as.character(nodes)) %>%
  mutate(model = map(node, make_model)) %>%
  mutate(fit = map2_dbl(model, node, calc_oos_fit)) %>%
  mutate(pred_change = map2_dbl(model, node, calc_change))
```

Full models do just as well at predicting relationships as the cognitive model does ...

```{r}
library(patchwork)

r_lower <- function(r,n){
  map2_dbl(r, n, function(r,n){psych::r.con(r,n)[1]})
}

r_upper <- function(r,n){
  map2_dbl(r, n, function(r,n){psych::r.con(r,n)[2]})
}

model_fits <- corrDF %>%
  rename(node = varName, model_fit = cor) %>%
  mutate(fit = as.numeric(model_fit)) %>%
  select(-model_fit) %>%
  mutate(model = "model_fit") %>%
  bind_rows(test_retest %>% mutate(model = "test_retest")) %>%
  bind_rows(oos_fits %>% mutate(model = "full_model") %>% select(-pred_change)) %>%
  # spread(model, fit) %>%
  # mutate(prop_var = model_fit^2/test_retest^2) %>%
  # gather(model, fit, model_fit, test_retest) %>%
  mutate(n = ifelse(model=="test_retest", 233, 226)) %>%
  mutate(ul = r_upper(fit,n), ll= r_lower(fit,n)) %>%
  mutate(node = recode_nodes2(node))

(
  test_v_retest_plot <- model_fits %>%
    # mutate(fit = fit^2, ul = ul^2, ll = ll^2)
  # filter(model!="full_fit") %>%
  # mutate(model = ifelse(model=="model_fit", "model", "test-retest")) %>%
  ggplot(aes(x=reorder(node, -fit), y = fit, color=model, ymin = ll, ymax =ul)) +
  # geom_errorbar(position = position_dodge(width=.25)) +
  geom_pointrange(size =.25, position = position_dodge(width=.25)) +
  ylim(0,1) +
  theme_bw(base_size = 12) +
  labs(x="Belief", y = "Correlation") +
    theme(
    legend.position = "bottom",
    axis.text.x = element_text(size=8),
    panel.grid = element_blank()
        )
  # theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust=.75))
  )

ggsave(plot = test_v_retest_plot, filename = "../local/s1_model_test_v_retest_plot2.png", width=8.5, height=5)
# # (
#   prop_var_plot <- model_fits %>%
#     group_by(node) %>%
#     summarise(prop_var = mean(prop_var), fit = mean(fit)) %>%
#   ggplot(aes(x=reorder(node, fit), y = prop_var)) + 
#   geom_bar(stat="identity", fill="salmon", width=.5) +
#   theme_bw(base_size=12) +
#   labs(x = "Belief", y = "Prop. non-error\nvariance") +
#     theme(axis.title.y= element_blank(), axis.text.y = element_blank()) +
#   coord_flip()
# # )

# (model_valid_comp_plot <- (test_v_retest_plot + prop_var_plot) * theme(panel.grid = element_blank()))
# 
# ggsave(plot = model_valid_comp_plot, filename = "../local/s1_model_valid_comp_plot.png", width=8, height=5)

```

Predicting changes using full-model ensemble approach ... (predicts poorly, r = .34)

```{r}
full_models_pred_changes <- oos_fits %>%
  rename(scale = node, Mean=pred_change) %>%
  mutate(type = "predicted") %>%
  select(-model,-fit)

obs_pred_fm <- bind_rows(full_models_pred_changes, obs_changes) %>%
  spread(type, Mean) %>%
  group_by(scale) %>%
  summarize_all(mean, na.rm=TRUE)

cor(obs_pred_fm$predicted, obs_pred_fm$observed)

(obs_pred_fm_plot <- obs_pred_fm %>% # a bit of a hack
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point(size=2) +
  geom_errorbar(alpha=.5, width=0) +
  coord_cartesian(xlim=c(-.06,.08), ylim=c(-.06,.08)) +
  # labs(title="full model ensemble") +
  labs(x="Predicted", y="Observed") +
  theme_bw(base_size=16) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1))

ggsave(plot = obs_pred_fm_plot, filename = "../local/naive_model_change_pred.png", width=5, height=5)
```

## Score distributions

First, let's look at the distributions of scores for all scales, pre- and post-test:

```{r scores histo, fig.width = 7, fig.height = 2}
ggplot(d_scored, 
       aes(x = mean, fill = phase)) +
  # facet_wrap(~ scale, ncol = 5) +
  facet_grid(condition ~ scale) +
  geom_histogram(bins = 14, position = "identity", alpha = 0.6) +
  scale_x_continuous(breaks = seq(-3, 3, 1)) + 
  theme_bw() +
  labs(title = "distributions of scores by scale, condition, and phase (pre/post)")
```

### 2019-02-12 study2/job-talk-s2.Rmd
post job talks, pre-reorganization

@@
 source("../study1/vacc_import_data.R", chdir = TRUE)
+
+ibm_palette <- c("#648fff", "#785ef0", "#dc267f", "#fe6100", "#ffb000")
 ```
@@
 
-ggsave(plot = plt.valid, filename = "../local/s1_predobs_plot.png", width=8.5, height=4)
+# ggsave(plot = plt.valid, filename = "../local/s1_predobs_plot.png", width=8.5, height=4)
 ```
@@
 
-ggsave(plot = legend, filename = "../local/legend.png")
+# ggsave(plot = legend, filename = "../local/legend.png")
 ```
@@
   # scale_color_brewer(palette = "Set1", direction = -1) +
-  scale_color_manual(values=ibm_palette[c(1,3)]) +
+  scale_color_manual(values=ibm_palette[c(3,1)]) + # this is a hack to make it match other fig
   theme_bw(base_size=14) +
@@
 
-ggsave(plot = vacc_intent_change_plot, filename = "../local/s2_vacc_intent.png", height=4, width=5)
+# ggsave(plot = vacc_intent_change_plot, filename = "../local/s2_vacc_intent.png", height=4, width=5)
 ```

### 2019-02-12 study1/vacc_import_data.R

@@ -21,8 +21,8 @@ d1 <- d_raw %>%
 
 # reformat variables
 d2 <- d1 %>% 
-  mutate_at(vars(StartDate), funs(parse_datetime)) %>% # parse dates
-  mutate_at(vars(Duration..in.seconds., age, children), funs(as.character)) %>% # parse numbers step 1
+  # mutate_at(vars(StartDate), funs(parse_datetime)) %>% # parse dates # 1/14/19, 3:12 PM this is throwing an error
+  # mutate_at(vars(Duration..in.seconds., age, children), funs(as.character)) %>% # parse numbers step 1
   mutate_at(vars(Duration..in.seconds., age, children), funs(as.numeric)) %>% # parse numbers step 2
   mutate(educ = factor(educ, # recode ordinal variables
                        levels = c("No Diploma", "High School or Equivalent",

### 2019-02-12 notebooks/s2-analysis.Rmd
some refactoring and updated readme

--- 2018-11-29 study2/vacc_manyBelief_study2_analysis.Rmd
@@
 library(rms)
+
 ```
@@
 ```{r tidy, include = F}
-# load data
-d_all <- read.csv("../data/study2_data.csv")[-1]
+# # load data
+# d_all <- read.csv("../data/study2_data.csv")[-1]
+# 
+# # reformat to match previous analyses (i.e., 2 rows per participant)
+# d_demo <- d_all %>% 
+#   select(workerId, condition, gender, age, ethnicity, education, job, income,
+#          political_party, political_beliefs, eligible_pretest, 
+#          is_parent_posttest, children_num_posttest, children_oldest_posttest, 
+#          children_youngest_posttest, plan_parent_posttest,
+#          starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
+#          starts_with("comments"), starts_with("duration"))
+# d_pre <- d_all %>% 
+#   select(workerId, ends_with("_pretest")) %>%
+#   select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
+#             starts_with("attention_"), starts_with("comments"), 
+#             starts_with("duration"))) %>%
+#   rename_all(funs(gsub("_pretest", "", .))) %>%
+#   mutate(phase = "pre")
+# d_post <- d_all %>% 
+#   select(workerId, ends_with("_posttest")) %>%
+#   select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
+#             children_youngest_posttest, plan_parent_posttest,
+#             starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
+#             starts_with("comments"), starts_with("duration"))) %>%
+#   rename_all(funs(gsub("_posttest", "", .))) %>%
+#   mutate(phase = "post")
+# 
+# d <- bind_rows(d_pre, d_post) %>% 
+#   gather(question, response, -c(workerId, phase)) %>%
+#   mutate(phase = factor(phase,
+#                         levels = c("pre", "post")),
+#          reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
+#          # NOTE: "response" has already been reverse coded!
+#          question = factor(question),
+#          scale = factor(gsub("_.*$", "", question),
+#                         levels = c("vaccIntent", "vaccDanger", "vaccEff", 
+#                                    "vaccStrain", "vaccTox", 
+#                                    "diseaseSevere", "diseaseRare", 
+#                                    "infantImmLimCap", "infantImmWeak", 
+#                                    "medSkept", "hb", "nat", 
+#                                    "overpar", "parentExpert"))) %>%
+#   full_join(d_demo) %>%
+#   mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
+#   filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
+#   distinct()
+#
 
-# reformat to match previous analyses (i.e., 2 rows per participant)
-d_demo <- d_all %>% 
-  select(workerId, condition, gender, age, ethnicity, education, job, income,
-         political_party, political_beliefs, eligible_pretest, 
-         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
-         children_youngest_posttest, plan_parent_posttest,
-         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
-         starts_with("comments"), starts_with("duration"))
-d_pre <- d_all %>% 
-  select(workerId, ends_with("_pretest")) %>%
-  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
-            starts_with("attention_"), starts_with("comments"), 
-            starts_with("duration"))) %>%
-  rename_all(funs(gsub("_pretest", "", .))) %>%
-  mutate(phase = "pre")
-d_post <- d_all %>% 
-  select(workerId, ends_with("_posttest")) %>%
-  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
-            children_youngest_posttest, plan_parent_posttest,
-            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
-            starts_with("comments"), starts_with("duration"))) %>%
-  rename_all(funs(gsub("_posttest", "", .))) %>%
-  mutate(phase = "post")
+source("../scripts/load-data-s2.R", chdir = TRUE)
 
-d <- bind_rows(d_pre, d_post) %>% 
-  gather(question, response, -c(workerId, phase)) %>%
-  mutate(phase = factor(phase,
-                        levels = c("pre", "post")),
-         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
-         # NOTE: "response" has already been reverse coded!
-         question = factor(question),
-         scale = factor(gsub("_.*$", "", question),
-                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
-                                   "vaccStrain", "vaccTox", 
-                                   "diseaseSevere", "diseaseRare", 
-                                   "infantImmLimCap", "infantImmWeak", 
-                                   "medSkept", "hb", "nat", 
-                                   "overpar", "parentExpert"))) %>%
-  full_join(d_demo) %>%
-  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
-  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
-  distinct()
-
-# how many left?
+# # how many left?
 d %>% distinct(workerId, condition) %>% count(condition)
@@
 # score all scales
-d_scored <- d %>%
-  select(workerId, condition, phase, scale, response,
-         gender:duration_posttest) %>%
-  group_by(workerId, condition, phase, scale) %>%
-  mutate(response = as.numeric(response)) %>%
-  summarise(mean = mean(response, na.rm = TRUE)) %>%
-  ungroup() %>%
-  distinct()
+# d_scored <- d %>%
+#   select(workerId, condition, phase, scale, response,
+#          gender:duration_posttest) %>%
+#   group_by(workerId, condition, phase, scale) %>%
+#   mutate(response = as.numeric(response)) %>%
+#   summarise(mean = mean(response, na.rm = TRUE)) %>%
+#   ungroup() %>%
+#   distinct()
 ```

### 2019-02-12 notebooks/s2-modeling.Rmd
some refactoring and updated readme

--- 2018-11-29 study2/study2_modeling.Rmd
@@
 
-source("../study1/vacc_import_data.R", chdir = TRUE)
+source("../scripts/load-data-s1.R", chdir = TRUE)
 source("../scripts/gmod_tools.R")
@@
 
-source("../study2/load-study2-data.R", chdir = TRUE)
+source("../scripts/load-data-s2.R", chdir = TRUE)
 

### 2019-02-12 scripts/load-data-s1.R

@@ -1,0 +1,118 @@
+
+# set wd (user-specific)
+# setwd("/Users/kweisman/Documents/Research (Stanford)/Projects/Vaccines/vaccineBeliefs/study1/")
+library(tidyverse)
+library(stringr)
+
+# working_dir <- getwd()
+# this.dir <- dirname(parent.frame(2)$ofile)
+# setwd(this.dir)
+
+# load in raw data
+d_raw <- read.csv("../data/study1_data.csv", header = T)
+
+# filter rows and select columns
+d1 <- d_raw %>%
+  filter(grepl("2017", StartDate)) %>% # remove extra headers
+  filter(Status == "IP Address") %>% # remove survey previews (?)
+  filter(Progress == 100) %>% # only get people who made it all the way through (?)
+  filter(as.numeric(as.character(age)) >= 18) %>% # exclude people who said they were <18 yo (could be more stringent)
+  select(StartDate, Duration..in.seconds., ResponseId, hb_1:comments) # include only selected columns
+
+# reformat variables
+d2 <- d1 %>% 
+  # mutate_at(vars(StartDate), funs(parse_datetime)) %>% # parse dates # 1/14/19, 3:12 PM this is throwing an error
+  # mutate_at(vars(Duration..in.seconds., age, children), funs(as.character)) %>% # parse numbers step 1
+  mutate_at(vars(Duration..in.seconds., age, children), funs(as.numeric)) %>% # parse numbers step 2
+  mutate(educ = factor(educ, # recode ordinal variables
+                       levels = c("No Diploma", "High School or Equivalent",
+                                  "Some Undergraduate Education", "Undergraduate Degree",
+                                  "Some Graduate or Professional Education",
+                                  "Graduate or Professional Degree", "Doctorate")),
+         income = factor(income, 
+                         levels = c("Less than $20,000", "$20,000 - $30,0000",
+                                    "$30,001 - $50,000", "$50,001 - $70,000",
+                                    "$70,001 - $100,000", "More than $100,000")),
+         parent = factor(parent, levels = c("No", "Yes")),
+         expecting = factor(expecting, levels =c ("No", "Yes")),
+         youngest_child = factor(youngest_child, 
+                                 levels = c("Less than 1 year old", "1 year old", "2 years old", 
+                                            "3 years old", "4 years old", "5 years old", "6 years old",
+                                            "7 years old", "8 years old", "9 years old", "10 years old",
+                                            "11 years old", "12 years old", "13 years old", "14 years old",
[…]

### 2019-02-13 notebooks/s1s2-pca-analysis.Rmd
added pca analysis

---
title: "int-theory-vacc PCA analysis"
output: html_notebook
---

During my visit to UCSD, several faculty I met with suggested taking a "dimensionality reduction" approach to examining these data. Ed Vul in particular suggested there may only be 1 or 2 components underlying these data, and that we could use changes in those components to predict the changes in the scales. He suggested I could "project" the changes in disease severity onto principle component space, and use that to simulate changes across beliefs following evidence.

This notebook is an attempt to test these suggestions.

```{r}
# library(FactoMineR)
library(tidyverse)
library(ggrepel)

source("../scripts/load-data-s1.R", chdir = TRUE)
source("../scripts/load-data-s2.R", chdir = TRUE)

# rescale_beta <- function(x, lower, upper) {
#   # rescales onto the open interval (0,1)
#   # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
# 
#   N <- length(x)
#   res <- (x - lower) / (upper - lower)
#   res <- (res * (N - 1) + .5) / N
# 
#   return(as.vector(res))
# }

# d_bn_scaled <- d_bn %>%
#  mutate_all(scale)

## set the seed to make your partition reproductible
set.seed(123)
trainInd <- sample(seq_len(nrow(d_bn)), size = floor(nrow(d_bn)*.80))

train <- d_bn[trainInd, ]
test <- d_bn[-trainInd, ]
```

## Exploring components

Let's look at how many factors we need to capture these data ...

```{r}
pca14 <- prcomp(train, scale. = TRUE, rank=14)

summary(pca14)
```

Fist factor gives 44% the variance. First 3 factors give 66% of the variance. That would be of similar complexity to the full Bayesian network model, in terms of number of parameters (33 edges + 14 leak nodes vs 14*3 loadings). From there, looks like you can get 85% of variance with 8 factors, 95% with 11 factors, and need 13 to get 99%.

## quick plots

To try to get a sense of these components, I'll look at the space of loadings for the first few factors.

```{r}

loadings <-  as.data.frame(pca14$rotation)

loadings %>%
  ggplot(aes(x=PC1, y = PC2, label=rownames(loadings))) +
  geom_point(color="red") +
  geom_text_repel() +
  theme_bw() +
  labs(title="Component Loadings")

loadings %>%
  ggplot(aes(x=PC1, y = PC3, label=rownames(loadings))) +
  geom_point(color="red") +
  geom_text_repel() +
  theme_bw() +
  labs(title="Component Loadings")

loadings %>%
  ggplot(aes(x=PC2, y = PC3, label=rownames(loadings))) +
  geom_point(color="red") +
  geom_text_repel() +
  theme_bw() +
  labs(title="Component Loadings")
```

Looks like PC1 is roughly, do you want to vaccinate or not. PC2 is less interpretable, but it seems to be separating out some of the oddballs, like infant immune system beliefs, and some kind of polarity b/c disease rare is on the opposite extreme. PC3 is kind of similar, I can't get much of a sense for it.

Now, to validate, let's see how a 3-component PCA solution reconstructs the test data.

```{r pca functions}
pca_reconstruct <- function(pca, newdata=NULL){
  # reconstruct data from pca compression
  # newdata: new data to reconstruct (in pca dimension)
  if (is_null(newdata)){
    newdata <- pca$x
  }

  if (dim(newdata)[1]==1) {
    newdata <- t(newdata) # pca with rank 1 behaves strangely for some reason
  }

  z <-  t(pca$rotation %*% t(newdata))
  z <- t(apply(z, 1, function(x){x*pca$scale + pca$center}))

  return(z)
}

pca_map_changes <- function(x, varname, pca, df=NULL) {
  # x: change in original units
  # varname: variable name as string
  # pca: pca solution (from prcomp)
  # returns new pc scores after change

  if (is_null(df)){
    df <- pca$x
  }

  if (is.numeric(pca$scale)) {
    scaled_change <- x/pca$scale[varname]
  } else {
    scaled_change <- x
  }

  var_loading <- pca$rotation[varname,]
  t(apply(df, 1, function(x){x + scaled_change*var_loading}))
}
```

```{r}
pca3 <- prcomp(train, scale. = TRUE, rank=3)
test_predicted <- pca_reconstruct(pca3, newdata = predict(pca3,test))

df_preds <- test_predicted %>%
  as_tibble() %>%
  mutate(id = seq(1,nrow(test))) %>%
  gather(scale, response, -id) %>%
  mutate(type = "predicted") %>%
  bind_rows(
    (
      test %>%
        mutate(id = seq(1,nrow(test))) %>%
        gather(scale, response, -id) %>%
        mutate(type = "observed")
    )
  ) %>%
  spread(type,response)

cors <- df_preds %>%
  group_by(scale) %>%
  summarize(correlation = cor(predicted, observed))

df_preds %>%
  ggplot(aes(x=predicted, y = observed)) +
  geom_point(shape=1, size=.5, color="darkturquoise") +
  geom_text(data = cors, inherit.aes = FALSE, aes(x = 3, y = -2, label=round(correlation,2))) +
  facet_wrap(~scale, nrow=2) +
  theme_bw() +
  theme(aspect.ratio=1)
```

Pretty good, as we would expect based on the variance accounted for. Three factors get approximately 65% of the variance, but the quality of predictions are a bit more even across scales (e.g., r = .66 for overparenting, vs .3 or so for bn). That's not necessarily surprising given the purpose of PCA. Overall however, predictions are of comaprable quality compared to the bayesian network model. Using fewer principle components does worse, so there isn't an opportunity for an appreciably "simpler" solution in number of parameters, or in degree of data reduction.

## Predicting changes using PCA

So now I'll take the PCA solution and try to generate predictions for how beliefs will change given a change in disease severity beliefs.

First, need to prepare data on observed changes for each scale.

```{r}

d_interv_pre <- d_scored %>%
  filter(condition=="diseaseRisk", phase=="pre") %>%
  spread(scale,mean) %>%
  select(-workerId, -condition, -phase)

d_changes <- d_scored %>%
  filter(condition=="diseaseRisk") %>%
  spread(phase, mean) %>%
  mutate(change = post-pre) %>%
  select(-pre,-post) %>%
  group_by(scale) %>%
  summarize(meanChange = mean(change))

d_changes
```

Then, need to map changes in disease severity beliefs onto pca space. Then, can generate predictions with reconstruction, projecting back into the original 14d space.

```{r}

pca3 <- prcomp(train, scale. = TRUE, rank=1)

# put s2 data in pca space
pre_pca <- predict(pca3, d_interv_pre)

# # map changes in diseaseSevere onto pca space
pre_pca_mod <- pca_map_changes(.32, "diseaseSevere", pca3, df=pre_pca) # based on observed change
# pre_pca_mod <- pca_map_changes(1.1, "diseaseSevere", pca3, df=pre_pca) # to approx obs change in pred vals

# # predict posttest scores by reconstruction from new pca values
pred_post<- pca_reconstruct(pca3, newdata = pre_pca_mod)

pred_post %>%
  as_tibble() %>%
  gather(scale, response) %>%
  group_by(scale) %>%
  summarize(posttest = mean(response)) %>%
  left_join(
    (
      d_interv_pre %>%
  gather(scale,response) %>%
  group_by(scale) %>%
  summarize(pretest = mean(response))
    ), by = "scale"
  ) %>%
  mutate(change = posttest-pretest) -> pred_changes

d_changes %>%
  rename(obs_changes = meanChange) %>%
  left_join(pred_changes) -> pred_obs_changes

cor(pred_obs_changes$obs_changes, pred_obs_changes$change)

pred_obs_changes %>%
  ggplot(aes(x=change, y=obs_changes)) +
  geom_point() +
  geom_abline(intercept=0, slope=1, linetype="dashed", alpha=.5) +
  theme_bw() +
  xlim(-.5,1) +
  ylim(-.5,1) +
  theme(aspect.ratio=1)
```

Seems to do quite poorly! Would be good to get another set of eyes on it, but I'm pretty confident my code is working. At least, when I use a full factor solution it adds the correct amount to disease severity scores and only disease severity scores. I'm not 100% sure this is exactly what Ed Vul and others have meant by using PCA, but it seems like the analogous approach.

So, tentatively, I don't think this PCA idea gives a very good solution and certainly it's hard to see it as an improvement (except maybe in ease of use and computation speed). It takes a similar number of parameters to get a similarly good reconstruction of S1 data, and the pca technique fails to predict changes in beliefs following evidence in S2.

### 2019-04-30 notebooks/s1s2-pca-analysis.Rmd
modeling updates

@@
   ggplot(aes(x=PC1, y = PC2, label=rownames(loadings))) +
+  geom_text_repel() +
   geom_point(color="red") +
-  geom_text_repel() +
   theme_bw() +
@@
   ggplot(aes(x=PC1, y = PC3, label=rownames(loadings))) +
+  geom_text_repel() +
   geom_point(color="red") +
-  geom_text_repel() +
   theme_bw() +
@@
   ggplot(aes(x=PC2, y = PC3, label=rownames(loadings))) +
+  geom_text_repel() +
   geom_point(color="red") +
-  geom_text_repel() +
   theme_bw() +
@@
 It takes a similar number of parameters to get a similarly good reconstruction of S1 data, and the pca technique fails to predict changes in beliefs following evidence in S2.
+
+Another thing worth considering is taht this isn't a "model" in any traditional sense.
+It's just a method of compressing and reconstructing the data.
+So in the predictions for s1, it's not really "predicting " each variable without being given any data on that specific variable.
+Instead, it's being given all the variables, then compressing them, then seeing if it can reconstruct them, but the values for, e.g., vaccine intentions are used to create the compressed components that are used in the reconstruction, so it's not really an out-of-sample "prediction" in the same way that the bayesian network (or regression models) are doing.

### 2019-04-30 study2/load-study2-data.R
fix data processing for s2: filter out attention checks before scoring

@@ -1,8 +1,15 @@
-# load data for study 3
+# load data for study 2
 # Kara's code
 
 library(tidyverse)
-d_all <- read.csv("../data/study2_data.csv")[-1]
+d_all <- read.csv("study2_data.csv")[-1] %>%
+  # filter out anyone who failed attention checks
+  filter(hb_check_5_pretest == 1, hb_check_5_posttest == 1,
+         vaccEff_check_1_pretest == -3, vaccEff_check_1_posttest == -3, 
+         vaccDanger_check_3_pretest == -1, vaccDanger_check_3_posttest == -1, 
+         vaccTox_check_6_pretest == 2, vaccTox_check_6_posttest ==2) %>%
+  # remove attention checks from dataset
+  select(-contains("check"))
 
 # reformat to match previous analyses (i.e., 2 rows per participant)
 d_demo <- d_all %>% 
@@ -12,6 +19,7 @@ d_demo <- d_all %>%
          children_youngest_posttest, plan_parent_posttest,
          starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
          starts_with("comments"), starts_with("duration"))
+
 d_pre <- d_all %>% 
   select(workerId, ends_with("_pretest")) %>%
   select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
@@ -19,6 +27,7 @@ d_pre <- d_all %>%
             starts_with("duration"))) %>%
   rename_all(funs(gsub("_pretest", "", .))) %>%
   mutate(phase = "pre")
+
 d_post <- d_all %>% 
   select(workerId, ends_with("_posttest")) %>%
   select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
@@ -46,7 +55,6 @@ d <- bind_rows(d_pre, d_post) %>%
   mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
   filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
   distinct()
-
 
 # score all scales
 d_scored <- d %>%

### 2019-04-30 study2/load-study2-data.R
fix filepath

@@ -2,7 +2,7 @@
 # Kara's code
 
 library(tidyverse)
-d_all <- read.csv("study2_data.csv")[-1] %>%
+d_all <- read.csv("../data/study2_data.csv")[-1] %>%
   # filter out anyone who failed attention checks
   filter(hb_check_5_pretest == 1, hb_check_5_posttest == 1,
          vaccEff_check_1_pretest == -3, vaccEff_check_1_posttest == -3, 

### 2019-04-30 study2/vacc_manyBelief_study2_analysis.Rmd
source fixed data loading script

@@
 
+```{r}
+source("./load-study2-data.R")
+```
+
 ```{r tidy, include = F}
-# load data
-d_all <- read.csv("../data/study2_data.csv")[-1]
-
-# reformat to match previous analyses (i.e., 2 rows per participant)
-d_demo <- d_all %>% 
-  select(workerId, condition, gender, age, ethnicity, education, job, income,
-         political_party, political_beliefs, eligible_pretest, 
-         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
-         children_youngest_posttest, plan_parent_posttest,
-         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
-         starts_with("comments"), starts_with("duration"))
-d_pre <- d_all %>% 
-  select(workerId, ends_with("_pretest")) %>%
-  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
-            starts_with("attention_"), starts_with("comments"), 
-            starts_with("duration"))) %>%
-  rename_all(funs(gsub("_pretest", "", .))) %>%
-  mutate(phase = "pre")
-d_post <- d_all %>% 
-  select(workerId, ends_with("_posttest")) %>%
-  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
-            children_youngest_posttest, plan_parent_posttest,
-            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
-            starts_with("comments"), starts_with("duration"))) %>%
-  rename_all(funs(gsub("_posttest", "", .))) %>%
-  mutate(phase = "post")
-
-d <- bind_rows(d_pre, d_post) %>% 
-  gather(question, response, -c(workerId, phase)) %>%
-  mutate(phase = factor(phase,
-                        levels = c("pre", "post")),
-         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
-         # NOTE: "response" has already been reverse coded!
-         question = factor(question),
-         scale = factor(gsub("_.*$", "", question),
-                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
-                                   "vaccStrain", "vaccTox", 
-                                   "diseaseSevere", "diseaseRare", 
-                                   "infantImmLimCap", "infantImmWeak", 
-                                   "medSkept", "hb", "nat", 
-                                   "overpar", "parentExpert"))) %>%
-  full_join(d_demo) %>%
-  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
-  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
-  distinct()
-
 # how many left?
 d %>% distinct(workerId, condition) %>% count(condition)
-```
-
-```{r scores, include = F}
-# score all scales
-d_scored <- d %>%
-  select(workerId, condition, phase, scale, response,
-         gender:duration_posttest) %>%
-  group_by(workerId, condition, phase, scale) %>%
-  mutate(response = as.numeric(response)) %>%
-  summarise(mean = mean(response, na.rm = TRUE)) %>%
-  ungroup() %>%
-  distinct()
 ```
@@
 library(brms)
-fit_ord <- cbrm(response ~ condition * phase + (1|workerId) + (1|question),
-               data = d %>%
-                    filter(scale=="vaccIntent") %>%
-                    mutate(
-                      condition = relevel(condition, ref="noInterv"),
-                      response = response + 4),
-               family=cumulative(),
-               control = list(adapt_delta = .85),
-               cores = parallel::detectCores(),
-               iter = 2000,
-               cached_file = "fit_ord.rds")
-summary(fit_ord)
+# fit_ord <- cbrm(response ~ condition * phase + (1|workerId) + (1|question),
+#                data = d %>%
+#                     filter(scale=="vaccIntent") %>%
+#                     mutate(
+#                       condition = relevel(condition, ref="noInterv"),
+#                       response = response + 4),
+#                family=cumulative(),
+#                control = list(adapt_delta = .85),
+#                cores = parallel::detectCores(),
+#                iter = 2000)
+#                # cached_file = "fit_ord.rds")
+# summary(fit_ord)
 ```
@@
 ```{r}
-fit_ord2 <- cbrm(post ~ condition + preMean + (1|workerId) + (1|question),
-               data=d1,
-               family=cumulative(),
-               control = list(adapt_delta = .85),
-               cores = parallel::detectCores(),
-               iter = 2000,
-               cached_file = "fit_ord2.rds")
-summary(fit_ord2)
+# fit_ord2 <- cbrm(post ~ condition + preMean + (1|workerId) + (1|question),
+#                data=d1,
+#                family=cumulative(),
+#                control = list(adapt_delta = .85),
+#                cores = parallel::detectCores(),
+#                iter = 2000)
+#                # cached_file = "fit_ord2.rds")
+# summary(fit_ord2)
 ```

### 2019-04-30 scripts/load-data-s2.R
remove redundant script

@@ -1,8 +1,15 @@
-# load data for study 3
+# load data for study 2
 # Kara's code
 
 library(tidyverse)
-d_all <- read.csv("../data/study2_data.csv")[-1]
+d_all <- read.csv("../data/study2_data.csv")[-1] %>%
+  # filter out anyone who failed attention checks
+  filter(hb_check_5_pretest == 1, hb_check_5_posttest == 1,
+         vaccEff_check_1_pretest == -3, vaccEff_check_1_posttest == -3, 
+         vaccDanger_check_3_pretest == -1, vaccDanger_check_3_posttest == -1, 
+         vaccTox_check_6_pretest == 2, vaccTox_check_6_posttest ==2) %>%
+  # remove attention checks from dataset
+  select(-contains("check"))
 
 # reformat to match previous analyses (i.e., 2 rows per participant)
 d_demo <- d_all %>% 
@@ -12,6 +19,7 @@ d_demo <- d_all %>%
          children_youngest_posttest, plan_parent_posttest,
          starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
          starts_with("comments"), starts_with("duration"))
+
 d_pre <- d_all %>% 
   select(workerId, ends_with("_pretest")) %>%
   select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
@@ -19,6 +27,7 @@ d_pre <- d_all %>%
             starts_with("duration"))) %>%
   rename_all(funs(gsub("_pretest", "", .))) %>%
   mutate(phase = "pre")
+
 d_post <- d_all %>% 
   select(workerId, ends_with("_posttest")) %>%
   select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
@@ -46,7 +55,6 @@ d <- bind_rows(d_pre, d_post) %>%
   mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
   filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
   distinct()
-
 
 # score all scales
 d_scored <- d %>%

### 2019-04-30 study2/load-study2-data.R
re-add copy of study 2 data file, until all sourcing has been corrected

@@ -1,0 +1,67 @@
+# load data for study 2
+# Kara's code
+
+library(tidyverse)
+d_all <- read.csv("../data/study2_data.csv")[-1] %>%
+  # filter out anyone who failed attention checks
+  filter(hb_check_5_pretest == 1, hb_check_5_posttest == 1,
+         vaccEff_check_1_pretest == -3, vaccEff_check_1_posttest == -3, 
+         vaccDanger_check_3_pretest == -1, vaccDanger_check_3_posttest == -1, 
+         vaccTox_check_6_pretest == 2, vaccTox_check_6_posttest ==2) %>%
+  # remove attention checks from dataset
+  select(-contains("check"))
+
+# reformat to match previous analyses (i.e., 2 rows per participant)
+d_demo <- d_all %>% 
+  select(workerId, condition, gender, age, ethnicity, education, job, income,
+         political_party, political_beliefs, eligible_pretest, 
+         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
+         children_youngest_posttest, plan_parent_posttest,
+         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
+         starts_with("comments"), starts_with("duration"))
+
+d_pre <- d_all %>% 
+  select(workerId, ends_with("_pretest")) %>%
+  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
+            starts_with("attention_"), starts_with("comments"), 
+            starts_with("duration"))) %>%
+  rename_all(funs(gsub("_pretest", "", .))) %>%
+  mutate(phase = "pre")
+
+d_post <- d_all %>% 
+  select(workerId, ends_with("_posttest")) %>%
+  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
+            children_youngest_posttest, plan_parent_posttest,
+            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
+            starts_with("comments"), starts_with("duration"))) %>%
+  rename_all(funs(gsub("_posttest", "", .))) %>%
+  mutate(phase = "post")
+
+d <- bind_rows(d_pre, d_post) %>% 
+  gather(question, response, -c(workerId, phase)) %>%
+  mutate(phase = factor(phase,
+                        levels = c("pre", "post")),
+         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
+         # NOTE: "response" has already been reverse coded!
+         question = factor(question),
[…]

### 2019-04-30 study2/vacc_manyBelief_study2_overpar.Rmd
update sourcing for loading study 2 data

@@
 ```{r tidy, include = F}
-# load data
-d_all <- read.csv("../data/study2_data.csv")[-1]
-
-# reformat to match previous analyses (i.e., 2 rows per participant)
-d_demo <- d_all %>% 
-  select(workerId, condition, gender, age, ethnicity, education, job, income,
-         political_party, political_beliefs, eligible_pretest, 
-         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
-         children_youngest_posttest, plan_parent_posttest,
-         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
-         starts_with("comments"), starts_with("duration"))
-d_pre <- d_all %>% 
-  select(workerId, ends_with("_pretest")) %>%
-  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
-            starts_with("attention_"), starts_with("comments"), 
-            starts_with("duration"))) %>%
-  rename_all(funs(gsub("_pretest", "", .))) %>%
-  mutate(phase = "pre")
-d_post <- d_all %>% 
-  select(workerId, ends_with("_posttest")) %>%
-  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
-            children_youngest_posttest, plan_parent_posttest,
-            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
-            starts_with("comments"), starts_with("duration"))) %>%
-  rename_all(funs(gsub("_posttest", "", .))) %>%
-  mutate(phase = "post")
-
-d <- bind_rows(d_pre, d_post) %>% 
-  gather(question, response, -c(workerId, phase)) %>%
-  mutate(phase = factor(phase,
-                        levels = c("pre", "post")),
-         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
-         # NOTE: "response" has already been reverse coded!
-         question = factor(question),
-         scale = factor(gsub("_.*$", "", question),
-                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
-                                   "vaccStrain", "vaccTox", 
-                                   "diseaseSevere", "diseaseRare", 
-                                   "infantImmLimCap", "infantImmWeak", 
-                                   "medSkept", "hb", "nat", 
-                                   "overpar", "parentExpert"))) %>%
-  full_join(d_demo) %>%
-  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
-  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
-  distinct()
-
-# how many left?
-# d %>% distinct(workerId, condition) %>% count(condition)
-```
-
-```{r scores, include = F}
-# score all scales
-d_scored <- d %>%
-  select(workerId, condition, phase, scale, response,
-         gender:duration_posttest) %>%
-  group_by(workerId, condition, phase, scale) %>%
-  mutate(response = as.numeric(response)) %>%
-  summarise(mean = mean(response, na.rm = TRUE)) %>%
-  ungroup() %>%
-  distinct()
+source("../scripts/load-data-s2.R")
 ```
@@
 ```{r}
-fit_pre <- brm(
-  vaccIntent ~ overpar * medSkept * diseaseSevere + (1|workerId),
-  prior = set_prior("normal(0,.5)", class = "b"),
-  family = Beta(),
-  data = d_bn %>% 
-    mutate(vaccIntent = rescale_beta(vaccIntent, -3, 3), workerId = 1:nrow(d_bn)),
-  control = list(adapt_delta = .90, max_treedepth = 15),
-  chains = 2,
-  cores = 2
-)
+# fit_pre <- brm(
+#   vaccIntent ~ overpar * medSkept * diseaseSevere + (1|workerId),
+#   prior = set_prior("normal(0,.5)", class = "b"),
+#   family = Beta(),
+#   data = d_bn %>% 
+#     mutate(vaccIntent = rescale_beta(vaccIntent, -3, 3), workerId = 1:nrow(d_bn)),
+#   control = list(adapt_delta = .90, max_treedepth = 15),
+#   chains = 2,
+#   cores = 2
+# )
 ```
@@
 ```{r}
-summary(fit_pre)
+# summary(fit_pre)
 ```

### 2019-04-30 study2/vmb_model_preds.Rmd
update sourcing for loading study 2 data

@@
 ```{r load and tidy study 3 data, include = F}
-# load data
-d_all <- read.csv("../data/study2_data.csv")
-
-# reformat to match previous analyses (i.e., 2 rows per participant)
-d_demo <- d_all %>% 
-  select(workerId, condition, gender, age, ethnicity, education, job, income,
-         political_party, political_beliefs, eligible_pretest, 
-         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
-         children_youngest_posttest, plan_parent_posttest,
-         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
-         starts_with("comments"), starts_with("duration"))
-d_pre <- d_all %>% 
-  select(workerId, ends_with("_pretest")) %>%
-  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
-            starts_with("attention_"), starts_with("comments"), 
-            starts_with("duration"))) %>%
-  rename_all(funs(gsub("_pretest", "", .))) %>%
-  mutate(phase = "pre")
-d_post <- d_all %>% 
-  select(workerId, ends_with("_posttest")) %>%
-  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
-            children_youngest_posttest, plan_parent_posttest,
-            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
-            starts_with("comments"), starts_with("duration"))) %>%
-  rename_all(funs(gsub("_posttest", "", .))) %>%
-  mutate(phase = "post")
-
-d <- bind_rows(d_pre, d_post) %>% 
-  gather(question, response, -c(workerId, phase)) %>%
-  mutate(phase = factor(phase,
-                        levels = c("pre", "post")),
-         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
-         # NOTE: "response" has already been reverse coded!
-         question = factor(question),
-         scale = factor(gsub("_.*$", "", question),
-                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
-                                   "vaccStrain", "vaccTox", 
-                                   "diseaseSevere", "diseaseRare", 
-                                   "infantImmLimCap", "infantImmWeak", 
-                                   "medSkept", "hb", "nat", 
-                                   "overpar", "parentExpert"))) %>%
-  full_join(d_demo) %>%
-  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
-  filter(!is.na(response), !is.na(workerId), !is.na(condition)) %>%
-  distinct()
-
-# how many left?
-d %>% distinct(workerId, condition) %>% count(condition)
-
-# score all scales
-d_scored <- d %>%
-  select(workerId, condition, phase, scale, response,
-         gender:duration_posttest) %>%
-  group_by(workerId, condition, phase, scale) %>%
-  mutate(response = as.numeric(response)) %>%
-  summarise(Mean = mean(response, na.rm = TRUE)) %>%
-  ungroup() %>%
-  distinct()
+source("../scripts/load-data-s2.R")
 

### 2019-04-30 notebooks/s1s2-pca-analysis.Rmd
re-run

@@
   group_by(scale) %>%
-  summarize(correlation = cor(predicted, observed))
+  summarise(correlation = cor(predicted, observed))
 
@@
   group_by(scale) %>%
-  summarize(meanChange = mean(change))
+  summarise(meanChange = mean(change))
 
@@
   group_by(scale) %>%
-  summarize(posttest = mean(response)) %>%
+  summarise(posttest = mean(response)) %>%
   left_join(
@@
   group_by(scale) %>%
-  summarize(pretest = mean(response))
+  summarise(pretest = mean(response))
     ), by = "scale"

### 2019-04-30 notebooks/s2-analysis.Rmd
re-run

@@
 ```{r}
-devtools::source_gist(id = "f1994c0f8325abbc5d300600744af39d", filename="cbrm.R")
-
-library(brms)
-fit_ord <- cbrm(response ~ condition * phase + (1|workerId) + (1|question),
-               data = d %>%
-                    filter(scale=="vaccIntent") %>%
-                    mutate(
-                      condition = relevel(condition, ref="noInterv"),
-                      response = response + 4),
-               family=cumulative(),
-               control = list(adapt_delta = .85),
-               cores = parallel::detectCores(),
-               iter = 2000,
-               cached_file = "fit_ord.rds")
-summary(fit_ord)
+# devtools::source_gist(id = "f1994c0f8325abbc5d300600744af39d", filename="cbrm.R")
+# 
+# library(brms)
+# fit_ord <- cbrm(response ~ condition * phase + (1|workerId) + (1|question),
+#                data = d %>%
+#                     filter(scale=="vaccIntent") %>%
+#                     mutate(
+#                       condition = relevel(condition, ref="noInterv"),
+#                       response = response + 4),
+#                family=cumulative(),
+#                control = list(adapt_delta = .85),
+#                cores = parallel::detectCores(),
+#                iter = 2000,
+#                cached_file = "fit_ord.rds")
+# summary(fit_ord)
 ```
@@
 ```{r}
-fit_ord2 <- cbrm(post ~ condition + preMean + (1|workerId) + (1|question),
-               data=d1,
-               family=cumulative(),
-               control = list(adapt_delta = .85),
-               cores = parallel::detectCores(),
-               iter = 2000,
-               cached_file = "fit_ord2.rds")
-summary(fit_ord2)
+# fit_ord2 <- cbrm(post ~ condition + preMean + (1|workerId) + (1|question),
+#                data=d1,
+#                family=cumulative(),
+#                control = list(adapt_delta = .85),
+#                cores = parallel::detectCores(),
+#                iter = 2000,
+#                cached_file = "fit_ord2.rds")
+# summary(fit_ord2)
 ```

### 2019-08-08 notebooks/cross-study-analysis-ucitalk.Rmd
before paper reorg

---
title: "R Notebook"
output: html_notebook
---

The relevant [NY Times front page article](https://www.nytimes.com/2019/04/29/health/measles-outbreak-cdc.html).

```{r}
# # load s1 data (original cogsci dataset)
source("../scripts/load-data-s1.R")

s1 <- d_sum %>%
  rename(scale = question_block) %>%
  group_by(scale, workerId) %>% 
  summarize(s1 = mean(score, na.rm = T)) %>%
  ungroup()

# load s2 data (disease risk intervention)
source("../scripts/load-data-s2.R")

s2 <- d_scored %>%
  # rename(subid = workerId) %>%
  filter(phase == "pre") %>% 
  group_by(scale, workerId) %>% 
  summarize(s2 = mean(mean, na.rm = T)) %>%
  ungroup()

# load S3 data (vaccine toxin intervention)

source("../scripts/load-data-s3.R")

s3 <- df_scored %>%
  # rename(subid = workerId) %>%
  group_by(scale, workerId) %>% 
  summarize(s3 = mean(pre, na.rm = T) - 4) %>% # put on -3, 3 scale
  ungroup()

source("../scripts/load-data-s4.R")

s4 <- df4 %>%
  mutate(prior_study = case_when(
    workerId %in% s1$workerId ~ "S1",
    workerId %in% s3$workerId ~ "S3",
    TRUE ~ "None"
  )) %>%
  mutate(resp = resp-4) %>%
  filter(prior_study != "S3") %>% # exclude Ps from s3, some of whom saw intervention
  group_by(scale, workerId) %>%
  summarize(s4 = mean(resp))
```

```{r}
# merge dataframes

df_studies <-  s1 %>%
  full_join(s2) %>%
  # full_join(s3) %>%
  full_join(s4) %>%
  gather(study, score, -c(workerId, scale)) %>%
  filter(!is.na(study), !is.na(score)) %>%
  group_by(scale) %>%
  mutate(score_std = scale(score, scale = T)) %>%
  ungroup()
```

## Changes across studies

```{r}
studies_plot <- df_studies %>%
  group_by(study, scale) %>%
  summarize(
    mean = mean(score),
    se = sd(score)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(study = ordered(study, labels=c("S1\n(9/17)", "S2\n(5/18)","S3\n(5/19)"))) %>%
  mutate(scale = recode_factor(
    scale,
    "vaccIntent" = "Vaccination\nIntentions",
    "nat" = "Naturalism",
    "hb" = "Holistic Balance",
    "overpar" = "Parental\nProtectiveness",
    "parentExpert" = "Parental Expertise",
    "medSkept" = "Medical Skepticism",
    "vaccDanger" = "Vaccine Danger",
    "vaccTox" = "Vaccine Toxicity",
    "vaccEff" = "Vaccine Efficacy",
    "diseaseRare" = "Disease Rarity",
    "diseaseSevere" = "Disease Severity",
    "infantImmWeak" = "IIS:\nWeakness",
    "infantImmLimCap" = "IIS:\nLimited Capacity",
    "vaccStrain" = "IIS:\nVaccines Strain")) %>%
  ggplot(aes(x=study, y = mean, ymin =ll, ymax=ul)) +
  # geom_pointrange() +
  geom_point(size=2.5, shape=16) +
  geom_errorbar(size=1, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, alpha=.5) +
  facet_wrap(~scale, scales="free", nrow = 2) +
  theme_bw(base_size = 16) +
  theme(
    # legend.position = "bottom",
    # axis.text.x = element_text(size=8),
    panel.grid = element_blank()
        ) +
  labs(y="Mean Resposne", x = "Study")

ggsave("../local/uci-longitudinal-averages.png",studies_plot, height=8, width=16)
```

Model changes across studies: I'm going to make a beta regression model with study as the predictor

```{r}
library(betareg)
library(brms)

rescale_beta <- function(x, lower, upper) {
  # rescales onto the open interval (0,1)
  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"

  N <- length(x)
  res <- (x - lower) / (upper - lower)
  res <- (res * (N - 1) + .5) / N

  return(as.vector(res))
}

fit <- betareg(score ~ study,
               data = df_studies %>%
                 filter(scale =="vaccIntent") %>%
                 mutate(score = rescale_beta(score,-3,3))
               )

summary(fit)

# fit_brm <- brm(
#   score ~ study,
#   data = df_studies %>%
#                  filter(scale =="vaccIntent") %>%
#                  mutate(score = rescale_beta(score,-3,3)),
#   family = Beta("logit"),
#   prior = prior(normal(0,1), class="b"),
#   iter = 2000,
#   warmup = 1000,
#   chains = 1,
#   cores = 1
# )

```

## Within-subjects test

let's focus on the clearest test of whether and how opinions have changed, a within-subjects comparison among our re-recruited participants. These are participants who completed all 14 scales over 18 months ago, and are now returning and completing them all again.

```{r}
combined <- df4  %>%
  filter(workerId %in% s1$workerId) %>%
  select(workerId, scale, item, resp) %>%
  group_by(workerId,scale) %>%
  summarize(posttest = mean(resp)-4) %>%
  right_join(s1) %>%
  rename(pretest = s1) %>%
  mutate(returned = !is.na(posttest))

# combined %>%
#   filter(returned == TRUE) %>%
#   ggplot(aes(x=pretest, y=posttest)) +
#   geom_jitter(alpha=.5) +
#   facet_wrap(~scale) +
#   theme_bw()

combined_long <- combined %>%
  gather(phase, resp, pretest, posttest)

combined_long %>%
  group_by(returned, phase, scale) %>%
  summarize(
    mean = mean(resp),
    se = sd(resp)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(scale = recode_factor(
  scale,
  "vaccIntent" = "Vaccination Intentions",
  "nat" = "Naturalism",
  "hb" = "Holistic Balance",
  "overpar" = "Parental Protectiveness",
  "parentExpert" = "Parental Expertise",
  "medSkept" = "Medical Skepticism",
  "vaccDanger" = "Vaccine Danger",
  "vaccTox" = "Vaccine Toxicity",
  "vaccEff" = "Vaccine Efficacy",
  "diseaseRare" = "Disease Rarity",
  "diseaseSevere" = "Disease Severity",
  "infantImmWeak" = "IIS: Weakness",
  "infantImmLimCap" = "IIS: Limited Capacity",
  "vaccStrain" = "IIS: Vaccines Strain")) %>%
  mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=phase, y = mean, ymin =ll, ymax=ul, color=returned)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  facet_wrap(~scale, scales="free") +
  theme_bw(base_size=18)

change_plot <- combined %>%
  filter(returned==TRUE) %>%
  mutate(diff = posttest-pretest) %>%
  mutate(scale = recode_factor(
    scale,
    "vaccIntent" = "Vaccination Intentions",
    "nat" = "Naturalism",
    "hb" = "Holistic Balance",
    "overpar" = "Parental Protectiveness",
    "parentExpert" = "Parental Expertise",
    "medSkept" = "Medical Skepticism",
    "vaccDanger" = "Vaccine Danger",
    "vaccTox" = "Vaccine Toxicity",
    "vaccEff" = "Vaccine Efficacy",
    "diseaseRare" = "Disease Rarity",
    "diseaseSevere" = "Disease Severity",
    "infantImmWeak" = "IIS: Weakness",
    "infantImmLimCap" = "IIS: Limited Capacity",
    "vaccStrain" = "IIS: Vaccines Strain")) %>%
  group_by(scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, -mean), y = mean, ymin =ll, ymax=ul)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  # facet_wrap(~scale, scales="free") +
  theme_bw(base_size = 18) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(
    panel.grid = element_blank()
        ) +
  labs(y = "Change scores", x = "Belief scale")

ggsave("../local/uci-longitudinal-changescores.png",change_plot, height=6, width=8)
```

```{r}
# diff_df <- combined %>% 
#   group_by(scale) %>% 
#   summarize(posttest = mean(posttest, na.rm=TRUE), 
#             pretest=mean(pretest)) %>% 
#   mutate(diff = posttest-pretest)

diff_df <- combined %>%
  filter(returned == TRUE) %>%
  mutate(difference = posttest-pretest) %>%
  group_by(scale) %>%
  summarize(diff = mean(difference), se = sd(difference)/sqrt(n()))

diff_df
```

Have vaccine intentions increased within subjects from 18 months ago? YES.

We could test this with a t-test, but I think it might be better to use a somewhat more sophisticated model. I'm going to test for differences across phases using beta regression. (I'm using "pretest" and "posttest" even though that's not qutie accurate, there was no intervention)

```{r}
t.test(resp ~ phase, data = combined_long %>% filter(returned, scale=="vaccIntent"), paired=TRUE)
```

```{r}

library(betareg)

fit <- betareg(resp ~ phase, data = combined_long %>% 
                 mutate(resp = rescale_beta(resp, -3, 3)) %>%
                 filter(scale=="vaccEff")
               )

summary(fit)
```

Do changes relate to media consumpion? (keeping in mind that's a noisy measure ...)

Yes, for our binary yes/no response variable, but no for our news frequency scale (Could try monotonic effects -- not seeing it at all vs seeing it is a much bigger difference than seeing it once vs twice, etc)

```{r}

df_prepost_news <- df4 %>%
  filter(workerId %in% s1$workerId) %>%
  select(workerId, scale, item, resp, 
         vacc_news, vacc_news_freq, news_favorable, outbreaks, vacc_conv
         ) %>%
  group_by(workerId,scale,vacc_news, vacc_news_freq, news_favorable, outbreaks, vacc_conv ) %>%
  summarize(posttest = mean(resp)-4) %>%
  left_join(s1) %>%
  rename(pretest = s1) %>%
  mutate(returned = !is.na(posttest)) %>%
  ungroup() %>%
  mutate(vacc_news_freq = ifelse(vacc_news==0, 0.0, vacc_news_freq))

fit <- betareg(
  posttest ~ pretest + vacc_news,
  data = df_prepost_news %>%
  filter(scale =="vaccIntent") %>%
  mutate(posttest = rescale_beta(posttest,-3,3))
)

summary(fit)
```

## Participants who saw news

```{r}
df_prepost_news %>%
  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
  mutate(diff = posttest-pretest) %>%
  mutate(vacc_news = as.factor(vacc_news)) %>%
  group_by(vacc_news,scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  # facet_wrap(~scale, scales="free") +
  theme_bw(base_size = 18) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "right") +
  labs(y = "Change scores", x = "Belief scale", color ="News\nexposure")

```

Are the changes coherent? What is driving the changes?

Let's see how they correlate imagining all changes are driven by different beliefs (these are approximations of what model will predict)

```{r message=F}
cors <- cor(d_bn)

# for (s in colnames(d_bn)){
#   
#   cors_df <- tibble(scale = names(cors[s,]), w = cors[s,])
#   
#   z <- cors_df %>% 
#   left_join(diff_df) %>%
#   mutate(pred_diff = w * diff_df[diff_df$scale==s,"diff"][[1]]) 
#   
#   print( paste(s,":",cor(z$pred_diff, z$diff)) )
# }

check_cor <- function(s){
  cors_df <- tibble(scale = names(cors[s,]), w = cors[s,])

  z <- cors_df %>% 
  left_join(diff_df) %>%
  mutate(pred_diff = w * diff_df[diff_df$scale==s,"diff"][[1]])

  return(cor(z$pred_diff, z$diff))
}

change_cors <- tibble(scale = colnames(d_bn), corr = map_dbl(scale, check_cor))

change_cors %>%
  ggplot(aes(y=reorder(scale, corr), x = corr)) +
  geom_point() +
  theme_bw(base_size=18) +
  theme(aspect.ratio=1) +
  theme(panel.grid = element_blank())
  labs(y="Scale", x = "Correlation")
```

Now, imagine it's a direct increase in intention to vaccinate ...

```{r}

targetted_belief <- "vaccIntent"

cors_df <- tibble(scale = names(cors[targetted_belief,]), w = cors[targetted_belief,])

z <- cors_df %>% 
left_join(diff_df) %>%
mutate(pred_diff = w * diff_df[diff_df$scale==targetted_belief,"diff"][[1]])

plot_cohere <- z %>%
  ggplot(aes(x=pred_diff, y=diff, ymin=diff-1.96*se, ymax=diff+1.96*se)) +
  geom_errorbar(width=0, color="grey") +
  geom_point() +
  geom_abline(intercept = 0, slope=1, linetype="dashed",alpha=.5) +
  theme_bw(base_size=18) +
  theme(aspect.ratio=1) +
  coord_cartesian(xlim=c(-.32,.32), ylim=c(-.32,.32)) +
  theme(panel.grid=element_blank()) +
  labs(x="Predicted change",y="Observed change")

# ggsave("../local/uci-talk-cohere.png", width=4, height=4)
cor(z$pred_diff, z$diff)
plot_cohere
```

That's a strong correlation!

# Actually predicting using the model ...

```{r}
## WARNING: THIS CODE IS HACKY!
## 
## script for generating model predictions based on vaccine toxins intervention
## run:
## int-theory-vacc/notebooks/s2-modeling.Rmd (to line 495)
##
## then run this notebook, and finally this code:

d_scored_longitudinal <- combined_long %>%
  filter(returned==TRUE) %>%
  mutate(resp = rescale_beta(resp, -3, 3)) %>%
  group_by(phase, scale) %>%
  summarize(mean = mean(resp)) %>%
  spread(phase,mean) %>%
  rename(pre = pretest, post = posttest)

# # update model fitting thing ignore control condition b/c of strange things in this data ...
find_evid_ratio <- function(data){
    optim(par = c(0), fn = evid_score_func, data = data, method="BFGS")
}
# find_evid_ratio <- function(data){
#   # HACK HACK HACK
#   return (data.frame(par = c(-.55, 7)))
# }
evid_score_func <- function(data, par) {

    inv_logit <- plogis
    logit <- qlogis

    pred_y <- with(data,
                   {
                       inv_logit( logit(pre) + par[1] )
                   }
    )

    # pred_beta_A <- pred_y * par[2]
    # pred_beta_B <- (1-pred_y) * par[2]

    # ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
    ll <- sum( (data$post-pred_y)^2 )
    return(ll)
}

get_evid_probs <- function(result){
  # this is a heuristic/hack, could be made better but probably doesn't matter
  evid_ratio <- exp(result$par[1])
  if (evid_ratio < 1) {
    p0 <- .90
  } else {
    p0 <- .5
  }

  if (p0*evid_ratio >= 1) {
    p0 <- p0*.9/(p0*evid_ratio)
  }
  p1 <- p0*evid_ratio

  c(p0,p1)
}

scale_name <- "vaccIntent"

predModel <- add_evid_node(d_scored_longitudinal %>% filter(scale==scale_name), base_model, scale_name)

pred0 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence=TRUE, n = 5e5)")
  eval(parse(text=statement))
})
pred1 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 5e5)")
  eval(parse(text=statement))
})
pred_changes <- pred1 - pred0
pred_changes <- as.data.frame(pred_changes)
pred_changes <- pred_changes %>%
  mutate(scale = nodes) %>%
  rename(Mean = pred_changes) %>%
  mutate(type = "predicted")

preds_obs <- d_scored_longitudinal %>%
  # spread(phase, mean) %>%
  mutate(change = post - pre) %>%
  group_by(scale) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes %>% rename(pred_mean = Mean), by = "scale")

preds_obs %>%
  rename(
    observed = Mean,
    predicted = pred_mean
  ) %>%
  gather(type, Mean, observed, predicted) %>%
  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
  geom_point()
```

```{r}
diff_df2 <- combined %>%
  filter(returned == TRUE) %>%
  mutate(
    posttest = rescale_beta(posttest, -3,3),
    pretest = rescale_beta(pretest, -3,3),
         ) %>%
  mutate(difference = posttest-pretest) %>%
  group_by(scale) %>%
  summarize(diff = mean(difference), se = sd(difference)/sqrt(n()))

plot_cohere <- diff_df2 %>%
  left_join(preds_obs %>% select(pred_mean, scale)) %>%
  ggplot(aes(x=pred_mean, y = diff, ymin = diff-1.96*se, ymax=diff+1.96*se)) +
  geom_errorbar(width=0, color="gray") +
  geom_point() +
  geom_abline(intercept=0,slope=1,alpha=.5,linetype="dashed") +
  theme_bw() +
  coord_cartesian(xlim=c(-.06,.06), ylim= c(-.06,.06)) +
  theme_bw(base_size=16) +
  theme(aspect.ratio=1, panel.grid=element_blank()) +
  labs(x = "Predicted change", y = "Observed change")

cor(preds_obs$Mean, preds_obs$pred_mean)

ggsave("../local/fb-talk-cohere.png", width=4, height=4)

pred_check <- preds_obs %>% filter(scale!=scale_name)
cor(pred_check$Mean, pred_check$pred_mean)

plot_cohere
```

```{r}
# plot_cohere <- preds_obs %>%
#   ggplot(aes(x=pred_mean, y = Mean, ymin = ll, ymax=ul)) +
#   geom_point() +
#   geom_errorbar(width=0) +
#   geom_abline(intercept=0,slope=1,alpha=.5,linetype="dashed") +
#   theme_bw() +
#   coord_cartesian(xlim=c(-.05,.05), ylim= c(-.05,.05)) +
#   theme_bw(base_size=16) +
#   theme(aspect.ratio=1, panel.grid=element_blank()) +
#   labs(x = "Predicted change", y = "Observed change")
# 
# cor(preds_obs$Mean, preds_obs$pred_mean)
# 
# # ggsave("../local/uci-talk-cohere.png", width=4, height=4)
# 
# pred_check <- preds_obs %>% filter(scale!=scale_name)
# cor(pred_check$Mean, pred_check$pred_mean)

# plot_cohere
```

```{r}
# needed for next section
base_model <- create_bnlearn_cog_model(map_dag, train)
```

```{r}
compare_pred_obs_r <- function(predicted, observed){

  obs_pred <- suppressWarnings(bind_rows(predicted, observed)) %>%
    spread(type, Mean) %>%
    group_by(scale) %>%
    summarize_all(mean, na.rm=TRUE)

  cor(obs_pred$predicted, obs_pred$observed)
}

compare_pred_obs_rmse <- function(predicted, observed){

  obs_pred <- suppressWarnings(bind_rows(predicted, observed)) %>%
    spread(type, Mean) %>%
    group_by(scale) %>%
    summarize_all(mean, na.rm=TRUE)

  sqrt(mean((obs_pred$observed-obs_pred$predicted)^2))

}

extract_obs_changes <- function(observed){
  obs_changes <- observed %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase,mean) %>%
  mutate(changeScore = posttest-pretest) %>%
  # filter(condition == "diseaseRisk") %>%
  group_by(scale) %>%
  summarise(
    Mean = mean(changeScore),
    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()), # replace with bootstrapping
    ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
    ) %>%
  mutate(type = "observed")

  return(obs_changes)
}

combined_long_diag <- combined_long %>%
  filter(returned) %>%
  rename(mean = resp)

filter_dscored <- function(data, scale_name){

  data %>%
  filter(scale == scale_name) %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase, mean) %>%
  # rename(pre=pretest, post=posttest)
  summarize(pre = mean(pretest), post=mean(posttest))
}

# -- takes about 1.5 hrs for 500 bootstrap samples

# do bootstrap comparison
set.seed(1234)
t1 <- Sys.time()

boot_fits <- as_tibble(expand.grid(
  list(
    replicate = 1:100, scale = nodes
  )
)) %>%
  nest(-replicate, .key="scales") %>%
  mutate(boot_d_scored = map(replicate, function(x) {
    totaln <- length(unique(combined_long_diag$workerId))
    combined_long_diag %>%
      nest(-workerId) %>%
      sample_n(totaln, replace = TRUE) %>%
      mutate(uniqueId = 1:totaln) %>%
      unnest()
  })) %>%
  unnest(scales, .drop=FALSE) %>%
  mutate(
      boot_d = map2(boot_d_scored, scale, function(x,y){filter_dscored(x, y)}),
      obs_changes = map(boot_d_scored, extract_obs_changes)
      ) %>%
  select(-boot_d_scored) %>%
  mutate(
    models = map2(boot_d, scale, function(x,y){add_evid_node(x, base_model, y)}),
    pred_changes = map(models, cogModel_predictions),
    r = map2_dbl(pred_changes, obs_changes, compare_pred_obs_r),
    rmse = map2_dbl(pred_changes, obs_changes, compare_pred_obs_rmse)
    )

print(Sys.time() - t1)
```

```{r}
# boot_fits %>%
#   mutate(r2 = r^2) %>%
#   ggplot(aes(x=reorder(scale,-r2), y = r2)) +
#   geom_boxplot(fill="lightgray") +
#   theme_bw() +
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
#   coord_flip()
  # theme(axis.text.x = element_text(angle = 90, hjust = 1))

diagnose_plot <- boot_fits %>%
  select(replicate, scale,r,rmse) %>%
  mutate(scale_order = r) %>%
  gather(meas, value, r, rmse) %>%
  mutate(meas = ifelse(meas=="rmse", "RMSE (lower is better)", "Correlation")) %>%
  mutate(meas = factor(meas, levels=c("RMSE (lower is better)", "Correlation"))) %>%
  mutate(scale = recode_factor(
  scale,
  "vaccIntent" = "Vaccination Intentions",
  "nat" = "Naturalism",
  "hb" = "Holistic Balance",
  "overpar" = "Parental Protectiveness",
  "parentExpert" = "Parental Expertise",
  "medSkept" = "Medical Skepticism",
  "vaccDanger" = "Vaccine Danger",
  "vaccTox" = "Vaccine Toxicity",
  "vaccEff" = "Vaccine Efficacy",
  "diseaseRare" = "Disease Rarity",
  "diseaseSevere" = "Disease Severity",
  "infantImmWeak" = "IIS: Weakness",
  "infantImmLimCap" = "IIS: Limited Capacity",
  "vaccStrain" = "IIS: Vaccines Strain")) %>%
  ggplot(aes(x=reorder(scale, scale_order), y = value)) +
  # geom_violin(fill="gray", alpha=.5) +
  geom_boxplot(fill = "lightgray") +
  facet_wrap(~meas, scales="free_x" ) +
  labs(x = "Belief", y = "Value") +
  theme_bw(base_size=16) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  coord_flip()

ggsave("../local/uci-talk-diagnose.png",width=6,height=3.5)

diagnose_plot

```

### 2019-08-08 notebooks/cross-study-analysis.Rmd
before paper reorg

--- 2019-08-08 notebooks/cross-study-analysis-ucitalk.Rmd
@@
 
+library(lubridate)
+
 s4 <- df4 %>%
@@
   mutate(resp = resp-4) %>%
-  filter(prior_study != "S3") %>% # exclude Ps from s3, some of whom saw intervention
+  filter(prior_study != "S3", 
+         StartDate < ymd_hms("2019-05-19:00:00:00")) %>% # exclude Ps from s3, some of whom saw intervention
+  # filter(prior_study == "None") %>% # Look only at fresh Ps
   group_by(scale, workerId) %>%
   summarize(s4 = mean(resp))
+
+s5 <- df4 %>%
+  mutate(resp = resp-4) %>%
+  filter(StartDate > ymd_hms("2019-05-19:00:00:00")) %>% # exclude Ps from s3, some of whom saw intervention
+  # filter(prior_study == "None") %>% # Look only at fresh Ps
+  group_by(scale, workerId) %>%
+  summarize(s5 = mean(resp))
 ```
@@
   full_join(s2) %>%
-  # full_join(s3) %>%
+  full_join(s3) %>%
   full_join(s4) %>%
+  full_join(s5) %>%
   gather(study, score, -c(workerId, scale)) %>%
@@
 ```{r}
-studies_plot <- df_studies %>%
+df_studies %>%
   group_by(study, scale) %>%
@@
   ungroup() %>%
-  mutate(study = ordered(study, labels=c("S1\n(9/17)", "S2\n(5/18)","S3\n(5/19)"))) %>%
-  mutate(scale = recode_factor(
-    scale,
-    "vaccIntent" = "Vaccination\nIntentions",
-    "nat" = "Naturalism",
-    "hb" = "Holistic Balance",
-    "overpar" = "Parental\nProtectiveness",
-    "parentExpert" = "Parental Expertise",
-    "medSkept" = "Medical Skepticism",
-    "vaccDanger" = "Vaccine Danger",
-    "vaccTox" = "Vaccine Toxicity",
-    "vaccEff" = "Vaccine Efficacy",
-    "diseaseRare" = "Disease Rarity",
-    "diseaseSevere" = "Disease Severity",
-    "infantImmWeak" = "IIS:\nWeakness",
-    "infantImmLimCap" = "IIS:\nLimited Capacity",
-    "vaccStrain" = "IIS:\nVaccines Strain")) %>%
+  mutate(study = ordered(study, 
+                         labels=c("S1\n(9/'17)", 
+                                  "S2\n(5/'18)", 
+                                  "S3\n(4/'19)", 
+                                  "S4\n(5/01)", 
+                                  "S5\n(5/20)")
+                         )
+         ) %>%
   ggplot(aes(x=study, y = mean, ymin =ll, ymax=ul)) +
-  # geom_pointrange() +
-  geom_point(size=2.5, shape=16) +
-  geom_errorbar(size=1, width=0, alpha=.8) +
-  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, alpha=.5) +
-  facet_wrap(~scale, scales="free", nrow = 2) +
-  theme_bw(base_size = 16) +
-  theme(
-    # legend.position = "bottom",
-    # axis.text.x = element_text(size=8),
-    panel.grid = element_blank()
-        ) +
-  labs(y="Mean Resposne", x = "Study")
+  geom_pointrange() +
+  facet_wrap(~scale, scales="free") +
+  theme_bw(base_size = 12) +
+  labs(y="Mean Response", x = "Study")
+```
 
-ggsave("../local/uci-longitudinal-averages.png",studies_plot, height=8, width=16)
+```{r}
+# important to recognize these are small changes in absolute terms ...
+df_studies %>%
+  ggplot(aes(x=study, y = score)) +
+  geom_violin(fill = "blue",color="white",alpha=.5, scale="width", draw_quantiles=c(.5)) +
+  facet_wrap(~scale, scales="free") +
+  theme_bw()
 ```
@@
 
-# combined %>%
-#   filter(returned == TRUE) %>%
-#   ggplot(aes(x=pretest, y=posttest)) +
-#   geom_jitter(alpha=.5) +
-#   facet_wrap(~scale) +
-#   theme_bw()
+combined %>%
+  filter(returned == TRUE) %>%
+  ggplot(aes(x=pretest, y=posttest)) +
+  geom_jitter(alpha=.5) +
+  facet_wrap(~scale) +
+  theme_bw()
 
@@
   ungroup() %>%
-  mutate(scale = recode_factor(
-  scale,
-  "vaccIntent" = "Vaccination Intentions",
-  "nat" = "Naturalism",
-  "hb" = "Holistic Balance",
-  "overpar" = "Parental Protectiveness",
-  "parentExpert" = "Parental Expertise",
-  "medSkept" = "Medical Skepticism",
-  "vaccDanger" = "Vaccine Danger",
-  "vaccTox" = "Vaccine Toxicity",
-  "vaccEff" = "Vaccine Efficacy",
-  "diseaseRare" = "Disease Rarity",
-  "diseaseSevere" = "Disease Severity",
-  "infantImmWeak" = "IIS: Weakness",
-  "infantImmLimCap" = "IIS: Limited Capacity",
-  "vaccStrain" = "IIS: Vaccines Strain")) %>%
   mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
@@
 
-change_plot <- combined %>%
+combined %>%
   filter(returned==TRUE) %>%
   mutate(diff = posttest-pretest) %>%
-  mutate(scale = recode_factor(
-    scale,
-    "vaccIntent" = "Vaccination Intentions",
-    "nat" = "Naturalism",
-    "hb" = "Holistic Balance",
-    "overpar" = "Parental Protectiveness",
-    "parentExpert" = "Parental Expertise",
-    "medSkept" = "Medical Skepticism",
-    "vaccDanger" = "Vaccine Danger",
-    "vaccTox" = "Vaccine Toxicity",
-    "vaccEff" = "Vaccine Efficacy",
-    "diseaseRare" = "Disease Rarity",
-    "diseaseSevere" = "Disease Severity",
-    "infantImmWeak" = "IIS: Weakness",
-    "infantImmLimCap" = "IIS: Limited Capacity",
-    "vaccStrain" = "IIS: Vaccines Strain")) %>%
   group_by(scale) %>%
@@
   # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
-  ggplot(aes(x=reorder(scale, -mean), y = mean, ymin =ll, ymax=ul)) +
+  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul)) +
   geom_point(position=position_dodge(width=.25), size=2, shape=16) +
@@
   theme_bw(base_size = 18) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  theme(
-    panel.grid = element_blank()
-        ) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   labs(y = "Change scores", x = "Belief scale")
-
-ggsave("../local/uci-longitudinal-changescores.png",change_plot, height=6, width=8)
 ```
@@
 ```{r}
-# diff_df <- combined %>% 
-#   group_by(scale) %>% 
-#   summarize(posttest = mean(posttest, na.rm=TRUE), 
-#             pretest=mean(pretest)) %>% 
-#   mutate(diff = posttest-pretest)
-
 diff_df <- combined %>% 
-  filter(returned == TRUE) %>%
-  mutate(difference = posttest-pretest) %>%
   group_by(scale) %>% 
-  summarize(diff = mean(difference), se = sd(difference)/sqrt(n()))
+  summarize(posttest = mean(posttest, na.rm=TRUE), 
+            pretest=mean(pretest)) %>% 
+  mutate(diff = posttest-pretest)
 
@@
   theme(aspect.ratio=1) +
-  theme(panel.grid = element_blank())
   labs(y="Scale", x = "Correlation")
@@
 
-plot_cohere <- z %>%
-  ggplot(aes(x=pred_diff, y=diff, ymin=diff-1.96*se, ymax=diff+1.96*se)) +
-  geom_errorbar(width=0, color="grey") +
+z %>%
+  ggplot(aes(x=pred_diff, y=diff)) +
   geom_point() +
-  geom_abline(intercept = 0, slope=1, linetype="dashed",alpha=.5) +
   theme_bw(base_size=18) +
   theme(aspect.ratio=1) +
-  coord_cartesian(xlim=c(-.32,.32), ylim=c(-.32,.32)) +
-  theme(panel.grid=element_blank()) +
-  labs(x="Predicted change",y="Observed change")
+  labs(x="Predicted change",y="Observed change", title=targetted_belief)
 
-# ggsave("../local/uci-talk-cohere.png", width=4, height=4)
 cor(z$pred_diff, z$diff)
-plot_cohere
 ```
@@
 
-# Actually predicting using the model ...
+# insepcting other ps
+
+For some reason our "fresh" participants don't look quite like our S1 and S3 participants.
+A difference between S3 participants seems plausible, but I don't see how they could meaningfully differ from S1 participants beyond by chance.
+I say that especially because returning and non-returning participants from S1 didn't look different across any of the scales.
 
 ```{r}
-## WARNING: THIS CODE IS HACKY!
-## 
-## script for generating model predictions based on vaccine toxins intervention
-## run:
-## int-theory-vacc/notebooks/s2-modeling.Rmd (to line 495)
-##
-## then run this notebook, and finally this code:
-
-d_scored_longitudinal <- combined_long %>%
-  filter(returned==TRUE) %>%
-  mutate(resp = rescale_beta(resp, -3, 3)) %>%
-  group_by(phase, scale) %>%
-  summarize(mean = mean(resp)) %>%
-  spread(phase,mean) %>%
-  rename(pre = pretest, post = posttest)
-
-# # update model fitting thing ignore control condition b/c of strange things in this data ...
-find_evid_ratio <- function(data){
-    optim(par = c(0), fn = evid_score_func, data = data, method="BFGS")
-}
-# find_evid_ratio <- function(data){
-#   # HACK HACK HACK
-#   return (data.frame(par = c(-.55, 7)))
-# }
-evid_score_func <- function(data, par) {
-
-    inv_logit <- plogis
-    logit <- qlogis
-
-    pred_y <- with(data,
-                   {
-                       inv_logit( logit(pre) + par[1] )
-                   }
-    )
-
-    # pred_beta_A <- pred_y * par[2]
-    # pred_beta_B <- (1-pred_y) * par[2]
-
-    # ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
-    ll <- sum( (data$post-pred_y)^2 )
-    return(ll)
-}
-
-get_evid_probs <- function(result){
-  # this is a heuristic/hack, could be made better but probably doesn't matter
-  evid_ratio <- exp(result$par[1])
-  if (evid_ratio < 1) {
-    p0 <- .90
-  } else {
-    p0 <- .5
-  }
-
-  if (p0*evid_ratio >= 1) {
-    p0 <- p0*.9/(p0*evid_ratio)
-  }
-  p1 <- p0*evid_ratio
-
-  c(p0,p1)
-}
-
-scale_name <- "vaccIntent"
-
-predModel <- add_evid_node(d_scored_longitudinal %>% filter(scale==scale_name), base_model, scale_name)
-
-pred0 <- sapply(nodes, function(x){
-  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence=TRUE, n = 5e5)")
-  eval(parse(text=statement))
-})
-pred1 <- sapply(nodes, function(x){
-  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 5e5)")
-  eval(parse(text=statement))
-})
-pred_changes <- pred1 - pred0
-pred_changes <- as.data.frame(pred_changes)
-pred_changes <- pred_changes %>%
-  mutate(scale = nodes) %>%
-  rename(Mean = pred_changes) %>%
-  mutate(type = "predicted")
-
-preds_obs <- d_scored_longitudinal %>%
-  # spread(phase, mean) %>%
-  mutate(change = post - pre) %>%
-  group_by(scale) %>%
-  summarize(
-    Mean = mean(change),
-    se = sd(change) / sqrt(n())
-  ) %>%
-  mutate(
-    ul = Mean + se,
-    ll = Mean - se
-  ) %>%
-  left_join(pred_changes %>% rename(pred_mean = Mean), by = "scale")
-
-preds_obs %>%
-  rename(
-    observed = Mean,
-    predicted = pred_mean
-  ) %>%
-  gather(type, Mean, observed, predicted) %>%
-  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
-  geom_point()
+df4 %>%
+  mutate(prior_study = case_when(
+    workerId %in% s1$workerId ~ "S1",
+    workerId %in% s3$workerId ~ "S3",
+    TRUE ~ "None"
+  )) %>%
+  mutate(resp = resp-4) %>%
+  # filter(prior_study != "S3") %>% # exclude Ps from s3, some of whom saw intervention
+  group_by(prior_study,scale, workerId) %>%
+  summarize(s4 = mean(resp)) %>%
+  group_by(prior_study, scale) %>%
+  summarize(Mean = mean(s4, na.rm=TRUE)) %>%
+  spread(prior_study, Mean)
 ```
-
-```{r}
-diff_df2 <- combined %>%
-  filter(returned == TRUE) %>%
-  mutate(
-    posttest = rescale_beta(posttest, -3,3),
-    pretest = rescale_beta(pretest, -3,3),
-         ) %>%
-  mutate(difference = posttest-pretest) %>%
-  group_by(scale) %>%
-  summarize(diff = mean(difference), se = sd(difference)/sqrt(n()))
-
-plot_cohere <- diff_df2 %>%
-  left_join(preds_obs %>% select(pred_mean, scale)) %>%
-  ggplot(aes(x=pred_mean, y = diff, ymin = diff-1.96*se, ymax=diff+1.96*se)) +
-  geom_errorbar(width=0, color="gray") +
-  geom_point() +
-  geom_abline(intercept=0,slope=1,alpha=.5,linetype="dashed") +
-  theme_bw() +
-  coord_cartesian(xlim=c(-.06,.06), ylim= c(-.06,.06)) +
-  theme_bw(base_size=16) +
-  theme(aspect.ratio=1, panel.grid=element_blank()) +
-  labs(x = "Predicted change", y = "Observed change")
-
-cor(preds_obs$Mean, preds_obs$pred_mean)
-
-ggsave("../local/fb-talk-cohere.png", width=4, height=4)
-
-pred_check <- preds_obs %>% filter(scale!=scale_name)
-cor(pred_check$Mean, pred_check$pred_mean)
-
-plot_cohere
-```
-
-```{r}
-# plot_cohere <- preds_obs %>%
-#   ggplot(aes(x=pred_mean, y = Mean, ymin = ll, ymax=ul)) +
-#   geom_point() +
-#   geom_errorbar(width=0) +
-#   geom_abline(intercept=0,slope=1,alpha=.5,linetype="dashed") +
-#   theme_bw() +
-#   coord_cartesian(xlim=c(-.05,.05), ylim= c(-.05,.05)) +
-#   theme_bw(base_size=16) +
-#   theme(aspect.ratio=1, panel.grid=element_blank()) +
-#   labs(x = "Predicted change", y = "Observed change")
-# 
-# cor(preds_obs$Mean, preds_obs$pred_mean)
-# 
-# # ggsave("../local/uci-talk-cohere.png", width=4, height=4)
-# 
-# pred_check <- preds_obs %>% filter(scale!=scale_name)
-# cor(pred_check$Mean, pred_check$pred_mean)
-
-# plot_cohere
-```
-
-```{r}
-# needed for next section
-base_model <- create_bnlearn_cog_model(map_dag, train)
-```
-
-```{r}
-compare_pred_obs_r <- function(predicted, observed){
-
-  obs_pred <- suppressWarnings(bind_rows(predicted, observed)) %>%
-    spread(type, Mean) %>%
-    group_by(scale) %>%
-    summarize_all(mean, na.rm=TRUE)
-
-  cor(obs_pred$predicted, obs_pred$observed)
-}
-
-compare_pred_obs_rmse <- function(predicted, observed){
-
-  obs_pred <- suppressWarnings(bind_rows(predicted, observed)) %>%
-    spread(type, Mean) %>%
-    group_by(scale) %>%
-    summarize_all(mean, na.rm=TRUE)
-
-  sqrt(mean((obs_pred$observed-obs_pred$predicted)^2))
-
-}
-
-extract_obs_changes <- function(observed){
-  obs_changes <- observed %>%
-  mutate(mean = rescale_beta(mean, -3, 3)) %>%
-  spread(phase,mean) %>%
-  mutate(changeScore = posttest-pretest) %>%
-  # filter(condition == "diseaseRisk") %>%
-  group_by(scale) %>%
-  summarise(
-    Mean = mean(changeScore),
-    ul = mean(changeScore) + 1.96*sd(changeScore)/sqrt(n()), # replace with bootstrapping
-    ll = mean(changeScore) - 1.96*sd(changeScore)/sqrt(n())
-    ) %>%
-  mutate(type = "observed")
-
-  return(obs_changes)
-}
-
-combined_long_diag <- combined_long %>%
-  filter(returned) %>%
-  rename(mean = resp)
-
-filter_dscored <- function(data, scale_name){
-
-  data %>%
-  filter(scale == scale_name) %>%
-  mutate(mean = rescale_beta(mean, -3, 3)) %>%
-  spread(phase, mean) %>%
-  # rename(pre=pretest, post=posttest)
-  summarize(pre = mean(pretest), post=mean(posttest))
-}
-
-# -- takes about 1.5 hrs for 500 bootstrap samples
-
-# do bootstrap comparison
-set.seed(1234)
-t1 <- Sys.time()
-
-boot_fits <- as_tibble(expand.grid(
-  list(
-    replicate = 1:100, scale = nodes
-  )
-)) %>%
-  nest(-replicate, .key="scales") %>%
-  mutate(boot_d_scored = map(replicate, function(x) {
-    totaln <- length(unique(combined_long_diag$workerId))
-    combined_long_diag %>%
-      nest(-workerId) %>%
-      sample_n(totaln, replace = TRUE) %>%
-      mutate(uniqueId = 1:totaln) %>%
-      unnest()
-  })) %>%
-  unnest(scales, .drop=FALSE) %>%
-  mutate(
-      boot_d = map2(boot_d_scored, scale, function(x,y){filter_dscored(x, y)}),
-      obs_changes = map(boot_d_scored, extract_obs_changes)
-      ) %>%
-  select(-boot_d_scored) %>%
-  mutate(
-    models = map2(boot_d, scale, function(x,y){add_evid_node(x, base_model, y)}),
-    pred_changes = map(models, cogModel_predictions),
-    r = map2_dbl(pred_changes, obs_changes, compare_pred_obs_r),
-    rmse = map2_dbl(pred_changes, obs_changes, compare_pred_obs_rmse)
-    )
-
-print(Sys.time() - t1)
-```
-
-```{r}
-# boot_fits %>%
-#   mutate(r2 = r^2) %>%
-#   ggplot(aes(x=reorder(scale,-r2), y = r2)) +
-#   geom_boxplot(fill="lightgray") +
-#   theme_bw() +
-#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-#   coord_flip()
-  # theme(axis.text.x = element_text(angle = 90, hjust = 1))
-
-diagnose_plot <- boot_fits %>%
-  select(replicate, scale,r,rmse) %>%
-  mutate(scale_order = r) %>%
-  gather(meas, value, r, rmse) %>%
-  mutate(meas = ifelse(meas=="rmse", "RMSE (lower is better)", "Correlation")) %>%
-  mutate(meas = factor(meas, levels=c("RMSE (lower is better)", "Correlation"))) %>%
-  mutate(scale = recode_factor(
-  scale,
-  "vaccIntent" = "Vaccination Intentions",
-  "nat" = "Naturalism",
-  "hb" = "Holistic Balance",
-  "overpar" = "Parental Protectiveness",
-  "parentExpert" = "Parental Expertise",
-  "medSkept" = "Medical Skepticism",
-  "vaccDanger" = "Vaccine Danger",
-  "vaccTox" = "Vaccine Toxicity",
-  "vaccEff" = "Vaccine Efficacy",
-  "diseaseRare" = "Disease Rarity",
-  "diseaseSevere" = "Disease Severity",
-  "infantImmWeak" = "IIS: Weakness",
-  "infantImmLimCap" = "IIS: Limited Capacity",
-  "vaccStrain" = "IIS: Vaccines Strain")) %>%
-  ggplot(aes(x=reorder(scale, scale_order), y = value)) +
-  # geom_violin(fill="gray", alpha=.5) +
-  geom_boxplot(fill = "lightgray") +
-  facet_wrap(~meas, scales="free_x" ) +
-  labs(x = "Belief", y = "Value") +
-  theme_bw(base_size=16) +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-  coord_flip()
-
-ggsave("../local/uci-talk-diagnose.png",width=6,height=3.5)
-
-diagnose_plot
-
-```

### 2019-08-08 notebooks/s2-analysis.Rmd
before paper reorg

@@
 library(psych)
-# library(ggcorrplot)
 library(lme4)
 library(brms)
-library(rms)
+library(Hmisc)
 
+if require(betareg)
 ```
@@
 g_diffs <- ggplot(d_diffs,
-                  aes(x = scale, y = Mean, 
+                  aes(x = reorder(scale, -Mean), y = Mean, 
                       color = condition, group = condition)) +
@@
 ```{r}
-library(betareg)
 

### 2019-08-08 notebooks/s2-modeling.Rmd
modeling updates
before paper reorg

@@
 ```{r load in existing objects, message=FALSE, warning=FALSE}
-# net.struct <- readRDS("net-struct-cogsci2018.rds")
+# # install missing packages
+devtools::install_github("thomasp85/patchwork")
+install.packages("rsample")
 
@@
 
-library(rsample)
+# library(rsample)
 
@@
 
-ggsave("../local/obs_pred_plot.png",obs_pred_plot)
+# ggsave("../local/obs_pred_plot.png",obs_pred_plot)
 ```

### 2019-08-08 scripts/load-data-s1-private.R

@@ -9,7 +9,7 @@ library(stringr)
 # setwd(this.dir)
 
 # load in raw data
-d_raw <- read.csv("../data/study1_data.csv", header = T)
+d_raw <- read.csv("../data_private/study1_data.csv", header = T)
 
 # filter rows and select columns
 d1 <- d_raw %>%
@@ -17,8 +17,7 @@ d1 <- d_raw %>%
   filter(Status == "IP Address") %>% # remove survey previews (?)
   filter(Progress == 100) %>% # only get people who made it all the way through (?)
   filter(as.numeric(as.character(age)) >= 18) %>% # exclude people who said they were <18 yo (could be more stringent)
-  select(StartDate, Duration..in.seconds., workerId, hb_1:comments) %>% # include only selected columns
-  filter(!duplicated(workerId)) # we had a worker take it twice somehow! caught 5/1/19, 2:33 PM
+  select(StartDate, Duration..in.seconds., workerId, hb_1:comments) # include only selected columns
 
 # reformat variables
 d2 <- d1 %>% 

### 2019-08-08 scripts/load-data-s3.R

@@ -1,0 +1,62 @@
+library(tidyverse)
+
+read_qualtrics <- function(fname){
+  # load raw qualtrics data
+  header <- colnames(read.csv(fname, header = TRUE))
+  df <- read.csv(fname, skip = 3, header = FALSE, col.names = header)
+  
+  # do some preliminary tidying
+  df <- df %>%
+    as_tibble()
+  
+  return(df)
+}
+
+pre <- read_qualtrics("../data/vacc+tox+interv+full+-+pre_April+3,+2019_15.38.csv")
+post <- read_qualtrics("../data/vacc+tox+interv+full+-+post_April+5,+2019_13.59.csv")
+
+
+df_pre <- pre %>%
+  filter(workerId!="e082cf59a57d4562") %>% # hashed manually
+  filter(Progress==100, check_3==3, check_5==5) %>%
+  mutate(parent = recode(parent, `23`=1, `24`=0)) %>%
+  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5, parent) %>%
+  gather(item, resp, -workerId, -parent) %>%
+  mutate(item = paste0("pre_",item)) %>%
+  spread(item, resp)
+
+df_post <- post %>%
+  filter(Progress==100, check_3==3, check_5==5) %>%
+  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5,
+         condition, interv_t_Page.Submit) %>%
+  rename(read_time = interv_t_Page.Submit) %>%
+  gather(item, resp, -workerId, -condition, -read_time) %>%
+  mutate(item = paste0("post_",item)) %>%
+  spread(item, resp)
+
+
+df <- left_join(filter(df_pre, workerId %in% df_post$workerId), df_post, by="workerId") %>%
+  mutate_at(vars(matches(".*(_[0-9]*r)")), funs(8 - .)) %>% # reverse code
+  gather(item, resp, matches(".*(_[0-9])")) %>%
+  mutate(phase = ifelse(grepl("pre_",item),"pre","post")) %>%
+  mutate(
+    item = gsub("pre_","",item),
+    item = gsub("post_","",item)
+  ) %>%
+  mutate(scale = gsub("(_([0-9])+(r)*)","",item))
+
+df_scored <- df %>%
+  group_by(workerId, condition, scale, phase, parent) %>%
+  summarize(mean_resp = mean(resp)) %>%
+  spread(phase, mean_resp) %>%
[…]

### 2019-08-18 supplement/S1-structure-learning.Rmd
initiating reorg

--- 2018-11-29 study1/custom-structure-learning-vaccData.Rmd
@@
 ```{r}
-source("vacc_import_data.R", chdir = TRUE)
+source("../code/load-data-s1.R", chdir = TRUE)
 ```
@@
 
-# source("cog-model-graph-tools.R")
-source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)
-source("../scripts/gmod_tools.R")
-source("../scripts/bnTheoryBlacklist.R")
-source("../scripts/custom-structure-learning/cog-model-jags-tools.R")
+source("../code/custom-structure-learning/cog-model-main.R", chdir = TRUE)
+source("../code/graph-model-tools.R")
+source("../code/custom-structure-learning/cog-model-jags-tools.R")
+source("../code/helpers.R")
 
@@
 # rescale beta
-
-rescale_beta <- function(x, lower, upper) {
-  # rescales onto the open interval (0,1)
-  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
-
-  N <- length(x)
-  res <- (x - lower) / (upper - lower)
-  res <- (res * (N - 1) + .5) / N
-
-  return(as.vector(res))
-}
 
@@
 compute_scoretables <- FALSE # uncomment to recompute scoretables
-source("../scripts/custom-structure-learning/fit-cog-models.R", chdir=TRUE)
+source("../code/custom-structure-learning/fit-cog-models.R", chdir=TRUE)
 
@@
 scoretables <- list(
-  readRDS("scoretable-unconstrained.rds"),
-  readRDS("scoretable-intent_is_dv.rds"),
-  readRDS("scoretable-abstract_are_parents.rds"),
-  readRDS("scoretable-abstract_are_parents_intent_dv.rds"),
-  readRDS("scoretable-theoryBasedHierarchy.rds")
+  readRDS("../local/scoretable-unconstrained.rds"),
+  readRDS("../local/scoretable-intent_is_dv.rds"),
+  readRDS("../local/scoretable-abstract_are_parents.rds"),
+  readRDS("../local/scoretable-abstract_are_parents_intent_dv.rds"),
+  readRDS("../local/scoretable-theoryBasedHierarchy.rds")
   )

### 2019-08-18 supplement/s2-modeling.Rmd
initiating reorg

--- 2019-08-08 notebooks/s2-modeling.Rmd
@@
 # # install missing packages
-devtools::install_github("thomasp85/patchwork")
-install.packages("rsample")
-
-source("../scripts/load-data-s1.R", chdir = TRUE)
-source("../scripts/gmod_tools.R")
+# devtools::install_github("thomasp85/patchwork")
+# install.packages("rsample")
+
+source("../code/load-data-s1.R", chdir = TRUE)
+source("../code/graph-model-tools.R")
+source("../code/helpers.R")
 # source("../../Scripts/virtualEvidence.R")
@@
 
-source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)
+source("../code/custom-structure-learning/cog-model-main.R", chdir = TRUE)
 ```
@@
 
-source("../scripts/load-data-s2.R", chdir = TRUE)
+source("../code/load-data-s2.R", chdir = TRUE)
 

### 2019-08-18 supplement/vaccTox-full.Rmd
initiating reorg

---
title: "Vaccine toxins full experiment"
author: Derek Powell
date: April 9, 2019
output: 
  html_notebook: 
    code_folding: hide
---

NOTE: All ps eventually saw the intervention, those in no-intervention control just saw it after they responsed to the questions. I'm not fully sure what my logic was there--equity I guess. I may have also been thinking we could ask them things about their reaction to the intervention, but we never did that. On reflection now, I think it was a poor decision. But, it doesn't seem to explain our differential dropout rate since that's mostly due to peopel dropping out at the 18% mark.

### Loading packages and importing data

```{r message=FALSE}
library(tidyverse)
library(brms)

# pre <- read_qualtrics("../data_private/vacc+tox+interv+full+-+pre_April+3,+2019_15.38.csv")
# post <- read_qualtrics("../data_private/vacc+tox+interv+full+-+post_April+5,+2019_13.59.csv")
source("../code/helpers.R")
source("../code/load-data-s3ab.R")
```

## Preliminaries

This is a full-sized experiment testing our vaccine toxins intervention following a successful pilot. The experiment was conducted across two days, with pretest session on April 3th, 2019 and participants re-recruited to an intervention/posttest session the next day, April 4th, 2019.

In part 1, we recruited `r nrow(pre %>% filter(Progress==100))` participants, of which `r nrow(df_pre)` passed check questions and were re-recruited for part 2. In part 2, `r nrow(post)` of those recruited joined the study, and `r nrow(post %>% filter(Progress==100))` finished it. Of these, `r nrow(df_post)` passed attention check questions and are included in the final data. Of these, `r nrow(df_post %>% filter(condition=="intervention"))` were assigned to the intervention condition and `r nrow(df_post %>% filter(condition=="noInterv"))` to a no-intervention control.

### Histograms

The distributions of responses at pretest appear very similar across conditions, and similar to those observed previously.

```{r}
s3_scored %>%
  ggplot(aes(x=pre, fill=condition)) + 
  geom_histogram(position="dodge",alpha=.7) + 
  facet_wrap(~scale) +
  theme_bw() +
  labs(title="Histogram of pretest scores", fill = "Condition", x = "Response")

```

### Scale correlations (pretest)

Correlations at pretest look very similar to those observed previously.

```{r fig.width=8, fig.height=8}

# borrowing code from
# http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization

reorder_cormat <- function(cormat){
  # Use correlation between variables as distance
  dd <- as.dist((1-cormat)/2)
  hc <- hclust(dd)
  cormat <-cormat[hc$order, hc$order]
}

# Get lower triangle of the correlation matrix
get_lower_tri<-function(cormat){
  cormat[upper.tri(cormat)] <- NA
  return(cormat)
}
# Get upper triangle of the correlation matrix
get_upper_tri <- function(cormat){
  cormat[lower.tri(cormat)]<- NA
  return(cormat)
}

s3_scored %>%
  select(workerId, condition, scale, pre) %>%
  spread(scale, pre) %>%
  select(-workerId, -condition) %>%
  cor() %>%
  reorder_cormat() %>%
  # get_lower_tri() %>%
  reshape2::melt(na.rm=TRUE) %>%
  ggplot(aes(x=Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_tile() +
  geom_text(aes(label=round(value,2))) +
  scale_fill_distiller(type="div", palette = "RdYlBu") +
  # scale_fill_viridis_c(limit = c(-1,1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust=1)) +
  theme(aspect.ratio = 1) +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(fill="corr.")
# 
# 
# s3_scored %>%
#   select(workerId, condition, scale, pre) %>%
#   spread(scale, pre) %>%
#   select(-workerId, -condition) %>%
#   cor() %>%
#   as_tibble() %>%
#   mutate(x_scale = names(.)) %>%
#   gather(y_scale, correl, -x_scale) %>%
#   ggplot( aes(x = x_scale, y=y_scale, fill=correl)) +
#   geom_tile() +
#   scale_fill_distiller(palette="RdYlBu") +
#   theme_minimal() +
#   theme(aspect.ratio = 1) +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Change scores

I computed a change score for each belief scale as `change = posttest - pretest`. Below, I'm plotting the change scores for all 14 belief scales in the intervention and control conditions.

```{r}
s3_scored %>%
  group_by(condition, scale) %>%
  summarize(
    Mean = mean(change),
    se = sd(change)/sqrt(n())
    ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  ungroup() %>%
  mutate(condition = factor(condition, labels = c("Intervention","Control"))) %>%
  ggplot(aes(x=reorder(scale, Mean), color = condition, y = Mean, ymin = ll, ymax = ul)) +
  geom_errorbar(width=.1) +
  geom_point() +
  geom_hline(yintercept=0, linetype="dashed") +
  # facet_wrap(~scale) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# s3_scored %>%
#   ggplot(aes(x=scale, color = condition, fill = condition, y = change)) +
#   geom_violin() +
#   geom_hline(yintercept=0, linetype="dashed") +
#   # facet_wrap(~scale) +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
result <- s3_scored %>%
  filter(scale=="vaccTox") %>%
  group_by(condition) %>%
  summarize(
    Mean = mean(change),
    SD = sd(change)
  )

cohens_D <- function(m1, m2, s1, s2) {

  s_pooled <- sqrt((s1^2 + s2^2)/2)
  d <- (m1 - m2)/s_pooled

  return(d)
}

obs_d <- cohens_D(result[[1,2]], result[[2,2]], result[[1,3]], result[[2,3]])
```

__The Good News__: We replicate the large effect on vaccine toxins beliefs, and see significant changes across other beliefs as well. There is also a significant difference between intervention and control for vaccine intentions.

The effect has a cohen's D of `r round(obs_d,2)`, even larger than what we observed in our original pilot! (though that maybe due to slight increase in control condition).

__The Bad News__: The difference between conditions for vaccine intentions is driven by a decrease in the _control_ condition moreso than the increase in the intervention condition. Comparing scores just within the intervention condition against zero, the intervention is not significantly increasing intentions to vaccinate.

### Inspecting vaccine intentions

```{r}
fit <- cbrm(
  resp ~ phase * condition + (1 | workerId),
  data = s3_scored %>%
    filter(scale == "vaccIntent") %>%
    gather(phase, resp, post, pre) %>%
    mutate(resp = rescale_beta(resp, 1, 7)),
  family = Beta(),
  prior = prior(normal(0,1), class="b"),
  chains = 2,
  cores = 2,
  iter = 2000,
  seed = 1234,
  file = "../local/s3ab-fit-vaccIntent.Rds"
)

```

```{r}
t.test(s3_scored %>% filter(scale=="vaccIntent", condition=="intervention") %>% .$change)
```

In contrast, the difference in the control condition for vaccine intentions is really quite huge. A one-sample t-test remains significant after correcting for multiple comparisons (bonferroni adjusted $\alpha$ = .0036).

```{r}
t.test(s3_scored %>% filter(scale=="vaccIntent", condition=="noInterv") %>% .$change)
```

So unfortunately something really is amiss with these vaccine intentions responses. There are also some suspicious changes in a handful of other beliefs: vaccine toxicity, holistic balance, naturalism, and infant immune system weakness, but using a one-sample t-test, but none of those changes are significantly different from zero by conventional standards, even without correcting for multiple comaprisons.

#### Regression

Inspecting this as a regression of `posttest ~ pretest + condition` and plotting it doesn't reveal anything too suspicious-looking in terms of outliers etc, looks like a genuine decrease.

```{r}

summary(
  lm(post ~ pre + condition, data = s3_scored %>% filter(scale=="vaccDanger"))
)

s3_scored %>%
  filter(scale=="vaccIntent") %>%
  ggplot(aes(x=pre, y = post, color=condition)) +
  geom_jitter() + 
  theme_bw() +
  theme(aspect.ratio=1)
```

#### Pretest differences?

Let's look at the pretest scores across the conditions, do they vary (by chance)? No significant pre-test differences, and if anything the difference shows the no-intervention group scoring lower at pretest, presumably offering the potential for more of an increase.

```{r}
pretest_scores <- s3_scored %>%
  filter(scale=="vaccIntent") %>%
  group_by(condition) %>%
  summarize(
    pre_mean = mean(pre),
    pre_sd = sd(pre),
    )

t.test(pre ~ condition, 
       data = s3_scored %>% filter(scale=="vaccIntent")
       )

s3_scored %>%
  filter(scale=="vaccIntent") %>%
  group_by(condition) %>%
  summarize(
    pre_mean = mean(pre),
    pre_se = sd(pre)/sqrt(n()),
    ) %>%
  mutate(
    ll = pre_mean - pre_se,
    ul = pre_mean + pre_se
  ) %>%
  ggplot(aes(x=condition, y=pre_mean, ymin=ll, ymax=ul)) +
  geom_pointrange() +
  theme_bw()
```

#### parents vs non-parents

Maybe if you're a parent who has already vaccinated, you can't change your beliefs much? If anything, looks like it's the other way around. Though, the non-parents seem to be showing a somewhat sharper decline.

```{r}
s3_scored %>%
  filter(scale=="vaccIntent") %>%
  filter(!is.na(parent)) %>%
  group_by(parent, condition) %>%
  summarize(mean_change = mean(change),
            se = sd(change)/sqrt(n()),
            N = n()
            ) %>%
  ungroup() %>%
  mutate(
    ll = mean_change - se,
    ul = mean_change + se,
    parent=factor(parent, labels=c("non-parents","parents"))
    ) %>%
  ggplot(aes(x=parent, y = mean_change, ymin = ll, ymax=ul, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  theme_bw()
```

### Did something genuinely happen between pretest and posstest?

So then the natural question is, did something happen between the two phases that could have changed paticipants attitudes? Or more generally, is there something fishy going on across the board? Clearly, it is somewhat odd that vaccine intentions shifted all by themselves, without attendant changes in highly-related beliefs about vaccine danger, efficacy, or disease severity (though there's some movement on toxicity).

So I'd like to test whether there is more going on overall than just the change in vaccine intentions, i.e., is it odd that we have 3 other scales also nearly significantly different from zero, or are those normal changes to expect. To test this, I'll use a bootstrapping approach. I'll compute the 14 observed t-scores and ask are there overall more extreme values than we would expect under a set of null results, in addition to the vaccIntent issue.

```{r}
# x <- t.test(s3_scored %>% filter(scale=="vaccIntent", condition=="noInterv") %>% .$change)

get_t_stat <- function(scale){
  data <- s3_scored %>% filter(scale==!!scale, condition=="noInterv")

  test <- t.test(data$change)

  return(test$statistic)
}

obs_F <- tibble(
  scale = unique(s3_scored$scale),
  t = map_dbl(scale, get_t_stat),
  F_stat = t^2
  ) %>%
  summarize(F_mean = mean(F_stat))

obs_F_noVacc <- tibble(
  scale = unique(s3_scored$scale),
  t = map_dbl(scale, get_t_stat),
  F_stat = t^2
  ) %>%
  filter(scale!="vaccIntent") %>% # comment
  summarize(F_mean = mean(F_stat))

tibble(x = rep(14,5000)) %>%
  mutate(F_mean = map_dbl(x, function(x){ mean(rt(x, 493)^2) }) ) %>%
  mutate(greater = ifelse(F_mean > obs_F$F_mean, 1, 0)) %>%
  summarize(p = mean(greater))

tibble(x = rep(13,5000)) %>%
  mutate(F_mean = map_dbl(x, function(x){ mean(rt(x, 493)^2) }) ) %>%
  mutate(greater = ifelse(F_mean > obs_F_noVacc$F_mean, 1, 0)) %>%
  summarize(p_no_vaccIntent = mean(greater))
```

Doing a bootstrap, things are overall more extreme than expected under the null across the 14 beliefs. If we remove the vaccIntent scale from consideration however, then things are no more extreme than expected.

Unfortunately that really just adds to the mystery--if there were systematic variations it would feel safe to conclude that "something happened" that affected resposnes in the control condition, suggesting these results are generally suspect. But it seems isolated to the vaccIntent scale. Nevertheless, it's problematic for our purposes.

## Comparison with model predictions

So there is something strange going on in the control group's responses for vaccine intentions which may prevent us from testing that main prediction properly. We can (maybe) still ask whether the changes across the other remaining beliefs are in line with the model's predictions.

```{r}
## ----------------------------------------

rescale_beta <- function(x, lower, upper) {
  # rescales onto the open interval (0,1)
  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"

  N <- length(x)
  res <- (x - lower) / (upper - lower)
  res <- (res * (N - 1) + .5) / N

  return(as.vector(res))
}

d_vacctox <- s3_scored %>%
  select(-change) %>%
  gather(phase, mean, pre,post) %>%
  mutate(mean = mean-4) %>%
  ungroup()

## ----------------------------------------
## this was just to double check my optim() solution is right
# library(brms)
#
# brm_fitodds <- brm(
#   bf(
#     post ~ log(pre/(1-pre)) + evid*logER1,
#     logER1 ~ 1,
#     nl = TRUE,
#     family = Beta("logit")
#      ),
#   prior = prior("normal(0,3)", nlpar = "logER1"),
#           # prior("normal(0,3)", nlpar = "logER0"),
#     # prior("uniform(0,1)", lb = 0, ub = 1, nlpar = "p0"),
#   data = filter_dscored(d_vacctox,"vaccTox"),
#   iter = 4000,
#   warmup = 2000,
#   chains = 2,
#   cores = 2,
#   control = list(adapt_delta=.90)
# )
```

```{r}
## WARNING: THIS CODE IS HACKY!
## 
## script for generating model predictions based on vaccine toxins intervention
## run:
## int-theory-vacc/notebooks/s2-modeling.Rmd (to line 495)
##
## then run this notebook, and finally this code:

filter_dscored <- function(data, scale_name){

  data %>%
  filter(scale == scale_name) %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase, mean) %>% 
  mutate(condition = relevel(condition, ref="noInterv")) %>%
  mutate(evid = ifelse(condition=="noInterv",0,1))
}

# # update model fitting thing ignore control condition b/c of strange things in this data ...

find_evid_ratio <- function(data){
    optim(par = c(0, 5), fn = evid_score_func, data = data, method="BFGS")
}

# find_evid_ratio <- function(data){
#   # HACK HACK HACK
#   return (data.frame(par = c(-.55, 7)))
# }

evid_score_func <- function(data, par) {

    inv_logit <- plogis
    logit <- qlogis

    pred_y <- with(data,
                   {
                       inv_logit( logit(pre) + evid*par[1] )
                   }
    )
    pred_beta_A <- pred_y * par[2]
    pred_beta_B <- (1-pred_y) * par[2]

    ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
    return(ll)
}

get_evid_probs <- function(result){
  # this is a heuristic/hack, could be made better but probably doesn't matter
  evid_ratio <- exp(result$par[1])
  if (evid_ratio < 1) {
    p0 <- .90
  } else {
    p0 <- .5
  }

  if (p0*evid_ratio >= 1) {
    p0 <- p0*.9/(p0*evid_ratio)
  }

  p1 <- p0*evid_ratio

  c(p0,p1)
}

predModel <- add_evid_node(filter_dscored(d_vacctox, "vaccTox"), base_model, "vaccTox")

pred0 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence=TRUE, n = 5e5)")
  eval(parse(text=statement))
})

pred1 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 5e5)")
  eval(parse(text=statement))
})

pred_changes <- pred1 - pred0

pred_changes <- as.data.frame(pred_changes)

pred_changes <- pred_changes %>%
  mutate(scale = nodes) %>%
  rename(Mean = pred_changes) %>%
  mutate(type = "predicted")

saveRDS(object = pred_changes, file = "pred_changes.Rds")
```

```{r}

pred_changes <- readRDS("pred_changes.Rds")

preds_obs <- s3_scored %>%
  filter(condition == "intervention") %>%
  group_by(scale) %>%
  mutate(
    pre = rescale_beta((pre - 4), -3, 3),
    post = rescale_beta((post - 4), -3, 3)
  ) %>%
  mutate(change = post - pre) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes %>% rename(pred_mean = Mean), by = "scale")

preds_obs %>%
  rename(
    observed = Mean,
    predicted = pred_mean
  ) %>%
  gather(type, Mean, observed, predicted) %>%
  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
  geom_point()

preds_obs %>%
  ggplot(aes(x=pred_mean, y = Mean, ymin = ll, ymax=ul)) +
  geom_point() +
  geom_errorbar(width=0) +
  geom_abline(intercept=0,slope=1,alpha=.5,linetype="dashed") +
  theme_bw() +
  coord_cartesian(xlim=c(-.13,.11), ylim= c(-.13,.11)) +
  theme(aspect.ratio=1)

pred_obs_cor <- rcor(preds_obs$pred_mean, preds_obs$Mean)

print(paste( c("Model x observed correlation, r = ", rcor(preds_obs$pred_mean, preds_obs$Mean))), quote=FALSE)
```

For some reason this simulation is not capturing the changes in vaccTox exactly, which I expected it would. I suppose it could have something to do with the distributions of pre and posttest scores, and/or the long tails in the distribution of change scores.

In any case, we can still pretty safely take this as an estimate of the correlation between model predictions and observed change scores: r = `r round(pred_obs_cor,3)` and $r^2$ = `r round(pred_obs_cor^2,3)`. That's considerably poorer than the model predictions for disease risk intervention, which correlated approximately r = .85 and got about 75% of the variance.

#### immune system beliefs?

Looking at that plot, predictions for beliefs about the infant immune system are pretty obviously poor. And, it's easy to imagine that we have inadvertantly targetted those beliefs directly: the intervention describes how the infants' body is able to process naturally-produced formaldehyde, potentially underscoring its robustness. This is my not-quite-right approach to fitting this (should be fitted jointly for both beliefs, can implement that later).

```{r}
vt_iw_model <- add_evid_node(filter_dscored(d_vacctox, "vaccTox"), 
                                  base_model, 
                                  "vaccTox", "_1")

vt_iw_model <- add_evid_node(filter_dscored(d_vacctox, "infantImmWeak"), 
                                  vt_iw_model, 
                                  "infantImmWeak", "_2")

# ----------------------------------------

set.seed(12345)

pred0_vt_iw <- sapply(nodes, function(x){
  statement <- paste0("cpquery(vt_iw_model, event = (", x, " == 'Yes'), evidence=TRUE, n = 1e6)")
  eval(parse(text=statement))
})

pred1_vt_iw <- sapply(nodes, function(x){
  statement <- paste0("cpquery(vt_iw_model, event = (", 
                      x,
                      " == 'Yes'), evidence= (evid_1 == 'Yes' & evid_2== 'Yes'), n = 1e6)")
  eval(parse(text=statement))
})

pred_changes2 <- pred1_vt_iw - pred0_vt_iw

pred_changes2 <- as.data.frame(pred_changes2)

pred_changes2 <- pred_changes2 %>%
  mutate(scale = nodes) %>%
  rename(Mean = pred_changes2) %>%
  mutate(type = "predicted")

preds_obs2 <- s3_scored %>%
  filter(condition == "intervention") %>%
  group_by(scale) %>%
  mutate(
    pre = rescale_beta((pre - 4), -3, 3),
    post = rescale_beta((post - 4), -3, 3)
  ) %>%
  mutate(change = post - pre) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes2 %>% rename(pred_mean = Mean), by = "scale")

preds_obs2 %>%
  ggplot(aes(x=pred_mean, y = Mean, ymin = ll, ymax=ul)) +
  geom_point() +
  geom_errorbar(width=0) +
  geom_abline(intercept=0,slope=1,alpha=.5,linetype="dashed") +
  theme_bw() +
  coord_cartesian(xlim=c(-.13,.11), ylim= c(-.13,.11)) +
  theme(aspect.ratio=1)

print(paste( c("Model x observed correlation, r = ", rcor(preds_obs2$pred_mean, preds_obs2$Mean))), quote=FALSE)
# ----------------------------------------

# obs_pred2 <- bind_rows(pred_changes2, obs_changes) %>%
#   spread(type, Mean) %>%
#   group_by(scale) %>%
#   summarize_all(mean, na.rm=TRUE)
# 
# cor(obs_pred2$predicted, obs_pred2$observed)
# 
# obs_pred2 %>% # a bit of a hack
#   ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
#   geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
#   geom_point() +
#   geom_errorbar() +
#   coord_cartesian(xlim=c(-.06,.08), ylim=c(-.06,.08)) +
#   theme_bw() +
#   theme(aspect.ratio = 1)
# 
# obs_pred2 %>%
#   gather(type, Mean, observed, predicted) %>%
#   ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
#   geom_point() +
#   geom_errorbarh(height=0)
```

Adding this link improves predictions by cleaning up predictions for immune system weakness (trivially, since we gave it to the model), and immune system limited capacity. Predictions for the remaining beliefs shift around a bit too but with no improvement to fit. Overall, things are still looking a good deal poorer than the model's predictions for the disease risk intervention. It's really considerably worse--whereas for the disease risk intervention the model's predictions were basically numerically right with a few exceptions, here they are numerically wrong with a few exceptions. They capture the overall trend, but don't really seem to capture all the systematic changes. The magnitudes are also off, with the model generally predicting larger changes than were observed. Not to mention, the failure to show anything clear with intentions really undercuts the applied perspective.

## Conclusions

As far as I can tell, this is a somewhat disappointing result for the study. We might ...

* try again/get new data?
* get more data? (Could do [sequential analysis](https://onlinelibrary.wiley.com/doi/pdf/10.1002/ejsp.2023), though I think adding to the sample until the bias goes away would require a lot of data ...)

----------------------------------------

### Some miscellany

change scores: plot and effect size

Change score for vaccTox is huge, d = .81--even bigger than the pilot study! but part of that is driven by a small (d=.11) increase in the control condition that is nearly significant by traditional standards. So, maybe the real increase is still comparable to what we originally observed.

```{r}

s3_scored %>%
  filter(scale=="vaccTox") %>%
  ggplot(aes(x=condition, y = change)) +
  geom_boxplot(width=.25) +
  theme_bw()

s3_scored %>%
  filter(scale=="vaccTox") %>%
  ggplot(aes(x=condition, y = change)) +
  stat_summary(fun.y = mean, geom = "point", size=3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width=.1) +
  theme_bw() +
  labs(x="Condition", y = "Mean Change Score")
```

I can quickly hack together the predictions we mdae in the preregistration with the observed changes. The absolute values will be off (way off b/c of rescaling) but the correlations would still be indicative. looks like there's a substantive correlation but not as strong as prior intervention study, also clearly biased, maybe a result of differences between pilot and full study and some scale bound issues?

```{r}
preds <-  read_csv("../data_private/model_preds_pilot.csv") %>%
  rename(pred_mean = Mean)

preds_obs <- s3_scored %>%
    group_by(condition, scale) %>%
  summarize(
    Mean = mean(change),
    se = sd(change)/sqrt(n())
    ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  filter(condition=="intervention") %>%
  left_join(preds, by ="scale")

cors <- s3_scored %>%
  ungroup() %>%
  select(workerId, scale, pre) %>%
  spread(scale, pre) %>%
  select(-workerId) %>%
  cor() %>%
  .["vaccTox",] %>%
  tibble(pred_cor = ., scale=names(.))

preds_obs <- left_join(preds_obs, cors, by="scale")

preds_obs %>%
  ggplot(aes(x=pred_mean, y = Mean, ymin = ll, ymax=ul)) +
  geom_point() +
  geom_errorbar(width=0) +
  theme_bw() +
  theme(aspect.ratio=1)

print(paste( c("Model x observed correlation, r = ", rcor(-1*preds_obs$pred_cor, preds_obs$Mean))), quote=FALSE)
```

What if we computed changes as difference between intervention and no intervention conditions? Answer: it looks pretty similar. And, no good reason really to support doing it this way over the other way.

```{r}
preds_obs2 <- s3_scored %>%
    group_by(condition, scale) %>%
  summarize(
    Mean = mean(change)
    # se = sd(change)/sqrt(n())
    ) %>%
  spread(condition, Mean) %>%
  mutate(difference = intervention - noInterv) %>%
  left_join(cors, by ="scale") %>%
  mutate(pred_cor = pred_cor/sd(.$pred_cor)*-1,
         difference = difference/sd(.$difference),
         intervention = intervention/sd(.$intervention)
         )

preds_obs2 %>%
  ggplot(aes(x=pred_cor, y=difference)) +
  geom_point() +
  geom_text(aes(label=scale)) +
  # geom_abline(intercept=0, slope=1) +
  # geom_errorbar(width=0) +
  theme_bw() +
  theme(aspect.ratio=1)

print(paste( c("Model x observed correlation, r = ", rcor(preds_obs2$difference, preds_obs2$pred_cor))), quote=FALSE)
```

### Participant locations ...

Looks like our participants come from all over the U.S., as I had hoped based on when I posted the study.

```{r}
# install.packages("maps")

loc_data <- post %>%
  filter(Progress==100, check_3==3, check_5==5) %>%
  select(workerId, LocationLatitude, LocationLongitude, condition) %>%
  filter(LocationLatitude < 50, LocationLatitude > 24, LocationLongitude < -50)

usa <- map_data("state") # we already did this, but we can do it again

ggplot() +
  geom_polygon(
    data = usa,
    aes(x = long, y = lat, fill = region, group = group),
    color = "white"
  ) +
  geom_point(
    data = loc_data,
    aes(x = LocationLongitude, y = LocationLatitude, color = condition),
    shape = 16, alpha = .75
  ) +
  # geom_hex(data = loc_data,
  #                 aes(x = LocationLongitude, y = LocationLatitude), binwidth=2) +
  # scale_fill_viridis_c() +
  coord_fixed(1.3) +
  theme_minimal() +
  scale_fill_grey() +
  guides(fill = FALSE) # do this to leave off the color legend
```

## Modeling effects in control condition

Can we model the effects in the control condition if we imagine that something directly affected participants' vaccine intentions?

```{r}
## WARNING: THIS CODE IS HACKY!
## 
## script for generating model predictions based on vaccine toxins intervention
## run:
## int-theory-vacc/notebooks/s2-modeling.Rmd (to line 495)
##
## then run this notebook, and finally this code:

filter_dscored <- function(data, scale_name){

  data %>%
  filter(scale == scale_name) %>%
  mutate(mean = rescale_beta(mean, -3, 3)) %>%
  spread(phase, mean) %>% 
  mutate(condition = relevel(condition, ref="noInterv")) %>%
  mutate(evid = 1)
}

# # update model fitting thing ignore control condition b/c of strange things in this data ...

find_evid_ratio <- function(data){
    optim(par = c(0, 5), fn = evid_score_func, data = data, method="BFGS")
}

# find_evid_ratio <- function(data){
#   # HACK HACK HACK
#   return (data.frame(par = c(-.55, 7)))
# }

evid_score_func <- function(data, par) {

    inv_logit <- plogis
    logit <- qlogis

    pred_y <- with(data,
                   {
                       inv_logit( logit(pre) + evid*par[1] )
                   }
    )
    pred_beta_A <- pred_y * par[2]
    pred_beta_B <- (1-pred_y) * par[2]

    ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
    return(ll)
}

get_evid_probs <- function(result){
  # this is a heuristic/hack, could be made better but probably doesn't matter
  evid_ratio <- exp(result$par[1])
  if (evid_ratio < 1) {
    p0 <- .90
  } else {
    p0 <- .5
  }

  if (p0*evid_ratio >= 1) {
    p0 <- p0*.9/(p0*evid_ratio)
  }

  p1 <- p0*evid_ratio

  c(p0,p1)
}

predModel <- add_evid_node(filter_dscored(d_vacctox, "vaccIntent"), base_model, "vaccIntent")

pred0 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence=TRUE, n = 5e5)")
  eval(parse(text=statement))
})

pred1 <- sapply(nodes, function(x){
  statement <- paste0("cpquery(predModel, event = (", x, " == 'Yes'), evidence= (evid == 'Yes'), n = 5e5)")
  eval(parse(text=statement))
})

pred_changes <- pred1 - pred0

pred_changes <- as.data.frame(pred_changes)

pred_changes <- pred_changes %>%
  mutate(scale = nodes) %>%
  rename(Mean = pred_changes) %>%
  mutate(type = "predicted")

preds_obs <- s3_scored %>%
  filter(condition == "noInterv") %>%
  group_by(scale) %>%
  mutate(
    pre = rescale_beta((pre - 4), -3, 3),
    post = rescale_beta((post - 4), -3, 3)
  ) %>%
  mutate(change = post - pre) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes %>% rename(pred_mean = Mean), by = "scale")

preds_obs %>%
  rename(
    observed = Mean,
    predicted = pred_mean
  ) %>%
  gather(type, Mean, observed, predicted) %>%
  ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
  geom_point()

preds_obs %>%
  ggplot(aes(x=pred_mean, y = Mean, ymin = ll, ymax=ul)) +
  geom_point() +
  geom_errorbar(width=0) +
  geom_abline(intercept=0,slope=1,alpha=.5,linetype="dashed") +
  theme_bw() +
  coord_cartesian(xlim=c(-.04,.04), ylim= c(-.04,.04)) +
  theme(aspect.ratio=1)

pred_obs_cor <- rcor(preds_obs$pred_mean, preds_obs$Mean)

print(paste( c("Model x observed correlation, r = ", rcor(preds_obs$pred_mean, preds_obs$Mean))), quote=FALSE)
```

That's actually a much better fit than I expected! But it's all driven by the shift on vaccine intentions, not likely to be meaningful among hte 13 remaining variables.

```{r}
z <-  preds_obs %>% filter(scale!="vaccIntent")
rcor(z$pred_mean, z$Mean)
```

## Is vaccIntent less correlated with other beliefs at pre/post in interv/control conditions (this is a variant of ellen's question about the model's predictions that will be much faster to answer)

```{r}
pre_control <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = s3_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="pre", condition=="noInterv")
))

post_control <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = s3_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="post", condition=="noInterv")
))

pre_interv <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = s3_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="pre", condition=="intervention")
))

post_interv <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = s3_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="post", condition=="intervention")
))

pre_control$r.squared
pre_interv$r.squared
post_control$r.squared
post_interv$r.squared

```

So vaccIntent is slightly more predictable (more tightly coupled with other beliefs) in the control condition at pretest than in other measures, by a fairly sizable amount, 4-9% of the variance (not sure how robust that is though).

### 2019-08-18 supplement/vaccTox-full2.Rmd
initiating reorg

--- 2019-08-18 supplement/vaccTox-full.Rmd
@@
 ---
-title: "Vaccine toxins full experiment"
+title: "Vaccine toxins full experiment 2"
 author: Derek Powell
@@
 
-NOTE: All ps eventually saw the intervention, those in no-intervention control just saw it after they responsed to the questions.
-I'm not fully sure what my logic was there--equity I guess.
-I may have also been thinking we could ask them things about their reaction to the intervention, but we never did that.
-On reflection now, I think it was a poor decision.
-But, it doesn't seem to explain our differential dropout rate since that's mostly due to peopel dropping out at the 18% mark.
+This is the second attempt at testing this intervention, hoping that we won't see changes in control condition this time.
 
@@
 ```{r message=FALSE}
+# !diagnostics off
 library(tidyverse)
-library(brms)
+```
 
-# pre <- read_qualtrics("../data_private/vacc+tox+interv+full+-+pre_April+3,+2019_15.38.csv")
-# post <- read_qualtrics("../data_private/vacc+tox+interv+full+-+post_April+5,+2019_13.59.csv")
-source("../code/helpers.R")
-source("../code/load-data-s3ab.R")
+```{r message=FALSE}
+read_qualtrics <- function(fname){
+    # load raw qualtrics data
+  header <- colnames(read.csv(fname, header = TRUE))
+  df <- read.csv(fname, skip = 3, header = FALSE, col.names = header)
+
+  # do some preliminary tidying
+  df <- df %>%
+    as_tibble()
+
+  return(df)
+}
+
+rcor <- function(x,y=NULL){
+  r <- cor(x,y)
+  return( round(r,3) )
+}
+
+pre <- read_qualtrics("../data_private/vacc+tox+interv+full2+-+pre_June+6,+2019_09.35.csv")
+post <- read_qualtrics("../data_private/vacc+tox+interv+full2+-+post_June+7,+2019_18.00.csv")
+```
+
+```{r warning=FALSE}
+
+df_pre <- pre %>%
+  distinct(workerId, .keep_all = TRUE) %>%
+  filter(Progress==100, check_3==3, check_5==5) %>%
+  mutate(parent = recode(parent, `23`=1, `24`=0)) %>%
+  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5, parent) %>%
+  gather(item, resp, -workerId, -parent) %>%
+  mutate(item = paste0("pre_",item)) %>%
+  spread(item, resp)
+
+df_post <- post %>%
+  filter(Progress==100, check_3==3, check_5==5) %>%
+  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5,
+         condition, interv_t_Page.Submit) %>%
+  rename(read_time = interv_t_Page.Submit) %>%
+  gather(item, resp, -workerId, -condition, -read_time) %>%
+  mutate(item = paste0("post_",item)) %>%
+  spread(item, resp)
+
+df <- left_join(filter(df_pre, workerId %in% df_post$workerId), df_post, by="workerId") %>%
+  mutate_at(vars(matches(".*(_[0-9]*r)")), funs(8 - .)) %>% # reverse code
+  gather(item, resp, matches(".*(_[0-9])")) %>%
+  mutate(phase = ifelse(grepl("pre_",item),"pre","post")) %>%
+  mutate(
+    item = gsub("pre_","",item),
+    item = gsub("post_","",item)
+    ) %>%
+  mutate(scale = gsub("(_([0-9])+(r)*)","",item))
+
+df_scored <- df %>%
+  group_by(workerId, condition, scale, phase, parent) %>%
+  summarize(mean_resp = mean(resp)) %>%
+  spread(phase, mean_resp) %>%
+  mutate(change = post - pre) %>%
+  ungroup()
+
 ```
@@
 ```{r}
-s3_scored %>%
+df_scored %>%
   ggplot(aes(x=pre, fill=condition)) + 
@@
 
-s3_scored %>%
+df_scored %>%
   select(workerId, condition, scale, pre) %>%
@@
 # 
-# s3_scored %>%
+# df_scored %>%
 #   select(workerId, condition, scale, pre) %>%
@@
 ```{r}
-s3_scored %>%
+df_scored %>%
   group_by(condition, scale) %>%
@@
 
-# s3_scored %>%
+# df_scored %>%
 #   ggplot(aes(x=scale, color = condition, fill = condition, y = change)) +
@@
 ```{r}
-result <- s3_scored %>%
+result <- df_scored %>%
   filter(scale=="vaccTox") %>%
@@
 
-__The Bad News__: The difference between conditions for vaccine intentions is driven by a decrease in the _control_ condition moreso than the increase in the intervention condition.
+__The Bad News__: The difference between conditions for vaccine intentions is PARTIALLY driven by a decrease in the _control_ condition moreso than the increase in the intervention condition.
 Comparing scores just within the intervention condition against zero, the intervention is not significantly increasing intentions to vaccinate.
@@
 ```{r}
-fit <- cbrm(
-  resp ~ phase * condition + (1 | workerId),
-  data = s3_scored %>%
-    filter(scale == "vaccIntent") %>%
-    gather(phase, resp, post, pre) %>%
-    mutate(resp = rescale_beta(resp, 1, 7)),
-  family = Beta(),
-  prior = prior(normal(0,1), class="b"),
-  chains = 2,
-  cores = 2,
-  iter = 2000,
-  seed = 1234,
-  file = "../local/s3ab-fit-vaccIntent.Rds"
-)
-
+t.test(df_scored %>% filter(scale=="vaccIntent", condition=="intervention") %>% .$change)
 ```
 
+This time, the control condition isn't significantly different from zero either.
+
 ```{r}
-t.test(s3_scored %>% filter(scale=="vaccIntent", condition=="intervention") %>% .$change)
+t.test(df_scored %>% filter(scale=="vaccIntent", condition=="noInterv") %>% .$change)
 ```
 
-In contrast, the difference in the control condition for vaccine intentions is really quite huge.
-A one-sample t-test remains significant after correcting for multiple comparisons (bonferroni adjusted $\alpha$ = .0036).
+So unfortunately we have essentially the same problem once again with the vaccine intentions responses.
 
-```{r}
-t.test(s3_scored %>% filter(scale=="vaccIntent", condition=="noInterv") %>% .$change)
-```
-
-So unfortunately something really is amiss with these vaccine intentions responses.
-There are also some suspicious changes in a handful of other beliefs: vaccine toxicity, holistic balance, naturalism, and infant immune system weakness, but using a one-sample t-test, but none of those changes are significantly different from zero by conventional standards, even without correcting for multiple comaprisons.
+And this time there are now a bunch of additional (!) suspicious changes in a handful of other beliefs, notably holistic balance and medical skepticism.
 
@@
 summary(
-  lm(post ~ pre + condition, data = s3_scored %>% filter(scale=="vaccDanger"))
+  lm(post ~ pre + condition, data = df_scored %>% filter(scale=="vaccIntent"))
 )
 
-s3_scored %>%
+df_scored %>%
   filter(scale=="vaccIntent") %>%
@@
 ```{r}
-pretest_scores <- s3_scored %>%
+pretest_scores <- df_scored %>%
   filter(scale=="vaccIntent") %>%
@@
 t.test(pre ~ condition, 
-       data = s3_scored %>% filter(scale=="vaccIntent")
+       data = df_scored %>% filter(scale=="vaccIntent")
        )
 
-s3_scored %>%
+df_scored %>%
   filter(scale=="vaccIntent") %>%
@@
 ```{r}
-s3_scored %>%
+df_scored %>%
   filter(scale=="vaccIntent") %>%
@@
 ```{r}
-# x <- t.test(s3_scored %>% filter(scale=="vaccIntent", condition=="noInterv") %>% .$change)
+# x <- t.test(df_scored %>% filter(scale=="vaccIntent", condition=="noInterv") %>% .$change)
 
 get_t_stat <- function(scale){
-  data <- s3_scored %>% filter(scale==!!scale, condition=="noInterv")
+  data <- df_scored %>% filter(scale==!!scale, condition=="noInterv")
 
@@
 obs_F <- tibble(
-  scale = unique(s3_scored$scale),
+  scale = unique(df_scored$scale),
   t = map_dbl(scale, get_t_stat),
@@
 obs_F_noVacc <- tibble(
-  scale = unique(s3_scored$scale),
+  scale = unique(df_scored$scale),
   t = map_dbl(scale, get_t_stat),
@@
 tibble(x = rep(14,5000)) %>%
-  mutate(F_mean = map_dbl(x, function(x){ mean(rt(x, 493)^2) }) ) %>%
+  mutate(F_mean = map_dbl(x, function(x){ mean(rt(x, 250)^2) }) ) %>%
   mutate(greater = ifelse(F_mean > obs_F$F_mean, 1, 0)) %>%
@@
 tibble(x = rep(13,5000)) %>%
-  mutate(F_mean = map_dbl(x, function(x){ mean(rt(x, 493)^2) }) ) %>%
+  mutate(F_mean = map_dbl(x, function(x){ mean(rt(x, 250)^2) }) ) %>%
   mutate(greater = ifelse(F_mean > obs_F_noVacc$F_mean, 1, 0)) %>%
@@
 Doing a bootstrap, things are overall more extreme than expected under the null across the 14 beliefs.
-If we remove the vaccIntent scale from consideration however, then things are no more extreme than expected.
-
-Unfortunately that really just adds to the mystery--if there were systematic variations it would feel safe to conclude that "something happened" that affected resposnes in the control condition, suggesting these results are generally suspect.
-But it seems isolated to the vaccIntent scale.
-Nevertheless, it's problematic for our purposes.
+This is also true if we remove the vaccIntent scale from consideration.
+So it seems that it was not safe to run this study again 😢.
 
@@
 
-d_vacctox <- s3_scored %>%
+d_vacctox <- df_scored %>%
   select(-change) %>%
@@
 
-saveRDS(object = pred_changes, file = "pred_changes.Rds")
+# saveRDS(object = pred_changes, file = "pred_changes.Rds")
 ```
@@
 
-pred_changes <- readRDS("pred_changes.Rds")
+# pred_changes <- readRDS("pred_changes.Rds")
 
-preds_obs <- s3_scored %>%
+preds_obs <- df_scored %>%
   filter(condition == "intervention") %>%
@@
 
-preds_obs2 <- s3_scored %>%
+preds_obs2 <- df_scored %>%
   filter(condition == "intervention") %>%
@@
 
-s3_scored %>%
+df_scored %>%
   filter(scale=="vaccTox") %>%
@@
 
-preds_obs <- s3_scored %>%
+preds_obs <- df_scored %>%
     group_by(condition, scale) %>%
@@
 
-cors <- s3_scored %>%
+cors <- df_scored %>%
   ungroup() %>%
@@
 ```{r}
-preds_obs2 <- s3_scored %>%
+preds_obs2 <- df_scored %>%
     group_by(condition, scale) %>%
@@
 
-preds_obs <- s3_scored %>%
+preds_obs <- df_scored %>%
   filter(condition == "noInterv") %>%
@@
   vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
-  data = s3_scored %>% 
+  data = df_scored %>% 
     gather(phase, mean, pre, post) %>% 

### 2019-08-18 code/custom-structure-learning/cog-model-discrete-funcs.R

@@ -1,0 +1,198 @@
+make_custom_cpt <- function(ps, dims, dim_names, data) {
+  # makes custom cpt in HydeNet format
+  output <- array(ps, dim=dims, dimnames=dim_names)
+  attr(output, "model") <- data
+  attr(output, "class") <- c("cpt","array")
+  
+  return(output)
+}
+
+
+result_to_cpt <- function(result, child, predictors, data) {
+  # compute cpt for child node given optim result and predictor variables
+  # result: optim result
+  # child: name of child node (string)
+  # data: dataframe
+  # return: array
+  states <- lapply(c(predictors,child), function(x){c(0,1)})
+  names(states) <- c(predictors,child)
+  states_labeled <- lapply(c(predictors,child), function(x){c("No","Yes")}) # not working 8/17/18, 9:44 AM
+  names(states_labeled) <- c(predictors,child)
+  ds <- ifelse(result > 0,1,0)
+  names(ds) <- sapply(names(result), function(x){paste0("d_",substr(x,3,100))})
+  result <- abs(c(result, ds[-(1:2)]))
+  
+  z <- expand.grid(states) %>%
+    mutate(
+      p = with(
+        as.data.frame(t(result)),
+        eval(parse(text=create_equation_expression(predictors)))
+      )
+    )
+  z[which(z[child]==0),"p"] <- 1-z[which(z[child]==0),"p"] # unnecessary to preserve child name oh well
+  
+  output <- make_custom_cpt(z$p, rep(2,length(predictors)+1), states_labeled, data)
+  return(output)
+}
+
+
+fake_xtabs <- function(node, data, trueval = 1, falseval = 0){
+  data <- as.data.frame(data)
+  probs <- data[, node]
+  p1 <- mean(probs)
+  count1 <- round(p1*1e5)
+  count0 <- 1e5 - count1
+  counts <- matrix(c(rep(trueval,count1), rep(falseval,count0)), ncol=1)
+  colnames(counts) <- c(node)
+  f <- paste0("~",node)
+  output <- xtabs(as.formula(f), data = counts)
+  attr(output, "call") <- list(formula = as.formula(f) )
+  
+  return(output)
+}
+
+
+fit_node_cpt <- function(node, data) {
+  child <- node$child # specific to format above ,could be imrpoved
[…]

### 2019-08-18 code/custom-structure-learning/cog-model-estimate-evid-ratio.R

@@ -1,0 +1,71 @@
+## functions for estimating evidence ratio and augmenting models
+
+inv_logit <- plogis
+logit <- qlogis
+
+evid_score_func <- function(data, par) {
+  
+  inv_logit <- plogis
+  logit <- qlogis
+  
+  pred_y <- with(data,
+                 {
+                   inv_logit(logit(pre) + evid*par[2] + par[1])
+                 }
+  )
+  pred_beta_A <- pred_y * par[3]
+  pred_beta_B <- (1-pred_y) * par[3]
+  
+  ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
+  return(ll)
+}
+
+get_evid_probs <- function(result){
+  # this is a heuristic/hack, could be made better but probably doesn't matter
+  evid_ratio <- exp(result$par[1] + result$par[2])
+  if (evid_ratio < 1) {
+    p0 <- .90
+  } else {
+    p0 <- .50
+  }
+  
+  if (p0*evid_ratio >= 1) {
+    p0 <- p0*.9/(p0*evid_ratio)
+  }
+  
+  p1 <- p0*evid_ratio
+  
+  c(p0,p1)
+}
+
+
+evid_probs_to_cpt <- function(probs, var_name, evid_name = "evid"){
+  p0 <- probs[1]
+  p1 <- probs[2]
+  
+  full_list <- paste0("list(",var_name,"=c('Yes','No'),", evid_name, " = c('Yes', 'No'))")
+  make_custom_cpt(c(p1, p0, (1-p1), (1-p0)), c(2,2), eval(parse(text=full_list)), NULL)
+}
+
+
+find_evid_ratio <- function(data){
+  optim(par = c(0, 0, 5), fn = evid_score_func, data = data, method="BFGS")
+}
+
+
+make_evid_cpt <- function(data, var_name, evid_name = "evid"){
+  result <- find_evid_ratio(data)
+  probs <- get_evid_probs(result)
+  cpt <- evid_probs_to_cpt(probs, var_name, evid_name)
+  
+  return(cpt)
+}
+
+make_evid_cpt_custom <- function(var_name, evid_ratio, evid_name = "evid"){
+  # result <- find_evid_ratio(data)
+  result <<- list(par = c(0, log(evid_ratio)) )
+  probs <- get_evid_probs(result)
+  cpt <- evid_probs_to_cpt(probs, var_name, evid_name)
+  
+  return(cpt)
+}

### 2019-08-18 code/custom-structure-learning/cog-model-iterativeMCMC.R

@@ -1,0 +1,383 @@
+# from BiDAG R package
+# 8/29/18, 2:21 PM
+# used under gpl 2/3 license
+
+
+#iterative MCMC search
+c_iterativeMCMCplus1<-function(n,param,iterations,stepsave,plus1it=NULL,MAP=TRUE, posterior=0.5,
+                             startorder=c(1:n),moveprobs,softlimit=9,hardlimit=12,plus1=FALSE,chainout=FALSE,
+                             scoreout=FALSE,startspace=NULL,blacklist=NULL,gamma=1,verbose=FALSE,alpha=NULL,
+                             cpdag=FALSE,mergecp="skeleton",addspace=NULL,scoretable=NULL) {
+  updatenodeslist<-list()
+  MCMCchains<-list()
+  updatenodes<-c(1:n)
+  maxorder<-startorder
+  
+  if (is.null(blacklist)) {
+    blacklist<-matrix(rep(0,n*n),ncol=n)
+  }
+  diag(blacklist)<-1
+  blacklistparents<-list()
+  for  (i in 1:n) {
+    blacklistparents[[i]]<-which(blacklist[,i]==1)
+  }
+  
+  if (is.null(startspace)) startspace<-BiDAG:::definestartspace(alpha,param,cpdag,n,algo="pc")
+  
+  startskeleton<-1*(startspace&!blacklist)
+  
+  if(!is.null(addspace)) {startskel<-1*((addspace|startskeleton)&!blacklist)
+  } else { startskel<-startskeleton }
+  
+  ptab<-BiDAG:::listpossibleparents.PC.aliases(startskel,isgraphNEL=FALSE,n,updatenodes)
+  
+  if (verbose) {
+    print("skeleton ready")
+    flush.console()
+  }
+  if (plus1==FALSE){
+    starttime<-Sys.time()
+    parenttable<-ptab$parenttable # basic parenttable without plus1 lists
+    aliases<-ptab$aliases #aliases for each node since all nodes in parent tables are named as 1,2,3,4. not real parent names
+    numberofparentsvec<-ptab$numberofparentsvec
+    numparents<-ptab$numparents
+    rowmaps<-BiDAG:::parentsmapping(parenttable,numberofparentsvec,n,updatenodes)
+    if(is.null(scoretable)) {
+      scoretable<-BiDAG:::scorepossibleparents.PLUS1(parenttable,plus1lists,n,param,updatenodes,rowmaps,numparents,numberofparentsvec)
+      
[…]

### 2019-08-18 code/custom-structure-learning/cog-model-jags-tools.R

@@ -1,0 +1,169 @@
+# # Doing inference on beta DAGs through rjags
+# # ----
+
+do_jags_inference <- function(model, variable.names, data = NULL, iter = 1e4, silent=TRUE) {
+  if (silent) {
+    pbar <- "none"
+  } else {
+    pbar <- "text"
+  }
+  tc <- textConnection(model)
+  jags <- rjags::jags.model(tc, data = data, quiet=silent)
+  close(tc)
+  
+  model_samples <- rjags::coda.samples(jags, variable.names, iter*2, progress.bar="none")
+  return(model_samples)
+}
+
+
+make_predictions <- function(model, orig_data, nodes_to_predict, nodes_held_out=c(), iter=1e3) {
+  # takes a model and dataframe and generates model predictions for variables listed in 
+  # nodes_to_predict. By default, uses all remaining nodes in orig_data. Hold out nodes from
+  # prediction with nodes_held_out. iter sets mcmc samples
+  
+  pred_df <- orig_data
+  pred_df[,nodes_to_predict] <- NA
+  
+  for (i in 1:nrow(pred_df)) {
+    row <- pred_df[i,]
+    row[nodes_held_out] <- NA
+    pred <- do_jags_inference(model, nodes_to_predict, data = row, iter = iter)
+    point_preds <- rowMeans(t(pred[[1]][(iter/2+1):iter,nodes_to_predict]))
+    pred_df[i,nodes_to_predict] <- point_preds
+  }
+  
+  return(pred_df)
+}
+
+assemble_fitted_equation <- function(w_leak, prevterms, genterms) {
+  # assembles the noisy-or-and-nor equation
+  # prevterms: probability of non-prevention (p(fail prevent))
+  # genterms: probability of non-generation (p(fail generate))
+  # return: equation string
+  
+  gen <- paste0("(1-",w_leak, ")*",terms_product(genterms))
+  prev <- terms_product(prevterms)
+  paste0(wrap_paren(paste0("1-",gen)), " * ", terms_product(prevterms))
+}
+
+
+create_fitted_equation_expression <- function(predictors, coefs, digits = 5){
+  # creates equation string
+  # predictors: list of names of predictor variables (parents)
+  # return: equation string (expression to evaluate)
+  
+  coefs <- as.list(coefs)
[…]

### 2019-08-18 code/custom-structure-learning/cog-model-predict-changes.R

@@ -1,0 +1,139 @@
+hyde_to_bn_cpt <- function(hyde_cpt) {
+  ndims <- length(dim(hyde_cpt))
+  
+  if ("xtabs" %in% class(hyde_cpt)) {
+    output <- hyde_cpt/1e5
+  } else {
+    
+    output <- aperm(hyde_cpt, ndims:1)
+  }
+  return (output) 
+}
+
+
+create_bnlearn_cog_model <- function(dag, data, evid_cpt = NULL, targetted_belief = NULL) {
+  arcs_df <- bnlearn_to_df(dag)
+  graph_list <- df_to_list(arcs_df)
+  bagOfModels <- lapply(graph_list, function(x){fit_node_cpt(x, data)})
+  model_string <- as.character(dag)
+  
+  if (!(is.null(evid_cpt))) {
+    bagOfModels$evid <- evid_cpt
+    model_string <- paste0(model_string,"[evid|", targetted_belief, "]")
+  }
+  model_network <- model2network(model_string)
+  bnlearn_models <- lapply(bagOfModels, hyde_to_bn_cpt)
+  predModel <- custom.fit(model_network, dist = bnlearn_models)
+  
+  return(predModel)
+}
+
+
+add_evid_node <- function(data, bnlearn_model, targetted_belief, evid_id = NULL) {
+  
+  if (!is.null(evid_id)) {
+    evid <- paste0("evid",evid_id)
+  } else {
+    evid <- "evid"
+  }
+  
+  evid_cpt <- make_evid_cpt(data, targetted_belief, evid)
+  model_list <- lapply(bnlearn_model, function(x){x$prob})
+  model_list[[evid]] <- hyde_to_bn_cpt(evid_cpt)
+  
+  model_string <- modelstring(bnlearn_model)
+  model_string <- paste0(model_string,"[", evid,"|", targetted_belief, "]")
+  
+  model_network <- model2network(model_string)
+  predModel <- custom.fit(model_network, dist = model_list)
+  
+  return(predModel)
+}
+
+
+add_evid_node_custom <- function(bnlearn_model, parents_string, evid_cpt) {
+  
+  model_list <- lapply(bnlearn_model, function(x){x$prob})
+  model_list$evid <- evid_cpt
+  
+  model_string <- modelstring(bnlearn_model)
+  model_string <- paste0(model_string,"[evid|", parents_string, "]")
+  model_network <- model2network(model_string)
[…]

### 2019-08-18 code/custom-structure-learning/fit-cog-models.R

@@ -1,0 +1,236 @@
+
+# load data
+# -----------------------------------------
+# source("../../study1/vacc_import_data.R", chd)
+
+
+# load packages
+# ----------------------------------------
+library(tidyverse)
+library(BiDAG)
+# BiDAG depends on 'graph' package, source: http://www.bioconductor.org/packages/release/bioc/html/graph.html
+# BiDAG depends on 'RBGL' package, source: https://bioconductor.org/packages/release/bioc/html/RBGL.html
+library(bnlearn)
+library(HydeNet)
+library(gtools)
+
+# source("cog-model-graph-tools.R")
+# source("cog-model-main.R")
+# source("../../Scripts/gmod_tools.R")
+# source("../../Scripts/bnTheoryBlacklist.R")
+
+
+# transform data
+# ----------------------------------------
+
+rescale_beta <- function(x, lower, upper) {
+  # rescales onto the open interval (0,1)
+  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
+  
+  N <- length(x)
+  res <- (x - lower) / (upper - lower)
+  res <- (res * (N - 1) + .5) / N
+  
+  return(as.vector(res))
+}
+
+d_bn_scaled <- d_bn %>%
+  mutate_all(function(x){rescale_beta(x,-3,3)})
+
+## set the seed to make your partition reproductible
+set.seed(123)
+trainInd <- sample(seq_len(nrow(d_bn_scaled)), size = floor(nrow(d_bn_scaled)*.80))
+
+train <- d_bn_scaled[trainInd, ]
+test <- d_bn_scaled[-trainInd, ]
+
+
+# generate blacklists
+# ----------------------------------------
+nodes <- c(
+  "diseaseRare",
+  "diseaseSevere",
+  "hb",
+  "infantImmLimCap",
+  "infantImmWeak",
+  "medSkept",
+  "nat",
+  "overpar",
+  "parentExpert",
+  "vaccDanger",
+  "vaccEff",
+  "vaccIntent",
+  "vaccStrain",
+  "vaccTox"
+)
+
+theoryBasedHierarchy <- data.frame(
+  node = nodes,
+  order = c(
+    3,
+    3,
+    1,
+    3,
+    3,
+    2,
+    1,
+    2,
+    2,
+    3,
+    3,
+    4,
+    3,
+    3
+  )
+)
+
+intent_is_dv <- data.frame(
+  node = nodes,
[…]

### 2019-08-18 code/graph-model-tools.R

@@ -423,32 +423,3 @@ make_dbn_df <- function(arcs_df) {
 }
 
 
-### ----------------------------------------
-### blacklist functions
-
-make_theory_blacklist <- function(data) {
-  
-  result <- NULL
-  
-  for (targNode in data$node) {
-    ord <- data %>% dplyr::filter(node==targNode) %>% dplyr::select(order) %>% as.numeric()
-    d <- data %>% dplyr::filter(order < ord) %>% dplyr::mutate(from=targNode, to=node) %>% dplyr::select(from, to)
-    
-    if (is.null(result)) {
-      result <- d
-    }
-    else {
-      result <- dplyr::bind_rows(result, d)
-    }
-  }
-  
-  result <- dplyr::distinct(result, to, from)
-  
-  return(result)
-}
-
-combine_blacklists <- function(bList1, bList2) {
-  
-  dplyr::bind_rows(bList1, bList2) %>% dplyr::distinct(to, from)
-  
-}

### 2019-08-18 code/helpers.R

@@ -1,0 +1,22 @@
+## Helpers for int-theory-vacc project
+
+devtools::source_gist(id = "f1994c0f8325abbc5d300600744af39d", filename="cbrm.R")
+
+rescale_beta <- function(x, lower, upper) {
+  # rescales onto the open interval (0,1)
+  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
+  
+  N <- length(x)
+  res <- (x - lower) / (upper - lower)
+  res <- (res * (N - 1) + .5) / N
+  
+  return(as.vector(res))
+}
+
+
+rcor <- function(x,y=NULL){
+  r <- cor(x,y)
+  return( round(r,3) )
+}
+
+

### 2019-08-18 code/load-data-s1.R

@@ -1,0 +1,119 @@
+
+# set wd (user-specific)
+# setwd("/Users/kweisman/Documents/Research (Stanford)/Projects/Vaccines/vaccineBeliefs/study1/")
+library(tidyverse)
+library(stringr)
+
+# working_dir <- getwd()
+# this.dir <- dirname(parent.frame(2)$ofile)
+# setwd(this.dir)
+
+# load in raw data
+d_raw <- read.csv("../data/study1_data.csv", header = T)
+
+# filter rows and select columns
+d1 <- d_raw %>%
+  filter(grepl("2017", StartDate)) %>% # remove extra headers
+  filter(Status == "IP Address") %>% # remove survey previews (?)
+  filter(Progress == 100) %>% # only get people who made it all the way through (?)
+  filter(as.numeric(as.character(age)) >= 18) %>% # exclude people who said they were <18 yo (could be more stringent)
+  select(StartDate, Duration..in.seconds., workerId, hb_1:comments) %>% # include only selected columns
+  filter(!duplicated(workerId)) # we had a worker take it twice somehow! caught 5/1/19, 2:33 PM
+
+# reformat variables
+d2 <- d1 %>% 
+  # mutate_at(vars(StartDate), funs(parse_datetime)) %>% # parse dates # 1/14/19, 3:12 PM this is throwing an error
+  # mutate_at(vars(Duration..in.seconds., age, children), funs(as.character)) %>% # parse numbers step 1
+  mutate_at(vars(Duration..in.seconds., age, children), funs(as.numeric)) %>% # parse numbers step 2
+  mutate(educ = factor(educ, # recode ordinal variables
+                       levels = c("No Diploma", "High School or Equivalent",
+                                  "Some Undergraduate Education", "Undergraduate Degree",
+                                  "Some Graduate or Professional Education",
+                                  "Graduate or Professional Degree", "Doctorate")),
+         income = factor(income, 
+                         levels = c("Less than $20,000", "$20,000 - $30,0000",
+                                    "$30,001 - $50,000", "$50,001 - $70,000",
+                                    "$70,001 - $100,000", "More than $100,000")),
+         parent = factor(parent, levels = c("No", "Yes")),
+         expecting = factor(expecting, levels =c ("No", "Yes")),
+         youngest_child = factor(youngest_child, 
+                                 levels = c("Less than 1 year old", "1 year old", "2 years old", 
+                                            "3 years old", "4 years old", "5 years old", "6 years old",
[…]

### 2019-08-18 code/load-data-s3.R

@@ -1,0 +1,63 @@
+library(tidyverse)
+
+read_qualtrics <- function(fname){
+  # load raw qualtrics data
+  header <- colnames(read.csv(fname, header = TRUE))
+  df <- read.csv(fname, skip = 3, header = FALSE, col.names = header)
+  
+  # do some preliminary tidying
+  df <- df %>%
+    as_tibble()
+  
+  return(df)
+}
+
+pre <- read_qualtrics("../data/vacc+tox+interv+full+-+pre_April+3,+2019_15.38.csv")
+post <- read_qualtrics("../data/vacc+tox+interv+full+-+post_April+5,+2019_13.59.csv")
+
+summarize <- dplyr::summarise
+
+df_pre <- pre %>%
+  filter(workerId!="e082cf59a57d4562") %>% # hashed manually
+  filter(Progress==100, check_3==3, check_5==5) %>%
+  mutate(parent = recode(parent, `23`=1, `24`=0)) %>%
+  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5, parent) %>%
+  gather(item, resp, -workerId, -parent) %>%
+  mutate(item = paste0("pre_",item)) %>%
+  spread(item, resp)
+
+df_post <- post %>%
+  filter(Progress==100, check_3==3, check_5==5) %>%
+  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5,
+         condition, interv_t_Page.Submit) %>%
+  rename(read_time = interv_t_Page.Submit) %>%
+  gather(item, resp, -workerId, -condition, -read_time) %>%
+  mutate(item = paste0("post_",item)) %>%
+  spread(item, resp)
+
+
+df <- left_join(filter(df_pre, workerId %in% df_post$workerId), df_post, by="workerId") %>%
+  mutate_at(vars(matches(".*(_[0-9]*r)")), funs(8 - .)) %>% # reverse code
+  gather(item, resp, matches(".*(_[0-9])")) %>%
+  mutate(phase = ifelse(grepl("pre_",item),"pre","post")) %>%
+  mutate(
+    item = gsub("pre_","",item),
+    item = gsub("post_","",item)
+  ) %>%
+  mutate(scale = gsub("(_([0-9])+(r)*)","",item))
+
+df_scored <- df %>%
+  group_by(workerId, condition, scale, phase, parent) %>%
+  summarize(mean_resp = mean(resp)) %>%
[…]

### 2019-08-18 code/load-data-s3ab.R

@@ -1,0 +1,58 @@
+pre_a <- read_qualtrics("../data/vacc+tox+interv+full+-+pre_April+3,+2019_15.38.csv") %>%
+  mutate(study="A")
+post_a <- read_qualtrics("../data/vacc+tox+interv+full+-+post_April+5,+2019_13.59.csv") %>%
+  mutate(study="A")
+
+pre_b <- read_qualtrics("../data/vacc+tox+interv+full2+-+pre_June+6,+2019_09.35.csv") %>%
+  mutate(study="B")
+post_b <- read_qualtrics("../data/vacc+tox+interv+full2+-+post_June+7,+2019_18.00.csv") %>%
+  mutate(study="B")
+
+pre <- bind_rows(pre_a, pre_b)
+post <- bind_rows(post_a, post_b)
+
+summarize <- dplyr::summarise
+
+df_pre <- pre %>%
+  filter(workerId!="e082cf59a57d4562") %>% # hashed manually
+  distinct(workerId, .keep_all = TRUE) %>%
+  filter(Progress==100, check_3==3, check_5==5) %>%
+  mutate(parent = recode(parent, `23`=1, `24`=0)) %>%
+  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5, parent, study) %>%
+  gather(item, resp, -workerId, -parent, -study) %>%
+  mutate(item = paste0("pre_",item)) %>%
+  spread(item, resp)
+
+df_post <- post %>%
+  filter(Progress==100, check_3==3, check_5==5) %>%
+  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5,
+         condition, interv_t_Page.Submit) %>%
+  rename(read_time = interv_t_Page.Submit) %>%
+  gather(item, resp, -workerId, -condition, -read_time) %>%
+  mutate(item = paste0("post_",item)) %>%
+  spread(item, resp)
+
+
+df <- left_join(filter(df_pre, workerId %in% df_post$workerId), df_post, by="workerId") %>%
+  mutate_at(vars(matches(".*(_[0-9]*r)")), funs(8 - .)) %>% # reverse code
+  gather(item, resp, matches(".*(_[0-9])")) %>%
+  mutate(phase = ifelse(grepl("pre_",item),"pre","post")) %>%
+  mutate(
+    item = gsub("pre_","",item),
+    item = gsub("post_","",item)
+  ) %>%
[…]

### 2019-08-18 code/load-data-s4.R

@@ -1,0 +1,34 @@
+library(tidyverse)
+library(lubridate)
+
+read_qualtrics <- function(fname){
+  # load raw qualtrics data
+  header <- colnames(read.csv(fname, header = TRUE))
+  df <- read.csv(fname, skip = 3, header = FALSE, col.names = header)
+  
+  # do some preliminary tidying
+  df <- df %>%
+    as_tibble()
+  
+  return(df)
+}
+
+df4 <- read_qualtrics("../data/vaccine+many+beliefs+-+may2019_May+21,+2019_16.12.csv")
+
+df4 <- df4 %>%
+  filter(!duplicated(workerId)) %>%
+  filter(check_3==3, check_5==5) %>%
+  mutate(StartDate = ymd_hms(StartDate)) %>%
+  rename(Duration = Duration..in.seconds.) %>%
+  select(workerId, matches(".*(_[0-9])"), vacc_news, vacc_news_freq, 
+         news_time, news_favorable, vacc_conv, conv_favorable, outbreaks, outbreak_favorable, other,
+         sex, age, race, religion, educ, income, 
+         pol_party, pol_ind_leaning, parent, expecting, children,
+         youngest_child, refuse, comments, StartDate,
+         -check_3, -check_5
+         ) %>%
+  mutate_at(vars(matches(".*(_[0-9]*r)"), -pol_party_4_TEXT, -pol_rating_1), funs(8 - .)) %>% # reverse code
+  gather(item, resp, matches(".*(_[0-9])"), -pol_party_4_TEXT, -pol_rating_1) %>%
+  mutate(scale = gsub("(_([0-9])+(r)*)","",item)) %>%
+  mutate(resp = as.numeric(resp))
+

### 2019-08-18 code/load-model.R

@@ -1,0 +1,31 @@
+# first load in mcmc results
+all_results <- readRDS("../local/allresults.rds")
+nodes <- colnames(train)
+
+# then grab map dag for theory-based constraints
+merged_chains <- merge_chains(all_results[[5]]) # note: this will need to be updated! [fix needed]
+map_dag <- extract_mapdag(merged_chains)
+
+arcs_df <- bnlearn_to_df(map_dag)
+
+df_to_list <- function(arcs_df, as.strings=FALSE) {
+  # take arcs_df and make list of formulas
+  arcs_df$to <- as.character(arcs_df$to)
+  arcs_df$from <- as.character(arcs_df$from)
+  
+  nodes <- unique(unlist(arcs_df))
+  output <- lapply(nodes, function(node) {
+    edges <- arcs_df[which(arcs_df$to == node), "from"]
+    if (length(edges) < 1) {
+      edges <- NULL
+    }
+    list(child=node, parents=edges)
+    
+  })
+  names(output) <- nodes
+  return(output)
+}
+
+graph_list <- df_to_list(arcs_df)
+
+bagOfModels <- lapply(graph_list, function(x){fit_node_cpt(x, train)})

### 2021-03-03 notebooks/s1-model-structure-learning.Rmd
some refactoring and updated readme
before looking back

--- 2018-11-29 study1/custom-structure-learning-vaccData.Rmd
@@
 ```{r}
-source("vacc_import_data.R", chdir = TRUE)
+source("../scripts/load-data-s1.R", chdir = TRUE)
 ```
@@
 
-compute_scoretables <- FALSE # uncomment to recompute scoretables
+# compute_scoretables <- FALSE # uncomment or set to TRUE to recompute scoretables
 source("../scripts/custom-structure-learning/fit-cog-models.R", chdir=TRUE)
 
+## NOTE: make sure to fix to recompute all 5
 ```
@@
 scoretables <- list(
-  readRDS("scoretable-unconstrained.rds"),
-  readRDS("scoretable-intent_is_dv.rds"),
-  readRDS("scoretable-abstract_are_parents.rds"),
-  readRDS("scoretable-abstract_are_parents_intent_dv.rds"),
-  readRDS("scoretable-theoryBasedHierarchy.rds")
+  readRDS("../local/scoretable-unconstrained.rds"),
+  readRDS("../local/scoretable-intent_is_dv.rds"),
+  readRDS("../local/scoretable-abstract_are_parents.rds"),
+  readRDS("../local/scoretable-abstract_are_parents_intent_dv.rds"),
+  readRDS("../local/scoretable-theoryBasedHierarchy.rds")
   )
 
-# # DO MCMC - comment to skip and load saved results
-# all_results <- list(list(), list(), list(), list(), list())
-# 
-# customize_BiDAG() # customize bidag!
-# 
-# for (i in 1:length(startspaces)) {
-#   all_results[[i]] <- parallel_orderMCMC(train,
+# DO MCMC - comment to skip and load saved results
+all_results <- list(list(), list(), list(), list(), list())
+
+customize_BiDAG() # customize bidag!
+
+for (i in 1:length(startspaces)) {
+  all_results[[i]] <- parallel_orderMCMC(train,
                                        # startspaces[[i]],
-#                                        scoretables[[i]],
-#                                        MAP = FALSE, # might error
-#                                        1e6,
-#                                        100,
-#                                        blacklist = blacklists[[i]],
-#                                        chains = 4,
-#                                        cores = 4
-#                                        )
-# 
-# }
-# 
-# reinit_BiDAG() # set it back!
+                                       t(startspaces[[i]]),
+                                       scoretables[[i]],
+                                       MAP = FALSE, # might error
+                                       1e6,
+                                       100,
+                                       blacklist = t(blacklists[[i]]),
+                                       chains = 4,
+                                       cores = 4
+                                       )
 
-# saveRDS(all_results, "allresults.rds")
+}
+
+reinit_BiDAG() # set it back!
+
+saveRDS(all_results, "../local/allresults.rds")
 

### 2021-03-03 scripts/bnTheoryBlacklist.R

@@ -38,13 +38,13 @@ library(tidyverse)
 #                                  3
 #                                ))
 
-make_theory_blacklist <- function(data) {
+make_theory_blacklist <- function(df) {
   
   result <- NULL
   
-  for (targNode in data$node) {
-    ord <- data %>% dplyr::filter(node==targNode) %>% dplyr::select(order) %>% as.numeric()
-    d <- data %>% dplyr::filter(order < ord) %>% dplyr::mutate(from=targNode, to=node) %>% dplyr::select(from, to)
+  for (targNode in df$node) {
+    ord <- df %>% dplyr::filter(node==targNode) %>% dplyr::select(order) %>% as.numeric()
+    d <- df %>% dplyr::filter(order < ord) %>% dplyr::mutate(from=targNode, to=node) %>% dplyr::select(from, to)
     
     if (is.null(result)) {
       result <- d

### 2021-03-03 scripts/custom-structure-learning/fit-cog-models.R

@@ -147,13 +147,13 @@ abstract_are_parents_intent_dv <- data.frame(
 
 make_adjacency_blacklist <- function(ordering_df){
   library(dplyr)
-  
+  nodes <- ordering_df$node
   blacklist <- make_theory_blacklist(ordering_df)
   blacklist <- suppressWarnings(bind_rows(blacklist, data.frame(from = nodes, to = nodes))) %>% arrange(from)
   adjBlacklist <- igraph::graph.data.frame(blacklist)
   adjBlacklist <- igraph::get.adjacency(adjBlacklist, sparse=FALSE)
   
-  # adjBlacklist <- abs(1-adjBlacklist)
+  adjBlacklist <- abs(1-adjBlacklist) ## updated 2021-02-04
   
   return(adjBlacklist)
 }
@@ -208,10 +208,11 @@ if (!exists("compute_scoretables")) {
 
 if (compute_scoretables) {
   for (i in 1:length(startspaces)) {
+  # for (i in 5:5) { ## just do the last one as test
     t1 <- Sys.time()
     scoretable <- generate_scoretable(startspaces[[i]], train, cores = nCores)
     print(Sys.time() - t1)
-    saveRDS(scoretable, paste0("scoretable-", fsuffixes[i], ".rds"))
+    saveRDS(scoretable, paste0("../../local/scoretable-", fsuffixes[i], ".rds"))
   }
   
 }

### 2021-05-24 supplement/supplement-main.Rmd
new supplement

---
title: "Supplement"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r s1_load}
source("../code/load-data-s1.R", chdir = TRUE)

library(tidyverse)
library(bnlearn)
library(HydeNet)

source("../code/custom-structure-learning/cog-model-main.R", chdir = TRUE)
source("../code/graph-model-tools.R")
source("../code/custom-structure-learning/cog-model-jags-tools.R")

d_bn_scaled <- d_bn %>%
 mutate_all(function(x){rescale_beta(x,-3,3)})

## set the seed to make your partition reproductible
set.seed(123)
trainInd <- sample(seq_len(nrow(d_bn_scaled)), size = floor(nrow(d_bn_scaled)*.80))

train <- d_bn_scaled[trainInd, ]
test <- d_bn_scaled[-trainInd, ]
```

```{r cross_validation}
# source("../code/custom-structure-learning/fit-cog-models-bnlearn.R")
cv_res <- readRDS("../local/cv-res.rds")

cv_res %>% 
  ggplot(aes(x=reorder(algo, loss), y=loss)) +
  geom_boxplot() +
  coord_flip()

# cv_res %>% 
#   group_by(algo) %>% 
#   summarize(M = mean(loss), se = sd(loss)) %>% 
#   ggplot(aes(x=algo, y=M, ymin=M-se, ymax=M+se)) +
#   geom_pointrange() +
#   coord_flip()
```
All algorithms produce fits of similar quality. Data doesn't tell which to pick from among these. So it's basically up to us to choose whichever result makes most sense or we like for whatever reason. And to just caveat that it's not the "one true model."

```{r fit_all_models}

hc_args <- list(score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000)

models <- list(
  hc = partial(hc, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
  hc_intentdv = partial(hc, blacklist=intent_dv_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
  hc_theory = partial(hc, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
  mmhc_05 = partial(mmhc, restrict.args=list(alpha=.05), maximize.args = hc_args),
  mmhc_01 = partial(mmhc, restrict.args=list(alpha=.01), maximize.args = hc_args),
  mmhc_intentdv_05 = partial(mmhc, blacklist = intent_dv_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
  mmhc_intentdv_01 = partial(mmhc, blacklist = intent_dv_bl, restrict.args=list(alpha=.01), maximize.args = hc_args),
  mmhc_theory_05 = partial(mmhc, blacklist = theory_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
  mmhc_theory_01 = partial(mmhc, blacklist = theory_bl, restrict.args=list(alpha=.01), maximize.args = hc_args)
)

models <- mclapply(
    models, 
    function(f){f(train)}, 
    mc.cores = detectCores(logical=TRUE)
  )

arc_counts <- map(models, ~nrow(arcs(.x)))
arc_counts
```

```{r}
# this is the favorite son (most likely)
h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(models$hc_theory)))
plot(h)
```
HC theory looks nice and interpretable, tho there are a fair number of edges.

We should maybe think on our theory-based hierarchy structure a bit more too. Where does overparenting belong? Maybe the abstract as parents intent dv is the way to go?

```{r}
# # can bootstrap strength of arcs for winning model approach, focus interpretations on strength of arcs / parameterizations

## very slow!
# boot.strength(train, R=200, algorithm="hc", algorithm.args = list(score="custom", fun=cog_model_score_func))
```

```{r}

predict_node <- function(targVar, model_string, data){

  tempDF <- data
  tempDF[[targVar]] <- NA
  tempDF[[targVar]] <- as.numeric(tempDF[[targVar]])
  imputed <- make_predictions(model_string, data, nodes_to_predict = targVar, iter=1e4)
  return(imputed[[targVar]])
}

main_model <- models$hc_theory
model_string <- suppressWarnings(write_jags_model(main_model, train))

# takes ~3m on 8 cores -------
start_time <- Sys.time()

predictions <- test %>% mutate_all(function(x){NA}) %>% mutate_all(as.numeric)

x <- mclapply(
  colnames(test),
  predict_node,
  model_string = model_string,
  data = test,
  mc.cores=8
)

names(x) <- colnames(test)

print(Sys.time() - start_time)
```

Inspect absolute fit

```{r validation_plot fig.height=6, fig.width=10}
predictions <- as_tibble(x) %>% mutate(subj = 1:n()) %>% gather(varName, predValue, -subj) 
test_analyze <- test %>%
  gather(varName, value) %>% 
  mutate(predValue = predictions$predValue)

recode_nodes <- function(x){
  recode(x,
         "diseaseRare" = "Disease Rarity",
         "diseaseSevere" = "Disease Severity",
         "hb" = "Holistic Balance",
         "infantImmLimCap" = "IIS: Limited\nCapacity",
         "infantImmWeak" = "IIS: Weakness",
         "medSkept" = "Medical\nSkepticism",
         "nat" = "Naturalism",
         "overpar" = "Parental\nProtectiveness",
         "parentExpert" = "Parental\nExpertise",
         "vaccDanger" = "Vaccine\nDanger",
         "vaccEff" = "Vaccine\nEffectiveness",
         "vaccIntent" = "Vaccination\nIntentions",
         "vaccStrain" = "IIS: Vaccines\nStrain",
         "vaccTox" = "Vaccines\nToxicity")}

predObsCor <- cor(test_analyze$value,test_analyze$predValue)

corrDF <- test_analyze %>%
  mutate(varName = recode_nodes(varName)) %>%
  group_by(varName) %>%
  summarize(cor = cor(value,predValue)) %>%
  mutate(cor = format(round(cor,2),nsmall=2))

plt.valid <- test_analyze %>%
  mutate(varName = recode_nodes(varName)) %>%
  ggplot(aes(x=predValue, y=value)) + 
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha=.33) +
  geom_point(shape=1, size=.5, color="darkturquoise") + 
  geom_text(data=corrDF, aes(label=paste("r =", cor)),
            x=-Inf, y=Inf, hjust=-0.12, vjust=1.4,
            size = 10*.352777778,
            color="grey25") +
  # geom_smooth(method="lm") +
  coord_fixed() + 
  facet_wrap(~varName, nrow=2) + 
  scale_x_continuous("Predicted values", limits = c(0, 1)) +
  scale_y_continuous("Observed values", limits = c(0, 1)) +
  theme_bw(base_size = 10) +
  theme(strip.background = element_rect(fill="grey90"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

plt.valid
# ggsave(plot = plt.valid, filename = "../local/s1_predobs_plot.png", width=8.5, height=4)
```

Maybe compare predicted correlation matrix against true correlation matrix? Could bootstrap resample and create distributon of distances to represent null, see where this falls? Hope would be for non-sig result, that the reconstructed corr matrix is within resampling error. Maybe not necessary to do this tho?

# Study 1

NOTE: these code blocks are cut/pasted from other nb and not yet tested.

```{r s1}
# data is already loaded
source("../code/load-data-s1.R")

```

A total of `r nrow(s1_all)` people recruited from Amazon Mechanical Turk (mTurk) participated in this study conducted in August of 2017. Participants were paid $1.60 for about 8 minutes of their time. `r s1_n_excluded` participants (6%) failed at least one of two attention check questions and were excluded from further analysis, leaving a final sample of n = `nrow(d_demo)`. After completing all 14 scales, participants were asked standard demographics questions as well as a handful of questions about whether they were or were expecting to be a parent. They were also debriefed with a brief statement noting that vaccines are safe and pointing them toward a WHO website for further information.

```{r}

compute_alpha <- function(data, varName){
  data %>%
  filter(question_block == varName) %>%
  select(workerId, question, response_num_rev) %>%
  spread(question, response_num_rev) %>%
  remove_rownames() %>%
  column_to_rownames("workerId") %>%
  psych::alpha()
}

# scale reliability analyses

var_names <- as.character(unique(s1_long$question_block))
alpha_values <- map(var_names, ~compute_alpha(s1_long,.x)$total[[2]])
names(alpha_values) <- var_names

# do something to pretty this up

as_tibble(alpha_values) %>% 
  gather(scale, alpha)

```

# Study 2

```{r s2}
# load data
suppressWarnings(suppressMessages(source("../code/load-data-s2.R", chdir=TRUE)))
```

_Participants._ We recruited `r s2_meta$n_recruited` people to participate in a two-day study via mTurk in April 2018. Two days later, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r s2_meta$n_recruited_post` participants returning (`r s2_meta$n_eligible` invited, retaining `r round(s2_meta$n_recruited_post/s2_meta$n_eligible*100,1)`% of the Day 1 sample). Participants were paid \$1.35 for their participation in each phase of the study. `r s2_meta$n_failed_post` participants (`r round( (s2_meta$n_failed_post/s2_meta$n_recruited_post)*100,1)`%) failed at least one attention check on Day 2 and were excluded from further analysis. We also excluded from analyses `r s2_meta$n_duplicate` additional participants who accessed the second survey more than once. This left a final sample of `r s2_meta$n_complete` participants.

```{r}

recode_scales <- function(x){
  recode(x,
         "diseaseRare" = "Disease Rarity",
         "diseaseSevere" = "Disease Severity",
         "hb" = "Holistic Balance",
         "infantImmLimCap" = "IIS: Lim. Capacity",
         "infantImmWeak" = "IIS: Weakness",
         "medSkept" = "Med. Skepticism",
         "nat" = "Naturalism",
         "overpar" = "Parental Protectiveness",
         "parentExpert" = "Parental Expertise",
         "vaccDanger" = "Vaccine Danger",
         "vaccEff" = "Vaccine Eff.",
         "vaccIntent" = "Vaccination Intentions",
         "vaccStrain" = "IIS: Vaccines Strain",
         "vaccTox" = "Vaccines Toxicity")}

# create plot of differences for all 14 scales

s2_scored %>% 
  spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_scales(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank()
    ) +
  labs(title="Study 2", y = "Mean difference", x = "Belief scale", color="Intervention")
```
```{r}
# compare conditions on vaccIntent scale w/ regression model
# probably do ordinal model with brms

# fit evidence node

# generate model predictions + create plot
```

# Study 3a and 3b

```{r s3}
# load data
source("../code/load-data-s3.R")
```

_Participants._ We recruited `r s3_meta$n_recruited` people to participate in a two-day study via mTurk in April (Experiment 3A) and June (Experiment 3B) of 2018. One day after their initial participation, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r s3_meta$n_recruited_post` participants returning (`r s3_meta$n_eligible` invited, retaining `r round(s3_meta$n_recruited_post/s3_meta$n_eligible*100,1)`% of the Day 1 sample). Participants were paid \$1.35 for their participation in each phase of the study and were allowed to participate in part 2 up to two days after their initial participation in part 1. `r s3_meta$n_failed_post` participants (`r round( (s3_meta$n_failed_post/s3_meta$n_recruited_post)*100,1)`%) failed at least one attention check on Day 2 and were excluded from further analysis.  This left a final sample of `r s3_meta$n_complete` participants.

```{r}

# compare conditions on vaccIntent w/ regression model

# create plot of differences for all 14 scales

s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_scales(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank()
    ) +
  labs(title="Study 3a and 3b", y = "Mean difference", x = "Belief scale", color="Intervention")

# fit evidence node

# generate model predictions + create plot
```

# Study 4

```{r}
# load data
source("../code/load-data-s4.R")

s4_meta <- list(
  n_recruited = s4_wide %>% filter(workerId %in% s1_all$workerId) %>%  distinct(workerId) %>% nrow(),
  n_recruited_post = s4_wide %>% filter(workerId %in% s1_all$workerId) %>%  distinct(workerId) %>% nrow(),
  n_failed_post = s4_wide %>% 
    filter(check_5!=5 | check_3!=3) %>% 
    filter(workerId %in% s1_all$workerId) %>% distinct(workerId) %>% nrow(), #%>% ,
  n_complete =s4_wide %>% 
    filter(check_5==5, check_3==3, workerId %in% s1_all$workerId) %>% distinct(workerId) %>% nrow()
)
```

We attempted to contact and re-recruit as many of the `r nrow(d_bn)` participants who completed Study 1 to participate in a follow-up study in May of 2019. We were able to re-recruit `r s4_meta$n_recruited` participants and of these`r n_complete` successfully completed the study including passing all attention checks.

```{r}
s1 <- d_sum %>%
  rename(scale = question_block) %>%
  group_by(scale, workerId) %>% 
  summarize(s1 = mean(score, na.rm = T)) %>%
  ungroup()

combined <- s4_long  %>%
  # filter(check_5==5, check_3==3, Progress==100) %>% 
  filter(workerId %in% s1$workerId) %>%
  # select(workerId, scale, item, resp, vacc_news) %>%
  group_by(workerId, scale, vacc_news) %>%
  summarize(posttest = mean(resp)-4) %>%
  ungroup() %>% 
  right_join(s1) %>%
  rename(pretest = s1) %>%
  mutate(returned = !is.na(posttest))
```

```{r s4}
# compare effects in graph

combined %>% 
  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
  mutate(diff = posttest-pretest) %>%
  mutate(
    vacc_news = as.factor(vacc_news),
    scale = recode_scales(scale)
    ) %>%
  group_by(vacc_news,scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  # facet_wrap(~scale, scales="free") +
  theme_bw(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "right",
    panel.grid = element_blank()) +
  labs(title="Study 4", y = "Change scores", x = "Belief scale", color ="News\nexposure")

# compare conditions on vaccIntent w/ regression model

# fit evidence node

# generate model predictions + create plot
```

# Overall demographics

```{r}
# compute overall demographics for all studies for paper

# and create big table with table1 and t1kable()
```

### 2021-05-24 code/custom-structure-learning/cog-model-main.R

@@ -13,6 +13,7 @@ rescale_beta <- function(x, lower, upper) {
   # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
   
   N <- length(x)
+  N <- min(20, N) # bound to [.025,.975] 
   res <- (x - lower) / (upper - lower)
   res <- (res * (N - 1) + .5) / N
   

### 2021-05-24 code/custom-structure-learning/fit-cog-models-bnlearn.R

@@ -48,7 +48,7 @@ nodes <- c(
 theory_bl <- tiers2blacklist(
   list(
     c("hb","nat"),
-    c("medSkept","overpar", "parentExpert"), 
+    c("medSkept", "overpar", "parentExpert"),  # idk if overparenting makes sense here
     c("diseaseRare","diseaseSevere","vaccEff","vaccTox","vaccStrain",
       "vaccDanger","infantImmLimCap","infantImmWeak"), 
     c("vaccIntent") 
@@ -101,11 +101,14 @@ hc_args <- list(score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000)
 models <- list(
   hc = partial(hc, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
   hc_intentdv = partial(hc, blacklist=intent_dv_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
+  hc_idv_abspar = partial(hc, blacklist=intent_dv_abstract_parents_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
   hc_theory = partial(hc, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
   mmhc_05 = partial(mmhc, restrict.args=list(alpha=.05), maximize.args = hc_args),
   mmhc_01 = partial(mmhc, restrict.args=list(alpha=.01), maximize.args = hc_args),
   mmhc_intentdv_05 = partial(mmhc, blacklist = intent_dv_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
   mmhc_intentdv_01 = partial(mmhc, blacklist = intent_dv_bl, restrict.args=list(alpha=.01), maximize.args = hc_args),
+  mmhc_idv_abspar_05 = partial(mmhc, blacklist = intent_dv_abstract_parents_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
+  mmhc_idv_abspar_01 = partial(mmhc, blacklist = intent_dv_abstract_parents_bl, restrict.args=list(alpha=.01), maximize.args = hc_args),
   mmhc_theory_05 = partial(mmhc, blacklist = theory_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
   mmhc_theory_01 = partial(mmhc, blacklist = theory_bl, restrict.args=list(alpha=.01), maximize.args = hc_args)
 )
[…]

### 2021-05-24 code/load-data-s1.R

@@ -81,6 +81,10 @@ d3 <- d2 %>%
 
 # save dataframes for analysis
 
+s1_all <- left_join(d1, exclude_ids %>% mutate(exclude=1), by="workerId") %>% 
+  mutate(exclude = ifelse(is.na(exclude), 0 , 1)) %>% 
+  as_tibble()
+
 # demographics info (1 row per participant, demographics only)
 d_demo <- d3 %>%
   select(StartDate:comments) %>%
@@ -101,13 +105,14 @@ d_sum <- d_long %>%
   ungroup() %>%
   full_join(d_demo)
 
-# remove extraneous dataframes
-rm(d1, d2, d3)
+s1_long <- d_long
+s1_wide <- d_wide
+
 
 # make dataframe for heatmpa, efa, etc.
-d_efa <- d_wide %>% select(-c(StartDate, Duration, sex:comments)) %>%
-  remove_rownames() %>%
-  column_to_rownames("workerId")
+# d_efa <- d_wide %>% select(-c(StartDate, Duration, sex:comments)) %>%
+#   remove_rownames() %>%
+#   column_to_rownames("workerId")
 
 # make dataframe for graphical model fitting
 d_bn <- d_sum %>%
@@ -115,5 +120,8 @@ d_bn <- d_sum %>%
   spread(question_block, score) %>%
   remove_rownames() %>%
   column_to_rownames("workerId")
+
+# remove extraneous dataframes
+rm(d1, d2, d3, exclude_ids, d_long, d_sum)
 
 # setwd(working_dir) # reset working directory

### 2021-05-24 code/load-data-s2.R

@@ -2,25 +2,221 @@
 # Kara's code
 
 library(tidyverse)
-d_all <- read.csv("../data/study2_data.csv")[-1] %>%
-  # filter out anyone who failed attention checks
-  filter(hb_check_5_pretest == 1, hb_check_5_posttest == 1,
-         vaccEff_check_1_pretest == -3, vaccEff_check_1_posttest == -3, 
-         vaccDanger_check_3_pretest == -1, vaccDanger_check_3_posttest == -1, 
-         vaccTox_check_6_pretest == 2, vaccTox_check_6_posttest ==2) %>%
-  # remove attention checks from dataset
-  select(-contains("check"))
+
+# make refactoring functions
+as.numchar <- function(x){return(as.numeric(as.character(x)))}
+as.likert7 <- function(x){
+  x1 <- factor(tolower(as.character(x)),
+               levels = c("1", "2", "3", "4", "5", "6", "7"),
+               labels = c("strongly disagree", "disagree",
+                          "somewhat disagree",
+                          "neither agree nor disagree",
+                          "somewhat agree",
+                          "agree", "strongly agree"))
+  x2 <- recode(x1,
+               "strongly disagree" = -3,
+               "disagree" = -2,
+               "somewhat disagree" = -1,
+               "neither agree nor disagree" = 0,
+               "somewhat agree" = 1,
+               "agree" = 2,
+               "strongly agree" = 3)
+  return(x2)
+}
+
+d_raw_pre <- read.csv("../data/vaccine+many+beliefs+-+interv+1+pre+-+APRIL_May+1%2C+2018_13.38.csv", encoding = "latin1") %>%
+  rename(gender = Q49,
+         age = Q51,
+         ethnicity = Q53,
+         education = Q55,
+         job = Q57,
+         income = Q59,
+         political_party = Q61,
+         political_beliefs = Q63_1)
+
+# get question text
+question_text_pre <- d_raw_pre[c(1,2),] %>%
+  t() %>%
+  data.frame() %>%
+  rownames_to_column("question") %>%
+  rename("question_text" = "X1", question_importId = "X2") %>%
+  mutate(question_importId = gsub('.*:\\"', '', question_importId),
+         question_importId = gsub('\\"}', '', question_importId), 
+         question_text = gsub(".* - ", "", question_text),
+         question_text = gsub("Ûª", "'", question_text),
+         question_text = gsub("â", "'", question_text))
+
+# tidy dataset 
[…]

### 2021-05-24 code/load-data-s3.R

@@ -12,8 +12,25 @@ read_qualtrics <- function(fname){
   return(df)
 }
 
-pre <- read_qualtrics("../data/vacc+tox+interv+full+-+pre_April+3,+2019_15.38.csv")
-post <- read_qualtrics("../data/vacc+tox+interv+full+-+post_April+5,+2019_13.59.csv")
+
+
+
+
+# pre <- read_qualtrics("../data/vacc+tox+interv+full+-+pre_April+3,+2019_15.38.csv")
+# post <- read_qualtrics("../data/vacc+tox+interv+full+-+post_April+5,+2019_13.59.csv")
+
+pre_a <- read_qualtrics("../data/vacc+tox+interv+full+-+pre_April+3,+2019_15.38.csv") %>%
+  mutate(study="A")
+post_a <- read_qualtrics("../data/vacc+tox+interv+full+-+post_April+5,+2019_13.59.csv") %>%
+  mutate(study="A")
+
+pre_b <- read_qualtrics("../data/vacc+tox+interv+full2+-+pre_June+6,+2019_09.35.csv") %>%
+  mutate(study="B")
+post_b <- read_qualtrics("../data/vacc+tox+interv+full2+-+post_June+7,+2019_18.00.csv") %>%
+  mutate(study="B")
+
+pre <- bind_rows(pre_a, pre_b)
+post <- bind_rows(post_a, post_b)
 
 summarize <- dplyr::summarise
 
@@ -21,20 +38,72 @@ df_pre <- pre %>%
   filter(workerId!="e082cf59a57d4562") %>% # hashed manually
   filter(Progress==100, check_3==3, check_5==5) %>%
   mutate(parent = recode(parent, `23`=1, `24`=0)) %>%
-  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5, parent) %>%
-  gather(item, resp, -workerId, -parent) %>%
+  # select(-check_3, -check_5) %>% 
+  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5, parent,
+         sex, age, race, religion, educ, income, expecting, children, 
+         youngest_child, refuse, return, StartDate) %>%
+  rename(StartDate_pre = StartDate) %>% 
+  gather(item, resp, matches(".*(_[0-9])")) %>%
   mutate(item = paste0("pre_",item)) %>%
-  spread(item, resp)
+  spread(item, resp) %>% 
+  mutate(
+    sex = case_when(
+      sex==1 ~ "male",
+      sex==0 ~ "female",
[…]

### 2021-05-24 code/load-data-s4.R

@@ -13,22 +13,27 @@ read_qualtrics <- function(fname){
   return(df)
 }
 
-df4 <- read_qualtrics("../data/vaccine+many+beliefs+-+may2019_May+21,+2019_16.12.csv")
+df4_raw <- read_qualtrics("../data/vaccine+many+beliefs+-+may2019_May+21,+2019_16.12.csv")
 
-df4 <- df4 %>%
+s4_wide <- df4_raw %>% 
+  # filter(StartDate > ymd_hms("2019-05-19:00:00:00")) %>%
   filter(!duplicated(workerId)) %>%
-  filter(check_3==3, check_5==5) %>%
+  filter(Progress==100) %>% 
+  # filter(check_3==3, check_5==5) %>%
   mutate(StartDate = ymd_hms(StartDate)) %>%
   rename(Duration = Duration..in.seconds.) %>%
   select(workerId, matches(".*(_[0-9])"), vacc_news, vacc_news_freq, 
          news_time, news_favorable, vacc_conv, conv_favorable, outbreaks, outbreak_favorable, other,
          sex, age, race, religion, educ, income, 
          pol_party, pol_ind_leaning, parent, expecting, children,
-         youngest_child, refuse, comments, StartDate,
-         -check_3, -check_5
-         ) %>%
-  mutate_at(vars(matches(".*(_[0-9]*r)"), -pol_party_4_TEXT, -pol_rating_1), funs(8 - .)) %>% # reverse code
+         youngest_child, refuse, comments, StartDate
+  ) %>%
+  mutate_at(vars(matches(".*(_[0-9]*r)"), -pol_party_4_TEXT, -pol_rating_1), funs(8 - .))  # reverse code
+
+s4_long <- s4_wide %>%
+  filter(check_3==3, check_5==5) %>% 
   gather(item, resp, matches(".*(_[0-9])"), -pol_party_4_TEXT, -pol_rating_1) %>%
   mutate(scale = gsub("(_([0-9])+(r)*)","",item)) %>%
   mutate(resp = as.numeric(resp))
 
+rm(df4_raw)

### 2021-05-27 supplement/supplement-main.Rmd
work on supplement

@@
 ---
-title: "Supplement"
+title: "Supplemental Materials"
+subtitle: "Untitled vaccination intuitive theory paper"
+authors: "Derek Powell, Kara Weisman, and Ellen M. Markman"
 output:
-  pdf_document: default
-  html_document: default
+  pdf_document: 
+    latex_engine: xelatex
+    fig_caption: yes
+figsintext : yes
+always_allow_html: true
+header-includes:
+ \usepackage{float}
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.pos = 'H')
 ```
 
-```{r s1_load}
+# Modeling
+
+## Bayesian network parameterization
+
+Figure 1 shows an example of a simple Bayesian Network.
+The network itself is a _directed acyclic graph_ (DAG), a type of graphical model.
+Graphical models represent variables as nodes connected by edges.
+In a DAG, these edges are directed, flowing from parent to child, and are constrained so that they cannot form cycles or loops.
+In a Bayesian network, these directed edges encode conditional dependencies among variables, so that the conditional probability distribution for a given variable is defined only in terms of its direct parents.
+Together, a child node and its parents are called a _family_.
+
+```{r, echo=F, message=F, warning=F, fig.width=4, fig.height=3, fig.align='center', fig.cap="Example DAG representing some variables related to wildfires"}
+
+library(DiagrammeR)
+library(DiagrammeRsvg)
+
+grViz(
+  diagram = "
+  digraph causal {
+
+	  # Nodes
+	  node [shape = oval]
+	  D [label = 'Dry']
+	  H [label = 'Heat']
+	  F [label = 'Fire']
+	  S [label = 'Smoke']
+
+	  # Edges
+	  edge [color = black,
+	        arrowhead = vee]
+	  rankdir = LR
+	  D->F
+	  H->F
+	  F->S
+
+	  # Graph
+	  graph [overlap = true, fontsize = 8]
+	}"
+) %>%
+  export_svg() %>%
+  xml2::read_xml() %>%
+  xml2::write_xml("../local/graph.svg")
+
+knitr::include_graphics("../local/graph.svg")
+```
+
+The probability of a node Y can be defined from its parents X in many different ways.
+For binary nodes, the most flexible specification is a conditional probability table (CPT) with $2^n$ entries specifying the probability of Y given the entire joint probability distribution over X, where n is the number of parents X.
+Given the exponential complexity of the CPT, simpler functions are often used to specify the probability of the child node, such as the noisy-or and noisy-and-not functions.
+A noisy-or function assumes each of the parents are independent generative forces, each with a probability of generating the effect.
+A noisy-and-not function assumes each of the parents are independent preventive forces, specifying the probability of the child node as the probability that it is generated _and not_ prevented by any one of its possible preventers.
+We construct our cognitive model parameterization using a combination of these two functions, using a distribution sometimes referred to as a “DeMorgan gate” (Maaskant & Druzdel, 2008).
+In our model, the probability of the child node Y can be expressed as:
+
+$$y = 1 \big[1-(1-w_0)\prod_i(1-w_i)^{x_i}\big]\prod_j(1-w_j)^{x_j}$$
+
+Here, each parent is either a generative (i) or preventive (j) influence, that generates or prevents the child node with probability weight $w_i$ or $w_j$.
+The weight $w_0$ represents the “leak” probability, or the baseline probability that the child occurs without any other generating influences.
+The first term in brackets represents the probability that y is generated, or alternately, that not all of the possible generating forces fail to generate it.
+The second term represents the probability that it is not then prevented, or that all the preventing forces fail.
+
+A cognitive model composed of these types of relations is capable of capturing a causal system of non-interactive generative and preventive causes.
+Although people’s intuitive theories are likely more flexible than this, there is ample evidence that people are highly capable of reasoning according to these types of causal relationships (see Holyoak & Cheng, 2011 for a review), and moreover, that their causal learning is strongly biased toward learning these kinds of relations (e.g., Novick & Cheng, 2004).
+
+Given measures of participants’ credences in each of the parent beliefs $x_i$ and the child belief $y$, we assume the following beta regression model:
+
+$$ \mu = \exp\Bigg(\ln\Big(1 - \exp\big(\ln\big(1-w_0) + \sum_i(1-w_i)x_i\big)\big) \Big) + \ln\Big(\sum_i(1-w_i)(1-x_i)\Big)\Bigg) $$
+$$y \sim beta\big(\mu k, (1-\mu)k\big)$$
+
+Via maximum likelihood estimation, we estimate for each parent a discrete parameter $x_i$ determining whether the relationship is generative or preventive, and a continuous weight $w_i$ determining its strength.
+We also estimate $w_0$, the “leak probability” which is assumed to be generative, and _k_, a measure of dispersion in the responses _y_.
+
+## Structure learning
+
+One way to learn a Bayesian network structure from data is to search through a space of networks, “score” each and choose the best scoring network.
+Many scoring metrics are possible, but a directly meaningful one is p(d|G), the likelihood of the data given the graph structure.
+Asymptotically, this can be estimated using the Bayesian Information Criterion (BIC) (citation):
+
+$$BIC = k \ln (n) - 2\sum_{i}\hat{\ell}(x_i|x_{va(x_i)})$$
+
+Which we estimate using the maximum log-likelihood estimated for our statistical model, calculated as the sum of the maximum log-likelihood for each node given its parents, from a total of _k_ parameters and _n_ data points.
+
+### Generative model principle
+
+We constrained our search by applying what we call the “generative model principle”, assuming that the intuitive theory is a generative model, so that influence relations (edges) should flow from “generating” states of affairs toward states of affairs that result, such as from cause to effect.
+
+We used “abstractness” as a heuristic for constraining structure learning according to the generative model assumption: We assume that abstract states of affairs generate more specific and concrete states of affairs, so that edges should flow from the abstract toward the concrete.
+For instance, an abstract belief, such as the belief that natural things are better than artificial things, could influence more concrete beliefs, such as the belief that vaccines are dangerous.
+We consider “naturalism” to be an abstract belief because it is a belief about two large classes of entities, “natural things” and “artificial things”.
+The belief that vaccines are dangerous is relatively more concrete: the class of “vaccines” is relatively smaller and largely subsumed by the class of “artificial things.” Here, what is true of a larger class influences what we should think about the more specific class.
+
+Before constructing our model, we sorted the 14 measured beliefs into “tiers” based on how broad or abstract each belief was.
+For instance, we considered holistic balance and naturalism to be the most abstract beliefs among those we measured, and labeled these “worldviews”; we considered our outcome of interest, vaccine intentions, to be the most concrete measurement of a specific intended action.
+In between, we judged “medical skepticism”, “parental protectiveness”, and “parental expertise” to be more general than beliefs about diseases and vaccines, and so separated these into two tiers as well.
+We then applied the generative model principle to induce a partial-ordering of these beliefs, and a corresponding “blacklist” stipulating that certain edges must not appear in the final DAG.
+For instance, that there is no edge from vaccine intentions to naturalism.
+This constraint can be thought of as a strong prior over the possible structures of this intuitive theory (namely, P(G)=0 for any graph G not respecting the principle).
+
+### Cross validation of structure learning results
+
+To conduct an efficient search through the super-exponential space of DAGs, we tested several variants of two structure learning algorithms implemented in the “bnlearn” R package.
+The first is purely score-based “hill-climbing” algorithm (cite) and the second was a hybrid algorithm that combined the hill-climbing algorithm with a prior “restriction” phase that pruned down the space of DAGs.
+This pruning was accomplished with the “min-max parents and children” algorithm (cite), which can be tuned with a hyperparameter alpha, which we tested at several levels.
+To speed computations, we restricted the maximum number of parents in the graph to five for all nodes, as the complexity of the scoring function is exponential in the number of parents.
+In all resulting networks no node was found to have more than four parents, suggesting this did not impact the final results.
+
+We performed a series of 10-run 10-fold cross validation analyses to evaluate the success of these different structure learning strategies.
+In addition to the different algorithms, we also compared four different “blacklists” that imposed different constraints on the structure learning process.
+In addition to our theory-driven blacklist based on our generative model assumptions, we also explored unconstrained structure learning, and two additional blacklists: one which stipulated only that “intentions to vaccinate” should be a child node with no children of its own, and another that stipulated also that the most abstract beliefs “holistic balance” and “naturalism” should be allowed to have no parents other than each other.
+
+Figure X presents the results of these cross validation tests.
+As seen in the figure, all structure learning approaches produced models with similar out-of-sample performance, with more variability among folds and runs than between algorithms.
+Thus the cross-validation does not uniquely identify an optimal structure learning strategy.
+
+```{r s1_load, include=FALSE}
 source("../code/load-data-s1.R", chdir = TRUE)
@@
 library(tidyverse)
+library(brms)
 library(bnlearn)
@@
 source("../code/custom-structure-learning/cog-model-jags-tools.R")
+source("../code/custom-structure-learning/cog-model-estimate-evid-ratio.R")
 
@@
 
-```{r cross_validation}
+```{r load_data, include=F}
+suppressWarnings(suppressMessages(source("../code/load-data-s2.R", chdir=TRUE))) # dplyr being too verbose
+source("../code/load-data-s3.R") 
+source("../code/load-data-s4.R")
+```
+
+```{r cross_validation, echo=FALSE, fig.height=4, fig.width=6, fig.cap="Cross-validation performance for diffrent structure learning algorithms on the training data from Study 1."}
+
+## uncomment to re-run cross validation
 # source("../code/custom-structure-learning/fit-cog-models-bnlearn.R")
+
 cv_res <- readRDS("../local/cv-res.rds")
@@
   geom_boxplot() +
-  coord_flip()
+  coord_flip() +
+  labs(y = "Log-likelihood loss", x = "Algorithm")
 
-# cv_res %>% 
-#   group_by(algo) %>% 
-#   summarize(M = mean(loss), se = sd(loss)) %>% 
-#   ggplot(aes(x=algo, y=M, ymin=M-se, ymax=M+se)) +
-#   geom_pointrange() +
-#   coord_flip()
 ```
-All algorithms produce fits of similar quality.
-Data doesn't tell which to pick from among these.
-So it's basically up to us to choose whichever result makes most sense or we like for whatever reason.
-And to just caveat that it's not the "one true model."
 
-```{r fit_all_models}
+```{r fit_all_models, include=FALSE}
 
-hc_args <- list(score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000)
+# hc_args <- list(score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000)
+# 
+# models <- list(
+#   hc = partial(hc, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
+#   hc_intentdv = partial(hc, blacklist=intent_dv_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
+#   hc_theory = partial(hc, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
+#   mmhc_05 = partial(mmhc, restrict.args=list(alpha=.05), maximize.args = hc_args),
+#   mmhc_01 = partial(mmhc, restrict.args=list(alpha=.01), maximize.args = hc_args),
+#   mmhc_intentdv_05 = partial(mmhc, blacklist = intent_dv_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
+#   mmhc_intentdv_01 = partial(mmhc, blacklist = intent_dv_bl, restrict.args=list(alpha=.01), maximize.args = hc_args),
+#   mmhc_theory_05 = partial(mmhc, blacklist = theory_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
+#   mmhc_theory_01 = partial(mmhc, blacklist = theory_bl, restrict.args=list(alpha=.01), maximize.args = hc_args)
+# )
+# 
+# models <- mclapply(
+#     models, 
+#     function(f){f(train)}, 
+#     mc.cores = detectCores(logical=TRUE)
+#   )
+# 
+# arc_counts <- map(models, ~nrow(arcs(.x)))
+# arc_counts
+```
 
-models <- list(
-  hc = partial(hc, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
-  hc_intentdv = partial(hc, blacklist=intent_dv_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
-  hc_theory = partial(hc, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
-  mmhc_05 = partial(mmhc, restrict.args=list(alpha=.05), maximize.args = hc_args),
-  mmhc_01 = partial(mmhc, restrict.args=list(alpha=.01), maximize.args = hc_args),
-  mmhc_intentdv_05 = partial(mmhc, blacklist = intent_dv_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
-  mmhc_intentdv_01 = partial(mmhc, blacklist = intent_dv_bl, restrict.args=list(alpha=.01), maximize.args = hc_args),
-  mmhc_theory_05 = partial(mmhc, blacklist = theory_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
-  mmhc_theory_01 = partial(mmhc, blacklist = theory_bl, restrict.args=list(alpha=.01), maximize.args = hc_args)
+Nevertheless, there were substantial differences among the approaches, especially from the application of different constraints through blacklists.
+In particular, structure learning conducted without any constraints produced a very different model than structure learning under the generative model constraints; although many edges were shared, the directions of these edges were very frequently reversed.
+For instance, in structures learned without constraints, vaccine intentions is very frequently a parent node with many children, rather than a child of other nodes.
+These findings underscore the need for top-down constraints in the use of structure learning algorithms to identify plausible cognitive models for relations among beliefs.
+Models identified without these constraints may serve fine for prediction, but appear unlikely to lend themselves to clear interpretations as cognitive models.
+
+Without any clear guidance from cross validation and with a clear need to apply top-down constraints, we elected to advance our modeling with a model learned with the hill-climbing algorithm and our generative model constraints.
+This model contained more arcs than models estimated with hybrid algorithms, because these hybrid algorithms include a restriction phase based on correlations rather than our statistical model, we preferred the unrestricted approach.
+
+## Interpreting the model
+
+We used a bootstrapping procedure to estimate the confidence in each of the links in this model, conducting the structure learning procedure repeatedly for N bootstrapped resamples of the original training data.
+Figure X visualizes the frequency with which each arc appeared in the resulting model across these replicates, and figure x visualizes the model with the coefficients for each link encoded by color.
+[interpret the models]
+
+```{r fit_main_model, include=FALSE, cache=TRUE}
+set.seed(73566)
+
+theory_bl <- tiers2blacklist(
+  list(
+    c("hb","nat"),
+    c("medSkept", "overpar", "parentExpert"),  # idk if overparenting makes sense here
+    c("diseaseRare","diseaseSevere","vaccEff","vaccTox","vaccStrain",
+      "vaccDanger","infantImmLimCap","infantImmWeak"), 
+    c("vaccIntent") 
+    )
   )
 
-models <- mclapply(
-    models, 
-    function(f){f(train)}, 
-    mc.cores = detectCores(logical=TRUE)
-  )
-
-arc_counts <- map(models, ~nrow(arcs(.x)))
-arc_counts
+# this is the favorite son (most likely)
+main_model <- hc(train, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1e3, restart=5)
+h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))
+plot(h)
 ```
 
-```{r}
-# this is the favorite son (most likely)
-h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(models$hc_theory)))
-plot(h)
-```
-HC theory looks nice and interpretable, tho there are a fair number of edges.
-
-We should maybe think on our theory-based hierarchy structure a bit more too. Where does overparenting belong? Maybe the abstract as parents intent dv is the way to go?
-
-```{r}
+```{r, include=FALSE}
 # # can bootstrap strength of arcs for winning model approach, focus interpretations on strength of arcs / parameterizations
 
-## very slow!
-# boot.strength(train, R=200, algorithm="hc", algorithm.args = list(score="custom", fun=cog_model_score_func))
+# set.seed(49126)
+# 
+# train_noise <- train %>%
+#   mutate_all(~.x+rnorm(n(),0,.002))
+# 
+# cl = parallel::makeCluster(detectCores(logical=TRUE))
+# 
+# clusterCall(cl,
+#             function(){
+#               source("../code/custom-structure-learning/cog-model-main.R", chdir=TRUE)
+#               library(purrr)
+#               }
+#   )
+# 
+# ## very slow!
+# boot_res <- boot.strength(
+#   train_noise,  #train
+#   R = 200,
+#   algorithm = "hc",
+#   algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e3),
+#   cluster = cl
+#   )
+# 
+# stopCluster(cl)
+# 
+# saveRDS(boot_res,"../local/boot_res.rds")
+
+# this runs for hours and hits an error on optim(), 
+# possibly a bootstrap replicate was not full rank / produced huge colinearity?
+# possibly getting a perfect prediction and coef --> infinity for some variable?
+# maybe adding a tiny bit of noise would help?
 ```
 
-```{r}
+<fig: model arc visualizations >
+
+## Validating the model
+
+We validated our final model by testing its predictions on the held-out testing data.
+The models’ predictions are plotted against the true values for the testing data in figure X below.
+As seen in the figure, the quality of predictions varied across beliefs, but in many cases was quite strong.
+
+```{r, include=FALSE, cache=TRUE}
 
@@
 
-main_model <- models$hc_theory
+# main_model <- models$hc_theory
 model_string <- suppressWarnings(write_jags_model(main_model, train))
@@
 
-x <- mclapply(
+test_preds <- mclapply(
   colnames(test),
@@
   data = test,
-  mc.cores=8
+  mc.cores = detectCores(logical=TRUE)
 )
 
-names(x) <- colnames(test)
+names(test_preds) <- colnames(test)
 
@@
 
-Inspect absolute fit
+```{r validation_plot, echo=FALSE, fig.height=6, fig.width=10, fig.align="center", fig.cap="Model predictions versus observed values for test data from Study 1."}
 
-```{r validation_plot fig.height=6, fig.width=10}
-predictions <- as_tibble(x) %>% mutate(subj = 1:n()) %>% gather(varName, predValue, -subj) 
+predictions <- as_tibble(test_preds) %>% mutate(subj = 1:n()) %>% gather(varName, predValue, -subj)
+
 test_analyze <- test %>%
@@
   group_by(varName) %>%
-  summarize(cor = cor(value,predValue)) %>%
-  mutate(cor = format(round(cor,2),nsmall=2))
+  summarize(cor = cor(value,predValue)) #%>%
+  # mutate(cor = format(round(cor,2),nsmall=2))
 
@@
   geom_point(shape=1, size=.5, color="darkturquoise") + 
-  geom_text(data=corrDF, aes(label=paste("r =", cor)),
+  geom_text(data=corrDF, aes(label=paste("r =", round(cor,2))),
             x=-Inf, y=Inf, hjust=-0.12, vjust=1.4,
@@
 plt.valid
-# ggsave(plot = plt.valid, filename = "../local/s1_predobs_plot.png", width=8.5, height=4)
+```
+For each node, we also compared the Bayesian network model’s predictions to a maximal naive model using values on all other belief scales as predictors.
+This captures the degree to which each belief is predictable from the others as a whole.
+As shown in table X, the relatively simpler Bayesian network model does not sacrifice any predictive power compared to the suite of maximal naive models.
+
+Finally, we can also compare the quality of our model predictions to the test-retest reliability of the belief scales, establishing an overall upper-bound on the predictability of these measures.
+As shown in table X, the Bayesian network model did approximately as well as possible for seven beliefs, but fell short for the other seven.
+These failures suggest that the model is missing the information that would be needed to predict these beliefs.
+Although the notion of an intuitive theory presupposes that there is some collective unit of cognitive machinery defining people’s thinking about a particular domain, defining the boundaries of an intuitive theory is far from straightforward.
+It could be that new measurements are needed to fully capture these aspects of the intuitive theory, or these beliefs are sufficiently peripheral that they should not be considered part of the intuitive theory.
+Given the fuzzy nature of the problem, and of cognition more generally, we expect that these types of decisions will be driven as much by investigators' pragmatic concerns as they are by psychological facts.
+
+```{r, echo=FALSE, message=F, warning=F}
+# compare S1 model predictions to test-retest reliability?
+
+test_retest_cor <- function(node){
+    df <- s2_scored %>%
+    filter(condition == "noInterv", scale == node) %>%
+    spread(phase, mean)
+
+  return( cor(df$pre, df$post) )
+}
+
+test_retest <- tibble(node=as.character(colnames(d_bn))) %>%
+  mutate(fit = map_dbl(node, test_retest_cor))
+
+library(betareg)
+
+build_formula <- function(node, all_nodes){
+
+  lhs_nodes <- all_nodes[all_nodes != node]
+
+  f <- paste(node, "~ ")
+  for (n in lhs_nodes){
+    f <- paste0(f, n, " + ")
+  }
+
+  f <- substr(f,1,nchar(f)-3)
+
+  return(f)
+}
+
+make_model <- function(node){
+  nodes <- colnames(train)
+  betareg(as.formula(build_formula(node, nodes)), 
+        data = train)
+}
+
+calc_oos_fit <- function(model, node){ # break this up
+
+  p <- predict(model, test)
+
+  cor(p, test[,node])
+}
+
+## don't think we need to show this to make the points
+# calc_change <- function(model,node){
+#   df <- s1_scored %>%
+#     filter(condition=="diseaseRisk") %>%
+#     group_by(scale, phase) %>%
+#     summarize(mean = mean(mean)) %>%
+#     spread(phase, mean)
+#   
+#   df1 <- df %>%
+#     select(scale, pre) %>%
+#     spread(scale, pre)
+#   
+#   # df2 <- df %>%
+#   #   select(scale,post) %>%
+#   #   spread(scale, post)
+#   
+#   df1[2,] <- df1[1,]  # can swap to have all changing ...
+#   df1[2,"diseaseSevere"] <- df[6, "post"]
+#   
+#   p <- predict(model, df1)
+#   
+#   p[2] - p[1]
+# }
+
+oos_fits <- tibble(node=as.character(colnames(d_bn))) %>%
+  mutate(model = map(node, make_model)) %>%
+  mutate(fit = map2_dbl(model, node, calc_oos_fit)) #%>%
+  # mutate(pred_change = map2_dbl(model, node, calc_change))
+
+r_lower <- function(r,n){
+  map2_dbl(r, n, function(r,n){psych::r.con(r,n)[1]})
+}
+
+r_upper <- function(r,n){
+  map2_dbl(r, n, function(r,n){psych::r.con(r,n)[2]})
+}
+
+model_fits <- tibble(
+  varName = as.character(colnames(d_bn)),
+  # model_fit = c(.50, .66, .48, .63, .64, .56, .71, .35, .63, .90, .83, .86, .81, .87),
+  `test-retest` = test_retest$fit,
+  `maximal` = oos_fits$fit
+  ) %>%
+  mutate(varName = recode_nodes(varName)) %>% 
+  left_join(corrDF, by ="varName") %>% 
+  rename(`Bayesian network` = cor) %>% 
+  gather(model, fit, `Bayesian network`, `test-retest`, `maximal`) %>%
+  mutate(n = ifelse(model=="test_retest", 233, 226)) %>%
+  mutate(ul = r_upper(fit,n), ll= r_lower(fit,n))
+
+# model_fits %>%
+#   # filter(model!="full_fit") %>%
+#   # mutate(model = ifelse(model=="model_fit", "model", "test-retest")) %>%
+#   ggplot(aes(x=reorder(varName, -fit), y = fit, color=model, ymin = ll, ymax =ul)) +
+#   # geom_errorbar(position = position_dodge(width=.25)) +
+#   geom_pointrange(size =.25, position = position_dodge(width=.25)) +
+#   ylim(0,1) +
+#   theme_bw(base_size = 14) +
+#   labs(x="Belief", y = "Correlation") +
+#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+library(kableExtra)
+model_fits_print <- model_fits %>% 
+  select(varName, model, fit) %>% 
+  rename(
+    `Belief scale` = varName,
+    Measure = model
+  ) %>% 
+  spread(Measure, fit) %>% 
+  arrange(desc(`test-retest`))
+
+kbl(model_fits_print, booktabs = T,
+    digits = 3, 
+    align = c('l','c','c','c'),
+    # format = "latex",
+    caption = "Correlations for observed and predicted out-of-sample values") %>% 
+  kable_classic(full_width = F, html_font = "Cambria")
 ```
 
-Maybe compare predicted correlation matrix against true correlation matrix?
-Could bootstrap resample and create distributon of distances to represent null, see where this falls?
-Hope would be for non-sig result, that the reconstructed corr matrix is within resampling error.
-Maybe not necessary to do this tho?
+## Estimating the strength of evidence from changes in belief reports
 
-# Study 1
+To model the effects of participants observing evidence, we augmented the Bayesian network representing the cognitive model (shown in figure #) with an additional node representing the evidence.
+For instance, to model the effects of the “disease risk” intervention (Study 2), we added an evidence node as a child of “disease severity,” acting as virtual evidence for this node (following Pearl, 1988).
+To compute the CPT for this node as a function of disease severity beliefs, we estimated an _evidence ratio_ based on participants’ pretest and posttest credences in disease severity.
+To so do, we made use of the log-odds expression of Bayes rule,
 
-NOTE: these code blocks are cut/pasted from other nb and not yet tested.
+$$ O(h|d) = O(h) + ln(\frac{P(d|h=1)}{P(d|h=0)}) $$
 
-```{r s1}
-# data is already loaded
-source("../code/load-data-s1.R")
+Where the final term is the evidence ratio, defined as:
 
+$$ER = \frac{P(d|h=1)}{P(d|h=0)}$$
+
+The evidence ratio can be estimated from a model that is linear in the log-odds. This allowed for estimation of the evidence ratio from the with the following beta-regression model:
+
+$$logit(\mu) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})$$
+$$y \sim beta\big(\mu k, (1-\mu)k\big)$$
+
+Where x was a binary variable representing the presence (1) or absence (0) of evidence at posttest, and participants’ prior and posterior (pretest and posttest) credences were transformed by the logit function.
+This allowed us to estimate the log evidence ratio implied by participants’ reactions to the intervention (ER1) as well as the intervening time period without any explicit evidence (ER0).
+Then, we constructed a CPT consistent with ER1.
+For instance, with an evidence ratio below 1, we set:
+
+$$ p(evidence = 1 | x ) = .50*ER_1$$ 
+$$ p(evidence = 0 | x) = .50. $$
+
+We used this approach to predict how evidence (either interventions or real-world events) would change participants’ beliefs in Studies 2-4 (see results for each study below).
+It should be noted that, with the exception of the data used to estimate this evidence ratio, these are out-of-sample and out-of-task predictions.
+
+# Methods
+
+## Qualitative Studies
+
+Before discovering a network connecting beliefs, we first needed to identify a set of beliefs that might plausibly influence vaccination decisions and develop ways of measuring these beliefs.
+
+To do this, we drew on a variety of sources, including academic articles on anti-vaccine skepticism (e.g., CITE) and anti-vaccine websites, and a qualitative survey with self-identified vaccine skeptics (_n_=16) via Amazon Mechanical Turk (MTurk).
+[add details of this study here]
+
+Ultimately, we generated a list of 13 underlying beliefs that might influence people’s decisions about whether to vaccinate their children (_vaccine intentions_, the last of our 14 beliefs).
+We translated these qualitative insights into 14 psychometrically-valid scales.
+In developing these scales, we stipulated that each scale should be brief, composed of 4-6 statements for participants to evaluate; include at least one reverse-coded item; and be highly reliable (Cronbach’s α ≥ .80).
+After extensive piloting and refinement, we created 14 scales that met these criteria, including one preexisting scale (the “holistic balance” subscale from McFadden et al., 2010).
+
+## General Methods: Studies 1-4
+
+Studies 1-4 were conducted using online surveys (administered with Qualtrics survey software) with participants recruited from Amazon’s mechanical turk (mTurk) work distribution website.
+All studies were conducted between [dates].
+Repeat participation was prevented, with no participants involved in more than one study, except as noted in Study 4.
+A total of # participants completed their participation in these studies.
+All participants had gained approval for ≥ 95% of previous work (≥ 100 assignments); had verified US MTurk accounts; and indicated that they were ≥ 18 years old.
+See the participant demographics summary section below for full demographic information.
+
+### Method.
+
+Participants in all of these studies were asked to respond at least once to 14 belief scales measuring beliefs relevant to vaccination decisions (as previously described).
+Across all studies, these scales were each presented on a separate survey page.
+On each page, participants were asked to rate “how much you agree or disagree” on a 7-point scale from Strongly disagree (coded as -3) to Strongly agree (+3).
+Scales, and questions within each scale, were presented in a random order for each participant.
+Two to four attention checks (“Please select somewhat agree” and “Please select somewhat disagree”) were embedded within two to four randomly chosen scales.
+
+_Data processing._ For each scale, we generated a score for each participant by averaging their responses to each question in that scale (after reverse-coding where appropriate), and then rescaling these values to fall between 0 and 1, to represent a credence.
+
+## Study 1
+
+### Participants
+
+```{r s1_meta, include=FALSE}
+s1_meta <- list(
+  n_total = nrow(s1_all),
+  n_exclude = s1_all %>% filter(exclude==1) %>%  nrow(),
+  n_include =  s1_all %>% filter(exclude==0) %>%  nrow()
+)
 ```
 
-A total of `r nrow(s1_all)` people recruited from Amazon Mechanical Turk (mTurk) participated in this study conducted in August of 2017.
-Participants were paid $1.60 for about 8 minutes of their time.
-`r s1_n_excluded` participants (6%) failed at least one of two attention check questions and were excluded from further analysis, leaving a final sample of n = `nrow(d_demo)`.
+A total of `r s1_meta$n_total` people recruited from Amazon Mechanical Turk (mTurk) participated in this study conducted in August of 2017.
+Participants were paid \$1.60 for about 8 minutes of their time.
+`r s1_meta$n_exclude` participants (6%) failed at least one of two attention check questions and were excluded from further analysis, leaving a final sample of n = `r s1_meta$n_include`.
 After completing all 14 scales, participants were asked standard demographics questions as well as a handful of questions about whether they were or were expecting to be a parent.
@@
 
-```{r}
+### Results
+
+```{r, echo=FALSE}
 
@@
 
-as_tibble(alpha_values) %>% 
-  gather(scale, alpha)
+# as_tibble(alpha_values) %>% 
+#   gather(scale, alpha) %>% 
+#   knitr::kable()
 
@@
 
-# Study 2
+Figure X presents correlations among the 14 belief scales measured in Study 1.
+As the figure shows, there are strong correlations among many of the beliefs, suggesting they are related by an underlying intuitive theory.
 
-```{r s2}
-# load data
-suppressWarnings(suppressMessages(source("../code/load-data-s2.R", chdir=TRUE)))
-```
+```{r, echo=FALSE, message=F, fig.height=8, fig.width=8, fig.align='center', fig.cap = "Correlations among 14 the belief scales measured in Study 1.
+Correlation matrix is arranged by hierarhical clustering algorithm to highlight connections among beliefs."}
+# plot correlation matrix
+library(corrplot)
 
-_Participants._ We recruited `r s2_meta$n_recruited` people to participate in a two-day study via mTurk in April 2018.
-Two days later, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r s2_meta$n_recruited_post` participants returning (`r s2_meta$n_eligible` invited, retaining `r round(s2_meta$n_recruited_post/s2_meta$n_eligible*100,1)`% of the Day 1 sample).
-Participants were paid \$1.35 for their participation in each phase of the study.
-`r s2_meta$n_failed_post` participants (`r round( (s2_meta$n_failed_post/s2_meta$n_recruited_post)*100,1)`%) failed at least one attention check on Day 2 and were excluded from further analysis.
-We also excluded from analyses `r s2_meta$n_duplicate` additional participants who accessed the second survey more than once.
-This left a final sample of `r s2_meta$n_complete` participants.
-
-```{r}
-
-recode_scales <- function(x){
+recode_nodes2 <- function(x){
   recode(x,
@@
 
+temp_order <- corrMatOrder(cor(d_bn))
+
+temp_cor <- cor(d_bn)[temp_order, temp_order] %>%
+  data.frame() %>%
+  rownames_to_column("scale1") %>%
+  mutate(order1 = 1:14) %>%
+  gather(scale2, cor, -c(scale1, order1))
+
+temp_cor_df <- temp_cor %>%
+  full_join(temp_cor %>% 
+              distinct(scale1, order1) %>%
+              rename(scale2 = scale1, order2 = order1)) %>%
+  mutate_at(vars(scale1, scale2), recode_nodes2)
+
+ggplot(temp_cor_df,
+       aes(x = reorder(scale1, desc(order1)), 
+           y = reorder(scale2, order2), 
+           fill = cor)) +
+  geom_tile(color = "black") +
+  geom_text(aes(label = format(round(cor, 2), digits = 2)), size = 3.5) +
+  scale_fill_distiller(palette ="RdBu", limits = c(-1, 1),
+                     guide = guide_colorbar(barheight = 15)) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
+        axis.title = element_blank(),
+        aspect.ratio=1) +
+  labs(fill = "Corr.")
+```
+
+## Study 2
+
+### Participants.
+
+We recruited `r s2_meta$n_recruited` people to participate in a two-day study via mTurk in April 2018.
+Two days later, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r s2_meta$n_recruited_post` participants returning (`r s2_meta$n_eligible` invited, retaining `r round(s2_meta$n_recruited_post/s2_meta$n_eligible*100, 1)`% of the Day 1 sample).
+Participants were paid \$1.35 for their participation in each phase of the study.
+`r s2_meta$n_failed_post` participants (`r round( (s2_meta$n_failed_post/s2_meta$n_recruited_post)*100, 1)`%) failed at least one attention check on Day 2 and were excluded from further analysis.
+We also excluded from analyses `r s2_meta$n_duplicate` additional participants who accessed the second survey more than once.
+This left a final sample of `r s2_meta$n_complete` participants.
+
+### Method.
+
+Procedures for part 1 of Study 2 were nearly identical to Study 1, save for the use of four rather than two attention check questions, and the removal of debriefing statements at the end of the survey.
+On Day 2 (XX days later), participants completed a study that was designed to be very similar to Horne, Powell, et al.’s (2015) original study.
+Participants were randomly assigned to either the Disease Risk condition or the No Intervention condition, with the constraint that the distributions of participants’ Day 1 _vaccine intentions_ should be similar across the two conditions; we accomplished this by stratifying participants into groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
+
+Participants were presented with a slightly modified version of the “Disease Risk” intervention from Horne, Powell et al.’s (2015) original study, which was based on materials available on the CDC website (XX).
+Compared with Horne, Powell et al.
+(2015), we modified the intervention to present these parts in a fixed (rather than randomized) order, made slight changes to wording to improve clarity, and added a final statement summarizing the take-home message of the intervention.
+Full text of this intervention can be found in appendix B of these supplementary materials.
+
+After reading this intervention, participants completed the same 14 belief scales that they had completed on Day 1.
+Finally, participants were asked about their own vaccination behavior, including whether they had received a flu shot this season, and whether they planned to get a flu shot next season.
+They were also asked whether they were parents, how many children they had, and their children’s ages.
+Parents were then asked additional questions about their vaccination decisions regarding their children, including whether their children had received flu shots and would receive them next season; whether they had ever chosen to delay a vaccine for their child; refused a vaccine for their child; or obtained an exemption for their child to attend school without a vaccination.
+At the end of the survey, participants were asked whether they had paid attention, avoided distractions, and taken the survey seriously.
+
+Participants in the No Intervention condition (_n_=XX) completed an identical set of questions, except that they did not read any material before completing the 14 belief scales and the questions about their personal background.
+
+### Results
+
+```{r s2_mean_diff_plot, echo=F, message=F, warning=F, fig.height=4, fig.width=6, fig.align='center', fig.cap="Mean difference scores from pretest to posttest for the 14 belief scales measured in Study 2.
+Error bars represent 95\\% confidence intervals."}
+
 # create plot of differences for all 14 scales
@@
   mutate(
-    scale = recode_scales(scale),
+    scale = recode_nodes2(scale),
     condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
@@
 ```
-```{r}
+
+```{r s2_model, include=F}
+# -- TODO: recode phase/condition 5/25/21, 11:07 AM
+
 # compare conditions on vaccIntent scale w/ regression model
 # probably do ordinal model with brms
+s2_reg <- s2_long %>% 
+  filter(scale=="vaccIntent") %>% 
+  mutate(
+    phase = relevel(factor(phase), ref="pre"),
+    condition = relevel(factor(condition), ref="noInterv"),
+    response = response+4
+    )
 
-# fit evidence node
+fit_s2_vaccIntent <- brm(
+  response ~ phase*condition + (1|item) + (1|workerId),
+  family = cumulative("logit"),
+  data = s2_reg,
+  chains = 6,
+  cores = 6,
+  control = list(adapt_delta=.95),
+  seed = 46179,
+  file = "../local/fit_s2_vaccIntent.rds"
+)
 
-# generate model predictions + create plot
+summary(fit_s2_vaccIntent)
 ```
 
-# Study 3a and 3b
+We conducted a mixed-effects Bayesian linear regression to assess the effects of the disease risk intervention on the _Vaccination Intentions_ score, using the “brms” package for R (CITE).
+We regressed phase (Day 1 vs.
+2, dummy-coded with Day 1 as the baseline), condition (dummy-coded with the Disease Risk condition as the baseline, so as to assess difference scores in our condition of primary interest), and an interaction between phase and condition onto participants’ _Vaccination Intentions_ scores, including random intercepts by subject.
+In this model, the unique effect of the intervention on vaccination intention scores is assessed by the interaction term (indicating the unique effect of phase 2 for intervention versus no-intervention participants).
+The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: _b_ = -0.15, 95% CI: [-0.27, -0.04]).
+We consider this to be a full replication of Horne, Powell, et al.’s (XX) results.
+See Figure XX, upper left, for a visualization of these findings.
 
-```{r s3}
-# load data
-source("../code/load-data-s3.R")
+To model the changes in the belief network, we estimate the “evidence ratio” using the method described in the modeling section.
+The maximum likelihood estimate of the evidence ratio was XXX.
+To simulate the impacts of this evidence, we supplied virtual evidence to the disease severity node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
+
+Figure X shows the correlation between predicted and observed belief changes conditional on the disease risk intervention.
+
+```{r, echo=FALSE}
+# create cognitive model for predicting change scores
+base_model <- create_bnlearn_cog_model(main_model, train)
 ```
 
-_Participants._ We recruited `r s3_meta$n_recruited` people to participate in a two-day study via mTurk in April (Experiment 3A) and June (Experiment 3B) of 2018.
+```{r s2_model_pred, echo=FALSE, fig.height=4, fig.width=4, fig.align="center", fig.cap="Mean observed and predicted change scores for Experiment 2. Error bars represent 95\\% confidence intervals."}
+# Generate model predictions + create plot
+# odd, I remember the results being slightly better than this, job talk says r=.87
+obs_pred <- make_pred_df(s2_mdf, base_model, "diseaseSevere")
+
+cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
+
+(obs_pred_plot <- obs_pred %>% # a bit of a hack
+  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
+  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+  geom_point(size=2.5) +
+  geom_errorbar(alpha=.5, width=0) +
+  annotate(geom="text", x=.03, y=-.04, label= paste("r =", cor_val)) +
+  coord_cartesian(xlim=c(-.06,.06), ylim=c(-.06,.06)) +
+  theme_bw(base_size=14) +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+  theme(aspect.ratio = 1)) +
+  labs(title="Belief changes", subtitle="Experiment 2")
+
+# obs_pred %>%
+#   gather(type, Mean, observed, predicted) %>%
+#   ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
+#   geom_point() +
+#   geom_errorbarh(height=0)
+```
+
+## Studies 3a and 3b
+
+### Participants.
+
+We recruited `r s3_meta$n_recruited` people to participate in a two-day study via mTurk in April (Experiment 3A) and June (Experiment 3B) of 2018.
 One day after their initial participation, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r s3_meta$n_recruited_post` participants returning (`r s3_meta$n_eligible` invited, retaining `r round(s3_meta$n_recruited_post/s3_meta$n_eligible*100,1)`% of the Day 1 sample).
@@
 
-```{r}
+### Methods.
 
-# compare conditions on vaccIntent w/ regression model
+Procedures for studies 3a and 3b closely followed those of Study 2, but these studies tested the effects of a novel intervention aimed at dispelling concerns about toxic additives in vaccines.
+Full text of this intervention is available in appendix C of these supplementary materials.
+In study 3a, participants were randomly assigned to either a no-intervention control condition or to the novel vaccine toxins intervention.
+In study 3b, the no-intervention control condition was replaced with a brief control intervention [describing X].
 
+### Results.
+
+Due to the similarity of their designs, we combined data from studies 3a and 3b for analysis.
+As in study 2, we conducted a mixed-effects Bayesian linear regression to assess the effects of the vaccine toxins intervention on participants’ _Vaccination Intentions_ scores.
+The vaccine toxins intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: b = [statistics]).
+However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: b = [statistics]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
+
+```{r, echo=FALSE, message=F, warning=F, fig.align="center", fig.cap = "Mean difference scores from pretest to posttest for the 14 belief scales measured in Experiment 3.
+Error bars represent 95\\% confidence intervals."}
 # create plot of differences for all 14 scales
@@
 
-# fit evidence node
-
-# generate model predictions + create plot
 ```
 
-# Study 4
+```{r, include=FALSE}
+# compare conditions on vaccIntent w/ regression model
+# -- TODO: recode phase/condition 5/25/21, 11:07 AM
+s3_reg <- s3_long %>% 
+  filter(scale=="vaccIntent") %>% 
+  mutate(
+    phase = relevel(factor(phase), ref="pre"),
+    condition = relevel(factor(condition), ref="noInterv"),
+    response = resp
+    )
 
-```{r}
-# load data
-source("../code/load-data-s4.R")
+fit_s3_vaccIntent <- brm(
+  response ~ phase*condition + (1|item) + (1|workerId),
+  family = cumulative("logit"),
+  data = s3_reg,
+  chains = 6,
+  cores = 6,
+  control = list(adapt_delta=.95),
+  seed = 69568,
+  file = "../local/fit_s3_vaccIntent.rds"
+)
+
+summary(fit_s3_vaccIntent)
+```
+
+To model the effect of the vaccine toxicity intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the vaccine toxicity intervention as a child of the vaccine toxins belief node.
+The maximum likelihood estimate of the evidence ratio for the vaccine toxicity intervention was XXX.
+To simulate the impacts of this evidence, we supplied virtual evidence to the disease severity node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
+
+Figure X shows the correlation between predicted and observed belief changes conditional on the vaccine toxicity intervention.
+
+```{r, echo=F, fig.width=4, fig.height=4, fig.align="center", fig.cap="Mean observed and predicted change scores for Experiment 3. Error bars represent 95\\% confidence intervals."}
+
+# this is not quite getting vacctox node right, could be because of effects in the control condition.
+
+# fit evidence node
+obs_pred <- make_pred_df(s3_mdf, base_model, "vaccTox")
+
+cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
+
+(
+  obs_pred_plot <- obs_pred %>% 
+  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
+  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+  geom_point(size=2.5) +
+  geom_errorbar(alpha=.5, width=0) +
+  # coord_fixed(ratio=1) +
+  coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
+  annotate(geom="text", x=.05, y=-.1, label= paste("r =", cor_val)) +
+  theme_bw(base_size=14) +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+  theme(aspect.ratio = 1) +
+  labs(title="Belief changes",subtitle="Experiment 3a & 3b")
+)
+```
+
+## Study 4
+
+### _Participants_.
+
+```{r process_s4_data, include=FALSE}
+
+# combine with S1
+s4_reg <- s4_long  %>%
+  filter(workerId %in% s1_wide$workerId) %>% 
+  filter(scale!="check") %>% 
+  select(workerId, item, scale, resp, vacc_news) %>% 
+  mutate(phase = "posttest") %>% 
+  rename(response = resp) %>% 
+  bind_rows(
+    s1_long %>% 
+      as_tibble() %>% 
+      filter(workerId %in% s4_long$workerId) %>% 
+      rename(item = question, scale = question_block) %>% 
+      select(workerId, item, scale, response_num_rev) %>% 
+      mutate(phase = "pretest") %>% 
+      mutate(response = response_num_rev + 4) %>% 
+      select(-response_num_rev)
+  ) %>% 
+  group_by(workerId) %>% 
+  mutate(
+    vacc_news = first(na.omit(vacc_news)),
+    phase = relevel(factor(phase), ref="pretest")
+  ) # carry this through for each respondent
+
+s4_mdf <- s4_reg %>% 
+  mutate(phase = gsub("test","", phase)) %>% 
+  group_by(workerId, scale, phase, vacc_news) %>% 
+  summarize(Mean = mean(response, na.rm=TRUE)) %>% 
+  ungroup() %>% 
+  mutate(Mean = rescale_beta(Mean, 1, 7)) %>%
+  # gather(phase, mean, pre, post) %>%
+  spread(phase, Mean) %>%
+  mutate(evid = vacc_news)
 
@@
 We attempted to contact and re-recruit as many of the `r nrow(d_bn)` participants who completed Study 1 to participate in a follow-up study in May of 2019.
-We were able to re-recruit `r s4_meta$n_recruited` participants and of these`r n_complete` successfully completed the study including passing all attention checks.
+We were able to re-recruit `r s4_meta$n_recruited` participants and of these`r s4_meta$n_complete` successfully completed the study including passing all attention checks.
 
-```{r}
-s1 <- d_sum %>%
-  rename(scale = question_block) %>%
-  group_by(scale, workerId) %>% 
-  summarize(s1 = mean(score, na.rm = T)) %>%
-  ungroup()
+### _Results._
+
+```{r, include=FALSE}
+
+x <- s1_long %>% 
+  group_by(workerId, question_block) %>%
+  summarise(score = mean(response_num_rev, na.rm = T)) %>%
+  ungroup() %>%
+  rename(scale = question_block) #%>%
+  # group_by(scale, workerId) %>%
+  # summarize(s1 = mean(score, na.rm = T)) %>%
+  # ungroup()
 
@@
   # filter(check_5==5, check_3==3, Progress==100) %>% 
-  filter(workerId %in% s1$workerId) %>%
+  filter(workerId %in% x$workerId) %>%
   # select(workerId, scale, item, resp, vacc_news) %>%
@@
   ungroup() %>% 
-  right_join(s1) %>%
-  rename(pretest = s1) %>%
+  right_join(x) %>%
+  rename(pretest = score) %>%
   mutate(returned = !is.na(posttest))
+
+rm(x)
 ```
 
-```{r s4}
+```{r s4_diff_plot, echo=FALSE, message=F, warning=F, fig.align='center', fig.cap="Mean difference scores from pretest to posttest for the 14 belief scales measured in Study 3.
+Thick error bars represent standard errors, thin error bars represent 95\\% confidence intervals."}
 # compare effects in graph
@@
     vacc_news = as.factor(vacc_news),
-    scale = recode_scales(scale)
+    scale = recode_nodes2(scale)
     ) %>%
@@
   labs(title="Study 4", y = "Change scores", x = "Belief scale", color ="News\nexposure")
+```
+```{r, include=FALSE}
+# compare conditions on vaccIntent w/ regression model
+# not run yet 5/25/21, 11:52 AM
 
-# compare conditions on vaccIntent w/ regression model
-
-# fit evidence node
-
-# generate model predictions + create plot
+fit_s4_vaccIntent <- brm(
+  response ~ phase*vacc_news + (1|item) + (1|workerId),
+  family = cumulative("logit"),
+  data = s4_reg %>% filter(scale=="vaccIntent"),
+  chains = 6,
+  cores = 6,
+  control = list(adapt_delta=.95),
+  seed = 40725,
+  file = "../local/fit_s4_vaccIntent.rds"
+)
 ```
 
-# Overall demographics
+We again conducted a series of mixed-effects Bayesian linear regression models to assess the effect of recent news exposures on participants’ attitudes toward vaccines.
+Mirroring our prior analyses, we regressed phase (X 2017 vs.
+May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ _Vaccination Intentions _scores, including random intercepts by subject.
+To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure.
+Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (stats).
 
-```{r}
+To model the effects of news exposure we followed the same procedure as in previous studies, but here augmented the model with a node representing news exposure as a child of the vaccine intentions node.
+The maximum likelihood estimate of the evidence ratio for the vaccine toxicity intervention was XXX.
+To simulate the impacts of this evidence, we supplied virtual evidence to the disease severity node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
+
+Figure X shows the correlation between predicted and observed belief changes for participants who were aware of the New York measles outbreak in May 2019.
+
+```{r, echo=FALSE, fig.height=4, fig.width=4, fig.align="center", fig.cap="Mean observed and predicted change scores for Experiment 2. Error bars represent 95\\% confidence intervals."}
+# fit evidence node -- do diagnosis w/ bootstrapping? or just assume vaccIntent? I think just assume
+# generate model predictions + create plot
+
+obs_pred <- make_pred_df(s4_mdf, base_model, "vaccIntent")
+
+cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
+
+(obs_pred_plot <- obs_pred %>% # a bit of a hack
+  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
+  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+  geom_point(size=2.5) +
+  geom_errorbar(alpha=.5, width=0) +
+  annotate(geom="text", x=.04, y=-.04, label= paste("r =", cor_val)) +
+  coord_cartesian(xlim=c(-.07,.06), ylim=c(-.07,.06)) +
+  theme_bw(base_size=14) +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+  theme(aspect.ratio = 1)) +
+  labs(title="Belief changes",subtitle="Study 4 - vaccIntent")
+
+```
+
+## Participant demographic summary
+
+[table will go here]
+
+```{r, include=FALSE}
 # compute overall demographics for all studies for paper
+s1_demo <- s1_all %>% 
+  filter(exclude==0) %>% 
+  select(workerId, age, sex, race, religion, educ, income, parent)
+
+# s2_demo needs recoding / renaming
+# s3_demo good 
+# s4_demo same as s1
 
@@
 ```
+
+\newpage
+
+# Appendix A
+
+Scale items + reliability coefficients
+
+\newpage
+# Appendix B
+
+Disease severity intervention
+
+\newpage
+# Appendix C
+
+Vaccine toxicity intervention

### 2021-05-27 code/custom-structure-learning/cog-model-estimate-evid-ratio.R

@@ -21,22 +21,42 @@ evid_score_func <- function(data, par) {
 }
 
 get_evid_probs <- function(result){
-  # this is a heuristic/hack, could be made better but probably doesn't matter
+  # this is a bit hacky and maybe could be made more elegant but probably doesn't matter
   evid_ratio <- exp(result$par[1] + result$par[2])
   if (evid_ratio < 1) {
     p0 <- .90
   } else {
     p0 <- .50
   }
-  
+
   if (p0*evid_ratio >= 1) {
     p0 <- p0*.9/(p0*evid_ratio)
   }
-  
+
   p1 <- p0*evid_ratio
-  
+
   c(p0,p1)
 }
+
+to_odds <- function(p){
+  p/(1-p)
+}
+
+to_prob <- function(x){
+  x/(1+x)
+}
+
+
+# get_evid_probs <- function(result){
+#   # this is a heuristic/hack, could be made better but probably doesn't matter 
+#   # 5/25/21, 3:52 PM thought this would be better but it's bad actually
+#   log_evid_ratio <- result$par[1] + result$par[2]
+#   p0 <- .5
+#   # logit_p1 <- plogis(p0) + log_evid_ratio
+#   p1 <- to_prob( exp(logit(p0) + log_evid_ratio))
+# 
+#   c(p0, p1)
+# }
 
 
 evid_probs_to_cpt <- function(probs, var_name, evid_name = "evid"){
@@ -57,7 +77,6 @@ make_evid_cpt <- function(data, var_name, evid_name = "evid"){
   result <- find_evid_ratio(data)
   probs <- get_evid_probs(result)
   cpt <- evid_probs_to_cpt(probs, var_name, evid_name)
-  
   return(cpt)
 }
 
@@ -68,4 +87,97 @@ make_evid_cpt_custom <- function(var_name, evid_ratio, evid_name = "evid"){
   cpt <- evid_probs_to_cpt(probs, var_name, evid_name)
   
   return(cpt)
+}
+
+
+create_bnlearn_cog_model <- function(dag, data, evid_cpt = NULL, targetted_belief = NULL) {
+  arcs_df <- bnlearn_to_df(dag)
+  graph_list <- df_to_list(arcs_df)
+  bagOfModels <- lapply(graph_list, function(x){fit_node_cpt(x, data)})
+  model_string <- as.character(dag)
+  
+  if (!(is.null(evid_cpt))) {
+    bagOfModels$evid <- evid_cpt
[…]

### 2021-05-27 code/load-data-s2.R

@@ -232,40 +232,80 @@ d_post <- d_keep %>%
   rename_all(funs(gsub("_posttest", "", .))) %>%
   mutate(phase = "post")
 
-d <- bind_rows(d_pre, d_post) %>% 
-  gather(question, response, -c(workerId, phase)) %>%
-  mutate(phase = factor(phase,
-                        levels = c("pre", "post")),
-         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
-         # NOTE: "response" has already been reverse coded!
-         question = factor(question),
-         scale = factor(gsub("_.*$", "", question),
-                        levels = c("vaccIntent", "vaccDanger", "vaccEff", 
-                                   "vaccStrain", "vaccTox", 
-                                   "diseaseSevere", "diseaseRare", 
-                                   "infantImmLimCap", "infantImmWeak", 
-                                   "medSkept", "hb", "nat", 
-                                   "overpar", "parentExpert"))) %>%
-  full_join(d_demo) %>%
-  mutate(condition = factor(condition, levels = c("noInterv", "diseaseRisk"))) %>%
-  filter(!is.na(response), !is.na(workerId), !is.na(condition)) #%>%
-  # distinct()
+## problems here, redoing this below
 
-# score all scales
-d_scored <- d %>%
-  select(workerId, condition, phase, scale, response,
-         gender:duration_posttest) %>%
-  group_by(workerId, condition, phase, scale) %>%
-  mutate(response = as.numeric(response)) %>%
-  summarise(mean = mean(response, na.rm = TRUE)) %>%
-  ungroup() #%>%
-  # distinct()
+# d <- bind_rows(d_pre, d_post) %>% 
+#   gather(question, response, -c(workerId, phase)) %>%
+#   mutate(phase = factor(phase,
+#                         levels = c("pre", "post")),
+#          reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
+#          # NOTE: "response" has already been reverse coded!
+#          question = factor(question),
+#          scale = factor(gsub("_.*$", "", question),
+#                         levels = c("vaccIntent", "vaccDanger", "vaccEff", 
+#                                    "vaccStrain", "vaccTox", 
[…]

### 2021-05-27 code/load-data-s3.R

@@ -41,7 +41,7 @@ df_pre <- pre %>%
   # select(-check_3, -check_5) %>% 
   select(workerId, matches(".*(_[0-9])"), -check_3, -check_5, parent,
          sex, age, race, religion, educ, income, expecting, children, 
-         youngest_child, refuse, return, StartDate) %>%
+         youngest_child, refuse, return, StartDate, study) %>%
   rename(StartDate_pre = StartDate) %>% 
   gather(item, resp, matches(".*(_[0-9])")) %>%
   mutate(item = paste0("pre_",item)) %>%
@@ -129,9 +129,21 @@ df_demo <- df %>%
   mutate(days_between = StartDate_post - StartDate_pre)
 
 s3_pre <- df_pre
-s3 <- df
+s3_long <- df
 s3_scored <- df_scored
 s3_demo <- df_demo
+
+
+s3_mdf <- s3_scored %>% 
+  select(-change) %>% 
+  gather(phase, mean, pre, post) %>% 
+  mutate(condition = factor(condition)) %>% 
+  # filter(scale == "vaccTox") %>%
+  mutate(mean = rescale_beta(mean, 1, 7)) %>%
+  spread(phase, mean) %>%
+  mutate(condition = relevel(condition, ref="noInterv")) %>%
+  mutate(evid = ifelse(condition=="noInterv",0,1))
+
 
 s3_meta <- list(
   n_recruited = pre %>% filter(Progress==100) %>% distinct(workerId) %>% nrow(),

### 2021-05-27 code/load-data-s4.R

@@ -37,3 +37,4 @@ s4_long <- s4_wide %>%
   mutate(resp = as.numeric(resp))
 
 rm(df4_raw)
+

### 2021-05-27 supplement/supplement-main.Rmd
supp demo table created

@@
 subtitle: "Untitled vaccination intuitive theory paper"
-authors: "Derek Powell, Kara Weisman, and Ellen M. Markman"
+author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
 output:
@@
 
-```{r, echo=F, message=F, warning=F, fig.width=4, fig.height=3, fig.align='center', fig.cap="Example DAG representing some variables related to wildfires"}
+```{r dag_example, echo=F, fig.align='center', out.width = '40%', fig.cap="Example DAG illustrating some variables related to wildfiles."}
 
@@
 	}"
-) %>%
-  export_svg() %>%
-  xml2::read_xml() %>%
-  xml2::write_xml("../local/graph.svg")
-
-knitr::include_graphics("../local/graph.svg")
+)
 ```
@@
 
-$$y = 1 \big[1-(1-w_0)\prod_i(1-w_i)^{x_i}\big]\prod_j(1-w_j)^{x_j}$$
+$$P(y) = 1 \big[1-(1-w_0)\prod_i(1-w_i)^{x_i}\big]\prod_j(1-w_j)^{x_j}$$
 
@@
 
-```{r cross_validation, echo=FALSE, fig.height=4, fig.width=6, fig.cap="Cross-validation performance for diffrent structure learning algorithms on the training data from Study 1."}
+```{r cross_validation, echo=FALSE, fig.align='center', fig.height=3, fig.width=4, fig.cap="Cross-validation performance for diffrent structure learning algorithms on the training data from Study 1."}
 
@@
   ggplot(aes(x=reorder(algo, loss), y=loss)) +
-  geom_boxplot() +
+  geom_boxplot(fill="skyblue") +
   coord_flip() +
-  labs(y = "Log-likelihood loss", x = "Algorithm")
+  labs(y = "Log-likelihood loss", x = "Algorithm") +
+  theme_bw() +
+  theme(panel.grid = element_blank())
 
@@
 h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))
+
+```
+
+```{r main_model_plot, echo=F, fig.align='center', fig.width=7, fig.height=7, fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions."}
 plot(h)
@@
 
-# set.seed(49126)
-# 
+set.seed(49126)
+
 # train_noise <- train %>%
 #   mutate_all(~.x+rnorm(n(),0,.002))
-# 
-# cl = parallel::makeCluster(detectCores(logical=TRUE))
-# 
-# clusterCall(cl,
-#             function(){
-#               source("../code/custom-structure-learning/cog-model-main.R", chdir=TRUE)
-#               library(purrr)
-#               }
-#   )
-# 
-# ## very slow!
-# boot_res <- boot.strength(
-#   train_noise,  #train
-#   R = 200,
-#   algorithm = "hc",
-#   algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e3),
-#   cluster = cl
-#   )
-# 
-# stopCluster(cl)
-# 
-# saveRDS(boot_res,"../local/boot_res.rds")
+
+cl = parallel::makeCluster(detectCores(logical=TRUE))
+
+clusterCall(cl,
+            function(){
+              source("../code/custom-structure-learning/cog-model-main.R", chdir=TRUE)
+              library(purrr)
+              }
+  )
+
+## very slow!
+boot_res <- boot.strength(
+  train,  #train
+  R = 50,
+  algorithm = "hc",
+  algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e3),
+  cluster = cl
+  )
+
+stopCluster(cl)
+
+saveRDS(boot_res,"../local/boot_res.rds")
 
 # this runs for hours and hits an error on optim(), 
-# possibly a bootstrap replicate was not full rank / produced huge colinearity?
+# possibly a bootstrap replicate was not full rank / produced huge collinearity?
 # possibly getting a perfect prediction and coef --> infinity for some variable?
@@
 
-```{r validation_plot, echo=FALSE, fig.height=6, fig.width=10, fig.align="center", fig.cap="Model predictions versus observed values for test data from Study 1."}
+```{r validation_plot, echo=FALSE, fig.height=6, fig.width=10, fig.align="center", fig.cap="Model predictions versus observed values for test data from Study 1. Dashed lines represent perfect fits."}
 
@@
   varName = as.character(colnames(d_bn)),
-  # model_fit = c(.50, .66, .48, .63, .64, .56, .71, .35, .63, .90, .83, .86, .81, .87),
   `test-retest` = test_retest$fit,
@@
 
-```{r, echo=FALSE, message=F, fig.height=8, fig.width=8, fig.align='center', fig.cap = "Correlations among 14 the belief scales measured in Study 1.
+```{r, echo=FALSE, message=F, fig.height=7, fig.width=7, fig.align='center', fig.cap = "Correlations among 14 the belief scales measured in Study 1.
 Correlation matrix is arranged by hierarhical clustering algorithm to highlight connections among beliefs."}
@@
   geom_tile(color = "black") +
-  geom_text(aes(label = format(round(cor, 2), digits = 2)), size = 3.5) +
+  geom_text(aes(label = format(round(cor, 2), digits = 2)), size = 3) +
   scale_fill_distiller(palette ="RdBu", limits = c(-1, 1),
                      guide = guide_colorbar(barheight = 15)) +
-  theme_minimal() +
+  theme_minimal(base_size=12) +
   theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
@@
 
-[table will go here]
+The table below presents demographic information for participants across all four studies.
 
 ```{r, include=FALSE}
+library(table1)
+
 # compute overall demographics for all studies for paper
@@
   filter(exclude==0) %>% 
-  select(workerId, age, sex, race, religion, educ, income, parent)
-
-# s2_demo needs recoding / renaming
-# s3_demo good 
-# s4_demo same as s1
+  mutate(age = as.numeric(age)) %>% 
+  select(workerId, age, sex, race, religion, educ, income, parent) %>% 
+  mutate(study = "1") %>% 
+  mutate(
+    # educ = gsub(" or Professional Degree", "Degree", educ),
+    educ = gsub(" or Professional","", educ),
+    educ = gsub(" Education","", educ),
+    educ = gsub(" or Equivalent", "", educ),
+    educ = ifelse(grepl("Click to", educ),NA,educ),
+    income = gsub("30,0000","30,000", income),
+    religion = gsub(",","", religion),
+    parent = ifelse(parent=="", NA, parent)
+  )
+
+df_demo <- s1_demo %>% 
+  bind_rows(
+    s2_demo %>% 
+      select(workerId, age, sex, race, religion, educ, income, parent) %>% 
+      mutate(
+        study = "2",
+        )
+  ) %>% 
+  bind_rows(
+    s3_demo %>% 
+      mutate(
+        study = paste0("3",study),
+        sex = ifelse(sex=="female","Female","Male")
+        ) %>% 
+      select(workerId, age, sex, race, religion, educ, income, parent, study)
+  ) %>% 
+  bind_rows(
+    s1_demo %>% 
+      filter(workerId %in% s4_wide$workerId) %>% 
+      mutate(study = "4")
+  ) %>% 
+  mutate(
+    race = ordered(race,
+                   levels = c(
+                          "White",
+                          "Black or African American",
+                          "Hispanic/Latino",
+                          "Hawaiian or PI",
+                          "Asian",
+                          "Native American",
+                          "Other or prefer not to say"
+                          )
+                   ),
+    educ = ordered(educ,
+                   levels = c(
+                          "No Diploma",
+                          "High School",
+                          "Some Undergraduate",
+                          "Undergraduate Degree",
+                          "Some Graduate",
+                          "Graduate Degree",
+                          "Doctorate",
+                          "Prefer not to say"
+                          )
+                   ),
+    income = ordered(income,
+                     levels = c(
+                          "Less than $20,000",
+                          "$20,000 - $30,000",
+                          "$30,001 - $50,000",
+                          "$50,001 - $70,000",
+                          "$70,001 - $100,000",
+                          "More than $100,000",
+                          "Prefer not to say"
+                          )
+                     )
+
+  ) %>% 
+  mutate(
+    age = ifelse(age < 18,NA,age),
+    income = str_replace_all(income, "\\$",""),
+    study = paste("Study", study)
+    )
+
+label(df_demo$sex) <- "Gender"
+label(df_demo$age) <- "Age"
+label(df_demo$race) <- "Race"
+label(df_demo$religion) <- "Religion"
+label(df_demo$educ) <- "Education"
+label(df_demo$income) <- "Income ($)"
+label(df_demo$parent) <- "Parent?"
 
 # and create big table with table1 and t1kable()
+demographics_tbl <- table1::table1(~ sex + age + race + religion + educ + income + parent  | study, data=df_demo)
+
+table1::t1kable(demographics_tbl, full_width=F) %>% 
+  kable_classic()
+
 ```

### 2021-05-27 code/load-data-s2.R

@@ -213,7 +213,65 @@ d_demo <- d_keep %>%
          children_youngest_posttest, plan_parent_posttest,
          starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
          starts_with("comments"), starts_with("duration"), starts_with("attn_")
-         )
+         ) %>% 
+  rename(
+    sex = gender,
+    race = ethnicity,
+    educ = education,
+    ) %>% 
+  mutate(
+    sex = case_when(
+      sex==1 ~ "Male",
+      sex== 2 ~ "Female",
+      TRUE ~ "Other or prefer not to say"
+    ),
+    race = case_when(
+      race == 1 ~ "White",
+      race == 2 ~ "Hispanic/Latino",
+      race == 3 ~ "Black or African American",
+      race == 4 ~ "Hawaiian or PI",
+      race == 5 ~ "Asian",
+      race == 6 ~ "Native American",
+      race == 7 ~ "Other or prefer not to say"
+    ),
+    # religion = case_when(
+    #   religion == 1 ~ "Christian",
+    #   religion == 2 ~ "Muslim",
+    #   religion == 3 ~ "Jewish",
+    #   religion == 4 ~ "Hindu",
+    #   religion == 5 ~ "Buddhist",
+    #   religion == 6 ~ "Non-religious",
+    #   religion == 7 ~ "Other or prefer not to say"
+    # ),
+    religion = NA,
+    educ = case_when(
+      educ == 1 ~ "No Diploma",
+      educ == 2 ~ "High School",
+      educ == 3 ~ "Some Undergraduate",
+      educ == 4 ~ "Undergraduate Degree",
+      educ == 5 ~ "Some Graduate",
+      educ == 6 ~ "Graduate Degree",
+      educ == 7 ~ "Doctorate",
+      educ == 8 ~ "Prefer not to say"
+    ),
+    income = case_when(
+      income == 1 ~ "Less than $20,000",
+      income == 2 ~ "$20,000 - $30,000",
+      income == 3 ~ "$30,001 - $50,000",
+      income == 4 ~ "$50,001 - $70,000",
+      income == 5 ~ "$70,001 - $100,000",
+      income == 6 ~ "More than $100,000",
+      income == 0 ~ "Prefer not to say",
+    ),
+    parent = case_when(
+    is_parent_posttest == 0 ~ "No",
+    is_parent_posttest == 1 ~ "Yes"
+    )
[…]

### 2021-05-27 code/load-data-s3.R

@@ -54,9 +54,9 @@ df_pre <- pre %>%
     ),
     race = case_when(
       race == 1 ~ "White",
-      race == 2 ~ "Hispanic/latino",
-      race == 3 ~ "Black",
-      race == 4 ~ "hawaiian or PI",
+      race == 2 ~ "Hispanic/Latino",
+      race == 3 ~ "Black or African American",
+      race == 4 ~ "Hawaiian or PI",
       race == 5 ~ "Asian",
       race == 6 ~ "Native American",
       race == 7 ~ "Other or prefer not to say"
@@ -71,28 +71,29 @@ df_pre <- pre %>%
       religion == 7 ~ "Other or prefer not to say"
     ),
     educ = case_when(
-      educ == 1 ~ "No diplomae",
-      educ == 2 ~ "HS",
-      educ == 3 ~ "some undergrad",
-      educ == 4 ~ "undergrad",
-      educ == 5 ~ "some grad",
-      educ == 6 ~ "graduate",
-      educ == 7 ~ "doctorate",
-      educ == 8 ~ "prefer not to say"
+      educ == 1 ~ "No Diploma",
+      educ == 2 ~ "High School",
+      educ == 3 ~ "Some Undergraduate",
+      educ == 4 ~ "Undergraduate Degree",
+      educ == 5 ~ "Some Graduate",
+      educ == 6 ~ "Graduate Degree",
+      educ == 7 ~ "Doctorate",
+      educ == 8 ~ "Prefer not to say"
     ),
     income = case_when(
-      income == 1 ~ "0-20k",
-      income == 2 ~ "20-30k",
-      income == 3 ~ "30-50k",
-      income == 4 ~ "50-70k",
-      income == 5 ~ "70-100k",
-      income == 6 ~ "100k+",
-      income == 0 ~ "prefer not to say",
+      income == 1 ~ "Less than $20,000",
+      income == 2 ~ "$20,000 - $30,000",
+      income == 3 ~ "$30,001 - $50,000",
+      income == 4 ~ "$50,001 - $70,000",
+      income == 5 ~ "$70,001 - $100,000",
+      income == 6 ~ "More than $100,000",
+      income == 0 ~ "Prefer not to say",
     ),
     expecting = case_when(
       expecting == 23 ~ "yes", #F@!&ing qualtrics
       expecting == 24 ~ "no"
-    )
+    ),
+    parent = ifelse(parent==1, "Yes","No")
   )
 
 df_post <- post %>%

### 2021-05-27 supplement/supplement-main.Rmd
supplement draft nearly complete

@@
 author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
+date: "May 27, 2021 (DRAFT)"
 output:
@@
 
-```{r dag_example, echo=F, fig.align='center', out.width = '40%', fig.cap="Example DAG illustrating some variables related to wildfiles."}
+```{r dag_example, echo=F, fig.align='center', out.width = '40%', fig.cap="Example DAG illustrating some variables related to wildfires."}
 
@@
 main_model <- hc(train, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1e3, restart=5)
-h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))
-
-```
-
-```{r main_model_plot, echo=F, fig.align='center', fig.width=7, fig.height=7, fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions."}
-plot(h)
-```
-
-```{r, include=FALSE}
-# # can bootstrap strength of arcs for winning model approach, focus interpretations on strength of arcs / parameterizations
-
-set.seed(49126)
-
-# train_noise <- train %>%
-#   mutate_all(~.x+rnorm(n(),0,.002))
-
-cl = parallel::makeCluster(detectCores(logical=TRUE))
-
-clusterCall(cl,
-            function(){
-              source("../code/custom-structure-learning/cog-model-main.R", chdir=TRUE)
-              library(purrr)
-              }
-  )
-
-## very slow!
-boot_res <- boot.strength(
-  train,  #train
-  R = 50,
-  algorithm = "hc",
-  algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e3),
-  cluster = cl
-  )
-
-stopCluster(cl)
-
-saveRDS(boot_res,"../local/boot_res.rds")
-
-# this runs for hours and hits an error on optim(), 
-# possibly a bootstrap replicate was not full rank / produced huge collinearity?
-# possibly getting a perfect prediction and coef --> infinity for some variable?
-# maybe adding a tiny bit of noise would help?
-```
-
-<fig: model arc visualizations >
-
-## Validating the model
-
-We validated our final model by testing its predictions on the held-out testing data.
-The models’ predictions are plotted against the true values for the testing data in figure X below.
-As seen in the figure, the quality of predictions varied across beliefs, but in many cases was quite strong.
-
-```{r, include=FALSE, cache=TRUE}
-
-predict_node <- function(targVar, model_string, data){
-
-  tempDF <- data
-  tempDF[[targVar]] <- NA
-  tempDF[[targVar]] <- as.numeric(tempDF[[targVar]])
-  imputed <- make_predictions(model_string, data, nodes_to_predict = targVar, iter=1e4)
-  return(imputed[[targVar]])
-}
-
-# main_model <- models$hc_theory
-model_string <- suppressWarnings(write_jags_model(main_model, train))
-
-# takes ~3m on 8 cores -------
-start_time <- Sys.time()
-
-predictions <- test %>% mutate_all(function(x){NA}) %>% mutate_all(as.numeric)
-
-test_preds <- mclapply(
-  colnames(test),
-  predict_node,
-  model_string = model_string,
-  data = test,
-  mc.cores = detectCores(logical=TRUE)
-)
-
-names(test_preds) <- colnames(test)
-
-print(Sys.time() - start_time)
-```
-
-```{r validation_plot, echo=FALSE, fig.height=6, fig.width=10, fig.align="center", fig.cap="Model predictions versus observed values for test data from Study 1. Dashed lines represent perfect fits."}
-
-predictions <- as_tibble(test_preds) %>% mutate(subj = 1:n()) %>% gather(varName, predValue, -subj)
-
-test_analyze <- test %>%
-  gather(varName, value) %>% 
-  mutate(predValue = predictions$predValue)
+
+```
+
+```{r, include=F}
+source("../code/custom_plotting.R")
 
@@
          "vaccStrain" = "IIS: Vaccines\nStrain",
-         "vaccTox" = "Vaccines\nToxicity")}
+         "vaccTox" = "Vaccines\nToxicity"
+         )
+  }
+h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))
+
+c <- find_dag_coefs(main_model, train)
+```
+
+```{r main_model_plot, echo=F, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
+Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links."}
+
+map_to_viridis <- function(vec, bins=64, option="D"){
+
+  binned <- cut(vec, bins)
+  levels(binned) <- viridis::viridis(bins, option=option)
+
+  return(as.character(binned))
+}
+
+map_to_brewer <- function(vec, bins=11, option="RdYlBu"){
+  binned <- cut(vec, bins)
+  levels(binned) <- RColorBrewer::brewer.pal(bins, name=option)
+
+  return(as.character(binned))
+}
+
+z <- custom_plot.HydeNetwork(h)
+
+coefs <- tidy_coefs(c)
+
+coefs %>%
+  filter(parameter!="phi",parameter!="w_leak") %>%
+  rename(from = parameter) %>%
+  mutate(from = gsub("w_","",from)) %>%
+  select(to, from, value) %>%
+  merge(z$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
+  mutate(from = id) %>%
+  select(-id) %>%
+  merge(z$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
+  mutate(to = id) %>%
+  arrange(to,from) -> edge_df_mod
+  # select(value, id.x, id.y) %>%
+  # mutate(from = id.x, to = id.y)
+
+# z$nodes_df
+z$nodes_df <- z$nodes_df %>% mutate(label = recode_nodes(label))
+z$nodes_df$fontname <- "Helvetica"
+z$nodes_df$shape <- "ellipse"
+# z$nodes_df$fillcolor <- ifelse(z$nodes_df$id==13, "grey","white")
+z$nodes_df$fixedsize <- FALSE
+z$edges_df$penwidth <- abs(edge_df_mod$value)*2
+z$edges_df$penwidth <- 1.5
+# z$edges_df$label <- round(edge_df_mod$value,2)
+# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
+z$edges_df$color <- map_to_brewer(edge_df_mod$value, option="RdBu")
+render_graph(z)
+
+```
+
+```{r, include=FALSE}
+# # can bootstrap strength of arcs for winning model approach, focus interpretations on strength of arcs / parameterizations
+
+set.seed(49126)
+
+# train_noise <- train %>%
+#   mutate_all(~.x+rnorm(n(),0,.002))
+if (!file.exists("../local/boot_res.rds")){
+  cl = parallel::makeCluster(detectCores(logical=TRUE))
+
+  clusterCall(cl,
+              function(){
+                source("../code/custom-structure-learning/cog-model-main.R", chdir=TRUE)
+                library(purrr)
+                }
+    )
+
+  ## very slow!
+  boot_res <- boot.strength(
+    train,  #train
+    R = 200,
+    algorithm = "hc",
+    algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e3),
+    cluster = cl
+    )
+
+  stopCluster(cl)
+
+  saveRDS(boot_res,"../local/boot_res.rds")
+} else {
+  boot_res <- readRDS("../local/boot_res.rds")
+}
+
+# this runs for hours and hits an error on optim(), 
+# possibly a bootstrap replicate was not full rank / produced huge collinearity?
+# possibly getting a perfect prediction and coef --> infinity for some variable?
+# maybe adding a tiny bit of noise would help?
+```
+
+```{r boot_strength_plot, echo=F, message=F, fig.cap="Bootstrapped confidence estimates for Bayesian network edges.
+Edge color indicates frequency with which edges appeared when conducting search across X bootstrap replicates.
+Only edges appearing in at least 20\\% of graphs are shown."}
+
+hyde_str <- df_to_hyde_string(boot_res %>% filter(strength>.2, direction>0) %>% select(from,to))
+h2 <- HydeNetwork(as.formula(hyde_str))
+# plot(h2)
+
+z2 <- custom_plot.HydeNetwork(h2)
+boot_res %>%
+  filter(direction>0, strength>.2) %>% 
+  # filter(parameter!="phi",parameter!="w_leak") %>%
+  # rename(from = parameter) %>%
+  # mutate(from = gsub("w_","",from)) %>%
+  select(to, from, strength) %>%
+  merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
+  mutate(from = id) %>%
+  select(-id) %>%
+  merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
+  mutate(to = id) %>%
+  arrange(to,from) -> edge_df_mod
+
+# z$nodes_df
+z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
+z2$nodes_df$fontname <- "Helvetica"
+z2$nodes_df$shape <- "ellipse"
+# z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$id==13, "grey","white")
+z2$nodes_df$fixedsize <- FALSE
+z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
+z2$edges_df$penwidth <- 2
+# z$edges_df$label <- round(edge_df_mod$value,2)
+# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
+z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
+# z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
+
+render_graph(z2)
+```
+
+## Validating the model
+
+We validated our final model by testing its predictions on the held-out testing data.
+The models’ predictions are plotted against the true values for the testing data in figure X below.
+As seen in the figure, the quality of predictions varied across beliefs, but in many cases was quite strong.
+
+```{r, include=FALSE, cache=TRUE}
+
+predict_node <- function(targVar, model_string, data){
+
+  tempDF <- data
+  tempDF[[targVar]] <- NA
+  tempDF[[targVar]] <- as.numeric(tempDF[[targVar]])
+  imputed <- make_predictions(model_string, data, nodes_to_predict = targVar, iter=1e4)
+  return(imputed[[targVar]])
+}
+
+# main_model <- models$hc_theory
+model_string <- suppressWarnings(write_jags_model(main_model, train))
+
+# takes ~3m on 8 cores -------
+start_time <- Sys.time()
+
+predictions <- test %>% mutate_all(function(x){NA}) %>% mutate_all(as.numeric)
+
+test_preds <- mclapply(
+  colnames(test),
+  predict_node,
+  model_string = model_string,
+  data = test,
+  mc.cores = detectCores(logical=TRUE)
+)
+
+names(test_preds) <- colnames(test)
+
+print(Sys.time() - start_time)
+```
+
+```{r validation_plot, echo=FALSE, fig.height=6, fig.width=10, fig.align="center", fig.cap="Model predictions versus observed values for test data from Study 1. Dashed lines represent perfect fits."}
+
+predictions <- as_tibble(test_preds) %>% mutate(subj = 1:n()) %>% gather(varName, predValue, -subj)
+
+test_analyze <- test %>%
+  gather(varName, value) %>% 
+  mutate(predValue = predictions$predValue)
 
@@
 
-```{r, include=FALSE}
+```{r, echo=FALSE, message=F, warning=F}
 library(table1)
@@
 
-table1::t1kable(demographics_tbl, full_width=F) %>% 
-  kable_classic()
+table1::t1kable(demographics_tbl) %>% 
+  kable_classic(latex_options="scale_down")
 

### 2021-06-09 supplement/supplement-main.Rmd
supplement updates

@@
 author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
-date: "May 27, 2021 (DRAFT)"
+date: "Jun 1, 2021 (DRAFT)"
 output:
@@
 source("../code/custom-structure-learning/cog-model-estimate-evid-ratio.R")
-
+source("../code/custom_plotting.R")
 d_bn_scaled <- d_bn %>%
@@
 ```{r, include=F}
+
+h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))
+
+c <- find_dag_coefs(main_model, train)
+```
+
+```{r main_model_plot, echo=F, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
+Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links."}
+
 source("../code/custom_plotting.R")
@@
   }
-h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))
-
-c <- find_dag_coefs(main_model, train)
-```
-
-```{r main_model_plot, echo=F, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
-Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links."}
 
@@
 z$edges_df$color <- map_to_brewer(edge_df_mod$value, option="RdBu")
+
+export_graph(z, "../local/main-graph.pdf")
 render_graph(z)
 
+```
+
+```{r}
+## NOTE: I just can't figure out how to nicely display the graph and legend in code
+## it's must easier just to export them both and then combine with a graphics app
+
+main_graph_legend <- (tibble(
+  weight = seq(min(edge_df_mod$value), max(edge_df_mod$value), length=11),
+) %>% 
+  ggplot(aes(y=1, x = weight, fill = weight)) +
+  geom_tile() +
+  scale_fill_distiller(palette="RdBu", direction=1)) %>% 
+  cowplot::get_legend()
+
+cowplot::ggdraw(main_graph_legend)
 ```
@@
 
-set.seed(49126)
+set.seed(77267)
 
@@
     algorithm = "hc",
-    algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e3),
+    algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e4),
     cluster = cl
@@
 
-# this runs for hours and hits an error on optim(), 
-# possibly a bootstrap replicate was not full rank / produced huge collinearity?
-# possibly getting a perfect prediction and coef --> infinity for some variable?
-# maybe adding a tiny bit of noise would help?
 ```
@@
 render_graph(z2)
+```
+
+```{r}
+boot_graph_legend <- (tibble(
+  Probability = seq(min(edge_df_mod$strength), max(edge_df_mod$strength), length=11),
+) %>% 
+  ggplot(aes(y=1, x = Probability, fill = Probability)) +
+  geom_tile() +
+  scale_fill_distiller(palette="RdPu", direction=1)
+) %>% 
+  cowplot::get_legend()
+
+cowplot::ggdraw(boot_graph_legend)
 ```
@@
 
-$$ O(h|d) = O(h) + ln(\frac{P(d|h=1)}{P(d|h=0)}) $$
+$$ ln\big(O(h|d)\big) = ln \big(O(h)\big) + ln\Bigg(\frac{P(d|h=1)}{P(d|h=0)}\Bigg) $$
 
@@
 ### Results
-
-```{r, echo=FALSE}
-
-compute_alpha <- function(data, varName){
-  data %>%
-  filter(question_block == varName) %>%
-  select(workerId, question, response_num_rev) %>%
-  spread(question, response_num_rev) %>%
-  remove_rownames() %>%
-  column_to_rownames("workerId") %>%
-  psych::alpha()
-}
-
-# scale reliability analyses
-
-var_names <- as.character(unique(s1_long$question_block))
-alpha_values <- map(var_names, ~compute_alpha(s1_long,.x)$total[[2]])
-names(alpha_values) <- var_names
-
-# do something to pretty this up
-
-# as_tibble(alpha_values) %>% 
-#   gather(scale, alpha) %>% 
-#   knitr::kable()
-
-```
 
@@
   geom_text(aes(label = format(round(cor, 2), digits = 2)), size = 3) +
-  scale_fill_distiller(palette ="RdBu", limits = c(-1, 1),
-                     guide = guide_colorbar(barheight = 15)) +
+  scale_fill_distiller(palette ="RdBu", limits = c(-1, 1), direction = 1,
+                     guide = guide_colorbar(barheight = 15)) + # direction = -1
   theme_minimal(base_size=12) +
@@
 
-```{r s2_model, include=F}
+```{r s2_model, echo=FALSE, message=F, warning=F}
 # -- TODO: recode phase/condition 5/25/21, 11:07 AM
@@
 
-summary(fit_s2_vaccIntent)
-```
-
-We conducted a mixed-effects Bayesian linear regression to assess the effects of the disease risk intervention on the _Vaccination Intentions_ score, using the “brms” package for R (CITE).
-We regressed phase (Day 1 vs.
-2, dummy-coded with Day 1 as the baseline), condition (dummy-coded with the Disease Risk condition as the baseline, so as to assess difference scores in our condition of primary interest), and an interaction between phase and condition onto participants’ _Vaccination Intentions_ scores, including random intercepts by subject.
-In this model, the unique effect of the intervention on vaccination intention scores is assessed by the interaction term (indicating the unique effect of phase 2 for intervention versus no-intervention participants).
-The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: _b_ = -0.15, 95% CI: [-0.27, -0.04]).
+make_table <- function(fit, caption=NULL){
+  fit_sum <- summary(fit)
+
+  tbl_sum <- as_tibble(fit_sum$fixed, rownames="Term") %>% 
+    bind_rows(
+      as_tibble(fit_sum$random$item, rownames="Term") %>% 
+        mutate(Term = paste0("item_",Term))
+    ) %>% 
+    bind_rows(
+      as_tibble(fit_sum$random$workerId, rownames="Term") %>% 
+        mutate(Term = paste0("subj_",Term))
+    ) %>% 
+    select(-Rhat, -Est.Error, -Bulk_ESS, -Tail_ESS)
+
+  kableExtra::kbl(tbl_sum, digits = 2, booktabs = T, caption=caption) %>% 
+    kableExtra::kable_classic(full_width=F)
+}
+
+make_table(fit_s2_vaccIntent, "Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 2.")
+
+```
+
+We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the _Vaccination Intentions_ scale items, using the “brms” package for R (CITE).
+We regressed responses on phase (Phase 1 vs.
+2, dummy-coded with Phase 1 as the baseline), condition (dummy-coded with the Disease Risk condition as the baseline, so as to assess difference scores in our condition of primary interest), and the interaction between phase and condition.
+We included random intercepts by subject and scale item.
+In this model, the unique effect of the intervention on vaccination intention responses is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants).
+The disease risk intervention increased participants’ vaccination intention ratings (see Table X).
 We consider this to be a full replication of Horne, Powell, et al.’s (XX) results.
-See Figure XX, upper left, for a visualization of these findings.
 
@@
 
+```{r echo=F, message=F}
+
+# this is some code to genrate predictions of vacc intent change based on
+# hypothetical interventions
+
+add_evid_node_custom <- function(bnlearn_model, parents_string, evid_cpt) {
+
+  model_list <- lapply(bnlearn_model, function(x){x$prob})
+  model_list$evid <- evid_cpt
+
+  model_string <- modelstring(bnlearn_model)
+  model_string <- paste0(model_string,"[evid|", parents_string, "]")
+  model_network <- model2network(model_string)
+  predModel <- custom.fit(model_network, dist = model_list)
+
+  return(predModel)
+}
+
+node_names <- nodes(main_model)
+vaccIntent_pred_results <- data.frame(scale=nodes(main_model), value = NA)
+
+for (i in 1:length(node_names)) {
+  if (cor(d_bn[,"vaccIntent"], d_bn[,node_names[i]]) >= 0) {
+    evid_ratio <- 2
+  } else {
+    evid_ratio <- .5
+  }
+  evid_cpt <- hyde_to_bn_cpt(make_evid_cpt_custom(node_names[i], evid_ratio))
+  vaccIntent_predNet <- add_evid_node_custom(base_model, node_names[i], evid_cpt)
+
+  preds <- cogModel_predictions(vaccIntent_predNet) %>%
+    filter(scale=="vaccIntent")
+
+  vaccIntent_pred_results[i,"value"] <- preds[1,"Mean"]
+
+}
+
+## combine this with observed correlations from study 1
+
+corrmat <- cor(d_bn)
+
+interv_sim <- corrmat["vaccIntent",] %>%
+  tibble(scale = names(.), value = ., type="correlation") %>%
+  bind_rows(vaccIntent_pred_results %>% mutate(type="model_pred")) %>%
+  spread(type,value)
+
+interv_sim %>%
+  ggplot(aes(x=abs(correlation), y = model_pred)) +
+  geom_point()
+
+(pred_change_plot <- interv_sim %>% 
+  filter(scale!="vaccIntent") %>%
+    mutate(scale = recode_nodes2(scale)) %>% 
+  ggplot(aes(x=reorder(scale, model_pred), y = model_pred)) + 
+  geom_bar(stat="identity") + 
+  coord_flip() +
+  labs(x="Targeted belief", y = "Predicted change in intentions") +
+  theme_bw(base_size=22) +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+  theme(aspect.ratio = 1.5))
+
+```
+
 ### Participants.
@@
 Due to the similarity of their designs, we combined data from studies 3a and 3b for analysis.
-As in study 2, we conducted a mixed-effects Bayesian linear regression to assess the effects of the vaccine toxins intervention on participants’ _Vaccination Intentions_ scores.
-The vaccine toxins intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: b = [statistics]).
-However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: b = [statistics]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
+As in study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine toxins intervention on participants’ Vaccination Intentions scores.
+The vaccine toxins intervention improved participant’s vaccination intention scores relative to the control conditions.
+However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions, suggesting that these attitudes were also being influenced by other factors during the course of the study.
 
@@
 
-```{r, include=FALSE}
+```{r, echo=FALSE, message=F, warning=F}
 # compare conditions on vaccIntent w/ regression model
@@
 
-summary(fit_s3_vaccIntent)
+make_table(fit_s3_vaccIntent, "Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3.")
 ```
@@
 ```
-```{r, include=FALSE}
+
+```{r, echo=FALSE, message=F, warning=F}
 # compare conditions on vaccIntent w/ regression model
@@
 )
-```
-
-We again conducted a series of mixed-effects Bayesian linear regression models to assess the effect of recent news exposures on participants’ attitudes toward vaccines.
-Mirroring our prior analyses, we regressed phase (X 2017 vs.
-May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ _Vaccination Intentions _scores, including random intercepts by subject.
+
+make_table(fit_s4_vaccIntent, "Bayesian regression model coefficients for model of Vaccine Intentions in Study 4.")
+```
+
+Mirroring our analyses of interventions, we regressed responses to the vaccine intentions scale items on predictors for phase (X 2017 vs.
+May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item.
 To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure.
-Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (stats).
+Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (see Table X).
 
@@
 # and create big table with table1 and t1kable()
-demographics_tbl <- table1::table1(~ sex + age + race + religion + educ + income + parent  | study, data=df_demo)
+# trying wrapping with factor() to get it to print integer counts
+demographics_tbl <- table1::table1(~ factor(sex) + age + factor(race) + factor(religion) + factor(educ) + factor(income) + factor(parent)  | study, data=df_demo)
 
@@
 
+```{r, echo=FALSE}
+
+compute_alpha <- function(data, varName){
+  data %>%
+  filter(question_block == varName) %>%
+  select(workerId, question, response_num_rev) %>%
+  spread(question, response_num_rev) %>%
+  remove_rownames() %>%
+  column_to_rownames("workerId") %>%
+  psych::alpha()
+}
+
+# scale reliability analyses
+
+var_names <- as.character(unique(s1_long$question_block))
+alpha_values <- map(var_names, ~compute_alpha(s1_long,.x)$total[[2]])
+names(alpha_values) <- var_names
+
+# do something to pretty this up
+
+# as_tibble(alpha_values) %>% 
+#   gather(scale, alpha) %>% 
+#   knitr::kable()
+
+```
+
 Scale items + reliability coefficients

### 2021-06-09 code/custom_plotting.R

@@ -1,0 +1,45 @@
+custom_plot.HydeNetwork <- function(x, 
+                             customNodes = NULL,
+                             customEdges = NULL,
+                             ..., 
+                             removeDeterm = FALSE,
+                             useHydeDefaults = TRUE)
+{
+  if (removeDeterm) x <- plot_nondeterm_only(x)
+  
+  node_df <- 
+    DiagrammeR::create_node_df(n = length(x[["nodes"]]),
+                               label = x[["nodes"]])
+  # 
+  # node_df <- data.frame(nodes = x[["nodes"]],
+  #                       stringsAsFactors = FALSE)
+  if (useHydeDefaults) node_df <- HydeNet:::mergeDefaultPlotOpts(x, node_df)
+  
+  if (!is.null(customNodes)) node_df <- HydeNet::mergeCustomNodes(node_df, customNodes)
+  
+  edge_table <- do.call("rbind", 
+                        mapply(FUN = HydeNet:::mapEdges, 
+                               x[["nodes"]], 
+                               x[["parents"]],
+                               MoreArgs = list(node_df = node_df)))
+  
+  edge_df <- DiagrammeR::create_edge_df(from = edge_table[, 2], 
+                                        to = edge_table[, 1])
+  
+  if (!is.null(customEdges)) HydeNet::mergeCustomEdges(edge_df, customEdges)
+  
+  
+  
+  DiagrammeR::create_graph(nodes_df = node_df,
+                           edges_df = edge_df,
+                           attr_theme = NULL)
+  
+}
+
+
+## ----------------------------------------
+
+# code to demo. For some reason set_edge_attrs() isn't working right, so have to do it manually
+# z <- custom_plot.HydeNetwork(h)
+# z$edges_df <- z$edges_df %>% mutate(color = "blue", penwidth=rep(c(1,2,3),10))
+# render_graph(z)

### 2021-06-18 supplement/supplement-main.Rmd
prettied graphs

@@
 
+```{r, include=FALSE}
+# # can bootstrap strength of arcs for winning model approach, focus interpretations on strength of arcs / parameterizations
+
+set.seed(77267)
+
+# train_noise <- train %>%
+#   mutate_all(~.x+rnorm(n(),0,.002))
+if (!file.exists("../local/boot_res.rds")){
+  cl = parallel::makeCluster(detectCores(logical=TRUE))
+
+  clusterCall(cl,
+              function(){
+                source("../code/custom-structure-learning/cog-model-main.R", chdir=TRUE)
+                library(purrr)
+                }
+    )
+
+  ## very slow!
+  boot_res <- boot.strength(
+    train,  #train
+    R = 200,
+    algorithm = "hc",
+    algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e4),
+    cluster = cl
+    )
+
+  stopCluster(cl)
+
+  saveRDS(boot_res,"../local/boot_res.rds")
+} else {
+  boot_res <- readRDS("../local/boot_res.rds")
+}
+
+```
+
+```{r boot_strength_plot, echo=F, message=F, fig.cap="Bootstrapped confidence estimates for Bayesian network edges.
+Edge color indicates frequency with which edges appeared when conducting search across X bootstrap replicates.
+Only edges appearing in at least 20\\% of graphs are shown."}
+
+hyde_str <- df_to_hyde_string(boot_res %>% filter(strength>.2, direction>0) %>% select(from,to))
+h2 <- HydeNetwork(as.formula(hyde_str))
+# plot(h2)
+
+z2 <- custom_plot.HydeNetwork(h2)
+boot_res %>%
+  filter(direction>0, strength>.2) %>% 
+  # filter(parameter!="phi",parameter!="w_leak") %>%
+  # rename(from = parameter) %>%
+  # mutate(from = gsub("w_","",from)) %>%
+  mutate(strength = strength*direction) %>% 
+  select(to, from, strength) %>%
+  merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
+  mutate(from = id) %>%
+  select(-id) %>%
+  merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
+  mutate(to = id) %>%
+  arrange(to,from) -> edge_df_mod
+
+# z$nodes_df
+z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
+z2$nodes_df$fontname <- "Helvetica"
+z2$nodes_df$shape <- "ellipse"
+# z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$id==13, "grey","white")
+z2$nodes_df$fixedsize <- FALSE
+z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
+z2$edges_df$penwidth <- 2
+# z$edges_df$label <- round(edge_df_mod$value,2)
+# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
+z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
+# z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
+
+render_graph(z2)
+```
+
+```{r}
+boot_graph_legend <- (tibble(
+  Probability = seq(min(edge_df_mod$strength), max(edge_df_mod$strength), length=11),
+) %>% 
+  ggplot(aes(y=1, x = Probability, fill = Probability)) +
+  geom_tile() +
+  scale_fill_distiller(palette="RdPu", direction=1)
+) %>% 
+  cowplot::get_legend()
+
+cowplot::ggdraw(boot_graph_legend)
+```
+
 ```{r, include=F}
@@
 c <- find_dag_coefs(main_model, train)
+```
+
+```{r}
+boot_df <- boot_res %>% filter(strength>.2, direction>0)
 ```
@@
 z$edges_df$penwidth <- 1.5
-# z$edges_df$label <- round(edge_df_mod$value,2)
+z$edges_df$label <- round(edge_df_mod$value,2)
 # z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
@@
 cowplot::ggdraw(main_graph_legend)
-```
-
-```{r, include=FALSE}
-# # can bootstrap strength of arcs for winning model approach, focus interpretations on strength of arcs / parameterizations
-
-set.seed(77267)
-
-# train_noise <- train %>%
-#   mutate_all(~.x+rnorm(n(),0,.002))
-if (!file.exists("../local/boot_res.rds")){
-  cl = parallel::makeCluster(detectCores(logical=TRUE))
-
-  clusterCall(cl,
-              function(){
-                source("../code/custom-structure-learning/cog-model-main.R", chdir=TRUE)
-                library(purrr)
-                }
-    )
-
-  ## very slow!
-  boot_res <- boot.strength(
-    train,  #train
-    R = 200,
-    algorithm = "hc",
-    algorithm.args = list(score="custom", fun=cog_model_score_func, blacklist = theory_bl, maxp=5, max.iter=1e4),
-    cluster = cl
-    )
-
-  stopCluster(cl)
-
-  saveRDS(boot_res,"../local/boot_res.rds")
-} else {
-  boot_res <- readRDS("../local/boot_res.rds")
-}
-
-```
-
-```{r boot_strength_plot, echo=F, message=F, fig.cap="Bootstrapped confidence estimates for Bayesian network edges.
-Edge color indicates frequency with which edges appeared when conducting search across X bootstrap replicates.
-Only edges appearing in at least 20\\% of graphs are shown."}
-
-hyde_str <- df_to_hyde_string(boot_res %>% filter(strength>.2, direction>0) %>% select(from,to))
-h2 <- HydeNetwork(as.formula(hyde_str))
-# plot(h2)
-
-z2 <- custom_plot.HydeNetwork(h2)
-boot_res %>%
-  filter(direction>0, strength>.2) %>% 
-  # filter(parameter!="phi",parameter!="w_leak") %>%
-  # rename(from = parameter) %>%
-  # mutate(from = gsub("w_","",from)) %>%
-  select(to, from, strength) %>%
-  merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
-  mutate(from = id) %>%
-  select(-id) %>%
-  merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
-  mutate(to = id) %>%
-  arrange(to,from) -> edge_df_mod
-
-# z$nodes_df
-z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
-z2$nodes_df$fontname <- "Helvetica"
-z2$nodes_df$shape <- "ellipse"
-# z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$id==13, "grey","white")
-z2$nodes_df$fixedsize <- FALSE
-z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
-z2$edges_df$penwidth <- 2
-# z$edges_df$label <- round(edge_df_mod$value,2)
-# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
-z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
-# z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
-
-render_graph(z2)
-```
-
-```{r}
-boot_graph_legend <- (tibble(
-  Probability = seq(min(edge_df_mod$strength), max(edge_df_mod$strength), length=11),
-) %>% 
-  ggplot(aes(y=1, x = Probability, fill = Probability)) +
-  geom_tile() +
-  scale_fill_distiller(palette="RdPu", direction=1)
-) %>% 
-  cowplot::get_legend()
-
-cowplot::ggdraw(boot_graph_legend)
 ```
@@
 
+```{r echo=F, fig.width=8, fig.height=4}
+## combined plot for paper
+library(patchwork)
+
+s2_diff_plot <- s2_scored %>% 
+  spread(phase, mean) %>% 
+  drop_na(scale) %>% 
+  mutate(diff = post-pre) %>% 
+  mutate(
+    scale = recode_nodes2(scale),
+    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
+    ) %>% 
+  group_by(condition, scale) %>%
+  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
+  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
+  geom_pointrange(position=position_dodge(width=.25)) +
+  geom_hline(yintercept=0, linetype="dashed", color="grey") +
+  scale_color_manual(values=c("#0067b1","#c50024")) +
+  theme_bw(base_size=11) +
+  theme(
+    axis.text.x = element_text(angle=45, hjust=1),
+    panel.grid = element_blank(),
+    legend.position = c(.35,.9),
+    legend.direction = "horizontal",
+    aspect.ratio=.5
+    ) +
+  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention")
+
+obs_pred <- make_pred_df(s2_mdf, base_model, "diseaseSevere")
+
+cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
+
+s2_obs_pred_plot <- obs_pred %>% # a bit of a hack
+  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
+  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+  geom_errorbar( width=0, color="grey") +
+  geom_point(size=2.5) +
+  annotate(geom="text", x=.03, y=-.04, label= paste("r =", cor_val)) +
+  coord_cartesian(xlim=c(-.06,.06), ylim=c(-.06,.06)) +
+  theme_bw(base_size=11) +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+  theme(aspect.ratio = 1) +
+  labs(title = "B", y = "Observed change", x="Predicted change")
+
+s2_diff_plot + s2_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
+```
+
 ## Studies 3a and 3b
@@
 )
+```
+
+```{r fig.width=8, fig.height=4}
+s3_diff_plot <- s3_scored %>% 
+  # spread(phase, mean) %>% 
+  drop_na(scale) %>% 
+  mutate(diff = post-pre) %>% 
+  mutate(
+    scale = recode_nodes2(scale),
+    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
+    ) %>% 
+  group_by(condition, scale) %>%
+  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
+  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
+  geom_pointrange(position=position_dodge(width=.25)) +
+  geom_hline(yintercept=0, linetype="dashed", color="grey") +
+  scale_color_manual(values=c("#0067b1","#c50024")) +
+  theme_bw(base_size=11) +
+  theme(
+    axis.text.x = element_text(angle=45, hjust=1),
+    panel.grid = element_blank(),
+    legend.position = c(.6,.15),
+    legend.direction = "horizontal",
+    aspect.ratio=.5
+    ) +
+  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention")
+
+obs_pred <- make_pred_df(s3_mdf, base_model, "vaccTox")
+
+cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
+
+s3_obs_pred_plot <- obs_pred %>% 
+  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
+  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+  geom_point(size=2.5) +
+  geom_errorbar(alpha=.5, width=0) +
+  # coord_fixed(ratio=1) +
+  coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
+  annotate(geom="text", x=.05, y=-.1, label= paste("r =", cor_val)) +
+  theme_bw(base_size=11) +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+  theme(aspect.ratio = 1) +
+  labs(title = "B", y = "Observed change", x="Predicted change")
+
+s3_diff_plot + s3_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
 ```
@@
 
+```{r fig.width=8, fig.height=4}
+s4_diff_plot <- combined %>% 
+  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
+  mutate(diff = posttest-pretest) %>%
+  mutate(
+    vacc_news = as.factor(vacc_news),
+    scale = recode_nodes2(scale)
+    ) %>%
+  group_by(vacc_news,scale) %>%
+  summarize(
+    mean = mean(diff),
+    se = sd(diff)/sqrt(n()),
+    ul = mean + se,
+    ll = mean - se,
+    ul95 = mean + 1.96*se,
+    ll95 = mean - 1.96*se
+  ) %>%
+  ungroup() %>%
+  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
+  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
+  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
+  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
+  geom_errorbar(position=position_dodge(width=.25), width=0, alpha=.8) +
+  # geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
+  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
+  scale_color_manual(values=c("#0067b1","#c50024")) +
+  theme_bw(base_size=11) +
+  theme(
+    axis.text.x = element_text(angle=45, hjust=1),
+    panel.grid = element_blank(),
+    legend.position = c(.35,.85),
+    legend.direction = "horizontal",
+    aspect.ratio=.5
+    ) +
+  labs(title="A", y = "Mean difference", x = "Belief scale", color="News Exposure")
+
+obs_pred <- make_pred_df(s4_mdf, base_model, "vaccIntent")
+
+cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
+
+s4_obs_pred_plot <- obs_pred %>% # a bit of a hack
+  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
+  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+  geom_point(size=2.5) +
+  geom_errorbar(alpha=.5, width=0) +
+  annotate(geom="text", x=.04, y=-.04, label= paste("r =", cor_val)) +
+  coord_cartesian(xlim=c(-.07,.06), ylim=c(-.07,.06)) +
+  theme_bw(base_size=11) +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+  theme(aspect.ratio = 1) +
+  labs(title = "B", y = "Observed change", x="Predicted change")
+
+s4_diff_plot + s4_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
+```
+
 ## Participant demographic summary
@@
                    ),
+    income = str_replace_all(income, "\\$",""),
     income = ordered(income,
                      levels = c(
-                          "Less than $20,000",
-                          "$20,000 - $30,000",
-                          "$30,001 - $50,000",
-                          "$50,001 - $70,000",
-                          "$70,001 - $100,000",
-                          "More than $100,000",
+                          "Less than 20,000",
+                          "20,000 - 30,000",
+                          "30,001 - 50,000",
+                          "50,001 - 70,000",
+                          "70,001 - 100,000",
+                          "More than 100,000",
                           "Prefer not to say"
@@
     age = ifelse(age < 18,NA,age),
-    income = str_replace_all(income, "\\$",""),
+    # income = str_replace_all(income, "\\$",""),
     study = paste("Study", study)
@@
 # trying wrapping with factor() to get it to print integer counts
-demographics_tbl <- table1::table1(~ factor(sex) + age + factor(race) + factor(religion) + factor(educ) + factor(income) + factor(parent)  | study, data=df_demo)
-
-table1::t1kable(demographics_tbl) %>% 
+# demographics_tbl <- table1::table1(~ factor(sex) + age + factor(race) + factor(religion) + factor(educ) + factor(income) + factor(parent)  | study, data=df_demo)
+
+demographics_tbl <- table1::table1(~ sex + age + race + religion + educ+ income + parent  | study, data=df_demo)
+
+table1::t1kable(demographics_tbl, booktabs = T) %>% 
   kable_classic(latex_options="scale_down")

### 2021-06-21 supplement/supplement-main.Rmd
supp updates

@@
 
+```{r}
+## explore cpdag
+
+main_cpdag <- cpdag(main_model)
+
+# do plotting -- will likely see lots of ambiguity??
+plot(main_cpdag)
+
+# CPDAG edge directions ruled out by blacklist (10)
+ruled_out <- inner_join(as.data.frame(undirected.arcs(main_cpdag)), as.data.frame(theory_bl), by=c("from","to"))
+
+# leaves 5 arcs that are unconstrained by both data and theory
+anti_join(as.data.frame(undirected.arcs(main_cpdag)), (ruled_out %>% bind_rows(ruled_out %>% rename(to="from", from="to")) ), by = c("from", "to"))
+
+# most substantive are vaccTox <--> vaccDanger, vaccEff
+```
+
 ```{r, include=FALSE}
@@
 
-```{r boot_strength_plot, echo=F, message=F, fig.cap="Bootstrapped confidence estimates for Bayesian network edges.
-Edge color indicates frequency with which edges appeared when conducting search across X bootstrap replicates.
-Only edges appearing in at least 20\\% of graphs are shown."}
-
-hyde_str <- df_to_hyde_string(boot_res %>% filter(strength>.2, direction>0) %>% select(from,to))
-h2 <- HydeNetwork(as.formula(hyde_str))
-# plot(h2)
-
-z2 <- custom_plot.HydeNetwork(h2)
-boot_res %>%
-  filter(direction>0, strength>.2) %>% 
-  # filter(parameter!="phi",parameter!="w_leak") %>%
-  # rename(from = parameter) %>%
-  # mutate(from = gsub("w_","",from)) %>%
-  mutate(strength = strength*direction) %>% 
-  select(to, from, strength) %>%
-  merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
-  mutate(from = id) %>%
-  select(-id) %>%
-  merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
-  mutate(to = id) %>%
-  arrange(to,from) -> edge_df_mod
-
-# z$nodes_df
-z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
-z2$nodes_df$fontname <- "Helvetica"
-z2$nodes_df$shape <- "ellipse"
-# z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$id==13, "grey","white")
-z2$nodes_df$fixedsize <- FALSE
-z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
-z2$edges_df$penwidth <- 2
-# z$edges_df$label <- round(edge_df_mod$value,2)
-# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
-z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
-# z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
-
-render_graph(z2)
-```
-
-```{r}
-boot_graph_legend <- (tibble(
-  Probability = seq(min(edge_df_mod$strength), max(edge_df_mod$strength), length=11),
-) %>% 
-  ggplot(aes(y=1, x = Probability, fill = Probability)) +
-  geom_tile() +
-  scale_fill_distiller(palette="RdPu", direction=1)
-) %>% 
-  cowplot::get_legend()
-
-cowplot::ggdraw(boot_graph_legend)
-```
-
 ```{r, include=F}
-
-h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))
-
-c <- find_dag_coefs(main_model, train)
-```
-
-```{r}
-boot_df <- boot_res %>% filter(strength>.2, direction>0)
-```
-
-```{r main_model_plot, echo=F, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
-Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links."}
 
@@
 
+```
+
+```{r boot_strength_plot, echo=F, message=F, fig.cap="Bootstrapped confidence estimates for Bayesian network edges.
+Edge color indicates frequency with which edges appeared when conducting search across X bootstrap replicates.
+Only edges appearing in at least 20\\% of graphs are shown."}
+
+hyde_str <- df_to_hyde_string(boot_res %>% filter(strength>.2, direction>0) %>% select(from,to))
+h2 <- HydeNetwork(as.formula(hyde_str))
+# plot(h2)
+
+z2 <- custom_plot.HydeNetwork(h2)
+boot_res %>%
+  filter(direction>0, strength>.2) %>% 
+  # filter(parameter!="phi",parameter!="w_leak") %>%
+  # rename(from = parameter) %>%
+  # mutate(from = gsub("w_","",from)) %>%
+  mutate(strength = strength*direction) %>% 
+  select(to, from, strength) %>%
+  merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
+  mutate(from = id) %>%
+  select(-id) %>%
+  merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
+  mutate(to = id) %>%
+  arrange(to,from) -> edge_df_mod
+
+# z$nodes_df
+z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
+z2$nodes_df$fontname <- "Helvetica"
+z2$nodes_df$shape <- "ellipse"
+# z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$id==13, "grey","white")
+z2$nodes_df$fixedsize <- FALSE
+z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
+z2$edges_df$penwidth <- 2
+# z$edges_df$label <- round(edge_df_mod$value,2)
+# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
+z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
+# z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
+
+render_graph(z2)
+```
+
+```{r}
+boot_graph_legend <- (tibble(
+  Probability = seq(min(edge_df_mod$strength), max(edge_df_mod$strength), length=11),
+) %>% 
+  ggplot(aes(y=1, x = Probability, fill = Probability)) +
+  geom_tile() +
+  scale_fill_distiller(palette="RdPu", direction=1)
+) %>% 
+  cowplot::get_legend()
+
+cowplot::ggdraw(boot_graph_legend)
+```
+
+```{r, include=F}
+
+h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))
+
+c <- find_dag_coefs(main_model, train)
+```
+
+```{r}
+boot_df <- boot_res %>% filter(strength>.2, direction>0)
+```
+
+```{r main_model_plot, echo=F, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
+Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links."}
+
 z <- custom_plot.HydeNetwork(h)
@@
   geom_abline(slope=1, intercept=0, linetype="dashed", alpha=.33) +
-  geom_point(shape=1, size=.5, color="darkturquoise") + 
+  geom_point(shape=1, size=.5, color="#0067B1") + 
   geom_text(data=corrDF, aes(label=paste("r =", round(cor,2))),
@@
 # create plot of differences for all 14 scales
-
-s2_scored %>% 
-  spread(phase, mean) %>% 
-  drop_na(scale) %>% 
-  mutate(diff = post-pre) %>% 
-  mutate(
-    scale = recode_nodes2(scale),
-    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
-    ) %>% 
-  group_by(condition, scale) %>%
-  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
-  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
-  geom_pointrange(position=position_dodge(width=.25)) +
-  geom_hline(yintercept=0, linetype="dashed", color="grey") +
-  theme_bw() +
-  theme(
-    axis.text.x = element_text(angle=45, hjust=1),
-    panel.grid = element_blank()
-    ) +
-  labs(title="Study 2", y = "Mean difference", x = "Belief scale", color="Intervention")
+# 
+# s2_scored %>% 
+#   spread(phase, mean) %>% 
+#   drop_na(scale) %>% 
+#   mutate(diff = post-pre) %>% 
+#   mutate(
+#     scale = recode_nodes2(scale),
+#     condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
+#     ) %>% 
+#   group_by(condition, scale) %>%
+#   summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
+#   ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
+#   geom_pointrange(position=position_dodge(width=.25)) +
+#   geom_hline(yintercept=0, linetype="dashed", color="grey") +
+#   theme_bw() +
+#   theme(
+#     axis.text.x = element_text(angle=45, hjust=1),
+#     panel.grid = element_blank()
+#     ) +
+#   labs(title="Study 2", y = "Mean difference", x = "Belief scale", color="Intervention")
 ```
@@
 
-make_table <- function(fit, caption=NULL){
+make_table_df <- function(fit){
   fit_sum <- summary(fit)
@@
 
-  kableExtra::kbl(tbl_sum, digits = 2, booktabs = T, caption=caption) %>% 
+  return(tbl_sum)
+}
+
+make_table <- function(table_df, caption=NULL){
+
+  kableExtra::kbl(table_df, digits = 2, booktabs = T, caption=caption) %>% 
     kableExtra::kable_classic(full_width=F)
@@
 
-make_table(fit_s2_vaccIntent, "Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 2.")
+fit_s2_vaccIntent %>% 
+  make_table_df() %>% 
+  mutate(
+    Term = case_when(
+      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
+      #                                            gsub("(diseaseRisk|post)", "", Term),
+      #                                            "}$"),
+      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
+      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
+      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
+      TRUE ~ gsub("(diseaseRisk|post)","", Term)
+    )
+  ) %>% 
+  make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 2.")
 
@@
 # odd, I remember the results being slightly better than this, job talk says r=.87
-obs_pred <- make_pred_df(s2_mdf, base_model, "diseaseSevere")
-
-cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
-
-(obs_pred_plot <- obs_pred %>% # a bit of a hack
-  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
-  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
-  geom_point(size=2.5) +
-  geom_errorbar(alpha=.5, width=0) +
-  annotate(geom="text", x=.03, y=-.04, label= paste("r =", cor_val)) +
-  coord_cartesian(xlim=c(-.06,.06), ylim=c(-.06,.06)) +
-  theme_bw(base_size=14) +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-  theme(aspect.ratio = 1)) +
-  labs(title="Belief changes", subtitle="Experiment 2")
+# obs_pred <- make_pred_df(s2_mdf, base_model, "diseaseSevere")
+# 
+# cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
+# 
+# (obs_pred_plot <- obs_pred %>% # a bit of a hack
+#   ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
+#   geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+#   geom_point(size=2.5) +
+#   geom_errorbar(alpha=.5, width=0) +
+#   annotate(geom="text", x=.03, y=-.04, label= paste("r =", cor_val)) +
+#   coord_cartesian(xlim=c(-.06,.06), ylim=c(-.06,.06)) +
+#   theme_bw(base_size=14) +
+#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+#   theme(aspect.ratio = 1)) +
+#   labs(title="Belief changes", subtitle="Experiment 2")
 
@@
 
-```{r echo=F, fig.width=8, fig.height=4}
+```{r echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiment 2.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
+Right, mean observed and model predicted change scores for the disease risk intervention condition.
+In both plots, error bars represent 95\\% confidence intervals."}
 ## combined plot for paper
@@
   summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
-  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
+  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition, shape=condition)) +
   geom_pointrange(position=position_dodge(width=.25)) +
@@
     ) +
-  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention")
+  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention", shape="Intervention")
 
@@
 
-s2_diff_plot + s2_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
+s2_plt <- s2_diff_plot + s2_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
+
+s2_plt
 ```
@@
 
-```{r echo=F, message=F}
+```{r echo=F, message=F, fig.align='center', fig.height=3, fig.width=3}
 
@@
 
-interv_sim %>%
-  ggplot(aes(x=abs(correlation), y = model_pred)) +
-  geom_point()
+# interv_sim %>%
+#   ggplot(aes(x=abs(correlation), y = model_pred)) +
+#   geom_point()
 
@@
   ggplot(aes(x=reorder(scale, model_pred), y = model_pred)) + 
-  geom_bar(stat="identity") + 
+  geom_bar(stat="identity", fill = "#0067B1") + 
   coord_flip() +
-  labs(x="Targeted belief", y = "Predicted change in intentions") +
-  theme_bw(base_size=22) +
+  labs(x="Targeted belief", y = "Predicted change\nin intentions") +
+  theme_bw(base_size=10) +
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-  theme(aspect.ratio = 1.5))
+  theme(aspect.ratio = 1))
 
@@
 
-s3_scored %>% 
-  # spread(phase, mean) %>% 
-  drop_na(scale) %>% 
-  mutate(diff = post-pre) %>% 
-  mutate(
-    scale = recode_nodes2(scale),
-    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
-    ) %>% 
-  group_by(condition, scale) %>%
-  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
-  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
-  geom_pointrange(position=position_dodge(width=.25)) +
-  geom_hline(yintercept=0, linetype="dashed", color="grey") +
-  theme_bw() +
-  theme(
-    axis.text.x = element_text(angle=45, hjust=1),
-    panel.grid = element_blank()
-    ) +
-  labs(title="Study 3a and 3b", y = "Mean difference", x = "Belief scale", color="Intervention")
+# s3_scored %>% 
+#   # spread(phase, mean) %>% 
+#   drop_na(scale) %>% 
+#   mutate(diff = post-pre) %>% 
+#   mutate(
+#     scale = recode_nodes2(scale),
+#     condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
+#     ) %>% 
+#   group_by(condition, scale) %>%
+#   summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
+#   ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
+#   geom_pointrange(position=position_dodge(width=.25)) +
+#   geom_hline(yintercept=0, linetype="dashed", color="grey") +
+#   theme_bw() +
+#   theme(
+#     axis.text.x = element_text(angle=45, hjust=1),
+#     panel.grid = element_blank()
+#     ) +
+#   labs(title="Study 3a and 3b", y = "Mean difference", x = "Belief scale", color="Intervention")
 
@@
 # compare conditions on vaccIntent w/ regression model
+
 # -- TODO: recode phase/condition 5/25/21, 11:07 AM
@@
 
-make_table(fit_s3_vaccIntent, "Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3.")
+fit_s3_vaccIntent %>% 
+  make_table_df() %>% 
+  mutate(
+    Term = case_when(
+      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
+      #                                            gsub("(diseaseRisk|post)", "", Term),
+      #                                            "}$"),
+      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
+      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
+      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
+      TRUE ~ gsub("(intervention|post)","", Term)
+    )
+  ) %>% 
+make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3.")
+```
+
+We also analyzed each experiment individually.
+
+```{r, echo=FALSE, message=F, warning=F}
+
+fit_s3a_vaccIntent <- brm(
+  response ~ phase*condition + (1|item) + (1|workerId),
+  family = cumulative("logit"),
+  data = s3_reg %>% filter(study=="A"),
+  chains = 6,
+  cores = 6,
+  control = list(adapt_delta=.95),
+  seed = 69568,
+  file = "../local/fit_s3a_vaccIntent.rds"
+)
+
+fit_s3b_vaccIntent <- brm(
+  response ~ phase*condition + (1|item) + (1|workerId),
+  family = cumulative("logit"),
+  data = s3_reg %>% filter(study=="B"),
+  chains = 6,
+  cores = 6,
+  control = list(adapt_delta=.95),
+  seed = 69568,
+  file = "../local/fit_s3b_vaccIntent.rds"
+)
+
+fit_s3a_vaccIntent %>% 
+  make_table_df() %>% 
+  mutate(
+    Term = case_when(
+      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
+      #                                            gsub("(diseaseRisk|post)", "", Term),
+      #                                            "}$"),
+      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
+      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
+      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
+      TRUE ~ gsub("(intervention|post)","", Term)
+    )
+  ) %>% 
+make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3a.")
+
+fit_s3b_vaccIntent %>% 
+  make_table_df() %>% 
+  mutate(
+    Term = case_when(
+      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
+      #                                            gsub("(diseaseRisk|post)", "", Term),
+      #                                            "}$"),
+      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
+      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
+      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
+      TRUE ~ gsub("(intervention|post)","", Term)
+    )
+  ) %>% 
+make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3b.")
 ```
@@
 
-```{r, echo=F, fig.width=4, fig.height=4, fig.align="center", fig.cap="Mean observed and predicted change scores for Experiment 3. Error bars represent 95\\% confidence intervals."}
+```{r, echo=F, fig.width=4, fig.height=4, fig.align="center", fig.cap="Plots of belief changes following the intervention in Experiment 3.
+Left, mean difference scores from pretest to posttest for the 14 belief scales measured in Experiment 3.
+Mean observed and predicted change scores for Experiment 3.
+Error bars in both plots represent 95\\% confidence intervals.
+"}
 
@@
 # fit evidence node
-obs_pred <- make_pred_df(s3_mdf, base_model, "vaccTox")
-
-cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
-
-(
-  obs_pred_plot <- obs_pred %>% 
-  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
-  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
-  geom_point(size=2.5) +
-  geom_errorbar(alpha=.5, width=0) +
-  # coord_fixed(ratio=1) +
-  coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
-  annotate(geom="text", x=.05, y=-.1, label= paste("r =", cor_val)) +
-  theme_bw(base_size=14) +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-  theme(aspect.ratio = 1) +
-  labs(title="Belief changes",subtitle="Experiment 3a & 3b")
-)
-```
-
-```{r fig.width=8, fig.height=4}
+# obs_pred <- make_pred_df(s3_mdf, base_model, "vaccTox")
+# 
+# cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
+# 
+# (
+#   obs_pred_plot <- obs_pred %>% 
+#   ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
+#   geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+#   geom_point(size=2.5) +
+#   geom_errorbar(alpha=.5, width=0) +
+#   # coord_fixed(ratio=1) +
+#   coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
+#   annotate(geom="text", x=.05, y=-.1, label= paste("r =", cor_val)) +
+#   theme_bw(base_size=14) +
+#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+#   theme(aspect.ratio = 1) +
+#   labs(title="Belief changes",subtitle="Experiment 3a & 3b")
+# )
+```
+
+```{r fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
+Right, mean observed and model predicted change scores for the toxins intervention condition.
+In both plots, error bars represent 95\\% confidence intervals."}
 s3_diff_plot <- s3_scored %>% 
@@
 
-s3_diff_plot + s3_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
+s3_plt <- s3_diff_plot + s3_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
+
+s3_plt
 ```
@@
   n_complete =s4_wide %>% 
-    filter(check_5==5, check_3==3, workerId %in% s1_all$workerId) %>% distinct(workerId) %>% nrow()
+    filter(check_5==5, check_3==3, workerId %in% s1_all$workerId) %>% distinct(workerId) %>% nrow(),
+  n_news = s4_wide %>%
+    filter(check_5==5, check_3==3, workerId %in% s1_all$workerId) %>% 
+    filter(vacc_news==1) %>% 
+    distinct(workerId) %>% 
+    nrow()
 )
@@
 
-combined %>% 
-  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
-  mutate(diff = posttest-pretest) %>%
-  mutate(
-    vacc_news = as.factor(vacc_news),
-    scale = recode_nodes2(scale)
-    ) %>%
-  group_by(vacc_news,scale) %>%
-  summarize(
-    mean = mean(diff),
-    se = sd(diff)/sqrt(n()),
-    ul = mean + se,
-    ll = mean - se,
-    ul95 = mean + 1.96*se,
-    ll95 = mean - 1.96*se
-  ) %>%
-  ungroup() %>%
-  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
-  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
-  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
-  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
-  geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
-  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
-  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
-  # facet_wrap(~scale, scales="free") +
-  theme_bw(base_size = 12) +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1), 
-    legend.position = "right",
-    panel.grid = element_blank()) +
-  labs(title="Study 4", y = "Change scores", x = "Belief scale", color ="News\nexposure")
+# combined %>% 
+#   filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
+#   mutate(diff = posttest-pretest) %>%
+#   mutate(
+#     vacc_news = as.factor(vacc_news),
+#     scale = recode_nodes2(scale)
+#     ) %>%
+#   group_by(vacc_news,scale) %>%
+#   summarize(
+#     mean = mean(diff),
+#     se = sd(diff)/sqrt(n()),
+#     ul = mean + se,
+#     ll = mean - se,
+#     ul95 = mean + 1.96*se,
+#     ll95 = mean - 1.96*se
+#   ) %>%
+#   ungroup() %>%
+#   mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
+#   # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
+#   ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
+#   geom_point(position=position_dodge(width=.25), size=2, shape=16) +
+#   geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
+#   geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
+#   geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
+#   # facet_wrap(~scale, scales="free") +
+#   theme_bw(base_size = 12) +
+#   theme(
+#     axis.text.x = element_text(angle = 45, hjust = 1), 
+#     legend.position = "right",
+#     panel.grid = element_blank()) +
+#   labs(title="Study 4", y = "Change scores", x = "Belief scale", color ="News\nexposure")
 ```
@@
 
-make_table(fit_s4_vaccIntent, "Bayesian regression model coefficients for model of Vaccine Intentions in Study 4.")
+fit_s4_vaccIntent %>% 
+make_table_df() %>% 
+  mutate(
+    Term = case_when(
+      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
+      #                                            gsub("(diseaseRisk|post)", "", Term),
+      #                                            "}$"),
+      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
+      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
+      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
+      TRUE ~ gsub("(intervention|posttest)","", Term)
+    ),
+    Term = gsub("vacc_news", "awareness", Term)
+  ) %>% 
+make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Study 4.")
 ```
@@
 
-obs_pred <- make_pred_df(s4_mdf, base_model, "vaccIntent")
-
-cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
-
-(obs_pred_plot <- obs_pred %>% # a bit of a hack
-  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
-  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
-  geom_point(size=2.5) +
-  geom_errorbar(alpha=.5, width=0) +
-  annotate(geom="text", x=.04, y=-.04, label= paste("r =", cor_val)) +
-  coord_cartesian(xlim=c(-.07,.06), ylim=c(-.07,.06)) +
-  theme_bw(base_size=14) +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-  theme(aspect.ratio = 1)) +
-  labs(title="Belief changes",subtitle="Study 4 - vaccIntent")
-
-```
-
-```{r fig.width=8, fig.height=4}
+# obs_pred <- make_pred_df(s4_mdf, base_model, "vaccIntent")
+# 
+# cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
+# 
+# (obs_pred_plot <- obs_pred %>% # a bit of a hack
+#   ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
+#   geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+#   geom_point(size=2.5) +
+#   geom_errorbar(alpha=.5, width=0) +
+#   annotate(geom="text", x=.04, y=-.04, label= paste("r =", cor_val)) +
+#   coord_cartesian(xlim=c(-.07,.06), ylim=c(-.07,.06)) +
+#   theme_bw(base_size=14) +
+#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+#   theme(aspect.ratio = 1)) +
+#   labs(title="Belief changes",subtitle="Study 4 - vaccIntent")
+
+```
+
+```{r echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4.
+Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York.
+Right, mean observed and model predicted change scores for those who were exposed to news of the outbreak.
+In both plots, error bars represent 95\\% confidence intervals."}
 s4_diff_plot <- combined %>% 
@@
   # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
-  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
-  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
-  geom_errorbar(position=position_dodge(width=.25), width=0, alpha=.8) +
+  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll95, ymax=ul95, color=vacc_news, shape=vacc_news)) +
+  geom_point(position=position_dodge(width=.25), size=2) +
+  geom_errorbar(position=position_dodge(width=.25), width=0) +
   # geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
   geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
-  scale_color_manual(values=c("#0067b1","#c50024")) +
+  scale_color_manual(values=c("#0067b1","grey")) +
   theme_bw(base_size=11) +
@@
     ) +
-  labs(title="A", y = "Mean difference", x = "Belief scale", color="News Exposure")
+  labs(title="A", y = "Mean difference", x = "Belief scale", color="News Exposure", shape="News Exposure")
 
@@
 
-s4_diff_plot + s4_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
+s4_plt <- s4_diff_plot + s4_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
+
+s4_plt
 ```
@@
 
-The table below presents demographic information for participants across all four studies.
+The table below presents demographic information for participants across all five studies.
 
@@
 
+```{r exports_for_paper, include=F}
+
+## save plots
+# export network plot as pdf/svg
+saveRDS(plt.valid, "../local/valid_plt.rds")
+saveRDS(s2_plt, "../local/s2_plt.rds")
+saveRDS(s3_plt, "../local/s3_plt.rds")
+saveRDS(s4_plt, "../local/s4_plt.rds")
+saveRDS(pred_change_plot, "../local/pred_change_plt.rds")
+
+## save numerical results
+results <- list(
+  s1 = list(demo = s1_meta),
+  s2 = list(demo = s2_meta, reg = fit_s2_vaccIntent),
+  s3 = list(demo = s3_meta, reg = fit_s3_vaccIntent),
+  s4 = list(demo = s4_meta, reg = fit_s4_vaccIntent)
+)
+
+saveRDS(results, "../local/paper-results.rds")
+```
+
 \newpage

### 2021-06-21 code/custom-structure-learning/cog-model-scoring.R

@@ -413,7 +413,7 @@ score_family <- function(node, predictors, data) { # comment to switch back to o
         par = pars,
         fn = score,
         method = "L-BFGS-B", # BFGS need to add error catching!
-        upper = c(Inf, 1, rep(1,length(predictors))),
+        upper = c(Inf, 1, rep(1,length(predictors))), # maybe constrain to .99?
         lower = c(0, 0, rep(0,length(predictors))),
         control = list(fnscale = -1),
         data = data

### 2021-06-21 supplement/supplement-main.Rmd
refactored

@@
 main_model <- hc(train, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1e3, restart=5)
-
 ```
@@
 ## NOTE: I just can't figure out how to nicely display the graph and legend in code
-## it's must easier just to export them both and then combine with a graphics app
+## it's easier just to export them both and then combine with a graphics app
 

### 2021-06-21 code/custom-structure-learning/cog-model-bidag-functions.R

@@ -1,333 +1,0 @@
-
-## ----------------------------------------
-## Generating BiDAG scoretable 
-## -------------------------------------------
-## Code below is modified from BiDAG package v1.2 under GPL 2/3 license 
-## 8/21/18, 1:11 PM
-library(parallel)
-
-c_definestartspace <- function(alpha, param, cpdag = FALSE, n, algo = "pc") {
-  # condense, just error out for other score types 
-  if (is.null(alpha)) {
-    if (n < 50) {
-      alpha <- 0.4
-    }
-    else {
-      alpha <- max(20/n, 0.01)
-    }
-  }
-  if (param$type == "bde") {
-    if (cpdag) {
-      pc.skel <- pc(suffStat = list(d1 = param$d1, d0 = param$d0, 
-                                    data = param$data), indepTest = weightedbinCItest, 
-                    alpha = alpha, labels = colnames(param$data), 
-                    verbose = FALSE)
-    }
-    else {
-      pc.skel <- pcalg::skeleton(suffStat = list(d1 = param$d1, 
-                                                 d0 = param$d0, data = param$data), indepTest = weightedbinCItest, 
-                                 alpha = alpha, labels = colnames(param$data), 
-                                 verbose = FALSE)
-    }
-  }
-  else if (param$type != "bde") {
-    if (is.null(param$weightvector)) {
-      cormat <- cor(param$data)
-      N <- nrow(param$data)
-    }
-    else {
-      N <- sum(param$weightvector)
-      cormat <- cov.wt(param$data, wt = param$weightvector, 
-                       cor = TRUE)$cor
-    }
-    if (cpdag) {
-      pc.skel <- pcalg::pc(suffStat = list(C = cormat, 
-                                           n = N), indepTest = pcalg::gaussCItest, alpha = alpha, 
-                           labels = colnames(param$data), skel.method = "stable", 
-                           verbose = FALSE)
-    }
-    else {
-      pc.skel <- pcalg::skeleton(suffStat = list(C = cormat, 
-                                                 n = N), indepTest = pcalg::gaussCItest, alpha = alpha, 
[…]

### 2021-06-21 code/custom-structure-learning/cog-model-iterativeMCMC.R

@@ -1,383 +1,0 @@
-# from BiDAG R package
-# 8/29/18, 2:21 PM
-# used under gpl 2/3 license
-
-
-#iterative MCMC search
-c_iterativeMCMCplus1<-function(n,param,iterations,stepsave,plus1it=NULL,MAP=TRUE, posterior=0.5,
-                             startorder=c(1:n),moveprobs,softlimit=9,hardlimit=12,plus1=FALSE,chainout=FALSE,
-                             scoreout=FALSE,startspace=NULL,blacklist=NULL,gamma=1,verbose=FALSE,alpha=NULL,
-                             cpdag=FALSE,mergecp="skeleton",addspace=NULL,scoretable=NULL) {
-  updatenodeslist<-list()
-  MCMCchains<-list()
-  updatenodes<-c(1:n)
-  maxorder<-startorder
-  
-  if (is.null(blacklist)) {
-    blacklist<-matrix(rep(0,n*n),ncol=n)
-  }
-  diag(blacklist)<-1
-  blacklistparents<-list()
-  for  (i in 1:n) {
-    blacklistparents[[i]]<-which(blacklist[,i]==1)
-  }
-  
-  if (is.null(startspace)) startspace<-BiDAG:::definestartspace(alpha,param,cpdag,n,algo="pc")
-  
-  startskeleton<-1*(startspace&!blacklist)
-  
-  if(!is.null(addspace)) {startskel<-1*((addspace|startskeleton)&!blacklist)
-  } else { startskel<-startskeleton }
-  
-  ptab<-BiDAG:::listpossibleparents.PC.aliases(startskel,isgraphNEL=FALSE,n,updatenodes)
-  
-  if (verbose) {
-    print("skeleton ready")
-    flush.console()
-  }
-  if (plus1==FALSE){
-    starttime<-Sys.time()
-    parenttable<-ptab$parenttable # basic parenttable without plus1 lists
-    aliases<-ptab$aliases #aliases for each node since all nodes in parent tables are named as 1,2,3,4. not real parent names
-    numberofparentsvec<-ptab$numberofparentsvec
-    numparents<-ptab$numparents
-    rowmaps<-BiDAG:::parentsmapping(parenttable,numberofparentsvec,n,updatenodes)
-    if(is.null(scoretable)) {
-      scoretable<-BiDAG:::scorepossibleparents.PLUS1(parenttable,plus1lists,n,param,updatenodes,rowmaps,numparents,numberofparentsvec)
-      
[…]

### 2021-06-21 code/custom-structure-learning/cog-model-main.R

@@ -5,7 +5,7 @@
 
 source("cog-model-scoring.R")
 source("cog-model-jags-tools.R")
-source("cog-model-bidag-functions.R")
+# source("cog-model-bidag-functions.R")
 source("cog-model-discrete-funcs.R")
 
 rescale_beta <- function(x, lower, upper) {

### 2021-06-21 code/custom-structure-learning/fit-cog-models-bnlearn.R

@@ -8,6 +8,7 @@ source("../load-data-s1.R", chdir=TRUE)
 library(tidyverse)
 library(bnlearn)
 library(HydeNet)
+library(parallel)
 
 source("cog-model-main.R")
 source("../graph-model-tools.R")

### 2021-06-21 scripts/bdToBn.R

@@ -1,68 +1,0 @@
-# author: Kara Weisman
-# created: 11/10/17, 2:28 PM
-# last updated: 11/10/17, 2:28 PM
-
-# script for translating BDgraph posterior probabilities to bnlearn
-
-library(tidyverse)
-library(bnlearn)
-library(BDgraph)
-library(tidygraph)
-
-# make model with BDgraph -----
-fit.bd.ggm <- bdgraph(d_bn, method = "ggm")
-plot(fit.bd.ggm)
-
-# approach #1: from last graph -----
-
-## get links
-links.bd.ggm <- fit.bd.ggm$last_graph
-
-# ## format as arcs for bnlearn
-# arcs.whitelist <- links.bd.ggm %>%
-#   data.frame() %>%
-#   rownames_to_column("from") %>%
-#   gather(to, yes_no, -from) %>%
-#   filter(yes_no == 1) %>%
-#   data.frame() %>%
-#   dplyr::select(from, to)
-
-## make the blacklist for bnlearn
-arcs.blacklist <- links.bd.ggm %>%
-  data.frame() %>%
-  rownames_to_column("from") %>%
-  gather(to, yes_no, -from) %>%
-  filter(yes_no == 0) %>%
-  data.frame() %>%
-  dplyr::select(from, to)
-
-## make model with bnlearn
-fit.mmhc.blacklist <- mmhc(d_bn, blacklist = arcs.blacklist)
-plot(fit.mmhc.blacklist)
-
-# approach #2: from posterior probabilities -----
-
-## format as arcs for bnlearn
-arcs.whitelist995 <- fit.bd.ggm$p_links %>%
-  data.frame() %>%
-  rownames_to_column("from") %>%
-  gather(to, posterior, -from) %>%
-  filter(posterior >= 0.995) %>%
-  data.frame() %>%
-  dplyr::select(from, to)
-
-## make the blacklist for bnlearn
-arcs.blacklist995 <- fit.bd.ggm$p_links %>%
-  data.frame() %>%
-  rownames_to_column("from") %>%
-  gather(to, posterior, -from) %>%
-  filter(posterior < 0.995) %>%
-  data.frame() %>%
-  dplyr::select(from, to)
-
-## make model with bnlearn
-fit.mmhc.blacklist995 <- mmhc(d_bn, blacklist = arcs.blacklist995)
-plot(fit.mmhc.blacklist995)
-
-# convert to tidy -----
-tidy_graph <- as_tbl_graph(fit.mmhc.blacklist995$arcs)

### 2021-06-21 scripts/bdgraphToBnlearn.R

@@ -1,49 +1,0 @@
-# Author: Derek (but just rearranging kara's code into functions)
-# Last Updated: 11/21/17, 4:26 PM
-
-# NOTE: only blacklist code works
-
-# source("../study1/vacc_import_data.R")
-
-library(tidyverse)
-
-# 
-# bd_to_bn_whitelist <- function(bdSummaryObj, threshold=.995) {
-#   # creates a whitelist for bnlearn from BDgraph adjacency matrix
-#   
-#   s <- bdSummaryObj
-#   s[lower.tri(s)] = t(s)[lower.tri(s)]
-#   
-#   fromDF <- s %>%
-#     data.frame() %>%
-#     rownames_to_column("from") %>%
-#     gather(to, posterior, -from) %>%
-#     filter(posterior >= threshold) %>%
-#     data.frame() %>%
-#     dplyr::select(from, to)
-#   toDF <- bdSummaryObj %>%
-#     data.frame() %>%
-#     rownames_to_column("to") %>%
-#     gather(from, posterior, -to) %>%
-#     filter(posterior >= threshold) %>%
-#     data.frame() %>%
-#     dplyr::select(from, to)
-#   whitelist <- bind_rows(fromDF,toDF)
-# }
-
-bd_to_bn_blacklist <- function(BDtrimmed) {
-  # creates a blacklist for bnlearn from BDgraph adjacency matrix
-  
-    s <- as.matrix(BDtrimmed)
-    s[lower.tri(s)] = t(s)[lower.tri(s)]
-  
-    blacklist <- s %>%
-      data.frame() %>%
-      rownames_to_column("from") %>%
-      gather(to, present, -from) %>%
-      filter(present==0) %>%
-      filter(from!=to) %>%
-      data.frame() %>%
-      dplyr::select(from, to)
-    
-}

### 2021-06-21 scripts/bnLavaan.R

@@ -1,164 +1,0 @@
-# author: Derek Powell
-# created: 11/3/17, 10:28 AM
-# last updated: 11/3/17, 1:44 PM
-
-# script for translating bnlearn arcs to lavaan
-
-library(tidyverse)
-library(stringr)
-
-cat_string_list <- function(listOfStrings) {
-  paste(listOfStrings, collapse="")
-}
-
-
-cat_plus <- function(x) {
-  return(paste(x,"+ "))
-}
-
-
-cat_weight <- function(x,wVal) {
-  wVal <- round(wVal,4) # to keep human-readable
-  paste0(wVal,"*",x)
-}
-
-
-cat_weight_list <- function(x,wVals) {
-  mapply(cat_weight,x,wVals)
-}
-
-
-write_sum <- function(toBeSummed) {
-  firstPart <- sapply(toBeSummed[1:length(toBeSummed)-1],cat_plus)
-  cat_string_list(c(firstPart,toBeSummed[length(toBeSummed)]))
-}
-
-
-cat_and_sort <- function(x,y) {
-  sort(c(x,y)) %>% as.character(collapse="") %>% paste(collapse="")
-}
-
-
-tag_arcs <- function(graphStruct) {
-  g <- graphStruct %>% 
-    mutate(from =  as.character(from)) %>%
-    mutate(to = as.character(to)) %>%
-    mutate(id = map2_chr(from, to, cat_and_sort))
-  return(as_tibble(g))
-}
-
-get_graphStruct <- function(bnObject) {
-  # Returns the graph structure ($arcs) from a bn object
-  # bnObject: any object of class bn
-  
-  graphStruct <- bnObject$arcs %>% as_tibble()
-  return(graphStruct)
-}
-
-make_weighted_lavaan_paths <- function(graphStruct, pathParams, residParams) {
-  # Translates bnlearn graph into lavaan syntax with randomly sampled weights
-  # for simulating data from graphical models
-  # Note: this function requires fully directed graph
-  # ---
-  # baseGraph: DAG from bnlearn
-  # pathParams: c(a,b) for Beta(a, b) for path coefficients 
-  # residParams: c(a,b) for Beta(a, b) for variances
-  
-  graphStruct <- graphStruct %>% mutate(from = as.character(from),
-                                        to = as.character(to))
-  allNodes <- unique(c(graphStruct$from, graphStruct$to)) %>% as.character()
-  
-  modelStr <- ""
[…]

### 2021-06-21 scripts/bnTheoryBlacklist.R

@@ -1,83 +1,0 @@
-# bnTheoryBlacklist.R
-# Author: derek powell
-# created: 1/17/18, 12:56 PM
-
-# this script will take a dataframe with variables for the "order" of nodes
-# and create a blacklist that prevents violations of that order
-
-library(tidyverse)
-
-# testData <- data.frame(node=c("diseaseRare", 
-#                               "diseaseSevere", 
-#                               "hb", 
-#                               "infantImmLimCap", 
-#                               "infantImmWeak", 
-#                               "medSkept", 
-#                               "nat", 
-#                               "overpar", 
-#                               "parentExpert", 
-#                               "vaccDanger", 
-#                               "vaccEff", 
-#                               "vaccIntent", 
-#                               "vaccStrain",
-#                               "vaccTox"),
-#                        order = c(
-#                                  3,
-#                                  3,
-#                                  1,
-#                                  3,
-#                                  3,
-#                                  2,
-#                                  1,
-#                                  2,
-#                                  2,
-#                                  3,
-#                                  3,
-#                                  4,
-#                                  3,
-#                                  3
-#                                ))
-
-make_theory_blacklist <- function(df) {
-  
-  result <- NULL
-  
-  for (targNode in df$node) {
-    ord <- df %>% dplyr::filter(node==targNode) %>% dplyr::select(order) %>% as.numeric()
-    d <- df %>% dplyr::filter(order < ord) %>% dplyr::mutate(from=targNode, to=node) %>% dplyr::select(from, to)
-    
-    if (is.null(result)) {
-      result <- d
-    }
-    else {
-      result <- dplyr::bind_rows(result, d)
-    }
-  }
-  
-  result <- dplyr::distinct(result, to, from)
-  
-  return(result)
-}
-
-combine_blacklists <- function(bList1, bList2) {
-
-  dplyr::bind_rows(bList1, bList2) %>% dplyr::distinct(to, from)
-
-  }
-
-# 
-# result <- NULL
-# 
-# for (targNode in testData$node) {
-#   ord <- testData %>% filter(node==targNode) %>% select(order) %>% as.numeric()
-#   d <- testData %>% filter(order < ord) %>% mutate(from=targNode, to=node) %>% select(from, to)
-#   
-#   if (is.null(result)) {
-#     result <- d
-#   }
-#   else {
-#     result <- bind_rows(result, d)
-#   }
-# }
-# 
-# result <- distinct(result, to, from)

### 2021-06-21 scripts/cextend_all.R

@@ -1,53 +1,0 @@
-# Author: Derek Powell
-# Created: 12/20/17, 3:34 PM
-# Last updated: 12/20/17, 3:34 PM
-
-tag_arcs <- function(graphStruct) {
-  g <- graphStruct %>% 
-    mutate(from =  as.character(from)) %>%
-    mutate(to = as.character(to)) %>%
-    mutate(id = map2_chr(from, to, cat_and_sort))
-  return(as_tibble(g))
-}
-
-cextend_all <- function(cpDAG) {
-  # Generate all consistent extensions of equivalence class
-  # cpDAG: complete partially directed graph (cpdag(bnobject))
-  # returns: a list of bn objects
-  library(gtools)
-  undirected <- undirected.arcs(cpDAG) %>% as_tibble() %>% tag_arcs()
-  uniqueArcs <- unique(undirected$id)
-  
-  arcDF <- undirected %>% distinct(id, .keep_all=TRUE)
-  arcNum <- nrow(arcDF)
-  
-  # m <- as.data.frame(matrix(rbinom(arcNum*2, 1, 0.5),ncol=arcNum))
-  
-  grid <- gtools::permutations(2,arcNum,v=c(0,1),repeats.allowed=TRUE)
-  # permutations(2,i,v=c(0,1),repeats.allowed=TRUE)
-  # grid <- expand.grid(m)
-  
-  graphList <- list()
-  for (i in 1:dim(grid)[1]) {
-    # for (i in 1:50) {
-    gDF <- arcDF %>% mutate(direction = as.numeric(grid[i,]))
-    g <- cpDAG
-    for (j in 1:nrow(gDF)) {
-      arc <- gDF[j,]
-      if (arc$direction==1){
-        g <- set.arc(g,arc$from,arc$to, check.cycles=FALSE, check.illegal=FALSE)
-        
-      } else if (arc$direction==0) {
-        g <- set.arc(g, arc$to, arc$from, check.cycles=FALSE, check.illegal=FALSE)
-      }
-    }
-    checkDag <- acyclic(g)
-    
-    if (checkDag==TRUE) {
-      # graphList <- c(graphList, g)
-      graphList[[length(graphList)+1]] <- g
-    }
-    
-  }
-  return(graphList)
-}

### 2021-06-21 scripts/crossValidate.R

@@ -1,181 +1,0 @@
-# author: Derek Powell
-# created: 11-02-2017
-# last updated: 1/11/18, 5:19 PM
-# Also available as gist:
-# devtools::source_gist("8838d867daa4185c9c09187a6b02f96b", filename="crossValidate.R")
-
-library(tidyverse)
-library(multidplyr)
-library(modelr)
-library(purrr)
-
-cross_validate <- function(df, model_func, score_func, nFolds=10, nRuns=10) {
-  # Function to perform cross validation and return results
-  # uses serial processing, for faster processing use multi_cross_validate
-  # df: data to examine
-  # model_func: model to use for train and test
-  # score_func: scoring function to measure model performance
-  # cluster: multidplyer cluster
-  # nFolds: number of folds for k-fold cross validation
-  # nRuns: number of runs to average over
-  
-  for (rep in 1:nRuns) {
-    repDF <- df %>% crossv_kfold(nFolds) %>% mutate(run = rep)
-    
-    if (rep == 1) {
-      mainDF <- repDF
-    }
-    
-    if (rep > 1) {
-      mainDF <- rbind(repDF, mainDF)
-    }
-  }
-  
-  mainDF %>%
-    mutate(train = map(train, as.data.frame)) %>%
-    mutate(model = map(train, model_func)) %>% 
-    mutate(test = map(test, as.data.frame)) %>%
-    mutate(score = map2_dbl(model, test, score_func)) #%>%
-    # group_by(run) %>% 
-    # summarize(score=mean(score)) # should add weighting for uneven kfolds
-}
-
-
-cv_compare <- function(df, model_funcs, model_names, score_func, nFolds=10, nRuns=10) {
-  # Function to perform cross validation with several functions and compare results
-  # uses serial processing, for faster processing use multi_cv_compare
-  # df: data to examine
-  # model_funcs: list of model to use for train and test
-  # model_names: list of model names to label results
-  # score_func: scoring function to measure model performance
-  # cluster: multidplyer cluster
-  # nFolds: number of folds for k-fold cross validation
-  # nRuns: number of runs to average over
-  
-  for (i in 1:length(model_funcs)) {
-    model_func <- model_funcs[i]
-    model_name <- model_names[i]
-    cvResult <- cross_validate(df, model_func, score_func, nFolds, nRuns) %>%
[…]

### 2021-06-21 scripts/custom-structure-learning/cog-model-discrete-funcs.R

@@ -1,198 +1,0 @@
-make_custom_cpt <- function(ps, dims, dim_names, data) {
-  # makes custom cpt in HydeNet format
-  output <- array(ps, dim=dims, dimnames=dim_names)
-  attr(output, "model") <- data
-  attr(output, "class") <- c("cpt","array")
-  
-  return(output)
-}
-
-
-result_to_cpt <- function(result, child, predictors, data) {
-  # compute cpt for child node given optim result and predictor variables
-  # result: optim result
-  # child: name of child node (string)
-  # data: dataframe
-  # return: array
-  states <- lapply(c(predictors,child), function(x){c(0,1)})
-  names(states) <- c(predictors,child)
-  states_labeled <- lapply(c(predictors,child), function(x){c("No","Yes")}) # not working 8/17/18, 9:44 AM
-  names(states_labeled) <- c(predictors,child)
-  ds <- ifelse(result > 0,1,0)
-  names(ds) <- sapply(names(result), function(x){paste0("d_",substr(x,3,100))})
-  result <- abs(c(result, ds[-(1:2)]))
-  
-  z <- expand.grid(states) %>%
-    mutate(
-      p = with(
-        as.data.frame(t(result)),
-        eval(parse(text=create_equation_expression(predictors)))
-      )
-    )
-  z[which(z[child]==0),"p"] <- 1-z[which(z[child]==0),"p"] # unnecessary to preserve child name oh well
-  
-  output <- make_custom_cpt(z$p, rep(2,length(predictors)+1), states_labeled, data)
-  return(output)
-}
-
-
-fake_xtabs <- function(node, data, trueval = 1, falseval = 0){
-  data <- as.data.frame(data)
-  probs <- data[, node]
-  p1 <- mean(probs)
-  count1 <- round(p1*1e5)
-  count0 <- 1e5 - count1
-  counts <- matrix(c(rep(trueval,count1), rep(falseval,count0)), ncol=1)
-  colnames(counts) <- c(node)
-  f <- paste0("~",node)
-  output <- xtabs(as.formula(f), data = counts)
-  attr(output, "call") <- list(formula = as.formula(f) )
-  
-  return(output)
-}
-
-
-fit_node_cpt <- function(node, data) {
-  child <- node$child # specific to format above ,could be imrpoved
[…]

### 2021-06-21 scripts/custom-structure-learning/cog-model-jags-tools.R

@@ -1,169 +1,0 @@
-# # Doing inference on beta DAGs through rjags
-# # ----
-
-do_jags_inference <- function(model, variable.names, data = NULL, iter = 1e4, silent=TRUE) {
-  if (silent) {
-    pbar <- "none"
-  } else {
-    pbar <- "text"
-  }
-  tc <- textConnection(model)
-  jags <- rjags::jags.model(tc, data = data, quiet=silent)
-  close(tc)
-  
-  model_samples <- rjags::coda.samples(jags, variable.names, iter*2, progress.bar="none")
-  return(model_samples)
-}
-
-
-make_predictions <- function(model, orig_data, nodes_to_predict, nodes_held_out=c(), iter=1e3) {
-  # takes a model and dataframe and generates model predictions for variables listed in 
-  # nodes_to_predict. By default, uses all remaining nodes in orig_data. Hold out nodes from
-  # prediction with nodes_held_out. iter sets mcmc samples
-  
-  pred_df <- orig_data
-  pred_df[,nodes_to_predict] <- NA
-  
-  for (i in 1:nrow(pred_df)) {
-    row <- pred_df[i,]
-    row[nodes_held_out] <- NA
-    pred <- do_jags_inference(model, nodes_to_predict, data = row, iter = iter)
-    point_preds <- rowMeans(t(pred[[1]][(iter/2+1):iter,nodes_to_predict]))
-    pred_df[i,nodes_to_predict] <- point_preds
-  }
-  
-  return(pred_df)
-}
-
-assemble_fitted_equation <- function(w_leak, prevterms, genterms) {
-  # assembles the noisy-or-and-nor equation
-  # prevterms: probability of non-prevention (p(fail prevent))
-  # genterms: probability of non-generation (p(fail generate))
-  # return: equation string
-  
-  gen <- paste0("(1-",w_leak, ")*",terms_product(genterms))
-  prev <- terms_product(prevterms)
-  paste0(wrap_paren(paste0("1-",gen)), " * ", terms_product(prevterms))
-}
-
-
-create_fitted_equation_expression <- function(predictors, coefs, digits = 5){
-  # creates equation string
-  # predictors: list of names of predictor variables (parents)
-  # return: equation string (expression to evaluate)
-  
-  coefs <- as.list(coefs)
[…]

### 2021-06-21 scripts/custom-structure-learning/cog-model-main.R

@@ -1,9 +1,0 @@
-## Inferring Discrete Cognitive Models from Continuous Belief Reports 
-## Beta regression of belief reports
-
-## initialize ...
-
-source("cog-model-scoring.R")
-source("cog-model-jags-tools.R")
-source("cog-model-bidag-functions.R")
-source("cog-model-discrete-funcs.R")

### 2021-06-21 scripts/custom-structure-learning/cog-model-scoring.R

@@ -1,519 +1,0 @@
-## Inferring Discrete Cognitive Models from Continuous Belief Reports 
-## Beta regression of belief reports
-
-## ----------------------------------------
-## functions to assemble model-fitting expressions 
-## ----------------------------------------
- 
-wrap_paren <- function(string){
-  # wrap string in parentheses
-  paste0("(",string,")")
-}
-
-
-terms_product <- function(termlist){
-  # writes formula for product of terms in termlist
-  # termlist: list of strings
-  # return: string
-  
-  output <- ""
-  for (i in 1:length(termlist)) {
-    output <- paste0(termlist[i],"*",output)
-  }
-  output <- substr(output, 1, nchar(output)-1)
-  return(output)
-}
-
-
-assemble_equation <- function(prevterms, genterms) {
-  # assembles the noisy-or-and-nor equation
-  # prevterms: probability of non-prevention (p(fail prevent))
-  # genterms: probability of non-generation (p(fail generate))
-  # return: equation string
-  
-  gen <- paste0("(1-w_leak)*",terms_product(genterms))
-  prev <- terms_product(prevterms)
-  paste0(wrap_paren(paste0("1-",gen)), " * ", terms_product(prevterms))
-}
-
-
-assign_pars_exp <- function(pars){
-  # creates expressions to initialize named weight parameters from par
-  # input: par_weights vector
-  # return: list of strings (to be evaluated as expressions)
-  
-  Map(function(x, i) paste0(x," <- abs(par[",i+2,"])"), pars, seq_along(pars))
-}
-
-
-assign_dpars_exp <- function(predictors){
-  # creates expressions to initialize named direction parameters from predictors
-  # input: predictors vector
-  # return: list of strings (to be evaluated as expressions)
-  
-  Map(function(x, i) paste0("d_",x," <- ifelse(par[",i+2,"] > 0,1,0)"), predictors, seq_along(predictors))
-}
-
-
-create_init_expression <- function(child, predictors){
-  # assembles initialization expressions
-  # child: name of predicted variable
-  # predictors: list of names of predictor variables (parents)
-  # return: list of strings (expressions to evaluate)
-  
-  par_weights <- sapply(predictors, function(x){paste0("w_",x)})
-  par_directions <- sapply(predictors, function(x){paste0("d_",x)})
[…]

### 2021-06-21 scripts/custom-structure-learning/fit-cog-models.R

@@ -1,237 +1,0 @@
-
-# load data
-# -----------------------------------------
-# source("../../study1/vacc_import_data.R", chd)
-
-
-# load packages
-# ----------------------------------------
-library(tidyverse)
-library(BiDAG)
-# BiDAG depends on 'graph' package, source: http://www.bioconductor.org/packages/release/bioc/html/graph.html
-# BiDAG depends on 'RBGL' package, source: https://bioconductor.org/packages/release/bioc/html/RBGL.html
-library(bnlearn)
-library(HydeNet)
-library(gtools)
-
-# source("cog-model-graph-tools.R")
-# source("cog-model-main.R")
-# source("../../Scripts/gmod_tools.R")
-# source("../../Scripts/bnTheoryBlacklist.R")
-
-
-# transform data
-# ----------------------------------------
-
-rescale_beta <- function(x, lower, upper) {
-  # rescales onto the open interval (0,1)
-  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"
-  
-  N <- length(x)
-  res <- (x - lower) / (upper - lower)
-  res <- (res * (N - 1) + .5) / N
-  
-  return(as.vector(res))
-}
-
-d_bn_scaled <- d_bn %>%
-  mutate_all(function(x){rescale_beta(x,-3,3)})
-
-## set the seed to make your partition reproductible
-set.seed(123)
-trainInd <- sample(seq_len(nrow(d_bn_scaled)), size = floor(nrow(d_bn_scaled)*.80))
-
-train <- d_bn_scaled[trainInd, ]
-test <- d_bn_scaled[-trainInd, ]
-
-
-# generate blacklists
-# ----------------------------------------
-nodes <- c(
-  "diseaseRare",
-  "diseaseSevere",
-  "hb",
-  "infantImmLimCap",
-  "infantImmWeak",
-  "medSkept",
-  "nat",
-  "overpar",
-  "parentExpert",
-  "vaccDanger",
-  "vaccEff",
-  "vaccIntent",
-  "vaccStrain",
-  "vaccTox"
-)
-
-theoryBasedHierarchy <- data.frame(
-  node = nodes,
-  order = c(
-    3,
-    3,
-    1,
-    3,
-    3,
-    2,
-    1,
-    2,
-    2,
-    3,
-    3,
-    4,
-    3,
-    3
-  )
-)
-
-intent_is_dv <- data.frame(
-  node = nodes,
[…]

### 2021-06-21 scripts/custom_plotting.R

@@ -1,45 +1,0 @@
-custom_plot.HydeNetwork <- function(x, 
-                             customNodes = NULL,
-                             customEdges = NULL,
-                             ..., 
-                             removeDeterm = FALSE,
-                             useHydeDefaults = TRUE)
-{
-  if (removeDeterm) x <- plot_nondeterm_only(x)
-  
-  node_df <- 
-    DiagrammeR::create_node_df(n = length(x[["nodes"]]),
-                               label = x[["nodes"]])
-  # 
-  # node_df <- data.frame(nodes = x[["nodes"]],
-  #                       stringsAsFactors = FALSE)
-  if (useHydeDefaults) node_df <- HydeNet:::mergeDefaultPlotOpts(x, node_df)
-  
-  if (!is.null(customNodes)) node_df <- HydeNet::mergeCustomNodes(node_df, customNodes)
-  
-  edge_table <- do.call("rbind", 
-                        mapply(FUN = HydeNet:::mapEdges, 
-                               x[["nodes"]], 
-                               x[["parents"]],
-                               MoreArgs = list(node_df = node_df)))
-  
-  edge_df <- DiagrammeR::create_edge_df(from = edge_table[, 2], 
-                                        to = edge_table[, 1])
-  
-  if (!is.null(customEdges)) HydeNet::mergeCustomEdges(edge_df, customEdges)
-  
-  
-  
-  DiagrammeR::create_graph(nodes_df = node_df,
-                           edges_df = edge_df,
-                           attr_theme = NULL)
-  
-}
-
-
-## ----------------------------------------
-
-# code to demo. For some reason set_edge_attrs() isn't working right, so have to do it manually
-z <- custom_plot.HydeNetwork(h)
-z$edges_df <- z$edges_df %>% mutate(color = "blue", penwidth=rep(c(1,2,3),10))
-render_graph(z)

### 2021-06-21 scripts/gmod_tools.R

@@ -1,454 +1,0 @@
-# gmod_tools.R
-# Author: Derek Powell
-# Created: 4/24/18
-# Updated: 5/10/18, 4:04 PM
-#
-# Tools for working with graphical models. Gathering functions created across notebooks/scripts into a single set of tools
-# for the project. May split them back out again if this gets too unweildy
-#
-# 1. Translating graphs/networks among existing R packages
-# 2. Doing MCMC inference on DAGs
-# 3. Creating pseudo-dbn networks
-
-# todo: 
-# 1. document functions
-# 2. refactor and possibly rename funcs/arguments
-# 3. explicitly map package functions with :: (done?)
-# 4. reduce dependencies(?)
-
-library(tidyverse)
-library(stringr)
-
-### ----------------------------------------
-# Translation functions
-# bnlearn, bdgraph, lavaan, and HydeNet
-
-
-# basic string functions
-cat_string_list <- function(listOfStrings) {
-  paste(listOfStrings, collapse = "")
-}
-
-
-cat_plus <- function(x) {
-  return(paste(x, "+ "))
-}
-
-
-cat_weight <- function(x, wVal) {
-  wVal <- round(wVal, 4) # to keep human-readable
-  paste0(wVal, "*", x)
-}
-
-
-cat_weight_list <- function(x, wVals) {
-  mapply(cat_weight, x, wVals)
-}
-
-
-write_sum <- function(toBeSummed) {
-  firstPart <- sapply(toBeSummed[1:length(toBeSummed) - 1], cat_plus)
-  cat_string_list(c(firstPart, toBeSummed[length(toBeSummed)]))
-}
-
-cat_and_sort <- function(x, y) {
-  sort(c(x, y)) %>% as.character(collapse = "") %>% paste(collapse = "")
-}
-
-wrap_brackets <- function(string) {
-  return(paste0("[", string, "]"))
-}
-
-wrap_space <- function(string) {
-  return(paste0(" ", string, " "))
-}
-
-get_left_of <- function(pattern, string) {
-  trimws(strsplit(string, pattern)[[1]][1])
-}
-
-# bnlearn --> arcs_df
-
-bnlearn_to_df <- function(bn.net) {
-  arcs <- data.frame(from = bnlearn::arcs(bn.net)[,1],
-                     to = bnlearn::arcs(bn.net)[,2])
-  return(arcs)
-}
-
-# arcs_df --> bnlearn
-
[…]

### 2021-06-21 scripts/load-data-s1-private.R

@@ -1,118 +1,0 @@
-
-# set wd (user-specific)
-# setwd("/Users/kweisman/Documents/Research (Stanford)/Projects/Vaccines/vaccineBeliefs/study1/")
-library(tidyverse)
-library(stringr)
-
-# working_dir <- getwd()
-# this.dir <- dirname(parent.frame(2)$ofile)
-# setwd(this.dir)
-
-# load in raw data
-d_raw <- read.csv("../data_private/study1_data.csv", header = T)
-
-# filter rows and select columns
-d1 <- d_raw %>%
-  filter(grepl("2017", StartDate)) %>% # remove extra headers
-  filter(Status == "IP Address") %>% # remove survey previews (?)
-  filter(Progress == 100) %>% # only get people who made it all the way through (?)
-  filter(as.numeric(as.character(age)) >= 18) %>% # exclude people who said they were <18 yo (could be more stringent)
-  select(StartDate, Duration..in.seconds., workerId, hb_1:comments) # include only selected columns
-
-# reformat variables
-d2 <- d1 %>% 
-  # mutate_at(vars(StartDate), funs(parse_datetime)) %>% # parse dates # 1/14/19, 3:12 PM this is throwing an error
-  # mutate_at(vars(Duration..in.seconds., age, children), funs(as.character)) %>% # parse numbers step 1
-  mutate_at(vars(Duration..in.seconds., age, children), funs(as.numeric)) %>% # parse numbers step 2
-  mutate(educ = factor(educ, # recode ordinal variables
-                       levels = c("No Diploma", "High School or Equivalent",
-                                  "Some Undergraduate Education", "Undergraduate Degree",
-                                  "Some Graduate or Professional Education",
-                                  "Graduate or Professional Degree", "Doctorate")),
-         income = factor(income, 
-                         levels = c("Less than $20,000", "$20,000 - $30,0000",
-                                    "$30,001 - $50,000", "$50,001 - $70,000",
-                                    "$70,001 - $100,000", "More than $100,000")),
-         parent = factor(parent, levels = c("No", "Yes")),
-         expecting = factor(expecting, levels =c ("No", "Yes")),
-         youngest_child = factor(youngest_child, 
-                                 levels = c("Less than 1 year old", "1 year old", "2 years old", 
-                                            "3 years old", "4 years old", "5 years old", "6 years old",
-                                            "7 years old", "8 years old", "9 years old", "10 years old",
-                                            "11 years old", "12 years old", "13 years old", "14 years old",
[…]

### 2021-06-21 scripts/load-data-s1.R

@@ -1,119 +1,0 @@
-
-# set wd (user-specific)
-# setwd("/Users/kweisman/Documents/Research (Stanford)/Projects/Vaccines/vaccineBeliefs/study1/")
-library(tidyverse)
-library(stringr)
-
-# working_dir <- getwd()
-# this.dir <- dirname(parent.frame(2)$ofile)
-# setwd(this.dir)
-
-# load in raw data
-d_raw <- read.csv("../data/study1_data.csv", header = T)
-
-# filter rows and select columns
-d1 <- d_raw %>%
-  filter(grepl("2017", StartDate)) %>% # remove extra headers
-  filter(Status == "IP Address") %>% # remove survey previews (?)
-  filter(Progress == 100) %>% # only get people who made it all the way through (?)
-  filter(as.numeric(as.character(age)) >= 18) %>% # exclude people who said they were <18 yo (could be more stringent)
-  select(StartDate, Duration..in.seconds., workerId, hb_1:comments) %>% # include only selected columns
-  filter(!duplicated(workerId)) # we had a worker take it twice somehow! caught 5/1/19, 2:33 PM
-
-# reformat variables
-d2 <- d1 %>% 
-  # mutate_at(vars(StartDate), funs(parse_datetime)) %>% # parse dates # 1/14/19, 3:12 PM this is throwing an error
-  # mutate_at(vars(Duration..in.seconds., age, children), funs(as.character)) %>% # parse numbers step 1
-  mutate_at(vars(Duration..in.seconds., age, children), funs(as.numeric)) %>% # parse numbers step 2
-  mutate(educ = factor(educ, # recode ordinal variables
-                       levels = c("No Diploma", "High School or Equivalent",
-                                  "Some Undergraduate Education", "Undergraduate Degree",
-                                  "Some Graduate or Professional Education",
-                                  "Graduate or Professional Degree", "Doctorate")),
-         income = factor(income, 
-                         levels = c("Less than $20,000", "$20,000 - $30,0000",
-                                    "$30,001 - $50,000", "$50,001 - $70,000",
-                                    "$70,001 - $100,000", "More than $100,000")),
-         parent = factor(parent, levels = c("No", "Yes")),
-         expecting = factor(expecting, levels =c ("No", "Yes")),
-         youngest_child = factor(youngest_child, 
-                                 levels = c("Less than 1 year old", "1 year old", "2 years old", 
-                                            "3 years old", "4 years old", "5 years old", "6 years old",
[…]

### 2021-06-21 scripts/load-data-s2.R

@@ -1,67 +1,0 @@
-# load data for study 2
-# Kara's code
-
-library(tidyverse)
-d_all <- read.csv("../data/study2_data.csv")[-1] %>%
-  # filter out anyone who failed attention checks
-  filter(hb_check_5_pretest == 1, hb_check_5_posttest == 1,
-         vaccEff_check_1_pretest == -3, vaccEff_check_1_posttest == -3, 
-         vaccDanger_check_3_pretest == -1, vaccDanger_check_3_posttest == -1, 
-         vaccTox_check_6_pretest == 2, vaccTox_check_6_posttest ==2) %>%
-  # remove attention checks from dataset
-  select(-contains("check"))
-
-# reformat to match previous analyses (i.e., 2 rows per participant)
-d_demo <- d_all %>% 
-  select(workerId, condition, gender, age, ethnicity, education, job, income,
-         political_party, political_beliefs, eligible_pretest, 
-         is_parent_posttest, children_num_posttest, children_oldest_posttest, 
-         children_youngest_posttest, plan_parent_posttest,
-         starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
-         starts_with("comments"), starts_with("duration"))
-
-d_pre <- d_all %>% 
-  select(workerId, ends_with("_pretest")) %>%
-  select(-c(eligible_pretest, starts_with("flushot_"), starts_with("vax_"), 
-            starts_with("attention_"), starts_with("comments"), 
-            starts_with("duration"))) %>%
-  rename_all(funs(gsub("_pretest", "", .))) %>%
-  mutate(phase = "pre")
-
-d_post <- d_all %>% 
-  select(workerId, ends_with("_posttest")) %>%
-  select(-c(is_parent_posttest, children_num_posttest, children_oldest_posttest,
-            children_youngest_posttest, plan_parent_posttest,
-            starts_with("flushot_"), starts_with("vax_"), starts_with("attention_"),
-            starts_with("comments"), starts_with("duration"))) %>%
-  rename_all(funs(gsub("_posttest", "", .))) %>%
-  mutate(phase = "post")
-
-d <- bind_rows(d_pre, d_post) %>% 
-  gather(question, response, -c(workerId, phase)) %>%
-  mutate(phase = factor(phase,
-                        levels = c("pre", "post")),
-         reverse_cat = ifelse(grepl("_[1-9]r$", question), TRUE, FALSE),
-         # NOTE: "response" has already been reverse coded!
-         question = factor(question),
[…]

### 2021-06-21 scripts/load-data-s3.R

@@ -1,62 +1,0 @@
-library(tidyverse)
-
-read_qualtrics <- function(fname){
-  # load raw qualtrics data
-  header <- colnames(read.csv(fname, header = TRUE))
-  df <- read.csv(fname, skip = 3, header = FALSE, col.names = header)
-  
-  # do some preliminary tidying
-  df <- df %>%
-    as_tibble()
-  
-  return(df)
-}
-
-pre <- read_qualtrics("../data/vacc+tox+interv+full+-+pre_April+3,+2019_15.38.csv")
-post <- read_qualtrics("../data/vacc+tox+interv+full+-+post_April+5,+2019_13.59.csv")
-
-
-df_pre <- pre %>%
-  filter(workerId!="e082cf59a57d4562") %>% # hashed manually
-  filter(Progress==100, check_3==3, check_5==5) %>%
-  mutate(parent = recode(parent, `23`=1, `24`=0)) %>%
-  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5, parent) %>%
-  gather(item, resp, -workerId, -parent) %>%
-  mutate(item = paste0("pre_",item)) %>%
-  spread(item, resp)
-
-df_post <- post %>%
-  filter(Progress==100, check_3==3, check_5==5) %>%
-  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5,
-         condition, interv_t_Page.Submit) %>%
-  rename(read_time = interv_t_Page.Submit) %>%
-  gather(item, resp, -workerId, -condition, -read_time) %>%
-  mutate(item = paste0("post_",item)) %>%
-  spread(item, resp)
-
-
-df <- left_join(filter(df_pre, workerId %in% df_post$workerId), df_post, by="workerId") %>%
-  mutate_at(vars(matches(".*(_[0-9]*r)")), funs(8 - .)) %>% # reverse code
-  gather(item, resp, matches(".*(_[0-9])")) %>%
-  mutate(phase = ifelse(grepl("pre_",item),"pre","post")) %>%
-  mutate(
-    item = gsub("pre_","",item),
-    item = gsub("post_","",item)
-  ) %>%
-  mutate(scale = gsub("(_([0-9])+(r)*)","",item))
-
-df_scored <- df %>%
-  group_by(workerId, condition, scale, phase, parent) %>%
-  summarize(mean_resp = mean(resp)) %>%
-  spread(phase, mean_resp) %>%
[…]

### 2021-06-21 scripts/load-data-s4.R

@@ -1,34 +1,0 @@
-library(tidyverse)
-library(lubridate)
-
-read_qualtrics <- function(fname){
-  # load raw qualtrics data
-  header <- colnames(read.csv(fname, header = TRUE))
-  df <- read.csv(fname, skip = 3, header = FALSE, col.names = header)
-  
-  # do some preliminary tidying
-  df <- df %>%
-    as_tibble()
-  
-  return(df)
-}
-
-df4 <- read_qualtrics("../data/vaccine+many+beliefs+-+may2019_May+21,+2019_16.12.csv")
-
-df4 <- df4 %>%
-  filter(!duplicated(workerId)) %>%
-  filter(check_3==3, check_5==5) %>%
-  mutate(StartDate = ymd_hms(StartDate)) %>%
-  rename(Duration = Duration..in.seconds.) %>%
-  select(workerId, matches(".*(_[0-9])"), vacc_news, vacc_news_freq, 
-         news_time, news_favorable, vacc_conv, conv_favorable, outbreaks, outbreak_favorable, other,
-         sex, age, race, religion, educ, income, 
-         pol_party, pol_ind_leaning, parent, expecting, children,
-         youngest_child, refuse, comments, StartDate,
-         -check_3, -check_5
-         ) %>%
-  mutate_at(vars(matches(".*(_[0-9]*r)"), -pol_party_4_TEXT, -pol_rating_1), funs(8 - .)) %>% # reverse code
-  gather(item, resp, matches(".*(_[0-9])"), -pol_party_4_TEXT, -pol_rating_1) %>%
-  mutate(scale = gsub("(_([0-9])+(r)*)","",item)) %>%
-  mutate(resp = as.numeric(resp))
-

### 2021-06-21 scripts/loss.R

@@ -1,140 +1,0 @@
-# this is from bnlearn package
-# available at:
-# https://github.com/cran/bnlearn/blob/1100114a7e14b447b80f95ae2790c1bb18198c57/R/loss.R
-# copy/pasted 1/4/18, 10:32 AM
-
-loss.function = function(fitted, data, loss, extra.args, debug = FALSE) {
-
-  if (loss %in% c("logl", "logl-g", "logl-cg")) {
-
-    result = entropy.loss(fitted = fitted, data = data, debug = debug)
-
-  }#THEN
-  else if (loss %in% c("pred", "pred-lw", "pred-lw-cg")) {
-
-    result = classification.error(node = extra.args$target, fitted = fitted,
-               prior = extra.args$prior, n = extra.args$n,
-               from = extra.args$from, data = data, loss = loss, debug = debug)
-
-  }#THEN
-  else if (loss %in% c("cor", "cor-lw", "cor-lw-cg")) {
-
-    result = predictive.correlation(node = extra.args$target, fitted = fitted,
-               n = extra.args$n, from = extra.args$from, data = data,
-               loss = loss, debug = debug)
-
-  }#THEN
-  else if (loss %in% c("mse", "mse-lw", "mse-lw-cg")) {
-
-    result = mean.square.error(node = extra.args$target, fitted = fitted,
-               n = extra.args$n, from = extra.args$from, data = data,
-               loss = loss, debug = debug)
-
-  }#THEN
-
-  if (debug)
-    cat("  @ total loss is", result$loss, ".\n")
-
-  return(result)
-
-}#LOSS.FUNCTION
-
-# how to aggregate loss functions across the folds of cross-validation.
-kfold.loss.postprocess = function(kcv, kcv.length, loss, extra.args, data) {
-
-  if (loss %in% c("cor", "cor-lw")) {
-
-    if (all(is.na(unlist(sapply(kcv, "[", "loss"))))) {
-
-      # this happens for root nodes, whose predictions are just the mean of
-      # the response over the test set; propagate the NAs to the CV estimate.
-      mean = NA
-
-    }#THEN
-    else {
-
-      # match predicted and observed values.
-      pred = unlist(lapply(kcv, "[[", "predicted"))
-      obs = unlist(lapply(kcv, "[[", "observed"))
-      # compute the predictive correlation.
-      mean = cor(obs, pred)
-
-    }#ELSE
-
-  }#THEN
-  else {
-
[…]

### 2021-06-21 scripts/modelstringFuncs.R

@@ -1,96 +1,0 @@
-# Functions for translating network objects across packages via model strings / formulas
-# Author: Derek Powell
-# Created: 3/8/18, 3:46 PM
-# Updated: 3/8/18, 4:24 PM
-
-wrap_brackets <- function(string) {
-  return(paste0("[",string,"]"))
-}
-
-wrap_space <- function(string) {
-  return(paste0(" ",string," "))
-}
-
-make_bnlearn_node_string <- function(node, children) {
-  output <- as.character(node)
-  
-  if (length(children) > 0) {
-    output <- paste0(output,"|")
-    for (c in children) {
-      output <- paste0(output,c,":") 
-      
-    }
-    output <- substr(output,1,nchar(output)-1)
-  }
-  
-  return(wrap_brackets(output))
-}
-
-make_hyde_node_string <- function(node, children) {
-  output <- as.character(node)
-  
-  if (length(children) > 0) {
-    output <- paste0(output,"|")
-    for (c in children) {
-      output <- paste0(output,c,"*") 
-      
-    }
-    output <- substr(output,1,nchar(output)-1)
-  }
-  
-  return(wrap_space(output))
-}
-
-df_to_hyde_string <- function(df) {
-  output <- ""
-  for (node in unique(unlist(df))) {
-    edges <- df[which(df$to==node),"from"]
-    edges <- edges$from
-    nodeString <- make_hyde_node_string(node, edges)
-    output <- paste0(output,"+",nodeString)
-    
-  }
-  output <- paste0("~",substr(output, 2, nchar(output)))
-  
-  return(output)
-}
-
-
-df_to_bnlearn_string <- function(df) {
-  output <- ""
-  for (node in unique(unlist(df))) {
-    edges <- df[which(df$to==node),"from"]
-    edges <- edges$from
-    nodeString <- make_node_string(node, edges)
-    output <- paste0(output,nodeString)
-    
-  }
-  return(output)
-}
-
-bnlearn_to_hyde <- function(bn.net) {
-  arcs <- as.data.frame(bnlearn::arcs(bn.net))
-  return(df_to_hyde_string(arcs))
-}
-
-bn_to_dbn <- function(model) {
-  # takes a bnlearn bn, bn.fit, or modelstring and transforms it into a dynamic bayes net
-  # with a second mirrored stage (could later be generalized to add a timestep)
[…]

### 2021-06-21 scripts/prettyGraph.R

@@ -1,208 +1,0 @@
-# library(GGally)
-# library(network)
-# library(sna)
-library(ggthemes)
-set.seed(123)
-# make function to get edge weights out of fitted network
-get_weights <- function(bnFitted) {
-  arcDf <- arcs(bnFitted)
-  
-  apply(arcDf, 1, function(x){
-    from <- x[1]
-    to <- x[2]
-    
-    val <- bnFitted[[to]][["coefficients"]][[from]]
-  })
-  
-}
-
-train.scaled <- train %>% scale() %>% as_tibble()
-net.fit.std <- bn.fit(net.bd.hc, train.scaled)
-# make function to label nodes with abstractness tiers
-recode_nodes <- function(x){
-  recode(x,
-         "diseaseRare" = "disease\nrarity",
-         "diseaseSevere" = "disease\nseverity",
-         "hb" = "holistic\nbalance",
-         "infantImmLimCap" = "IIS:\nlimited\ncapacity",
-         "infantImmWeak" = "IIS:\nweakness",
-         "medSkept" = "medical\nskepticism",
-         "nat" = "naturalism",
-         "overpar" = "parental\nprotective-\nness",
-         "parentExpert" = "parental\nexpertise",
-         "vaccDanger" = "vaccine\ndanger",
-         "vaccEff" = "vaccine\neffective-\nness",
-         "vaccIntent" = "vaccination\nintentions",
-         "vaccStrain" = "IIS:\nvaccines\nstrain",
-         "vaccTox" = "vacc. toxic\nadditives")}
-
-tiers <- c("claims", "worldviews", "claims", 
-           "theories", "worldviews", "theories", 
-           "theories", "claims", "claims", 
-           "claims", "claims", "claims", 
-           "claims", "intentions")
-
-# make dataframe for plotting
-temp_df <- arcs(net.fit.std) %>%
-  data.frame() %>%
-  mutate(edge_param = get_weights(net.fit.std),
-         edge_weight = edge_param,
-         pprint_edge_weight = pprint_cor(edge_param)
-         # edge_weight = abs(edge_param),
-         # edge_sign = factor(sign(edge_param))
-         ) %>%
-  mutate_at(vars(from, to), funs(recode_nodes))
-
-# manually flag arbitrarily directed arcs
-temp_df[4,5] <- temp_df[4,5] %>% paste0("*")
[…]

### 2021-06-21 scripts/transformation.R

@@ -1,18 +1,0 @@
-boxcox_transform <- function(x, lambda2=NULL) {
-	# finds optimal boxcox transformation parameters and performs transformation
-  	# (requires AID and car packages)
-  	# returns box-cox transformed variable
-  minval <- min(x)
-  
-  if(minval <= 0) {lambda2 <- abs(minval) + .01}
-  if(!is.null(lambda2)) {x <- x + lambda2}
-  
-  bc <- AID::boxcoxnc(x, lambda = seq(-10,10,.01), lambda2=lambda2, plot=FALSE, verbose=FALSE)
-    
-  return(car::bcPower(x, bc$lambda.hat))
-}
-
-normalize <- function(x) {
-	# rescale variable to (0,1) range
-    return ((x - min(x)) / (max(x) - min(x)))
-  }

### 2021-06-21 scripts/virtualEvidence.R

@@ -1,216 +1,0 @@
-# # Author: Derek Powell
-# # Updated: 5/14/18, 2:57 PM
-
-# # code for applying virtual evidence to cognitive model
-
-# functions for creating virtual evidence formula links
-
-make_ve_formula_strings <- function(nodes, suffix = "_v") {
-  lapply(nodes, function(x){paste0(x, suffix, " ~ ", x)})
-}
-
-# functions for fitting the weights of those links
-fit_formulas <- function(formula_strings, data, family="gaussian") {
-  # take a list of formulas as strings and return fit glm objects
-  # formula_strings: strings specifying formulas
-  # data: data for analyses
-  # family: glm family string or function object
-  
-  if (family %in% c("gaussian","binomial","gamma")) {# etc, finish later
-    lapply(formula_strings, function(x) {
-      glm(as.formula(x), data = data, family = family)
-    })
-  } else if (family=="beta") {
-    require(betareg)
-    lapply(formula_strings, function(x) {
-      betareg::betareg(as.formula(x), data = data)
-    })
-  }
-}
-
-# A function to assemble the results with the original model
-# 1. get lm coefficients and make jags code (modify make_jags_eq for lm())
-
-glm_to_jags_eq <- function(fit, digits=5) {
-  # fit: glm fit object
-  # returns jags code
-  
-  if (class(fit) == "glm") {
-    response_node <- as.character(formula(fit))[2]
-    coefs <- round(fit$coefficients, digits)
-    linear_eq <- paste0(coefs[1])
-    
-    if (length(coefs) > 1) {
-      
-      for (i in 2:length(coefs)) {
-        
-        coef_name <- names(coefs)[i]
-        coef <- coefs[i]
-        linear_eq <- paste0(linear_eq, " + ", coef, "*", coef_name)
-      }
-    }
-    if (fit$family$family == "gaussian") {
-      precision <- 1/stats::sigma(fit)^2
-      paste0(response_node," ~ ", "dnorm(", linear_eq,", ", round(precision,5),")")
-    } else if (fit$family$family == "binomial") {
-      paste0(response_node, " ~ ", "dbern(ilogit(", linear_eq, "))")
-    }
-  } else if (class(fit) == "betareg") {
-    
[…]

### 2021-06-21 study1/vacc_import_data.R

@@ -1,118 +1,0 @@
-
-# set wd (user-specific)
-# setwd("/Users/kweisman/Documents/Research (Stanford)/Projects/Vaccines/vaccineBeliefs/study1/")
-library(tidyverse)
-library(stringr)
-
-# working_dir <- getwd()
-# this.dir <- dirname(parent.frame(2)$ofile)
-# setwd(this.dir)
-
-# load in raw data
-d_raw <- read.csv("../data/study1_data.csv", header = T)
-
-# filter rows and select columns
-d1 <- d_raw %>%
-  filter(grepl("2017", StartDate)) %>% # remove extra headers
-  filter(Status == "IP Address") %>% # remove survey previews (?)
-  filter(Progress == 100) %>% # only get people who made it all the way through (?)
-  filter(as.numeric(as.character(age)) >= 18) %>% # exclude people who said they were <18 yo (could be more stringent)
-  select(StartDate, Duration..in.seconds., ResponseId, hb_1:comments) # include only selected columns
-
-# reformat variables
-d2 <- d1 %>% 
-  # mutate_at(vars(StartDate), funs(parse_datetime)) %>% # parse dates # 1/14/19, 3:12 PM this is throwing an error
-  # mutate_at(vars(Duration..in.seconds., age, children), funs(as.character)) %>% # parse numbers step 1
-  mutate_at(vars(Duration..in.seconds., age, children), funs(as.numeric)) %>% # parse numbers step 2
-  mutate(educ = factor(educ, # recode ordinal variables
-                       levels = c("No Diploma", "High School or Equivalent",
-                                  "Some Undergraduate Education", "Undergraduate Degree",
-                                  "Some Graduate or Professional Education",
-                                  "Graduate or Professional Degree", "Doctorate")),
-         income = factor(income, 
-                         levels = c("Less than $20,000", "$20,000 - $30,0000",
-                                    "$30,001 - $50,000", "$50,001 - $70,000",
-                                    "$70,001 - $100,000", "More than $100,000")),
-         parent = factor(parent, levels = c("No", "Yes")),
-         expecting = factor(expecting, levels =c ("No", "Yes")),
-         youngest_child = factor(youngest_child, 
-                                 levels = c("Less than 1 year old", "1 year old", "2 years old", 
-                                            "3 years old", "4 years old", "5 years old", "6 years old",
-                                            "7 years old", "8 years old", "9 years old", "10 years old",
-                                            "11 years old", "12 years old", "13 years old", "14 years old",
[…]

### 2021-06-21 supplement/supplement-main.Rmd
minor updates

@@
 author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
-date: "Jun 1, 2021 (DRAFT)"
+date: "June 21, 2021 (DRAFT)"
 output:
@@
 # leaves 5 arcs that are unconstrained by both data and theory
-anti_join(as.data.frame(undirected.arcs(main_cpdag)), (ruled_out %>% bind_rows(ruled_out %>% rename(to="from", from="to")) ), by = c("from", "to"))
+uncompelled_edges <- anti_join(as.data.frame(undirected.arcs(main_cpdag)), (ruled_out %>% bind_rows(ruled_out %>% rename(to="from", from="to")) ), by = c("from", "to"))
 
@@
 
-coefs %>%
+edge_df_mod <- coefs %>%
   filter(parameter!="phi",parameter!="w_leak") %>%
@@
   merge(z$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
-  mutate(from = id) %>%
-  select(-id) %>%
+  # mutate(from = id) %>%
+  rename(from_id = id) %>% 
   merge(z$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
-  mutate(to = id) %>%
-  arrange(to,from) -> edge_df_mod
-  # select(value, id.x, id.y) %>%
-  # mutate(from = id.x, to = id.y)
+  rename(to_id = id) %>%
+  arrange(to_id,from_id)
+
+## flag edges that could be flipped
+edge_df_mod <- uncompelled_edges %>% 
+  mutate(label="*") %>% 
+  right_join(edge_df_mod, by = c("to", "from")) %>% 
+  mutate(label = ifelse(is.na(label), "", label)) %>% 
+  arrange(to_id,from_id)
 
@@
 z$edges_df$penwidth <- 1.5
-z$edges_df$label <- round(edge_df_mod$value,2)
+# z$edges_df$label <- round(edge_df_mod$value,2)
+z$edges_df$label <- edge_df_mod$label
 # z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
-z$edges_df$color <- map_to_brewer(edge_df_mod$value, option="RdBu")
+z$edges_df$color <- map_to_brewer(edge_df_mod$value, bins=11, option="RdBu")
 
@@
 
+```
+```{r}
+coefs %>%
+  filter(parameter!="phi",parameter!="w_leak") %>%
+  rename(from = parameter) %>%
+  mutate(from = gsub("w_","",from)) %>%
+  select(to, from, value) %>%
+  merge(z$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
+  # mutate(from = id) %>%
+  rename(from_id = id) %>% 
+  merge(z$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
+  rename(to_id = id) %>%
+  arrange(to_id,from_id)
 ```
@@
 
+cowplot::save_plot("../local/graph-legend.svg", main_graph_legend)
 cowplot::ggdraw(main_graph_legend)
+
 ```
@@
   ) %>% 
-make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3.")
+make_table("Bayesian regression model coefficients for model of Vaccine Intentions combining data from Experiments 3a and 3b.")
 ```

### 2021-06-21 code/custom-structure-learning/fit-cog-models-bnlearn.R

@@ -159,53 +159,3 @@ for (i in 1:length(models)) {
 saveRDS(res_df_all, file="../../local/cv-res.rds")
 
 print("all completed, output saved")
-
-
-## as a first pass just do mmhc to see if blacklist is being respected
-
-
-
-
-# cog_model_score_func <- function(node, parents, data, args=NULL){
-#   return(score_family(node, parents, data))
-# }
-
-# mmhc_cv <- purrr::partial(mmhc, 
-#                           maximize.args = hc_args
-# )
-# 
-# mmhc_theory_cv <- purrr::partial(mmhc, 
-#                                  blacklist = theory_bl,
-#                                  maximize.args = hc_args
-# )
-# 
-# mmhc_intent_dv_cv <- partial(mmhc, blacklist = intent_dv_bl, maximize.args = hc_args)
-
-
-
-## going to have to implement my own CV functions and loss functions for held-out data
-## the jags thing is gonna be too slow, so gotta do it family-by-family ala scoring
-
-# already have the start of this with find_node_coefs(), just need to create a score from that
-## -------
-# 
-# bntest3 <- mmhc(
-#   train, 
-#   blacklist = theory_bl,
-#   maximize.args = list(score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000)
-#   )
-# 
-# # can get score but it is finding new parameters given the structure
-# # could pass in the training data in args and estimate w/ that rather than
-# # the original data being passed
-# # score(bntest3, test, type="custom", fun=cog_model_score_func, args=NULL)
-# 
-# # cog_model_score_func("vaccIntent",c("diseaseRare","vaccEff"), test)
-# 
-# 
-# # testing .. it works!
-# h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(bntest3)))
-# plot(h)
-# 
-# model_string <- suppressWarnings(write_jags_model(bntest3, train))
-# cat(model_string)

### 2021-06-22 install-packages.R
deleted extra notebooks

@@ -1,0 +1,20 @@
+## this will install all required packages
+## untested 6/22/21, 11:03 AM
+
+package_list <- c(
+  "tidyverse",
+  "brms",
+  "bnlearn",
+  "HydeNet",
+  "betareg",
+  "kableExtra",
+  "DiagrammeR",
+  "DiagrammeRsvg",
+  "corrplot",
+  "cowplot",
+  "caret"
+)
+
+install.packages(package_list)
+
+devtools::install_github("thomasp85/patchwork")

### 2021-06-22 supplement/supplement-main.Rmd
fixed prior commit

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 knitr::opts_chunk$set(fig.pos = 'H')
 ```
+
+This project represents a line of theoretical and empirical work seeking to understand misconceptions and belief revision in the context of people’s intuitive theories.
+We focus our efforts on reducing vaccine skepticism by identifying people’s intuitive theories surrounding vaccination decisions.
+Through this case study we hope to shed light on why such misconceptions persist and how educators and interventionists might address misconceptions more effectively across domains.
+We argue that correcting misconceptions requires presenting evidence in a way that is sensitive to and persuasive within the broader conceptual context in which those misconceptions reside (see Gershman, 2018; Weisman & Markman, 2017).
+Understanding the revision of any one specific belief (e.g., a misconception like _vaccines are dangerous_) demands a holistic understanding of the wider set of related beliefs that make up people's intuitive theories.
+
+First, we describe in further detail the modeling process for developing a Bayesian network model of the intuitive theory surrounding vaccination decisions.
+
+Then, we describe our empirical methods in detail.
+This begins with the qualitative research we conducted with vaccine skeptics to develop psychometrically-valid quantitative scales measuring a network of 14 beliefs related to vaccine skepticism.
+Then, we report the detailed methods for each of the empirical studies reported in the paper.
+In Study 1, we used Bayesian network structure learning algorithms to develop a cognitive model of the relationships among these beliefs in a large sample of people.
+This model can predict how beliefs correlate across people and how they would be revised in the face of evidence.
+In Study 2, we replicated the success of an existing intervention emphasizing the dangers of childhood diseases (Horne et al., 2015) and used our model to provide a more detailed understanding of _how and why_ this intervention increases vaccine intentions.
+In Study 3, we drew inspiration from our model to create and validate the success of  a novel intervention aimed at debunking concerns about toxic additives.
+Finally, in Study 4 we tested whether people's beliefs changed coherently following relevant real-world events, by examining beliefs before and after serious outbreaks of measles in the United States in early 2019.
 
@@
 
+In this graph, the edge $FIRE \rightarrow SMOKE$ captures that fire causes smoke.^[The example of cause and effect is especially intuitive, but these edges need not be causal.
+Instead, they are better thought of as representing “influence relations”, which may also include relationships like logical implication and set membership (Williamson, 2001).] This relationship is represented as a probabilistic function, where the probability of smoke depends on the probability of fire.
 The probability of a node Y can be defined from its parents X in many different ways.
-For binary nodes, the most flexible specification is a conditional probability table (CPT) with $2^n$ entries specifying the probability of Y given the entire joint probability distribution over X, where n is the number of parents X.
+For binary nodes, the most flexible specification is a conditional probability table (CPT) with 2^n^ entries specifying the probability of Y given the entire joint probability distribution over X, where n is the number of parents X.
 Given the exponential complexity of the CPT, simpler functions are often used to specify the probability of the child node, such as the noisy-or and noisy-and-not functions.
@@
 
+This gives us a formalism for representing relations within an intuitive theory.
+Now we need methods for estimating the relationship that are actually represented within people’s intuitive theories.
 Given measures of participants’ credences in each of the parent beliefs $x_i$ and the child belief $y$, we assume the following beta regression model:
 
-$$ \mu = \exp\Bigg(\ln\Big(1 - \exp\big(\ln\big(1-w_0) + \sum_i(1-w_i)x_i\big)\big) \Big) + \ln\Big(\sum_i(1-w_i)(1-x_i)\Big)\Bigg) $$
+$$\mu = \exp\Bigg(\ln\Big(1 - \exp\big(\ln\big(1-w_0) + \sum_i(1-w_i)x_i\big)\big) \Big) + \ln\Big(\sum_i(1-w_i)(1-x_i)\Big)\Bigg)$$
+
 $$y \sim beta\big(\mu k, (1-\mu)k\big)$$
@@
 Via maximum likelihood estimation, we estimate for each parent a discrete parameter $x_i$ determining whether the relationship is generative or preventive, and a continuous weight $w_i$ determining its strength.
-We also estimate $w_0$, the “leak probability” which is assumed to be generative, and _k_, a measure of dispersion in the responses _y_.
+We also estimate $w_0$, the “leak probability” which is assumed to be generative, and $k$, a measure of dispersion in the responses $y$.
 
@@
 
+Where the structure of an intuitive theory is known, Bayesian networks offer powerful tools for predicting and understanding how evidence will affect people's beliefs.
+However, there are many cases where the structure of the intuitive theory is unknown and is itself the very question under investigation.
+
+Fortunately, the formalism of Bayesian Networks provides tools for navigating these challenges.
+Here, we used Bayesian network structure learning algorithms to construct a model of the intuitive theory of vaccine decisions (see Scutari & Denis, 2021).
 One way to learn a Bayesian network structure from data is to search through a space of networks, “score” each and choose the best scoring network.
@@
 
-Which we estimate using the maximum log-likelihood estimated for our statistical model, calculated as the sum of the maximum log-likelihood for each node given its parents, from a total of _k_ parameters and _n_ data points.
+Which we estimate using the maximum log-likelihood estimated for our statistical model, calculated as the sum of the maximum log-likelihood for each node given its parents, from a total of $k$ parameters and $n$ data points.
 
@@
 For instance, that there is no edge from vaccine intentions to naturalism.
-This constraint can be thought of as a strong prior over the possible structures of this intuitive theory (namely, P(G)=0 for any graph G not respecting the principle).
+This constraint can be thought of as a strong prior over the possible structures of this intuitive theory (namely, $P(G)=0$ for any graph $G$ not respecting the principle).
 
@@
 To conduct an efficient search through the super-exponential space of DAGs, we tested several variants of two structure learning algorithms implemented in the “bnlearn” R package.
-The first is purely score-based “hill-climbing” algorithm (cite) and the second was a hybrid algorithm that combined the hill-climbing algorithm with a prior “restriction” phase that pruned down the space of DAGs.
+The first is a purely score-based “hill-climbing” algorithm (cite) and the second was a hybrid algorithm that combined the hill-climbing algorithm with a prior “restriction” phase that pruned down the space of DAGs.
 This pruning was accomplished with the “min-max parents and children” algorithm (cite), which can be tuned with a hyperparameter alpha, which we tested at several levels.
@@
 library(HydeNet)
+library(parallel)
 
@@
 
-```{r fit_all_models, include=FALSE}
-
-# hc_args <- list(score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000)
-# 
-# models <- list(
-#   hc = partial(hc, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
-#   hc_intentdv = partial(hc, blacklist=intent_dv_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
-#   hc_theory = partial(hc, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1000),
-#   mmhc_05 = partial(mmhc, restrict.args=list(alpha=.05), maximize.args = hc_args),
-#   mmhc_01 = partial(mmhc, restrict.args=list(alpha=.01), maximize.args = hc_args),
-#   mmhc_intentdv_05 = partial(mmhc, blacklist = intent_dv_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
-#   mmhc_intentdv_01 = partial(mmhc, blacklist = intent_dv_bl, restrict.args=list(alpha=.01), maximize.args = hc_args),
-#   mmhc_theory_05 = partial(mmhc, blacklist = theory_bl, restrict.args=list(alpha=.05), maximize.args = hc_args),
-#   mmhc_theory_01 = partial(mmhc, blacklist = theory_bl, restrict.args=list(alpha=.01), maximize.args = hc_args)
-# )
-# 
-# models <- mclapply(
-#     models, 
-#     function(f){f(train)}, 
-#     mc.cores = detectCores(logical=TRUE)
-#   )
-# 
-# arc_counts <- map(models, ~nrow(arcs(.x)))
-# arc_counts
-```
-
 Nevertheless, there were substantial differences among the approaches, especially from the application of different constraints through blacklists.
@@
 Without any clear guidance from cross validation and with a clear need to apply top-down constraints, we elected to advance our modeling with a model learned with the hill-climbing algorithm and our generative model constraints.
-This model contained more arcs than models estimated with hybrid algorithms, because these hybrid algorithms include a restriction phase based on correlations rather than our statistical model, we preferred the unrestricted approach.
+This model contained more arcs than models estimated with hybrid algorithms, but because these hybrid algorithms include a restriction phase based on correlations rather than our statistical model, we preferred the unrestricted approach.
 
@@
 
-We used a bootstrapping procedure to estimate the confidence in each of the links in this model, conducting the structure learning procedure repeatedly for N bootstrapped resamples of the original training data.
+We used a bootstrapping procedure to estimate the confidence in each of the links in this model, conducting the structure learning procedure repeatedly for 200 bootstrapped resamples of the original training data.
 Figure X visualizes the frequency with which each arc appeared in the resulting model across these replicates, and figure x visualizes the model with the coefficients for each link encoded by color.
-[interpret the models]
 
@@
 
-```{r}
-## explore cpdag
-
-main_cpdag <- cpdag(main_model)
-
-# do plotting -- will likely see lots of ambiguity??
-plot(main_cpdag)
-
-# CPDAG edge directions ruled out by blacklist (10)
-ruled_out <- inner_join(as.data.frame(undirected.arcs(main_cpdag)), as.data.frame(theory_bl), by=c("from","to"))
-
-# leaves 5 arcs that are unconstrained by both data and theory
-uncompelled_edges <- anti_join(as.data.frame(undirected.arcs(main_cpdag)), (ruled_out %>% bind_rows(ruled_out %>% rename(to="from", from="to")) ), by = c("from", "to"))
-
-# most substantive are vaccTox <--> vaccDanger, vaccEff
-```
+Though we found the uncovered network structure to be quite revealing and informative, there are also some important limitations that should be acknowledged.
+In particular, the edges from the vaccine danger and vaccine effectiveness nodes to the vaccine toxicity node strike us as counterintuitive.
+Intuitively, we might imagine that vaccines having toxins could cause them to be dangerous and ineffective.
+Yet the edges in the model run from in the opposite direction, and so do not support a clear causal interpretation.
+
+We can examine the robustness of the model’s features in two ways.
+First, we can ask about the “skeleton” of the graphical model: whether the relationships between pairs of nodes are robust, irrespective of their directions.
+To test this, we applied our chosen structure learning algorithm against 1000 bootstrapped replicates of our data (following Friedman et al., 2013).
+As shown in figure X, we have a high degree of confidence in the “skeleton” of the graph: nodes which are connected in the final graph are reliably connected across bootstrapping runs.
 
@@
 
+```
+
+```{r, echo=F}
+## examine bootstrapping results
+
+## which arcs are most likely?
+boot_res %>% 
+  filter(strength > .80, direction > .5)
+
+## what is strength of each arc in final graph?
+bnlearn_to_df(main_model) %>% 
+  left_join(boot_res, by=c("from","to"))  %>% 
+  filter(strength > .80)
 ```
@@
 Only edges appearing in at least 20\\% of graphs are shown."}
-
-hyde_str <- df_to_hyde_string(boot_res %>% filter(strength>.2, direction>0) %>% select(from,to))
-h2 <- HydeNetwork(as.formula(hyde_str))
-# plot(h2)
-
-z2 <- custom_plot.HydeNetwork(h2)
-boot_res %>%
-  filter(direction>0, strength>.2) %>% 
-  # filter(parameter!="phi",parameter!="w_leak") %>%
-  # rename(from = parameter) %>%
-  # mutate(from = gsub("w_","",from)) %>%
-  mutate(strength = strength*direction) %>% 
-  select(to, from, strength) %>%
-  merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
-  mutate(from = id) %>%
-  select(-id) %>%
-  merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
-  mutate(to = id) %>%
-  arrange(to,from) -> edge_df_mod
-
-# z$nodes_df
-z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
-z2$nodes_df$fontname <- "Helvetica"
-z2$nodes_df$shape <- "ellipse"
-# z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$id==13, "grey","white")
-z2$nodes_df$fixedsize <- FALSE
-z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
-z2$edges_df$penwidth <- 2
-# z$edges_df$label <- round(edge_df_mod$value,2)
-# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
-z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
-# z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
-
-render_graph(z2)
-```
-
-```{r}
-boot_graph_legend <- (tibble(
-  Probability = seq(min(edge_df_mod$strength), max(edge_df_mod$strength), length=11),
-) %>% 
-  ggplot(aes(y=1, x = Probability, fill = Probability)) +
-  geom_tile() +
-  scale_fill_distiller(palette="RdPu", direction=1)
-) %>% 
-  cowplot::get_legend()
-
-cowplot::ggdraw(boot_graph_legend)
-```
+# 
+# hyde_str <- df_to_hyde_string(boot_res %>% filter(strength>.2, direction>0) %>% select(from,to))
+# h2 <- HydeNetwork(as.formula(hyde_str))
+# # plot(h2)
+# 
+# z2 <- custom_plot.HydeNetwork(h2)
+# boot_res %>%
+#   filter(direction>0, strength>.2) %>% 
+#   # filter(parameter!="phi",parameter!="w_leak") %>%
+#   # rename(from = parameter) %>%
+#   # mutate(from = gsub("w_","",from)) %>%
+#   mutate(strength = strength*direction) %>% 
+#   select(to, from, strength) %>%
+#   merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
+#   mutate(from = id) %>%
+#   select(-id) %>%
+#   merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
+#   mutate(to = id) %>%
+#   arrange(to,from) -> edge_df_mod
+# 
+# 
+# # z$nodes_df
+# z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
+# z2$nodes_df$fontname <- "Helvetica"
+# z2$nodes_df$shape <- "ellipse"
+# # z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$id==13, "grey","white")
+# z2$nodes_df$fixedsize <- FALSE
+# z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
+# z2$edges_df$penwidth <- 2
+# # z$edges_df$label <- round(edge_df_mod$value,2)
+# # z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
+# z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
+# # z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
+# 
+# render_graph(z2)
+```
+
+```{r, echo=F, warning=F, message=F}
+# boot_graph_legend <- (tibble(
+#   Probability = seq(min(edge_df_mod$strength), max(edge_df_mod$strength), length=11),
+# ) %>% 
+#   ggplot(aes(y=1, x = Probability, fill = Probability)) +
+#   geom_tile() +
+#   scale_fill_distiller(palette="RdPu", direction=1)
+# ) %>% 
+#   cowplot::get_legend()
+# 
+# cowplot::ggdraw(boot_graph_legend)
+```
+
+Next, we can ask about the directions of the relationships within the model by examining the “completed partially directed acyclic graph” (CPDAG) derived from the structure learning algorithm.
+This is a graph with both directed and undirected edges which represents the “Markov equivalence class” of DAGs: the set of DAGs representing equivalent patterns of conditional (in)dependence among variables.
+Alternatively, this can be conceived of as “score equivalence,” the set of graphs which would produce equivalent scores for the observed data (Chickering, 2013).
+The CPDAG derived from our fit model contains 14 directed edges and 15 undirected arcs—indicating that the data do not constrain the directions of 15 of the edges in the final model.
+Of these undirected arcs, 10 directions are determined by our generative model constraints that we applied before fitting the model.
+Five arcs were determined neither by these constraints nor the data: these were $\text{holistic balance} \leftrightarrow \text{naturalism}$; $\text{medical skepticism} \leftrightarrow  \text{parental expertise}$, $\text{vaccine toxicity} \leftrightarrow \text{vaccine efficacy}$, $\text{vaccine toxicity} \leftrightarrow \text{vaccine danger}$ and $\text{vaccine danger} \leftrightarrow \text{vaccine efficacy}$.
+Thus, we feel that no strong conclusions should be drawn surrounding the counterintuitive relationships regarding vaccine toxicity, danger, and effectiveness.
 
 ```{r, include=F}
+## explore cpdag
+
+main_cpdag <- cpdag(main_model)
+
+# do plotting -- will likely see lots of ambiguity??
+plot(main_cpdag)
+
+# CPDAG edge directions ruled out by blacklist (10)
+ruled_out <- inner_join(as.data.frame(undirected.arcs(main_cpdag)), as.data.frame(theory_bl), by=c("from","to"))
+
+# leaves 5 arcs that are unconstrained by both data and theory
+uncompelled_edges <- anti_join(as.data.frame(undirected.arcs(main_cpdag)), (ruled_out %>% bind_rows(ruled_out %>% rename(to="from", from="to")) ), by = c("from", "to"))
+
+# most substantive are vaccTox <--> vaccDanger, vaccEff
+```
+
+```{r, include=F}
 
@@
 c <- find_dag_coefs(main_model, train)
-```
-
-```{r}
-boot_df <- boot_res %>% filter(strength>.2, direction>0)
 ```
@@
 
+## export graph code as txt
+graph_text <- DiagrammeR::generate_dot(z)
+write_file(graph_text, "graph-dot-code.txt")
+
+# export graph image and render
 export_graph(z, "../local/main-graph.pdf")
 render_graph(z)
-
-```
-```{r}
-coefs %>%
-  filter(parameter!="phi",parameter!="w_leak") %>%
-  rename(from = parameter) %>%
-  mutate(from = gsub("w_","",from)) %>%
-  select(to, from, value) %>%
-  merge(z$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
-  # mutate(from = id) %>%
-  rename(from_id = id) %>% 
-  merge(z$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
-  rename(to_id = id) %>%
-  arrange(to_id,from_id)
-```
-
-```{r}
+```
+
+```{r, echo=F, warning=F, message=F}
 ## NOTE: I just can't figure out how to nicely display the graph and legend in code
@@
 ```
+
+Altogether, these findings might be seen as demonstrating the need for a heavier hand in establishing top-down constraints on the model fitting.
+Certainly, they call for caution in interpreting the relationships represented in this model.
+Due to their tight connections with structural causal networks, it is tempting to interpret the edges in Bayesian networks as “causal”.
+However, these relationships are best thought of simply as probabilistic dependencies or “influence” relations (cite).
+Indeed, there are other cases where it is unclear if an edge should be directed at all: e.g., it is not obvious to us what would be the “correct” direction for the edge between naturalism and holistic balance.
+We might even speculate there is an additional unmeasured variable that connects these beliefs and that would best account for their association.
+Ultimately, this model should be understood as offering a plausible, but not definitive, account for a cognitive model connecting these different beliefs.
+
+What does the resulting model reveal about the intuitive theory undergirding vaccination decisions?
+
+The three nodes with direct connections to _vaccine intentions_ are beliefs about _vaccine effectiveness_, _vaccine danger_, and the severity of childhood diseases (_disease severity_)--concrete beliefs that are, at face value, especially closely related to vaccination decisions.
+The directionality of these edges is informed by the constraints we applied via the generative model principle, but the identification of these three factors as the most proximal to vaccine intentions is a product of the structure learning approach.
+This gives us some confidence that the model is capturing important relationships.
+
+Other parts of the model shed new light on the role of lay theories in vaccine decisions.
+For example, _naturalism_—the general view that natural things are better than artificial things—appears to be strongly related to _medical skepticism_ and _parental expertise_; all three of these abstract beliefs are related to concrete beliefs that, in turn, feed into participants’ vaccination intentions.
+This hierarchical structure is at least partly a product of our constraints that sorted these beliefs into “tiers” of abstractness.
+However, the [fact that a model with these constraints still functions well for prediction demonstrates that this hierarchical structure is plausible].
+
+Finally, this model structure also helps explain some initially surprising findings.
+For example, before collecting these data we speculated that dispelling the misconceptions about the capacity of the infant immune system could promote positive attitudes toward vaccination.
+We were disappointed to observe the weak first-order correlation between this belief and vaccine intentions in our behavioral data (r = -.097 in our training split).
+The model sheds light on this surprising (lack of) relationship: Although the belief that the infant immune system is limited in capacity is positively related to the belief that vaccines strain the immune system—discouraging vaccination, as we had assumed—it also seems to promote the belief that childhood diseases have severe consequences for young children (_disease severity_), which might, in turn, encourage vaccination.
+These countervailing forces—which, on average, seem to have cancelled each other out in this sample—dissuaded us from our plans to develop an intervention aimed at dispelling misconceptions about limited capacity in order to encourage childhood vaccination.
 
@@
 ```
-For each node, we also compared the Bayesian network model’s predictions to a maximal naive model using values on all other belief scales as predictors.
-This captures the degree to which each belief is predictable from the others as a whole.
+For each node, we also compared the Bayesian network model’s predictions to a naive “maximal” model using values on all other belief scales as predictors.
+Our intention was to capture the degree to which each belief is predictable from the others as a whole.
 As shown in table X, the relatively simpler Bayesian network model does not sacrifice any predictive power compared to the suite of maximal naive models.
@@
 ```
-
 ## Estimating the strength of evidence from changes in belief reports
 
+Returning to the DAG shown in Figure 1 above, consider the subgraph $FIRE \rightarrow SMOKE$, capturing the fact that fire causes smoke.
+This relationship is represented as a probabilistic function, where the probability of SMOKE depends on the probability of FIRE.
+If we observe the presence of SMOKE, we can draw inferences about FIRE.
+
+However, sometimes reasoners have only indirect evidence at their disposal.
+For instance, a person might not directly observe smoke, but instead hear from a witness who claimed to have seen it.
+Indirect or partial observations can be captured by augmenting the network, creating the graph $FIRE \rightarrow SMOKE \rightarrow WITNESS$.
+Here, a new node WITNESS represents another person’s testimony that they saw smoke, providing imperfect evidence for SMOKE, encoded by another probabilistic function.
+Observing WITNESS informs beliefs about SMOKE, in turn informing beliefs about FIRE.
+This approach to representing uncertain evidence is known as “virtual evidence” (Pearl, 1988).
+
 To model the effects of participants observing evidence, we augmented the Bayesian network representing the cognitive model (shown in figure #) with an additional node representing the evidence.
-For instance, to model the effects of the “disease risk” intervention (Study 2), we added an evidence node as a child of “disease severity,” acting as virtual evidence for this node (following Pearl, 1988).
+For instance, to model the effects of the “disease risk” intervention (Study 2), we added an evidence node as a child of “disease severity,” acting as virtual evidence for this node.
 To compute the CPT for this node as a function of disease severity beliefs, we estimated an _evidence ratio_ based on participants’ pretest and posttest credences in disease severity.
@@
 
-$$ ln\big(O(h|d)\big) = ln \big(O(h)\big) + ln\Bigg(\frac{P(d|h=1)}{P(d|h=0)}\Bigg) $$
+$$ log\big(O(h|d)\big) = log\big(O(h)\big) + ln\Big(\frac{P(d|h=1)}{P(d|h=0)}\Big) $$
 
@@
 
-The evidence ratio can be estimated from a model that is linear in the log-odds. This allowed for estimation of the evidence ratio from the with the following beta-regression model:
+The evidence ratio can be estimated from a model that is linear in the log-odds. This allows for estimation of the evidence ratio from the with the following beta-regression model:
 
 $$logit(\mu) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})$$
+
 $$y \sim beta\big(\mu k, (1-\mu)k\big)$$
@@
 $$ p(evidence = 1 | x ) = .50*ER_1$$
+
 $$ p(evidence = 0 | x) = .50. $$
@@
 
-## Qualitative Studies
+## Qualitative Study
 
@@
 
-To do this, we drew on a variety of sources, including academic articles on anti-vaccine skepticism (e.g., CITE) and anti-vaccine websites, and a qualitative survey with self-identified vaccine skeptics (_n_=16) via Amazon Mechanical Turk (MTurk).
-[add details of this study here]
-
-Ultimately, we generated a list of 13 underlying beliefs that might influence people’s decisions about whether to vaccinate their children (_vaccine intentions_, the last of our 14 beliefs).
-We translated these qualitative insights into 14 psychometrically-valid scales.
-In developing these scales, we stipulated that each scale should be brief, composed of 4-6 statements for participants to evaluate; include at least one reverse-coded item; and be highly reliable (Cronbach’s α ≥ .80).
-After extensive piloting and refinement, we created 14 scales that met these criteria, including one preexisting scale (the “holistic balance” subscale from McFadden et al., 2010).
+To do this, we drew on a variety of sources, including a qualitative survey with participants in a previous study who had self-identified as vaccine skeptics.
+Out of 23 people invited to participate, n=16 participants completed the survey via Amazon Mechanical Turk (MTurk).
+All participants answered “yes” to the question “Are you concerned that childhood vaccinations might cause serious side-effects?” When asked, “Do you have concerns about all vaccines or only some specific vaccines?” nearly all participants (14 of 16) expressed being concerned about specific vaccines; 3 of these participants, as well as the remaining 2 participants, expressed concern about all vaccines.
+
+The remainder of the survey was devoted to open-ended questions, which we will summarize here as they were a major source of inspiration for the development of the 14 “belief scales” employed in Studies 1-4.
+
+When asked about the potential side effects of vaccines, most participants (10 of 16) mentioned autism as a potential side effect; some mentioned other serious medical issues (e.g., stunting, cancer; 8 out 16); temporary, less serious physical symptoms (e.g., fever, headache; 7 of 16); other cognitive impairments and developmental disorders (e.g., learning disabilities, loss of speech; 6 of 16), and risk of death (6 of 16).
+Interestingly, 2 participants (of 16) specifically discussed the possibility that vaccines might have negative impacts on a child’s immune system; for example, one wrote that a vaccine “penetrates and actually weakens the immune system overall (despite increasing immunity to specific sicknesses).” In explaining _how_ vaccines might cause these side effects, many participants (9 of 15; 1 participant did not provide explanations) expressed concern that children’s bodies and immune systems may be too weak or underdeveloped to tolerate vaccines (e.g., “The vaccines are given to the children when they are babies and their brains have not begun development”; “Too many are given all at once at too young an age”; “They overwhelm the child's nervous system”).
+Several participants (5 of 15) mentioned the presence of specific toxic additives in vaccines (e.g., “high levels of heavy metal, especially mercury”), or invoked the idea that vaccines are generally unnatural (e.g., “Vaccines are unnatural additions to the body.
+The human body should naturally fight off the disease and we should not be controlling how nature plays its role on mankind”; “These vaccines are simply chemicals that should not play a role in a young naturally developing child”).
+Several participants (4 of 15) expressed concern that individual differences across children might render some children particularly vulnerable to these side effects (e.g., “The vaccine itself could interact with the specific child in a way that is unique and unforeseen”; “Sorry, I don't know the EXACT cause of it.
+I just think it has to do with the child's body being able to take the vaccine or not”).
+Individual participants also related personal stories of neighbors and friends, mentioned their mistrust of the government, or mentioned that the side effects of vaccines are worse than the symptoms of the diseases they are intended to prevent.
+
+When asked whether vaccines were effective in preventing the diseases they were designed to prevent, participants were evenly split (8 said “yes” and 8 said “no”) -- but in both groups, participants’ open-ended explanations touched on a common set of caveats and concerns.
+For example, some participants (7 of 15; 1 participant did not provide explanations) indicated that some vaccines are effective, at least for some individuals, but other vaccines are not (e.g., “Some work for some people, some don't”).
+Several participants (5 of 15) indicated that, regardless of efficacy, vaccines are no longer necessary because the diseases they prevent are no longer prevalent (e.g., “In certain circumstances they are, but in many cases the disease isn't really much of a risk so it doesn't make sense to fill the body with chemicals”; “I think that the potential of getting a disease is overblown and people get scared so they needlessly get vaccines”).
+Two (of 15) of participants mentioned that vaccines would be effective if they were given to children on a modified schedule (e.g., “Yes, if you give them ONE AT A TIME, spaced out over time and starting at older ages”); and two (of 15) related their personal mistrust of pharmaceutical companies (e.g., “THEY SEEMED TO BE A BIG MONEY MAKING SCAM BY THE BIG PHARMS”).
+(Individual participants related additional personal theories and concerns.)
+
+When asked whether it would be safer to vaccine a 2-month-old child for 5 separate diseases in one doctor’s visit (as the CDC recommends) or to spread these vaccinations out at a rate of 1 every 2 months, nearly all participants (15 of 16) said it would be safer to spread the vaccinations out.
+Many of these participants (8 of 15) indicated that this would be safer because it would prevent the  immature system from being overwhelmed (e.g., “It gives a [child’s] body time to adapt and doesn't overwhelm their tiny immune systems”); and several (4 of 15) suggested that this would be preferable because it would allow the parent more control over the process (e.g., “Ideally I would choose neither for my child, but if forced to choose between the two I would pick the latter.
+This would allow me to stop the vaccination process if things are not progressing well”; “I think a parent should have a choice which ones to have given to their child”).
+At least two participants expressed being deeply appalled by this choice, e.g., “He is only 8 weeks old.
+Who in their right mind decided it was safe to put 5 disease substances in a baby?
+Dead or alive, still horrific”; Honestly I do not think either is safe I think in both instances the child's body and health is actually being raped.”
+
+Finally, when asked why most healthcare providers recommend vaccinating young children, most participants (7 of 15; 1 participant did not respond) stated explicitly that healthcare providers have financial incentives to recommend vaccination -- but many (7 of 15, including several who mentioned financial incentives) also acknowledged that healthcare providers likely believe (in the participants’ view, mistakenly) that vaccinations are harmless and effective.
+Some participants (6 of 15) stated that healthcare providers are following protocol
+
+Drawing on these responses as well as anti-vaccine websites and academic articles on anti-vaccine skepticism (e.g., CITE), we generated a list of 13 underlying beliefs that might influence people’s decisions about whether to vaccinate their children (_vaccine intentions_, the last of our 14 beliefs).
+These included a variety of claims about vaccines, including beliefs about (1) the overall danger of vaccines (_vaccine danger_); (2) _toxic additives in vaccines_; and (3) _vaccine effectiveness_, how effective vaccines are in preventing disease; as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about (4) _disease rarity_ and (5) _disease severity_.
+Inspired by the many participants who invoked concerns about the effect of vaccines on infants’ immature immune systems, we also developed scales to assess beliefs that (6) the infant immune system is weak (_IIS: weakness_); (7) the infant immune system is limited in its capacity and can be easily overwhelmed (_IIS: limited capacity_); and (8) vaccines strain the infant immune system (_IIS: vaccines strain_).
+Beyond this, we developed two scales to assess general theories about parenting, including (9) general _parental protectiveness_; (10) _parental expertise_, namely the belief that parents usually know more about their children’s health than medical experts; and one scale to assess (12) _medical skepticism_, including concerns about pharmaceutical companies and corruption in the medical community.
+Finally, we decided to assess two broad worldviews: (12) _naturalism_, a general preference for natural over artificial things; and (13) _holistic balance_, one important aspect of attitudes toward alternative medicine (e.g., “The body is essentially self-healing and the task of a health care provider is to assist the healing process”; McFadden, Hernandez, & Ito, 2010).
+
+_Holistic balance_ was the only belief for which we could identify a pre-existing psychometrically valid scale (McFadden et al., 2010).
+For each of the other 13 beliefs, we translated our qualitative insights into new psychometrically-valid scales through an iterative series of pilot studies not described here.
+We stipulated that each scale should be brief, composed of 4-6 statements for participants to evaluate; include at least one reverse-coded item; and be highly reliable (Cronbach’s α ≥ .80).
 
@@
 
-### Method.
-
-Participants in all of these studies were asked to respond at least once to 14 belief scales measuring beliefs relevant to vaccination decisions (as previously described).
+_Method._ Participants in all of these studies were asked to respond at least once to 14 belief scales measuring beliefs relevant to vaccination decisions (as previously described).
 Across all studies, these scales were each presented on a separate survey page.
@@
 
-```{r s2_mean_diff_plot, echo=F, message=F, warning=F, fig.height=4, fig.width=6, fig.align='center', fig.cap="Mean difference scores from pretest to posttest for the 14 belief scales measured in Study 2.
-Error bars represent 95\\% confidence intervals."}
-
-# create plot of differences for all 14 scales
-# 
-# s2_scored %>% 
-#   spread(phase, mean) %>% 
-#   drop_na(scale) %>% 
-#   mutate(diff = post-pre) %>% 
-#   mutate(
-#     scale = recode_nodes2(scale),
-#     condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
-#     ) %>% 
-#   group_by(condition, scale) %>%
-#   summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
-#   ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
-#   geom_pointrange(position=position_dodge(width=.25)) +
-#   geom_hline(yintercept=0, linetype="dashed", color="grey") +
-#   theme_bw() +
-#   theme(
-#     axis.text.x = element_text(angle=45, hjust=1),
-#     panel.grid = element_blank()
-#     ) +
-#   labs(title="Study 2", y = "Mean difference", x = "Belief scale", color="Intervention")
-```
-
 ```{r s2_model, echo=FALSE, message=F, warning=F}
-# -- TODO: recode phase/condition 5/25/21, 11:07 AM
-
-# compare conditions on vaccIntent scale w/ regression model
-# probably do ordinal model with brms
+
 s2_reg <- s2_long %>% 
@@
 
-  kableExtra::kbl(table_df, digits = 2, booktabs = T, caption=caption) %>% 
+  kableExtra::kbl(table_df, digits = 2, booktabs = T, caption=caption, escape = T, format = "latex") %>% 
     kableExtra::kable_classic(full_width=F)
@@
 
-To model the changes in the belief network, we estimate the “evidence ratio” using the method described in the modeling section.
+To model the changes in the belief network, we estimate the “evidence ratio” using the method described in the modeling section above.
 The maximum likelihood estimate of the evidence ratio was XXX.
 To simulate the impacts of this evidence, we supplied virtual evidence to the disease severity node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
-
-Figure X shows the correlation between predicted and observed belief changes conditional on the disease risk intervention.
+Given that our cognitive model is parameterized via noisy-logical functions, the predicted influence of each belief is closely related to its first-order correlation.
+
+Figure X (right) shows the correlation between predicted and observed belief changes conditional on the disease risk intervention.
 
@@
 base_model <- create_bnlearn_cog_model(main_model, train)
-```
-
-```{r s2_model_pred, echo=FALSE, fig.height=4, fig.width=4, fig.align="center", fig.cap="Mean observed and predicted change scores for Experiment 2. Error bars represent 95\\% confidence intervals."}
-# Generate model predictions + create plot
-# odd, I remember the results being slightly better than this, job talk says r=.87
-# obs_pred <- make_pred_df(s2_mdf, base_model, "diseaseSevere")
-# 
-# cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
-# 
-# (obs_pred_plot <- obs_pred %>% # a bit of a hack
-#   ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
-#   geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
-#   geom_point(size=2.5) +
-#   geom_errorbar(alpha=.5, width=0) +
-#   annotate(geom="text", x=.03, y=-.04, label= paste("r =", cor_val)) +
-#   coord_cartesian(xlim=c(-.06,.06), ylim=c(-.06,.06)) +
-#   theme_bw(base_size=14) +
-#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-#   theme(aspect.ratio = 1)) +
-#   labs(title="Belief changes", subtitle="Experiment 2")
-
-# obs_pred %>%
-#   gather(type, Mean, observed, predicted) %>%
-#   ggplot(aes(y = reorder(scale, Mean), x = Mean, xmin = ll, xmax = ul, color=type)) +
-#   geom_point() +
-#   geom_errorbarh(height=0)
 ```
@@
 
-```{r echo=F, message=F, fig.align='center', fig.height=3, fig.width=3}
+In our paper, we laid out three qualitative features of intuitive theories.
+
+1) Where beliefs about two states of affairs, A and B, are related through a shared intuitive theory (e.g., A causes B), those beliefs will be systematically correlated across individuals (e.g., people who believe A will also tend to believe B);
+
+2) When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g., evidence for B will increase credence in A, and vice versa); and
+
+3) Following from the prior points, across individuals, the average change in one belief following evidence affecting another belief will be proportional to the correlation between those beliefs across individuals (evidence for B will increase credence in A in proportion to the correlation between beliefs A and B).
+
+By assuming that these beliefs are connected via an intuitive theory, we can infer how any given belief in the network will change in response to evidence targeting any other belief in the network.
+We used the cognitive model to predict how vaccination intentions would be influenced by an intervention targeting each of the 13 other beliefs in the network.
+Given that our cognitive model is parameterized via noisy-logical functions, the predicted influence of each belief is closely related to its first-order correlation.
+This captures qualitative Feature 3 of intuitive theories.
+Figure X presents these predictions, assuming the changes in beliefs are designed to move vaccine intentions in a positive direction (e.g.
+increasing “disease severity” beliefs but decreasing “vaccine danger” beliefs).
+
+```{r echo=F, message=F, fig.align='center', fig.height=3, fig.width=3, fig.cap="Predicted effects on Vaccine Intentions for hypothetical interventions targeting each of the 13 other beliefs"}
 
@@
 ```
+Guided by these predictions, we identified beliefs about toxins in vaccines as a potentially useful site of intervention--it is among the most strongly related and it is a concrete belief that could be addressed directly.
+We developed an educational intervention aimed at alleviating these concerns and tested its efficacy in two experiments.
 
@@
 
-We recruited `r s3_meta$n_recruited` people to participate in a two-day study via mTurk in April (Experiment 3A) and June (Experiment 3B) of 2018.
+We recruited `r s3_meta$n_recruited` people to participate in a two-day study via mTurk in April (Experiment 3A) and June (Experiment 3B) of 2019.
 One day after their initial participation, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r s3_meta$n_recruited_post` participants returning (`r s3_meta$n_eligible` invited, retaining `r round(s3_meta$n_recruited_post/s3_meta$n_eligible*100,1)`% of the Day 1 sample).
@@
 Full text of this intervention is available in appendix C of these supplementary materials.
-In study 3a, participants were randomly assigned to either a no-intervention control condition or to the novel vaccine toxins intervention.
-In study 3b, the no-intervention control condition was replaced with a brief control intervention [describing X].
+In both studies, participants were randomly assigned to either a no-intervention control condition or to the novel vaccine toxins intervention.
 
@@
 
-Due to the similarity of their designs, we combined data from studies 3a and 3b for analysis.
-As in study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine toxins intervention on participants’ Vaccination Intentions scores.
-The vaccine toxins intervention improved participant’s vaccination intention scores relative to the control conditions.
-However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions, suggesting that these attitudes were also being influenced by other factors during the course of the study.
-
-```{r, echo=FALSE, message=F, warning=F, fig.align="center", fig.cap = "Mean difference scores from pretest to posttest for the 14 belief scales measured in Experiment 3.
-Error bars represent 95\\% confidence intervals."}
-# create plot of differences for all 14 scales
-
-# s3_scored %>% 
-#   # spread(phase, mean) %>% 
-#   drop_na(scale) %>% 
-#   mutate(diff = post-pre) %>% 
-#   mutate(
-#     scale = recode_nodes2(scale),
-#     condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
-#     ) %>% 
-#   group_by(condition, scale) %>%
-#   summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
-#   ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
-#   geom_pointrange(position=position_dodge(width=.25)) +
-#   geom_hline(yintercept=0, linetype="dashed", color="grey") +
-#   theme_bw() +
-#   theme(
-#     axis.text.x = element_text(angle=45, hjust=1),
-#     panel.grid = element_blank()
-#     ) +
-#   labs(title="Study 3a and 3b", y = "Mean difference", x = "Belief scale", color="Intervention")
-
-```
+Due to the similarity of their designs, we combined data from studies 3a and 3b for our primary analysis.
+However, for full transparency we first describe analyses for these studies individually.
+As in Experiment 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine toxins intervention on participants’ _Vaccination Intentions_ scores.
+The vaccine toxins intervention improved participant’s vaccination intention scores relative to a no-intervention control condition.
+Tables X-X show the results of these regression analyses for Experiment 3a, 3b, and the two studies combined.
+In each analysis, the coefficient representing the interaction between phase and condition is positive and credibly differs from zero, indicating that the vaccine toxins intervention positively impacted vaccination intentions.
+
+However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions in both experiments (indicated by a credibly non-zero phase coefficient in each corresponding table).
+Observing this in Experiment 3a, we suspected that these attitudes were also being influenced by other factors during the course of the study.
+Approximately two months later we conducted Experiment 3b.
+However, we found similar patterns of changes in this later study as well.
+We now speculate that news of an ongoing measles outbreak at the time of these studies (Spring of 2019) may have influenced participants’ beliefs about vaccines, although it is not obvious what specific news stories could have caused these shifts from one day to the next.
 
@@
 
-```{r, echo=F, fig.width=4, fig.height=4, fig.align="center", fig.cap="Plots of belief changes following the intervention in Experiment 3.
-Left, mean difference scores from pretest to posttest for the 14 belief scales measured in Experiment 3.
-Mean observed and predicted change scores for Experiment 3.
-Error bars in both plots represent 95\\% confidence intervals.
-"}
-
-# this is not quite getting vacctox node right, could be because of effects in the control condition.
-
-# fit evidence node
-# obs_pred <- make_pred_df(s3_mdf, base_model, "vaccTox")
-# 
-# cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
-# 
-# (
-#   obs_pred_plot <- obs_pred %>% 
-#   ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
-#   geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
-#   geom_point(size=2.5) +
-#   geom_errorbar(alpha=.5, width=0) +
-#   # coord_fixed(ratio=1) +
-#   coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
-#   annotate(geom="text", x=.05, y=-.1, label= paste("r =", cor_val)) +
-#   theme_bw(base_size=14) +
-#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-#   theme(aspect.ratio = 1) +
-#   labs(title="Belief changes",subtitle="Experiment 3a & 3b")
-# )
-```
-
-```{r fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
+```{r echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
@@
 
-```{r s4_diff_plot, echo=FALSE, message=F, warning=F, fig.align='center', fig.cap="Mean difference scores from pretest to posttest for the 14 belief scales measured in Study 3.
-Thick error bars represent standard errors, thin error bars represent 95\\% confidence intervals."}
-# compare effects in graph
-
-# combined %>% 
-#   filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
-#   mutate(diff = posttest-pretest) %>%
-#   mutate(
-#     vacc_news = as.factor(vacc_news),
-#     scale = recode_nodes2(scale)
-#     ) %>%
-#   group_by(vacc_news,scale) %>%
-#   summarize(
-#     mean = mean(diff),
-#     se = sd(diff)/sqrt(n()),
-#     ul = mean + se,
-#     ll = mean - se,
-#     ul95 = mean + 1.96*se,
-#     ll95 = mean - 1.96*se
-#   ) %>%
-#   ungroup() %>%
-#   mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
-#   # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
-#   ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
-#   geom_point(position=position_dodge(width=.25), size=2, shape=16) +
-#   geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
-#   geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
-#   geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
-#   # facet_wrap(~scale, scales="free") +
-#   theme_bw(base_size = 12) +
-#   theme(
-#     axis.text.x = element_text(angle = 45, hjust = 1), 
-#     legend.position = "right",
-#     panel.grid = element_blank()) +
-#   labs(title="Study 4", y = "Change scores", x = "Belief scale", color ="News\nexposure")
-```
-
 ```{r, echo=FALSE, message=F, warning=F}
@@
 
-Mirroring our analyses of interventions, we regressed responses to the vaccine intentions scale items on predictors for phase (X 2017 vs.
-May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item.
+Mirroring our analyses of interventions, we regressed responses to the _vaccine intentions_ scale items on predictors for phase (pre-outbreak in August and September 2017 vs.
+post-outbreak May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item.
 To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure.
@@
 Figure X shows the correlation between predicted and observed belief changes for participants who were aware of the New York measles outbreak in May 2019.
-
-```{r, echo=FALSE, fig.height=4, fig.width=4, fig.align="center", fig.cap="Mean observed and predicted change scores for Experiment 2. Error bars represent 95\\% confidence intervals."}
-# fit evidence node -- do diagnosis w/ bootstrapping? or just assume vaccIntent? I think just assume
-# generate model predictions + create plot
-
-# obs_pred <- make_pred_df(s4_mdf, base_model, "vaccIntent")
-# 
-# cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
-# 
-# (obs_pred_plot <- obs_pred %>% # a bit of a hack
-#   ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
-#   geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
-#   geom_point(size=2.5) +
-#   geom_errorbar(alpha=.5, width=0) +
-#   annotate(geom="text", x=.04, y=-.04, label= paste("r =", cor_val)) +
-#   coord_cartesian(xlim=c(-.07,.06), ylim=c(-.07,.06)) +
-#   theme_bw(base_size=14) +
-#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
-#   theme(aspect.ratio = 1)) +
-#   labs(title="Belief changes",subtitle="Study 4 - vaccIntent")
-
-```
 
@@
 
+## export images of plots
+ggsave("../local/valid_plt.png", plt.valid, height=4, width=8)
+ggsave("../local/s2_plt.png", s2_plt, height=4, width=8)
+ggsave("../local/s3_plt.png", s3_plt, height=4, width=8)
+ggsave("../local/s4_plt.png", s4_plt, height=4, width=8)
+ggsave("../local/pred_change_plt.png", pred_change_plot, height=4, width=4)
+
 ## save numerical results

### 2021-06-22 supplement/supplement-main.Rmd
minor supplement edits
fixing cog model running

@@
 
+$$y \sim beta\big(\mu k, (1-\mu)k\big)$$
 $$\mu = \exp\Bigg(\ln\Big(1 - \exp\big(\ln\big(1-w_0) + \sum_i(1-w_i)x_i\big)\big) \Big) + \ln\Big(\sum_i(1-w_i)(1-x_i)\Big)\Bigg)$$
-
-$$y \sim beta\big(\mu k, (1-\mu)k\big)$$
 
@@
 
-## uncomment to re-run cross validation
-# source("../code/custom-structure-learning/fit-cog-models-bnlearn.R")
+if (!file.exists("../local/cv-res.rds")){
+  source("../code/custom-structure-learning/fit-cog-models-bnlearn.R", chdir=TRUE)
+}
 
@@
 
-```{r, echo=F}
+```{r, echo=F, include=F}
 ## examine bootstrapping results
@@
   left_join(boot_res, by=c("from","to"))  %>% 
-  filter(strength > .80)
+  filter(strength > .95)
 ```
@@
 
+$$y \sim beta\big(\mu k, (1-\mu)k\big)$$
 $$logit(\mu) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})$$
-
-$$y \sim beta\big(\mu k, (1-\mu)k\big)$$
 
@@
 $$ p(evidence = 1 | x ) = .50*ER_1$$ 
-
 $$ p(evidence = 0 | x) = .50. $$

### 2021-06-22 supplement/supplement-main.Rmd
minor graphing edits

@@
 
-```{r main_model_plot, echo=F, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
+```{r main_model_plot, echo=F, fig.width=8, fig.height=5, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
 Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links."}
 
-z <- custom_plot.HydeNetwork(h)
+z <- custom_plot.HydeNetwork(h, attr_theme="tb")
 
@@
 z$nodes_df$shape <- "ellipse"
-# z$nodes_df$fillcolor <- ifelse(z$nodes_df$id==13, "grey","white")
+z$nodes_df$fillcolor <- ifelse(z$nodes_df$id==11, "grey","white")
 z$nodes_df$fixedsize <- FALSE

### 2021-06-22 code/custom_plotting.R

@@ -32,7 +32,8 @@ custom_plot.HydeNetwork <- function(x,
   
   DiagrammeR::create_graph(nodes_df = node_df,
                            edges_df = edge_df,
-                           attr_theme = NULL)
+                           ...
+                           )
   
 }
 

### 2021-07-08 supplement/supplement-main.Rmd
supplement edits

@@
     train,  #train
-    R = 200,
+    R = 500,
     algorithm = "hc",
@@
 
-# do plotting -- will likely see lots of ambiguity??
+# there are 15 undirected edges, here's a plot 
 plot(main_cpdag)
 
-# CPDAG edge directions ruled out by blacklist (10)
+# CPDAG edge directions ruled out by blacklist (10 of 15)
 ruled_out <- inner_join(as.data.frame(undirected.arcs(main_cpdag)), as.data.frame(theory_bl), by=c("from","to"))
@@
 # most substantive are vaccTox <--> vaccDanger, vaccEff
+
+## can start setting these as makes sense theoretically
+my_model <- bnlearn::set.arc(main_model, "vaccTox", "vaccDanger", check.cycles=TRUE)
+# my_model <- set.arc(main_model, "vaccDanger", "vaccTox")
+my_model <- bnlearn::set.arc(my_model, "vaccTox", "vaccEff", check.cycles=TRUE)
+
+## setting those two compels edge for vaccine efficacy --> vaccine danger
+## leaves just HB--naturalism and medskept -- parental expertise undirected
+ruled_out <- inner_join(as.data.frame(undirected.arcs(cpdag(my_model))), as.data.frame(theory_bl), by=c("from","to"))
+
+anti_join(as.data.frame(undirected.arcs(cpdag(my_model))), (ruled_out %>% bind_rows(ruled_out %>% rename(to="from", from="to")) ), by = c("from", "to"))
 ```
@@
 
-## flag edges that could be flipped
+# flag edges that could be flipped
 edge_df_mod <- uncompelled_edges %>%
@@
 z$nodes_df$shape <- "ellipse"
-z$nodes_df$fillcolor <- ifelse(z$nodes_df$id==11, "grey","white")
+z$nodes_df$fillcolor <- ifelse(z$nodes_df$label=="Vaccination\nIntentions", "grey","white")
 z$nodes_df$fixedsize <- FALSE
@@
 # z$edges_df$label <- round(edge_df_mod$value,2)
-z$edges_df$label <- edge_df_mod$label
+# z$edges_df$label <- edge_df_mod$label
 # z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
@@
   drop_na(scale) %>% 
+  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
+  # group_by(scale) %>% 
+  # mutate(post = post/sd(post), pre = pre/sd(pre)) %>% 
   mutate(diff = post-pre) %>% 
@@
   drop_na(scale) %>% 
+  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
   mutate(diff = post-pre) %>% 
@@
   filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
+  mutate(posttest = rescale_beta(posttest, -3, 3), pretest = rescale_beta(pretest, -3, 3)) %>% 
   mutate(diff = posttest-pretest) %>%

### 2021-07-08 supplement/supplement-main.Rmd
added .rds outputs

@@
 
-if (!file.exists("../local/cv-res.rds")){
+if (!file.exists("../outputs/cv-res.rds")){
   source("../code/custom-structure-learning/fit-cog-models-bnlearn.R", chdir=TRUE)
-}
-
-cv_res <- readRDS("../local/cv-res.rds")
+} else {
+  cv_res <- readRDS("../outputs/cv-res.rds")
+}
 
@@
 #   mutate_all(~.x+rnorm(n(),0,.002))
-if (!file.exists("../local/boot_res.rds")){
+if (!file.exists("../outputs/boot-res.rds")){
   cl = parallel::makeCluster(detectCores(logical=TRUE))
@@
 
-  saveRDS(boot_res,"../local/boot_res.rds")
+  saveRDS(boot_res,"../outputs/boot-res.rds")
 } else {
-  boot_res <- readRDS("../local/boot_res.rds")
+  boot_res <- readRDS("../outputs/boot-res.rds")
 }

### 2021-07-12 supplement/supplement-main.Rmd
supplement fixes

@@
   cores = 6,
-  control = list(adapt_delta=.95),
+  control = list(adapt_delta=.99),
   seed = 46179,
@@
 
-  kableExtra::kbl(table_df, digits = 2, booktabs = T, caption=caption, escape = T, format = "latex") %>% 
+  kableExtra::kbl(table_df, digits = 2, booktabs = T, caption=caption, escape = F, format="latex") %>% 
     kableExtra::kable_classic(full_width=F)
@@
   make_table_df() %>% 
+  rename(`$CI_{2.5\\%}$` = `l-95% CI`,`$CI_{97.5\\%}$` = `u-95% CI`) %>% 
   mutate(
     Term = case_when(
-      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
-      #                                            gsub("(diseaseRisk|post)", "", Term),
-      #                                            "}$"),
+      grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta_{",
+                                                 gsub("(diseaseRisk|post)", "", Term),
+                                                 "}$"),
       grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
@@
   scale_color_manual(values=c("#0067b1","#c50024")) +
+  scale_shape_manual(values=c(17,16)) +
   theme_bw(base_size=11) +
@@
   make_table_df() %>% 
+  rename(`$CI_{2.5\\%}$` = `l-95% CI`,`$CI_{97.5\\%}$` = `u-95% CI`) %>% 
   mutate(
     Term = case_when(
-      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
-      #                                            gsub("(diseaseRisk|post)", "", Term),
-      #                                            "}$"),
+      grepl("(intervention|post)", Term) ~ paste0("$\\beta_{",
+                                                 gsub("(intervention|phase)", "", Term),
+                                                 "}$"),
       grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
@@
   cores = 6,
-  control = list(adapt_delta=.95),
+  control = list(adapt_delta=.99),
   seed = 69568,
@@
   cores = 6,
-  control = list(adapt_delta=.95),
+  control = list(adapt_delta=.99),
   seed = 40725,
@@
 make_table_df() %>% 
+  rename(`$CI_{2.5\\%}$` = `l-95% CI`,`$CI_{97.5\\%}$` = `u-95% CI`) %>% 
   mutate(
     Term = case_when(
-      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
-      #                                            gsub("(diseaseRisk|post)", "", Term),
-      #                                            "}$"),
+      grepl("(vacc_news|post)", Term) ~ paste0("$\\beta_{",
+                                                 gsub("(posttest)", "", Term),
+                                                 "}$"),
       grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
@@
       Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
-      TRUE ~ gsub("(intervention|posttest)","", Term)
+      TRUE ~ gsub("(posttest)","", Term)
     ),
@@
   scale_color_manual(values=c("#0067b1","grey")) +
+  # scale_shape_manual(values=c(17,16)) +
   theme_bw(base_size=11) +

### 2021-07-17 supplement/supplement-main.Rmd
supplement updates

@@
 author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
-date: "June 21, 2021 (DRAFT)"
+date: "Jul 17, 2021 (DRAFT)"
 output:
@@
     fig_caption: yes
+bibliography: references.bib
+csl: pnas.csl
 figsintext : yes
@@
 
-Figure 1 shows an example of a simple Bayesian Network.
+Figure \@ref(fig:dag-example) shows an example of a simple Bayesian Network.
 The network itself is a _directed acyclic graph_ (DAG), a type of graphical model.
@@
 
-```{r dag_example, echo=F, fig.align='center', out.width = '40%', fig.cap="Example DAG illustrating some variables related to wildfires."}
+```{r dag-example, echo=F, fig.align='center', out.width = '40%', fig.cap="Example DAG illustrating some variables related to wildfires."}
 
@@
 A noisy-and-not function assumes each of the parents are independent preventive forces, specifying the probability of the child node as the probability that it is generated _and not_ prevented by any one of its possible preventers.
-We construct our cognitive model parameterization using a combination of these two functions, using a distribution sometimes referred to as a “DeMorgan gate” (Maaskant & Druzdel, 2008).
+We construct our cognitive model parameterization using a combination of these two functions, using a distribution sometimes referred to as a “DeMorgan gate” [@maaskant.druzdzel2008].
 In our model, the probability of the child node Y can be expressed as:
@@
 A cognitive model composed of these types of relations is capable of capturing a causal system of non-interactive generative and preventive causes.
-Although people’s intuitive theories are likely more flexible than this, there is ample evidence that people are highly capable of reasoning according to these types of causal relationships (see Holyoak & Cheng, 2011 for a review), and moreover, that their causal learning is strongly biased toward learning these kinds of relations (e.g., Novick & Cheng, 2004).
+Although people’s intuitive theories are likely more flexible than this, there is ample evidence that people are highly capable of reasoning according to these types of causal relationships [see @holyoak.cheng2011 for a review], and moreover, that their causal learning is strongly biased toward learning these kinds of relations [e.g.
+@novick.cheng2004].
 
@@
 
-To conduct an efficient search through the super-exponential space of DAGs, we tested several variants of two structure learning algorithms implemented in the “bnlearn” R package.
-The first is a purely score-based “hill-climbing” algorithm (cite) and the second was a hybrid algorithm that combined the hill-climbing algorithm with a prior “restriction” phase that pruned down the space of DAGs.
-This pruning was accomplished with the “min-max parents and children” algorithm (cite), which can be tuned with a hyperparameter alpha, which we tested at several levels.
+To conduct an efficient search through the super-exponential space of DAGs, we tested several variants of two structure learning algorithms implemented in the “bnlearn” R package [@scutari2010a].
+The first is a purely score-based “hill-climbing” algorithm  and the second was a hybrid algorithm that combined the hill-climbing algorithm with a prior “restriction” phase that pruned down the space of DAGs.
+This pruning was accomplished with the “min-max parents and children” algorithm, which can be tuned with a hyperparameter alpha, which we tested at several levels.
 To speed computations, we restricted the maximum number of parents in the graph to five for all nodes, as the complexity of the scoring function is exponential in the number of parents.
@@
 
-Figure X presents the results of these cross validation tests.
+Figure \@ref(fig:cross-validation) presents the results of these cross validation tests.
 As seen in the figure, all structure learning approaches produced models with similar out-of-sample performance, with more variability among folds and runs than between algorithms.
@@
 
-```{r cross_validation, echo=FALSE, fig.align='center', fig.height=3, fig.width=4, fig.cap="Cross-validation performance for diffrent structure learning algorithms on the training data from Study 1."}
+```{r cross-validation, echo=FALSE, fig.align='center', fig.height=3, fig.width=4, fig.cap="Cross-validation performance for diffrent structure learning algorithms on the training data from Study 1."}
 
@@
 We used a bootstrapping procedure to estimate the confidence in each of the links in this model, conducting the structure learning procedure repeatedly for 200 bootstrapped resamples of the original training data.
-Figure X visualizes the frequency with which each arc appeared in the resulting model across these replicates, and figure x visualizes the model with the coefficients for each link encoded by color.
+Figure \@ref(fig:disp-bootgraph) visualizes the frequency with which each arc appeared in the resulting model across these replicates, and figure \@ref(fig:disp-maingraph) visualizes the model with the coefficients for each link encoded by color.
 
@@
 ```
-
-Though we found the uncovered network structure to be quite revealing and informative, there are also some important limitations that should be acknowledged.
-In particular, the edges from the vaccine danger and vaccine effectiveness nodes to the vaccine toxicity node strike us as counterintuitive.
-Intuitively, we might imagine that vaccines having toxins could cause them to be dangerous and ineffective.
-Yet the edges in the model run from in the opposite direction, and so do not support a clear causal interpretation.
-
-We can examine the robustness of the model’s features in two ways.
-First, we can ask about the “skeleton” of the graphical model: whether the relationships between pairs of nodes are robust, irrespective of their directions.
-To test this, we applied our chosen structure learning algorithm against 1000 bootstrapped replicates of our data (following Friedman et al., 2013).
-As shown in figure X, we have a high degree of confidence in the “skeleton” of the graph: nodes which are connected in the final graph are reliably connected across bootstrapping runs.
 
@@
 
-```{r boot_strength_plot, echo=F, message=F, fig.cap="Bootstrapped confidence estimates for Bayesian network edges.
-Edge color indicates frequency with which edges appeared when conducting search across X bootstrap replicates.
-Only edges appearing in at least 20\\% of graphs are shown."}
+```{r boot_strength_plot, include=F, fig.width=5, fig.height=8}
 # 
-# hyde_str <- df_to_hyde_string(boot_res %>% filter(strength>.2, direction>0) %>% select(from,to))
-# h2 <- HydeNetwork(as.formula(hyde_str))
-# # plot(h2)
-# 
-# z2 <- custom_plot.HydeNetwork(h2)
-# boot_res %>%
-#   filter(direction>0, strength>.2) %>% 
-#   # filter(parameter!="phi",parameter!="w_leak") %>%
-#   # rename(from = parameter) %>%
-#   # mutate(from = gsub("w_","",from)) %>%
-#   mutate(strength = strength*direction) %>% 
-#   select(to, from, strength) %>%
-#   merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
-#   mutate(from = id) %>%
-#   select(-id) %>%
-#   merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
-#   mutate(to = id) %>%
-#   arrange(to,from) -> edge_df_mod
-# 
-# 
-# # z$nodes_df
-# z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
-# z2$nodes_df$fontname <- "Helvetica"
-# z2$nodes_df$shape <- "ellipse"
-# # z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$id==13, "grey","white")
-# z2$nodes_df$fixedsize <- FALSE
-# z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
-# z2$edges_df$penwidth <- 2
-# # z$edges_df$label <- round(edge_df_mod$value,2)
-# # z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
-# z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
-# # z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
+hyde_str <- df_to_hyde_string(boot_res %>% filter(strength>.2, direction>0) %>% select(from,to))
+h2 <- HydeNetwork(as.formula(hyde_str))
+# plot(h2)
+
+z2 <- custom_plot.HydeNetwork(h2)
+
+boot_res %>%
+  filter(direction>0, strength>.2) %>%
+  # filter(parameter!="phi",parameter!="w_leak") %>%
+  # rename(from = parameter) %>%
+  # mutate(from = gsub("w_","",from)) %>%
+  mutate(strength = strength*direction) %>%
+  select(to, from, strength) %>%
+  merge(z2$nodes_df %>% rename(from = label) %>% select(id, from), by="from") %>%
+  mutate(from = id) %>%
+  select(-id) %>%
+  merge(z2$nodes_df %>% rename(to = label) %>% select(id, to), by="to") %>%
+  mutate(to = id) %>%
+  arrange(to,from) -> edge_df_mod
+
+# z$nodes_df
+z2$nodes_df <- z2$nodes_df %>% mutate(label = recode_nodes(label))
+z2$nodes_df$fontname <- "Helvetica"
+z2$nodes_df$shape <- "ellipse"
+z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$label=="Vaccination\nIntentions", "grey","white")
+z2$nodes_df$fixedsize <- FALSE
+z2$edges_df$penwidth <- abs(edge_df_mod$strength)*2
+z2$edges_df$penwidth <- 1.5
+# z$edges_df$label <- round(edge_df_mod$value,2)
+# z$edges_df$color <- ifelse(edge_df_mod$value > 0, "blue","red")
+z2$edges_df$color <- map_to_brewer(edge_df_mod$strength, bins=9, option="RdPu")
+# z2$edges_df$color <- map_to_viridis(edge_df_mod$strength, option="magma")
 # 
 # render_graph(z2)
-```
-
-```{r, echo=F, warning=F, message=F}
-# boot_graph_legend <- (tibble(
-#   Probability = seq(min(edge_df_mod$strength), max(edge_df_mod$strength), length=11),
-# ) %>% 
-#   ggplot(aes(y=1, x = Probability, fill = Probability)) +
-#   geom_tile() +
-#   scale_fill_distiller(palette="RdPu", direction=1)
-# ) %>% 
-#   cowplot::get_legend()
-# 
+
+export_graph(z2, "../local/boot-graph.pdf")
+```
+
+```{r, include=F}
+boot_graph_legend <- (tibble(
+  Probability = seq(min(edge_df_mod$strength), max(edge_df_mod$strength), length=11),
+) %>%
+  ggplot(aes(y=1, x = Probability, fill = Probability)) +
+  geom_tile() +
+  scale_fill_distiller(palette="RdPu", direction=1)
+) %>%
+  cowplot::get_legend()
+
+cowplot::save_plot("../local/boot-graph-legend.svg", boot_graph_legend)
 # cowplot::ggdraw(boot_graph_legend)
@@
 
-Next, we can ask about the directions of the relationships within the model by examining the “completed partially directed acyclic graph” (CPDAG) derived from the structure learning algorithm.
-This is a graph with both directed and undirected edges which represents the “Markov equivalence class” of DAGs: the set of DAGs representing equivalent patterns of conditional (in)dependence among variables.
-Alternatively, this can be conceived of as “score equivalence,” the set of graphs which would produce equivalent scores for the observed data (Chickering, 2013).
-The CPDAG derived from our fit model contains 14 directed edges and 15 undirected arcs—indicating that the data do not constrain the directions of 15 of the edges in the final model.
-Of these undirected arcs, 10 directions are determined by our generative model constraints that we applied before fitting the model.
-Five arcs were determined neither by these constraints nor the data: these were $\text{holistic balance} \leftrightarrow \text{naturalism}$; $\text{medical skepticism} \leftrightarrow  \text{parental expertise}$, $\text{vaccine toxicity} \leftrightarrow \text{vaccine efficacy}$, $\text{vaccine toxicity} \leftrightarrow \text{vaccine danger}$ and $\text{vaccine danger} \leftrightarrow \text{vaccine efficacy}$.
-Thus, we feel that no strong conclusions should be drawn surrounding the counterintuitive relationships regarding vaccine toxicity, danger, and effectiveness.
+```{r disp-bootgraph, echo=F, fig.width=8, fig.height=5, fig.cap="Bootstrapped confidence estimates for Bayesian network edges.
+Edge color indicates frequency with which edges appeared when conducting search across 200 bootstrap replicates.
+Only edges appearing in at least 20\\% of graphs are shown."}
+
+## assemble bootstrapping graph and legend into pdf and display here
+knitr::include_graphics("../local/boot-graph.pdf") 
+```
+
+Though we found the uncovered network structure to be quite revealing and informative, there are also some important limitations that should be acknowledged.
+In particular, the edges from the vaccine danger and vaccine effectiveness nodes to the vaccine toxicity node strike us as counterintuitive.
+Intuitively, we might imagine that vaccines having toxins could cause them to be dangerous and ineffective.
+Yet the edges in the model run from in the opposite direction, and so do not support a clear causal interpretation.
+
+A Bayesian network is a factorized representation of a probability distribution and any given network is a member of a "Markov equivalence class"—a set of networks capable of factorizing the same distribution.
+This set of DAGs can be represented as a "completed partially directed acyclic graph" (CPDAG), a graph with both directed and undirected edges.
+The equivalence class for our model can be represented as a CPDAG with 14 directed edges and 15 undirected edges—indicating that the data do not constrain the directions of 15 of the edges in the final model.
+However, 10 of these edges’ directions are directly constrained by our top-down "generative model" constraints, which in turn constrains all but two of the remaining undirected edges, including the counterintuitive edges running toward vaccine toxins.
+This is also reflected in a bootstrapping analysis applying our chosen structure learning algorithm against 1000 bootstrapped replicates of our data.
+We found that the direction of some edges within the graph differed across bootstrapped runs (Holistic balance -- naturalism, medical skepticism -- parental expertise), but that these unintuitive relationships surrounding vaccine toxins were robust.
+
+Altogether, these findings might be seen as demonstrating the need for a heavier hand in establishing top-down constraints on the model fitting.
+Certainly, they call for caution in interpreting the relationships represented in this model.
+Due to their tight connections with structural causal networks, it is tempting to interpret the edges in Bayesian networks as “causal.” However, these relationships are best thought of as probabilistic dependencies or “influence” relations (Williamson, 2001).
+Indeed, there are other cases where it is unclear if an edge should be directed at all: e.g., it is not obvious to us what would be the “correct” direction for the edge between naturalism and holistic balance.
+We might even speculate there is an additional unmeasured variable that connects these beliefs and that would best account for their association.
+Ultimately, this model should be understood as offering a plausible, but not definitive, account for a cognitive model connecting these different beliefs.
 
@@
 
+What does the resulting model reveal about the intuitive theory undergirding vaccination decisions?
+
+The three nodes with direct connections to _vaccine intentions_ are beliefs about _vaccine effectiveness_, _vaccine danger_, and the severity of childhood diseases (_disease severity_)---concrete beliefs that are, at face value, especially closely related to vaccination decisions.
+The directionality of these edges is informed by the constraints we applied via the generative model principle, but the identification of these three factors as the most proximal to vaccine intentions is a product of the structure learning approach.
+This gives us some confidence that the model is capturing important relationships.
+
+Other parts of the model shed new light on the role of lay theories in vaccine decisions.
+For example, _naturalism_—--the general view that natural things are better than artificial things—appears to be strongly related to _medical skepticism_ and _parental expertise_; all three of these abstract beliefs are related to concrete beliefs that, in turn, feed into participants’ vaccination intentions.
+This hierarchical structure is at least partly a product of our constraints that sorted these beliefs into “tiers” of abstractness.
+However, the fact that a model with these constraints still functions well for prediction demonstrates that this hierarchical structure is plausible.
+
+Finally, this model structure also helps explain some initially surprising findings.
+For example, before collecting these data we speculated that dispelling the misconceptions about the capacity of the infant immune system could promote positive attitudes toward vaccination.
+We were disappointed to observe the weak first-order correlation between this belief and vaccine intentions in our behavioral data ($r$ = -.09 in our training split).
+The model sheds light on this surprising (lack of) relationship: Although the belief that the infant immune system is limited in capacity is positively related to the belief that vaccines strain the immune system—discouraging vaccination, as we had assumed—it also seems to promote the belief that childhood diseases have severe consequences for young children (_disease severity_), which might, in turn, encourage vaccination.
+These countervailing forces—which, on average, seem to have canceled each other out in this sample—dissuaded us from our plans to develop an intervention aimed at dispelling misconceptions about limited capacity in order to encourage childhood vaccination.
+
 ```{r, include=F}
@@
 
-```{r main_model_plot, echo=F, fig.width=8, fig.height=5, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
-Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links."}
+```{r main_model_plot, include=F}
 
@@
 
-# export graph image and render
+# export graph image
 export_graph(z, "../local/main-graph.pdf")
-render_graph(z)
-```
-
-```{r, echo=F, warning=F, message=F}
+# render_graph(z)
+```
+
+```{r, include=F}
 ## NOTE: I just can't figure out how to nicely display the graph and legend in code
@@
 cowplot::save_plot("../local/graph-legend.svg", main_graph_legend)
-cowplot::ggdraw(main_graph_legend)
-
+# cowplot::ggdraw(main_graph_legend)
+
+```
+
+```{r disp-maingraph, echo=F, fig.width=8, fig.height=5, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
+Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links."}
+
+## assemble main model graph and legend into pdf and display here (main-graph-combined.pdf)
+## currently just the output graph w/ no legend (main-graph.pdf)
+knitr::include_graphics("../local/main-graph.pdf") 
 ```
@@
 
-Finally, we can also compare the quality of our model predictions to the test-retest reliability of the belief scales, establishing an overall upper-bound on the predictability of these measures.
-As shown in table X, the Bayesian network model did approximately as well as possible for seven beliefs, but fell short for the other seven.
+Finally, we can also compare the quality of our model predictions to the test-retest reliability of the belief scales (estimated from the pre-test and post-test measures in the control condition of Study 2), establishing an overall upper-bound on the predictability of these measures.
+As shown in Table \@ref(tab:model_valid_table), the Bayesian network model did approximately as well as possible for seven beliefs, but fell short for the other seven.
 These failures suggest that the model is missing the information that would be needed to predict these beliefs.
@@
 
-```{r, echo=FALSE, message=F, warning=F}
+```{r model_valid_table, echo=FALSE, message=F, warning=F}
 # compare S1 model predictions to test-retest reliability?
@@
 ```
+
 ## Estimating the strength of evidence from changes in belief reports
 
-Returning to the DAG shown in Figure 1 above, consider the subgraph $FIRE \rightarrow SMOKE$, capturing the fact that fire causes smoke.
+Returning to the DAG shown in Figure \@ref(fig:dag_example) above, consider the subgraph $FIRE \rightarrow SMOKE$, capturing the fact that fire causes smoke.
 This relationship is represented as a probabilistic function, where the probability of SMOKE depends on the probability of FIRE.
@@
 Observing WITNESS informs beliefs about SMOKE, in turn informing beliefs about FIRE.
-This approach to representing uncertain evidence is known as “virtual evidence” (Pearl, 1988).
-
-To model the effects of participants observing evidence, we augmented the Bayesian network representing the cognitive model (shown in figure #) with an additional node representing the evidence.
+This approach to representing uncertain evidence is known as “virtual evidence” [@pearl1988].
+
+To model the effects of participants observing evidence, we augmented the Bayesian network representing the cognitive model (shown in Figure \@ref(fig:disp-maingraph)) with an additional node representing the evidence.
 For instance, to model the effects of the “disease risk” intervention (Study 2), we added an evidence node as a child of “disease severity,” acting as virtual evidence for this node.
@@
 
-Where x was a binary variable representing the presence (1) or absence (0) of evidence at posttest, and participants’ prior and posterior (pretest and posttest) credences were transformed by the logit function.
-This allowed us to estimate the log evidence ratio implied by participants’ reactions to the intervention (ER1) as well as the intervening time period without any explicit evidence (ER0).
-Then, we constructed a CPT consistent with ER1.
+Where $x$ was a binary variable representing the presence (1) or absence (0) of evidence at posttest, and participants’ prior and posterior (pretest and posttest) credences were transformed by the logit function.
+This allowed us to estimate the log evidence ratio implied by participants’ reactions to the intervention ($ER_1$) as well as the intervening time period without any explicit evidence ($ER_0$).
+Then, we constructed a CPT consistent with $ER_1$.
 For instance, with an evidence ratio below 1, we set:
@@
 
-To do this, we drew on a variety of sources, including a qualitative survey with participants in a previous study who had self-identified as vaccine skeptics.
+To do this, we drew on a variety of sources, including a qualitative survey with a set of pre-screened participants who had self-identified as vaccine skeptics.
 Out of 23 people invited to participate, n=16 participants completed the survey via Amazon Mechanical Turk (MTurk).
-All participants answered “yes” to the question “Are you concerned that childhood vaccinations might cause serious side-effects?” When asked, “Do you have concerns about all vaccines or only some specific vaccines?” nearly all participants (14 of 16) expressed being concerned about specific vaccines; 3 of these participants, as well as the remaining 2 participants, expressed concern about all vaccines.
+All participants had previously answered “yes” to the question “Are you concerned that childhood vaccinations might cause serious side-effects?” When asked, “Do you have concerns about all vaccines or only some specific vaccines?” nearly all participants (14 of 16) expressed being concerned about specific vaccines; 3 of these participants, as well as the remaining 2 participants, expressed concern about all vaccines.
 
@@
 
-Drawing on these responses as well as anti-vaccine websites and academic articles on anti-vaccine skepticism (e.g., CITE), we generated a list of 13 underlying beliefs that might influence people’s decisions about whether to vaccinate their children (_vaccine intentions_, the last of our 14 beliefs).
-These included a variety of claims about vaccines, including beliefs about (1) the overall danger of vaccines (_vaccine danger_); (2) _toxic additives in vaccines_; and (3) _vaccine effectiveness_, how effective vaccines are in preventing disease; as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about (4) _disease rarity_ and (5) _disease severity_.
+Drawing on these responses as well as anti-vaccine websites and academic articles on anti-vaccine skepticism [@dube.etal2015, @larson.etal2015, @salmon.etal2015, @williams2014], we generated a list of 13 underlying beliefs that might influence people’s decisions about whether to vaccinate their children (_vaccine intentions_, the last of our 14 beliefs).
+These included a variety of claims about vaccines, including beliefs about (1) the overall danger of vaccines (_vaccine danger_); (2) _toxic additives in vaccines_; and (3) _vaccine effectiveness_, how effective vaccines are in preventing disease; as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about (4) _disease rarity _and (5) _disease severity_.
 Inspired by the many participants who invoked concerns about the effect of vaccines on infants’ immature immune systems, we also developed scales to assess beliefs that (6) the infant immune system is weak (_IIS: weakness_); (7) the infant immune system is limited in its capacity and can be easily overwhelmed (_IIS: limited capacity_); and (8) vaccines strain the infant immune system (_IIS: vaccines strain_).
 Beyond this, we developed two scales to assess general theories about parenting, including (9) general _parental protectiveness_; (10) _parental expertise_, namely the belief that parents usually know more about their children’s health than medical experts; and one scale to assess (12) _medical skepticism_, including concerns about pharmaceutical companies and corruption in the medical community.
-Finally, we decided to assess two broad worldviews: (12) _naturalism_, a general preference for natural over artificial things; and (13) _holistic balance_, one important aspect of attitudes toward alternative medicine (e.g., “The body is essentially self-healing and the task of a health care provider is to assist the healing process”; McFadden, Hernandez, & Ito, 2010).
-
-_Holistic balance_ was the only belief for which we could identify a pre-existing psychometrically valid scale (McFadden et al., 2010).
+Finally, we decided to assess two broad worldviews: (12) _naturalism_, a general preference for natural over artificial things; and (13) _holistic balance_, one important aspect of attitudes toward alternative medicine (e.g., “The body is essentially self-healing and the task of a health care provider is to assist the healing process”; [@mcfadden.etal2010].
+
+_Holistic balance_ was the only belief for which we could identify a pre-existing psychometrically valid scale [@mcfadden.etal2010].
 For each of the other 13 beliefs, we translated our qualitative insights into new psychometrically-valid scales through an iterative series of pilot studies not described here.
-We stipulated that each scale should be brief, composed of 4-6 statements for participants to evaluate; include at least one reverse-coded item; and be highly reliable (Cronbach’s α ≥ .80).
+We stipulated that each scale should be brief, composed of 4-6 statements for participants to evaluate; include at least one reverse-coded item; and be highly reliable (Cronbach’s $\alpha \geq .80$).
 
@@
 
-_Method._ Participants in all of these studies were asked to respond at least once to 14 belief scales measuring beliefs relevant to vaccination decisions (as previously described).
+### Method
+
+Participants in all of these studies were asked to respond at least once to 14 belief scales measuring beliefs relevant to vaccination decisions (as previously described).
 Across all studies, these scales were each presented on a separate survey page.
@@
 
-_Data processing._ For each scale, we generated a score for each participant by averaging their responses to each question in that scale (after reverse-coding where appropriate), and then rescaling these values to fall between 0 and 1, to represent a credence.
+### Data processing
+
+For each scale, we generated a score for each participant by averaging their responses to each question in that scale (after reverse-coding where appropriate), and then rescaling these values to fall between 0 and 1, to represent a credence.
 
@@
 
-Figure X presents correlations among the 14 belief scales measured in Study 1.
+Figure \@ref(fig:corrplot) presents correlations among the 14 belief scales measured in Study 1.
 As the figure shows, there are strong correlations among many of the beliefs, suggesting they are related by an underlying intuitive theory.
 
-```{r, echo=FALSE, message=F, fig.height=7, fig.width=7, fig.align='center', fig.cap = "Correlations among 14 the belief scales measured in Study 1.
+```{r corrplot, echo=FALSE, message=F, fig.height=7, fig.width=7, fig.align='center', fig.cap = "Correlations among 14 the belief scales measured in Study 1.
 Correlation matrix is arranged by hierarhical clustering algorithm to highlight connections among beliefs."}
@@
 
-We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the _Vaccination Intentions_ scale items, using the “brms” package for R (CITE).
+We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the _Vaccination Intentions_ scale items, using the “brms” package for R [@burkner2017].
 We regressed responses on phase (Phase 1 vs.
@@
 In this model, the unique effect of the intervention on vaccination intention responses is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants).
-The disease risk intervention increased participants’ vaccination intention ratings (see Table X).
-We consider this to be a full replication of Horne, Powell, et al.’s (XX) results.
+The disease risk intervention increased participants’ vaccination intention ratings (see Table \@ref(tab:s2_model)).
+We consider this to be a full replication of Horne et al.’s [-@horne.etal2015] results.
 
@@
 
-Figure X (right) shows the correlation between predicted and observed belief changes conditional on the disease risk intervention.
-
-```{r, echo=FALSE}
+Figure \@ref(fig:s2_plot) (right) shows the correlation between predicted and observed belief changes conditional on the disease risk intervention.
+
+```{r s2_plot, echo=FALSE}
 # create cognitive model for predicting change scores
@@
 
+The models’ predictions are strongly correlated with observed changes.
+Thus the model developed in Study 1 generalizes both across samples and across tasks: The model was developed from the correlations among beliefs in one sample of participants at a single time-point, and was able to accurately predict how a separate sample of participants revised their beliefs following evidence.
+
 ## Studies 3a and 3b
@@
 
-1) Where beliefs about two states of affairs, A and B, are related through a shared intuitive theory (e.g., A causes B), those beliefs will be systematically correlated across individuals (e.g., people who believe A will also tend to believe B);
-
-2) When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g., evidence for B will increase credence in A, and vice versa); and
-
-3) Following from the prior points, across individuals, the average change in one belief following evidence affecting another belief will be proportional to the correlation between those beliefs across individuals (evidence for B will increase credence in A in proportion to the correlation between beliefs A and B).
+1.
+Where beliefs about two states of affairs, A and B, are related through a shared intuitive theory (e.g., A causes B), those beliefs will be systematically correlated across individuals (e.g., people who believe A will also tend to believe B);
+
+2.
+When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g., evidence for B will increase credence in A, and vice versa); and
+
+3.
+Following from the prior points, across individuals, the average change in one belief following evidence affecting another belief will be proportional to the correlation between those beliefs across individuals (evidence for B will increase credence in A in proportion to the correlation between beliefs A and B).
 
@@
 This captures qualitative Feature 3 of intuitive theories.
-Figure X presents these predictions, assuming the changes in beliefs are designed to move vaccine intentions in a positive direction (e.g.
+Figure \@ref(fig:predicted_impacts) presents these predictions, assuming the changes in beliefs are designed to move vaccine intentions in a positive direction (e.g.
 increasing “disease severity” beliefs but decreasing “vaccine danger” beliefs).
 
-```{r echo=F, message=F, fig.align='center', fig.height=3, fig.width=3, fig.cap="Predicted effects on Vaccine Intentions for hypothetical interventions targeting each of the 13 other beliefs"}
+```{r predicted_impacts, echo=F, message=F, fig.align='center', fig.height=3, fig.width=3, fig.cap="Predicted effects on Vaccine Intentions for hypothetical interventions targeting each of the 13 other beliefs"}
 
@@
 ```
-Guided by these predictions, we identified beliefs about toxins in vaccines as a potentially useful site of intervention--it is among the most strongly related and it is a concrete belief that could be addressed directly.
-We developed an educational intervention aimed at alleviating these concerns and tested its efficacy in two experiments.
+
+Guided by these predictions, we identified beliefs about toxins in vaccines as a potentially useful site of intervention--it is among the most strongly related and it is a concrete belief that could be addressed directly.Using information from the University of Oxford’s “Vaccine Knowledge Project”, the U.S.
+Department of Health and Human Services, Federal Drug Administration, and CDC, we developed an educational intervention aimed at alleviating these concerns and tested its efficacy in two experiments.
 
@@
 Procedures for studies 3a and 3b closely followed those of Study 2, but these studies tested the effects of a novel intervention aimed at dispelling concerns about toxic additives in vaccines.
-Full text of this intervention is available in appendix C of these supplementary materials.
+Full text of this intervention is available in Appendix C of these supplementary materials.
 In both studies, participants were randomly assigned to either a no-intervention control condition or to the novel vaccine toxins intervention.
@@
 The vaccine toxins intervention improved participant’s vaccination intention scores relative to a no-intervention control condition.
-Tables X-X show the results of these regression analyses for Experiment 3a, 3b, and the two studies combined.
+Tables below show the results of these regression analyses for Experiment 3a, 3b, and the two studies combined.
 In each analysis, the coefficient representing the interaction between phase and condition is positive and credibly differs from zero, indicating that the vaccine toxins intervention positively impacted vaccination intentions.
@@
 
-Figure X shows the correlation between predicted and observed belief changes conditional on the vaccine toxicity intervention.
-
-```{r echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
+Figure \@ref(fig:s3_plot) (right) shows the correlation between predicted and observed belief changes conditional on the vaccine toxicity intervention.
+
+```{r s3_plot, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
@@
     scale = recode_nodes2(scale),
-    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
+    condition = ifelse(condition=="noInterv", "Control", "Vaccine Ingredients")
     ) %>% 
@@
 
-### _Participants_.
-
 ```{r process_s4_data, include=FALSE}
@@
 
+### _Participants_.
+
 We attempted to contact and re-recruit as many of the `r nrow(d_bn)` participants who completed Study 1 to participate in a follow-up study in May of 2019.
@@
 
-```{r, echo=FALSE, message=F, warning=F}
+```{r s4_table, echo=FALSE, message=F, warning=F}
 # compare conditions on vaccIntent w/ regression model
@@
 To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure.
-Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (see Table X).
+Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (see Table \@ref(tab:s4_table)).
 
@@
 
-Figure X shows the correlation between predicted and observed belief changes for participants who were aware of the New York measles outbreak in May 2019.
-
-```{r echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4.
+Figure \@ref(fig:s4_plot) (right) shows the correlation between predicted and observed belief changes for participants who were aware of the New York measles outbreak in May 2019.
+
+```{r s4_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4.
 Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York.
@@
 
-# Appendix A
-
 ```{r, echo=FALSE}
@@
 
-Scale items + reliability coefficients
+# Appendix A
+
+At the beginning of the study, participants read the following instructions: “In this study, you will be asked to read a range of statements.
+Some of these statements may be controversial, and others less so.
+We are interested in your opinions about these issues.
+On each of the following screens, you'll see several statements.
+Please indicate how much you agree or disagree with each statement.”
+
+Participants then proceeded through 14 pages, with a different scale presented on each page.
+Scales, and questions within each scale, were presented in a random order for each participant.
+On each page, participants were asked to rate “how much you agree or disagree” on a 7-point scale from “Strongly disagree” to “Strongly agree.” After completing all 14 scales, participants were asked standard demographics questions (gender, age, race/ethnicity, religious affiliation, educational attainment, annual household income) as well as a handful of questions about whether they were or were expecting to be a parent.
+The study concluded with a brief statement about the safety of vaccines, as follows: “We very much appreciate hearing your opinions about these various issues.
+Some of these statements concerned vaccines.
+The overwhelming consensus in the scientific and medical communities is that vaccines are safe and effective.
+In case you're interested in learning more about this, below is a statement from the World Health Organization (WHO) on this topic, and a link to their website: ‘Vaccination is one of the most cost-effective health interventions available, saving millions of people from illness, disability and death each year.
+Effective and safe vaccines, which protect against a number of serious diseases, are available and many promising new vaccines are being developed.’ (WHO Website: www.who.int/immunization/diseases/en/).”
+
+The 14 scales are presented in their entirety below.
+
+_Holistic balance_, from McFadden et al.’s (2010) Complementary, Alternative, and Conventional Medicine Attitudes Scale (CACMAS) (observed α=.82)
+
+1. The body is essentially self-healing and the task of a health care provider is to assist the healing process.
+2. Physical and mental health are maintained by an underlying energy or vital force.
+3. A patient’s symptoms should be regarded as a manifestation of a general imbalance or dysfunction affecting the whole body.
+4. Health and disease are a reflection of balance between positive life enhancing forces and negative destructive forces.
+
+_Naturalism_ (observed α=.77)
+
+1. Natural things are always better than synthetic alternatives.
+2. In some cases, it’s fair to say that science has improved on nature. (reversed)
+3. I’m always wary of any chemicals that were developed in a lab. 
+4. Overall, advances in chemistry and the creation of synthetic chemicals have done more harm than good for human health.
+5. Childbirth should take place at home rather than in a hospital.
+6. I’m not concerned about preservatives in food. (reversed)
+
+_Medical skepticism_ (observed α=.78)
+
+1. Pharmaceutical companies are more interested in making money than in helping people be healthy.
+2. FDA regulations ensure that approved pharmaceutical drugs are safe. (reversed)
+3. Pharmaceutical companies put pressure on the FDA and CDC to suppress negative findings.
+4. Most researchers are biased against the idea that medications or vaccinations could cause health problems.
+5. Pharmaceutical companies don’t make huge profits from the sale of vaccines. (reversed)
+6. For researchers developing vaccines, safety is a top priority. (reversed)
+
+_Disease rarity_ (observed α=.79)
+
+1. Diseases like measles and whooping cough are so rare that there is no real need to worry about them.
+2. Nowadays parents can feel certain their children will not contract measles or mumps.
+3. It’s not paranoid for parents to worry about their children getting measles. (reversed)
+4. It is almost impossible for a child currently living in the US to catch whooping cough.
+5. Measles and whooping cough are more common than people realize. (reversed)
+
+_Disease severity _(observed α=.84)
+
+1. Measles, mumps, and whooping cough are no more severe than the flu. (reversed)
+2. Childhood diseases are serious diseases.
+3. Diseases like measles, mumps, and whooping cough can cause permanent damage to a child who contracts them.
+4. Childhood diseases are not that big a deal. (reversed)
+5. Diseases like measles and whooping cough are extremely dangerous for young children.
+
+_Vaccine effectiveness _(observed α=.84)
+
+1. Your chances of getting a disease after being vaccinated against it are incredibly low.
+2. Improved nutrition and sanitation played a larger role than vaccines in the decline of diseases like measles. (reversed)
+3. Recent outbreaks of diseases like measles and whooping cough show that vaccines don’t work very well. (reversed)
+4. Vaccines are one of the most effective medical treatments.
+
+_Vaccine danger _(observed α=.88)
+
+1. Childhood vaccines can cause autism.
+2. It is safe for infants to receive multiple vaccines at once. (reversed)
+3. Many children have severe adverse reactions to the MMR vaccine.
+4. Vaccines are a very safe medical treatment. (reversed)
+
+_Toxic additives in vaccines _(observed α=.91)
+
+1. Vaccines do not contain dangerous amounts of toxins. (reversed)
+2. Vaccines are actually highly toxic to humans.
+3. Exposure to certain additives in vaccines can cause major health problems. 
+4. The quantities of chemical additives in vaccines are so small that they do not pose any health risks. (reversed)
+
+_Infant immune system: Vaccines strain _(observed α=.86)
+
+1. Vaccines strain the immune system much like the actual disease.
+2. One great benefit of vaccines is that they provide immunity without the immune system having to work so hard. (reversed)
+3. Vaccines can use up the capacity of the immune system, leaving a baby vulnerable.
+4. Vaccines are not very taxing for an infant's immune system. (reversed)
+5. Getting multiple vaccines at once can exhaust an infant’s immune system.
+
+_Vaccination intentions _(observed α=.83)
+
+1. The risk of side effects outweighs any protective benefits of vaccines. (reversed)
+2. If I had a young baby I would have him or her vaccinated. 
+3. If I had a baby, I would opt to spread out his or her vaccinations, rather than following the traditional schedule. (reversed)
+4. I feel confident that vaccinating children is the right thing to do.
+5. I would never vaccinate my child. (reversed)
+
+_Parental expertise _(observed α=.83)
+
+1. Every individual is different and a parent knows their own child best.
+2. Parents have insights into their children’s health and well-being that no health professional can match.
+3. When a child encounters health problems, the child’s parents are often better equipped than doctors to identify the many subtle causes of those issues.
+4. Parents should trust a doctor’s advice even if it goes against their intuitions. (reversed)
+5. Advice from doctors is the best resource for keeping your child healthy. (reversed)
+
+_Infant immune system: Limited capacity_ (observed α=.86)
+
+1. When babies are exposed to one illness it leaves them especially vulnerable to other viruses and infections.
+2. Babies are able to fight off multiple viruses at the same time. (reversed)
+3. Babies’ immune systems can only develop a limited number of antibodies.
+4. Babies’ immune systems are severely limited in how much they can cope with at one time.
+5. Babies’ immune systems can deal with many threats at one time. (reversed)
+
+_Infant immune system: Weakness_ (observed α=.85)
+
+1. Babies should be sheltered from exposure to viruses and bacteria to the greatest extent possible.
+2. Babies have a very limited ability to fight off diseases.
+3. Babies’ immune systems are weak.
+4. Babies have an innate ability to fight off diseases. (reversed)
+5. Babies’ immune systems are more robust than many people think. (reversed)
+
+_Parental protectiveness _(observed α=.73)
+
+1. Parents should strive to control their baby’s environments as much as possible.
+2. Parents of babies should never leave anything to chance.
+3. There is no such thing as being overprotective of a baby.
+4. Many things that parents of babies worry about won’t actually have major consequences.
+5. Some parents go overboard trying to make everything perfect for their babies. (reversed)
 
@@
 
-Disease severity intervention
+_Text of the Disease Risk intervention adapted from [@horne.etal2015]_
+
+All children should be vaccinated for measles, mumps, and rubella. These are serious diseases. Please read the descriptions of these diseases and carefully view the pictures.
+
+```{r measles-image, echo=F}
+# display measles image here
+```
+
+__Measles__
+
+Measles virus causes rash, cough, runny nose, eye irritation, and fever. It can lead to ear infections, pneumonia, seizures (jerking and staring), brain damage, and death.
+
+```{r mumps-image, echo=F}
+# display mumps image here
+```
+
+__Mumps__
+
+Mumps virus causes fever, headache, and swollen glands.
+It can lead to deafness, meningitis (infection of the brain and spinal cord covering), painful swelling of the testicles or ovaries, and, rarely, death.
+
+```{r rubellas-image, echo=F}
+# display rubella image here
+```
+
+__Rubella (German Measles)__
+
+Rubella virus causes rash, mild fever, and arthritis (mostly in women).
+If a woman gets rubella while she is pregnant, she could have a miscarriage or her baby could be born with serious birth defects.
+
+You or your child could catch these diseases by being around someone who has them. They spread from person to person through the air.
+
+Measles, mumps, and rubella (MMR) vaccine can prevent these diseases. Most children who get their MMR shots will not get these diseases. Many more children would get them if we stopped vaccinating.
+
+**Here is a true story that shows why vaccination is so important.**
+
+If you hear “106 degrees” you probably think “heat wave,” not a baby’s temperature.
+But for Megan Campbell’s 10-month-old son, a life-threatening bout of measles caused fevers spiking to 106 degrees and sent him to the hospital.
+“We spent 3 days in the hospital fearing we might lose our baby boy,” Campbell said.
+“He couldn't drink or eat, so he was on an IV, and for a while he seemed to be wasting away.
+When he could drink again, we got to take him home.
+But the doctors told us to expect the disease to continue to run its course, including high fever – which spiked as high as 106 degrees.
+We spent a week waking at all hours and soothing him with damp washcloths.”
+
+Thankfully, the baby recovered fully.
+
+Megan now knows that her son was exposed to measles when another mother brought her ill son into their pediatrician’s waiting room.
 
@@
 
-Vaccine toxicity intervention
+_Text of the Vaccine Ingredients intervention targeting beliefs about toxins in vaccines._
+
+Vaccines are one of the most important medical advances in history, but some parents worry that vaccines contain toxins that could harm their babies.
+In fact, all of the ingredients in a vaccine serve important purposes that help ensure the safety and effectiveness of the vaccine.
+Decades of research have shown vaccine ingredients to be safe, even in much larger quantities than those found in vaccines.
+
+**What’s in a vaccine?**
+
+**Active ingredients**
+
+The key ingredient in all vaccines is one or more active ingredients, whose purpose is to train the immune system to recognize and combat the pathogens that cause diseases.
+To do this, certain molecules from the pathogen are introduced into the body to trigger an immune response.
+These molecules are called antigens, and they are present on all viruses and bacteria.
+By injecting these antigens into the body, the immune system can safely learn to recognize them as hostile invaders, produce antibodies, and remember them for the future.
+
+**Other Ingredients**
+
+A typical dose of an injected vaccines is just 0.5 millilitres of liquid, which is just a few drops.
+Apart from active ingredients, the main ingredient in vaccines is water.
+All other ingredients weigh a few thousandths of a gram or even less.
+All of the ingredients in vaccines have been proven to be safe for children in these minute quantities.
+
+All of the ingredients in a vaccine serve important purposes, and are present to ensure that the vaccine is safe and effective.
+Some of these added ingredients are adjuvants, added to enhance the immune system response; others are antibiotics, to prevent contamination during the manufacturing process; and still other ingredients act as preservatives and stabilizers.
+
+To take one example, consider one of the scariest things you may have heard about the ingredients in vaccines: that some vaccines contain formaldehyde.
+It may surprise you to learn that formaldehyde is actually produced by the human body as part of normal metabolic processes.
+Human bodies—even babies’ bodies—naturally produce, process, and safely excrete formaldehyde.
+The amount of formaldehyde in vaccines is extremely small compared to what our bodies produce on their own: the amount of formaldehyde naturally present in a 2-month-old infant’s blood (around 1.1 milligrams) is ten times greater than the amount found in any vaccine (less than 0.1 milligrams).
+In addition, many healthy foods--such as apples, grapes, bananas, and pears--naturally contain formaldehyde.
+A pear, for example, contains around 50 times more formaldehyde than is found in any vaccine.
+
+**Conclusion**
+
+Vaccines are extremely safe.
+A vaccine is just a few drops of liquid, the vast majority of which is water, and all of the ingredients in vaccines serve specific purposes to help make them safe and effective.
+Although some vaccine ingredients may sound scary, many of them are natural substances that are already in our bodies.
+In large quantities anything can be toxic, but extensive testing has shown that none of the ingredients in vaccines are toxic in the tiny quantities with which they’re used.
+Vaccines have been carefully studied to ensure both their safety and their effectiveness in protecting babies from serious diseases.
+
+\newpage
+# References

### 2021-07-18 paper/paper.Rmd
added paper skeleton

---
title: "Untitled Vaccine Intuitive theories paper"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

[add abstract]

[add significance statement]

One remarkable feature of human psychology is our ability to form rich mental representations of what is true, how things work, and how best to navigate the world around us. Much of this type of thinking can be understood as deriving from people’s *intuitive theories*—explanatory frameworks, analogous to scientific theories, that capture the causal and logical structure of the world within a domain. From early in life, people are driven to seek out such causal explanations and to use their mental representations of these causal systems to explain, predict, and intervene in the world; and to make sense of new information and experiences. (See Carey, 2009; Gelman & Legare, 2011; Gerstenberg & Tenenbaum; Gopnik & Wellman, 1994; Keil, 1994; Murphy & Medin, 1985; and Wellman & Gelman, 1992; for influential  treatments of this topic.)  Intuitive theories inform reasoning in a wide variety of domains, from reasoning about physical systems (e.g., Baillargeon, 2004; Battaglia, Hamrick, & Tenenbaum, 2013; Spelke, 1994; Ullman et al., 2017), to reasoning about biological processes (e.g., Carey, 1985, 2009; Medin & Atran, 1999) and about the contents of other people’s minds (e.g., Gopnik & Wellman, 1992; Wellman, 2015; Baker, Jara-Ettinger, Saxe, & Tenenbaum).

Because intuitive theories are powerful tools for making sense of the world, when these theories are mistaken there can be serious consequences. In this paper, we focus on a timely example: misconceptions about vaccine safety.

Even before the coronavirus pandemic, misconceptions about vaccine safety drove public health crises around the world. Undervaccination resulted in outbreaks of measles affecting over 1000 children across the United States in 2019, and over 80,000 children across Europe in 2018 (WHO, 2018). Misconceptions about childhood vaccination—particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects—have proved remarkably difficult to correct (e.g., Betsch & Sachse, 2013; Horne, Powell, Hummel, & Holyoak, 2015). Sadly, only a handful of educational interventions have been found to improve vaccine attitudes (e.g., Horne et al., 2015; Vannice et al., 2011; Wallace et al., 2006; Dube et al., 2015). This is especially  sobering in the context of the coronavirus pandemic: reluctance to be vaccinated against COVID-19 threatens our ability to end a pandemic that has already claimed millions of lives around the world.

The difficulty of convincing people to vaccinate themselves and their children illustrates a general pattern of findings showing that people often do not respond to evidence in ways that educators might wish (e.g. Lewandowsky et al., 2012). Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems—intuitive theories—that guide how people interpret and respond to evidence (e.g., Lewandowsky et al., 2012; Jern et al., 2014; Gershman, 2019).

Consider some of the beliefs people who are skeptical of childhood vaccination expressed when we asked them to explain their views in an open-ended qualitative survey (conducted pre-pandemic; N=16). Several participants saw vaccines as "unnatural" and expressed concerns about toxic additives in vaccines, such as heavy metals and mercury. One said, “Vaccines are unnatural additions to the body. The human body should naturally fight off the disease and we should not be controlling how nature plays its role on mankind.” Some doubted whether certain diseases were worth worrying over, while others feared that the contents of vaccines “are too strong and too concentrated for a baby's body to properly handle.” A number of respondents were skeptical of the medical community’s objectivity in testing the safety of vaccines. One respondent wrote that vaccines were “A BIG MONEY MAKING SCAM BY THE BIG PHARMS” (emphasis theirs); another thought that health professionals “are brainwashed by the medical media and the government.” To people holding these beliefs, it could well seem unreasonable to vaccinate a 2-month-old baby against 5 or more diseases at once. Moreover, if skeptics believe that the medical community is unduly influenced by pharmaceutical companies, they might doubt the validity of medical studies coming out in favor of these companies’ interests. Altogether, these beliefs might sustain misconceptions about vaccine safety, even in the face of counter-evidence.

The way in which evidence affects any particular belief is unavoidably shaped by other interrelated beliefs. Duhem (1954) and Quine (1951) famously argued that scientific theories necessarily incorporate *auxiliary hypotheses* that influence how observations are interpreted: When an observation is inconsistent with a hypothesis under certain auxiliary assumptions, a scientist cannot necessarily know whether to revise the hypothesis or the auxiliary assumptions. Similarly, we argue that intuitive theories incorporate auxiliary beliefs that affect how other beliefs are revised in light of evidence (also see Gershman, 2019).

Here we present a line of theoretical and empirical work that seeks to understand misconceptions and belief revision in the context of people’s intuitive theories. We focus on reducing hesitancy toward childhood vaccination by identifying intuitive theories surrounding these vaccination decisions. Through this case study we hope to shed light on why such misconceptions persist and how  interventions might address misconceptions more effectively across domains.

We argue that correcting misconceptions requires presenting evidence in a way that is sensitive to and persuasive within the broader conceptual context in which those misconceptions reside (see Gershman, 2019; Weisman & Markman, 2017). Understanding the revision of any one specific belief (e.g., a misconception like *vaccines are dangerous*) demands a holistic understanding of the wider set of interrelated beliefs that make up people's intuitive theories.

## Modelling intuitive theories

Quine argued that all of one’s beliefs are intertwined in a “web of belief” (1951; 1970)—an apt metaphor for intuitive theories. Intuitive theories consist of relations between beliefs that specify how states of affairs causally, logically, or otherwise interconnect with one another. Given this definition, we argue that any set of beliefs related by an intuitive theory can be expected to exhibit several qualitative features:

1) Where beliefs about two states of affairs, A and B, are related through a shared intuitive theory (e.g., A causes B), those beliefs will be systematically correlated across individuals (e.g., people who believe A will also tend to believe B);

2) When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g., evidence for B will increase credence in A, and vice versa); and

3) Thus across individuals, the average change in one belief following evidence affecting another belief will be proportional to the correlation between those beliefs across individuals (evidence for B will increase credence in A in proportion to the correlation between beliefs A and B).

Here, we sought to formalize this understanding of intuitive theories by representing an intuitive theory as a Bayesian network. Originally designed as tools for artificial intelligence (Pearl, 1988), Bayesian networks are a class of probabilistic graphical models that have been deployed widely across cognitive science (e.g. Gopnik et al., 2004; Griffiths & Tenenbaum, 2005; Jern et al., 2012). The heart of a Bayesian Network is a graphical structure—not unlike a "web of belief"—that represents variables as nodes connected by edges, where those edges represent probabilistic or statistical relations.

For example, the graph *FIRE → SMOKE* represents a Bayesian network capturing the understanding  that fire causes smoke. The example of cause and effect is especially intuitive, but edges in a Bayesian network need not be causal; they are better thought of as representing “influence relations,” which may also include relationships like logical implication and set membership (Williamson, 2001). This influence relationship is represented as a probabilistic function, where the probability of smoke depends on the probability of fire.

This model captures each of the qualitative features laid out above: First, it captures people’s  reasoning  about these states of affairs given observations: observing smoke would lead someone to infer that there is likely to be a fire, and observing fire would lead someone to predict smoke will soon follow (Feature 1). This model can also capture how these beliefs might covary across individuals: if two people hold different degrees of belief in FIRE, this model specifies the degree of belief each should have in SMOKE (Feature 2). Moreover, both the correlation in beliefs across individuals and the change in beliefs given observations are determined by the conditional probability of SMOKE given FIRE. Thus, changes in beliefs following evidence will be proportional to their correlations across individuals (Feature 3). Formulating these features in a formal model, rather than a verbal theory, allows us to specify not just the presence but the quantitative strength of these relations, and to simulate the cumulative influences of many factors in more complex networks (for example, incorporating beliefs about the frequency of wildfires, recent weather conditions, etc.).

Where the structure of an intuitive theory is known, Bayesian networks thus offer powerful tools for predicting and understanding how evidence will affect people's beliefs. However, there are many cases where the structure of the intuitive theory is itself the very question under investigation. Consider vaccine hesitancy: Earlier, we speculated that beliefs about the infant immune system and beliefs about the trustworthiness of the medical community (among many others) might affect people’s beliefs about vaccines. But the structure of the intuitive theory that might relate these beliefs is not at all clear.

Fortunately, the formalism of Bayesian networks provides tools for navigating these challenges. Roughly, when the relationships among beliefs are unknown, we can use the qualitative features of intuitive theories to *infer* the structure of an intuitive theory from observed correlations among beliefs. Structure learning algorithms (see Scutari & Denis, 2021) provide a means for searching through the (super-exponentially large) possible space of Bayesian networks to find the structure most likely to have generated some observed data. These approaches allow us to scale the Bayesian network modelling framework beyond the simple models characteristic of early computational work on intuitive theories (e.g., Griffiths & Tenenbaum, 2005).

Here, we used Bayesian network structure learning algorithms to construct a model of the intuitive theory underlying adults’ decisions about whether or not to vaccinate children against diseases like measles, mumps, and rubella.

# Current studies

In Study 1, we used Bayesian network structure learning algorithms to develop a cognitive model of the relationships among 14 beliefs related to vaccine hesitancy in a large sample of people. In Study 2, we replicated the success of an existing intervention emphasizing the dangers of childhood diseases (Horne et al., 2015) and used our model to provide a more detailed understanding of *how* *and why* this intervention increases vaccine intentions and its effects on related beliefs. In Study 3a and 3b, we drew inspiration from our model to create and validate the success of  a novel intervention aimed at debunking concerns about toxic additives. Finally, in Study 4 we tested whether people's beliefs changed coherently following relevant real-world events, by examining beliefs before and after serious outbreaks of measles in the United States in early 2019. Taken together, this work illustrates the promise of understanding belief revision in terms of intuitive theories and the utility of discovering and formalizing intuitive theories via computational models. And, it lays the foundation for empirically-validated, theory-based educational interventions that could encourage people to vaccinate their children and themselves against dangerous diseases like measles and Covid-19.

## Results

### Study 1: Assessing and modeling intuitive theories of vaccination**

Our primary outcome of interest was participants’ intentions to vaccinate their children against diseases like measles, mumps, and rubella (*vaccination intentions*). Drawing on a variety of sources, including research on anti-vaccine skepticism, anti-vaccine websites, and our own qualitative work with vaccine skeptics (see SI), we generated a list of 13 additional beliefs that, though surely not exhaustive, might jointly offer a reasonable means of understanding and predicting vaccine intentions.

These included a variety of claims about vaccines, including beliefs about (1) the overall danger of vaccines (*vaccine danger*); (2) *toxic additives in vaccines*; and (3) *vaccine effectiveness*, how effective vaccines are in preventing disease; as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about (4) *disease rarity* and (5) *disease severity*. Beyond this, we theorized that participants’ understanding of the infant immune system might be relevant, including beliefs that (6) the infant immune system is weak (*IIS: weakness*); (7) the infant immune system is limited in its capacity and can be easily overwhelmed (*IIS: limited capacity*); and (8) vaccines strain the infant immune system (*IIS: vaccines strain*). We also included general theories about parenting and medicine: (11) general *parental protectiveness*; (12) *parental expertise*, namely the belief that parents usually know more about their children’s health than medical experts; and (13) *medical skepticism*, including concerns about pharmaceutical companies and corruption in the medical community; and two two broad worldviews: (9) *naturalism*, a general preference for natural over artificial things; and (10) *holistic balance*, one important aspect of attitudes toward alternative medicine (e.g., “The body is essentially self-healing and the task of a health care provider is to assist the healing process”; McFadden, Hernandez, & Ito, 2010).

We developed psychometrically robust scales to measure these beliefs, then administered these 14 belief scales to participants and in an online survey with 1130 participants. There were strong intercorrelations among these 14 beliefs confirming that these beliefs are, in fact, closely related to each other and to intentions to vaccinate children (see SI).

#### Structure learning

We used these intercorrelations to build a cognitive model of the relations among these beliefs using Bayesian network structure learning techniques, using an 80% training split of the data (n = 904). Based on the observed associations among participants' beliefs about each of theses issues, we sought to infer how these states of affairs (e.g., that vaccines are dangerous, that diseases are severe) are connected in people's intuitive theories--how people understand these states of affairs to cause, imply, or otherwise influence one another.

We assumed  that the intuitive theory is a generative model, so that these influence relations (“edges”) should flow from causes or other “generating” states of affairs toward effects. For instance, we stipulated that *vaccine intentions* would be a “child node,” with edges only flowing inwards and not outwards (since one’s intention to vaccinate cannot “generate” the facts about vaccinations safety, effectiveness, etc). These constraints and their consequences are considered in more detail in Methods.

Applying these techniques resulted in an estimate of the network shown in Figure 1.

```{r fig1-maingraph, fig.align='center', fig.height=8, fig.width=5, fig.cap="Bayesian network model resulting from hill-climbing algorithm applied to data in Study 1 training test split (n = 904). The network has 29 edges connecting these 14 variables. Edge polarity and weights are indicated by color, with red hues indicating negative or preventive influences, and blue hues indicating positive or generating influences. The direction of the edge was not determinable from the data and modeling constraints for two edges: $\\text{Naturalism} \\rightarrow \\text{Holistic Balance}$ and $\\text{Medical Skepticism} \\rightarrow \\text{Parental Expertise}$; see SI."}

knitr::include_graphics("../local/main-graph-combined.pdf")
```

We evaluated the model’s performance by testing its accuracy in predicting responses in the 20% testing split (n = 226). We generated predictions for held-out participants’ responses for each variable by conditioning the network on the remaining 13 observed variables. Figure 2 compares the model’s predictions with participants’ actual responses. Collapsing across all variables, the average correlation between predicted and observed responses was r = .XXX, accounting for [\~70]% of the variance in observed responses.

```{r fig2-validation, fig.align='center', fig.height=4, fig.width=7, fig.cap="Observed responses and model predictions for each belief among participants in the Study 1 testing split. Correlations between observed and predicted values ranged from XXX to XXX across the different belief scales. In general, the model showed greater predictive accuracy for more central beliefs (e.g., *vaccine danger*) than for more peripheral beliefs (e.g., *parental protectiveness;* see SI for details)."}
knitr::include_graphics("../local/valid_plt.png")
```

What does this model reveal about the intuitive theory underlying vaccination decisions?

The three nodes with direct connections to *vaccine intentions* are beliefs about *vaccine effectiveness*, *vaccine danger*, and the severity of childhood diseases (*disease severity*)—concrete beliefs that are, at face value, especially closely related to vaccination decisions.  This gives us confidence that the model is capturing important relationships.

Other parts of the model shed new light on the role of lay theories in vaccination decisions. For example, *naturalism*—the general view that natural things are better than artificial things—appears to be strongly related to *medical skepticism* and *parental expertise*; all three of these abstract beliefs are related to concrete beliefs that, in turn, feed into participants’ vaccination intentions.

This model structure also helps explain some initially surprising findings. For example, we originally speculated that dispelling misconceptions about the capacity of the infant immune system could promote positive attitudes toward vaccination. We were disappointed to observe the weak first-order correlation between this belief and *vaccine intentions* in our behavioral data (r = -.097 in our training split). The model sheds light on this surprising (lack of) relationship: Although the belief that the infant immune system is limited in capacity is positively related to the belief that vaccines strain the immune system—discouraging vaccination, as we had assumed—it also seems to promote the belief that childhood diseases have severe consequences for young children (*disease severity*), which might, in turn, encourage vaccination. These countervailing forces—which, on average, seem to have cancelled each other out in this sample—dissuaded us from our plan to develop an intervention aimed at dispelling misconceptions about limited capacity in order to encourage childhood vaccination.

In sum: From a set of potentially relevant beliefs and a general principle guiding the likely relationships among these beliefs, we generated a cognitive model of an intuitive theory of this domain. In Studies 2-4, we use this same model to predict how this intuitive theory guides reasoning about new information.

### Study 2: Targeting disease severity beliefs

One of the few successful educational interventions in this domain was tested by Horne et al. (2015), who found that emphasizing the dangers of preventable diseases like mumps, measles, and rubella improved participants’ attitudes toward vaccines. Their intervention included descriptions of the symptoms of mumps, measles, and rubella; vivid photos of children suffering from these diseases; and a brief story from the perspective of a parent whose child was hospitalized with measles (see SI). This “disease risk” intervention improved attitudes toward vaccines compared to an irrelevant control essay and compared to an intervention aimed at debunking concerns about vaccines causing autism.

In Study 2, we used the belief network established in Study 1 to predict how Horne et al.’s (2015) intervention would affect the beliefs in this network, including people’s intentions to vaccinate their children. Participants completed the 14 belief scales from Study 1, then returned two days later to complete either the disease risk intervention or a no-intervention control, followed by the same 14 belief scales.

Figure 3 shows the change in participants’ attitudes across all 14 belief scales, from pretest to posttest. As expected, the largest change was observed for *disease severity* beliefs—the belief directly targeted by the intervention. Most importantly, the disease risk intervention significantly increased participant’s *vaccination intentions*, conceptually replicating earlier findings regarding this intervention (Horne et al., 2015).

Changes were also observed across the belief network identified in Study 1. Not only did participants exposed to the intervention come to see childhood diseases as more severe, they also came to see vaccines as less dangerous, and demonstrated less medical skepticism as well as less commitment to “holistic balance”. These results suggest that targeted educational interventions could have wide-ranging effects, from influencing whom people turn to for future information, to shaping the more abstract worldviews they bring to bear in understanding health and science.

```{r fig3-s2, fig.align='center', fig.height=4, fig.width=7, fig.cap="Belief changes following the intervention in Study 2. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions. Right, mean observed and model predicted change scores for the disease risk intervention condition. In both plots, error bars represent 95\\% confidence intervals. In both plots, changes were calculated after transforming responses to lie between 0 and 1."}

knitr::include_graphics("../local/s2_plt.png")
```

How did this intervention—which focused solely on the dangers of childhood diseases—affect beliefs about *vaccine danger*, *medical skepticism*, *holistic balance*, and so on? One explanation is that this intervention provides direct evidence for *disease severity* beliefs and that other beliefs are revised as a result of their relationships with *disease severity* as captured in the intuitive theory. To examine this, we used the same model developed in Study 1 to simulate how the 13 other beliefs in the intuitive theory would change if we intervened directly on *disease severity* (see Methods). As shown in figure #, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (R = .86).

### Study 3a and 3b: Targeting beliefs about vaccine toxicity

The intervention developed by Horne et al. and employed in Study 2 is notable for being one of the few educational interventions shown to decrease vaccine hesitancy—but is disease severity the only (or most) effective target for educational interventions in this domain?

One advantage of having developed a formal, computational representation of a network of beliefs supporting vaccination decisions is that it can guide our search for effective interventions, allowing us to compare how interventions targeting each of these other beliefs might potentially change people’s vaccination intentions (see figure 4). Countering myths about toxic additives is one approach the model developed in Study 1 predicts should be effective.

```{r fig4-predimpacts, fig.align='center', fig.height=3, fig.width=3, fig.cap="Predicted change in vaccination intentions following an equivalent hypothetical change in each of the other 13 beliefs."}
knitr::include_graphics("../local/pred_change_plt.png")
```

We developed a novel educational intervention that addresses fears about toxic additives in vaccines. This Vaccine Ingredients intervention explained the common components of vaccines, emphasized the minute quantities of all vaccine ingredients, and explained the roles that various vaccine additives play in ensuring the stability and safety of vaccines, such as antibiotics, adjuvants, and stabilizers. We gave special attention to defusing concerns about the use of formaldehyde in vaccines because our assessment of anti-vaccination websites suggested that this was a particular concern for many vaccine skeptics. The intervention acknowledged that some vaccines contain trace amounts of formaldehyde, but also pointed out that formaldehyde is a naturally-occurring metabolic byproduct  **in all living things and that it is already present in children’s bodies (and even in foods like pears) in far larger quantities than contained in any vaccine. The full intervention text can be found in SI.

We conducted two preregistered experiments (3a and 3b) testing the effects of this novel intervention using the same pretest-posttest design as Study 2. Collapsing across these two studies, figure 5 shows the change in participants’ (n = XXX) attitudes across all 14 belief scales from pretest to posttest. Most importantly, the Vaccine Ingredients intervention significantly improved participants’ vaccination intentions compared to the no-intervention control condition. Changes were also evident across many of the 14 beliefs, with the largest changes being a reduction in vaccine toxicity beliefs.

```{r fig5-s3, fig.align='center', fig.height=4, fig.width=7, fig.cap="Belief changes following the intervention in studies 3a and 3b. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions. Right, mean observed and model predicted change scores for the disease risk intervention condition. In both plots, changes were calculated after combining data from both studies and transforming responses to lie between 0 and 1 and error bars represent 95\\% confidence intervals."}
knitr::include_graphics("../local/s3_plt.png")
```

As in Study 2, we used our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in participants’ vaccine toxicity beliefs following the intervention. As shown in Figure 5, the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker R = .XX than those observed in our other studies.

In Study 3a, we were surprised to observe that beliefs also changed significantly from pretest to posttest among participants in the no-intervention control condition. Two months later we conducted a direct replication (Study 3b) in the hopes that any transient factors that might have caused these changes in beliefs might have dissipated, but we obtained very similar results (see SI).

We speculate that changes from pretest to posttest among control participants in both experiments were related to media coverage of measles outbreaks in the U.S. during the time these studies were conducted (April and June of 2019), so that participants’ beliefs were not only affected by our intervention between pretest and posttest, but also potentially by additional news stories or social media content related to the outbreaks. As we employed a pretest-posttest design and randomly assigned participants to conditions, these changes do not impair our ability to draw causal inferences as to the efficacy of our intervention. However, these additional unmodeled influences may be negatively impacting performance of the model’s predictions.

Nevertheless, the success of this intervention in changing people’s responses to our *vaccine intentions* scale highlights the potential of this computational, theory-based approach to understanding belief revision. This model allowed us to design a novel educational intervention focusing on vaccine ingredients that successfully changed participants’ beliefs in a domain where many previously-researched educational approaches have failed—while sparing the time and resources we might have otherwise expended on interventions which our model predicts are unlikely to be successful.

### Study 4: Natural experiment

The early months of 2019 saw the worst U.S. measles outbreak in decades, with over 1000 cases reported by June, mostly in the state of New York. These outbreaks were covered in every major newspaper and by every major news program. Would learning about these tragic events lead people to revise their beliefs about vaccines?

```{r fig6-s4, fig.align='center', fig.height=4, fig.width=7, fig.cap="Participants’ belief changes from participation in Study 1 to Study 4. Left, mean difference scores comparing beliefs reported in September 2017 and May 2019 for the 14 belief scales, across participants who did and did not report exposure to news of the ongoing New York measles outbreak. Right, mean observed and model predicted change scores for those participants who did report exposure to this news. In both plots, changes were calculated after transforming responses to lie between 0 and 1 and error bars represent 95\\% confidence intervals."}
knitr::include_graphics("../local/s4_plt.png")
```

To examine this possibility, we invited participants from Study 1 (conducted in September 2017) to participate in a new study measuring each of those 14 beliefs again (conducted on May 1st, 2019; approximately 18 months later). Of the 1130 participants in Study 1, 555 returned. Approximately [80]% of participants reported recently seeing, hearing, or reading about measles outbreaks.

Figure 6 shows the average change in participants’ beliefs following the outbreaks of 2019. Among participants who were exposed to relevant news covered, we observed changes in a number of beliefs, with notable increases in intentions to vaccinate, perceptions of vaccine efficacy, and perceptions of disease severity, as well as notable decreases in concern about vaccine danger. In contrast, most beliefs remained unchanged for those participants who did not report exposure to media, although there were modest changes in their beliefs about disease severity and disease rarity. These outbreaks appear to have significantly impacted people’s beliefs surrounding vaccination.

Were these changes coherent with respect to the intuitive theory specified by the model developed in Study 1? Unlike in the intervention studies, where a specific belief was targeted by the intervention, it is likely that many beliefs were addressed by media coverage of these outbreaks. To assess whether these changes were coherent, we examined how they were related to the most central of the beliefs we measured, *vaccine intentions*, using our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in *vaccine intentions.* As shown in Figure 6, the changes in participants’ beliefs are very similar to the model’s predictions (r = XX), suggesting that the changes in their beliefs were highly coherent with respect to their intuitive theories of the domain. Modeling these beliefs as united by an intuitive theory not only captures how these beliefs are revised immediately in light of evidence, but also how they are changed by real-world events.

**Discussion**

Across five studies, we examined how understanding people’s intuitive theories surrounding vaccination decisions could help us formulate educational interventions that would counteract misconceptions about vaccine safety and encourage vaccination. We identified 14 beliefs related to vaccination decisions and captured the relationships among these beliefs in a generative probabilistic cognitive model. Using this model we were able to predict how these beliefs would be affected by controlled educational interventions as well as real-world events. Inspired by our findings and model, we developed an intervention targeting beliefs about toxins in vaccines and found it successfully increased people’s intentions to vaccinate their children—adding to the very short list of effective interventions in this domain.

Our findings indicate that beliefs related to vaccination decisions can be understood as situated within a coherent intuitive theory: these beliefs were systematically related across individuals (Study 1), and these relationships were predictive of changes across these beliefs following evidence, whether that evidence took the form of educational interventions (Studies 2-3) or real-world events (Study 4). Modeling this intuitive theory formally as a Bayesian network allowed us to create a cognitive model that demonstrates these key features of intuitive theories quantitatively. Looking forward, this formal representation—though simplified and imperfect—lays a foundation for richer and more complex descriptions in the future: For instance, networks with richer parameterizations could capture how intuitive theories differ across individuals, opening up the possibility of fine-tuning predictions and perhaps even crafting tailored educational interventions for specific individuals or groups.

Developing this model also had practical benefits. By providing a graphical representation of the structure of this intuitive theory, this approach helped us to understand relationships between beliefs that were puzzling when considered only as correlations (e.g., the lack of correlation between beliefs about the infant immune system and vaccine intentions), and allowed us to “spot” opportunities to develop novel interventions.

More broadly, the approaches we have introduced here may shed light on long-standing theoretical questions about belief revision. Many researchers have argued that people's belief updating is subject to various biases, or is skewed by motivational factors (e.g. Kahan, 2013; Flynn et al., 2017; Kunda, 1990). Yet many of the phenomena traditionally taken as evidence for these theories can also be explained by normative models of belief revision, so long as we are willing to posit that other auxiliary beliefs can affect the relationships between a belief and evidence (e.g., Gershman, 2019; Jern et al., 2012). Adjudicating between competing views of belief revision will require us to move beyond minimal models and illustrative simulations by assessing whether people actually do hold these auxiliary beliefs, and whether their broader belief systems behave according to the rules of probabilistic inference. The Bayesian network structure learning techniques applied here are one tool we might use to build these richer models.

Though these studies were conducted before the onset of the COVID-19 pandemic and focused on childhood diseases, many similar concerns are likely to animate hesitancy toward COVID-19 vaccines, and certain insights might be readily applied to addressing them. For one, in the spirit of Horne et al.’s (2015) disease risk intervention, we suspect that education focused on how severely ill many people become and the prevalence of long-term health problems following even mild cases of COVID-19 might encourage people to accept coronavirus vaccines.

On the other hand, the pandemic has presented its own unique issues. MRNA vaccines like those from Pfizer-BioNtech and Moderna represent highly novel technologies that are currently approved only under emergency use authorizations after being developed at a pace far faster than previously imagined possible. These facts could engender hesitancy even among people who are otherwise comfortable with vaccinations.

Beyond this, in many countries COVID-19 and vaccines against it have been politicized in a way that other public health concerns are not. Political affiliations often imply concrete beliefs about the world that could be incorporated into a model of an intuitive theory: for instance, the belief that the coronavirus pandemic is a “hoax.” However, these affiliations are also associated with social commitments, personal values, and other identity-constituting beliefs that may be more challenging to  capture in an intuitive theory as we have conceived of it here (Van Leeuwen, 2014). Relatedly, the coronavirus pandemic has raised public awareness of many social issues that could also play an important role in people's intuitive theories of vaccination more broadly. The uneven impacts of the pandemic have laid bare inequities within the American healthcare system, and prompted a greater awareness of and reckoning with a history of racism and abuses by the medical community. Understanding of these issues, which might differ across members of majority and minoritized communities, is well worth exploration in future studies. At the same time, the concept of "herd immunity" has likely never had greater public understanding and appreciation than now. This understanding is potentially a prime target for future interventions, though one whose impacts are likely to depend on other auxiliary ethical commitments, such as moral beliefs about individuals’ obligations to their wider communities.

Intuitive theories are powerful cognitive tools, for better and for worse. Coherent networks of beliefs allow people to understand, predict, and navigate the world, but they can also sustain misconceptions and lead to suboptimal—even dangerous—decisions and behaviors. Deciding to opt out of getting vaccinated against diseases like measles or COVID-19 is not only dangerous for the individual, but a serious threat to public health. We hope the studies presented here have shed light on how people might come to such decisions, why the misconceptions that support these decisions can be so hard to combat, and how to develop educational interventions that are persuasive and effective in encouraging and sustaining healthier behaviors.

# Methods

## Qualitative studies and scale development

We drew on a variety of sources, including academic articles on anti-vaccine skepticism (e.g., Dube et al., 2015; Larson et al. 2015; Salmon et al., 2015; Williams, 2014), anti-vaccine websites, and a qualitative survey with self-identified vaccine skeptics (*n*=16) via Amazon Mechanical Turk (MTurk) to generate a list of beliefs that might influence people’s decisions about whether to vaccinate their children (*vaccine intentions*): *vaccine danger*, *toxic additives in vaccines*, *vaccine effectiveness*, *disease rarity*, *disease severity, infant immune system (IIS): weakness*, *IIS: limited capacity*, *IIS: vaccines strain*, *parental protectiveness*, *parental expertise*, *medical skepticism*, *naturalism*, and *holistic balance*. (See main text for descriptions, and SI for the items included in these scales.) We translated these qualitative insights into 14 psychometrically-valid scales; each scale measured agreement with 4-6 statements, including at least one reverse-coded item, and was highly reliable (All Cronbach’s $\alpha \geq .73$). We developed 13 of these scales, and included one preexisting scale (the “holistic balance” subscale from McFadden et al., 2010).

These 14 scales formed the backbone of Studies 1-4.

## General Methods: Studies 1-4

Studies 1-4 were conducted online via Amazon Mechanical Turk. Repeat participation was prevented, with no participants involved in more than one study, except as noted in Study 4. A breakdown of demographics and compensation by study is available in the SI.

All participants responded at least once to the 14 belief scales just described. Each scale was presented on a separate survey page, and participants rated a series of statements on a 7-point scale from “Strongly disagree” (coded as -3) to “Strongly agree” (+3). Scales, and questions within each scale, were presented in a random order for each participant. Attention checks (e.g., “Please select somewhat agree”) were embedded within two to four randomly chosen scales and participants who failed any of these checks were excluded from analyses.

We scored each belief scale by averaging a participant’s responses to each item (after reverse-coding where appropriate), then rescaling these values to fall between 0 and 1. We considered this score to represent the participant’s credence in the belief.

## Study 1

### Method

Participants (final *n* = 1130) responded to the 14 belief scales, followed by demographics questions and a handful of questions about whether they were or were expecting to be a parent. They were then debriefed with a brief statement noting that vaccines are safe and pointing them toward a WHO website for further information.

### Analyses

The goal of this study was to use these data to conduct a bottom-up search for a Bayesian network that would represent the intuitive theory surrounding vaccination decisions as a network of related beliefs.

*Bayesian network parameterization*. A Bayesian network is a directed acyclic graph that represents variables as nodes connected by directed edges. Each set of “child” and “parent” nodes in the larger network is a “family”. The network’s directed edges encode conditional dependencies among variables, and many parameterizations for the individual families are possible. In our model, the probability of some “child” belief node *y* can be expressed as a noisy-logical function of the influence of one or more “parent” belief nodes *x*:

$$P(y) = 1 \big[1-(1-w_0)\prod_i(1-w_i)^{x_i}\big]\prod_j(1-w_j)^{x_j}$$

Here, each parent node *x* is either a generative (*i*) or preventive (*j*) influence, that generates or prevents the child node with some probability weight (*wi* or *wj*). The weight *w0* represents the “leak” probability, or the baseline probability that the child occurs without any other generating influences. The first term in brackets represents the probability that *y* is generated (or, put another way, that not all of the possible generating forces fail to generate it). The second term represents the probability that it is not then prevented (i.e., that all the preventing forces fail; see Maaskant & Druzdel, 2008).

Having transformed participants’ averaged belief scale responses to fall between 0 and 1, we estimated the parameters of the model as a beta regression using maximum likelihood methods (see SI).

*A cognitive model underlying the data model.* We aimed to represent not only the relationships among variables in the data but the *cognitive model* that gave rise to these observed relationships, i.e., the relationships among beliefs in the mind. We actually estimated two models: First, we estimated a data model assuming that participants possess a shared mental model from which they generate their responses to the belief scales. In this model, the *x* in the equation above corresponded to participants’ continuous responses to the belief scales (e.g. a participants score for the *vaccine danger* scale). Then, from the parameters estimated in the data model we created a cognitive model of participants’ reasoning, where the *x* are binary, indicating whether that state of affairs obtains (e.g., whether “vaccines are dangerous”). We used this cognitive model to simulate how beliefs could change following exposure to evidence.

*Structure learning, constrained by a “generative model principle.”* Rather than specifying a priori all of the connections among the 14 beliefs included in this study, we deployed Bayesian network structure learning to search for the most likely network structure given the observed correlations between beliefs—with the constraint that this structure conform to some of our strongest high-level intuitions about what an intuitive theory should look like in this domain.

In particular, we applied what we call the “generative model principle,” specifying that influence relations (edges) should flow from causes (or other generating states of affairs) to effects; instilling a core assumption in research on intuitive theories and causal explanatory reasoning (e.g. Cheng, 1997; Gopnik et al., 2004; Gerstenberg et al., 2021). We sorted the 14 measured beliefs into four tiers based on how general or abstract each belief was, reasoning that general and abstract states of affairs should be understood to cause (or otherwise generate) more specific and concrete states of affairs, so edges should flow from the general and abstract toward the specific and concrete (e.g., if natural things are better than artificial things, this should set an expectation about whether a specific class of artificial things—vaccines—is safe). We considered *holistic balance* and *naturalism* to be the most general and abstract beliefs among those we measured; followed by theories about parenting and medicine; then specific beliefs about vaccines, diseases, and the infant immune system; and finally our outcome of interest, *vaccine intentions*—the most concrete measurement of a specific intended action.

We used this sorting to induce a partial ordering of these 14 beliefs, stipulating that directed edges that violated this ordering must not appear in the final network of beliefs (e.g., that there should be no edge from *vaccine intentions* to *naturalism*, although there could be an edge from *naturalism* to *vaccine intentions*).

To conduct an efficient search through the super-exponential space of DAGs, we tested several learning algorithms implemented in the “bnlearn” R package (Scutari, 2010) and evaluated their performance through cross validation in our training split (see SI). Following this analysis, we chose to fit our model with the score-based “hill-climbing” algorithm, scoring models via the Bayesian Information Criteria, an asymptotic estimate of the likelihood of the data under a given graph structure. This produced the network shown in Figure 1. See SI for more detailed explanations of these modeling choices.

Some caution should be exercised in interpreting the relationships in the network. Due to Bayesian networks' tight connections with structural causal networks, it is tempting to interpret the edges in this network as representing a mental causal model. But, in some cases these relationships are better thought of as probabilistic dependencies or “influence” relations (Williamson, 2001). For instance, intuitively we might imagine that vaccines having toxins could cause them to be dangerous and ineffective. These nodes are connected in the model, but the edges between them run in the opposite directions, and therefore do not support a clear causal interpretation. In other cases, our data and explicit constraints do not perfectly identify the directions of the edges. This is the case for two edges (Naturalism →  Holistic Balance and Medical Skepticism → Parental Expertise; see supplemental implementation for details). In both cases, we do not feel it is intuitive which direction the edge should flow in, nor even that it should be directed at all; we might even speculate there is an additional unmeasured variable that connects these beliefs and that would best account for their association.

Bearing these qualifications in mind, we see this Bayesian network as a limited but plausible cognitive model of these beliefs.

## Study 2

In Study 2 we used this model to understand belief revision in the context of an intervention highlighting the danger of measles, mumps, and rubella.

### Method

Procedures for Phase 1 were nearly identical to Study 1, but the debriefing statement was moved to the end of Phase 2. In Phase 2 (XX days later), participants completed a study very similar to Horne et al.’s (2015) original intervention study. Participants were randomly assigned to either the disease risk condition or the No Intervention condition, with the constraint that the distributions of participants’ Phase 1 *vaccine intentions* scores should be similar across the two conditions; we accomplished this by stratifying participants into three groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.

Participants (n = XX passed attention checks in total) in the intervention conditions were presented with a version of Horne et al.’s  “disease risk” intervention, modified to present subparts in a fixed (rather than randomized) order, with slight changes to wording to improve clarity, and with a final statement summarizing the take-home message of the intervention; see SI. They then completed the same 14 belief scales and demographic questions that they had completed in Phase 1.

Participants in the No Intervention condition completed the belief scales and demographics questions without reading any material first.

### Analyses

*Regression analyses*. We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the *Vaccination Intentions* scale items, using the “brms” package for R (Buerkner, 2017). We regressed responses on phase (Phase 1 vs. 2, dummy-coded with Phase 1 as the baseline), condition (dummy-coded with the disease risk condition as the baseline, so as to assess difference scores in our condition of primary interest), and the interaction between phase and condition. We included random intercepts by subject and scale item. In this model, the unique effect of the intervention on vaccination intention scores is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants). The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: *b* = -0.15, 95% CI: [-0.27, -0.04]). We consider this to be a full replication of Horne, Powell, et al.’s (2015) results. See Figure 3, panel A.

*Modeling belief revision.* To model the effects of the intervention presented in Study 2 on the intuitive theory surfaced in Study 1, we augmented the belief network representing the intuitive theory with an additional node representing the information about measles, mumps, and rubella presented in the intervention. This evidence node was added as a child of the *disease severity* node, allowing the intervention to act as virtual evidence for *disease severity* (following Pearl, 1988).

To compute the conditional probability table (CPT) for this new node as a function of *disease severity* beliefs, we estimated an evidence ratio based on participants’ pretest and posttest credences in *disease severity*. To so do, we made use of the log-odds expression of Bayes rule, with the following regression equation:

$$logit(posttest) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})$$

Where *x* was a binary variable representing the presence (1) or absence (0) of evidence at posttest, and participants’ prior and posterior (pretest and posttest) credences were transformed into log odds. This allowed us to estimate the log evidence ratio implied by participants’ reactions to the intervention. Then, we constructed a CPT consistent with that evidence ratio.

Using this augmented model, we are able to “condition” the model on this evidence node, and thereby predict how observing evidence will affect all of the beliefs in the network; see Figure 3, panel B.

Given that our cognitive model is parameterized via noisy-logical functions, it should be noted that the marginal predicted influence of each belief is closely related to its first-order correlation with disease severity. This is in keeping with the qualitative features of intuitive theories we laid out in the introduction, and we should expect this to hold true (on average) for any plausible model of an intuitive theory. However, future models with more complex or nuanced parameterizations could potentially make additional predictions not evident from first-order correlations, such as individualized predictions for how individuals or groups would respond to evidence.

## Studies 3a and 3b

In Studies 3a and 3b we developed a novel intervention targeting the misconception that vaccines contain dangerous toxins and used the model developed in Study 1 to predict the effects of this intervention.

### Methods

Study 3a and 3b tested the effects of a novel intervention aimed at dispelling concerns about toxic additives in vaccines. These studies followed similar design procedures as Study 2, with phase 2 conducted XX days after phase 1. In both Study 3a (April 2019; final n = XX) and Study 3b (May 2019; final n = XX) the vaccine toxin intervention was compared against no-intervention control.

### Analyses

*Regression analyses*. As they shared the same design, we combined data from studies 3a and 3b for analysis. As in study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine toxins intervention on participants’ *vaccination intentions* scores. The vaccine toxins intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: b = [statistics]); see Figure 5, panel A. However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: b = [statistics]), suggesting that these attitudes were also being influenced by other factors during the course of the study.

*Modeling belief revision.* To model the effect of the vaccine toxicity intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the vaccine toxicity intervention as a child of the vaccine toxins belief node (for details, see SI). This allowed us to predict how other beliefs in the network would change in light of the observed changes participant’s beliefs about whether vaccines contain dangerous toxins; see Figure 5, panel B.

## Study 4

In Study 4 we used the same model to understand belief revision in the context of the measles outbreaks of 2019.

### Participants and Methods

We contacted XXX of the 1130 participants who completed Study 1 and invited them to participate in Study 4, in which they completed the same 14 belief scales and answered questions about their exposure to media coverage of the measles outbreaks. Of these, 555 participants returned and XXX successfully completed the study including passing attention checks. These participants completed all 14 belief scales and also indicated whether they had seen or heard anything about measles in the news recently.

### Analyses

*Regression analyses*. Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (X 2017 vs. May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item. To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure. Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (stats); see Figure 6, panel A.

*Modeling belief revision*. To model the effects of news exposure we followed the same procedure as in previous studies, but here augmented the model with a node representing media exposure as a child of the *vaccine intentions* node (for details, see SI); see Figure 6, panel B.

### 2021-07-18 install-packages.R
add rsvg (necessary for exporting graphs)

@@ -10,6 +10,7 @@ package_list <- c(
   "kableExtra",
   "DiagrammeR",
   "DiagrammeRsvg",
+  "rsvg",
   "corrplot",
   "cowplot",
   "caret"

### 2021-07-18 paper/paper.Rmd
paper format fixes

@@
 output: pdf_document
+bibliography: "../supplement/references.bib"
+csl: "../supplement/pnas.csl"
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
+```
+
+```{r load-required-data, include=FALSE}
+
 ```
@@
 One remarkable feature of human psychology is our ability to form rich mental representations of what is true, how things work, and how best to navigate the world around us.
-Much of this type of thinking can be understood as deriving from people’s *intuitive theories*—explanatory frameworks, analogous to scientific theories, that capture the causal and logical structure of the world within a domain.
+Much of this type of thinking can be understood as deriving from people’s *intuitive theories*---explanatory frameworks, analogous to scientific theories, that capture the causal and logical structure of the world within a domain.
 From early in life, people are driven to seek out such causal explanations and to use their mental representations of these causal systems to explain, predict, and intervene in the world; and to make sense of new information and experiences.
@@
 Undervaccination resulted in outbreaks of measles affecting over 1000 children across the United States in 2019, and over 80,000 children across Europe in 2018 (WHO, 2018).
-Misconceptions about childhood vaccination—particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects—have proved remarkably difficult to correct (e.g., Betsch & Sachse, 2013; Horne, Powell, Hummel, & Holyoak, 2015).
+Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct (e.g., Betsch & Sachse, 2013; Horne, Powell, Hummel, & Holyoak, 2015).
 Sadly, only a handful of educational interventions have been found to improve vaccine attitudes (e.g., Horne et al., 2015; Vannice et al., 2011; Wallace et al., 2006; Dube et al., 2015).
@@
 Lewandowsky et al., 2012).
-Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems—intuitive theories—that guide how people interpret and respond to evidence (e.g., Lewandowsky et al., 2012; Jern et al., 2014; Gershman, 2019).
+Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence (e.g., Lewandowsky et al., 2012; Jern et al., 2014; Gershman, 2019).
 
@@
 
-Quine argued that all of one’s beliefs are intertwined in a “web of belief” (1951; 1970)—an apt metaphor for intuitive theories.
+Quine argued that all of one’s beliefs are intertwined in a “web of belief” (1951; 1970)---an apt metaphor for intuitive theories.
 Intuitive theories consist of relations between beliefs that specify how states of affairs causally, logically, or otherwise interconnect with one another.
@@
 Gopnik et al., 2004; Griffiths & Tenenbaum, 2005; Jern et al., 2012).
-The heart of a Bayesian Network is a graphical structure—not unlike a "web of belief"—that represents variables as nodes connected by edges, where those edges represent probabilistic or statistical relations.
+The heart of a Bayesian Network is a graphical structure ---not unlike a "web of belief"---that represents variables as nodes connected by edges, where those edges represent probabilistic or statistical relations.
 
-For example, the graph *FIRE → SMOKE* represents a Bayesian network capturing the understanding  that fire causes smoke.
+For example, the graph $\text{FIRE} \rightarrow \text{SMOKE}$ represents a Bayesian network capturing the understanding  that fire causes smoke.
 The example of cause and effect is especially intuitive, but edges in a Bayesian network need not be causal; they are better thought of as representing “influence relations,” which may also include relationships like logical implication and set membership (Williamson, 2001).
@@
 In Study 1, we used Bayesian network structure learning algorithms to develop a cognitive model of the relationships among 14 beliefs related to vaccine hesitancy in a large sample of people.
-In Study 2, we replicated the success of an existing intervention emphasizing the dangers of childhood diseases (Horne et al., 2015) and used our model to provide a more detailed understanding of *how* *and why* this intervention increases vaccine intentions and its effects on related beliefs.
+In Study 2, we replicated the success of an existing intervention emphasizing the dangers of childhood diseases (Horne et al., 2015) and used our model to provide a more detailed understanding of *how and why* this intervention increases vaccine intentions and its effects on related beliefs.
 In Study 3a and 3b, we drew inspiration from our model to create and validate the success of  a novel intervention aimed at debunking concerns about toxic additives.
@@
 
-### Study 1: Assessing and modeling intuitive theories of vaccination**
+### Study 1: Assessing and modeling intuitive theories of vaccination
 
@@
 
-The three nodes with direct connections to *vaccine intentions* are beliefs about *vaccine effectiveness*, *vaccine danger*, and the severity of childhood diseases (*disease severity*)—concrete beliefs that are, at face value, especially closely related to vaccination decisions.
+The three nodes with direct connections to *vaccine intentions* are beliefs about *vaccine effectiveness*, *vaccine danger*, and the severity of childhood diseases (*disease severity*) ---concrete beliefs that are, at face value, especially closely related to vaccination decisions.
 This gives us confidence that the model is capturing important relationships.
@@
 Other parts of the model shed new light on the role of lay theories in vaccination decisions.
-For example, *naturalism*—the general view that natural things are better than artificial things—appears to be strongly related to *medical skepticism* and *parental expertise*; all three of these abstract beliefs are related to concrete beliefs that, in turn, feed into participants’ vaccination intentions.
+For example, *naturalism* ---the general view that natural things are better than artificial things ---appears to be strongly related to *medical skepticism* and *parental expertise*; all three of these abstract beliefs are related to concrete beliefs that, in turn, feed into participants’ vaccination intentions.
 
@@
 For example, we originally speculated that dispelling misconceptions about the capacity of the infant immune system could promote positive attitudes toward vaccination.
-We were disappointed to observe the weak first-order correlation between this belief and *vaccine intentions* in our behavioral data (r = -.097 in our training split).
-The model sheds light on this surprising (lack of) relationship: Although the belief that the infant immune system is limited in capacity is positively related to the belief that vaccines strain the immune system—discouraging vaccination, as we had assumed—it also seems to promote the belief that childhood diseases have severe consequences for young children (*disease severity*), which might, in turn, encourage vaccination.
-These countervailing forces—which, on average, seem to have cancelled each other out in this sample—dissuaded us from our plan to develop an intervention aimed at dispelling misconceptions about limited capacity in order to encourage childhood vaccination.
+We were disappointed to observe the weak first-order correlation between this belief and *vaccine intentions* in our behavioral data (r = -.09 in our training split).
+The model sheds light on this surprising (lack of) relationship: Although the belief that the infant immune system is limited in capacity is positively related to the belief that vaccines strain the immune system---discouraging vaccination, as we had assumed---it also seems to promote the belief that childhood diseases have severe consequences for young children (*disease severity*), which might, in turn, encourage vaccination.
+These countervailing forces---which, on average, seem to have cancelled each other out in this sample---dissuaded us from our plan to develop an intervention aimed at dispelling misconceptions about limited capacity in order to encourage childhood vaccination.
 
@@
 Figure 3 shows the change in participants’ attitudes across all 14 belief scales, from pretest to posttest.
-As expected, the largest change was observed for *disease severity* beliefs—the belief directly targeted by the intervention.
+As expected, the largest change was observed for *disease severity* beliefs---the belief directly targeted by the intervention.
 Most importantly, the disease risk intervention significantly increased participant’s *vaccination intentions*, conceptually replicating earlier findings regarding this intervention (Horne et al., 2015).
@@
 
-How did this intervention—which focused solely on the dangers of childhood diseases—affect beliefs about *vaccine danger*, *medical skepticism*, *holistic balance*, and so on?
+How did this intervention---which focused solely on the dangers of childhood diseases---affect beliefs about *vaccine danger*, *medical skepticism*, *holistic balance*, and so on?
 One explanation is that this intervention provides direct evidence for *disease severity* beliefs and that other beliefs are revised as a result of their relationships with *disease severity* as captured in the intuitive theory.
 To examine this, we used the same model developed in Study 1 to simulate how the 13 other beliefs in the intuitive theory would change if we intervened directly on *disease severity* (see Methods).
-As shown in figure #, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (R = .86).
+As shown in Figure 3, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (R = .86).
 
@@
 The intervention developed by Horne et al.
-and employed in Study 2 is notable for being one of the few educational interventions shown to decrease vaccine hesitancy—but is disease severity the only (or most) effective target for educational interventions in this domain?
+and employed in Study 2 is notable for being one of the few educational interventions shown to decrease vaccine hesitancy---but is disease severity the only (or most) effective target for educational interventions in this domain?
 
-One advantage of having developed a formal, computational representation of a network of beliefs supporting vaccination decisions is that it can guide our search for effective interventions, allowing us to compare how interventions targeting each of these other beliefs might potentially change people’s vaccination intentions (see figure 4).
+One advantage of having developed a formal, computational representation of a network of beliefs supporting vaccination decisions is that it can guide our search for effective interventions, allowing us to compare how interventions targeting each of these other beliefs might potentially change people’s vaccination intentions (see Figure 4).
 Countering myths about toxic additives is one approach the model developed in Study 1 predicts should be effective.
@@
 We gave special attention to defusing concerns about the use of formaldehyde in vaccines because our assessment of anti-vaccination websites suggested that this was a particular concern for many vaccine skeptics.
-The intervention acknowledged that some vaccines contain trace amounts of formaldehyde, but also pointed out that formaldehyde is a naturally-occurring metabolic byproduct  **in all living things and that it is already present in children’s bodies (and even in foods like pears) in far larger quantities than contained in any vaccine.
+The intervention acknowledged that some vaccines contain trace amounts of formaldehyde, but also pointed out that formaldehyde is a naturally-occurring metabolic byproduct in all living things and that it is already present in children’s bodies (and even in foods like pears) in far larger quantities than contained in any vaccine.
 The full intervention text can be found in SI.
@@
 We conducted two preregistered experiments (3a and 3b) testing the effects of this novel intervention using the same pretest-posttest design as Study 2.
-Collapsing across these two studies, figure 5 shows the change in participants’ (n = XXX) attitudes across all 14 belief scales from pretest to posttest.
+Collapsing across these two studies, Figure 5 shows the change in participants’ (n = XXX) attitudes across all 14 belief scales from pretest to posttest.
 Most importantly, the Vaccine Ingredients intervention significantly improved participants’ vaccination intentions compared to the no-intervention control condition.
@@
 Nevertheless, the success of this intervention in changing people’s responses to our *vaccine intentions* scale highlights the potential of this computational, theory-based approach to understanding belief revision.
-This model allowed us to design a novel educational intervention focusing on vaccine ingredients that successfully changed participants’ beliefs in a domain where many previously-researched educational approaches have failed—while sparing the time and resources we might have otherwise expended on interventions which our model predicts are unlikely to be successful.
+This model allowed us to design a novel educational intervention focusing on vaccine ingredients that successfully changed participants’ beliefs in a domain where many previously-researched educational approaches have failed---while sparing the time and resources we might have otherwise expended on interventions which our model predicts are unlikely to be successful.
 
@@
 
-**Discussion**
+## Discussion
 
@@
 Using this model we were able to predict how these beliefs would be affected by controlled educational interventions as well as real-world events.
-Inspired by our findings and model, we developed an intervention targeting beliefs about toxins in vaccines and found it successfully increased people’s intentions to vaccinate their children—adding to the very short list of effective interventions in this domain.
+Inspired by our findings and model, we developed an intervention targeting beliefs about toxins in vaccines and found it successfully increased people’s intentions to vaccinate their children---adding to the very short list of effective interventions in this domain.
 
@@
 Modeling this intuitive theory formally as a Bayesian network allowed us to create a cognitive model that demonstrates these key features of intuitive theories quantitatively.
-Looking forward, this formal representation—though simplified and imperfect—lays a foundation for richer and more complex descriptions in the future: For instance, networks with richer parameterizations could capture how intuitive theories differ across individuals, opening up the possibility of fine-tuning predictions and perhaps even crafting tailored educational interventions for specific individuals or groups.
+Looking forward, this formal representation ---though simplified and imperfect ---lays a foundation for richer and more complex descriptions in the future: For instance, networks with richer parameterizations could capture how intuitive theories differ across individuals, opening up the possibility of fine-tuning predictions and perhaps even crafting tailored educational interventions for specific individuals or groups.
 
@@
 Intuitive theories are powerful cognitive tools, for better and for worse.
-Coherent networks of beliefs allow people to understand, predict, and navigate the world, but they can also sustain misconceptions and lead to suboptimal—even dangerous—decisions and behaviors.
+Coherent networks of beliefs allow people to understand, predict, and navigate the world, but they can also sustain misconceptions and lead to suboptimal---even dangerous---decisions and behaviors.
 Deciding to opt out of getting vaccinated against diseases like measles or COVID-19 is not only dangerous for the individual, but a serious threat to public health.
@@
 
-*Bayesian network parameterization*.
+#### Bayesian network parameterization.
+
 A Bayesian network is a directed acyclic graph that represents variables as nodes connected by directed edges.
@@
 The network’s directed edges encode conditional dependencies among variables, and many parameterizations for the individual families are possible.
-In our model, the probability of some “child” belief node *y* can be expressed as a noisy-logical function of the influence of one or more “parent” belief nodes *x*:
+In our model, the probability of some “child” belief node $y$ can be expressed as a noisy-logical function of the influence of one or more “parent” belief nodes $x$:
 
 $$P(y) = 1 \big[1-(1-w_0)\prod_i(1-w_i)^{x_i}\big]\prod_j(1-w_j)^{x_j}$$ 
-
-Here, each parent node *x* is either a generative (*i*) or preventive (*j*) influence, that generates or prevents the child node with some probability weight (*wi* or *wj*).
-The weight *w0* represents the “leak” probability, or the baseline probability that the child occurs without any other generating influences.
-The first term in brackets represents the probability that *y* is generated (or, put another way, that not all of the possible generating forces fail to generate it).
+Here, each parent node $x$ is either a generative ($i$) or preventive ($j$) influence, that generates or prevents the child node with some probability weight ($w_i$ or $w_j$).
+The weight $w_0$ represents the “leak” probability, or the baseline probability that the child occurs without any other generating influences.
+The first term in brackets represents the probability that $y$ is generated (or, put another way, that not all of the possible generating forces fail to generate it).
 The second term represents the probability that it is not then prevented (i.e., that all the preventing forces fail; see Maaskant & Druzdel, 2008).
@@
 
-*A cognitive model underlying the data model.* We aimed to represent not only the relationships among variables in the data but the *cognitive model* that gave rise to these observed relationships, i.e., the relationships among beliefs in the mind.
+#### A cognitive model underlying the data model.
+
+We aimed to represent not only the relationships among variables in the data but the *cognitive model* that gave rise to these observed relationships, i.e., the relationships among beliefs in the mind.
 We actually estimated two models: First, we estimated a data model assuming that participants possess a shared mental model from which they generate their responses to the belief scales.
-In this model, the *x* in the equation above corresponded to participants’ continuous responses to the belief scales (e.g.
+In this model, the $x$ in the equation above corresponded to participants’ continuous responses to the belief scales (e.g.
 a participants score for the *vaccine danger* scale).
-Then, from the parameters estimated in the data model we created a cognitive model of participants’ reasoning, where the *x* are binary, indicating whether that state of affairs obtains (e.g., whether “vaccines are dangerous”).
+Then, from the parameters estimated in the data model we created a cognitive model of participants’ reasoning, where the $x$ are binary, indicating whether that state of affairs obtains (e.g., whether “vaccines are dangerous”).
 We used this cognitive model to simulate how beliefs could change following exposure to evidence.
 
-*Structure learning, constrained by a “generative model principle.”* Rather than specifying a priori all of the connections among the 14 beliefs included in this study, we deployed Bayesian network structure learning to search for the most likely network structure given the observed correlations between beliefs—with the constraint that this structure conform to some of our strongest high-level intuitions about what an intuitive theory should look like in this domain.
+#### Structure learning, constrained by a “generative model principle.”
+
+Rather than specifying a priori all of the connections among the 14 beliefs included in this study, we deployed Bayesian network structure learning to search for the most likely network structure given the observed correlations between beliefs---with the constraint that this structure conform to some of our strongest high-level intuitions about what an intuitive theory should look like in this domain.
 
@@
 Cheng, 1997; Gopnik et al., 2004; Gerstenberg et al., 2021).
-We sorted the 14 measured beliefs into four tiers based on how general or abstract each belief was, reasoning that general and abstract states of affairs should be understood to cause (or otherwise generate) more specific and concrete states of affairs, so edges should flow from the general and abstract toward the specific and concrete (e.g., if natural things are better than artificial things, this should set an expectation about whether a specific class of artificial things—vaccines—is safe).
-We considered *holistic balance* and *naturalism* to be the most general and abstract beliefs among those we measured; followed by theories about parenting and medicine; then specific beliefs about vaccines, diseases, and the infant immune system; and finally our outcome of interest, *vaccine intentions*—the most concrete measurement of a specific intended action.
+We sorted the 14 measured beliefs into four tiers based on how general or abstract each belief was, reasoning that general and abstract states of affairs should be understood to cause (or otherwise generate) more specific and concrete states of affairs, so edges should flow from the general and abstract toward the specific and concrete (e.g., if natural things are better than artificial things, this should set an expectation about whether a specific class of artificial things--vaccines--is safe).
+We considered *holistic balance* and *naturalism* to be the most general and abstract beliefs among those we measured; followed by theories about parenting and medicine; then specific beliefs about vaccines, diseases, and the infant immune system; and finally our outcome of interest, *vaccine intentions*---the most concrete measurement of a specific intended action.
 
@@
 
-*Regression analyses*.
+#### Regression analyses.
+
 We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the *Vaccination Intentions* scale items, using the “brms” package for R (Buerkner, 2017).
@@
 
-*Modeling belief revision.* To model the effects of the intervention presented in Study 2 on the intuitive theory surfaced in Study 1, we augmented the belief network representing the intuitive theory with an additional node representing the information about measles, mumps, and rubella presented in the intervention.
+#### Modeling belief revision.
+
+To model the effects of the intervention presented in Study 2 on the intuitive theory surfaced in Study 1, we augmented the belief network representing the intuitive theory with an additional node representing the information about measles, mumps, and rubella presented in the intervention.
 This evidence node was added as a child of the *disease severity* node, allowing the intervention to act as virtual evidence for *disease severity* (following Pearl, 1988).
@@
 
-*Regression analyses*.
+#### Regression analyses.
+
 As they shared the same design, we combined data from studies 3a and 3b for analysis.
@@
 
-*Modeling belief revision.* To model the effect of the vaccine toxicity intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the vaccine toxicity intervention as a child of the vaccine toxins belief node (for details, see SI).
+#### Modeling belief revision.
+
+To model the effect of the vaccine toxicity intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the vaccine toxicity intervention as a child of the vaccine toxins belief node (for details, see SI).
 This allowed us to predict how other beliefs in the network would change in light of the observed changes participant’s beliefs about whether vaccines contain dangerous toxins; see Figure 5, panel B.
@@
 
-*Regression analyses*.
+#### Regression analyses.
+
 Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (X 2017 vs.
@@
 
-*Modeling belief revision*.
+#### Modeling belief revision.
+
 To model the effects of news exposure we followed the same procedure as in previous studies, but here augmented the model with a node representing media exposure as a child of the *vaccine intentions* node (for details, see SI); see Figure 6, panel B.

### 2021-07-18 paper/paper.Rmd
updated references

@@
 Much of this type of thinking can be understood as deriving from people’s *intuitive theories*---explanatory frameworks, analogous to scientific theories, that capture the causal and logical structure of the world within a domain.
-From early in life, people are driven to seek out such causal explanations and to use their mental representations of these causal systems to explain, predict, and intervene in the world; and to make sense of new information and experiences.
-(See Carey, 2009; Gelman & Legare, 2011; Gerstenberg & Tenenbaum; Gopnik & Wellman, 1994; Keil, 1994; Murphy & Medin, 1985; and Wellman & Gelman, 1992; for influential  treatments of this topic.)  Intuitive theories inform reasoning in a wide variety of domains, from reasoning about physical systems (e.g., Baillargeon, 2004; Battaglia, Hamrick, & Tenenbaum, 2013; Spelke, 1994; Ullman et al., 2017), to reasoning about biological processes (e.g., Carey, 1985, 2009; Medin & Atran, 1999) and about the contents of other people’s minds (e.g., Gopnik & Wellman, 1992; Wellman, 2015; Baker, Jara-Ettinger, Saxe, & Tenenbaum).
+From early in life, people are driven to seek out such causal explanations and to use their mental representations of these causal systems to explain, predict, and intervene in the world; and to make sense of new information and experiences [see @carey2009; @gelman.legare2011; @gerstenberg.etal2021; @gopnik.wellman1994; @keil1994; @murphy.medin1985; @wellman.gelman1992 for influential treatments of this topic].
+Intuitive theories inform reasoning in a wide variety of domains, from reasoning about physical systems [e.g., @baillargeon2004; @battaglia.etal2013; @spelke1994a; @ullman.etal2017], to reasoning about biological processes [e.g., @carey1985; @carey2009; @medin.atran1999] and about the contents of other people’s minds [e.g., @gopnik.wellman1994; @wellman2015; @baker.etal2017].
 
@@
 Undervaccination resulted in outbreaks of measles affecting over 1000 children across the United States in 2019, and over 80,000 children across Europe in 2018 (WHO, 2018).
-Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct (e.g., Betsch & Sachse, 2013; Horne, Powell, Hummel, & Holyoak, 2015).
-Sadly, only a handful of educational interventions have been found to improve vaccine attitudes (e.g., Horne et al., 2015; Vannice et al., 2011; Wallace et al., 2006; Dube et al., 2015).
+Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct [e.g., @betsch.sachse2013; @horne.etal2015].
+Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @horne.etal2015; @vannice.etal2011; @wallace.etal2006; @dube.etal2015].
 This is especially  sobering in the context of the coronavirus pandemic: reluctance to be vaccinated against COVID-19 threatens our ability to end a pandemic that has already claimed millions of lives around the world.
 
-The difficulty of convincing people to vaccinate themselves and their children illustrates a general pattern of findings showing that people often do not respond to evidence in ways that educators might wish (e.g.
-Lewandowsky et al., 2012).
-Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence (e.g., Lewandowsky et al., 2012; Jern et al., 2014; Gershman, 2019).
+The difficulty of convincing people to vaccinate themselves and their children illustrates a general pattern of findings showing that people often do not respond to evidence in ways that educators might wish [e.g.
+@lewandowsky.etal2012].
+Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence [e.g., @lewandowsky.etal2012; @jern.etal2014; @gershman2019].
 
@@
 The way in which evidence affects any particular belief is unavoidably shaped by other interrelated beliefs.
-Duhem (1954) and Quine (1951) famously argued that scientific theories necessarily incorporate *auxiliary hypotheses* that influence how observations are interpreted: When an observation is inconsistent with a hypothesis under certain auxiliary assumptions, a scientist cannot necessarily know whether to revise the hypothesis or the auxiliary assumptions.
-Similarly, we argue that intuitive theories incorporate auxiliary beliefs that affect how other beliefs are revised in light of evidence (also see Gershman, 2019).
+Duhem [-@duhem1954] and Quine [-@quine1951] famously argued that scientific theories necessarily incorporate *auxiliary hypotheses* that influence how observations are interpreted: When an observation is inconsistent with a hypothesis under certain auxiliary assumptions, a scientist cannot necessarily know whether to revise the hypothesis or the auxiliary assumptions.
+Similarly, we argue that intuitive theories incorporate auxiliary beliefs that affect how other beliefs are revised in light of evidence [also see @gershman2019].
 
@@
 
-We argue that correcting misconceptions requires presenting evidence in a way that is sensitive to and persuasive within the broader conceptual context in which those misconceptions reside (see Gershman, 2019; Weisman & Markman, 2017).
+We argue that correcting misconceptions requires presenting evidence in a way that is sensitive to and persuasive within the broader conceptual context in which those misconceptions reside [see @gershman2019; @weisman.markman2017].
 Understanding the revision of any one specific belief (e.g., a misconception like *vaccines are dangerous*) demands a holistic understanding of the wider set of interrelated beliefs that make up people's intuitive theories.
@@
 
-Quine argued that all of one’s beliefs are intertwined in a “web of belief” (1951; 1970)---an apt metaphor for intuitive theories.
+Quine argued that all of one’s beliefs are intertwined in a “web of belief” [@quine1951; @quine.ullian1978]---an apt metaphor for intuitive theories.
 Intuitive theories consist of relations between beliefs that specify how states of affairs causally, logically, or otherwise interconnect with one another.
@@
 Here, we sought to formalize this understanding of intuitive theories by representing an intuitive theory as a Bayesian network.
-Originally designed as tools for artificial intelligence (Pearl, 1988), Bayesian networks are a class of probabilistic graphical models that have been deployed widely across cognitive science (e.g.
-Gopnik et al., 2004; Griffiths & Tenenbaum, 2005; Jern et al., 2012).
+Originally designed as tools for artificial intelligence [@pearl1988], Bayesian networks are a class of probabilistic graphical models that have been deployed widely across cognitive science [e.g.
+@jern.etal2014; @gopnik.etal2004; @griffiths.tenenbaum2005].
 The heart of a Bayesian Network is a graphical structure ---not unlike a "web of belief"---that represents variables as nodes connected by edges, where those edges represent probabilistic or statistical relations.
@@
 For example, the graph $\text{FIRE} \rightarrow \text{SMOKE}$ represents a Bayesian network capturing the understanding  that fire causes smoke.
-The example of cause and effect is especially intuitive, but edges in a Bayesian network need not be causal; they are better thought of as representing “influence relations,” which may also include relationships like logical implication and set membership (Williamson, 2001).
+The example of cause and effect is especially intuitive, but edges in a Bayesian network need not be causal; they are better thought of as representing “influence relations,” which may also include relationships like logical implication and set membership [@williamson2001].
 This influence relationship is represented as a probabilistic function, where the probability of smoke depends on the probability of fire.
@@
 Roughly, when the relationships among beliefs are unknown, we can use the qualitative features of intuitive theories to *infer* the structure of an intuitive theory from observed correlations among beliefs.
-Structure learning algorithms (see Scutari & Denis, 2021) provide a means for searching through the (super-exponentially large) possible space of Bayesian networks to find the structure most likely to have generated some observed data.
-These approaches allow us to scale the Bayesian network modelling framework beyond the simple models characteristic of early computational work on intuitive theories (e.g., Griffiths & Tenenbaum, 2005).
+Structure learning algorithms [see @scutari.denis2021] provide a means for searching through the (super-exponentially large) possible space of Bayesian networks to find the structure most likely to have generated some observed data.
+These approaches allow us to scale the Bayesian network modelling framework beyond the simple models characteristic of early computational work on intuitive theories [e.g., @griffiths.tenenbaum2005].
 
@@
 In Study 1, we used Bayesian network structure learning algorithms to develop a cognitive model of the relationships among 14 beliefs related to vaccine hesitancy in a large sample of people.
-In Study 2, we replicated the success of an existing intervention emphasizing the dangers of childhood diseases (Horne et al., 2015) and used our model to provide a more detailed understanding of *how and why* this intervention increases vaccine intentions and its effects on related beliefs.
+In Study 2, we replicated the success of an existing intervention emphasizing the dangers of childhood diseases [@horne.etal2015] and used our model to provide a more detailed understanding of *how and why* this intervention increases vaccine intentions and its effects on related beliefs.
 In Study 3a and 3b, we drew inspiration from our model to create and validate the success of  a novel intervention aimed at debunking concerns about toxic additives.
@@
 Beyond this, we theorized that participants’ understanding of the infant immune system might be relevant, including beliefs that (6) the infant immune system is weak (*IIS: weakness*); (7) the infant immune system is limited in its capacity and can be easily overwhelmed (*IIS: limited capacity*); and (8) vaccines strain the infant immune system (*IIS: vaccines strain*).
-We also included general theories about parenting and medicine: (11) general *parental protectiveness*; (12) *parental expertise*, namely the belief that parents usually know more about their children’s health than medical experts; and (13) *medical skepticism*, including concerns about pharmaceutical companies and corruption in the medical community; and two two broad worldviews: (9) *naturalism*, a general preference for natural over artificial things; and (10) *holistic balance*, one important aspect of attitudes toward alternative medicine (e.g., “The body is essentially self-healing and the task of a health care provider is to assist the healing process”; McFadden, Hernandez, & Ito, 2010).
+We also included general theories about parenting and medicine: (11) general *parental protectiveness*; (12) *parental expertise*, namely the belief that parents usually know more about their children’s health than medical experts; and (13) *medical skepticism*, including concerns about pharmaceutical companies and corruption in the medical community; and two two broad worldviews: (9) *naturalism*, a general preference for natural over artificial things; and (10) *holistic balance*, one important aspect of attitudes toward alternative medicine (e.g., “The body is essentially self-healing and the task of a health care provider is to assist the healing process”; [@mcfadden.etal2010]).
 
@@
 One of the few successful educational interventions in this domain was tested by Horne et al.
-(2015), who found that emphasizing the dangers of preventable diseases like mumps, measles, and rubella improved participants’ attitudes toward vaccines.
+[-@horne.etal2015], who found that emphasizing the dangers of preventable diseases like mumps, measles, and rubella improved participants’ attitudes toward vaccines.
 Their intervention included descriptions of the symptoms of mumps, measles, and rubella; vivid photos of children suffering from these diseases; and a brief story from the perspective of a parent whose child was hospitalized with measles (see SI).
@@
 
-In Study 2, we used the belief network established in Study 1 to predict how Horne et al.’s (2015) intervention would affect the beliefs in this network, including people’s intentions to vaccinate their children.
+In Study 2, we used the belief network established in Study 1 to predict how Horne et al.’s [-@horne.etal2015] intervention would affect the beliefs in this network, including people’s intentions to vaccinate their children.
 Participants completed the 14 belief scales from Study 1, then returned two days later to complete either the disease risk intervention or a no-intervention control, followed by the same 14 belief scales.
@@
 As expected, the largest change was observed for *disease severity* beliefs---the belief directly targeted by the intervention.
-Most importantly, the disease risk intervention significantly increased participant’s *vaccination intentions*, conceptually replicating earlier findings regarding this intervention (Horne et al., 2015).
+Most importantly, the disease risk intervention significantly increased participant’s *vaccination intentions*, conceptually replicating earlier findings regarding this intervention [@horne.etal2015].
 
@@
 The intervention developed by Horne et al.
-and employed in Study 2 is notable for being one of the few educational interventions shown to decrease vaccine hesitancy---but is disease severity the only (or most) effective target for educational interventions in this domain?
+[-@horne.etal2015] and employed in Study 2 is notable for being one of the few educational interventions shown to decrease vaccine hesitancy---but is disease severity the only (or most) effective target for educational interventions in this domain?
 
@@
 More broadly, the approaches we have introduced here may shed light on long-standing theoretical questions about belief revision.
-Many researchers have argued that people's belief updating is subject to various biases, or is skewed by motivational factors (e.g.
-Kahan, 2013; Flynn et al., 2017; Kunda, 1990).
-Yet many of the phenomena traditionally taken as evidence for these theories can also be explained by normative models of belief revision, so long as we are willing to posit that other auxiliary beliefs can affect the relationships between a belief and evidence (e.g., Gershman, 2019; Jern et al., 2012).
+Many researchers have argued that people's belief updating is subject to various biases, or is skewed by motivational factors [e.g.
+@kahan2013; @flynn.etal2017; @kunda1990].
+Yet many of the phenomena traditionally taken as evidence for these theories can also be explained by normative models of belief revision, so long as we are willing to posit that other auxiliary beliefs can affect the relationships between a belief and evidence [e.g., @jern.etal2014; @gershman2019].
 Adjudicating between competing views of belief revision will require us to move beyond minimal models and illustrative simulations by assessing whether people actually do hold these auxiliary beliefs, and whether their broader belief systems behave according to the rules of probabilistic inference.
@@
 Though these studies were conducted before the onset of the COVID-19 pandemic and focused on childhood diseases, many similar concerns are likely to animate hesitancy toward COVID-19 vaccines, and certain insights might be readily applied to addressing them.
-For one, in the spirit of Horne et al.’s (2015) disease risk intervention, we suspect that education focused on how severely ill many people become and the prevalence of long-term health problems following even mild cases of COVID-19 might encourage people to accept coronavirus vaccines.
+For one, in the spirit of Horne et al.’s [-@horne.etal2015] disease risk intervention, we suspect that education focused on how severely ill many people become and the prevalence of long-term health problems following even mild cases of COVID-19 might encourage people to accept coronavirus vaccines.
 
@@
 Beyond this, in many countries COVID-19 and vaccines against it have been politicized in a way that other public health concerns are not.
-Political affiliations often imply concrete beliefs about the world that could be incorporated into a model of an intuitive theory: for instance, the belief that the coronavirus pandemic is a “hoax.” However, these affiliations are also associated with social commitments, personal values, and other identity-constituting beliefs that may be more challenging to  capture in an intuitive theory as we have conceived of it here (Van Leeuwen, 2014).
+Political affiliations often imply concrete beliefs about the world that could be incorporated into a model of an intuitive theory: for instance, the belief that the coronavirus pandemic is a “hoax.” However, these affiliations are also associated with social commitments, personal values, and other identity-constituting beliefs that may be more challenging to  capture in an intuitive theory as we have conceived of it here [@vanleeuwen2014].
 Relatedly, the coronavirus pandemic has raised public awareness of many social issues that could also play an important role in people's intuitive theories of vaccination more broadly.
@@
 
-We drew on a variety of sources, including academic articles on anti-vaccine skepticism (e.g., Dube et al., 2015; Larson et al.
-2015; Salmon et al., 2015; Williams, 2014), anti-vaccine websites, and a qualitative survey with self-identified vaccine skeptics (*n*=16) via Amazon Mechanical Turk (MTurk) to generate a list of beliefs that might influence people’s decisions about whether to vaccinate their children (*vaccine intentions*): *vaccine danger*, *toxic additives in vaccines*, *vaccine effectiveness*, *disease rarity*, *disease severity, infant immune system (IIS): weakness*, *IIS: limited capacity*, *IIS: vaccines strain*, *parental protectiveness*, *parental expertise*, *medical skepticism*, *naturalism*, and *holistic balance*.
+We drew on a variety of sources, including academic articles on anti-vaccine skepticism [e.g.,  @dube.etal2015; @larson.etal2015; @salmon.etal2015; @williams2014], anti-vaccine websites, and a qualitative survey with self-identified vaccine skeptics (*n*=16) via Amazon Mechanical Turk (MTurk) to generate a list of beliefs that might influence people’s decisions about whether to vaccinate their children (*vaccine intentions*): *vaccine danger*, *toxic additives in vaccines*, *vaccine effectiveness*, *disease rarity*, *disease severity, infant immune system (IIS): weakness*, *IIS: limited capacity*, *IIS: vaccines strain*, *parental protectiveness*, *parental expertise*, *medical skepticism*, *naturalism*, and *holistic balance*.
 (See main text for descriptions, and SI for the items included in these scales.) We translated these qualitative insights into 14 psychometrically-valid scales; each scale measured agreement with 4-6 statements, including at least one reverse-coded item, and was highly reliable (All Cronbach’s $\alpha \geq .73$).
-We developed 13 of these scales, and included one preexisting scale (the “holistic balance” subscale from McFadden et al., 2010).
+We developed 13 of these scales, and included one preexisting scale [the “holistic balance” subscale from @mcfadden.etal2010].
 
@@
 The first term in brackets represents the probability that $y$ is generated (or, put another way, that not all of the possible generating forces fail to generate it).
-The second term represents the probability that it is not then prevented (i.e., that all the preventing forces fail; see Maaskant & Druzdel, 2008).
+The second term represents the probability that it is not then prevented [i.e., that all the preventing forces fail; see @maaskant.druzdzel2008].
 
@@
 
-In particular, we applied what we call the “generative model principle,” specifying that influence relations (edges) should flow from causes (or other generating states of affairs) to effects; instilling a core assumption in research on intuitive theories and causal explanatory reasoning (e.g.
-Cheng, 1997; Gopnik et al., 2004; Gerstenberg et al., 2021).
+In particular, we applied what we call the “generative model principle,” specifying that influence relations (edges) should flow from causes (or other generating states of affairs) to effects; instilling a core assumption in research on intuitive theories and causal explanatory reasoning [e.g.
+@gopnik.etal2004; @gerstenberg.etal2021; @cheng1997].
 We sorted the 14 measured beliefs into four tiers based on how general or abstract each belief was, reasoning that general and abstract states of affairs should be understood to cause (or otherwise generate) more specific and concrete states of affairs, so edges should flow from the general and abstract toward the specific and concrete (e.g., if natural things are better than artificial things, this should set an expectation about whether a specific class of artificial things--vaccines--is safe).
@@
 
-To conduct an efficient search through the super-exponential space of DAGs, we tested several learning algorithms implemented in the “bnlearn” R package (Scutari, 2010) and evaluated their performance through cross validation in our training split (see SI).
+To conduct an efficient search through the super-exponential space of DAGs, we tested several learning algorithms implemented in the “bnlearn” R package [@scutari2010] and evaluated their performance through cross validation in our training split (see SI).
 Following this analysis, we chose to fit our model with the score-based “hill-climbing” algorithm, scoring models via the Bayesian Information Criteria, an asymptotic estimate of the likelihood of the data under a given graph structure.
@@
 Due to Bayesian networks' tight connections with structural causal networks, it is tempting to interpret the edges in this network as representing a mental causal model.
-But, in some cases these relationships are better thought of as probabilistic dependencies or “influence” relations (Williamson, 2001).
+But, in some cases these relationships are better thought of as probabilistic dependencies or “influence” relations [@williamson2001].
 For instance, intuitively we might imagine that vaccines having toxins could cause them to be dangerous and ineffective.
@@
 In other cases, our data and explicit constraints do not perfectly identify the directions of the edges.
-This is the case for two edges (Naturalism →  Holistic Balance and Medical Skepticism → Parental Expertise; see supplemental implementation for details).
+This is the case for two edges (Naturalism $\rightarrow$  Holistic Balance and Medical Skepticism $\rightarrow$ Parental Expertise; see supplemental implementation for details).
 In both cases, we do not feel it is intuitive which direction the edge should flow in, nor even that it should be directed at all; we might even speculate there is an additional unmeasured variable that connects these beliefs and that would best account for their association.
@@
 
-We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the *Vaccination Intentions* scale items, using the “brms” package for R (Buerkner, 2017).
+We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the *Vaccination Intentions* scale items, using the “brms” package for R [@burkner2017].
 We regressed responses on phase (Phase 1 vs.
@@
 The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: *b* = -0.15, 95% CI: [-0.27, -0.04]).
-We consider this to be a full replication of Horne, Powell, et al.’s (2015) results.
+We consider this to be a full replication of Horne, Powell, et al.’s [-@horne.etal2015] results.
 See Figure 3, panel A.
@@
 To model the effects of the intervention presented in Study 2 on the intuitive theory surfaced in Study 1, we augmented the belief network representing the intuitive theory with an additional node representing the information about measles, mumps, and rubella presented in the intervention.
-This evidence node was added as a child of the *disease severity* node, allowing the intervention to act as virtual evidence for *disease severity* (following Pearl, 1988).
+This evidence node was added as a child of the *disease severity* node, allowing the intervention to act as virtual evidence for *disease severity* [following @pearl1988].
 
@@
 To model the effects of news exposure we followed the same procedure as in previous studies, but here augmented the model with a node representing media exposure as a child of the *vaccine intentions* node (for details, see SI); see Figure 6, panel B.
+
+\newpage
+# References

### 2021-07-18 supplement/supplement-main.Rmd
updated references

@@
 
-To conduct an efficient search through the super-exponential space of DAGs, we tested several variants of two structure learning algorithms implemented in the “bnlearn” R package [@scutari2010a].
+To conduct an efficient search through the super-exponential space of DAGs, we tested several variants of two structure learning algorithms implemented in the “bnlearn” R package [@scutari2010].
 The first is a purely score-based “hill-climbing” algorithm  and the second was a hybrid algorithm that combined the hill-climbing algorithm with a prior “restriction” phase that pruned down the space of DAGs.

### 2021-07-18 paper/paper.Rmd
added ref

@@
 Even before the coronavirus pandemic, misconceptions about vaccine safety drove public health crises around the world.
-Undervaccination resulted in outbreaks of measles affecting over 1000 children across the United States in 2019, and over 80,000 children across Europe in 2018 (WHO, 2018).
+Undervaccination resulted in outbreaks of measles affecting over 1000 children across the United States in 2019, and over 80,000 children across Europe in 2018 [@thornton2019].
 Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct [e.g., @betsch.sachse2013; @horne.etal2015].

### 2021-07-20 supplement/supplement-main.Rmd
tweaks to plots

--- 2021-07-17 supplement/supplement-main.Rmd
@@
 author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
-date: "Jul 17, 2021 (DRAFT)"
+date: "Jul 18, 2021 (DRAFT)"
 output:
@@
 library(DiagrammeRsvg)
+library(rsvg)
 
@@
 z2$nodes_df$shape <- "ellipse"
-z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$label=="Vaccination\nIntentions", "grey","white")
+z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$label=="Vaccination\nIntentions", 
+                                "#fffaba","white")
+z2$nodes_df$fillalpha <- 0.1
 z2$nodes_df$fixedsize <- FALSE
@@
 Edge color indicates frequency with which edges appeared when conducting search across 200 bootstrap replicates.
-Only edges appearing in at least 20\\% of graphs are shown."}
+Only edges appearing in at least 20\\% of graphs are shown.
+Our primary outcome of interest, vaccination intentions, is highlighted in yellow."}
 
@@
 Though we found the uncovered network structure to be quite revealing and informative, there are also some important limitations that should be acknowledged.
-In particular, the edges from the vaccine danger and vaccine effectiveness nodes to the vaccine toxicity node strike us as counterintuitive.
+In particular, the edges from the vaccine danger and vaccine effectiveness nodes to the _vaccine toxicity_ node strike us as counterintuitive.
 Intuitively, we might imagine that vaccines having toxins could cause them to be dangerous and ineffective.
@@
 The equivalence class for our model can be represented as a CPDAG with 14 directed edges and 15 undirected edges—indicating that the data do not constrain the directions of 15 of the edges in the final model.
-However, 10 of these edges’ directions are directly constrained by our top-down "generative model" constraints, which in turn constrains all but two of the remaining undirected edges, including the counterintuitive edges running toward vaccine toxins.
+However, 10 of these edges’ directions are directly constrained by our top-down "generative model" constraints, which in turn constrains all but two of the remaining undirected edges, including the counterintuitive edges running toward _vaccine toxicity_.
 This is also reflected in a bootstrapping analysis applying our chosen structure learning algorithm against 1000 bootstrapped replicates of our data.
-We found that the direction of some edges within the graph differed across bootstrapped runs (Holistic balance -- naturalism, medical skepticism -- parental expertise), but that these unintuitive relationships surrounding vaccine toxins were robust.
+We found that the direction of some edges within the graph differed across bootstrapped runs (Holistic balance -- naturalism, medical skepticism -- parental expertise), but that these unintuitive relationships surrounding _vaccine toxicity_ were robust.
 
@@
 ```{r, include=F}
-
 h <- HydeNetwork(as.formula(bnlearn_to_hyde_string(main_model)))
@@
 ```{r main_model_plot, include=F}
-
 z <- custom_plot.HydeNetwork(h, attr_theme="tb")
@@
 z$nodes_df$shape <- "ellipse"
-z$nodes_df$fillcolor <- ifelse(z$nodes_df$label=="Vaccination\nIntentions", "grey","white")
+z$nodes_df$fillcolor <- ifelse(z$nodes_df$label=="Vaccination\nIntentions", "#fffaba","white")
 z$nodes_df$fixedsize <- FALSE
@@
 ```{r disp-maingraph, echo=F, fig.width=8, fig.height=5, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
-Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links."}
+Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links.
+Our primary outcome of interest, vaccination intentions, is highlighted in yellow."}
 
@@
 To model the effects of participants observing evidence, we augmented the Bayesian network representing the cognitive model (shown in Figure \@ref(fig:disp-maingraph)) with an additional node representing the evidence.
-For instance, to model the effects of the “disease risk” intervention (Study 2), we added an evidence node as a child of “disease severity,” acting as virtual evidence for this node.
+For instance, to model the effects of the “Disease Risk” intervention (Study 2), we added an evidence node as a child of “disease severity,” acting as virtual evidence for this node.
 To compute the CPT for this node as a function of disease severity beliefs, we estimated an _evidence ratio_ based on participants’ pretest and posttest credences in disease severity.
@@
   cores = 6,
-  control = list(adapt_delta=.99),
+  # control = list(adapt_delta=.99),
   seed = 46179,
@@
 
-We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the _Vaccination Intentions_ scale items, using the “brms” package for R [@burkner2017].
+We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the Disease Risk intervention on responses to the _Vaccination Intentions_ scale items, using the “brms” package for R [@burkner2017].
 We regressed responses on phase (Phase 1 vs.
@@
 In this model, the unique effect of the intervention on vaccination intention responses is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants).
-The disease risk intervention increased participants’ vaccination intention ratings (see Table \@ref(tab:s2_model)).
+The Disease Risk intervention increased participants’ vaccination intention ratings (see Table \@ref(tab:s2_model)).
 We consider this to be a full replication of Horne et al.’s [-@horne.etal2015] results.
@@
 The maximum likelihood estimate of the evidence ratio was XXX.
-To simulate the impacts of this evidence, we supplied virtual evidence to the disease severity node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
+To simulate the impacts of this evidence, we supplied virtual evidence to the _disease severity_ node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
 Given that our cognitive model is parameterized via noisy-logical functions, the predicted influence of each belief is closely related to its first-order correlation.
 
-Figure \@ref(fig:s2_plot) (right) shows the correlation between predicted and observed belief changes conditional on the disease risk intervention.
+Figure \@ref(fig:s2_plot) (right) shows the correlation between predicted and observed belief changes conditional on the Disease Risk intervention.
 
@@
 ```{r echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiment 2.
-Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
-Right, mean observed and model predicted change scores for the disease risk intervention condition.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
+Right, mean observed and model predicted change scores for the Disease Risk intervention condition.
 In both plots, error bars represent 95\\% confidence intervals."}
@@
 library(patchwork)
+
+s2_scale_order <- s2_scored %>% 
+  drop_na(scale) %>% 
+  spread(phase, mean) %>%
+  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
+  mutate(diff = post-pre) %>% 
+  mutate(scale = recode_nodes2(scale)) %>% 
+  group_by(condition, scale) %>%
+  summarize(M = mean(diff, na.rm=TRUE)) %>%
+  ungroup() %>%
+  group_by(scale) %>%
+  summarize(diff_diff = mean(M, na.rm = T)) %>%
+  ungroup() %>%
+  arrange(desc(diff_diff)) %>% # descending because intervention is expected to increase disease risk beliefs
+  mutate(order = 1:nrow(.))
 
@@
     scale = recode_nodes2(scale),
-    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
-    ) %>% 
+    condition = recode_factor(condition, 
+                              "noInterv" = "Control",
+                              .default = "Disease Risk")) %>% 
   group_by(condition, scale) %>%
   summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
-  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition, shape=condition)) +
+  ungroup() %>%
+  left_join(s2_scale_order) %>%
+  ggplot(aes(x = reorder(scale,order), y = M, 
+             ymin = M-se*2, ymax=M+se*2, 
+             color=condition, shape=condition)) +
+  scale_x_discrete() +
+  annotate("rect", 
+           xmin = s2_scale_order %>%
+             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.25,
+           xmax = s2_scale_order %>%
+             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.25,
+           ymin = -Inf,
+           ymax = Inf,
+           fill = "#fffaba") +
   geom_pointrange(position=position_dodge(width=.25)) +
@@
   scale_color_manual(values=c("#0067b1","#c50024")) +
-  scale_shape_manual(values=c(17,16)) +
+  scale_shape_manual(values=c(16,17)) +
   theme_bw(base_size=11) +
@@
     panel.grid = element_blank(),
-    legend.position = c(.35,.9),
+    legend.position = c(.5,.9),
     legend.direction = "horizontal",
+    legend.background = element_rect(fill = NA),
     aspect.ratio=.5
     ) +
-  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention", shape="Intervention")
+  labs(title="A", y = "Mean difference", x = "Belief scale", 
+       color="Intervention", shape="Intervention")
 
@@
 
-cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
+cor_val <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
 
@@
 Full text of this intervention is available in Appendix C of these supplementary materials.
-In both studies, participants were randomly assigned to either a no-intervention control condition or to the novel vaccine toxins intervention.
+In both studies, participants were randomly assigned to either a no-intervention control condition or to the novel Vaccine Ingredients intervention.
 
@@
 However, for full transparency we first describe analyses for these studies individually.
-As in Experiment 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine toxins intervention on participants’ _Vaccination Intentions_ scores.
-The vaccine toxins intervention improved participant’s vaccination intention scores relative to a no-intervention control condition.
+As in Experiment 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the Vaccine Ingredients intervention on participants’ _Vaccination Intentions_ scores.
+The Vaccine Ingredients intervention improved participant’s vaccination intention scores relative to a no-intervention control condition.
 Tables below show the results of these regression analyses for Experiment 3a, 3b, and the two studies combined.
-In each analysis, the coefficient representing the interaction between phase and condition is positive and credibly differs from zero, indicating that the vaccine toxins intervention positively impacted vaccination intentions.
+In each analysis, the coefficient representing the interaction between phase and condition is positive and credibly differs from zero, indicating that the Vaccine Ingredients intervention positively impacted vaccination intentions.
 
@@
   mutate(
+    study = relevel(factor(study), ref="A"),
     phase = relevel(factor(phase), ref="pre"),
@@
 
+contrasts(s3_reg$study) <- contr.sum(2)
+
 fit_s3_vaccIntent <- brm(
-  response ~ phase*condition + (1|item) + (1|workerId),
+  response ~ phase*condition*study + (1|item) + (1|workerId),
   family = cumulative("logit"),
@@
   cores = 6,
-  control = list(adapt_delta=.95),
+  # control = list(adapt_delta=.99),
   seed = 69568,
@@
   cores = 6,
-  control = list(adapt_delta=.99),
+  # control = list(adapt_delta=.99),
   seed = 69568,
@@
 
-To model the effect of the vaccine toxicity intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the vaccine toxicity intervention as a child of the vaccine toxins belief node.
-The maximum likelihood estimate of the evidence ratio for the vaccine toxicity intervention was XXX.
-To simulate the impacts of this evidence, we supplied virtual evidence to the disease severity node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
-
-Figure \@ref(fig:s3_plot) (right) shows the correlation between predicted and observed belief changes conditional on the vaccine toxicity intervention.
+To model the effect of the Vaccine Ingredients intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the Vaccine Ingredients intervention as a child of the _vaccine toxicity_ belief node.
+The maximum likelihood estimate of the evidence ratio for the Vaccine Ingredients intervention was XXX.
+To simulate the impacts of this evidence, we supplied virtual evidence to the _vaccine toxicity_ node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
+
+Figure \@ref(fig:s3_plot) (right) shows the correlation between predicted and observed belief changes conditional on the Vaccine Ingredients intervention.
 
 ```{r s3_plot, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
-Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
-Right, mean observed and model predicted change scores for the toxins intervention condition.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
+Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition.
 In both plots, error bars represent 95\\% confidence intervals."}
+
+s3_scale_order <- s3_scored %>% 
+  drop_na(scale) %>% 
+  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
+  mutate(diff = post-pre) %>% 
+  mutate(scale = recode_nodes2(scale)) %>% 
+  group_by(condition, scale) %>%
+  summarize(M = mean(diff, na.rm=TRUE)) %>%
+  ungroup() %>%
+  group_by(scale) %>%
+  summarize(diff_diff = mean(M, na.rm = T)) %>%
+  ungroup() %>%
+  arrange(diff_diff) %>% # ascending because intervention is expected to decrease vaccine toxicity beliefs
+  mutate(order = 1:nrow(.))
+
 s3_diff_plot <- s3_scored %>% 
@@
     scale = recode_nodes2(scale),
-    condition = ifelse(condition=="noInterv", "Control", "Vaccine Ingredients")
-    ) %>% 
+    condition = recode_factor(condition, 
+                              "noInterv" = "Control",
+                              .default = "Vaccine Ingredients")) %>% 
   group_by(condition, scale) %>%
   summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
-  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition, shape=condition)) +
+  ungroup() %>%
+  left_join(s3_scale_order) %>%
+  ggplot(aes(x = reorder(scale,order), y = M, ymin = M-se*2, ymax=M+se*2, 
+             color=condition, shape=condition)) +
+  scale_x_discrete() +
+  annotate("rect", 
+           xmin = s3_scale_order %>%
+             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.25,
+           xmax = s3_scale_order %>%
+             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.25,
+           ymin = -Inf,
+           ymax = Inf,
+           fill = "#fffaba") +
   geom_pointrange(position=position_dodge(width=.25)) +
@@
     panel.grid = element_blank(),
-    legend.position = c(.6,.15),
+    legend.position = c(.5,.1),
     legend.direction = "horizontal",
+    legend.background = element_rect(fill = NA),
     aspect.ratio=.5
     ) +
-  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention", shape="Intervention")
+  labs(title="A", y = "Mean difference", x = "Belief scale", 
+       color="Intervention", shape="Intervention")
 
@@
 s3_plt
+```
+
+```{r s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
+Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition.
+In both plots, error bars represent 95\\% confidence intervals."}
+
+# see previous chunk for scale order
+
+s3_diff_plot_bystudy <- s3_scored %>% 
+  # spread(phase, mean) %>% 
+  drop_na(scale) %>% 
+  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
+  mutate(diff = post-pre) %>% 
+  mutate(
+    scale = recode_nodes2(scale),
+    condition = recode_factor(condition, 
+                              "noInterv" = "Control",
+                              .default = "Vaccine Ingredients")) %>% 
+  left_join(s3_demo %>% distinct(workerId, study)) %>%
+  mutate(study = recode_factor(study, "A" = "Expt. 3A", "B" = "Expt. 3B")) %>%
+  group_by(study, condition, scale) %>%
+  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
+  ungroup() %>%
+  left_join(s3_scale_order) %>%
+  ggplot(aes(x = reorder(scale,order), y = M, ymin = M-se*2, ymax=M+se*2, 
+             color = interaction(condition, study, sep = ": "), 
+             shape = interaction(condition, study, sep = ": "))) +
+  scale_x_discrete() +
+  annotate("rect", 
+           xmin = s3_scale_order %>%
+             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.35,
+           xmax = s3_scale_order %>%
+             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.35,
+           ymin = -Inf,
+           ymax = Inf,
+           fill = "#fffaba") +
+  geom_pointrange(aes(group = interaction(condition, study)),
+                  position=position_dodge(width=.4), fill = "white") +
+  geom_hline(yintercept=0, linetype="dashed", color="grey") +
+  scale_color_manual(values=rep(c("#0067b1","#c50024"), 2)) +
+  scale_shape_manual(values=c(16, 17, 21, 24)) +
+  theme_bw(base_size=11) +
+  theme(
+    axis.text.x = element_text(angle=45, hjust=1),
+    panel.grid = element_blank(),
+    legend.position = c(.5,.1),
+    legend.direction = "horizontal",
+    legend.background = element_rect(fill = NA),
+    aspect.ratio=.5
+    ) +
+  labs(title="A", y = "Mean difference", x = "Belief scale", 
+       color="Intervention", shape="Intervention") +
+  guides(shape = guide_legend(nrow = 2, byrow = T),
+         color = guide_legend(nrow = 2, byrow = T))
+
+obs_pred_A <- make_pred_df(s3_mdf %>%
+                             filter(workerId %in% s3_demo$workerId[s3_demo$study == "A"]), 
+                           base_model, "vaccTox")
+obs_pred_B <- make_pred_df(s3_mdf %>%
+                             filter(workerId %in% s3_demo$workerId[s3_demo$study == "B"]), 
+                           base_model, "vaccTox")
+
+cor_val_A <- format(round(cor(obs_pred_A$predicted, obs_pred_A$observed),3), nsmall = 3)
+cor_val_B <- format(round(cor(obs_pred_B$predicted, obs_pred_B$observed),3), nsmall = 3)
+
+s3_obs_pred_plot_bystudy <- bind_rows(obs_pred_A %>% mutate(study = "A"),
+                                      obs_pred_B %>% mutate(study = "B")) %>%
+  mutate(study = recode_factor(study, "A" = "Expt. 3A", "B" = "Expt. 3B")) %>%
+  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul,
+             shape = study)) +
+  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
+  geom_errorbar(alpha=.5, width=0) +
+  geom_point(size=2.5, fill = "white") +
+  scale_shape_manual(values=c(16, 21)) +
+  # coord_fixed(ratio=1) +
+  coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
+  annotate(geom = "text", x = .05, y = -.08, 
+           label = bquote(paste("r"["A"]*" = ", .(cor_val_A)))) +
+  annotate(geom = "text", x = .05, y = -.105, 
+           label = bquote(paste("r"["B"]*" = ", .(cor_val_B)))) +
+  theme_bw(base_size=11) +
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        legend.position = c(.15,.85),
+        legend.background = element_rect(fill = NA)) +
+  theme(aspect.ratio = 1) +
+  labs(title = "B", y = "Observed change", x="Predicted change", 
+       shape = "Experiment")
+
+s3_plt_bystudy <- s3_diff_plot_bystudy + s3_obs_pred_plot_bystudy + 
+  plot_layout(ncol=2, widths = c(2,1))
+
+s3_plt_bystudy
 ```
@@
   cores = 6,
-  control = list(adapt_delta=.99),
+  # control = list(adapt_delta=.99),
   seed = 40725,
@@
 post-outbreak May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item.
-To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure.
+To assess the effects of recent news exposure on _vaccine intentions_, we examined the interaction between phase and news exposure.
 Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (see Table \@ref(tab:s4_table)).
 
-To model the effects of news exposure we followed the same procedure as in previous studies, but here augmented the model with a node representing news exposure as a child of the vaccine intentions node.
-The maximum likelihood estimate of the evidence ratio for the vaccine toxicity intervention was XXX.
-To simulate the impacts of this evidence, we supplied virtual evidence to the disease severity node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
+To model the effects of news exposure we followed the same procedure as in previous studies, but here augmented the model with a node representing news exposure as a child of the _vaccine intentions_ node.
+The maximum likelihood estimate of the evidence ratio for news exposure was XXX.
+To simulate the impacts of this evidence, we supplied virtual evidence to the _vaccine intentions_ node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
 
@@
 ```{r s4_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4.
-Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York.
+Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
 Right, mean observed and model predicted change scores for those who were exposed to news of the outbreak.
 In both plots, error bars represent 95\\% confidence intervals."}
+
+s4_scale_order <- combined %>% 
+  drop_na(scale) %>% 
+  mutate(posttest = rescale_beta(posttest, -3, 3), 
+         pretest = rescale_beta(pretest, -3, 3)) %>% 
+  mutate(diff = posttest-pretest) %>% 
+  mutate(scale = recode_nodes2(scale)) %>% 
+  group_by(vacc_news, scale) %>%
+  summarize(M = mean(diff, na.rm=TRUE)) %>%
+  ungroup() %>%
+  group_by(scale) %>%
+  summarize(diff_diff = mean(M, na.rm = T)) %>%
+  ungroup() %>%
+  arrange(diff_diff) %>% # ascending because news exposure is expected to increase vaccine intentions
+  mutate(order = 1:nrow(.))
+
 s4_diff_plot <- combined %>% 
@@
   ungroup() %>%
-  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
+  mutate(vacc_news = factor(vacc_news, 
+                            levels = c(0,1), 
+                            labels=c("No","Yes"))) %>%
   # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
-  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll95, ymax=ul95, color=vacc_news, shape=vacc_news)) +
+  left_join(s4_scale_order) %>%
+  ggplot(aes(x=reorder(scale, order), 
+             y = mean, ymin =ll95, ymax=ul95, 
+             color=vacc_news, shape=vacc_news)) +
+  scale_x_discrete() +
+  annotate("rect", 
+           xmin = s4_scale_order %>%
+             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.25,
+           xmax = s4_scale_order %>%
+             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.25,
+           ymin = -Inf,
+           ymax = Inf,
+           fill = "#fffaba") +
   geom_point(position=position_dodge(width=.25), size=2) +
@@
   geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
-  scale_color_manual(values=c("#0067b1","grey")) +
-  # scale_shape_manual(values=c(17,16)) +
+  scale_color_manual(values=c("#0067b1","#ff7f00")) +
+  scale_shape_manual(values=c(16,17)) +
   theme_bw(base_size=11) +
@@
     panel.grid = element_blank(),
-    legend.position = c(.35,.85),
+    legend.position = c(.5,.9),
     legend.direction = "horizontal",
@@
     ) +
-  labs(title="A", y = "Mean difference", x = "Belief scale", color="News Exposure", shape="News Exposure")
+  labs(title="A", y = "Mean difference", x = "Belief scale", 
+       color="News Exposure", shape="News Exposure")
 
@@
 ggsave("../local/s3_plt.png", s3_plt, height=4, width=8)
+ggsave("../local/s3_plt_bystudy.png", s3_plt_bystudy, height=4, width=8)
 ggsave("../local/s4_plt.png", s4_plt, height=4, width=8)
@@
 
-_Holistic balance_, from McFadden et al.’s (2010) Complementary, Alternative, and Conventional Medicine Attitudes Scale (CACMAS) (observed α=.82)
+_Holistic balance_, from McFadden et al.’s (2010) Complementary, Alternative, and Conventional Medicine Attitudes Scale (CACMAS) (Study 1 observed $\alpha$ = `r format(round(alpha_values$hb, 2), nsmall = 2)`)
 
@@
 
-_Naturalism_ (observed α=.77)
+_Naturalism_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$nat, 2), nsmall = 2)`)
 
@@
 
-_Medical skepticism_ (observed α=.78)
+_Medical skepticism_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$medSkept, 2), nsmall = 2)`)
 
@@
 
-_Disease rarity_ (observed α=.79)
+_Disease rarity_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$diseaseRare, 2), nsmall = 2)`)
 
@@
 
-_Disease severity _(observed α=.84)
+_Disease severity_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$diseaseSevere, 2), nsmall = 2)`)
 
@@
 
-_Vaccine effectiveness _(observed α=.84)
+_Vaccine effectiveness_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccEff, 2), nsmall = 2)`)
 
@@
 
-_Vaccine danger _(observed α=.88)
+_Vaccine danger_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccDanger, 2), nsmall = 2)`)
 
@@
 
-_Toxic additives in vaccines _(observed α=.91)
+_Toxic additives in vaccines_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccTox, 2), nsmall = 2)`)
 
@@
 
-_Infant immune system: Vaccines strain _(observed α=.86)
+_Infant immune system: Vaccines strain_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccStrain, 2), nsmall = 2)`)
 
@@
 
-_Vaccination intentions _(observed α=.83)
+_Vaccination intentions_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccIntent, 2), nsmall = 2)`)
 
@@
 
-_Parental expertise _(observed α=.83)
+_Parental expertise_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$parentExpert, 2), nsmall = 2)`)
 
@@
 
-_Infant immune system: Limited capacity_ (observed α=.86)
+_Infant immune system: Limited capacity_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$infantImmLimCap, 2), nsmall = 2)`)
 
@@
 
-_Infant immune system: Weakness_ (observed α=.85)
+_Infant immune system: Weakness_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$infantImmWeak, 2), nsmall = 2)`)
 
@@
 
-_Parental protectiveness _(observed α=.73)
+_Parental protectiveness_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$overpar, 2), nsmall = 2)`)
 

### 2021-07-20 supplement/supplement-main.Rmd
fix table for study 3

@@
 author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
-date: "Jul 18, 2021 (DRAFT)"
+date: "Jul 20, 2021 (DRAFT)"
 output:
@@
     Term = case_when(
-      grepl("(intervention|post)", Term) ~ paste0("$\\beta_{",
-                                                 gsub("(intervention|phase)", "", Term),
+      grepl("(intervention|post)", Term) ~ 
+        paste0("$\\beta_{",
+               gsub("(intervention|phase)", "", 
+                    gsub("study1", "3A", Term)),
+               "}$"),
+      grepl("(study1)", Term) ~ paste0("$\\beta_{",
+                                       gsub("(study1)", "3a", Term),
                                        "}$"),
@@
       Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
-      TRUE ~ gsub("(intervention|post)","", Term)
+      TRUE ~ gsub("(intervention|post)","", gsub("study1", "3a", Term))
     )

### 2021-07-20 supplement/supplement-main.Rmd
figure aspect ratios, observed alphas

@@
 
-```{r s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
+```{r s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=10, fig.height=5, fig.cap="Belief changes following the intervention in Experiments 3a and 3b, broken out by experiment.
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
@@
     panel.grid = element_blank(),
-    legend.position = c(.5,.1),
+    legend.position = c(.5,.15),
     legend.direction = "horizontal",
@@
         panel.grid.minor = element_blank(),
-        legend.position = c(.15,.85),
+        legend.position = c(.2,.8),
         legend.background = element_rect(fill = NA)) +
@@
 
-_Holistic balance_, from McFadden et al.’s (2010) Complementary, Alternative, and Conventional Medicine Attitudes Scale (CACMAS) (Study 1 observed $\alpha$ = `r format(round(alpha_values$hb, 2), nsmall = 2)`)
+_Holistic balance_, from McFadden et al.’s (2010) Complementary, Alternative, and Conventional Medicine Attitudes Scale (CACMAS) (Study 1: observed $\alpha$ = `r format(round(alpha_values$hb, 2), nsmall = 2)`)
 
@@
 
-_Naturalism_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$nat, 2), nsmall = 2)`)
+_Naturalism_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$nat, 2), nsmall = 2)`)
 
@@
 
-_Medical skepticism_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$medSkept, 2), nsmall = 2)`)
+_Medical skepticism_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$medSkept, 2), nsmall = 2)`)
 
@@
 
-_Disease rarity_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$diseaseRare, 2), nsmall = 2)`)
+_Disease rarity_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$diseaseRare, 2), nsmall = 2)`)
 
@@
 
-_Disease severity_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$diseaseSevere, 2), nsmall = 2)`)
+_Disease severity_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$diseaseSevere, 2), nsmall = 2)`)
 
@@
 
-_Vaccine effectiveness_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccEff, 2), nsmall = 2)`)
+_Vaccine effectiveness_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$vaccEff, 2), nsmall = 2)`)
 
@@
 
-_Vaccine danger_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccDanger, 2), nsmall = 2)`)
+_Vaccine danger_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$vaccDanger, 2), nsmall = 2)`)
 
@@
 
-_Toxic additives in vaccines_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccTox, 2), nsmall = 2)`)
+_Toxic additives in vaccines_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$vaccTox, 2), nsmall = 2)`)
 
@@
 
-_Infant immune system: Vaccines strain_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccStrain, 2), nsmall = 2)`)
+_Infant immune system: Vaccines strain_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$vaccStrain, 2), nsmall = 2)`)
 
@@
 
-_Vaccination intentions_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccIntent, 2), nsmall = 2)`)
+_Vaccination intentions_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$vaccIntent, 2), nsmall = 2)`)
 
@@
 
-_Parental expertise_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$parentExpert, 2), nsmall = 2)`)
+_Parental expertise_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$parentExpert, 2), nsmall = 2)`)
 
@@
 
-_Infant immune system: Limited capacity_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$infantImmLimCap, 2), nsmall = 2)`)
+_Infant immune system: Limited capacity_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$infantImmLimCap, 2), nsmall = 2)`)
 
@@
 
-_Infant immune system: Weakness_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$infantImmWeak, 2), nsmall = 2)`)
+_Infant immune system: Weakness_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$infantImmWeak, 2), nsmall = 2)`)
 
@@
 
-_Parental protectiveness_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$overpar, 2), nsmall = 2)`)
+_Parental protectiveness_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$overpar, 2), nsmall = 2)`)
 

### 2021-07-20 paper/paper.Rmd
minor fix
figure fixes

@@
 ```{r load-required-data, include=FALSE}
-
+results <- readRDS("../local/paper-results.rds") 
 ```
@@
 As in Study 2, we used our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in participants’ vaccine toxicity beliefs following the intervention.
-As shown in Figure 5, the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker R = .XX than those observed in our other studies.
+As shown in Figure 5, the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker (r = .XX) than those observed in our other studies.
 
@@
 
-We contacted XXX of the 1130 participants who completed Study 1 and invited them to participate in Study 4, in which they completed the same 14 belief scales and answered questions about their exposure to media coverage of the measles outbreaks.
-Of these, 555 participants returned and XXX successfully completed the study including passing attention checks.
+We contacted as many of the 1130 participants who completed Study 1 as we could and invited them to participate in Study 4, in which they completed the same 14 belief scales and answered questions about their exposure to media coverage of the measles outbreaks.
+A total of 555 participants returned and XXX successfully completed the study including passing attention checks.
 These participants completed all 14 belief scales and also indicated whether they had seen or heard anything about measles in the news recently.
@@
 
-Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (X 2017 vs.
+Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (September 2017 vs.
 May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item.

### 2021-07-20 supplement/supplement-main.Rmd
figure fixes

@@
 
-z2 <- custom_plot.HydeNetwork(h2)
+z2 <- custom_plot.HydeNetwork(h2, attr_theme="tb")
 
@@
 z2$nodes_df$fillcolor <- ifelse(z2$nodes_df$label=="Vaccination\nIntentions", 
-                                "#fffaba","white")
+                                "#dcdcdc","white")
 z2$nodes_df$fillalpha <- 0.1
@@
 # 
-# render_graph(z2)
+render_graph(z2)
 
@@
 z$nodes_df$shape <- "ellipse"
-z$nodes_df$fillcolor <- ifelse(z$nodes_df$label=="Vaccination\nIntentions", "#fffaba","white")
+z$nodes_df$fillcolor <- ifelse(z$nodes_df$label=="Vaccination\nIntentions", "#dcdcdc","white")
 z$nodes_df$fixedsize <- FALSE
@@
            ymax = Inf,
-           fill = "#fffaba") +
+           fill = "#dcdcdc") +
   geom_pointrange(position=position_dodge(width=.25)) +
@@
   scale_color_manual(values=c("#0067b1","#c50024")) +
-  scale_shape_manual(values=c(16,17)) +
+  scale_shape_manual(values=c(17,16)) +
   theme_bw(base_size=11) +
@@
     panel.grid = element_blank(),
-    legend.position = c(.5,.9),
+    legend.position = c(.6,.9),
     legend.direction = "horizontal",
@@
            ymax = Inf,
-           fill = "#fffaba") +
+           fill = "#dcdcdc") +
   geom_pointrange(aes(group = interaction(condition, study)),
@@
   scale_color_manual(values=rep(c("#0067b1","#c50024"), 2)) +
-  scale_shape_manual(values=c(16, 17, 21, 24)) +
+  scale_shape_manual(values=c(17, 16, 24, 21)) +
   theme_bw(base_size=11) +
@@
            ymax = Inf,
-           fill = "#fffaba") +
+           fill = "#dcdcdc") +
   geom_point(position=position_dodge(width=.25), size=2) +
@@
   geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
-  scale_color_manual(values=c("#0067b1","#ff7f00")) +
-  scale_shape_manual(values=c(16,17)) +
+  scale_color_manual(values=c("gray50","#C50024")) +
+  scale_shape_manual(values=c(17,16)) +
   theme_bw(base_size=11) +
@@
 
-```{r measles-image, echo=F}
+```{r measles-image, echo=F, fig.align='center', out.height='2in'}
 # display measles image here
+knitr::include_graphics("img_0.png")
 ```
@@
 
-```{r mumps-image, echo=F}
+```{r mumps-image, echo=F, fig.align='center', out.height='2in'}
 # display mumps image here
+knitr::include_graphics("img_1.jpg")
 ```
@@
 
-```{r rubellas-image, echo=F}
+```{r rubellas-image, echo=F, fig.align='center', out.width='2in'}
 # display rubella image here
+knitr::include_graphics("img_2.jpg")
 ```

### 2021-07-20 code/load-data-s1.R
revert to old data

@@ -13,7 +13,7 @@ d_raw <- read.csv("../data/study1_data.csv", header = T)
 
 # filter rows and select columns
 d1 <- d_raw %>%
-  filter(!grepl("Import", StartDate), !grepl("Start", StartDate)) %>% # remove extra headers
+  # filter(!grepl("Import", StartDate), !grepl("Start", StartDate)) %>% # remove extra headers
   filter(Status == "IP Address") %>% # remove survey previews (?)
   filter(Progress == 100) %>% # only get people who made it all the way through (?)
   filter(as.numeric(as.character(age)) >= 18) %>% # exclude people who said they were <18 yo (could be more stringent)

### 2021-07-20 paper/paper.Rmd
made reproducible

@@
 ```{r load-required-data, include=FALSE}
+library(tidyverse)
 results <- readRDS("../local/paper-results.rds") 
@@
 
-[add abstract]
+## Abstract
 
-[add significance statement]
+WIP
+
+## Significance Statement
+
+When people decide whether to vaccinate their children and themselves against dangerous diseases like measles and Covid-19, their decisions are affected by a network of interrelated beliefs about specific diseases, vaccine safety and efficacy, the immune system, the medical system, and health and nature more generally.
+By creating a computational model of the intuitive theory connecting these different beliefs, we were able to make accurate predictions about how these beliefs are revised in light of educational interventions, design an effective new intervention encouraging vaccination, and understand how these beliefs were affected by real-world events.
+This approach provides the foundation for richer understandings of intuitive theories more broadly and sheds new light on long-standing theoretical questions about belief revision.
+
+\newpage
 
@@
 
-Consider some of the beliefs people who are skeptical of childhood vaccination expressed when we asked them to explain their views in an open-ended qualitative survey (conducted pre-pandemic; N=16).
+Consider some of the beliefs people who are skeptical of childhood vaccination expressed when we asked them to explain their views in an open-ended qualitative survey (conducted pre-pandemic; *n* = 16).
 Several participants saw vaccines as "unnatural" and expressed concerns about toxic additives in vaccines, such as heavy metals and mercury.
@@
 
-We developed psychometrically robust scales to measure these beliefs, then administered these 14 belief scales to participants and in an online survey with 1130 participants.
+We developed psychometrically robust scales to measure these beliefs, then administered these 14 belief scales to participants and in an online survey with `r results$s1$demo$n_include` participants.
 There were strong intercorrelations among these 14 beliefs confirming that these beliefs are, in fact, closely related to each other and to intentions to vaccinate children (see SI).
@@
 
-We used these intercorrelations to build a cognitive model of the relations among these beliefs using Bayesian network structure learning techniques, using an 80% training split of the data (n = 904).
+We used these intercorrelations to build a cognitive model of the relations among these beliefs using Bayesian network structure learning techniques, using an 80% training split of the data (*n* = 904).
 Based on the observed associations among participants' beliefs about each of theses issues, we sought to infer how these states of affairs (e.g., that vaccines are dangerous, that diseases are severe) are connected in people's intuitive theories--how people understand these states of affairs to cause, imply, or otherwise influence one another.
@@
 
-We evaluated the model’s performance by testing its accuracy in predicting responses in the 20% testing split (n = 226).
+```{r, include=F}
+
+avg_corr <- results$s1$validcorrs %>% 
+  mutate(z = psych::fisherz(cor)) %>% 
+  summarize(z = mean(z)) %>% 
+  mutate(cor = psych::fisherz2r(z)) %>% 
+  .$cor
+
+min_corr <- round(min(results$s1$validcorrs$cor),3)
+max_corr <- round(max(results$s1$validcorrs$cor),3)
+```
+
+We evaluated the model’s performance by testing its accuracy in predicting responses in the 20% testing split (*n* = 226).
 We generated predictions for held-out participants’ responses for each variable by conditioning the network on the remaining 13 observed variables.
 Figure 2 compares the model’s predictions with participants’ actual responses.
-Collapsing across all variables, the average correlation between predicted and observed responses was r = .XXX, accounting for [\~70]% of the variance in observed responses.
+Collapsing across all variables, the average correlation between predicted and observed responses was *r* = `r round(avg_corr, 3)`, accounting for `r round(100*avg_corr^2, 0)`% of the variance in observed responses.
 
 ```{r fig2-validation, fig.align='center', fig.height=4, fig.width=7, fig.cap="Observed responses and model predictions for each belief among participants in the Study 1 testing split.
-Correlations between observed and predicted values ranged from XXX to XXX across the different belief scales.
-In general, the model showed greater predictive accuracy for more central beliefs (e.g., *vaccine danger*) than for more peripheral beliefs (e.g., *parental protectiveness;* see SI for details)."}
+Correlations between observed and predicted values ranged from .380 to .898 across the different belief scales.
+In general, the model showed greater predictive accuracy for more central beliefs (e.g., \\emph{vaccine danger}) than for more peripheral beliefs (e.g., \\emph{parental protectiveness}; see SI for details)."}
 knitr::include_graphics("../local/valid_plt.png")
@@
 To examine this, we used the same model developed in Study 1 to simulate how the 13 other beliefs in the intuitive theory would change if we intervened directly on *disease severity* (see Methods).
-As shown in Figure 3, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (R = .86).
+As shown in Figure 3, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (*r* = `r results$s2$modcorr`).
 
@@
 We conducted two preregistered experiments (3a and 3b) testing the effects of this novel intervention using the same pretest-posttest design as Study 2.
-Collapsing across these two studies, Figure 5 shows the change in participants’ (n = XXX) attitudes across all 14 belief scales from pretest to posttest.
+Collapsing across these two studies, Figure 5 shows the change in participants’ (*n* = `r results$s3$demo$n_complete`) attitudes across all 14 belief scales from pretest to posttest.
 Most importantly, the Vaccine Ingredients intervention significantly improved participants’ vaccination intentions compared to the no-intervention control condition.
@@
 As in Study 2, we used our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in participants’ vaccine toxicity beliefs following the intervention.
-As shown in Figure 5, the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker (r = .XX) than those observed in our other studies.
+As shown in Figure 5, the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker (*r* = `r results$s3$modcorr`) than those observed in our other studies.
 
@@
 Right, mean observed and model predicted change scores for those participants who did report exposure to this news.
+Belief changes were modeled assuming that news of the outbreak directly impacted participant's vaccine intentions, the most central of the 14 beliefs, in order to evaluate the overall coherence of these belief changes.
 In both plots, changes were calculated after transforming responses to lie between 0 and 1 and error bars represent 95\\% confidence intervals."}
@@
 To examine this possibility, we invited participants from Study 1 (conducted in September 2017) to participate in a new study measuring each of those 14 beliefs again (conducted on May 1st, 2019; approximately 18 months later).
-Of the 1130 participants in Study 1, 555 returned.
-Approximately [80]% of participants reported recently seeing, hearing, or reading about measles outbreaks.
+Of the `r results$s1$demo$n_include` participants in Study 1, `r results$s4$demo$n_complete` returned and completed the study.
+Approximately `r round(100*(results$s4$demo$n_news/results$s4$demo$n_complete),0) `% of participants reported recently seeing, hearing, or reading about measles outbreaks.
 
@@
 Unlike in the intervention studies, where a specific belief was targeted by the intervention, it is likely that many beliefs were addressed by media coverage of these outbreaks.
-To assess whether these changes were coherent, we examined how they were related to the most central of the beliefs we measured, *vaccine intentions*, using our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in *vaccine intentions.* As shown in Figure 6, the changes in participants’ beliefs are very similar to the model’s predictions (r = XX), suggesting that the changes in their beliefs were highly coherent with respect to their intuitive theories of the domain.
+To assess whether these changes were coherent, we examined how they were related to the most central of the beliefs we measured, *vaccine intentions*, using our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in *vaccine intentions.* As shown in Figure 6, the changes in participants’ beliefs are very similar to the model’s predictions (*r* = `r results$s4$modcorr`), suggesting that the changes in their beliefs were highly coherent with respect to their intuitive theories of the domain.
 Modeling these beliefs as united by an intuitive theory not only captures how these beliefs are revised immediately in light of evidence, but also how they are changed by real-world events.
@@
 
-Participants (final *n* = 1130) responded to the 14 belief scales, followed by demographics questions and a handful of questions about whether they were or were expecting to be a parent.
+Participants (final *n* = `r results$s1$demo$n_include`) responded to the 14 belief scales, followed by demographics questions and a handful of questions about whether they were or were expecting to be a parent.
 They were then debriefed with a brief statement noting that vaccines are safe and pointing them toward a WHO website for further information.
@@
 $$P(y) = 1 \big[1-(1-w_0)\prod_i(1-w_i)^{x_i}\big]\prod_j(1-w_j)^{x_j}$$
+
 Here, each parent node $x$ is either a generative ($i$) or preventive ($j$) influence, that generates or prevents the child node with some probability weight ($w_i$ or $w_j$).
@@
 Procedures for Phase 1 were nearly identical to Study 1, but the debriefing statement was moved to the end of Phase 2.
-In Phase 2 (XX days later), participants completed a study very similar to Horne et al.’s (2015) original intervention study.
+In Phase 2 (approximately two days later), participants completed a study very similar to Horne et al.’s (2015) original intervention study.
 Participants were randomly assigned to either the disease risk condition or the No Intervention condition, with the constraint that the distributions of participants’ Phase 1 *vaccine intentions* scores should be similar across the two conditions; we accomplished this by stratifying participants into three groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
 
-Participants (n = XX passed attention checks in total) in the intervention conditions were presented with a version of Horne et al.’s  “disease risk” intervention, modified to present subparts in a fixed (rather than randomized) order, with slight changes to wording to improve clarity, and with a final statement summarizing the take-home message of the intervention; see SI.
+Participants (*n* = `r results$s2$demo$n_complete` passed attention checks in total) in the intervention conditions were presented with a version of Horne et al.’s  “disease risk” intervention, modified to present subparts in a fixed (rather than randomized) order, with slight changes to wording to improve clarity, and with a final statement summarizing the take-home message of the intervention; see SI.
 They then completed the same 14 belief scales and demographic questions that they had completed in Phase 1.
@@
 
+```{r, include=F}
+s2_reg <- summary(results$s2$reg)
+```
+
 We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the *Vaccination Intentions* scale items, using the “brms” package for R [@burkner2017].
@@
 In this model, the unique effect of the intervention on vaccination intention scores is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants).
-The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: *b* = -0.15, 95% CI: [-0.27, -0.04]).
+The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: $b$ = `r round(s2_reg$fixed[9,1],3)`, 95% CI: [`r round(s2_reg$fixed[9,3], 3)`, `r round(s2_reg$fixed[9,4], 3)`]).
 We consider this to be a full replication of Horne, Powell, et al.’s [-@horne.etal2015] results.
@@
 Study 3a and 3b tested the effects of a novel intervention aimed at dispelling concerns about toxic additives in vaccines.
-These studies followed similar design procedures as Study 2, with phase 2 conducted XX days after phase 1.
-In both Study 3a (April 2019; final n = XX) and Study 3b (May 2019; final n = XX) the vaccine toxin intervention was compared against no-intervention control.
+These studies followed similar design procedures as Study 2, with phase 2 conducted 1-2 days after phase 1.
+In both Study 3a (April 2019) and Study 3b (May 2019; combined final *n* = `r results$s3$demo$n_complete`) the vaccine toxin intervention was compared against no-intervention control.
 
@@
 
+```{r, include=F}
+s3_reg <- summary(results$s3$reg)
+```
+
 As they shared the same design, we combined data from studies 3a and 3b for analysis.
 As in study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine toxins intervention on participants’ *vaccination intentions* scores.
-The vaccine toxins intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: b = [statistics]); see Figure 5, panel A.
-However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: b = [statistics]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
+The vaccine toxins intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: $b$ = `r round(s3_reg$fixed[9,1],3)`, 95% CI: [`r round(s3_reg$fixed[9,3], 3)`, `r round(s3_reg$fixed[9,4], 3)`]); see Figure 5, panel A.
+However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: $b$ = `r round(s3_reg$fixed[7,1],3)`, 95% CI: [`r round(s3_reg$fixed[7,3], 3)`, `r round(s3_reg$fixed[7,4], 3)`]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
 
@@
 
-We contacted as many of the 1130 participants who completed Study 1 as we could and invited them to participate in Study 4, in which they completed the same 14 belief scales and answered questions about their exposure to media coverage of the measles outbreaks.
-A total of 555 participants returned and XXX successfully completed the study including passing attention checks.
+We contacted as many of the `r results$s1$demo$n_include` participants who completed Study 1 as we could and invited them to participate in Study 4, in which they completed the same 14 belief scales and answered questions about their exposure to media coverage of the measles outbreaks.
+A total of `r results$s4$demo$n_recruited` participants returned and `r results$s4$demo$n_complete` successfully completed the study including passing attention checks.
 These participants completed all 14 belief scales and also indicated whether they had seen or heard anything about measles in the news recently.
@@
 
+```{r, include=F}
+s4_reg <- summary(results$s4$reg)
+```
+
 Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (September 2017 vs.
@@
 To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure.
-Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (stats); see Figure 6, panel A.
+Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (interaction effect: $b$ = `r round(s4_reg$fixed[9,1],3)`, 95% CI: [`r round(s4_reg$fixed[9,3], 3)`, `r round(s4_reg$fixed[9,4], 3)`]); see Figure 6, panel A.
 

### 2021-07-20 supplement/supplement-main.Rmd
made reproducible

@@
 This model can predict how beliefs correlate across people and how they would be revised in the face of evidence.
-In Study 2, we replicated the success of an existing intervention emphasizing the dangers of childhood diseases (Horne et al., 2015) and used our model to provide a more detailed understanding of _how and why_ this intervention increases vaccine intentions.
+In Study 2, we replicated the success of an existing intervention emphasizing the dangers of childhood diseases [@horne.etal2015] and used our model to provide a more detailed understanding of _how and why_ this intervention increases vaccine intentions.
 In Study 3, we drew inspiration from our model to create and validate the success of  a novel intervention aimed at debunking concerns about toxic additives.
@@
 
-Figure \@ref(fig:dag-example) shows an example of a simple Bayesian Network.
+Figure 1 shows an example of a simple Bayesian Network.
 The network itself is a _directed acyclic graph_ (DAG), a type of graphical model.
@@
 
-```{r dag-example, echo=F, fig.align='center', out.width = '40%', fig.cap="Example DAG illustrating some variables related to wildfires."}
+```{r fig1-dag-example, echo=F, message=F, warning=F, fig.align='center', out.width = '40%', fig.cap="Example DAG illustrating some variables related to wildfires."}
 
@@
 To conduct an efficient search through the super-exponential space of DAGs, we tested several variants of two structure learning algorithms implemented in the “bnlearn” R package [@scutari2010].
-The first is a purely score-based “hill-climbing” algorithm  and the second was a hybrid algorithm that combined the hill-climbing algorithm with a prior “restriction” phase that pruned down the space of DAGs.
+The first is a purely score-based “hill-climbing” algorithm(HC) and the second was a hybrid algorithm that combined the hill-climbing algorithm with a prior “restriction” phase that pruned down the space of DAGs (MMHC).
 This pruning was accomplished with the “min-max parents and children” algorithm, which can be tuned with a hyperparameter alpha, which we tested at several levels.
@@
 In addition to the different algorithms, we also compared four different “blacklists” that imposed different constraints on the structure learning process.
-In addition to our theory-driven blacklist based on our generative model assumptions, we also explored unconstrained structure learning, and two additional blacklists: one which stipulated only that “intentions to vaccinate” should be a child node with no children of its own, and another that stipulated also that the most abstract beliefs “holistic balance” and “naturalism” should be allowed to have no parents other than each other.
-
-Figure \@ref(fig:cross-validation) presents the results of these cross validation tests.
+In addition to our theory-driven blacklist based on our generative model assumptions ("theory"), we also explored unconstrained structure learning, and two additional blacklists: one which stipulated only that “intentions to vaccinate” should be a child node with no children of its own ("child"), and another that stipulated also that the most abstract beliefs “holistic balance” and “naturalism” should be allowed to have no parents other than each other ("parents").
+
+Figure 2 displays the results of these cross-validation tests.
 As seen in the figure, all structure learning approaches produced models with similar out-of-sample performance, with more variability among folds and runs than between algorithms.
@@
 
-```{r cross-validation, echo=FALSE, fig.align='center', fig.height=3, fig.width=4, fig.cap="Cross-validation performance for diffrent structure learning algorithms on the training data from Study 1."}
+```{r fig2-cross-validation, echo=FALSE, fig.align='center', fig.height=3, fig.width=4, fig.cap="Cross-validation performance for diffrent structure learning algorithms on the training data from Study 1."}
 
@@
 cv_res %>% 
+  mutate(algo = case_when(
+    algo == "hc" ~ "HC",
+    algo == "mmhc_05" ~ "MMHC .05",
+    algo == "mmhc_01" ~ "MMHC .01",
+    algo == "hc_intentdv" ~ "HC (child)",
+    algo == "mmhc_intentdv_05" ~ "MMHC .05 (child)",
+    algo == "mmhc_intentdv_01" ~ "MMHC .01 (child)",
+    algo == "hc_idv_abspar" ~ "HC (parents)",
+    algo == "mmhc_idv_abspar_05" ~ "MMHC .05 (parents)",
+    algo == "mmhc_idv_abspar_01" ~ "MMHC .01 (parents)",
+    algo == "hc_theory" ~ "HC (theory)",
+    algo == "mmhc_theory_05" ~ "MMHC .05 (theory)",
+    algo == "mmhc_theory_01" ~ "MMHC .01 (theory)"
+  )) %>% 
   ggplot(aes(x=reorder(algo, loss), y=loss)) +
@@
 We used a bootstrapping procedure to estimate the confidence in each of the links in this model, conducting the structure learning procedure repeatedly for 200 bootstrapped resamples of the original training data.
-Figure \@ref(fig:disp-bootgraph) visualizes the frequency with which each arc appeared in the resulting model across these replicates, and figure \@ref(fig:disp-maingraph) visualizes the model with the coefficients for each link encoded by color.
+Figure 3 visualizes the frequency with which each arc appeared in the resulting model across these replicates, and figure \@ref(fig:disp-maingraph) visualizes the model with the coefficients for each link encoded by color.
 
@@
 
-```{r disp-bootgraph, echo=F, fig.width=8, fig.height=5, fig.cap="Bootstrapped confidence estimates for Bayesian network edges.
+```{r fig3-disp-bootgraph, echo=F, fig.width=8, fig.height=5, fig.cap="Bootstrapped confidence estimates for Bayesian network edges.
 Edge color indicates frequency with which edges appeared when conducting search across 200 bootstrap replicates.
@@
 
-```{r disp-maingraph, echo=F, fig.width=8, fig.height=5, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
+```{r fig4-disp-maingraph, echo=F, fig.width=8, fig.height=5, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions.
 Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links.
@@
 We validated our final model by testing its predictions on the held-out testing data.
-The models’ predictions are plotted against the true values for the testing data in figure X below.
+The models’ predictions are plotted against the true values for the testing data in figure 5 below.
 As seen in the figure, the quality of predictions varied across beliefs, but in many cases was quite strong.
@@
 
-```{r validation_plot, echo=FALSE, fig.height=6, fig.width=10, fig.align="center", fig.cap="Model predictions versus observed values for test data from Study 1. Dashed lines represent perfect fits."}
+```{r fig5-validation_plot, echo=FALSE, fig.height=6, fig.width=10, fig.align="center", fig.cap="Model predictions versus observed values for test data from Study 1.
+Dashed lines represent perfect fits."}
 
@@
 Our intention was to capture the degree to which each belief is predictable from the others as a whole.
-As shown in table X, the relatively simpler Bayesian network model does not sacrifice any predictive power compared to the suite of maximal naive models.
+As shown in table 1, the relatively simpler Bayesian network model does not sacrifice any predictive power compared to the suite of maximal naive models.
 
 Finally, we can also compare the quality of our model predictions to the test-retest reliability of the belief scales (estimated from the pre-test and post-test measures in the control condition of Study 2), establishing an overall upper-bound on the predictability of these measures.
-As shown in Table \@ref(tab:model_valid_table), the Bayesian network model did approximately as well as possible for seven beliefs, but fell short for the other seven.
+As shown in Table 1, the Bayesian network model did approximately as well as possible for seven beliefs, but fell short for the other seven.
 These failures suggest that the model is missing the information that would be needed to predict these beliefs.
@@
 
-```{r model_valid_table, echo=FALSE, message=F, warning=F}
+```{r tab1-model_valid_table, echo=FALSE, message=F, warning=F}
 # compare S1 model predictions to test-retest reliability?
@@
 
-Returning to the DAG shown in Figure \@ref(fig:dag_example) above, consider the subgraph $FIRE \rightarrow SMOKE$, capturing the fact that fire causes smoke.
+Returning to the DAG shown in Figure 1 above, consider the subgraph $FIRE \rightarrow SMOKE$, capturing the fact that fire causes smoke.
 This relationship is represented as a probabilistic function, where the probability of SMOKE depends on the probability of FIRE.
@@
 
-To model the effects of participants observing evidence, we augmented the Bayesian network representing the cognitive model (shown in Figure \@ref(fig:disp-maingraph)) with an additional node representing the evidence.
+To model the effects of participants observing evidence, we augmented the Bayesian network representing the cognitive model (shown in Figure 4) with an additional node representing the evidence.
 For instance, to model the effects of the “Disease Risk” intervention (Study 2), we added an evidence node as a child of “disease severity,” acting as virtual evidence for this node.
@@
 
-Figure \@ref(fig:corrplot) presents correlations among the 14 belief scales measured in Study 1.
+Figure 6 presents correlations among the 14 belief scales measured in Study 1.
 As the figure shows, there are strong correlations among many of the beliefs, suggesting they are related by an underlying intuitive theory.
 
-```{r corrplot, echo=FALSE, message=F, fig.height=7, fig.width=7, fig.align='center', fig.cap = "Correlations among 14 the belief scales measured in Study 1.
+```{r fig6-corrplot, echo=FALSE, message=F, fig.height=7, fig.width=7, fig.align='center', fig.cap = "Correlations among 14 the belief scales measured in Study 1.
 Correlation matrix is arranged by hierarhical clustering algorithm to highlight connections among beliefs."}
@@
   geom_tile(color = "black") +
-  geom_text(aes(label = format(round(cor, 2), digits = 2)), size = 3) +
+  geom_text(aes(label = format(round(cor, 2), digits = 2)), size = 2.75) +
   scale_fill_distiller(palette ="RdBu", limits = c(-1, 1), direction = 1,
@@
 Procedures for part 1 of Study 2 were nearly identical to Study 1, save for the use of four rather than two attention check questions, and the removal of debriefing statements at the end of the survey.
-On Day 2 (XX days later), participants completed a study that was designed to be very similar to Horne, Powell, et al.’s (2015) original study.
+On Day 2 (approximately two days later), participants completed a study that was designed to be very similar to Horne, Powell, et al.’s [-@horne.etal2015] original study.
 Participants were randomly assigned to either the Disease Risk condition or the No Intervention condition, with the constraint that the distributions of participants’ Day 1 _vaccine intentions_ should be similar across the two conditions; we accomplished this by stratifying participants into groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
 
-Participants were presented with a slightly modified version of the “Disease Risk” intervention from Horne, Powell et al.’s (2015) original study, which was based on materials available on the CDC website (XX).
-Compared with Horne, Powell et al.
-(2015), we modified the intervention to present these parts in a fixed (rather than randomized) order, made slight changes to wording to improve clarity, and added a final statement summarizing the take-home message of the intervention.
+Participants were presented with a slightly modified version of the “Disease Risk” intervention from Horne et al.’s [-@horne.etal2015] original study, which was based on materials available on the CDC website.
+Compared with Horne et al.
+[-@horne.etal2015], we modified the intervention to present these parts in a fixed (rather than randomized) order, made slight changes to wording to improve clarity, and added a final statement summarizing the take-home message of the intervention.
 Full text of this intervention can be found in appendix B of these supplementary materials.
@@
 
-Participants in the No Intervention condition (_n_=XX) completed an identical set of questions, except that they did not read any material before completing the 14 belief scales and the questions about their personal background.
+Participants in the No Intervention condition (_n_ = `r sum(s2_demo$condition=="noInterv")`) completed an identical set of questions, except that they did not read any material before completing the 14 belief scales and the questions about their personal background.
 
@@
 
-```{r s2_model, echo=FALSE, message=F, warning=F}
+```{r tab2-s2_model, echo=FALSE, message=F, warning=F}
 
@@
 In this model, the unique effect of the intervention on vaccination intention responses is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants).
-The Disease Risk intervention increased participants’ vaccination intention ratings (see Table \@ref(tab:s2_model)).
+The Disease Risk intervention increased participants’ vaccination intention ratings (see Table 2).
 We consider this to be a full replication of Horne et al.’s [-@horne.etal2015] results.
@@
 To model the changes in the belief network, we estimate the “evidence ratio” using the method described in the modeling section above.
-The maximum likelihood estimate of the evidence ratio was XXX.
 To simulate the impacts of this evidence, we supplied virtual evidence to the _disease severity_ node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
@@
 
-Figure \@ref(fig:s2_plot) (right) shows the correlation between predicted and observed belief changes conditional on the Disease Risk intervention.
-
-```{r s2_plot, echo=FALSE}
+Figure 7 (right) shows the correlation between predicted and observed belief changes conditional on the Disease Risk intervention.
+
+```{r, echo=FALSE}
 # create cognitive model for predicting change scores
@@
 
-```{r echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiment 2.
+```{r fig7-s2_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiment 2.
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
@@
 
-cor_val <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
+cor_val_s2 <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
 
@@
   geom_point(size=2.5) +
-  annotate(geom="text", x=.03, y=-.04, label= paste("r =", cor_val)) +
+  annotate(geom="text", x=.03, y=-.04, label= paste("r =", cor_val_s2)) +
   coord_cartesian(xlim=c(-.06,.06), ylim=c(-.06,.06)) +
@@
 This captures qualitative Feature 3 of intuitive theories.
-Figure \@ref(fig:predicted_impacts) presents these predictions, assuming the changes in beliefs are designed to move vaccine intentions in a positive direction (e.g.
+Figure 8 presents these predictions, assuming the changes in beliefs are designed to move vaccine intentions in a positive direction (e.g.
 increasing “disease severity” beliefs but decreasing “vaccine danger” beliefs).
 
-```{r predicted_impacts, echo=F, message=F, fig.align='center', fig.height=3, fig.width=3, fig.cap="Predicted effects on Vaccine Intentions for hypothetical interventions targeting each of the 13 other beliefs"}
+```{r fig8-predicted_impacts, echo=F, message=F, fig.align='center', fig.height=3, fig.width=3, fig.cap="Predicted effects on Vaccine Intentions for hypothetical interventions targeting each of the 13 other beliefs"}
 
@@
 
-```{r, echo=FALSE, message=F, warning=F}
+```{r tab3-s3_reg, echo=FALSE, message=F, warning=F}
 # compare conditions on vaccIntent w/ regression model
@@
 
-```{r, echo=FALSE, message=F, warning=F}
+```{r tab4-tab5, echo=FALSE, message=F, warning=F}
 
@@
 To model the effect of the Vaccine Ingredients intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the Vaccine Ingredients intervention as a child of the _vaccine toxicity_ belief node.
-The maximum likelihood estimate of the evidence ratio for the Vaccine Ingredients intervention was XXX.
 To simulate the impacts of this evidence, we supplied virtual evidence to the _vaccine toxicity_ node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
 
-Figure \@ref(fig:s3_plot) (right) shows the correlation between predicted and observed belief changes conditional on the Vaccine Ingredients intervention.
-
-```{r s3_plot, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
+Figure 9 (right) shows the correlation between predicted and observed belief changes conditional on the Vaccine Ingredients intervention.
+
+```{r fig9-s3_plot, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
@@
 
-cor_val <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
+cor_val_s3 <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
 
@@
   coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
-  annotate(geom="text", x=.05, y=-.1, label= paste("r =", cor_val)) +
+  annotate(geom="text", x=.05, y=-.1, label= paste("r =", cor_val_s3)) +
   theme_bw(base_size=11) +
@@
 
-```{r s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=10, fig.height=5, fig.cap="Belief changes following the intervention in Experiments 3a and 3b, broken out by experiment.
+```{r fig10-s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=10, fig.height=5, fig.cap="Belief changes following the intervention in Experiments 3a and 3b, broken out by experiment.
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
@@
 
-```{r s4_table, echo=FALSE, message=F, warning=F}
+```{r tab6-s4_table, echo=FALSE, message=F, warning=F}
 # compare conditions on vaccIntent w/ regression model
@@
 To assess the effects of recent news exposure on _vaccine intentions_, we examined the interaction between phase and news exposure.
-Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (see Table \@ref(tab:s4_table)).
+Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (see Table 6).
 
 To model the effects of news exposure we followed the same procedure as in previous studies, but here augmented the model with a node representing news exposure as a child of the _vaccine intentions_ node.
-The maximum likelihood estimate of the evidence ratio for news exposure was XXX.
 To simulate the impacts of this evidence, we supplied virtual evidence to the _vaccine intentions_ node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
 
-Figure \@ref(fig:s4_plot) (right) shows the correlation between predicted and observed belief changes for participants who were aware of the New York measles outbreak in May 2019.
-
-```{r s4_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4.
+Figure 11 (right) shows the correlation between predicted and observed belief changes for participants who were aware of the New York measles outbreak in May 2019.
+
+```{r fig11-s4_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4.
 Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
@@
 
-cor_val <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
+cor_val_s4 <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
 
@@
   geom_errorbar(alpha=.5, width=0) +
-  annotate(geom="text", x=.04, y=-.04, label= paste("r =", cor_val)) +
+  annotate(geom="text", x=.04, y=-.04, label= paste("r =", cor_val_s4)) +
   coord_cartesian(xlim=c(-.07,.06), ylim=c(-.07,.06)) +
@@
 
-```{r, echo=FALSE, message=F, warning=F}
+```{r tab-demo, echo=FALSE, message=F, warning=F}
 library(table1)
@@
 results <- list(
-  s1 = list(demo = s1_meta),
-  s2 = list(demo = s2_meta, reg = fit_s2_vaccIntent),
-  s3 = list(demo = s3_meta, reg = fit_s3_vaccIntent),
-  s4 = list(demo = s4_meta, reg = fit_s4_vaccIntent)
+  s1 = list(demo = s1_meta, validcorrs = corrDF),
+  s2 = list(demo = s2_meta, reg = fit_s2_vaccIntent, modcorr = cor_val_s2),
+  s3 = list(demo = s3_meta, reg = fit_s3_vaccIntent, modcorr = cor_val_s3),
+  s4 = list(demo = s4_meta, reg = fit_s4_vaccIntent, modcorr = cor_val_s4)
 )

### 2021-07-20 supplement/supplement-main.Rmd
updated model figs

@@
 
-export_graph(z2, "../local/boot-graph.pdf")
+export_graph(z2, "../outputs/boot-graph.pdf")
 ```
@@
 
-cowplot::save_plot("../local/boot-graph-legend.svg", boot_graph_legend)
+cowplot::save_plot("../outputs/boot-graph-legend.svg", boot_graph_legend)
 # cowplot::ggdraw(boot_graph_legend)
@@
 ## assemble bootstrapping graph and legend into pdf and display here
-knitr::include_graphics("../local/boot-graph.pdf") 
+knitr::include_graphics("../outputs/boot-combined.pdf") 
 ```
@@
 # export graph image
-export_graph(z, "../local/main-graph.pdf")
+export_graph(z, "../outputs/main-graph.pdf")
 # render_graph(z)
@@
 
-cowplot::save_plot("../local/graph-legend.svg", main_graph_legend)
+cowplot::save_plot("../outputs/graph-legend.svg", main_graph_legend)
 # cowplot::ggdraw(main_graph_legend)
@@
 ## currently just the output graph w/ no legend (main-graph.pdf)
-knitr::include_graphics("../local/main-graph.pdf") 
+knitr::include_graphics("../outputs/main-combined.pdf") 
 ```

### 2021-07-20 supplement/supplement-main.Rmd
reverse order of x-axis on fig 6, correct scale labels

@@
          "vaccDanger" = "Vaccine Danger",
-         "vaccEff" = "Vaccine Eff.",
+         "vaccEff" = "Vaccine Effectiveness",
          "vaccIntent" = "Vaccination Intentions",
          "vaccStrain" = "IIS: Vaccines Strain",
-         "vaccTox" = "Vaccines Toxicity")}
+         "vaccTox" = "Vaccine Toxicity")}
 
@@
   ungroup() %>%
-  arrange(diff_diff) %>% # ascending because news exposure is expected to increase vaccine intentions
+  arrange(desc(diff_diff)) %>% # ascending because news exposure is expected to increase vaccine intentions
   mutate(order = 1:nrow(.))

### 2021-07-21 paper/paper.Rmd
updated model figs
added abstract draft

@@
 
-WIP
+Much of the richness of human thought is supported by people’s intuitive theories---explanatory mental frameworks that capture the perceived causal and relational structure of the world.
+But serious consequences can arise when these theories are mistaken, such as when they contain misconceptions about vaccine safety that discourage vaccination.
+We argue that addressing misconceptions requires awareness of the broader conceptual context in which they are embedded.
+Here, we examine the role of intuitive theories in misconceptions and belief revision by focusing on vaccine hesitancy as a case study.
+First, we developed a cognitive model of the intuitive theory surrounding vaccination decisions by identifying a set of relevant beliefs, surveying a large sample of U.S.
+adults, and applying Bayesian network structure learning algorithms to their responses (Study 1).Then, we applied this model to understand belief revision within this larger conceptual system.
+We found that our model helped to explain belief revision following an established educational intervention (Study 2), provided insight that supported our formulation of a novel educational intervention that successfully increased vaccination intentions (Studies 3a, 3b), and also helped to explain how people’s beliefs changed following real-world events (Study 4).
+Taken together, this work illustrates the promise of understanding belief revision in terms of intuitive theories and of discovering and formalizing intuitive theories via computational models.
+Moreover, it lays the foundation for theory-based educational interventions that could encourage people to vaccinate their children and themselves against dangerous diseases like measles and Covid-19.
 
@@
 
-knitr::include_graphics("../local/main-graph-combined.pdf")
+knitr::include_graphics("../outputs/main-combined.pdf")
 ```

### 2021-07-21 paper/paper.Rmd
cleaning up

@@
 ---
-title: "Untitled Vaccine Intuitive theories paper"
+title: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
+author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
 output: pdf_document
@@
 First, we developed a cognitive model of the intuitive theory surrounding vaccination decisions by identifying a set of relevant beliefs, surveying a large sample of U.S.
-adults, and applying Bayesian network structure learning algorithms to their responses (Study 1).Then, we applied this model to understand belief revision within this larger conceptual system.
+adults, and applying Bayesian network structure learning algorithms to their responses (Study 1).
+Then, we applied this model to understand belief revision within this larger conceptual system.
 We found that our model helped to explain belief revision following an established educational intervention (Study 2), provided insight that supported our formulation of a novel educational intervention that successfully increased vaccination intentions (Studies 3a, 3b), and also helped to explain how people’s beliefs changed following real-world events (Study 4).

### 2021-07-21 supplement/supplement-main.Rmd
fig 11 changes again

@@
 author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
-date: "Jul 20, 2021 (DRAFT)"
+date: "Jul 21, 2021 (DRAFT)"
 output:

### 2021-07-22 paper/paper.Rmd
minor fixes

@@
 Much of the richness of human thought is supported by people’s intuitive theories---explanatory mental frameworks that capture the perceived causal and relational structure of the world.
-But serious consequences can arise when these theories are mistaken, such as when they contain misconceptions about vaccine safety that discourage vaccination.
-We argue that addressing misconceptions requires awareness of the broader conceptual context in which they are embedded.
-Here, we examine the role of intuitive theories in misconceptions and belief revision by focusing on vaccine hesitancy as a case study.
-First, we developed a cognitive model of the intuitive theory surrounding vaccination decisions by identifying a set of relevant beliefs, surveying a large sample of U.S.
+But serious consequences can arise when these theories are mistaken.
+In this paper, we take up an important example of the consequences of faulty intuitive theories: when misconceptions about vaccine safety discourage vaccination.
+We argue that addressing misconceptions like these requires awareness of the broader conceptual context in which they are embedded.
+We present a cognitive model of the intuitive theory surrounding vaccination decisions, which we developed by identifying a set of relevant beliefs, surveying a large sample of U.S.
 adults, and applying Bayesian network structure learning algorithms to their responses (Study 1).
-Then, we applied this model to understand belief revision within this larger conceptual system.
+We then apply this model to understand belief revision within this larger conceptual system.
 We found that our model helped to explain belief revision following an established educational intervention (Study 2), provided insight that supported our formulation of a novel educational intervention that successfully increased vaccination intentions (Studies 3a, 3b), and also helped to explain how people’s beliefs changed following real-world events (Study 4).
 Taken together, this work illustrates the promise of understanding belief revision in terms of intuitive theories and of discovering and formalizing intuitive theories via computational models.
-Moreover, it lays the foundation for theory-based educational interventions that could encourage people to vaccinate their children and themselves against dangerous diseases like measles and Covid-19.
+Moreover, it lays the foundation for theory-based educational interventions that could encourage people to vaccinate their children and themselves against dangerous diseases like measles and COVID-19.
 
@@
 
-When people decide whether to vaccinate their children and themselves against dangerous diseases like measles and Covid-19, their decisions are affected by a network of interrelated beliefs about specific diseases, vaccine safety and efficacy, the immune system, the medical system, and health and nature more generally.
+When people decide whether to vaccinate their children and themselves against dangerous diseases like measles and COVID-19, their decisions are affected by a network of interrelated beliefs about specific diseases, vaccine safety and efficacy, the immune system, the medical system, and health and nature more generally.
 By creating a computational model of the intuitive theory connecting these different beliefs, we were able to make accurate predictions about how these beliefs are revised in light of educational interventions, design an effective new intervention encouraging vaccination, and understand how these beliefs were affected by real-world events.
@@
 Much of this type of thinking can be understood as deriving from people’s *intuitive theories*---explanatory frameworks, analogous to scientific theories, that capture the causal and logical structure of the world within a domain.
-From early in life, people are driven to seek out such causal explanations and to use their mental representations of these causal systems to explain, predict, and intervene in the world; and to make sense of new information and experiences [see @carey2009; @gelman.legare2011; @gerstenberg.etal2021; @gopnik.wellman1994; @keil1994; @murphy.medin1985; @wellman.gelman1992 for influential treatments of this topic].
-Intuitive theories inform reasoning in a wide variety of domains, from reasoning about physical systems [e.g., @baillargeon2004; @battaglia.etal2013; @spelke1994a; @ullman.etal2017], to reasoning about biological processes [e.g., @carey1985; @carey2009; @medin.atran1999] and about the contents of other people’s minds [e.g., @gopnik.wellman1994; @wellman2015; @baker.etal2017].
+From early in life, people are driven to seek out such causal explanations and to use their mental representations of these causal systems to explain, predict, and intervene in the world [see @carey2009; @gelman.legare2011; @gerstenberg.etal2021; @gopnik.wellman1994; @keil1994; @murphy.medin1985; @wellman.gelman1992 for influential treatments of this topic].
+Intuitive theories inform reasoning in a wide variety of domains, from reasoning about physical systems [e.g., @baillargeon2004; @battaglia.etal2013; @spelke1994a; @ullman.etal2017], biological processes [e.g., @carey1985; @carey2009; @medin.atran1999] andthe contents of other people’s minds [e.g., @gopnik.wellman1994; @wellman2015; @baker.etal2017].
 
 Because intuitive theories are powerful tools for making sense of the world, when these theories are mistaken there can be serious consequences.
-In this paper, we focus on a timely example: misconceptions about vaccine safety.
+In this paper, we focus on an important and timely example: misconceptions about vaccine safety.
 
@@
 Taken together, this work illustrates the promise of understanding belief revision in terms of intuitive theories and the utility of discovering and formalizing intuitive theories via computational models.
-And, it lays the foundation for empirically-validated, theory-based educational interventions that could encourage people to vaccinate their children and themselves against dangerous diseases like measles and Covid-19.
+And, it lays the foundation for empirically-validated, theory-based educational interventions that could encourage people to vaccinate their children and themselves against dangerous diseases like measles and COVID-19.
 
@@
 We used these intercorrelations to build a cognitive model of the relations among these beliefs using Bayesian network structure learning techniques, using an 80% training split of the data (*n* = 904).
-Based on the observed associations among participants' beliefs about each of theses issues, we sought to infer how these states of affairs (e.g., that vaccines are dangerous, that diseases are severe) are connected in people's intuitive theories--how people understand these states of affairs to cause, imply, or otherwise influence one another.
+Based on the observed associations among participants' beliefs about each of theses issues, we sought to infer how these states of affairs (e.g., that vaccines are dangerous, that diseases are severe) are connected in people's intuitive theories---how people understand these states of affairs to cause, imply, or otherwise influence one another.
 
@@
 Other parts of the model shed new light on the role of lay theories in vaccination decisions.
-For example, *naturalism* ---the general view that natural things are better than artificial things ---appears to be strongly related to *medical skepticism* and *parental expertise*; all three of these abstract beliefs are related to concrete beliefs that, in turn, feed into participants’ vaccination intentions.
+For example, *naturalism* ---the general view that natural things are better than artificial things ---appears to be strongly related to *medical skepticism* and *parental expertise*; and all three of these abstract beliefs are related to concrete beliefs that, in turn, feed into participants’ vaccination intentions.
 
@@
 We developed a novel educational intervention that addresses fears about toxic additives in vaccines.
-This Vaccine Ingredients intervention explained the common components of vaccines, emphasized the minute quantities of all vaccine ingredients, and explained the roles that various vaccine additives play in ensuring the stability and safety of vaccines, such as antibiotics, adjuvants, and stabilizers.
+This "vaccine ingredients" intervention explained the common components of vaccines, emphasized the minute quantities of all vaccine ingredients, and explained the roles that various vaccine additives play in ensuring the stability and safety of vaccines, such as antibiotics, adjuvants, and stabilizers.
 We gave special attention to defusing concerns about the use of formaldehyde in vaccines because our assessment of anti-vaccination websites suggested that this was a particular concern for many vaccine skeptics.
-The intervention acknowledged that some vaccines contain trace amounts of formaldehyde, but also pointed out that formaldehyde is a naturally-occurring metabolic byproduct in all living things and that it is already present in children’s bodies (and even in foods like pears) in far larger quantities than contained in any vaccine.
+The intervention acknowledged that some vaccines contain trace amounts of formaldehyde, but pointed out that formaldehyde is a metabolic byproduct that occurs naturally in all living things.
+The intervention highlights that formaldehyde is already present in children’s bodies (and even in foods like pears) in far larger quantities than contained in any vaccine.
 The full intervention text can be found in SI.
@@
 Collapsing across these two studies, Figure 5 shows the change in participants’ (*n* = `r results$s3$demo$n_complete`) attitudes across all 14 belief scales from pretest to posttest.
-Most importantly, the Vaccine Ingredients intervention significantly improved participants’ vaccination intentions compared to the no-intervention control condition.
+Most importantly, the vaccine ingredients intervention significantly improved participants’ vaccination intentions compared to the no-intervention control condition.
 Changes were also evident across many of the 14 beliefs, with the largest changes being a reduction in vaccine toxicity beliefs.

### 2021-07-23 supplement/supplement-main.Rmd
small tweaks and typos

@@
 We used a bootstrapping procedure to estimate the confidence in each of the links in this model, conducting the structure learning procedure repeatedly for 200 bootstrapped resamples of the original training data.
-Figure 3 visualizes the frequency with which each arc appeared in the resulting model across these replicates, and figure \@ref(fig:disp-maingraph) visualizes the model with the coefficients for each link encoded by color.
+Figure 3 visualizes the frequency with which each arc appeared in the resulting model across these replicates, and Figure 4 visualizes the model with the coefficients for each link encoded by color.
 
@@
 Only edges appearing in at least 20\\% of graphs are shown.
-Our primary outcome of interest, vaccination intentions, is highlighted in yellow."}
+Our primary outcome of interest, vaccination intentions, is highlighted in gray."}
 
@@
 Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links.
-Our primary outcome of interest, vaccination intentions, is highlighted in yellow."}
+Our primary outcome of interest, vaccination intentions, is highlighted in gray."}
 
@@
 Finally, when asked why most healthcare providers recommend vaccinating young children, most participants (7 of 15; 1 participant did not respond) stated explicitly that healthcare providers have financial incentives to recommend vaccination -- but many (7 of 15, including several who mentioned financial incentives) also acknowledged that healthcare providers likely believe (in the participants’ view, mistakenly) that vaccinations are harmless and effective.
-Some participants (6 of 15) stated that healthcare providers are following protocol
+Some participants (6 of 15) stated that healthcare providers are following protocol.
 
@@
 For each of the other 13 beliefs, we translated our qualitative insights into new psychometrically-valid scales through an iterative series of pilot studies not described here.
-We stipulated that each scale should be brief, composed of 4-6 statements for participants to evaluate; include at least one reverse-coded item; and be highly reliable (Cronbach’s $\alpha \geq .80$).
+We stipulated that each scale should be brief, composed of 4-6 statements for participants to evaluate; include at least one reverse-coded item; and be highly reliable in these pilot studies (observed reliability in final pilot study: all Cronbach’s $\alpha \geq .80$).
 
@@
 Studies 1-4 were conducted using online surveys (administered with Qualtrics survey software) with participants recruited from Amazon’s mechanical turk (mTurk) work distribution website.
-All studies were conducted between [dates].
+All studies were conducted between August 2017 and June 2019.
 Repeat participation was prevented, with no participants involved in more than one study, except as noted in Study 4.
@@
 ```{r fig7-s2_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiment 2.
-Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in gray.
 Right, mean observed and model predicted change scores for the Disease Risk intervention condition.
@@
 ```{r fig9-s3_plot, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
-Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in gray.
 Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition.
@@
 ```{r fig10-s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=10, fig.height=5, fig.cap="Belief changes following the intervention in Experiments 3a and 3b, broken out by experiment.
-Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in gray.
 Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition.
@@
 We attempted to contact and re-recruit as many of the `r nrow(d_bn)` participants who completed Study 1 to participate in a follow-up study in May of 2019.
-We were able to re-recruit `r s4_meta$n_recruited` participants and of these`r s4_meta$n_complete` successfully completed the study including passing all attention checks.
+We were able to re-recruit `r s4_meta$n_recruited` participants and, of these, `r s4_meta$n_complete` successfully completed the study including passing all attention checks.
 
@@
 ```{r fig11-s4_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4.
-Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
+Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York; our primary outcome of interest, vaccination intentions, is highlighted in gray.
 Right, mean observed and model predicted change scores for those who were exposed to news of the outbreak.
@@
 
-At the beginning of the study, participants read the following instructions: “In this study, you will be asked to read a range of statements.
+_Text of the belief scales used in Studies 1-4_
+
+At the beginning of each study, participants read the following instructions: “In this study, you will be asked to read a range of statements.
 Some of these statements may be controversial, and others less so.
@@
 On each page, participants were asked to rate “how much you agree or disagree” on a 7-point scale from “Strongly disagree” to “Strongly agree.” After completing all 14 scales, participants were asked standard demographics questions (gender, age, race/ethnicity, religious affiliation, educational attainment, annual household income) as well as a handful of questions about whether they were or were expecting to be a parent.
-The study concluded with a brief statement about the safety of vaccines, as follows: “We very much appreciate hearing your opinions about these various issues.
+
+In Study 1, but not Studies 2-4, the study concluded with a brief statement about the safety of vaccines, as follows: “We very much appreciate hearing your opinions about these various issues.
 Some of these statements concerned vaccines.

### 2021-07-25 paper/paper.Rmd
kara's edits

@@
 We then apply this model to understand belief revision within this larger conceptual system.
-We found that our model helped to explain belief revision following an established educational intervention (Study 2), provided insight that supported our formulation of a novel educational intervention that successfully increased vaccination intentions (Studies 3a, 3b), and also helped to explain how people’s beliefs changed following real-world events (Study 4).
+Our model helped to explain belief revision following an established educational intervention (Study 2), provided insight that supported our formulation of a novel educational intervention that successfully increased vaccination intentions (Studies 3a, 3b), and also helped to explain how people’s beliefs changed following real-world events (Study 4).
 Taken together, this work illustrates the promise of understanding belief revision in terms of intuitive theories and of discovering and formalizing intuitive theories via computational models.
@@
 From early in life, people are driven to seek out such causal explanations and to use their mental representations of these causal systems to explain, predict, and intervene in the world [see @carey2009; @gelman.legare2011; @gerstenberg.etal2021; @gopnik.wellman1994; @keil1994; @murphy.medin1985; @wellman.gelman1992 for influential treatments of this topic].
-Intuitive theories inform reasoning in a wide variety of domains, from reasoning about physical systems [e.g., @baillargeon2004; @battaglia.etal2013; @spelke1994a; @ullman.etal2017], biological processes [e.g., @carey1985; @carey2009; @medin.atran1999] andthe contents of other people’s minds [e.g., @gopnik.wellman1994; @wellman2015; @baker.etal2017].
+Intuitive theories inform reasoning in a wide variety of domains, including reasoning about physical systems [e.g., @baillargeon2004; @battaglia.etal2013; @spelke1994a; @ullman.etal2017], biological processes [e.g., @carey2009; @carey1985; @medin.atran1999] and the contents of other people’s minds [e.g., @gopnik.wellman1994; @wellman2015; @baker.etal2017].
 
@@
 The way in which evidence affects any particular belief is unavoidably shaped by other interrelated beliefs.
-Duhem [-@duhem1954] and Quine [-@quine1951] famously argued that scientific theories necessarily incorporate *auxiliary hypotheses* that influence how observations are interpreted: When an observation is inconsistent with a hypothesis under certain auxiliary assumptions, a scientist cannot necessarily know whether to revise the hypothesis or the auxiliary assumptions.
+Duhem [-@duhem1954] and Quine [-@quine1951] famously argued that scientific theories necessarily incorporate *auxiliary hypotheses* that influence how observations are interpreted: When an observation is inconsistent with a hypothesis under certain auxiliary assumptions, a scientist cannot know whether to revise the hypothesis or the auxiliary assumptions.
 Similarly, we argue that intuitive theories incorporate auxiliary beliefs that affect how other beliefs are revised in light of evidence [also see @gershman2019].
@@
 This model can also capture how these beliefs might covary across individuals: if two people hold different degrees of belief in FIRE, this model specifies the degree of belief each should have in SMOKE (Feature 2).
-Moreover, both the correlation in beliefs across individuals and the change in beliefs given observations are determined by the conditional probability of SMOKE given FIRE.
-Thus, changes in beliefs following evidence will be proportional to their correlations across individuals (Feature 3).
+Because the condition probability of SMOKE given FIRE determines both the change in beliefs given observations and the correlation in beliefs across individuals, changes in beliefs following evidence will be proportional to their correlations across individuals (Feature 3).
 Formulating these features in a formal model, rather than a verbal theory, allows us to specify not just the presence but the quantitative strength of these relations, and to simulate the cumulative influences of many factors in more complex networks (for example, incorporating beliefs about the frequency of wildfires, recent weather conditions, etc.).
@@
 Here, we used Bayesian network structure learning algorithms to construct a model of the intuitive theory underlying adults’ decisions about whether or not to vaccinate children against diseases like measles, mumps, and rubella.
-
-# Current studies
 
@@
 
-We used these intercorrelations to build a cognitive model of the relations among these beliefs using Bayesian network structure learning techniques, using an 80% training split of the data (*n* = 904).
+We used these intercorrelations to build a cognitive model of the relations among these beliefs via Bayesian network structure learning techniques, using an 80% training split of the data (*n* = 904).
 Based on the observed associations among participants' beliefs about each of theses issues, we sought to infer how these states of affairs (e.g., that vaccines are dangerous, that diseases are severe) are connected in people's intuitive theories---how people understand these states of affairs to cause, imply, or otherwise influence one another.
@@
 
-```{r fig1-maingraph, fig.align='center', fig.height=8, fig.width=5, fig.cap="Bayesian network model resulting from hill-climbing algorithm applied to data in Study 1 training test split (n = 904).
+```{r fig1-maingraph, fig.align='center', fig.height=8, fig.width=5, fig.cap="Bayesian network model resulting from hill-climbing algorithm applied to data in Study 1 training split (n = 904).
 The network has 29 edges connecting these 14 variables.
@@
 The intervention acknowledged that some vaccines contain trace amounts of formaldehyde, but pointed out that formaldehyde is a metabolic byproduct that occurs naturally in all living things.
-The intervention highlights that formaldehyde is already present in children’s bodies (and even in foods like pears) in far larger quantities than contained in any vaccine.
+The intervention highlighted that formaldehyde is already present in children’s bodies (and even in foods like pears) in far larger quantities than contained in any vaccine.
 The full intervention text can be found in SI.
@@
 ```{r fig6-s4, fig.align='center', fig.height=4, fig.width=7, fig.cap="Participants’ belief changes from participation in Study 1 to Study 4.
-Left, mean difference scores comparing beliefs reported in September 2017 and May 2019 for the 14 belief scales, across participants who did and did not report exposure to news of the ongoing New York measles outbreak.
+Left, mean difference scores comparing beliefs reported in August-September 2017 and May 2019 for the 14 belief scales, across participants who did and did not report exposure to news of the ongoing New York measles outbreak.
 Right, mean observed and model predicted change scores for those participants who did report exposure to this news.
@@
 
-To examine this possibility, we invited participants from Study 1 (conducted in September 2017) to participate in a new study measuring each of those 14 beliefs again (conducted on May 1st, 2019; approximately 18 months later).
+To examine this possibility, we invited participants from Study 1 (conducted in August-September 2017) to participate in a new study measuring each of those 14 beliefs again (conducted on May 1st, 2019; approximately 18 months later).
 Of the `r results$s1$demo$n_include` participants in Study 1, `r results$s4$demo$n_complete` returned and completed the study.
@@
 We drew on a variety of sources, including academic articles on anti-vaccine skepticism [e.g.,  @dube.etal2015; @larson.etal2015; @salmon.etal2015; @williams2014], anti-vaccine websites, and a qualitative survey with self-identified vaccine skeptics (*n*=16) via Amazon Mechanical Turk (MTurk) to generate a list of beliefs that might influence people’s decisions about whether to vaccinate their children (*vaccine intentions*): *vaccine danger*, *toxic additives in vaccines*, *vaccine effectiveness*, *disease rarity*, *disease severity, infant immune system (IIS): weakness*, *IIS: limited capacity*, *IIS: vaccines strain*, *parental protectiveness*, *parental expertise*, *medical skepticism*, *naturalism*, and *holistic balance*.
-(See main text for descriptions, and SI for the items included in these scales.) We translated these qualitative insights into 14 psychometrically-valid scales; each scale measured agreement with 4-6 statements, including at least one reverse-coded item, and was highly reliable (All Cronbach’s $\alpha \geq .73$).
+(See main text for descriptions, and SI for the items included in these scales.) We translated these qualitative insights into 14 psychometrically-valid scales; each scale measured agreement with 4-6 statements, including at least one reverse-coded item, and was highly reliable (observed reliability, Study 1: all Cronbach’s $\alpha \geq .73$).
 We developed 13 of these scales, and included one preexisting scale [the “holistic balance” subscale from @mcfadden.etal2010].
@@
 
-Studies 1-4 were conducted online via Amazon Mechanical Turk.
+Studies 1-4 were conducted online via Amazon Mechanical Turk between August 2017 and June 2019.
 Repeat participation was prevented, with no participants involved in more than one study, except as noted in Study 4.
@@
 
-As they shared the same design, we combined data from studies 3a and 3b for analysis.
+As they shared the same design, we combined data from studies 3a and 3b for analysis (but see SI for separate analyses by study).
 As in study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine toxins intervention on participants’ *vaccination intentions* scores.
@@
 
-Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (September 2017 vs.
+Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (August-September 2017 vs.
 May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item.
 To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure.
-Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months ago (interaction effect: $b$ = `r round(s4_reg$fixed[9,1],3)`, 95% CI: [`r round(s4_reg$fixed[9,3], 3)`, `r round(s4_reg$fixed[9,4], 3)`]); see Figure 6, panel A.
+Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months earlier (interaction effect: $b$ = `r round(s4_reg$fixed[9,1],3)`, 95% CI: [`r round(s4_reg$fixed[9,3], 3)`, `r round(s4_reg$fixed[9,4], 3)`]); see Figure 6, panel A.
 

### 2021-07-25 supplement/supplement-main.Rmd
kara's edits

--- 2021-07-21 supplement/supplement-main.Rmd
@@
 
-Figure 9 (right) shows the correlation between predicted and observed belief changes conditional on the Vaccine Ingredients intervention.
-
 ```{r fig9-s3_plot, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
@@
 ```
+
+Figure 9 (right) shows the correlation between predicted and observed belief changes conditional on the Vaccine Ingredients intervention.
+the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker (*r* = `r cor_val_s3`) than those observed in our other studies.
+
+In Study 3a, we observed smaller differences than predicted for vaccineeffectiveness (observed minus predicted difference: -0.07), IIS: weak (-0.06), and vaccine intentions (-0.06); and larger differences than predicted for vaccine danger (+0.06), and parental expertise (+0.05); all other discrepancies were smaller than ±0.05.
+
+In Study 3b, we again observed smaller differences than predicted for vaccine effectiveness (observed minus predicted difference: -0.06) and vaccine intentions (-0.05); and in this case we observed larger differences than predicted for naturalism (+0.05); all other discrepancies were smaller than ± 0.05.
 

### 2021-07-25 supplement/supplement-main.Rmd

--- 2021-07-23 supplement/supplement-main.Rmd
@@
 
-Figure 9 (right) shows the correlation between predicted and observed belief changes conditional on the Vaccine Ingredients intervention.
-
 ```{r fig9-s3_plot, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
-Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in gray.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
 Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition.
@@
 
+Figure 9 (right) shows the correlation between predicted and observed belief changes conditional on the Vaccine Ingredients intervention.
+the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker (*r* = `r cor_val_s3`) than those observed in our other studies.
+
+In Study 3a, we observed smaller differences than predicted for vaccineeffectiveness (observed minus predicted difference: -0.07), IIS: weak (-0.06), and vaccine intentions (-0.06); and larger differences than predicted for vaccine danger (+0.06), and parental expertise (+0.05); all other discrepancies were smaller than ±0.05.
+
+In Study 3b, we again observed smaller differences than predicted for vaccine effectiveness (observed minus predicted difference: -0.06) and vaccine intentions (-0.05); and in this case we observed larger differences than predicted for naturalism (+0.05); all other discrepancies were smaller than ± 0.05.
+
 ```{r fig10-s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=10, fig.height=5, fig.cap="Belief changes following the intervention in Experiments 3a and 3b, broken out by experiment.
-Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in gray.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
 Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition.

### 2021-07-26 supplement/supplement-main.Rmd
minor text edits

@@
 ---
-title: "Supplemental Materials"
-subtitle: "Untitled vaccination intuitive theory paper"
+title: "Supplemental Information"
+subtitle: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
 author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
-date: "Jul 21, 2021 (DRAFT)"
 output:
@@
 
+# Data Availability
+
+Data and code for this project are available at: https://github.com/derekpowell/int-theory-vacc
+
+Preregistrations information is available at: https://osf.io/uemq4
+
+\newpage
+
 ```{r, echo=FALSE}

### 2021-07-26 paper/paper.Rmd
minor paper edit
minor text edits
revisions before submit

@@
 But serious consequences can arise when these theories are mistaken.
-In this paper, we take up an important example of the consequences of faulty intuitive theories: when misconceptions about vaccine safety discourage vaccination.
-We argue that addressing misconceptions like these requires awareness of the broader conceptual context in which they are embedded.
+In this paper, we take up an important example of these risks: when misconceptions about vaccine safety discourage vaccination.
+We argue that addressing misconceptions like these requires awareness of the broader conceptual contexts in which they are embedded.
 We present a cognitive model of the intuitive theory surrounding vaccination decisions, which we developed by identifying a set of relevant beliefs, surveying a large sample of U.S.
@@
 
-When people decide whether to vaccinate their children and themselves against dangerous diseases like measles and COVID-19, their decisions are affected by a network of interrelated beliefs about specific diseases, vaccine safety and efficacy, the immune system, the medical system, and health and nature more generally.
+When people decide whether to vaccinate their children and themselves against dangerous diseases like measles and COVID-19, their decisions are affected by a network of interrelated beliefs about specific diseases, vaccine safety and efficacy, the immune system, the medical system, health, and nature more generally.
 By creating a computational model of the intuitive theory connecting these different beliefs, we were able to make accurate predictions about how these beliefs are revised in light of educational interventions, design an effective new intervention encouraging vaccination, and understand how these beliefs were affected by real-world events.
@@
 One respondent wrote that vaccines were “A BIG MONEY MAKING SCAM BY THE BIG PHARMS” (emphasis theirs); another thought that health professionals “are brainwashed by the medical media and the government.” To people holding these beliefs, it could well seem unreasonable to vaccinate a 2-month-old baby against 5 or more diseases at once.
-Moreover, if skeptics believe that the medical community is unduly influenced by pharmaceutical companies, they might doubt the validity of medical studies coming out in favor of these companies’ interests.
+Moreover, if skeptics believe that the medical community is unduly influenced by pharmaceutical companies, they might doubt the validity of medical findings that favor these companies’ interests.
 Altogether, these beliefs might sustain misconceptions about vaccine safety, even in the face of counter-evidence.
@@
 This model can also capture how these beliefs might covary across individuals: if two people hold different degrees of belief in FIRE, this model specifies the degree of belief each should have in SMOKE (Feature 2).
-Because the condition probability of SMOKE given FIRE determines both the change in beliefs given observations and the correlation in beliefs across individuals, changes in beliefs following evidence will be proportional to their correlations across individuals (Feature 3).
+Because the conditional probability of SMOKE given FIRE determines both the change in beliefs given observations and the correlation of beliefs across individuals, changes in beliefs following evidence will be proportional to their correlations across individuals (Feature 3).
 Formulating these features in a formal model, rather than a verbal theory, allows us to specify not just the presence but the quantitative strength of these relations, and to simulate the cumulative influences of many factors in more complex networks (for example, incorporating beliefs about the frequency of wildfires, recent weather conditions, etc.).
@@
 
-In Study 1, we used Bayesian network structure learning algorithms to develop a cognitive model of the relationships among 14 beliefs related to vaccine hesitancy in a large sample of people.
+In Study 1, we used Bayesian network structure learning algorithms to develop a cognitive model of the relationships among 14 beliefs related to vaccine hesitancy in a large sample of U.S.
+adults.
 In Study 2, we replicated the success of an existing intervention emphasizing the dangers of childhood diseases [@horne.etal2015] and used our model to provide a more detailed understanding of *how and why* this intervention increases vaccine intentions and its effects on related beliefs.
@@
 
-These included a variety of claims about vaccines, including beliefs about (1) the overall danger of vaccines (*vaccine danger*); (2) *toxic additives in vaccines*; and (3) *vaccine effectiveness*, how effective vaccines are in preventing disease; as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about (4) *disease rarity* and (5) *disease severity*.
-Beyond this, we theorized that participants’ understanding of the infant immune system might be relevant, including beliefs that (6) the infant immune system is weak (*IIS: weakness*); (7) the infant immune system is limited in its capacity and can be easily overwhelmed (*IIS: limited capacity*); and (8) vaccines strain the infant immune system (*IIS: vaccines strain*).
-We also included general theories about parenting and medicine: (11) general *parental protectiveness*; (12) *parental expertise*, namely the belief that parents usually know more about their children’s health than medical experts; and (13) *medical skepticism*, including concerns about pharmaceutical companies and corruption in the medical community; and two two broad worldviews: (9) *naturalism*, a general preference for natural over artificial things; and (10) *holistic balance*, one important aspect of attitudes toward alternative medicine (e.g., “The body is essentially self-healing and the task of a health care provider is to assist the healing process”; [@mcfadden.etal2010]).
+These included a variety of claims about vaccines, including beliefs about 1) the overall danger of vaccines (*vaccine danger*); 2) *toxic additives in vaccines*; and 3) *vaccine effectiveness*, how effective vaccines are in preventing disease; as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about 4) *disease rarity* and 5) *disease severity*.
+Beyond this, we theorized that participants’ understanding of the infant immune system might be relevant, including beliefs that 6) the infant immune system is weak (*IIS: weakness*); 7) the infant immune system is limited in its capacity and can be easily overwhelmed (*IIS: limited capacity*); and 8) vaccines strain the infant immune system (*IIS: vaccines strain*).
+We also included general theories about parenting and medicine: 9) general *parental protectiveness*; 10) *parental expertise*, namely the belief that parents usually know more about their children’s health than medical experts; and 11) *medical skepticism*, including concerns about pharmaceutical companies and corruption in the medical community; and two two broad worldviews: 12) *naturalism*, a general preference for natural over artificial things; and 13) *holistic balance*, one important aspect of attitudes toward alternative medicine (e.g., “The body is essentially self-healing and the task of a health care provider is to assist the healing process”; [@mcfadden.etal2010]).
 
@@
 For instance, we stipulated that *vaccine intentions* would be a “child node,” with edges only flowing inwards and not outwards (since one’s intention to vaccinate cannot “generate” the facts about vaccinations safety, effectiveness, etc).
-These constraints and their consequences are considered in more detail in Methods.
+These constraints and their consequences are considered in more detail in Materials and methods.
 
@@
 
-```{r fig1-maingraph, fig.align='center', fig.height=8, fig.width=5, fig.cap="Bayesian network model resulting from hill-climbing algorithm applied to data in Study 1 training split (n = 904).
+```{r fig1-maingraph, fig.align='center', fig.height=8, fig.width=5, fig.cap="Bayesian network model resulting from hill-climbing algorithm with our generative-model constraints applied to data in Study 1 training split (n = 904).
 The network has 29 edges connecting these 14 variables.
@@
 Not only did participants exposed to the intervention come to see childhood diseases as more severe, they also came to see vaccines as less dangerous, and demonstrated less medical skepticism as well as less commitment to “holistic balance”.
-These results suggest that targeted educational interventions could have wide-ranging effects, from influencing whom people turn to for future information, to shaping the more abstract worldviews they bring to bear in understanding health and science.
+These results suggest that targeted educational interventions could have wide-ranging effects, from influencing who people turn to for future information, to shaping the more abstract worldviews they bring to bear in understanding health and science.
 
@@
 One explanation is that this intervention provides direct evidence for *disease severity* beliefs and that other beliefs are revised as a result of their relationships with *disease severity* as captured in the intuitive theory.
-To examine this, we used the same model developed in Study 1 to simulate how the 13 other beliefs in the intuitive theory would change if we intervened directly on *disease severity* (see Methods).
+To examine this, we used the same model developed in Study 1 to simulate how the 13 other beliefs in the intuitive theory would change as a result of the observed change in *disease severity* beliefs (see Materials and methods).
 As shown in Figure 3, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (*r* = `r results$s2$modcorr`).
@@
 
-To examine this possibility, we invited participants from Study 1 (conducted in August-September 2017) to participate in a new study measuring each of those 14 beliefs again (conducted on May 1st, 2019; approximately 18 months later).
+To examine this possibility, we invited participants from Study 1 (conducted in August-September 2017) to participate in a new study measuring each of those 14 beliefs again (conducted from May 1st to 3rd, 2019; approximately 18 months later).
 Of the `r results$s1$demo$n_include` participants in Study 1, `r results$s4$demo$n_complete` returned and completed the study.
@@
 Modeling this intuitive theory formally as a Bayesian network allowed us to create a cognitive model that demonstrates these key features of intuitive theories quantitatively.
-Looking forward, this formal representation ---though simplified and imperfect ---lays a foundation for richer and more complex descriptions in the future: For instance, networks with richer parameterizations could capture how intuitive theories differ across individuals, opening up the possibility of fine-tuning predictions and perhaps even crafting tailored educational interventions for specific individuals or groups.
+Looking forward, this formal representation ---though simplified and imperfect ---lays a foundation for richer and more complex descriptions in the future.
+For instance, networks with richer parameterizations could capture how intuitive theories differ across individuals, opening up the possibility of fine-tuning predictions and perhaps even crafting tailored educational interventions for specific individuals or groups.
 
@@
 
-# Methods
+# Materials and methods
 
@@
 
-$$P(y) = 1 \big[1-(1-w_0)\prod_i(1-w_i)^{x_i}\big]\prod_j(1-w_j)^{x_j}$$
+$$P(y) = \Big(1-(1-w_0)\prod_i(1-w_i)^{x_i}\Big)\prod_j(1-w_j)^{x_j}$$
 
@@
 The weight $w_0$ represents the “leak” probability, or the baseline probability that the child occurs without any other generating influences.
-The first term in brackets represents the probability that $y$ is generated (or, put another way, that not all of the possible generating forces fail to generate it).
+The first term represents the probability that $y$ is generated (or, put another way, that not all of the possible generating forces fail to generate it).
 The second term represents the probability that it is not then prevented [i.e., that all the preventing forces fail; see @maaskant.druzdzel2008].
@@
 In particular, we applied what we call the “generative model principle,” specifying that influence relations (edges) should flow from causes (or other generating states of affairs) to effects; instilling a core assumption in research on intuitive theories and causal explanatory reasoning [e.g.
-@gopnik.etal2004; @gerstenberg.etal2021; @cheng1997].
+@gerstenberg.etal2021; @gopnik.etal2004; @cheng1997].
 We sorted the 14 measured beliefs into four tiers based on how general or abstract each belief was, reasoning that general and abstract states of affairs should be understood to cause (or otherwise generate) more specific and concrete states of affairs, so edges should flow from the general and abstract toward the specific and concrete (e.g., if natural things are better than artificial things, this should set an expectation about whether a specific class of artificial things--vaccines--is safe).
@@
 These nodes are connected in the model, but the edges between them run in the opposite directions, and therefore do not support a clear causal interpretation.
+One interpretation is that this edge instead reflects a set membership relation; that toxins are one type of danger vaccines might present.
 In other cases, our data and explicit constraints do not perfectly identify the directions of the edges.
-This is the case for two edges (Naturalism $\rightarrow$  Holistic Balance and Medical Skepticism $\rightarrow$ Parental Expertise; see supplemental implementation for details).
+This is the case for two edges (Naturalism $\rightarrow$  Holistic Balance and Medical Skepticism $\rightarrow$ Parental Expertise; see SI for details).
 In both cases, we do not feel it is intuitive which direction the edge should flow in, nor even that it should be directed at all; we might even speculate there is an additional unmeasured variable that connects these beliefs and that would best account for their association.
@@
 In Phase 2 (approximately two days later), participants completed a study very similar to Horne et al.’s (2015) original intervention study.
-Participants were randomly assigned to either the disease risk condition or the No Intervention condition, with the constraint that the distributions of participants’ Phase 1 *vaccine intentions* scores should be similar across the two conditions; we accomplished this by stratifying participants into three groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
+Participants were randomly assigned to either the disease risk condition or the no-intervention condition, with the constraint that the distributions of participants’ Phase 1 *vaccine intentions* scores should be similar across the two conditions; we accomplished this by stratifying participants into three groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
 
@@
 
-Participants in the No Intervention condition completed the belief scales and demographics questions without reading any material first.
+Participants in the no-intervention condition completed the belief scales and demographics questions without reading any material first.
 
@@
 These studies followed similar design procedures as Study 2, with phase 2 conducted 1-2 days after phase 1.
-In both Study 3a (April 2019) and Study 3b (May 2019; combined final *n* = `r results$s3$demo$n_complete`) the vaccine toxin intervention was compared against no-intervention control.
+In both Study 3a (April 2019) and Study 3b (May 2019; combined final *n* = `r results$s3$demo$n_complete`) the vaccine ingredients intervention was compared against no-intervention control.
+Unlike Study 2, we did not stratify participants before random assignment to conditions.
 
@@
 As they shared the same design, we combined data from studies 3a and 3b for analysis (but see SI for separate analyses by study).
-As in study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine toxins intervention on participants’ *vaccination intentions* scores.
-The vaccine toxins intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: $b$ = `r round(s3_reg$fixed[9,1],3)`, 95% CI: [`r round(s3_reg$fixed[9,3], 3)`, `r round(s3_reg$fixed[9,4], 3)`]); see Figure 5, panel A.
+As in study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine ingredients intervention on participants’ *vaccination intentions* scores.
+The vaccine ingredients intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: $b$ = `r round(s3_reg$fixed[9,1],3)`, 95% CI: [`r round(s3_reg$fixed[9,3], 3)`, `r round(s3_reg$fixed[9,4], 3)`]); see Figure 5, panel A.
 However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: $b$ = `r round(s3_reg$fixed[7,1],3)`, 95% CI: [`r round(s3_reg$fixed[7,3], 3)`, `r round(s3_reg$fixed[7,4], 3)`]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
@@
 
-To model the effect of the vaccine toxicity intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the vaccine toxicity intervention as a child of the vaccine toxins belief node (for details, see SI).
+To model the effect of the vaccine ingredients intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the vaccine ingredients intervention as a child of the vaccine toxins belief node (for details, see SI).
 This allowed us to predict how other beliefs in the network would change in light of the observed changes participant’s beliefs about whether vaccines contain dangerous toxins; see Figure 5, panel B.

### 2021-07-26 supplement/supplement-main.Rmd
revisions before submit

@@
 ---
-title: "Supplemental Information"
+title: "Supporting Information"
 subtitle: "Modeling and leveraging intuitive theories to improve vaccine attitudes"

### 2021-07-26 paper/paper.Rmd
more presub fixes

@@
 But serious consequences can arise when these theories are mistaken.
-In this paper, we take up an important example of these risks: when misconceptions about vaccine safety discourage vaccination.
-We argue that addressing misconceptions like these requires awareness of the broader conceptual contexts in which they are embedded.
-We present a cognitive model of the intuitive theory surrounding vaccination decisions, which we developed by identifying a set of relevant beliefs, surveying a large sample of U.S.
-adults, and applying Bayesian network structure learning algorithms to their responses (Study 1).
-We then apply this model to understand belief revision within this larger conceptual system.
-Our model helped to explain belief revision following an established educational intervention (Study 2), provided insight that supported our formulation of a novel educational intervention that successfully increased vaccination intentions (Studies 3a, 3b), and also helped to explain how people’s beliefs changed following real-world events (Study 4).
+In this paper, we consider an important and timely example of these risks: when misconceptions about vaccine safety discourage vaccination.
+We argue that addressing misconceptions requires awareness of the broader conceptual contexts in which they are embedded.
+To this end, we sought to develop a cognitive model of the intuitive theory surrounding vaccination decisions.
+From qualitative research, we identified a set of beliefs relevant to this intuitive theory.
+Then, we built our model by surveying a large sample of U.S.
+adults and applying Bayesian network structure learning algorithms to their responses to uncover the connections among these beliefs (Study 1).
+The resulting model supports understanding of belief revision within this larger conceptual system: Our model helped to explain belief revision following an established educational intervention (Study 2), provided insight that supported our formulation of a novel educational intervention that successfully increased vaccination intentions (Studies 3a, 3b), and also helped to explain how people’s beliefs changed following real-world events (Study 4).
 Taken together, this work illustrates the promise of understanding belief revision in terms of intuitive theories and of discovering and formalizing intuitive theories via computational models.
@@
 One explanation is that this intervention provides direct evidence for *disease severity* beliefs and that other beliefs are revised as a result of their relationships with *disease severity* as captured in the intuitive theory.
-To examine this, we used the same model developed in Study 1 to simulate how the 13 other beliefs in the intuitive theory would change as a result of the observed change in *disease severity* beliefs (see Materials and methods).
+To examine this, we used the same model developed in Study 1 to simulate how the 13 other beliefs in the intuitive theory would change as a result of the intervention's direct effect on *disease severity* beliefs (see Materials and methods).
 As shown in Figure 3, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (*r* = `r results$s2$modcorr`).
@@
 
-To conduct an efficient search through the super-exponential space of DAGs, we tested several learning algorithms implemented in the “bnlearn” R package [@scutari2010] and evaluated their performance through cross validation in our training split (see SI).
+To conduct an efficient search through the super-exponential space of graphs, we tested several learning algorithms implemented in the “bnlearn” R package [@scutari2010] and evaluated their performance through cross validation in our training split (see SI).
 Following this analysis, we chose to fit our model with the score-based “hill-climbing” algorithm, scoring models via the Bayesian Information Criteria, an asymptotic estimate of the likelihood of the data under a given graph structure.

### 2021-07-26 supplement/supplement-main.Rmd
more presub fixes

@@
 Through this case study we hope to shed light on why such misconceptions persist and how educators and interventionists might address misconceptions more effectively across domains.
-We argue that correcting misconceptions requires presenting evidence in a way that is sensitive to and persuasive within the broader conceptual context in which those misconceptions reside (see Gershman, 2018; Weisman & Markman, 2017).
+We argue that correcting misconceptions requires presenting evidence in a way that is sensitive to and persuasive within the broader conceptual context in which those misconceptions reside [see @gershman2019; @weisman.markman2017].
 Understanding the revision of any one specific belief (e.g., a misconception like _vaccines are dangerous_) demands a holistic understanding of the wider set of related beliefs that make up people's intuitive theories.
@@
 In this graph, the edge $FIRE \rightarrow SMOKE$ captures that fire causes smoke.^[The example of cause and effect is especially intuitive, but these edges need not be causal.
-Instead, they are better thought of as representing “influence relations”, which may also include relationships like logical implication and set membership (Williamson, 2001).] This relationship is represented as a probabilistic function, where the probability of smoke depends on the probability of fire.
+Instead, they are better thought of as representing “influence relations”, which may also include relationships like logical implication and set membership [@williamson2001].] This relationship is represented as a probabilistic function, where the probability of smoke depends on the probability of fire.
 The probability of a node Y can be defined from its parents X in many different ways.
@@
 This is also reflected in a bootstrapping analysis applying our chosen structure learning algorithm against 1000 bootstrapped replicates of our data.
-We found that the direction of some edges within the graph differed across bootstrapped runs (Holistic balance -- naturalism, medical skepticism -- parental expertise), but that these unintuitive relationships surrounding _vaccine toxicity_ were robust.
+We found that the direction of some edges within the graph differed across bootstrapped runs (Holistic balance $\rightarrow$ naturalism, medical skepticism $\rightarrow$ parental expertise), but that these relationships surrounding _vaccine toxicity_ were robust.
 
@@
 Certainly, they call for caution in interpreting the relationships represented in this model.
-Due to their tight connections with structural causal networks, it is tempting to interpret the edges in Bayesian networks as “causal.” However, these relationships are best thought of as probabilistic dependencies or “influence” relations (Williamson, 2001).
+Due to their tight connections with structural causal networks, it is tempting to interpret the edges in Bayesian networks as “causal.” However, these relationships are best thought of as probabilistic dependencies or “influence” relations [@williamson2001].
 Indeed, there are other cases where it is unclear if an edge should be directed at all: e.g., it is not obvious to us what would be the “correct” direction for the edge between naturalism and holistic balance.
@@
 Due to their tight connections with structural causal networks, it is tempting to interpret the edges in Bayesian networks as “causal”.
-However, these relationships are best thought of simply as probabilistic dependencies or “influence” relations (cite).
+However, these relationships are best thought of simply as probabilistic dependencies or “influence” relations [@williamson2001].
 Indeed, there are other cases where it is unclear if an edge should be directed at all: e.g., it is not obvious to us what would be the “correct” direction for the edge between naturalism and holistic balance.
@@
 This hierarchical structure is at least partly a product of our constraints that sorted these beliefs into “tiers” of abstractness.
-However, the [fact that a model with these constraints still functions well for prediction demonstrates that this hierarchical structure is plausible].
+However, the fact that a model with these constraints provides similarly strong fits as those without these constraints demonstrates that this hierarchical structure is plausible.
 
@@
 To model the effects of participants observing evidence, we augmented the Bayesian network representing the cognitive model (shown in Figure 4) with an additional node representing the evidence.
-For instance, to model the effects of the “Disease Risk” intervention (Study 2), we added an evidence node as a child of “disease severity,” acting as virtual evidence for this node.
+For instance, to model the effects of the “disease risk” intervention (Study 2), we added an evidence node as a child of “disease severity,” acting as virtual evidence for this node.
 To compute the CPT for this node as a function of disease severity beliefs, we estimated an _evidence ratio_ based on participants’ pretest and posttest credences in disease severity.
@@
 Drawing on these responses as well as anti-vaccine websites and academic articles on anti-vaccine skepticism [@dube.etal2015, @larson.etal2015, @salmon.etal2015, @williams2014], we generated a list of 13 underlying beliefs that might influence people’s decisions about whether to vaccinate their children (_vaccine intentions_, the last of our 14 beliefs).
-These included a variety of claims about vaccines, including beliefs about (1) the overall danger of vaccines (_vaccine danger_); (2) _toxic additives in vaccines_; and (3) _vaccine effectiveness_, how effective vaccines are in preventing disease; as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about (4) _disease rarity _and (5) _disease severity_.
+These included a variety of claims about vaccines, including beliefs about (1) the overall danger of vaccines (_vaccine danger_); (2) _toxic additives in vaccines_; and (3) _vaccine effectiveness_, how effective vaccines are in preventing disease; as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about (4) _disease rarity_ and (5) _disease severity_.
 Inspired by the many participants who invoked concerns about the effect of vaccines on infants’ immature immune systems, we also developed scales to assess beliefs that (6) the infant immune system is weak (_IIS: weakness_); (7) the infant immune system is limited in its capacity and can be easily overwhelmed (_IIS: limited capacity_); and (8) vaccines strain the infant immune system (_IIS: vaccines strain_).
@@
 
+```{r s1_meta, include=FALSE}
+s1_meta <- list(
+  n_total = nrow(s1_all),
+  n_exclude = s1_all %>% filter(exclude==1) %>%  nrow(),
+  n_include =  s1_all %>% filter(exclude==0) %>%  nrow()
+)
+```
+
 Studies 1-4 were conducted using online surveys (administered with Qualtrics survey software) with participants recruited from Amazon’s mechanical turk (mTurk) work distribution website.
@@
 Repeat participation was prevented, with no participants involved in more than one study, except as noted in Study 4.
-A total of # participants completed their participation in these studies.
-All participants had gained approval for ≥ 95% of previous work (≥ 100 assignments); had verified US MTurk accounts; and indicated that they were ≥ 18 years old.
+A total of `r s1_meta$n_include + s2_meta$n_complete + s3_meta$n_complete` participants completed their participation in these studies.
+All participants had gained approval for $\geq$ 95% of previous work ($\geq$ 100 assignments); had verified US MTurk accounts; and indicated that they were $\geq$ 18 years old.
 See the participant demographics summary section below for full demographic information.
@@
 ### Participants
-
-```{r s1_meta, include=FALSE}
-s1_meta <- list(
-  n_total = nrow(s1_all),
-  n_exclude = s1_all %>% filter(exclude==1) %>%  nrow(),
-  n_include =  s1_all %>% filter(exclude==0) %>%  nrow()
-)
-```
 
@@
 On Day 2 (approximately two days later), participants completed a study that was designed to be very similar to Horne, Powell, et al.’s [-@horne.etal2015] original study.
-Participants were randomly assigned to either the Disease Risk condition or the No Intervention condition, with the constraint that the distributions of participants’ Day 1 _vaccine intentions_ should be similar across the two conditions; we accomplished this by stratifying participants into groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
-
-Participants were presented with a slightly modified version of the “Disease Risk” intervention from Horne et al.’s [-@horne.etal2015] original study, which was based on materials available on the CDC website.
+Participants were randomly assigned to either the disease risk condition or the no-intervention condition, with the constraint that the distributions of participants’ Day 1 _vaccine intentions_ should be similar across the two conditions; we accomplished this by stratifying participants into groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
+
+Participants were presented with a slightly modified version of the “disease risk” intervention from Horne et al.’s [-@horne.etal2015] original study, which was based on materials available on the CDC website.
 Compared with Horne et al.
@@
 
-Participants in the No Intervention condition (_n_ = `r sum(s2_demo$condition=="noInterv")`) completed an identical set of questions, except that they did not read any material before completing the 14 belief scales and the questions about their personal background.
+Participants in the no-intervention condition (_n_ = `r sum(s2_demo$condition=="noInterv")`) completed an identical set of questions, except that they did not read any material before completing the 14 belief scales and the questions about their personal background.
 
@@
 
-We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the Disease Risk intervention on responses to the _Vaccination Intentions_ scale items, using the “brms” package for R [@burkner2017].
+We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the _Vaccination Intentions_ scale items, using the “brms” package for R [@burkner2017].
 We regressed responses on phase (Phase 1 vs.
-2, dummy-coded with Phase 1 as the baseline), condition (dummy-coded with the Disease Risk condition as the baseline, so as to assess difference scores in our condition of primary interest), and the interaction between phase and condition.
+2, dummy-coded with Phase 1 as the baseline), condition (dummy-coded with the disease risk condition as the baseline, so as to assess difference scores in our condition of primary interest), and the interaction between phase and condition.
 We included random intercepts by subject and scale item.
 In this model, the unique effect of the intervention on vaccination intention responses is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants).
-The Disease Risk intervention increased participants’ vaccination intention ratings (see Table 2).
+The disease risk intervention increased participants’ vaccination intention ratings (see Table 2).
 We consider this to be a full replication of Horne et al.’s [-@horne.etal2015] results.
@@
 
-Figure 7 (right) shows the correlation between predicted and observed belief changes conditional on the Disease Risk intervention.
+Figure 7 (right) shows the correlation between predicted and observed belief changes conditional on the disease risk intervention.
 
@@
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in gray.
-Right, mean observed and model predicted change scores for the Disease Risk intervention condition.
+Right, mean observed and model predicted change scores for the disease risk intervention condition.
 In both plots, error bars represent 95\\% confidence intervals."}
@@
 Figure 9 (right) shows the correlation between predicted and observed belief changes conditional on the Vaccine Ingredients intervention.
-the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker (*r* = `r cor_val_s3`) than those observed in our other studies.
-
-In Study 3a, we observed smaller differences than predicted for vaccineeffectiveness (observed minus predicted difference: -0.07), IIS: weak (-0.06), and vaccine intentions (-0.06); and larger differences than predicted for vaccine danger (+0.06), and parental expertise (+0.05); all other discrepancies were smaller than ±0.05.
+The model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker (*r* = `r cor_val_s3`) than those observed in our other studies.
+
+In Study 3a, we observed smaller differences than predicted for vaccine effectiveness (observed minus predicted difference: -0.07), IIS: weak (-0.06), and vaccine intentions (-0.06); and larger differences than predicted for vaccine danger (+0.06), and parental expertise (+0.05); all other discrepancies were smaller than ±0.05.
 
@@
 
-Data and code for this project are available at: https://github.com/derekpowell/int-theory-vacc
-
-Preregistrations information is available at: https://osf.io/uemq4
+Data and code for this project are available at: https://github.com/derekpowell/int-theory-vacc as well as at https://osf.io/sdfpj/
+
+Preregistration information is available at: https://osf.io/uemq4
 

### 2021-08-27 paper/paper.Rmd
submitted
revised for 125w abstract

@@
 
-## Abstract
+# Abstract
 
-Much of the richness of human thought is supported by people’s intuitive theories---explanatory mental frameworks that capture the perceived causal and relational structure of the world.
-But serious consequences can arise when these theories are mistaken.
-In this paper, we consider an important and timely example of these risks: when misconceptions about vaccine safety discourage vaccination.
+Much of the richness of human thought is supported by people’s intuitive theories---mental frameworks capturing the perceived structure of the world.
+But intuitive theories can sometimes contain and reinforce misconceptions, such as misconceptions about vaccine safety that discourage vaccination.
 We argue that addressing misconceptions requires awareness of the broader conceptual contexts in which they are embedded.
-To this end, we sought to develop a cognitive model of the intuitive theory surrounding vaccination decisions.
-From qualitative research, we identified a set of beliefs relevant to this intuitive theory.
-Then, we built our model by surveying a large sample of U.S.
-adults and applying Bayesian network structure learning algorithms to their responses to uncover the connections among these beliefs (Study 1).
-The resulting model supports understanding of belief revision within this larger conceptual system: Our model helped to explain belief revision following an established educational intervention (Study 2), provided insight that supported our formulation of a novel educational intervention that successfully increased vaccination intentions (Studies 3a, 3b), and also helped to explain how people’s beliefs changed following real-world events (Study 4).
-Taken together, this work illustrates the promise of understanding belief revision in terms of intuitive theories and of discovering and formalizing intuitive theories via computational models.
-Moreover, it lays the foundation for theory-based educational interventions that could encourage people to vaccinate their children and themselves against dangerous diseases like measles and COVID-19.
-
-## Significance Statement
-
-When people decide whether to vaccinate their children and themselves against dangerous diseases like measles and COVID-19, their decisions are affected by a network of interrelated beliefs about specific diseases, vaccine safety and efficacy, the immune system, the medical system, health, and nature more generally.
-By creating a computational model of the intuitive theory connecting these different beliefs, we were able to make accurate predictions about how these beliefs are revised in light of educational interventions, design an effective new intervention encouraging vaccination, and understand how these beliefs were affected by real-world events.
-This approach provides the foundation for richer understandings of intuitive theories more broadly and sheds new light on long-standing theoretical questions about belief revision.
+Here, we developed a cognitive model of the intuitive theory surrounding vaccination decisions.
+Using this model, we were able to make accurate predictions about how people's beliefs would be revised in light of educational interventions, design an effective new intervention encouraging vaccination, and understand how these beliefs were affected by real-world events.
+This approach provides the foundation for richer understandings of intuitive theories and belief revision more broadly.
 
@@
 
-## Modelling intuitive theories
+## Modeling intuitive theories
 
@@
 
-## Results
+# Results
 
-### Study 1: Assessing and modeling intuitive theories of vaccination
+## Study 1: Assessing and modeling intuitive theories of vaccination
 
@@
 
-#### Structure learning
+### Structure learning
 
@@
 
-### Study 2: Targeting disease severity beliefs
+## Study 2: Targeting disease severity beliefs
 
@@
 
-### Study 3a and 3b: Targeting beliefs about vaccine toxicity
+## Study 3a and 3b: Targeting beliefs about vaccine toxicity
 
@@
 
-### Study 4: Natural experiment
+## Study 4: Natural experiment
 
@@
 
-## Discussion
+# Discussion
 

### 2021-08-31 supplement/supplement-main.Rmd
fixes to install

@@
 header-includes:
- \usepackage{float}
+  - \usepackage{float}
+  - \usepackage{setspace}\doublespacing
 ---

### 2021-08-31 install-packages.R

@@ -1,5 +1,6 @@
 ## this will install all required packages
 ## untested 6/22/21, 11:03 AM
+BiocManager::install("graph")
 
 package_list <- c(
   "tidyverse",

### 2021-09-01 supplement/supplement-main.Rmd
formatting minor

--- 2021-07-26 supplement/supplement-main.Rmd
@@
 bibliography: references.bib
-csl: pnas.csl
+csl: apa.csl
 figsintext : yes

### 2021-09-01 paper/paper.Rmd
doublespaced
formatting minor
final revs before submission2

@@
 title: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
-author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
-output: pdf_document
+author: 
+  - Derek Powell^[Arizona State University, dmpowell@asu.edu]
+  - Kara Weisman^[University of California, Riverside]
+  - Ellen M. Markman^[Stanford University]
+output:
+  pdf_document:
+    keep_tex: true
 bibliography: "../supplement/references.bib"
-csl: "../supplement/pnas.csl"
+csl: "../supplement/science.csl"
+header-includes:
+    - \usepackage{setspace}\doublespacing
 ---
@@
 
-# Abstract
+## One sentence summary
+
+We developed a cognitive model of the intuitive theory surrounding vaccination decisions capable of predicting how people's beliefs about vaccination would be revised in light of evidence and real-world events.
+
+## Abstract
 
@@
 \newpage
+
+# Main text
 
@@
 \newpage
+\singlespacing
 # References

### 2021-09-01 supplement/supplement-main.Rmd
final revs before submission2

--- 2021-07-26 supplement/supplement-main.Rmd
@@
 bibliography: references.bib
-csl: pnas.csl
+csl: science.csl
 figsintext : yes
@@
 \newpage
+\singlespace
 # References

### 2021-09-01 install-packages.R

@@ -20,3 +20,5 @@ package_list <- c(
 install.packages(package_list)
 
 devtools::install_github("thomasp85/patchwork")
+
+webshot::install_phantomjs()

### 2021-12-10 install-packages.R
submitted again

@@ -1,6 +1,5 @@
 ## this will install all required packages
 ## untested 6/22/21, 11:03 AM
-BiocManager::install("graph")
 
 package_list <- c(
   "tidyverse",
@@ -20,5 +19,3 @@ package_list <- c(
 install.packages(package_list)
 
 devtools::install_github("thomasp85/patchwork")
-
-webshot::install_phantomjs()

### 2021-12-10 paper/paper-papaja.Rmd
added papaja draft

--- 2021-08-27 paper/paper.Rmd
@@
 ---
-title: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
-author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
-output: pdf_document
-bibliography: "../supplement/references.bib"
-csl: "../supplement/pnas.csl"
+title             : "Modeling and leveraging intuitive theories to improve vaccine attitudes"
+shorttitle        : "Intuitive theories of vaccine attitudes"
+
+author: 
+  - name          : "Derek Powell"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "4701 W. Thunderbird Road, Glendale, AZ 85306"
+    email         : "dmpowell@asu.edu"
+    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+      - Conceptualization
+      - Data collection
+      - Analysis
+      - Writing
+  - name          : "Kara Weisman"
+    affiliation   : "2"
+    role:
+      - Conceptualization
+      - Data collection
+      - Analysis
+      - Writing
+  - name          : "Ellen M. Markman"
+    affiliation   : "3"
+    role:
+      - Conceptualization
+      - Writing
+
+affiliation:
+  - id            : "1"
+    institution   : "Arizona State University"
+  - id            : "2"
+    institution   : "University of California, Riverside"
+  - id            : "3"
+    institution   : "Stanford University"
+
+authornote: |
+  This manuscript has not yet been peer-reviewed.
+
+abstract: |
+  Much of the richness of human thought is supported by people’s intuitive theories---mental frameworks capturing the perceived structure of the world.
+But intuitive theories can sometimes contain and reinforce misconceptions, such as misconceptions about vaccine safety that discourage vaccination.
+We argue that addressing misconceptions requires awareness of the broader conceptual contexts in which they are embedded.
+Here, we developed a cognitive model of the intuitive theory surrounding vaccination decisions.
+Using this model, we were able to make accurate predictions about how people's beliefs would be revised in light of educational interventions, design an effective new intervention encouraging vaccination, and understand how these beliefs were affected by real-world events.
+This approach provides the foundation for richer understandings of intuitive theories and belief revision more broadly.
+
+  <!-- https://tinyurl.com/ybremelq -->
+
+keywords          : "keywords"
+wordcount         : "X"
+
+bibliography      : ["../supplement/references.bib"]
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : no
+mask              : no
+draft             : no
+
+documentclass     : "apa6"
+classoption       : "man"
+output            : papaja::apa6_pdf
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+```{r setup, include = FALSE}
+library("papaja")
+r_refs("r-references.bib")
 ```
@@
 
-# Abstract
-
-Much of the richness of human thought is supported by people’s intuitive theories---mental frameworks capturing the perceived structure of the world.
-But intuitive theories can sometimes contain and reinforce misconceptions, such as misconceptions about vaccine safety that discourage vaccination.
-We argue that addressing misconceptions requires awareness of the broader conceptual contexts in which they are embedded.
-Here, we developed a cognitive model of the intuitive theory surrounding vaccination decisions.
-Using this model, we were able to make accurate predictions about how people's beliefs would be revised in light of educational interventions, design an effective new intervention encouraging vaccination, and understand how these beliefs were affected by real-world events.
-This approach provides the foundation for richer understandings of intuitive theories and belief revision more broadly.
-
-\newpage
-
 One remarkable feature of human psychology is our ability to form rich mental representations of what is true, how things work, and how best to navigate the world around us.
@@
 From early in life, people are driven to seek out such causal explanations and to use their mental representations of these causal systems to explain, predict, and intervene in the world [see @carey2009; @gelman.legare2011; @gerstenberg.etal2021; @gopnik.wellman1994; @keil1994; @murphy.medin1985; @wellman.gelman1992 for influential treatments of this topic].
-Intuitive theories inform reasoning in a wide variety of domains, including reasoning about physical systems [e.g., @baillargeon2004; @battaglia.etal2013; @spelke1994a; @ullman.etal2017], biological processes [e.g., @carey2009; @carey1985; @medin.atran1999] and the contents of other people’s minds [e.g., @gopnik.wellman1994; @wellman2015; @baker.etal2017].
+Intuitive theories inform reasoning in a wide variety of domains, including reasoning about physical systems [e.g., @baillargeon2004; @battaglia.etal2013; @spelke1994a; @ullman.etal2017], biological processes [e.g., @carey1985; @carey2009;  @medin.atran1999] and the contents of other people’s minds [e.g., @baker.etal2017; @gopnik.wellman1994; @wellman2015].
 
@@
 Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct [e.g., @betsch.sachse2013; @horne.etal2015].
-Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @horne.etal2015; @vannice.etal2011; @wallace.etal2006; @dube.etal2015].
+Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @dube.etal2015; @horne.etal2015; @vannice.etal2011; @wallace.etal2006].
 This is especially  sobering in the context of the coronavirus pandemic: reluctance to be vaccinated against COVID-19 threatens our ability to end a pandemic that has already claimed millions of lives around the world.
@@
 @lewandowsky.etal2012].
-Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence [e.g., @lewandowsky.etal2012; @jern.etal2014; @gershman2019].
+Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence [e.g., @gershman2019; @lewandowsky.etal2012; @jern.etal2014].
 
@@
 Originally designed as tools for artificial intelligence [@pearl1988], Bayesian networks are a class of probabilistic graphical models that have been deployed widely across cognitive science [e.g.
-@jern.etal2014; @gopnik.etal2004; @griffiths.tenenbaum2005].
+@gopnik.etal2004; @jern.etal2014; @griffiths.tenenbaum2005].
 The heart of a Bayesian Network is a graphical structure ---not unlike a "web of belief"---that represents variables as nodes connected by edges, where those edges represent probabilistic or statistical relations.
@@
 
-# Results
+# The present studies
+
+## Qualitative studies and scale development
+
+We drew on a variety of sources, including academic articles on anti-vaccine skepticism [e.g.,  @dube.etal2015; @larson.etal2015; @salmon.etal2015; @williams2014], anti-vaccine websites, and a qualitative survey with self-identified vaccine skeptics (*n*=16) via Amazon Mechanical Turk (MTurk) to generate a list of beliefs that might influence people’s decisions about whether to vaccinate their children (*vaccine intentions*): *vaccine danger*, *toxic additives in vaccines*, *vaccine effectiveness*, *disease rarity*, *disease severity, infant immune system (IIS): weakness*, *IIS: limited capacity*, *IIS: vaccines strain*, *parental protectiveness*, *parental expertise*, *medical skepticism*, *naturalism*, and *holistic balance*.
+(See main text for descriptions, and SI for the items included in these scales.) We translated these qualitative insights into 14 psychometrically-valid scales; each scale measured agreement with 4-6 statements, including at least one reverse-coded item, and was highly reliable (observed reliability, Study 1: all Cronbach’s $\alpha \geq .73$).
+We developed 13 of these scales, and included one preexisting scale [the “holistic balance” subscale from @mcfadden.etal2010].
+
+These 14 scales formed the backbone of Studies 1-4.
+
+## General Methods: Studies 1-4
+
+Studies 1-4 were conducted online via Amazon Mechanical Turk between August 2017 and June 2019.
+Repeat participation was prevented, with no participants involved in more than one study, except as noted in Study 4.
+A breakdown of demographics and compensation by study is available in the SI.
+
+All participants responded at least once to the 14 belief scales just described.
+Each scale was presented on a separate survey page, and participants rated a series of statements on a 7-point scale from “Strongly disagree” (coded as -3) to “Strongly agree” (+3).
+Scales, and questions within each scale, were presented in a random order for each participant.
+Attention checks (e.g., “Please select somewhat agree”) were embedded within two to four randomly chosen scales and participants who failed any of these checks were excluded from analyses.
+
+We scored each belief scale by averaging a participant’s responses to each item (after reverse-coding where appropriate), then rescaling these values to fall between 0 and 1.
+We considered this score to represent the participant’s credence in the belief.
 
@@
 
-### Structure learning
+We used these intercorrelations to build a cognitive model of the relations among these beliefs via Bayesian network structure learning techniques.
 
-We used these intercorrelations to build a cognitive model of the relations among these beliefs via Bayesian network structure learning techniques, using an 80% training split of the data (*n* = 904).
+### Method
+
+#### Participants
+
+A total of `r results$s1$demo$n_total` people recruited from Amazon Mechanical Turk (mTurk) participated in this study conducted in August of 2017.
+Participants were paid \$1.60 for about 8 minutes of their time.
+`r results$s1$demo$n_exclude` participants (6%) failed at least one of two attention check questions and were excluded from further analysis, leaving a final sample of n = `r results$s1$demo$n_include`.
+After completing all 14 scales, participants were asked standard demographics questions as well as a handful of questions about whether they were or were expecting to be a parent.
+They were also debriefed with a brief statement noting that vaccines are safe and pointing them toward a WHO website for further information.
+
+#### Procedure
+
+Participants (final *n* = `r results$s1$demo$n_include`) responded to the 14 belief scales, followed by demographics questions and a handful of questions about whether they were or were expecting to be a parent.
+They were then debriefed with a brief statement noting that vaccines are safe and pointing them toward a WHO website for further information.
+
+### Results
+
+The goal of this study was to use these data to conduct a bottom-up search for a Bayesian network that would represent the intuitive theory surrounding vaccination decisions as a network of related beliefs.
 Based on the observed associations among participants' beliefs about each of theses issues, we sought to infer how these states of affairs (e.g., that vaccines are dangerous, that diseases are severe) are connected in people's intuitive theories---how people understand these states of affairs to cause, imply, or otherwise influence one another.
 
-We assumed  that the intuitive theory is a generative model, so that these influence relations (“edges”) should flow from causes or other “generating” states of affairs toward effects.
+#### Bayesian network parameterization.
+
+A Bayesian network is a directed acyclic graph that represents variables as nodes connected by directed edges.
+Each set of “child” and “parent” nodes in the larger network is a “family”.
+The network’s directed edges encode conditional dependencies among variables, and many parameterizations for the individual families are possible.
+In our model, the probability of some “child” belief node $y$ can be expressed as a noisy-logical function of the influence of one or more “parent” belief nodes $x$:
+
+$$P(y) = \Big(1-(1-w_0)\prod_i(1-w_i)^{x_i}\Big)\prod_j(1-w_j)^{x_j}$$
+
+Here, each parent node $x$ is either a generative ($i$) or preventive ($j$) influence, that generates or prevents the child node with some probability weight ($w_i$ or $w_j$).
+The weight $w_0$ represents the “leak” probability, or the baseline probability that the child occurs without any other generating influences.
+The first term represents the probability that $y$ is generated (or, put another way, that not all of the possible generating forces fail to generate it).
+The second term represents the probability that it is not then prevented [i.e., that all the preventing forces fail; see @maaskant.druzdzel2008].
+
+Having transformed participants’ averaged belief scale responses to fall between 0 and 1, we estimated the parameters of the model as a beta regression using maximum likelihood methods (see SI).
+
+#### A cognitive model underlying the data model.
+
+We aimed to represent not only the relationships among variables in the data but the *cognitive model* that gave rise to these observed relationships, i.e., the relationships among beliefs in the mind.
+We actually estimated two models: First, we estimated a data model assuming that participants possess a shared mental model from which they generate their responses to the belief scales.
+In this model, the $x$ in the equation above corresponded to participants’ continuous responses to the belief scales (e.g.
+a participants score for the *vaccine danger* scale).
+Then, from the parameters estimated in the data model we created a cognitive model of participants’ reasoning, where the $x$ are binary, indicating whether that state of affairs obtains (e.g., whether “vaccines are dangerous”).
+We used this cognitive model to simulate how beliefs could change following exposure to evidence.
+
+#### Structure learning, constrained by a “generative model principle.”
+
+Rather than specifying a priori all of the connections among the 14 beliefs included in this study, we deployed Bayesian network structure learning to search for the most likely network structure given the observed correlations between beliefs---with the constraint that this structure conform to some of our strongest high-level intuitions about what an intuitive theory should look like in this domain.
+
+In particular, we assumed  that the intuitive theory is a generative model, so that these influence relations (“edges”) should flow from causes or other “generating” states of affairs toward effects.
 For instance, we stipulated that *vaccine intentions* would be a “child node,” with edges only flowing inwards and not outwards (since one’s intention to vaccinate cannot “generate” the facts about vaccinations safety, effectiveness, etc).
-These constraints and their consequences are considered in more detail in Materials and methods.
 
+We applied a constraint we called the “generative model principle,” specifying that influence relations (edges) should flow from causes (or other generating states of affairs) to effects; instilling a core assumption in research on intuitive theories and causal explanatory reasoning [e.g.
+@gerstenberg.etal2021; @gopnik.etal2004; @cheng1997].
+We sorted the 14 measured beliefs into four tiers based on how general or abstract each belief was, reasoning that general and abstract states of affairs should be understood to cause (or otherwise generate) more specific and concrete states of affairs, so edges should flow from the general and abstract toward the specific and concrete (e.g., if natural things are better than artificial things, this should set an expectation about whether a specific class of artificial things--vaccines--is safe).
+We considered *holistic balance* and *naturalism* to be the most general and abstract beliefs among those we measured; followed by theories about parenting and medicine; then specific beliefs about vaccines, diseases, and the infant immune system; and finally our outcome of interest, *vaccine intentions*---the most concrete measurement of a specific intended action.
+
+We used this sorting to induce a partial ordering of these 14 beliefs, stipulating that directed edges that violated this ordering must not appear in the final network of beliefs (e.g., that there should be no edge from *vaccine intentions* to *naturalism*, although there could be an edge from *naturalism* to *vaccine intentions*).
+
+To conduct an efficient search through the super-exponential space of graphs, we tested several learning algorithms implemented in the “bnlearn” R package [@scutari2010] and evaluated their performance through cross validation in our training split (see SI).
+Following this analysis, we chose to fit our model with the score-based “hill-climbing” algorithm, scoring models via the Bayesian Information Criteria, an asymptotic estimate of the likelihood of the data under a given graph structure.
+This produced the network shown in Figure 1.
+See SI for more detailed explanations of these modeling choices.
+
+Some caution should be exercised in interpreting the relationships in the network.
+Due to Bayesian networks' tight connections with structural causal networks, it is tempting to interpret the edges in this network as representing a mental causal model.
+But, in some cases these relationships are better thought of as probabilistic dependencies or “influence” relations [@williamson2001].
+For instance, intuitively we might imagine that vaccines having toxins could cause them to be dangerous and ineffective.
+These nodes are connected in the model, but the edges between them run in the opposite directions, and therefore do not support a clear causal interpretation.
+One interpretation is that this edge instead reflects a set membership relation; that toxins are one type of danger vaccines might present.
+In other cases, our data and explicit constraints do not perfectly identify the directions of the edges.
+This is the case for two edges (Naturalism $\rightarrow$  Holistic Balance and Medical Skepticism $\rightarrow$ Parental Expertise; see SI for details).
+In both cases, we do not feel it is intuitive which direction the edge should flow in, nor even that it should be directed at all; we might even speculate there is an additional unmeasured variable that connects these beliefs and that would best account for their association.
+
+Bearing these qualifications in mind, we see this Bayesian network as a limited but plausible cognitive model of these beliefs.
+
+#### Structure learning
+
+To avoid overfitting, we used an 80% split of the data (*n* = 904) for training, and reserved the remaining 20% for evaluating model performance.
 Applying these techniques resulted in an estimate of the network shown in Figure 1.
 
-```{r fig1-maingraph, fig.align='center', fig.height=8, fig.width=5, fig.cap="Bayesian network model resulting from hill-climbing algorithm with our generative-model constraints applied to data in Study 1 training split (n = 904).
+```{r fig1-maingraph, fig.align='center', out.width="90%", fig.cap="Bayesian network model resulting from hill-climbing algorithm with our generative-model constraints applied to data in Study 1 training split (n = 904).
 The network has 29 edges connecting these 14 variables.
@@
 
-```{r fig2-validation, fig.align='center', fig.height=4, fig.width=7, fig.cap="Observed responses and model predictions for each belief among participants in the Study 1 testing split.
+```{r fig2-validation, fig.align='center', out.width="100%", fig.cap="Observed responses and model predictions for each belief among participants in the Study 1 testing split.
 Correlations between observed and predicted values ranged from .380 to .898 across the different belief scales.
@@
 
+### Method
+
+#### Participants.
+
+We recruited `r results$s2$demo$n_recruited` people to participate in a two-day study via mTurk in April 2018.
+Two days later, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r results$s2$demo$n_recruited_post` participants returning (`r results$s2$demo$n_eligible` invited, retaining `r round(results$s2$demo$n_recruited_post/results$s2$demo$n_eligible*100, 1)`% of the Day 1 sample).
+Participants were paid \$1.35 for their participation in each phase of the study.
+`r results$s2$demo$n_failed_post` participants (`r round( (results$s2$demo$n_failed_post/results$s2$demo$n_recruited_post)*100, 1)`%) failed at least one attention check on Day 2 and were excluded from further analysis.
+We also excluded from analyses `r results$s2$demo$n_duplicate` additional participants who accessed the second survey more than once.
+This left a final sample of `r results$s2$demo$n_complete` participants.
+
+#### Procedure
+
+Procedures for Phase 1 of Study 2 were nearly identical to those of Study 1, but the debriefing statement was moved to the end of Phase 2.
+In Phase 2 (approximately two days later), participants completed a study very similar to Horne et al.’s (2015) original intervention study.
+Participants were randomly assigned to either the disease risk condition or the no-intervention condition, with the constraint that the distributions of participants’ Phase 1 *vaccine intentions* scores should be similar across the two conditions; we accomplished this by stratifying participants into three groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
+
+Participants (*n* = `r results$s2$demo$n_complete` passed attention checks in total) in the intervention conditions were presented with a version of Horne et al.’s  “disease risk” intervention, modified to present subparts in a fixed (rather than randomized) order, with slight changes to wording to improve clarity, and with a final statement summarizing the take-home message of the intervention; see SI.
+They then completed the same 14 belief scales and demographic questions that they had completed in Phase 1.
+
+Participants in the no-intervention condition completed the belief scales and demographics questions without reading any material first.
+
+### Results
+
 Figure 3 shows the change in participants’ attitudes across all 14 belief scales, from pretest to posttest.
@@
 Most importantly, the disease risk intervention significantly increased participant’s *vaccination intentions*, conceptually replicating earlier findings regarding this intervention [@horne.etal2015].
+
+```{r, include=F}
+s2_reg <- summary(results$s2$reg)
+```
+
+We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the *Vaccination Intentions* scale items, using the “brms” package for R [@burkner2017].
+We regressed responses on phase (Phase 1 vs.
+2, dummy-coded with Phase 1 as the baseline), condition (dummy-coded with the disease risk condition as the baseline, so as to assess difference scores in our condition of primary interest), and the interaction between phase and condition.
+We included random intercepts by subject and scale item.
+In this model, the unique effect of the intervention on vaccination intention scores is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants).
+The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: $b$ = `r round(s2_reg$fixed[9,1],3)`, 95% CI: [`r round(s2_reg$fixed[9,3], 3)`, `r round(s2_reg$fixed[9,4], 3)`]).
+We consider this to be a full replication of Horne, Powell, et al.’s [-@horne.etal2015] results.
+See Figure 3, panel A.
 
@@
 
-```{r fig3-s2, fig.align='center', fig.height=4, fig.width=7, fig.cap="Belief changes following the intervention in Study 2.
+```{r fig3-s2, fig.align='center', out.width="100%", fig.cap="Belief changes following the intervention in Study 2.
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
@@
 
+#### Modeling belief revision.
+
 How did this intervention---which focused solely on the dangers of childhood diseases---affect beliefs about *vaccine danger*, *medical skepticism*, *holistic balance*, and so on?
 One explanation is that this intervention provides direct evidence for *disease severity* beliefs and that other beliefs are revised as a result of their relationships with *disease severity* as captured in the intuitive theory.
-To examine this, we used the same model developed in Study 1 to simulate how the 13 other beliefs in the intuitive theory would change as a result of the intervention's direct effect on *disease severity* beliefs (see Materials and methods).
+To examine this, we used the same model developed in Study 1 to simulate how the 13 other beliefs in the intuitive theory would change as a result of the intervention's direct effect on *disease severity* beliefs.
+
+To model the effects of the intervention presented in Study 2 on the intuitive theory surfaced in Study 1, we augmented the belief network representing the intuitive theory with an additional node representing the information about measles, mumps, and rubella presented in the intervention.
+This evidence node was added as a child of the *disease severity* node, allowing the intervention to act as virtual evidence for *disease severity* [following @pearl1988].
+
+To compute the conditional probability table (CPT) for this new node as a function of *disease severity* beliefs, we estimated an evidence ratio based on participants’ pretest and posttest credences in *disease severity*.
+To so do, we made use of the log-odds expression of Bayes rule, with the following regression equation:
+
+$$logit(posttest) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})$$
+
+Where *x* was a binary variable representing the presence (1) or absence (0) of evidence at posttest, and participants’ prior and posterior (pretest and posttest) credences were transformed into log odds.
+This allowed us to estimate the log evidence ratio implied by participants’ reactions to the intervention.
+Then, we constructed a CPT consistent with that evidence ratio.
+
+Using this augmented model, we are able to “condition” the model on this evidence node, and thereby predict how observing evidence will affect all of the beliefs in the network.
 As shown in Figure 3, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (*r* = `r results$s2$modcorr`).
+
+Given that our cognitive model is parameterized via noisy-logical functions, it should be noted that the marginal predicted influence of each belief is closely related to its first-order correlation with disease severity.
+This is in keeping with the qualitative features of intuitive theories we laid out in the introduction, and we should expect this to hold true (on average) for any plausible model of an intuitive theory.
+However, future models with more complex or nuanced parameterizations could potentially make additional predictions not evident from first-order correlations, such as individualized predictions for how individuals or groups would respond to evidence.
 
@@
 
-```{r fig4-predimpacts, fig.align='center', fig.height=3, fig.width=3, fig.cap="Predicted change in vaccination intentions following an equivalent hypothetical change in each of the other 13 beliefs."}
+```{r fig4-predimpacts, fig.align='center',  out.width="50%", fig.cap="Predicted change in vaccination intentions following an equivalent hypothetical change in each of the other 13 beliefs."}
 knitr::include_graphics("../local/pred_change_plt.png")
@@
 
-We conducted two preregistered experiments (3a and 3b) testing the effects of this novel intervention using the same pretest-posttest design as Study 2.
+### Methods
+
+We conducted two preregistered experiments (3a and 3b) testing the effects of this novel intervention aimed at dispelling concerns about toxic additives in vaccines using the same pretest-posttest design as Study 2.
+These studies followed similar design procedures as Study 2, with phase 2 conducted 1-2 days after phase 1.
+In both Study 3a (April 2019) and Study 3b (May 2019; combined final *n* = `r results$s3$demo$n_complete`) the vaccine ingredients intervention was compared against no-intervention control.
+Unlike Study 2, we did not stratify participants before random assignment to conditions.
+
+#### Participants.
+
+We recruited `r results$s3$demo$n_recruited` people to participate in a two-day study via mTurk in April (Experiment 3A) and June (Experiment 3B) of 2019.
+One day after their initial participation, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r results$s3$demo$n_recruited_post` participants returning (`r results$s3$demo$n_eligible` invited, retaining `r round(results$s3$demo$n_recruited_post/results$s3$demo$n_eligible*100,1)`% of the Day 1 sample).
+Participants were paid \$1.35 for their participation in each phase of the study and were allowed to participate in part 2 up to two days after their initial participation in part 1.
+`r results$s3$demo$n_failed_post` participants (`r round( (results$s3$demo$n_failed_post/results$s3$demo$n_recruited_post)*100,1)`%) failed at least one attention check on Day 2 and were excluded from further analysis.
+This left a final sample of `r results$s3$demo$n_complete` participants.
+
+#### Procedure
+
+Procedures for studies 3a and 3b closely followed those of Study 2, but these studies tested the effects of a novel intervention aimed at dispelling concerns about toxic additives in vaccines.
+Full text of this intervention is available in supplementary materials.
+In both studies, participants were randomly assigned to either a no-intervention control condition or to the novel Vaccine Ingredients intervention.
+
+### Results
+
+#### Regression analyses.
+
+```{r, include=F}
+s3_reg <- summary(results$s3$reg)
+```
+
+As they shared the same design, we combined data from studies 3a and 3b for analysis (but see SI for separate analyses by study).
+As in study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine ingredients intervention on participants’ *vaccination intentions* scores.
+The vaccine ingredients intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: $b$ = `r round(s3_reg$fixed[9,1],3)`, 95% CI: [`r round(s3_reg$fixed[9,3], 3)`, `r round(s3_reg$fixed[9,4], 3)`]); see Figure 5, panel A.
+However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: $b$ = `r round(s3_reg$fixed[7,1],3)`, 95% CI: [`r round(s3_reg$fixed[7,3], 3)`, `r round(s3_reg$fixed[7,4], 3)`]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
+
+#### Modeling belief revision.
+
+To model the effect of the vaccine ingredients intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the vaccine ingredients intervention as a child of the vaccine toxins belief node (for details, see SI).
+This allowed us to predict how other beliefs in the network would change in light of the observed changes participant’s beliefs about whether vaccines contain dangerous toxins; see Figure 5, panel B.
+
 Collapsing across these two studies, Figure 5 shows the change in participants’ (*n* = `r results$s3$demo$n_complete`) attitudes across all 14 belief scales from pretest to posttest.
@@
 
-```{r fig5-s3, fig.align='center', fig.height=4, fig.width=7, fig.cap="Belief changes following the intervention in studies 3a and 3b.
+```{r fig5-s3, fig.align='center',  out.width="100%", fig.cap="Belief changes following the intervention in studies 3a and 3b.
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
@@
 
-```{r fig6-s4, fig.align='center', fig.height=4, fig.width=7, fig.cap="Participants’ belief changes from participation in Study 1 to Study 4.
+```{r fig6-s4, fig.align='center',  out.width="100%", fig.cap="Participants’ belief changes from participation in Study 1 to Study 4.
 Left, mean difference scores comparing beliefs reported in August-September 2017 and May 2019 for the 14 belief scales, across participants who did and did not report exposure to news of the ongoing New York measles outbreak.
@@
 
+### Methods
+
 To examine this possibility, we invited participants from Study 1 (conducted in August-September 2017) to participate in a new study measuring each of those 14 beliefs again (conducted from May 1st to 3rd, 2019; approximately 18 months later).
-Of the `r results$s1$demo$n_include` participants in Study 1, `r results$s4$demo$n_complete` returned and completed the study.
+Of the `r results$s1$demo$n_include` participants in Study 1, a total of `r results$s4$demo$n_recruited` participants returned and `r results$s4$demo$n_complete` successfully completed the study, including passing attention checks.
 Approximately `r round(100*(results$s4$demo$n_news/results$s4$demo$n_complete),0) `% of participants reported recently seeing, hearing, or reading about measles outbreaks.
+
+### Results and discussion
 
@@
 
-Were these changes coherent with respect to the intuitive theory specified by the model developed in Study 1?
+```{r, include=F}
+s4_reg <- summary(results$s4$reg)
+```
+
+Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (August-September 2017 vs.
+May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item.
+To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure.
+Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months earlier (interaction effect: $b$ = `r round(s4_reg$fixed[9,1],3)`, 95% CI: [`r round(s4_reg$fixed[9,3], 3)`, `r round(s4_reg$fixed[9,4], 3)`]); see Figure 6, panel A.
+
+#### Modeling belief revision.
+
+Were changes in participants' beliefs following exposure to news of the measles outbreak coherent with respect to the intuitive theory specified by the model developed in Study 1?
 Unlike in the intervention studies, where a specific belief was targeted by the intervention, it is likely that many beliefs were addressed by media coverage of these outbreaks.
-To assess whether these changes were coherent, we examined how they were related to the most central of the beliefs we measured, *vaccine intentions*, using our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in *vaccine intentions.* As shown in Figure 6, the changes in participants’ beliefs are very similar to the model’s predictions (*r* = `r results$s4$modcorr`), suggesting that the changes in their beliefs were highly coherent with respect to their intuitive theories of the domain.
+To assess whether these changes were coherent, we examined how they were related to the most central of the beliefs we measured, *vaccine intentions*, using our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in *vaccine intentions.* That is, we followed the same procedure as in previous studies, but here augmented the model with a node representing media exposure as a child of the *vaccine intentions* node.
+
+As shown in Figure 6, the changes in participants’ beliefs are very similar to the model’s predictions (*r* = `r results$s4$modcorr`), suggesting that the changes in their beliefs were highly coherent with respect to their intuitive theories of the domain.
 Modeling these beliefs as united by an intuitive theory not only captures how these beliefs are revised immediately in light of evidence, but also how they are changed by real-world events.
@@
 @kahan2013; @flynn.etal2017; @kunda1990].
-Yet many of the phenomena traditionally taken as evidence for these theories can also be explained by normative models of belief revision, so long as we are willing to posit that other auxiliary beliefs can affect the relationships between a belief and evidence [e.g., @jern.etal2014; @gershman2019].
+Yet many of the phenomena traditionally taken as evidence for these theories can also be explained by normative models of belief revision, so long as we are willing to posit that other auxiliary beliefs can affect the relationships between a belief and evidence [e.g.,@gershman2019; @jern.etal2014].
 Adjudicating between competing views of belief revision will require us to move beyond minimal models and illustrative simulations by assessing whether people actually do hold these auxiliary beliefs, and whether their broader belief systems behave according to the rules of probabilistic inference.
@@
 On the other hand, the pandemic has presented its own unique issues.
-MRNA vaccines like those from Pfizer-BioNtech and Moderna represent highly novel technologies that are currently approved only under emergency use authorizations after being developed at a pace far faster than previously imagined possible.
-These facts could engender hesitancy even among people who are otherwise comfortable with vaccinations.
+MRNA vaccines like those from Pfizer-BioNtech and Moderna represent highly novel technologiesdeveloped at a pace far faster than previously imagined possible.
+The unprecedented nature of these vaccines could engender hesitancy even among people who are otherwise comfortable with vaccinations.
 
@@
 
-# Materials and methods
-
-## Qualitative studies and scale development
-
-We drew on a variety of sources, including academic articles on anti-vaccine skepticism [e.g.,  @dube.etal2015; @larson.etal2015; @salmon.etal2015; @williams2014], anti-vaccine websites, and a qualitative survey with self-identified vaccine skeptics (*n*=16) via Amazon Mechanical Turk (MTurk) to generate a list of beliefs that might influence people’s decisions about whether to vaccinate their children (*vaccine intentions*): *vaccine danger*, *toxic additives in vaccines*, *vaccine effectiveness*, *disease rarity*, *disease severity, infant immune system (IIS): weakness*, *IIS: limited capacity*, *IIS: vaccines strain*, *parental protectiveness*, *parental expertise*, *medical skepticism*, *naturalism*, and *holistic balance*.
-(See main text for descriptions, and SI for the items included in these scales.) We translated these qualitative insights into 14 psychometrically-valid scales; each scale measured agreement with 4-6 statements, including at least one reverse-coded item, and was highly reliable (observed reliability, Study 1: all Cronbach’s $\alpha \geq .73$).
-We developed 13 of these scales, and included one preexisting scale [the “holistic balance” subscale from @mcfadden.etal2010].
-
-These 14 scales formed the backbone of Studies 1-4.
-
-## General Methods: Studies 1-4
-
-Studies 1-4 were conducted online via Amazon Mechanical Turk between August 2017 and June 2019.
-Repeat participation was prevented, with no participants involved in more than one study, except as noted in Study 4.
-A breakdown of demographics and compensation by study is available in the SI.
-
-All participants responded at least once to the 14 belief scales just described.
-Each scale was presented on a separate survey page, and participants rated a series of statements on a 7-point scale from “Strongly disagree” (coded as -3) to “Strongly agree” (+3).
-Scales, and questions within each scale, were presented in a random order for each participant.
-Attention checks (e.g., “Please select somewhat agree”) were embedded within two to four randomly chosen scales and participants who failed any of these checks were excluded from analyses.
-
-We scored each belief scale by averaging a participant’s responses to each item (after reverse-coding where appropriate), then rescaling these values to fall between 0 and 1.
-We considered this score to represent the participant’s credence in the belief.
-
-## Study 1
-
-### Method
-
-Participants (final *n* = `r results$s1$demo$n_include`) responded to the 14 belief scales, followed by demographics questions and a handful of questions about whether they were or were expecting to be a parent.
-They were then debriefed with a brief statement noting that vaccines are safe and pointing them toward a WHO website for further information.
-
-### Analyses
-
-The goal of this study was to use these data to conduct a bottom-up search for a Bayesian network that would represent the intuitive theory surrounding vaccination decisions as a network of related beliefs.
-
-#### Bayesian network parameterization.
-
-A Bayesian network is a directed acyclic graph that represents variables as nodes connected by directed edges.
-Each set of “child” and “parent” nodes in the larger network is a “family”.
-The network’s directed edges encode conditional dependencies among variables, and many parameterizations for the individual families are possible.
-In our model, the probability of some “child” belief node $y$ can be expressed as a noisy-logical function of the influence of one or more “parent” belief nodes $x$:
-
-$$P(y) = \Big(1-(1-w_0)\prod_i(1-w_i)^{x_i}\Big)\prod_j(1-w_j)^{x_j}$$
-
-Here, each parent node $x$ is either a generative ($i$) or preventive ($j$) influence, that generates or prevents the child node with some probability weight ($w_i$ or $w_j$).
-The weight $w_0$ represents the “leak” probability, or the baseline probability that the child occurs without any other generating influences.
-The first term represents the probability that $y$ is generated (or, put another way, that not all of the possible generating forces fail to generate it).
-The second term represents the probability that it is not then prevented [i.e., that all the preventing forces fail; see @maaskant.druzdzel2008].
-
-Having transformed participants’ averaged belief scale responses to fall between 0 and 1, we estimated the parameters of the model as a beta regression using maximum likelihood methods (see SI).
-
-#### A cognitive model underlying the data model.
-
-We aimed to represent not only the relationships among variables in the data but the *cognitive model* that gave rise to these observed relationships, i.e., the relationships among beliefs in the mind.
-We actually estimated two models: First, we estimated a data model assuming that participants possess a shared mental model from which they generate their responses to the belief scales.
-In this model, the $x$ in the equation above corresponded to participants’ continuous responses to the belief scales (e.g.
-a participants score for the *vaccine danger* scale).
-Then, from the parameters estimated in the data model we created a cognitive model of participants’ reasoning, where the $x$ are binary, indicating whether that state of affairs obtains (e.g., whether “vaccines are dangerous”).
-We used this cognitive model to simulate how beliefs could change following exposure to evidence.
-
-#### Structure learning, constrained by a “generative model principle.”
-
-Rather than specifying a priori all of the connections among the 14 beliefs included in this study, we deployed Bayesian network structure learning to search for the most likely network structure given the observed correlations between beliefs---with the constraint that this structure conform to some of our strongest high-level intuitions about what an intuitive theory should look like in this domain.
-
-In particular, we applied what we call the “generative model principle,” specifying that influence relations (edges) should flow from causes (or other generating states of affairs) to effects; instilling a core assumption in research on intuitive theories and causal explanatory reasoning [e.g.
-@gerstenberg.etal2021; @gopnik.etal2004; @cheng1997].
-We sorted the 14 measured beliefs into four tiers based on how general or abstract each belief was, reasoning that general and abstract states of affairs should be understood to cause (or otherwise generate) more specific and concrete states of affairs, so edges should flow from the general and abstract toward the specific and concrete (e.g., if natural things are better than artificial things, this should set an expectation about whether a specific class of artificial things--vaccines--is safe).
-We considered *holistic balance* and *naturalism* to be the most general and abstract beliefs among those we measured; followed by theories about parenting and medicine; then specific beliefs about vaccines, diseases, and the infant immune system; and finally our outcome of interest, *vaccine intentions*---the most concrete measurement of a specific intended action.
-
-We used this sorting to induce a partial ordering of these 14 beliefs, stipulating that directed edges that violated this ordering must not appear in the final network of beliefs (e.g., that there should be no edge from *vaccine intentions* to *naturalism*, although there could be an edge from *naturalism* to *vaccine intentions*).
-
-To conduct an efficient search through the super-exponential space of graphs, we tested several learning algorithms implemented in the “bnlearn” R package [@scutari2010] and evaluated their performance through cross validation in our training split (see SI).
-Following this analysis, we chose to fit our model with the score-based “hill-climbing” algorithm, scoring models via the Bayesian Information Criteria, an asymptotic estimate of the likelihood of the data under a given graph structure.
-This produced the network shown in Figure 1.
-See SI for more detailed explanations of these modeling choices.
-
-Some caution should be exercised in interpreting the relationships in the network.
-Due to Bayesian networks' tight connections with structural causal networks, it is tempting to interpret the edges in this network as representing a mental causal model.
-But, in some cases these relationships are better thought of as probabilistic dependencies or “influence” relations [@williamson2001].
-For instance, intuitively we might imagine that vaccines having toxins could cause them to be dangerous and ineffective.
-These nodes are connected in the model, but the edges between them run in the opposite directions, and therefore do not support a clear causal interpretation.
-One interpretation is that this edge instead reflects a set membership relation; that toxins are one type of danger vaccines might present.
-In other cases, our data and explicit constraints do not perfectly identify the directions of the edges.
-This is the case for two edges (Naturalism $\rightarrow$  Holistic Balance and Medical Skepticism $\rightarrow$ Parental Expertise; see SI for details).
-In both cases, we do not feel it is intuitive which direction the edge should flow in, nor even that it should be directed at all; we might even speculate there is an additional unmeasured variable that connects these beliefs and that would best account for their association.
-
-Bearing these qualifications in mind, we see this Bayesian network as a limited but plausible cognitive model of these beliefs.
-
-## Study 2
-
-In Study 2 we used this model to understand belief revision in the context of an intervention highlighting the danger of measles, mumps, and rubella.
-
-### Method
-
-Procedures for Phase 1 were nearly identical to Study 1, but the debriefing statement was moved to the end of Phase 2.
-In Phase 2 (approximately two days later), participants completed a study very similar to Horne et al.’s (2015) original intervention study.
-Participants were randomly assigned to either the disease risk condition or the no-intervention condition, with the constraint that the distributions of participants’ Phase 1 *vaccine intentions* scores should be similar across the two conditions; we accomplished this by stratifying participants into three groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
-
-Participants (*n* = `r results$s2$demo$n_complete` passed attention checks in total) in the intervention conditions were presented with a version of Horne et al.’s  “disease risk” intervention, modified to present subparts in a fixed (rather than randomized) order, with slight changes to wording to improve clarity, and with a final statement summarizing the take-home message of the intervention; see SI.
-They then completed the same 14 belief scales and demographic questions that they had completed in Phase 1.
-
-Participants in the no-intervention condition completed the belief scales and demographics questions without reading any material first.
-
-### Analyses
-
-#### Regression analyses.
-
-```{r, include=F}
-s2_reg <- summary(results$s2$reg)
-```
-
-We conducted a mixed-effects Bayesian ordinal regression to assess the effects of the disease risk intervention on responses to the *Vaccination Intentions* scale items, using the “brms” package for R [@burkner2017].
-We regressed responses on phase (Phase 1 vs.
-2, dummy-coded with Phase 1 as the baseline), condition (dummy-coded with the disease risk condition as the baseline, so as to assess difference scores in our condition of primary interest), and the interaction between phase and condition.
-We included random intercepts by subject and scale item.
-In this model, the unique effect of the intervention on vaccination intention scores is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants).
-The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: $b$ = `r round(s2_reg$fixed[9,1],3)`, 95% CI: [`r round(s2_reg$fixed[9,3], 3)`, `r round(s2_reg$fixed[9,4], 3)`]).
-We consider this to be a full replication of Horne, Powell, et al.’s [-@horne.etal2015] results.
-See Figure 3, panel A.
-
-#### Modeling belief revision.
-
-To model the effects of the intervention presented in Study 2 on the intuitive theory surfaced in Study 1, we augmented the belief network representing the intuitive theory with an additional node representing the information about measles, mumps, and rubella presented in the intervention.
-This evidence node was added as a child of the *disease severity* node, allowing the intervention to act as virtual evidence for *disease severity* [following @pearl1988].
-
-To compute the conditional probability table (CPT) for this new node as a function of *disease severity* beliefs, we estimated an evidence ratio based on participants’ pretest and posttest credences in *disease severity*.
-To so do, we made use of the log-odds expression of Bayes rule, with the following regression equation:
-
-$$logit(posttest) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})$$
-
-Where *x* was a binary variable representing the presence (1) or absence (0) of evidence at posttest, and participants’ prior and posterior (pretest and posttest) credences were transformed into log odds.
-This allowed us to estimate the log evidence ratio implied by participants’ reactions to the intervention.
-Then, we constructed a CPT consistent with that evidence ratio.
-
-Using this augmented model, we are able to “condition” the model on this evidence node, and thereby predict how observing evidence will affect all of the beliefs in the network; see Figure 3, panel B.
-
-Given that our cognitive model is parameterized via noisy-logical functions, it should be noted that the marginal predicted influence of each belief is closely related to its first-order correlation with disease severity.
-This is in keeping with the qualitative features of intuitive theories we laid out in the introduction, and we should expect this to hold true (on average) for any plausible model of an intuitive theory.
-However, future models with more complex or nuanced parameterizations could potentially make additional predictions not evident from first-order correlations, such as individualized predictions for how individuals or groups would respond to evidence.
-
-## Studies 3a and 3b
-
-In Studies 3a and 3b we developed a novel intervention targeting the misconception that vaccines contain dangerous toxins and used the model developed in Study 1 to predict the effects of this intervention.
-
-### Methods
-
-Study 3a and 3b tested the effects of a novel intervention aimed at dispelling concerns about toxic additives in vaccines.
-These studies followed similar design procedures as Study 2, with phase 2 conducted 1-2 days after phase 1.
-In both Study 3a (April 2019) and Study 3b (May 2019; combined final *n* = `r results$s3$demo$n_complete`) the vaccine ingredients intervention was compared against no-intervention control.
-Unlike Study 2, we did not stratify participants before random assignment to conditions.
-
-### Analyses
-
-#### Regression analyses.
-
-```{r, include=F}
-s3_reg <- summary(results$s3$reg)
-```
-
-As they shared the same design, we combined data from studies 3a and 3b for analysis (but see SI for separate analyses by study).
-As in study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine ingredients intervention on participants’ *vaccination intentions* scores.
-The vaccine ingredients intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: $b$ = `r round(s3_reg$fixed[9,1],3)`, 95% CI: [`r round(s3_reg$fixed[9,3], 3)`, `r round(s3_reg$fixed[9,4], 3)`]); see Figure 5, panel A.
-However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: $b$ = `r round(s3_reg$fixed[7,1],3)`, 95% CI: [`r round(s3_reg$fixed[7,3], 3)`, `r round(s3_reg$fixed[7,4], 3)`]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
-
-#### Modeling belief revision.
-
-To model the effect of the vaccine ingredients intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the vaccine ingredients intervention as a child of the vaccine toxins belief node (for details, see SI).
-This allowed us to predict how other beliefs in the network would change in light of the observed changes participant’s beliefs about whether vaccines contain dangerous toxins; see Figure 5, panel B.
-
-## Study 4
-
-In Study 4 we used the same model to understand belief revision in the context of the measles outbreaks of 2019.
-
-### Participants and Methods
-
-We contacted as many of the `r results$s1$demo$n_include` participants who completed Study 1 as we could and invited them to participate in Study 4, in which they completed the same 14 belief scales and answered questions about their exposure to media coverage of the measles outbreaks.
-A total of `r results$s4$demo$n_recruited` participants returned and `r results$s4$demo$n_complete` successfully completed the study including passing attention checks.
-These participants completed all 14 belief scales and also indicated whether they had seen or heard anything about measles in the news recently.
-
-### Analyses
-
-#### Regression analyses.
-
-```{r, include=F}
-s4_reg <- summary(results$s4$reg)
-```
-
-Mirroring our analyses of interventions, we regressed responses to the *vaccine intentions* scale items on predictors for phase (August-September 2017 vs.
-May 2019, dummy-coded), news exposure (dummy-coded with non-exposure as the baseline), and an interaction between phase and news exposure onto participants’ scores, using a Bayesian mixed-effects ordinal regression including random intercepts by subject and item.
-To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure.
-Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months earlier (interaction effect: $b$ = `r round(s4_reg$fixed[9,1],3)`, 95% CI: [`r round(s4_reg$fixed[9,3], 3)`, `r round(s4_reg$fixed[9,4], 3)`]); see Figure 6, panel A.
-
-#### Modeling belief revision.
-
-To model the effects of news exposure we followed the same procedure as in previous studies, but here augmented the model with a node representing media exposure as a child of the *vaccine intentions* node (for details, see SI); see Figure 6, panel B.
-
 \newpage
 # References
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup

### 2022-02-09 paper/paper-apa-reformatting.Rmd
edits ahead of preprint

--- 2021-12-10 paper/paper-papaja.Rmd
@@
 ---
-title             : "Modeling and leveraging intuitive theories to improve vaccine attitudes"
-shorttitle        : "Intuitive theories of vaccine attitudes"
+title: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
+author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
+output: pdf_document
+bibliography: "../supplement/references.bib"
+csl: "../supplement/pnas.csl"
+header-includes:
+    - \usepackage{setspace}\doublespacing
+---
 
-author: 
-  - name          : "Derek Powell"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "4701 W. Thunderbird Road, Glendale, AZ 85306"
-    email         : "dmpowell@asu.edu"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Data collection
-      - Analysis
-      - Writing
-  - name          : "Kara Weisman"
-    affiliation   : "2"
-    role:
-      - Conceptualization
-      - Data collection
-      - Analysis
-      - Writing
-  - name          : "Ellen M. Markman"
-    affiliation   : "3"
-    role:
-      - Conceptualization
-      - Writing
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+```
 
-affiliation:
-  - id            : "1"
-    institution   : "Arizona State University"
-  - id            : "2"
-    institution   : "University of California, Riverside"
-  - id            : "3"
-    institution   : "Stanford University"
+```{r load-required-data, include=FALSE}
+library(tidyverse)
+results <- readRDS("../local/paper-results.rds") 
+```
 
-authornote: |
-  This manuscript has not yet been peer-reviewed.
+# Abstract
 
-abstract: |
 Much of the richness of human thought is supported by people’s intuitive theories---mental frameworks capturing the perceived structure of the world.
@@
 
-  <!-- https://tinyurl.com/ybremelq -->
+\newpage
 
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["../supplement/references.bib"]
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
----
-
-```{r setup, include = FALSE}
-library("papaja")
-r_refs("r-references.bib")
-```
-
-```{r load-required-data, include=FALSE}
-library(tidyverse)
-results <- readRDS("../local/paper-results.rds") 
-```
+# Main text
 
@@
 From early in life, people are driven to seek out such causal explanations and to use their mental representations of these causal systems to explain, predict, and intervene in the world [see @carey2009; @gelman.legare2011; @gerstenberg.etal2021; @gopnik.wellman1994; @keil1994; @murphy.medin1985; @wellman.gelman1992 for influential treatments of this topic].
-Intuitive theories inform reasoning in a wide variety of domains, including reasoning about physical systems [e.g., @baillargeon2004; @battaglia.etal2013; @spelke1994a; @ullman.etal2017], biological processes [e.g., @carey1985; @carey2009;  @medin.atran1999] and the contents of other people’s minds [e.g., @baker.etal2017; @gopnik.wellman1994; @wellman2015].
+Intuitive theories inform reasoning in a wide variety of domains, including reasoning about physical systems [e.g., @baillargeon2004; @battaglia.etal2013; @spelke1994a; @ullman.etal2017], biological processes [e.g., @carey2009; @carey1985; @medin.atran1999] and the contents of other people’s minds [e.g., @gopnik.wellman1994; @wellman2015; @baker.etal2017].
 
@@
 Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct [e.g., @betsch.sachse2013; @horne.etal2015].
-Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @dube.etal2015; @horne.etal2015; @vannice.etal2011; @wallace.etal2006].
+Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @horne.etal2015; @vannice.etal2011; @wallace.etal2006; @dube.etal2015].
 This is especially  sobering in the context of the coronavirus pandemic: reluctance to be vaccinated against COVID-19 threatens our ability to end a pandemic that has already claimed millions of lives around the world.
@@
 @lewandowsky.etal2012].
-Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence [e.g., @gershman2019; @lewandowsky.etal2012; @jern.etal2014].
+Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence [e.g., @lewandowsky.etal2012; @jern.etal2014; @gershman2019].
 
@@
 Originally designed as tools for artificial intelligence [@pearl1988], Bayesian networks are a class of probabilistic graphical models that have been deployed widely across cognitive science [e.g.
-@gopnik.etal2004; @jern.etal2014; @griffiths.tenenbaum2005].
+@jern.etal2014; @gopnik.etal2004; @griffiths.tenenbaum2005].
 The heart of a Bayesian Network is a graphical structure ---not unlike a "web of belief"---that represents variables as nodes connected by edges, where those edges represent probabilistic or statistical relations.
@@
 
-```{r fig1-maingraph, fig.align='center', out.width="90%", fig.cap="Bayesian network model resulting from hill-climbing algorithm with our generative-model constraints applied to data in Study 1 training split (n = 904).
+```{r fig1-maingraph, fig.align='center', fig.height=8, fig.width=5, fig.cap="Bayesian network model resulting from hill-climbing algorithm with our generative-model constraints applied to data in Study 1 training split (n = 904).
 The network has 29 edges connecting these 14 variables.
@@
 
-```{r fig2-validation, fig.align='center', out.width="100%", fig.cap="Observed responses and model predictions for each belief among participants in the Study 1 testing split.
+```{r fig2-validation, fig.align='center', fig.height=4, fig.width=7, fig.cap="Observed responses and model predictions for each belief among participants in the Study 1 testing split.
 Correlations between observed and predicted values ranged from .380 to .898 across the different belief scales.
@@
 
-```{r fig3-s2, fig.align='center', out.width="100%", fig.cap="Belief changes following the intervention in Study 2.
+```{r fig3-s2, fig.align='center', fig.height=4, fig.width=7, fig.cap="Belief changes following the intervention in Study 2.
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
@@
 
-```{r fig4-predimpacts, fig.align='center',  out.width="50%", fig.cap="Predicted change in vaccination intentions following an equivalent hypothetical change in each of the other 13 beliefs."}
+```{r fig4-predimpacts, fig.align='center', fig.height=3, fig.width=3, fig.cap="Predicted change in vaccination intentions following an equivalent hypothetical change in each of the other 13 beliefs."}
 knitr::include_graphics("../local/pred_change_plt.png")
@@
 
-```{r fig5-s3, fig.align='center',  out.width="100%", fig.cap="Belief changes following the intervention in studies 3a and 3b.
+```{r fig5-s3, fig.align='center', fig.height=4, fig.width=7, fig.cap="Belief changes following the intervention in studies 3a and 3b.
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
@@
 
-```{r fig6-s4, fig.align='center',  out.width="100%", fig.cap="Participants’ belief changes from participation in Study 1 to Study 4.
+```{r fig6-s4, fig.align='center', fig.height=4, fig.width=7, fig.cap="Participants’ belief changes from participation in Study 1 to Study 4.
 Left, mean difference scores comparing beliefs reported in August-September 2017 and May 2019 for the 14 belief scales, across participants who did and did not report exposure to news of the ongoing New York measles outbreak.
@@
 @kahan2013; @flynn.etal2017; @kunda1990].
-Yet many of the phenomena traditionally taken as evidence for these theories can also be explained by normative models of belief revision, so long as we are willing to posit that other auxiliary beliefs can affect the relationships between a belief and evidence [e.g.,@gershman2019; @jern.etal2014].
+Yet many of the phenomena traditionally taken as evidence for these theories can also be explained by normative models of belief revision, so long as we are willing to posit that other auxiliary beliefs can affect the relationships between a belief and evidence [e.g., @jern.etal2014; @gershman2019].
 Adjudicating between competing views of belief revision will require us to move beyond minimal models and illustrative simulations by assessing whether people actually do hold these auxiliary beliefs, and whether their broader belief systems behave according to the rules of probabilistic inference.
@@
 On the other hand, the pandemic has presented its own unique issues.
-MRNA vaccines like those from Pfizer-BioNtech and Moderna represent highly novel technologiesdeveloped at a pace far faster than previously imagined possible.
-The unprecedented nature of these vaccines could engender hesitancy even among people who are otherwise comfortable with vaccinations.
+MRNA vaccines like those from Pfizer-BioNtech and Moderna represent highly novel technologies that are currently approved only under emergency use authorizations after being developed at a pace far faster than previously imagined possible.
+These facts could engender hesitancy even among people who are otherwise comfortable with vaccinations.
 
@@
 # References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup

### 2022-02-09 paper/paper-papaja.Rmd
edits ahead of preprint

@@
       - Conceptualization
+      - Investigation
+      - Methodology
       - Data collection
-      - Analysis
+      - Formal Analysis
+      - Visualization
       - Writing
@@
     role:
-      - Conceptualization
+      - Conceptualization 6t            
+      - Investigation
       - Data collection
-      - Analysis
+      - Formal Analysis
+      - Visualization
       - Writing
@@
       - Conceptualization
+      - Methodology
       - Writing
@@
   - id            : "2"
-    institution   : "University of California, Riverside"
+    institution   : "University of California - Riverside"
   - id            : "3"
@@
 
+note: |
+  This manuscript has not yet been peer-reviewed.
+
 authornote: |
-  This manuscript has not yet been peer-reviewed.
+  All data, and analysis code for this project are available at https://osf.io/sdfpj/. Preregistration information for Studies 3a and 3b is available at https://osf.io/csnez/registrations.
 
@@
   Much of the richness of human thought is supported by people’s intuitive theories---mental frameworks capturing the perceived structure of the world.
-But intuitive theories can sometimes contain and reinforce misconceptions, such as misconceptions about vaccine safety that discourage vaccination.
-We argue that addressing misconceptions requires awareness of the broader conceptual contexts in which they are embedded.
-Here, we developed a cognitive model of the intuitive theory surrounding vaccination decisions.
-Using this model, we were able to make accurate predictions about how people's beliefs would be revised in light of educational interventions, design an effective new intervention encouraging vaccination, and understand how these beliefs were affected by real-world events.
-This approach provides the foundation for richer understandings of intuitive theories and belief revision more broadly.
+But intuitive theories can also contain and reinforce dangerous misconceptions.
+In this paper we take up the case of misconceptions about vaccine safety that discourage vaccination.
+These misconceptions constitute a major public health risk that predates the coronavirus pandemic but that has become all the more dire in recent years.
+We argue that addressing such misconceptions requires awareness of the broader conceptual contexts in which they are embedded.
+To build this understanding, we examined the structure and revision of people’s intuitive theories of vaccination in five large survey studies (total _N_ = 3196).
+Based on these data, we present a cognitive model of the intuitive theory surrounding people’s decisions about whether to vaccinate young children against diseases like measles, mumps, and rubella (MMR).
+Using this model, we were able to make accurate predictions about how people’s beliefs would be revised in light of educational interventions, design an effective new intervention encouraging vaccination, and understand how these beliefs were affected by real-world events (the measles outbreaks of 2019).
+In addition to presenting a promising way forward for promoting the MMR vaccine, this approach has clear implications for encouraging the uptake of COVID-19 vaccines, especially among parents of young children.
+At the same time, this work provides the foundation for richer understandings of intuitive theories and belief revision more broadly.
 
@@
 
-documentclass     : "apa6"
+documentclass     : "apa7"
+csl               : "apa7.csl"
 classoption       : "man"
@@
 
-Because intuitive theories are powerful tools for making sense of the world, when these theories are mistaken there can be serious consequences.
+Because intuitive theories are such powerful tools for making sense of the world, when these theories are mistaken there can be serious consequences.
 In this paper, we focus on an important and timely example: misconceptions about vaccine safety.
@@
 Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @dube.etal2015; @horne.etal2015; @vannice.etal2011; @wallace.etal2006].
-This is especially  sobering in the context of the coronavirus pandemic: reluctance to be vaccinated against COVID-19 threatens our ability to end a pandemic that has already claimed millions of lives around the world.
+This is especially  sobering in the context of the coronavirus pandemic: widespread reluctance to be vaccinated against COVID-19 threatens our ability to end a pandemic that has already claimed more than five million lives around the world.
 
@@
 Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence [e.g., @gershman2019; @lewandowsky.etal2012; @jern.etal2014].
+Consider some of the beliefs people who are skeptical of childhood vaccination expressed when we asked them to explain their views in an open-ended qualitative survey (conducted pre-pandemic; _n_ = 16).
+Several participants saw vaccines as “unnatural” and expressed concerns about toxic additives in vaccines, such as heavy metals and mercury.
+One said, “Vaccines are unnatural additions to the body.
+The human body should naturally fight off the disease and we should not be controlling how nature plays its role on mankind.” Some doubted whether certain diseases were worth worrying over, while others feared that the contents of vaccines “are too strong and too concentrated for a baby’s body to properly handle.” A number of respondents were skeptical of the medical community’s objectivity in testing the safety of vaccines.
+One respondent wrote that vaccines were “A BIG MONEY MAKING SCAM BY THE BIG PHARMS” (emphasis theirs); another thought that health professionals “are brainwashed by the medical media and the government.”
 
-Consider some of the beliefs people who are skeptical of childhood vaccination expressed when we asked them to explain their views in an open-ended qualitative survey (conducted pre-pandemic; *n* = 16).
-Several participants saw vaccines as "unnatural" and expressed concerns about toxic additives in vaccines, such as heavy metals and mercury.
-One said, “Vaccines are unnatural additions to the body.
-The human body should naturally fight off the disease and we should not be controlling how nature plays its role on mankind.” Some doubted whether certain diseases were worth worrying over, while others feared that the contents of vaccines “are too strong and too concentrated for a baby's body to properly handle.” A number of respondents were skeptical of the medical community’s objectivity in testing the safety of vaccines.
-One respondent wrote that vaccines were “A BIG MONEY MAKING SCAM BY THE BIG PHARMS” (emphasis theirs); another thought that health professionals “are brainwashed by the medical media and the government.” To people holding these beliefs, it could well seem unreasonable to vaccinate a 2-month-old baby against 5 or more diseases at once.
-Moreover, if skeptics believe that the medical community is unduly influenced by pharmaceutical companies, they might doubt the validity of medical findings that favor these companies’ interests.
-Altogether, these beliefs might sustain misconceptions about vaccine safety, even in the face of counter-evidence.
+To people holding these beliefs, it could well seem unreasonable to vaccinate a 2-month-old baby against 5 or more diseases at once, as the CDC recommends.
+Moreover, if skeptics believe that the medical community is unduly influenced by pharmaceutical companies, they might doubt the validity of medical findings that appear to favor these companies’ interests.
+Altogether, these beliefs might sustain misconceptions about vaccine safety, even in the face of counter-evidence: CDC guidelines, clinical studies, even the advice of the family’s pediatrician could be interpreted not as evidence that vaccines are safer than the person thought, but instead as further proof of the widespread corruption in the medical community.
 
 The way in which evidence affects any particular belief is unavoidably shaped by other interrelated beliefs.
-Duhem [-@duhem1954] and Quine [-@quine1951] famously argued that scientific theories necessarily incorporate *auxiliary hypotheses* that influence how observations are interpreted: When an observation is inconsistent with a hypothesis under certain auxiliary assumptions, a scientist cannot know whether to revise the hypothesis or the auxiliary assumptions.
-Similarly, we argue that intuitive theories incorporate auxiliary beliefs that affect how other beliefs are revised in light of evidence [also see @gershman2019].
+Duhem [-@duhem1954] and Quine [-@quine1951] famously argued that scientific theories necessarily incorporate *auxiliary hypotheses* that influence how observations are interpreted: when an observation is inconsistent with a hypothesis under certain auxiliary assumptions, a scientist cannot know whether to revise the hypothesis or the auxiliary assumptions.
+Similarly, we argue that intuitive theories incorporate auxiliary beliefs that affect how other beliefs are revised in light of evidence: when an observation is inconsistent with a person’s current belief under certain auxiliary assumptions, the person cannot know whether to revise the belief or the auxiliary assumptions [also see @gershman2019].
 
@@
 
-2) When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g., evidence for B will increase credence in A, and vice versa); and
+2) When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g., evidence for B will increase credence in A, and vice versa).
 
-3) Thus across individuals, the average change in one belief following evidence affecting another belief will be proportional to the correlation between those beliefs across individuals (evidence for B will increase credence in A in proportion to the correlation between beliefs A and B).
+3) Thus, across individuals, the average change in one belief following evidence affecting another belief will be proportional to the correlation between those beliefs across individuals (evidence for B will increase credence in A in proportion to the correlation between beliefs A and B).
 
@@
 @gopnik.etal2004; @jern.etal2014; @griffiths.tenenbaum2005].
-The heart of a Bayesian Network is a graphical structure ---not unlike a "web of belief"---that represents variables as nodes connected by edges, where those edges represent probabilistic or statistical relations.
+The heart of a Bayesian network is a graphical structure ---not unlike a "web of belief"---that represents variables as nodes connected by edges, where those edges represent probabilistic or statistical relations.
 
@@
 Structure learning algorithms [see @scutari.denis2021] provide a means for searching through the (super-exponentially large) possible space of Bayesian networks to find the structure most likely to have generated some observed data.
-These approaches allow us to scale the Bayesian network modelling framework beyond the simple models characteristic of early computational work on intuitive theories [e.g., @griffiths.tenenbaum2005].
+These approaches allow us to scale the Bayesian network modeling framework beyond the smaller models characteristic of early computational work on intuitive theories [e.g., @griffiths.tenenbaum2005].
+
+## Current studies
 
@@
 In Study 2, we replicated the success of an existing intervention emphasizing the dangers of childhood diseases [@horne.etal2015] and used our model to provide a more detailed understanding of *how and why* this intervention increases vaccine intentions and its effects on related beliefs.
-In Study 3a and 3b, we drew inspiration from our model to create and validate the success of  a novel intervention aimed at debunking concerns about toxic additives.
+In Study 3a and 3b, we drew inspiration from our model to create and validate the success of  a novel intervention aimed at addressing concerns about toxic additives in vaccines.
 Finally, in Study 4 we tested whether people's beliefs changed coherently following relevant real-world events, by examining beliefs before and after serious outbreaks of measles in the United States in early 2019.
+
 Taken together, this work illustrates the promise of understanding belief revision in terms of intuitive theories and the utility of discovering and formalizing intuitive theories via computational models.
-And, it lays the foundation for empirically-validated, theory-based educational interventions that could encourage people to vaccinate their children and themselves against dangerous diseases like measles and COVID-19.
+Of particular interest in the current moment, these findings lay a foundation for empirically-validated, theory-based educational interventions that could encourage people to vaccinate their children and themselves against dangerous diseases like measles and COVID-19.
 
-# The present studies
+# Study 1: Assessing and modeling intuitive theories of vaccination
 
-## Qualitative studies and scale development
+Across all our studies, our primary outcome of interest was participants’ intentions to vaccinate their children against diseases like measles, mumps, and rubella (which we refer to henceforth as *vaccination intentions*).
+Drawing on a variety of sources, including research on anti-vaccine skepticism [e.g.,  @dube.etal2015; @larson.etal2015; @salmon.etal2015; @williams2014], anti-vaccine websites, and our own qualitative work with vaccine skeptics (see SI), we generated a list of 13 additional beliefs that, though surely not exhaustive, might jointly offer a reasonable means of understanding and predicting vaccine intentions.
 
-We drew on a variety of sources, including academic articles on anti-vaccine skepticism [e.g.,  @dube.etal2015; @larson.etal2015; @salmon.etal2015; @williams2014], anti-vaccine websites, and a qualitative survey with self-identified vaccine skeptics (*n*=16) via Amazon Mechanical Turk (MTurk) to generate a list of beliefs that might influence people’s decisions about whether to vaccinate their children (*vaccine intentions*): *vaccine danger*, *toxic additives in vaccines*, *vaccine effectiveness*, *disease rarity*, *disease severity, infant immune system (IIS): weakness*, *IIS: limited capacity*, *IIS: vaccines strain*, *parental protectiveness*, *parental expertise*, *medical skepticism*, *naturalism*, and *holistic balance*.
-(See main text for descriptions, and SI for the items included in these scales.) We translated these qualitative insights into 14 psychometrically-valid scales; each scale measured agreement with 4-6 statements, including at least one reverse-coded item, and was highly reliable (observed reliability, Study 1: all Cronbach’s $\alpha \geq .73$).
-We developed 13 of these scales, and included one preexisting scale [the “holistic balance” subscale from @mcfadden.etal2010].
+We translated these qualitative insights into 14 psychometrically-valid scales.
+In addition to 1) _vaccination intentions_ (e.g.
+“If I had a young baby I would have him or her vaccinated.”), these included a variety of beliefs about vaccines, including beliefs about 2) _vaccine danger_, the overall danger of vaccines (e.g., “Many children have severe adverse reactions to the MMR vaccine”); 3) _toxic additives in vaccines_ (e.g., “Exposure to certain additives in vaccines can cause major health problems.”); and 4) _vaccine effectiveness_, how effective vaccines are in preventing disease (e.g., “Your chances of getting a disease after being vaccinated against it are incredibly low”); as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about 5) _disease rarity _(e.g., “Diseases like measles and whooping cough are so rare that there is no real need to worry about them”) and 6) _disease severity_ (e.g., “Diseases like measles and whooping cough are extremely dangerous for young children”).
+Beyond this, we theorized that participants’ understanding of the infant immune system might be relevant, including beliefs that 7) the infant immune system is weak (_IIS: weakness_; e.g., “Babies’ immune systems are weak”); 8) the infant immune system is limited in its capacity and can be easily overwhelmed (_IIS: limited capacity_; e.g., “Babies’ immune systems are severely limited in how much they can cope with at one time.”); and 9) vaccines strain the infant immune system (_IIS: vaccines strain_; e.g., “Vaccines strain the immune system much like the actual disease”).
+We also included general theories about parenting and medicine: 10) general _parental protectiveness_ (e.g., “Parents should strive to control their baby’s environments as much as possible”); 11) _parental expertise_, namely the belief that parents usually know more about their children’s health than medical experts (e.g., “Every individual is different and a parent knows their own child best”); and 12) _medical skepticism_, including concerns about pharmaceutical companies and corruption in the medical community (e.g., “Pharmaceutical companies put pressure on the FDA and CDC to suppress negative findings”); and two two broad worldviews: 13) _naturalism_, a general preference for natural over artificial things (e.g., “Natural things are always better than synthetic alternatives”); and 14) _holistic balance_, one important aspect of attitudes toward alternative medicine (e.g., “The body is essentially self-healing and the task of a health care provider is to assist the healing process”; [@mcfadden.etal2010]).
 
-These 14 scales formed the backbone of Studies 1-4.
+Each scale measured agreement with 4-6 statements, including at least one reverse-coded item, and was highly reliable (observed reliability, Study 1: all Cronbach’s $\alpha \geq .73$ .73).
+We developed 13 of these scales, and included one preexisting scale (the “holistic balance” subscale from [@mcfadden.etal2010].
+See SI for all items included in all scales.
 
-## General Methods: Studies 1-4
-
-Studies 1-4 were conducted online via Amazon Mechanical Turk between August 2017 and June 2019.
-Repeat participation was prevented, with no participants involved in more than one study, except as noted in Study 4.
-A breakdown of demographics and compensation by study is available in the SI.
-
-All participants responded at least once to the 14 belief scales just described.
-Each scale was presented on a separate survey page, and participants rated a series of statements on a 7-point scale from “Strongly disagree” (coded as -3) to “Strongly agree” (+3).
-Scales, and questions within each scale, were presented in a random order for each participant.
-Attention checks (e.g., “Please select somewhat agree”) were embedded within two to four randomly chosen scales and participants who failed any of these checks were excluded from analyses.
-
-We scored each belief scale by averaging a participant’s responses to each item (after reverse-coding where appropriate), then rescaling these values to fall between 0 and 1.
-We considered this score to represent the participant’s credence in the belief.
-
-## Study 1: Assessing and modeling intuitive theories of vaccination
-
-Our primary outcome of interest was participants’ intentions to vaccinate their children against diseases like measles, mumps, and rubella (*vaccination intentions*).
-Drawing on a variety of sources, including research on anti-vaccine skepticism, anti-vaccine websites, and our own qualitative work with vaccine skeptics (see SI), we generated a list of 13 additional beliefs that, though surely not exhaustive, might jointly offer a reasonable means of understanding and predicting vaccine intentions.
-
-These included a variety of claims about vaccines, including beliefs about 1) the overall danger of vaccines (*vaccine danger*); 2) *toxic additives in vaccines*; and 3) *vaccine effectiveness*, how effective vaccines are in preventing disease; as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about 4) *disease rarity* and 5) *disease severity*.
-Beyond this, we theorized that participants’ understanding of the infant immune system might be relevant, including beliefs that 6) the infant immune system is weak (*IIS: weakness*); 7) the infant immune system is limited in its capacity and can be easily overwhelmed (*IIS: limited capacity*); and 8) vaccines strain the infant immune system (*IIS: vaccines strain*).
-We also included general theories about parenting and medicine: 9) general *parental protectiveness*; 10) *parental expertise*, namely the belief that parents usually know more about their children’s health than medical experts; and 11) *medical skepticism*, including concerns about pharmaceutical companies and corruption in the medical community; and two two broad worldviews: 12) *naturalism*, a general preference for natural over artificial things; and 13) *holistic balance*, one important aspect of attitudes toward alternative medicine (e.g., “The body is essentially self-healing and the task of a health care provider is to assist the healing process”; [@mcfadden.etal2010]).
-
-We developed psychometrically robust scales to measure these beliefs, then administered these 14 belief scales to participants and in an online survey with `r results$s1$demo$n_include` participants.
-There were strong intercorrelations among these 14 beliefs confirming that these beliefs are, in fact, closely related to each other and to intentions to vaccinate children (see SI).
-
-We used these intercorrelations to build a cognitive model of the relations among these beliefs via Bayesian network structure learning techniques.
+In Study 1, we administered these 14 belief scales to participants and in an online survey with `r results$s1$demo$n_include` participants.
+We then used these intercorrelations to build a cognitive model of the relations among these beliefs via Bayesian network structure learning techniques.
 
@@
 `r results$s1$demo$n_exclude` participants (6%) failed at least one of two attention check questions and were excluded from further analysis, leaving a final sample of n = `r results$s1$demo$n_include`.
-After completing all 14 scales, participants were asked standard demographics questions as well as a handful of questions about whether they were or were expecting to be a parent.
-They were also debriefed with a brief statement noting that vaccines are safe and pointing them toward a WHO website for further information.
+See SI for demographic information about this sample.
 
@@
 
-Participants (final *n* = `r results$s1$demo$n_include`) responded to the 14 belief scales, followed by demographics questions and a handful of questions about whether they were or were expecting to be a parent.
-They were then debriefed with a brief statement noting that vaccines are safe and pointing them toward a WHO website for further information.
+Participants (final *n* = `r results$s1$demo$n_include`) responded to the 14 belief scales.
+Each scale was presented on a separate survey page, and participants rated a series of statements on a 7-point scale from “Strongly disagree” (coded as -3) to “Strongly agree” (+3).
+Scales, and questions within each scale, were presented in a random order for each participant.
+Attention checks (e.g., “Please select somewhat agree”) were embedded within two to four randomly chosen scales and participants who failed any of these checks were excluded from analyses.
+We scored each belief scale by averaging a participant’s responses to each item (after reverse-coding where appropriate), then rescaling these values to fall between 0 and 1.
+We considered this score to represent the participant’s credence in the belief.
+
+The 14 belief scales were followed by demographics questions and a handful of questions about whether participants were or were expecting to be a parent.
+Participants were then debriefed with a brief statement noting that vaccines are safe and pointing them toward a WHO website for further information.
 
@@
 The goal of this study was to use these data to conduct a bottom-up search for a Bayesian network that would represent the intuitive theory surrounding vaccination decisions as a network of related beliefs.
+There were strong intercorrelations among these 14 beliefs confirming that these beliefs are, in fact, closely related to each other and to intentions to vaccinate children (see SI).
 Based on the observed associations among participants' beliefs about each of theses issues, we sought to infer how these states of affairs (e.g., that vaccines are dangerous, that diseases are severe) are connected in people's intuitive theories---how people understand these states of affairs to cause, imply, or otherwise influence one another.
@@
 
-Having transformed participants’ averaged belief scale responses to fall between 0 and 1, we estimated the parameters of the model as a beta regression using maximum likelihood methods (see SI).
+Having transformed participants’ scores on each belief scale to fall between 0 and 1, we estimated the parameters of the model as a beta regression using maximum likelihood methods (see SI).
 
@@
 In this model, the $x$ in the equation above corresponded to participants’ continuous responses to the belief scales (e.g.
-a participants score for the *vaccine danger* scale).
+a participant's score for the *vaccine danger* scale).
 Then, from the parameters estimated in the data model we created a cognitive model of participants’ reasoning, where the $x$ are binary, indicating whether that state of affairs obtains (e.g., whether “vaccines are dangerous”).
@@
 
-In particular, we assumed  that the intuitive theory is a generative model, so that these influence relations (“edges”) should flow from causes or other “generating” states of affairs toward effects.
-For instance, we stipulated that *vaccine intentions* would be a “child node,” with edges only flowing inwards and not outwards (since one’s intention to vaccinate cannot “generate” the facts about vaccinations safety, effectiveness, etc).
+In particular, we applied a constraint we called the “generative model principle,” based on the assumption that the intuitive theory is a generative model, so that these influence relations (“edges”) should flow from causes or other “generating” states of affairs toward effects.
+For instance, we stipulated that vaccine intentions---our outcome of interest---would be a “child node,” with edges only flowing inwards and not outwards (since one’s intention to vaccinate cannot “generate” the facts about vaccinations safety, effectiveness, etc).
+This generative model principle instills a common core assumption in research on intuitive theories and causal explanatory reasoning[e.g.
+@gerstenberg.etal2021; @gopnik.etal2004; @cheng1997].
 
-We applied a constraint we called the “generative model principle,” specifying that influence relations (edges) should flow from causes (or other generating states of affairs) to effects; instilling a core assumption in research on intuitive theories and causal explanatory reasoning [e.g.
-@gerstenberg.etal2021; @gopnik.etal2004; @cheng1997].
-We sorted the 14 measured beliefs into four tiers based on how general or abstract each belief was, reasoning that general and abstract states of affairs should be understood to cause (or otherwise generate) more specific and concrete states of affairs, so edges should flow from the general and abstract toward the specific and concrete (e.g., if natural things are better than artificial things, this should set an expectation about whether a specific class of artificial things--vaccines--is safe).
+To apply our generative model principle, we sorted the 14 measured beliefs into four tiers based on how general or abstract each belief was, reasoning that general and abstract states of affairs should be understood to cause (or otherwise generate) more specific and concrete states of affairs, so edges should flow from the general and abstract toward the specific and concrete (e.g., if natural things are better than artificial things, this should set an expectation about whether a specific class of artificial things--vaccines--is safe).
 We considered *holistic balance* and *naturalism* to be the most general and abstract beliefs among those we measured; followed by theories about parenting and medicine; then specific beliefs about vaccines, diseases, and the infant immune system; and finally our outcome of interest, *vaccine intentions*---the most concrete measurement of a specific intended action.
@@
 See SI for more detailed explanations of these modeling choices.
-
-Some caution should be exercised in interpreting the relationships in the network.
-Due to Bayesian networks' tight connections with structural causal networks, it is tempting to interpret the edges in this network as representing a mental causal model.
-But, in some cases these relationships are better thought of as probabilistic dependencies or “influence” relations [@williamson2001].
-For instance, intuitively we might imagine that vaccines having toxins could cause them to be dangerous and ineffective.
-These nodes are connected in the model, but the edges between them run in the opposite directions, and therefore do not support a clear causal interpretation.
-One interpretation is that this edge instead reflects a set membership relation; that toxins are one type of danger vaccines might present.
-In other cases, our data and explicit constraints do not perfectly identify the directions of the edges.
-This is the case for two edges (Naturalism $\rightarrow$  Holistic Balance and Medical Skepticism $\rightarrow$ Parental Expertise; see SI for details).
-In both cases, we do not feel it is intuitive which direction the edge should flow in, nor even that it should be directed at all; we might even speculate there is an additional unmeasured variable that connects these beliefs and that would best account for their association.
-
-Bearing these qualifications in mind, we see this Bayesian network as a limited but plausible cognitive model of these beliefs.
 
@@
 The three nodes with direct connections to *vaccine intentions* are beliefs about *vaccine effectiveness*, *vaccine danger*, and the severity of childhood diseases (*disease severity*) ---concrete beliefs that are, at face value, especially closely related to vaccination decisions.
-This gives us confidence that the model is capturing important relationships.
+This gives us confidence that the model is capturing important aspects of the intuitive theory of interest.
 
@@
 The model sheds light on this surprising (lack of) relationship: Although the belief that the infant immune system is limited in capacity is positively related to the belief that vaccines strain the immune system---discouraging vaccination, as we had assumed---it also seems to promote the belief that childhood diseases have severe consequences for young children (*disease severity*), which might, in turn, encourage vaccination.
-These countervailing forces---which, on average, seem to have cancelled each other out in this sample---dissuaded us from our plan to develop an intervention aimed at dispelling misconceptions about limited capacity in order to encourage childhood vaccination.
+These countervailing forces---which, on average, seem to have cancelled one-another out in this sample---dissuaded us from our plan to develop an intervention aimed at dispelling misconceptions about limited capacity in order to encourage childhood vaccination.
 
-In sum: From a set of potentially relevant beliefs and a general principle guiding the likely relationships among these beliefs, we generated a cognitive model of an intuitive theory of this domain.
+It is worth pointing out that not all of the relationships represented in the model should be interpreted as _causal_.
+Due to Bayesian networks’ tight connections with structural causal networks, it can be tempting to give the edges this interpretation, but in some cases these relationships are better thought of as probabilistic dependencies or “influence” relations (Williamson, 2001).
+For instance, intuitively we might imagine that vaccines having toxins (_toxic additives in vaccines_) could cause them to be dangerous (_vaccine danger_).
+These nodes are connected in the model, but the edges between them run in the opposite direction, and therefore do not support a clear causal interpretation.
+One interpretation is that this edge instead reflects a set membership relation; that toxins are one type of danger vaccines might present.
+
+In other cases, our data and explicit constraints do not perfectly identify the directions of the edges.
+This is the case for two edges (Naturalism $\rightarrow$  Holistic Balance and Medical Skepticism $\rightarrow$ Parental Expertise; see SI for details).
+In both cases, we do not feel it is intuitive which direction the edge should flow in, nor even that it should be directed at all; we might even speculate there is an additional unmeasured variable that connects these beliefs and that would best account for their association.
+
+### Summary
+
+From a set of potentially relevant beliefs and a general principle guiding the likely relationships among these beliefs, we generated a cognitive model of an intuitive theory of this domain.
 In Studies 2-4, we use this same model to predict how this intuitive theory guides reasoning about new information.
@@
 
+Very few educational interventions have been shown to improve attitudes toward childhood vaccination.
 One of the few successful educational interventions in this domain was tested by Horne et al.
@@
 This “disease risk” intervention improved attitudes toward vaccines compared to an irrelevant control essay and compared to an intervention aimed at debunking concerns about vaccines causing autism.
+In Study 2, we aimed to replicate this success and leverage the cognitive model developed in Study 1 to gain insight into how and why such an intervention successfully induces  belief revision in this domain.
 
@@
 We recruited `r results$s2$demo$n_recruited` people to participate in a two-day study via mTurk in April 2018.
-Two days later, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r results$s2$demo$n_recruited_post` participants returning (`r results$s2$demo$n_eligible` invited, retaining `r round(results$s2$demo$n_recruited_post/results$s2$demo$n_eligible*100, 1)`% of the Day 1 sample).
+Two days later, participants who completed Phase 1 and passed attention checks were invited via email to participate in Phase 2 of the study, with `r results$s2$demo$n_recruited_post` participants returning (`r results$s2$demo$n_eligible` invited, retaining `r round(results$s2$demo$n_recruited_post/results$s2$demo$n_eligible*100, 1)`% of the Phase 1 sample).
 Participants were paid \$1.35 for their participation in each phase of the study.
-`r results$s2$demo$n_failed_post` participants (`r round( (results$s2$demo$n_failed_post/results$s2$demo$n_recruited_post)*100, 1)`%) failed at least one attention check on Day 2 and were excluded from further analysis.
+`r results$s2$demo$n_failed_post` participants (`r round( (results$s2$demo$n_failed_post/results$s2$demo$n_recruited_post)*100, 1)`%) failed at least one attention check on Phase 2 and were excluded from further analysis.
 We also excluded from analyses `r results$s2$demo$n_duplicate` additional participants who accessed the second survey more than once.
@@
 In Phase 2 (approximately two days later), participants completed a study very similar to Horne et al.’s (2015) original intervention study.
-Participants were randomly assigned to either the disease risk condition or the no-intervention condition, with the constraint that the distributions of participants’ Phase 1 *vaccine intentions* scores should be similar across the two conditions; we accomplished this by stratifying participants into three groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
+Participants were randomly assigned to either the disease risk condition or a no-intervention control condition, with the constraint that the distributions of participants’ Phase 1 *vaccine intentions* scores should be similar across the two conditions; we accomplished this by stratifying participants into three groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
 
@@
 
-Changes were also observed across the belief network identified in Study 1.
+Visual inspection of Figure 3, panel A, further reveals that changes were also observed across the belief network identified in Study 1.
 Not only did participants exposed to the intervention come to see childhood diseases as more severe, they also came to see vaccines as less dangerous, and demonstrated less medical skepticism as well as less commitment to “holistic balance”.
@@
 Using this augmented model, we are able to “condition” the model on this evidence node, and thereby predict how observing evidence will affect all of the beliefs in the network.
-As shown in Figure 3, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (*r* = `r results$s2$modcorr`).
+As shown in Figure 3, panel B, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (*r* = `r results$s2$modcorr`).
 
@@
 The intervention highlighted that formaldehyde is already present in children’s bodies (and even in foods like pears) in far larger quantities than contained in any vaccine.
-The full intervention text can be found in SI.
+The full intervention text is presented below.
+
+> **"Vaccine ingredients" intervention text**\
+> Vaccines are one of the most important medical advances in history, but some parents worry that vaccines contain toxins that could harm their babies.
+In fact, all of the ingredients in a vaccine serve important purposes that help ensure the safety and effectiveness of the vaccine.
+Decades of research have shown vaccine ingredients to be safe, even in much larger quantities than those found in vaccines.\
+> **What’s in a vaccine?**\
+> **Active ingredients**\
+> The key ingredient in all vaccines is one or more active ingredients, whose purpose is to train the immune system to recognize and combat the pathogens that cause diseases.
+To do this, certain molecules from the pathogen are introduced into the body to trigger an immune response.
+These molecules are called antigens, and they are present on all viruses and bacteria.
+By injecting these antigens into the body, the immune system can safely learn to recognize them as hostile invaders, produce antibodies, and remember them for the future.\
+>**Other Ingredients**\
+> A typical dose of an injected vaccines is just 0.5 millilitres of liquid, which is just a few drops.
+Apart from active ingredients, the main ingredient in vaccines is water.
+All other ingredients weigh a few thousandths of a gram or even less.
+All of the ingredients in vaccines have been proven to be safe for children in these minute quantities.\
+> All of the ingredients in a vaccine serve important purposes, and are present to ensure that the vaccine is safe and effective.
+Some of these added ingredients are adjuvants, added to enhance the immune system response; others are antibiotics, to prevent contamination during the manufacturing process; and still other ingredients act as preservatives and stabilizers.\
+> To take one example, consider one of the scariest things you may have heard about the ingredients in vaccines: that some vaccines contain formaldehyde.
+It may surprise you to learn that formaldehyde is actually produced by the human body as part of normal metabolic processes.
+Human bodies---even babies’ bodies---naturally produce, process, and safely excrete formaldehyde.
+The amount of formaldehyde in vaccines is extremely small compared to what our bodies produce on their own: the amount of formaldehyde naturally present in a 2-month-old infant’s blood (around 1.1 milligrams) is ten times greater than the amount found in any vaccine (less than 0.1 milligrams).
+In addition, many healthy foods--such as apples, grapes, bananas, and pears---naturally contain formaldehyde.
+A pear, for example, contains around 50 times more formaldehyde than is found in any vaccine.
 
@@
 
-We conducted two preregistered experiments (3a and 3b) testing the effects of this novel intervention aimed at dispelling concerns about toxic additives in vaccines using the same pretest-posttest design as Study 2.
-These studies followed similar design procedures as Study 2, with phase 2 conducted 1-2 days after phase 1.
+We conducted two preregistered experiments[^prereg] (Study 3a and Study 3b) testing the effects of this novel intervention aimed at dispelling concerns about toxic additives in vaccines using the same pretest-posttest design as Study 2.
+These studies followed similar design procedures as Study 2, with Phase 2 conducted 1-2 days after Phase 1.
 In both Study 3a (April 2019) and Study 3b (May 2019; combined final *n* = `r results$s3$demo$n_complete`) the vaccine ingredients intervention was compared against no-intervention control.
 Unlike Study 2, we did not stratify participants before random assignment to conditions.
+
+[^prereg]: https://osf.io/csnez/registrations
 
@@
 This left a final sample of `r results$s3$demo$n_complete` participants.
+See SI for demographic information about this sample.
 
@@
 
-Procedures for studies 3a and 3b closely followed those of Study 2, but these studies tested the effects of a novel intervention aimed at dispelling concerns about toxic additives in vaccines.
-Full text of this intervention is available in supplementary materials.
-In both studies, participants were randomly assigned to either a no-intervention control condition or to the novel Vaccine Ingredients intervention.
+Procedures for Studies 3a and 3b closely followed those of Study 2, but these studies tested the effects of a novel intervention aimed at dispelling concerns about toxic additives in vaccines.
+In both studies, participants were randomly assigned to either a no-intervention control condition or to the novel "vaccine ingredients" intervention.
 
@@
 
-As they shared the same design, we combined data from studies 3a and 3b for analysis (but see SI for separate analyses by study).
-As in study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine ingredients intervention on participants’ *vaccination intentions* scores.
+As they shared the same design, we combined data from Studies 3a and 3b for analysis (but see SI for separate analyses by study).
+As in Study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine ingredients intervention on participants’ *vaccination intentions* scores.
 The vaccine ingredients intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: $b$ = `r round(s3_reg$fixed[9,1],3)`, 95% CI: [`r round(s3_reg$fixed[9,3], 3)`, `r round(s3_reg$fixed[9,4], 3)`]); see Figure 5, panel A.
-However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: $b$ = `r round(s3_reg$fixed[7,1],3)`, 95% CI: [`r round(s3_reg$fixed[7,3], 3)`, `r round(s3_reg$fixed[7,4], 3)`]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
+It is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: $b$ = `r round(s3_reg$fixed[7,1],3)`, 95% CI: [`r round(s3_reg$fixed[7,3], 3)`, `r round(s3_reg$fixed[7,4], 3)`]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
+We discuss this further below, but given that these studies were randomized controlled trial designs, these findings do not impair our ability to conclude that the intervention was causally efficacious in affecting vaccine intentions.
 
@@
 Approximately `r round(100*(results$s4$demo$n_news/results$s4$demo$n_complete),0) `% of participants reported recently seeing, hearing, or reading about measles outbreaks.
+See SI for demographic information about this sample.
 
@@
 
-Figure 6 shows the average change in participants’ beliefs following the outbreaks of 2019.
+Figure 6, panel A, shows the average change in participants’ beliefs following the outbreaks of 2019.
 Among participants who were exposed to relevant news covered, we observed changes in a number of beliefs, with notable increases in intentions to vaccinate, perceptions of vaccine efficacy, and perceptions of disease severity, as well as notable decreases in concern about vaccine danger.
@@
 
-As shown in Figure 6, the changes in participants’ beliefs are very similar to the model’s predictions (*r* = `r results$s4$modcorr`), suggesting that the changes in their beliefs were highly coherent with respect to their intuitive theories of the domain.
+As shown in Figure 6, panel B, the changes in participants’ beliefs are very similar to the model’s predictions (*r* = `r results$s4$modcorr`), suggesting that the changes in their beliefs were highly coherent with respect to their intuitive theories of the domain.
 Modeling these beliefs as united by an intuitive theory not only captures how these beliefs are revised immediately in light of evidence, but also how they are changed by real-world events.
@@
 
-Our findings indicate that beliefs related to vaccination decisions can be understood as situated within a coherent intuitive theory: these beliefs were systematically related across individuals (Study 1), and these relationships were predictive of changes across these beliefs following evidence, whether that evidence took the form of educational interventions (Studies 2-3) or real-world events (Study 4).
+Our findings indicate that beliefs related to vaccination decisions can be understood as situated within a coherent intuitive theory: these beliefs were systematically related across individuals (Study 1), and these relationships were predictive of changes across these beliefs following evidence, whether that evidence took the form of educational interventions (Studies 2, 3a, 3b) or real-world events (Study 4).
 Modeling this intuitive theory formally as a Bayesian network allowed us to create a cognitive model that demonstrates these key features of intuitive theories quantitatively.
-Looking forward, this formal representation ---though simplified and imperfect ---lays a foundation for richer and more complex descriptions in the future.
+Looking forward, this formal representation ---though simplified and imperfect---lays a foundation for richer and more complex descriptions in the future.
 For instance, networks with richer parameterizations could capture how intuitive theories differ across individuals, opening up the possibility of fine-tuning predictions and perhaps even crafting tailored educational interventions for specific individuals or groups.
@@
 
-Though these studies were conducted before the onset of the COVID-19 pandemic and focused on childhood diseases, many similar concerns are likely to animate hesitancy toward COVID-19 vaccines, and certain insights might be readily applied to addressing them.
-For one, in the spirit of Horne et al.’s [-@horne.etal2015] disease risk intervention, we suspect that education focused on how severely ill many people become and the prevalence of long-term health problems following even mild cases of COVID-19 might encourage people to accept coronavirus vaccines.
+## Implications for and insights from the COVID-19 pandemic
 
-On the other hand, the pandemic has presented its own unique issues.
-MRNA vaccines like those from Pfizer-BioNtech and Moderna represent highly novel technologiesdeveloped at a pace far faster than previously imagined possible.
-The unprecedented nature of these vaccines could engender hesitancy even among people who are otherwise comfortable with vaccinations.
+Though these studies were conducted before the onset of the COVID-19 pandemic and focused on childhood diseases, many similar concerns are likely to animate hesitancy toward COVID-19 vaccines, and our findings may provide some leverage into addressing the current surge of vaccine hesitancy.
 
-Beyond this, in many countries COVID-19 and vaccines against it have been politicized in a way that other public health concerns are not.
-Political affiliations often imply concrete beliefs about the world that could be incorporated into a model of an intuitive theory: for instance, the belief that the coronavirus pandemic is a “hoax.” However, these affiliations are also associated with social commitments, personal values, and other identity-constituting beliefs that may be more challenging to  capture in an intuitive theory as we have conceived of it here [@vanleeuwen2014].
-Relatedly, the coronavirus pandemic has raised public awareness of many social issues that could also play an important role in people's intuitive theories of vaccination more broadly.
-The uneven impacts of the pandemic have laid bare inequities within the American healthcare system, and prompted a greater awareness of and reckoning with a history of racism and abuses by the medical community.
-Understanding of these issues, which might differ across members of majority and minoritized communities, is well worth exploration in future studies.
-At the same time, the concept of "herd immunity" has likely never had greater public understanding and appreciation than now.
-This understanding is potentially a prime target for future interventions, though one whose impacts are likely to depend on other auxiliary ethical commitments, such as moral beliefs about individuals’ obligations to their wider communities.
+First, in the spirit of Horne et al.’s [-@horne.etal2015] disease risk intervention, we suspect that education focused on how severely ill many people become and the prevalence of long-term health problems following even mild cases of COVID-19 might encourage people to accept coronavirus vaccines.
+Indeed, controlled intervention studies have shown that messages focused on personal risk increase vaccination intentions [@motta.etal2021].
+However, as the pandemic has continued, it has become clear that the severity of COVID-19 is highly variable across individuals and across variants of the virus, potentially rendering the formation, updating, and use of beliefs about severity much more nuanced in the case of COVID-19 than in the case of diseases like measles.
+
+Our findings also suggest that beliefs about vaccine efficacy are central to determining vaccination intentions.
+In the case of mumps, measles, and rubella, strong vaccines and robust vaccination campaigns have led to the near eradication of these diseases in the U.S.
+and other developed nations.
+Correspondingly, we observed most participants in our studies believed quite strongly that these vaccines are effective in preventing infection.
+In contrast, the high prevalence of COVID-19 makes the risk of infection substantial even for the vaccinated, although these vaccines remain highly effective at preventing severe illness and death.
+The rising prevalence of breakthrough infections and the need for boosters relatively soon after initial doses are likely to lead people to doubt the effectiveness of vaccines---but we see promise in educational interventions that clarify the many ways in which a vaccine can be “effective” (e.g., by preventing infection vs.
+by preventing severe illness, preventing death, or lowering transmissibility), or explain the need for booster shots (e.g., addressing the misconception that the need for a booster shot indicates a problem with the vaccine).
+
+The coronavirus pandemic has also presented its own unique challenges.
+In the U.S.
+and abroad, COVID-19 vaccines and mitigation measures have become deeply politicized, which may complicate the role of intuitive theories in people’s vaccination decisions.
+Political affiliations often imply concrete beliefs about the world that could be incorporated into a model of an intuitive theory: for instance, that COVID-19 is "like the flu" or that infection can be treated with off-label pharmaceuticals.
+Still, these affiliations are also associated with social commitments, personal values, and other identity-constituting “beliefs” that may be more challenging to capture in an intuitive theory as we have conceived of it here [@vanleeuwen2014].
+
+In concert with its politicization, the pandemic has fueled a flurry of novel conspiracy theories.
+Through exposure to misinformation, not-insignificant numbers of people have come to believe that COVID-19 is caused by 5G telecommunications, that the virus was developed in a lab to be used as a bio-weapon, or even that the virus is not real at all, and instead is a "hoax" perpetrated by a globalist elite.
+As is the case with attempts to debunk the misconception that childhood vaccines cause autism, directly addressing these false conspiracy theories could prove to be extremely difficult.
+More promisingly, general education about COVID-19 vaccines may help to address these misconceptions indirectly.
+Our findings demonstrate that general beliefs, such as skeptical beliefs about the medical community, are revised in light of evidence concerning specific diseases or vaccines.
+
+Looking forward, living through the COVID-19 pandemic is likely to have deepened the public’s understanding of infectious diseases and public health.
+For example, the concept of “herd immunity” has likely never had greater public understanding and appreciation than now.
+This understanding seems like a prime target for future interventions aimed at increasing the uptake of vaccines for both COVID-19 and other diseases---although its impacts are likely to depend on other auxiliary ethical commitments, such as moral beliefs about individuals’ obligations to their wider communities.
+
+In addition, the COVID-19 pandemic has raised public awareness of how social group membership modulates individuals’ experiences of the world---and, by extension, their intuitive theories of how the world works.
+In particular, the uneven impacts of the pandemic have laid bare inequities within the American healthcare system, prompted a greater awareness of and reckoning with a history of racism and abuses by the medical community.
+People from different social groups---for example, White vs.
+Black Americans---are likely to have different first-hand experiences with doctors, are exposed to different second-hand accounts of interactions with the healthcare system, and have different levels of awareness of relevant historical events (e.g., the Tuskegee Syphilis Study) For these reasons, their intuitive theories of vaccination and the medical establishment more broadly may differ in important ways.
+The interconnections among social group membership, personal experience, intuitive theories, and health outcomes are well worth further exploration in future studies.
+
+## Conclusions
 
@@
 Coherent networks of beliefs allow people to understand, predict, and navigate the world, but they can also sustain misconceptions and lead to suboptimal---even dangerous---decisions and behaviors.
-Deciding to opt out of getting vaccinated against diseases like measles or COVID-19 is not only dangerous for the individual, but a serious threat to public health.
+As the past two years have made abundantly clear, deciding to opt out of getting vaccinated against diseases like measles or COVID-19 is not only dangerous for the individual, but a serious threat to public health.
 We hope the studies presented here have shed light on how people might come to such decisions, why the misconceptions that support these decisions can be so hard to combat, and how to develop educational interventions that are persuasive and effective in encouraging and sustaining healthier behaviors.

### 2022-02-09 supplement/supplement-main.Rmd
edits ahead of preprint

--- 2021-09-01 supplement/supplement-main.Rmd
@@
 bibliography: references.bib
-csl: apa.csl
+csl: apa7.csl
 figsintext : yes
@@
 header-includes:
-  - \usepackage{float}
-  - \usepackage{setspace}\doublespacing
+ \usepackage{float}
 ---
@@
 
-# this is the favorite son (most likely)
 main_model <- hc(train, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1e3, restart=5)
@@
 
-$$ log\big(O(h|d)\big) = log\big(O(h)\big) + ln\Big(\frac{P(d|h=1)}{P(d|h=0)}\Big) $$
+$$ log\big(O(h|d)\big) = \ln\big(O(h)\big) + \ln\Big(\frac{P(d|h=1)}{P(d|h=0)}\Big) $$
 
@@
 
-We recruited `r s2_meta$n_recruited` people to participate in a two-day study via mTurk in April 2018.
-Two days later, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r s2_meta$n_recruited_post` participants returning (`r s2_meta$n_eligible` invited, retaining `r round(s2_meta$n_recruited_post/s2_meta$n_eligible*100, 1)`% of the Day 1 sample).
+We recruited `r s2_meta$n_recruited` people to participate in a two-part study via mTurk in April 2018.
+Two days later, participants who completed Phase 1 and passed attention checks were invited via email to participate in Phase 2 of the study, with `r s2_meta$n_recruited_post` participants returning (`r s2_meta$n_eligible` invited, retaining `r round(s2_meta$n_recruited_post/s2_meta$n_eligible*100, 1)`% of the Phase 1 sample).
 Participants were paid \$1.35 for their participation in each phase of the study.
-`r s2_meta$n_failed_post` participants (`r round( (s2_meta$n_failed_post/s2_meta$n_recruited_post)*100, 1)`%) failed at least one attention check on Day 2 and were excluded from further analysis.
+`r s2_meta$n_failed_post` participants (`r round( (s2_meta$n_failed_post/s2_meta$n_recruited_post)*100, 1)`%) failed at least one attention check in Phase 2 and were excluded from further analysis.
 We also excluded from analyses `r s2_meta$n_duplicate` additional participants who accessed the second survey more than once.
@@
 
-Procedures for part 1 of Study 2 were nearly identical to Study 1, save for the use of four rather than two attention check questions, and the removal of debriefing statements at the end of the survey.
-On Day 2 (approximately two days later), participants completed a study that was designed to be very similar to Horne, Powell, et al.’s [-@horne.etal2015] original study.
-Participants were randomly assigned to either the disease risk condition or the no-intervention condition, with the constraint that the distributions of participants’ Day 1 _vaccine intentions_ should be similar across the two conditions; we accomplished this by stratifying participants into groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
+Procedures for Phase 1 of Study 2 were nearly identical to Study 1, save for the use of four rather than two attention check questions, and the removal of debriefing statements at the end of the survey.
+In Phase 2 (approximately two days later), participants completed a study that was designed to be very similar to Horne, Powell, et al.’s [-@horne.etal2015] original study.
+Participants were randomly assigned to either the disease risk condition or the no-intervention condition, with the constraint that the distributions of participants’ Phase 1 _vaccine intentions_ should be similar across the two conditions; we accomplished this by stratifying participants into groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
 
@@
 
-After reading this intervention, participants completed the same 14 belief scales that they had completed on Day 1.
+After reading this intervention, participants completed the same 14 belief scales that they had completed in Phase 1.
 Finally, participants were asked about their own vaccination behavior, including whether they had received a flu shot this season, and whether they planned to get a flu shot next season.
@@
 
-We recruited `r s3_meta$n_recruited` people to participate in a two-day study via mTurk in April (Experiment 3A) and June (Experiment 3B) of 2019.
-One day after their initial participation, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r s3_meta$n_recruited_post` participants returning (`r s3_meta$n_eligible` invited, retaining `r round(s3_meta$n_recruited_post/s3_meta$n_eligible*100,1)`% of the Day 1 sample).
-Participants were paid \$1.35 for their participation in each phase of the study and were allowed to participate in part 2 up to two days after their initial participation in part 1.
-`r s3_meta$n_failed_post` participants (`r round( (s3_meta$n_failed_post/s3_meta$n_recruited_post)*100,1)`%) failed at least one attention check on Day 2 and were excluded from further analysis.
+We recruited `r s3_meta$n_recruited` people to participate in a two-part study via mTurk in April (Experiment 3A) and June (Experiment 3B) of 2019.
+One day after their initial participation, participants who completed Phase 1 and passed attention checks were invited via email to participate in Phase 2 of the study, with `r s3_meta$n_recruited_post` participants returning (`r s3_meta$n_eligible` invited, retaining `r round(s3_meta$n_recruited_post/s3_meta$n_eligible*100,1)`% of the Phase 1 sample).
+Participants were paid \$1.35 for their participation in each phase of the study and were allowed to participate in Phase 2 up to two days after their initial participation in Phase 1.
+`r s3_meta$n_failed_post` participants (`r round( (s3_meta$n_failed_post/s3_meta$n_recruited_post)*100,1)`%) failed at least one attention check in Phase 2 and were excluded from further analysis.
 This left a final sample of `r s3_meta$n_complete` participants.
@@
 
-Procedures for studies 3a and 3b closely followed those of Study 2, but these studies tested the effects of a novel intervention aimed at dispelling concerns about toxic additives in vaccines.
+Procedures for Studies 3a and 3b closely followed those of Study 2, but these studies tested the effects of a novel intervention aimed at dispelling concerns about toxic additives in vaccines.
 Full text of this intervention is available in Appendix C of these supplementary materials.
@@
 
-Due to the similarity of their designs, we combined data from studies 3a and 3b for our primary analysis.
+Due to the similarity of their designs, we combined data from Studies 3a and 3b for our primary analysis.
 However, for full transparency we first describe analyses for these studies individually.
-As in Experiment 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the Vaccine Ingredients intervention on participants’ _Vaccination Intentions_ scores.
+As in Study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the Vaccine Ingredients intervention on participants’ _Vaccination Intentions_ scores.
 The Vaccine Ingredients intervention improved participant’s vaccination intention scores relative to a no-intervention control condition.
-Tables below show the results of these regression analyses for Experiment 3a, 3b, and the two studies combined.
+Tables below show the results of these regression analyses for Studies 3a, 3b, and the two studies combined.
 In each analysis, the coefficient representing the interaction between phase and condition is positive and credibly differs from zero, indicating that the Vaccine Ingredients intervention positively impacted vaccination intentions.
@@
 However, it is worth noting that reliable changes were also observed from pretest to posttest in the control conditions in both experiments (indicated by a credibly non-zero phase coefficient in each corresponding table).
-Observing this in Experiment 3a, we suspected that these attitudes were also being influenced by other factors during the course of the study.
-Approximately two months later we conducted Experiment 3b.
+Observing this in Study 3a, we suspected that these attitudes were also being influenced by other factors during the course of the study.
+Approximately two months later we conducted Study 3b.
 However, we found similar patterns of changes in this later study as well.
@@
 To simulate the impacts of this evidence, we supplied virtual evidence to the _vaccine toxicity_ node by adding a child node to the cognitive-model network with a CPT capturing this evidence ratio.
+
+After our initial preregistration for Study 3a and 3b, we did slightly modify our model-fitting approach for the data in Study 1.
+This means that the final model being compared differs slightly from the exact numerical predictions of the preregistration.
 

### 2022-02-09 install-packages.R

@@ -1,6 +1,8 @@
 ## this will install all required packages
 ## untested 6/22/21, 11:03 AM
 
+devtools::install_bioc("graph")
+
 package_list <- c(
   "tidyverse",
   "brms",

### 2022-02-15 paper/paper-papaja.Rmd
preprint

@@
 But intuitive theories can also contain and reinforce dangerous misconceptions.
-In this paper we take up the case of misconceptions about vaccine safety that discourage vaccination.
+In this paper, we take up the case of misconceptions about vaccine safety that discourage vaccination.
 These misconceptions constitute a major public health risk that predates the coronavirus pandemic but that has become all the more dire in recent years.
@@
 
-keywords          : "keywords"
-wordcount         : "X"
+keywords          : "Intuitive theories; Belief revision; Vaccine attitudes; Cognitive modeling"
+wordcount         : "9163"
 
@@
 Even before the coronavirus pandemic, misconceptions about vaccine safety drove public health crises around the world.
-Undervaccination resulted in outbreaks of measles affecting over 1000 children across the United States in 2019, and over 80,000 children across Europe in 2018 [@thornton2019].
+Undervaccination resulted in outbreaks of measles affecting over one thousand children across the United States in 2019, and over 80,000 children across Europe in 2018 [@thornton2019].
 Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct [e.g., @betsch.sachse2013; @horne.etal2015].
@@
 
-To people holding these beliefs, it could well seem unreasonable to vaccinate a 2-month-old baby against 5 or more diseases at once, as the CDC recommends.
+To people holding these beliefs, it could well seem unreasonable to vaccinate a 2-month-old baby against five or more diseases at once, as the CDC recommends.
 Moreover, if skeptics believe that the medical community is unduly influenced by pharmaceutical companies, they might doubt the validity of medical findings that appear to favor these companies’ interests.
-Altogether, these beliefs might sustain misconceptions about vaccine safety, even in the face of counter-evidence: CDC guidelines, clinical studies, even the advice of the family’s pediatrician could be interpreted not as evidence that vaccines are safer than the person thought, but instead as further proof of the widespread corruption in the medical community.
+Altogether, these beliefs might sustain misconceptions about vaccine safety, even in the face of counter-evidence: CDC guidelines, clinical studies, and even the advice of the family’s pediatrician could be interpreted not as evidence that vaccines are safer than the person thought, but instead as further proof of the widespread corruption in the medical community.
 
@@
 
-1) Where beliefs about two states of affairs, A and B, are related through a shared intuitive theory (e.g., A causes B), those beliefs will be systematically correlated across individuals (e.g., people who believe A will also tend to believe B);
+1) Where beliefs about two states of affairs, A and B, are related through a shared intuitive theory (e.g., A causes B), those beliefs will be systematically correlated across individuals (e.g.
+people who believe A will also tend to believe B);
 
-2) When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g., evidence for B will increase credence in A, and vice versa).
+2) When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g.
+evidence for B will increase credence in A, and vice versa).
 
-3) Thus, across individuals, the average change in one belief following evidence affecting another belief will be proportional to the correlation between those beliefs across individuals (evidence for B will increase credence in A in proportion to the correlation between beliefs A and B).
+3) Thus, across individuals, the average change in one belief following evidence affecting another belief will be proportional to the correlation between those beliefs across individuals (e.g.
+evidence for B will increase credence in A in proportion to the correlation between beliefs A and B).
 
@@
 Very few educational interventions have been shown to improve attitudes toward childhood vaccination.
-One of the few successful educational interventions in this domain was tested by Horne et al.
-[-@horne.etal2015], who found that emphasizing the dangers of preventable diseases like mumps, measles, and rubella improved participants’ attitudes toward vaccines.
+One of the few successful educational interventions in this domain was tested by Horne and colleagues [-@horne.etal2015], who found that emphasizing the dangers of preventable diseases like mumps, measles, and rubella improved participants’ attitudes toward vaccines.
 Their intervention included descriptions of the symptoms of mumps, measles, and rubella; vivid photos of children suffering from these diseases; and a brief story from the perspective of a parent whose child was hospitalized with measles (see SI).
@@
 
-In Study 2, we used the belief network established in Study 1 to predict how Horne et al.’s [-@horne.etal2015] intervention would affect the beliefs in this network, including people’s intentions to vaccinate their children.
+In Study 2, we used the belief network established in Study 1 to predict how Horne and colleagues’ [-@horne.etal2015] intervention would affect the beliefs in this network, including people’s intentions to vaccinate their children.
 Participants completed the 14 belief scales from Study 1, then returned two days later to complete either the disease risk intervention or a no-intervention control, followed by the same 14 belief scales.
@@
 Procedures for Phase 1 of Study 2 were nearly identical to those of Study 1, but the debriefing statement was moved to the end of Phase 2.
-In Phase 2 (approximately two days later), participants completed a study very similar to Horne et al.’s (2015) original intervention study.
+In Phase 2 (approximately two days later), participants completed a study very similar to Horne and colleagues' (2015) original intervention study.
 Participants were randomly assigned to either the disease risk condition or a no-intervention control condition, with the constraint that the distributions of participants’ Phase 1 *vaccine intentions* scores should be similar across the two conditions; we accomplished this by stratifying participants into three groups based on their pretest vaccine intentions, and randomly assigning them to conditions in equal numbers within each group.
 
-Participants (*n* = `r results$s2$demo$n_complete` passed attention checks in total) in the intervention conditions were presented with a version of Horne et al.’s  “disease risk” intervention, modified to present subparts in a fixed (rather than randomized) order, with slight changes to wording to improve clarity, and with a final statement summarizing the take-home message of the intervention; see SI.
+Participants (*n* = `r results$s2$demo$n_complete` passed attention checks in total) in the intervention conditions were presented with a version of Horne and colleagues'  “disease risk” intervention, modified to present subparts in a fixed (rather than randomized) order, with slight changes to wording to improve clarity, and with a final statement summarizing the take-home message of the intervention; see SI.
 They then completed the same 14 belief scales and demographic questions that they had completed in Phase 1.
@@
 The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: $b$ = `r round(s2_reg$fixed[9,1],3)`, 95% CI: [`r round(s2_reg$fixed[9,3], 3)`, `r round(s2_reg$fixed[9,4], 3)`]).
-We consider this to be a full replication of Horne, Powell, et al.’s [-@horne.etal2015] results.
+We consider this to be a full replication of Horne and colleagues' [-@horne.etal2015] results.
 See Figure 3, panel A.
@@
 
-#### Modeling belief revision.
+#### Modeling belief revision
 
@@
 
-The intervention developed by Horne et al.
-[-@horne.etal2015] and employed in Study 2 is notable for being one of the few educational interventions shown to decrease vaccine hesitancy---but is disease severity the only (or most) effective target for educational interventions in this domain?
+The intervention developed by Horne and colleagues [-@horne.etal2015] and employed in Study 2 is notable for being one of the few educational interventions shown to decrease vaccine hesitancy---but is disease severity the only (or most) effective target for educational interventions in this domain?
 
@@
 
-First, in the spirit of Horne et al.’s [-@horne.etal2015] disease risk intervention, we suspect that education focused on how severely ill many people become and the prevalence of long-term health problems following even mild cases of COVID-19 might encourage people to accept coronavirus vaccines.
+First, in the spirit of Horne and colleagues’ [-@horne.etal2015] disease risk intervention, we suspect that education focused on how severely ill many people become and the prevalence of long-term health problems following even mild cases of COVID-19 might encourage people to accept coronavirus vaccines.
 Indeed, controlled intervention studies have shown that messages focused on personal risk increase vaccination intentions [@motta.etal2021].
@@
 
-The coronavirus pandemic has also presented its own unique challenges.
-In the U.S.
-and abroad, COVID-19 vaccines and mitigation measures have become deeply politicized, which may complicate the role of intuitive theories in people’s vaccination decisions.
-Political affiliations often imply concrete beliefs about the world that could be incorporated into a model of an intuitive theory: for instance, that COVID-19 is "like the flu" or that infection can be treated with off-label pharmaceuticals.
-Still, these affiliations are also associated with social commitments, personal values, and other identity-constituting “beliefs” that may be more challenging to capture in an intuitive theory as we have conceived of it here [@vanleeuwen2014].
-
-In concert with its politicization, the pandemic has fueled a flurry of novel conspiracy theories.
-Through exposure to misinformation, not-insignificant numbers of people have come to believe that COVID-19 is caused by 5G telecommunications, that the virus was developed in a lab to be used as a bio-weapon, or even that the virus is not real at all, and instead is a "hoax" perpetrated by a globalist elite.
-As is the case with attempts to debunk the misconception that childhood vaccines cause autism, directly addressing these false conspiracy theories could prove to be extremely difficult.
-More promisingly, general education about COVID-19 vaccines may help to address these misconceptions indirectly.
-Our findings demonstrate that general beliefs, such as skeptical beliefs about the medical community, are revised in light of evidence concerning specific diseases or vaccines.
-
 Looking forward, living through the COVID-19 pandemic is likely to have deepened the public’s understanding of infectious diseases and public health.
 For example, the concept of “herd immunity” has likely never had greater public understanding and appreciation than now.
-This understanding seems like a prime target for future interventions aimed at increasing the uptake of vaccines for both COVID-19 and other diseases---although its impacts are likely to depend on other auxiliary ethical commitments, such as moral beliefs about individuals’ obligations to their wider communities.
+This understanding seems like a prime target for future interventions aimed at increasing the uptake of vaccines for both COVID and other diseases—although its impacts are likely to depend on other auxiliary ethical commitments, such as moral beliefs about individuals’ obligations to their wider communities.
 
-In addition, the COVID-19 pandemic has raised public awareness of how social group membership modulates individuals’ experiences of the world---and, by extension, their intuitive theories of how the world works.
-In particular, the uneven impacts of the pandemic have laid bare inequities within the American healthcare system, prompted a greater awareness of and reckoning with a history of racism and abuses by the medical community.
-People from different social groups---for example, White vs.
-Black Americans---are likely to have different first-hand experiences with doctors, are exposed to different second-hand accounts of interactions with the healthcare system, and have different levels of awareness of relevant historical events (e.g., the Tuskegee Syphilis Study) For these reasons, their intuitive theories of vaccination and the medical establishment more broadly may differ in important ways.
-The interconnections among social group membership, personal experience, intuitive theories, and health outcomes are well worth further exploration in future studies.
+Unfortunately, the scale and spread of dis- and misinformation about COVID-19 has far eclipsed the spread of fringe ideas about MMR vaccines: millions of people have come to believe that COVID-19 is caused by 5G telecommunications, that the virus was developed in a lab to be used as a bio-weapon, or even that the virus is not real at all, and instead is a "hoax" perpetrated by a globalist elite.
+As is the case with attempts to debunk the misconception that childhood vaccines cause autism, directly addressing these false conspiracy theories could prove to be extremely difficult.
+However, there is some cause for hope that clear education about COVID-19 vaccines may help to address these misconceptions indirectly.
+Our findings demonstrate that revising beliefs about  specific diseases or vaccines can have “upstream” consequences for more abstract beliefs, such as naturalism and medical skepticism—hinting at a novel approach for addressing the kinds of fringe theories that have emerged during the pandemic.
+
+Finally, like all pandemics, the COVID-19 pandemic is inescapably social.
+For one, in the U.S.
+and abroad, COVID-19 vaccines and mitigation measures have become deeply politicized.
+According to Gallup polling in the U.S., COVID-19 vaccination rates have at times been nearly twice as high among Democrats as among Republicans [@gallup2021].
+Messages from political elites often imply concrete beliefs about the world that could be incorporated into a model of an intuitive theory: for instance, that COVID-19 is "like the flu" or that infection can be treated with off-label pharmaceuticals—or, conversely, that COVID-19 vaccines are safe and effective.
+Still, these affiliations are also associated with social commitments and personal values that may behave differently than the beliefs examined here.
+Whereas beliefs about “matters of fact” might be driven by an underlying intuitive theory and thereby sensitive to evidence, these sorts of identity-constituting “beliefs” may operate by different principles [@vanleeuwen2014] or may be entirely socially-motivated [@kahan2016].
+
+More broadly, people from different social groups have different experiences and knowledge that are likely to shape their intuitive theories of vaccination and the medical establishment in important ways—something that the approach we have taken in the current studies does not yet account for.
+For example, White vs.
+Black Americans are likely to have different experiences with medical racism.
+Future work should explore how differences in people’s wider intuitive theories might explain vaccination behaviors, as well as how a more nuanced understanding of these theories might support messages tailored to different individuals and communities.
 

### 2022-02-15 install-packages.R

@@ -20,4 +20,4 @@ package_list <- c(
 
 install.packages(package_list)
 
-devtools::install_github("thomasp85/patchwork")
+devtools::install_github("thomasp85/patchwork", "crsh/papaja")

### 2022-02-15 paper/paper-papaja.Rmd
references fixed

@@
 note: |
-  This manuscript has not yet been peer-reviewed.
+  This manuscript has not yet been peer-reviewed (2/15/2022).
 
@@
 keywords          : "Intuitive theories; Belief revision; Vaccine attitudes; Cognitive modeling"
-wordcount         : "9163"
+wordcount         : "9161"
 

### 2022-06-06 paper/paper-papaja.Rmd
may-june revisions

@@
 authornote: |
-  All data, and analysis code for this project are available at https://osf.io/sdfpj/. Preregistration information for Studies 3a and 3b is available at https://osf.io/csnez/registrations.
+  All data, and analysis code for this project are available at https://osf.io/sdfpj/.
+Preregistration information for Studies 3a and 3b is available at https://osf.io/csnez/registrations.
+Earlier modeling and analyses of data from Study 1 were presented at the 40th Annual Conference of the Cognitive Science Society.
+A six-page paper also appeared in the proceedings [@powell.etal2018].
 
@@
 Undervaccination resulted in outbreaks of measles affecting over one thousand children across the United States in 2019, and over 80,000 children across Europe in 2018 [@thornton2019].
-Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct [e.g., @betsch.sachse2013; @horne.etal2015].
+Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct [e.g., @betsch.sachse2013; @horne.etal2015; @lewandowsky.etal2012].
 Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @dube.etal2015; @horne.etal2015; @vannice.etal2011; @wallace.etal2006].
@@
 @lewandowsky.etal2012].
-Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence [e.g., @gershman2019; @lewandowsky.etal2012; @jern.etal2014].
+Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence [e.g., @gershman2019; @lewandowsky.etal2012; @jern.etal2014; @cook.lewandowsky2016].
+
 Consider some of the beliefs people who are skeptical of childhood vaccination expressed when we asked them to explain their views in an open-ended qualitative survey (conducted pre-pandemic; _n_ = 16).
@@
 
-We argue that correcting misconceptions requires presenting evidence in a way that is sensitive to and persuasive within the broader conceptual context in which those misconceptions reside [see @gershman2019; @weisman.markman2017].
+We argue that correcting misconceptions requires presenting evidence in a way that is sensitive to and persuasive within the broader conceptual context in which those misconceptions reside [see @gershman2019; @weisman.markman2017; @cook.lewandowsky2016].
 Understanding the revision of any one specific belief (e.g., a misconception like *vaccines are dangerous*) demands a holistic understanding of the wider set of interrelated beliefs that make up people's intuitive theories.
@@
 Structure learning algorithms [see @scutari.denis2021] provide a means for searching through the (super-exponentially large) possible space of Bayesian networks to find the structure most likely to have generated some observed data.
-These approaches allow us to scale the Bayesian network modeling framework beyond the smaller models characteristic of early computational work on intuitive theories [e.g., @griffiths.tenenbaum2005].
+These approaches allow us to scale the Bayesian network modeling framework beyond the smaller models characteristic of early computational work on intuitive theories [e.g., @cook.lewandowsky2016; @griffiths.tenenbaum2005; @jern.etal2012].
 
@@
 In addition to 1) _vaccination intentions_ (e.g.
-“If I had a young baby I would have him or her vaccinated.”), these included a variety of beliefs about vaccines, including beliefs about 2) _vaccine danger_, the overall danger of vaccines (e.g., “Many children have severe adverse reactions to the MMR vaccine”); 3) _toxic additives in vaccines_ (e.g., “Exposure to certain additives in vaccines can cause major health problems.”); and 4) _vaccine effectiveness_, how effective vaccines are in preventing disease (e.g., “Your chances of getting a disease after being vaccinated against it are incredibly low”); as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about 5) _disease rarity _(e.g., “Diseases like measles and whooping cough are so rare that there is no real need to worry about them”) and 6) _disease severity_ (e.g., “Diseases like measles and whooping cough are extremely dangerous for young children”).
+“If I had a young baby I would have him or her vaccinated.”), these included a variety of beliefs about vaccines, including beliefs about 2) _vaccine danger_, the overall danger of vaccines (e.g., “Many children have severe adverse reactions to the MMR vaccine”); 3) _toxic additives in vaccines_ (e.g., “Exposure to certain additives in vaccines can cause major health problems.”); and 4) _vaccine effectiveness_, how effective vaccines are in preventing disease (e.g., “Your chances of getting a disease after being vaccinated against it are incredibly low”); as well as a variety of specific claims about childhood diseases like measles, mumps, and rubella, including beliefs about 5) _disease rarity_ (e.g., “Diseases like measles and whooping cough are so rare that there is no real need to worry about them”) and 6) _disease severity_ (e.g., “Diseases like measles and whooping cough are extremely dangerous for young children”).
 Beyond this, we theorized that participants’ understanding of the infant immune system might be relevant, including beliefs that 7) the infant immune system is weak (_IIS: weakness_; e.g., “Babies’ immune systems are weak”); 8) the infant immune system is limited in its capacity and can be easily overwhelmed (_IIS: limited capacity_; e.g., “Babies’ immune systems are severely limited in how much they can cope with at one time.”); and 9) vaccines strain the infant immune system (_IIS: vaccines strain_; e.g., “Vaccines strain the immune system much like the actual disease”).
@@
 
-Each scale measured agreement with 4-6 statements, including at least one reverse-coded item, and was highly reliable (observed reliability, Study 1: all Cronbach’s $\alpha \geq .73$ .73).
+Each scale measured agreement with 4-6 statements, including at least one reverse-coded item, and was highly reliable (observed reliability, Study 1: all Cronbach’s $\alpha \geq .73$).
 We developed 13 of these scales, and included one preexisting scale (the “holistic balance” subscale from [@mcfadden.etal2010].
@@
 
-$$P(y) = \Big(1-(1-w_0)\prod_i(1-w_i)^{x_i}\Big)\prod_j(1-w_j)^{x_j}$$
+$$P(y=1) = \Big(1-(1-w_0)\prod_i(1-w_i)^{x_i}\Big)\prod_j(1-w_j)^{x_j}$$
 
@@
 
-Having transformed participants’ scores on each belief scale to fall between 0 and 1, we estimated the parameters of the model as a beta regression using maximum likelihood methods (see SI).
+A cognitive model composed of these types of relations is capable of capturing a causal system of non-interactive generative and preventive causes.
+But it bears noting that this simplification comes with limitations.
+For instance, returning to the example network in Figure 1d, this parameterization would not permit capturing the relationships between dryness, lightning, and fire.
+Dryness is an enabling condition that both increases the probability of fire but also increases the probability that lightning would cause a fire.
+So the influences of these variables are not independent and would need a more complex parameterization to be properly represented.
+
+Finally, having transformed participants’ scores on each belief scale to fall between 0 and 1, we estimated the parameters of this model as a Beta regression using maximum likelihood methods (see SI for details).
 
@@
 For instance, we stipulated that vaccine intentions---our outcome of interest---would be a “child node,” with edges only flowing inwards and not outwards (since one’s intention to vaccinate cannot “generate” the facts about vaccinations safety, effectiveness, etc).
-This generative model principle instills a common core assumption in research on intuitive theories and causal explanatory reasoning[e.g.
+This generative model principle instills a common core assumption in research on intuitive theories and causal explanatory reasoning [e.g.
 @gerstenberg.etal2021; @gopnik.etal2004; @cheng1997].
@@
 To avoid overfitting, we used an 80% split of the data (*n* = 904) for training, and reserved the remaining 20% for evaluating model performance.
+We compared performance of different structure learning algorithms using k-fold cross validation within the training split.
+Based on these results, we chose to apply a hill-climbing learning algorithm using our generative model constraints (see SI for details).
 Applying these techniques resulted in an estimate of the network shown in Figure 1.
 
-```{r fig1-maingraph, fig.align='center', out.width="90%", fig.cap="Bayesian network model resulting from hill-climbing algorithm with our generative-model constraints applied to data in Study 1 training split (n = 904).
+```{r fig1-maingraph, fig.align='center', out.width="90%", fig.cap="Bayesian network cognitive model resulting from application of hill-climbing algorithm with our generative-model constraints applied to data in Study 1 training split (n = 904).
 The network has 29 edges connecting these 14 variables.
@@
 
-We evaluated the model’s performance by testing its accuracy in predicting responses in the 20% testing split (*n* = 226).
+We evaluated the resulting cognitive model’s performance by testing its accuracy in predicting responses in the 20% testing split (*n* = 226).
 We generated predictions for held-out participants’ responses for each variable by conditioning the network on the remaining 13 observed variables.
@@
 
-```{r fig2-validation, fig.align='center', out.width="100%", fig.cap="Observed responses and model predictions for each belief among participants in the Study 1 testing split.
+Our goal in developing this cognitive model was to create a psychologically plausible and intelligible model of the intuitive theory surrounding vaccination decisions.
+However, it is also reasonable to ask whether other less-constrained models might be more predictive.
+To address this, we compared the Bayesian network model’s predictions to a suite of 14 naive “maximal” regression models, each using values on all 13 other belief scales as predictors for each belief.
+Our simpler model provided equally strong predictions (see SI).
+And, as will be evidenced in later studies, our model can also be used to generate accurate predictions about how beliefs will change following evidence.
+
+```{r fig2-validation, fig.align='center', out.width="100%", fig.cap="Observed responses and cognitive model predictions for each belief among participants in the Study 1 testing split.
 Correlations between observed and predicted values ranged from .380 to .898 across the different belief scales.
@@
 
-What does this model reveal about the intuitive theory underlying vaccination decisions?
+What does this cognitive model reveal about the intuitive theory underlying vaccination decisions?
 
@@
 This is the case for two edges (Naturalism $\rightarrow$  Holistic Balance and Medical Skepticism $\rightarrow$ Parental Expertise; see SI for details).
-In both cases, we do not feel it is intuitive which direction the edge should flow in, nor even that it should be directed at all; we might even speculate there is an additional unmeasured variable that connects these beliefs and that would best account for their association.
+In both cases, we do not feel it is intuitive which direction the edge should flow in, nor even that it should be directed at all.
+Such a counterintuitive result might be taken as indicating a limitation of Bayesian network models, which are composed solely of directed, acyclic relationships.
+Prior work has successfully modeled coherent belief revision by leveraging models with undirected or bidirected relations [e.g.
+@spellman.etal1993].
+Alternatively, we might imagine there is an additional unmeasured variable that connects these beliefs that could more intelligibly account for their association within the context of a directed network.
+For instance, a more abstract epistemic belief might influence both medical skepticism and parental expertise beliefs.
+To speculate, such an abstract belief might be in one's own expertise or in how we come to have knowledge (e.g.
+through direct experience versus science).
 
@@
 In this model, the unique effect of the intervention on vaccination intention scores is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants).
-The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: $b$ = `r round(s2_reg$fixed[9,1],3)`, 95% CI: [`r round(s2_reg$fixed[9,3], 3)`, `r round(s2_reg$fixed[9,4], 3)`]).
+The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: $b$ = `r round(s2_reg$fixed[9,1],3)`, 95% Credible Interval (CI): [`r round(s2_reg$fixed[9,3], 3)`, `r round(s2_reg$fixed[9,4], 3)`]).
 We consider this to be a full replication of Horne and colleagues' [-@horne.etal2015] results.
@@
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
-Right, mean observed and model predicted change scores for the disease risk intervention condition.
+Right, mean observed and predicted change scores from the cognitive model for the disease risk intervention condition.
 In both plots, error bars represent 95\\% confidence intervals.
@@
 Where *x* was a binary variable representing the presence (1) or absence (0) of evidence at posttest, and participants’ prior and posterior (pretest and posttest) credences were transformed into log odds.
-This allowed us to estimate the log evidence ratio implied by participants’ reactions to the intervention.
-Then, we constructed a CPT consistent with that evidence ratio.
+The variables $ER_0$ and $ER_1$ represent measures of the evidence seen by participants in the control and intervention conditions.
+These are defined as:
 
-Using this augmented model, we are able to “condition” the model on this evidence node, and thereby predict how observing evidence will affect all of the beliefs in the network.
+$$ER_i = \ln\frac{(P(d_i|h=1))}{(P(d_i|h=0))}$$
+
+In equation X, $ER_0$ represents whatever background "evidence" participants would see between phases outside  the experimental context, that would be shared by participants in both conditions.
+$ER_1$ represents the evidence provided by the intervention information, which is assumed to be independent from $ER_0$.
+These log evidence ratios were both estimated via regression.
+Then, we constructed a conditional probability table consistent with $ER_1$ and augmented the cognitive model with this evidence node (see SI for details).
+
+Using this augmented model, we are able to “condition” our cognitive model on this evidence node, and thereby predict how observing evidence will affect all of the beliefs in the network.
 As shown in Figure 3, panel B, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (*r* = `r results$s2$modcorr`).
 
-Given that our cognitive model is parameterized via noisy-logical functions, it should be noted that the marginal predicted influence of each belief is closely related to its first-order correlation with disease severity.
-This is in keeping with the qualitative features of intuitive theories we laid out in the introduction, and we should expect this to hold true (on average) for any plausible model of an intuitive theory.
+Given that our cognitive model is parameterized via noisy-logical functions wherein each parent independently influences each child node, it should be noted that the marginal predicted influence of each belief is closely related to its first-order correlation with disease severity.
+This is in keeping with the qualitative features of intuitive theories we laid out in the introduction, and we should often expect this to hold true on average for any plausible model of an intuitive theory.
 However, future models with more complex or nuanced parameterizations could potentially make additional predictions not evident from first-order correlations, such as individualized predictions for how individuals or groups would respond to evidence.
@@
 One advantage of having developed a formal, computational representation of a network of beliefs supporting vaccination decisions is that it can guide our search for effective interventions, allowing us to compare how interventions targeting each of these other beliefs might potentially change people’s vaccination intentions (see Figure 4).
-Countering myths about toxic additives is one approach the model developed in Study 1 predicts should be effective.
+Countering myths about toxic additives is one approach the cognitive model developed in Study 1 predicts should be effective.
 
-```{r fig4-predimpacts, fig.align='center',  out.width="50%", fig.cap="Predicted change in vaccination intentions following an equivalent hypothetical change in each of the other 13 beliefs."}
+```{r fig4-predimpacts, fig.align='center',  out.width="50%", fig.cap="Predicted change in vaccination intentions based on cognitive model following an equivalent hypothetical change in each of the other 13 beliefs."}
 knitr::include_graphics("../local/pred_change_plt.png")
@@
 These studies followed similar design procedures as Study 2, with Phase 2 conducted 1-2 days after Phase 1.
-In both Study 3a (April 2019) and Study 3b (May 2019; combined final *n* = `r results$s3$demo$n_complete`) the vaccine ingredients intervention was compared against no-intervention control.
+In both Study 3a (April 2019) and Study 3b (June 2019; combined final *n* = `r results$s3$demo$n_complete`) the vaccine ingredients intervention was compared against no-intervention control.
 Unlike Study 2, we did not stratify participants before random assignment to conditions.
@@
 
-We recruited `r results$s3$demo$n_recruited` people to participate in a two-day study via mTurk in April (Experiment 3A) and June (Experiment 3B) of 2019.
+We recruited `r results$s3$demo$n_recruited` people to participate in a two-day study via mTurk in April (Experiment 3a) and June (Experiment 3b) of 2019.
 One day after their initial participation, participants who completed part 1 and passed attention checks were invited via email to participate in Day 2 of the study, with `r results$s3$demo$n_recruited_post` participants returning (`r results$s3$demo$n_eligible` invited, retaining `r round(results$s3$demo$n_recruited_post/results$s3$demo$n_eligible*100,1)`% of the Day 1 sample).
@@
 As in Study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine ingredients intervention on participants’ *vaccination intentions* scores.
-The vaccine ingredients intervention improved participant’s vaccination intention scores relative to the control conditions (interaction effect: $b$ = `r round(s3_reg$fixed[9,1],3)`, 95% CI: [`r round(s3_reg$fixed[9,3], 3)`, `r round(s3_reg$fixed[9,4], 3)`]); see Figure 5, panel A.
+The vaccine ingredients intervention improved participants' vaccination intention scores relative to the control conditions (interaction effect: $b$ = `r round(s3_reg$fixed[9,1],3)`, 95% CI: [`r round(s3_reg$fixed[9,3], 3)`, `r round(s3_reg$fixed[9,4], 3)`]); see Figure 5, panel A.
 It is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: $b$ = `r round(s3_reg$fixed[7,1],3)`, 95% CI: [`r round(s3_reg$fixed[7,3], 3)`, `r round(s3_reg$fixed[7,4], 3)`]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
@@
 
-To model the effect of the vaccine ingredients intervention, we followed the same procedure as in Study 2, but this time augmented the model with a node representing the vaccine ingredients intervention as a child of the vaccine toxins belief node (for details, see SI).
-This allowed us to predict how other beliefs in the network would change in light of the observed changes participant’s beliefs about whether vaccines contain dangerous toxins; see Figure 5, panel B.
+To model the effect of the vaccine ingredients intervention, we followed the same procedure as in Study 2, but this time augmented the cognitive model with a node representing the vaccine ingredients intervention as a child of the vaccine toxins belief node (for details, see SI).
+This allowed us to predict how other beliefs in the network would change in light of the observed changes in participant’s beliefs about whether vaccines contain dangerous toxins; see Figure 5, panel B.
 
@@
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
-Right, mean observed and model predicted change scores for the disease risk intervention condition.
+Right, mean observed and  predicted change scores from the cognitive model for the disease risk intervention condition.
 In both plots, changes were calculated after combining data from both studies and transforming responses to lie between 0 and 1 and error bars represent 95\\% confidence intervals."}
@@
 Left, mean difference scores comparing beliefs reported in August-September 2017 and May 2019 for the 14 belief scales, across participants who did and did not report exposure to news of the ongoing New York measles outbreak.
-Right, mean observed and model predicted change scores for those participants who did report exposure to this news.
+Right, mean observed and  predicted change scores from the cognitive model for those participants who did report exposure to this news.
 Belief changes were modeled assuming that news of the outbreak directly impacted participant's vaccine intentions, the most central of the 14 beliefs, in order to evaluate the overall coherence of these belief changes.
@@
 
-Were changes in participants' beliefs following exposure to news of the measles outbreak coherent with respect to the intuitive theory specified by the model developed in Study 1?
-Unlike in the intervention studies, where a specific belief was targeted by the intervention, it is likely that many beliefs were addressed by media coverage of these outbreaks.
-To assess whether these changes were coherent, we examined how they were related to the most central of the beliefs we measured, *vaccine intentions*, using our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in *vaccine intentions.* That is, we followed the same procedure as in previous studies, but here augmented the model with a node representing media exposure as a child of the *vaccine intentions* node.
+Were changes in participants' beliefs following exposure to news of the measles outbreak coherent with respect to the intuitive theory specified by the cognitive model developed in Study 1?
+Unlike in the intervention studies, where a specific belief was quite precisely targeted by the intervention, it is likely that many beliefs were addressed by media coverage of these outbreaks.
+Given that we cannot reasonably measure the exact information that participants were exposed to, it is not feasible to attempt to precisely model the impacts of this total evidence.
+However, we can leverage our model to assess whether the changes in their beliefs were *coherent*.
+
+Throughout our prior studies, we have focused primarily on *vaccine intentions* as the most crucial and proximal belief for determining vaccination decisions.
+So, we sought to examine whether the changes across all the measured beliefs were coherent with respect to the changes in vaccination intensions.
+Using our model, we generated predictions for how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in vaccine intentions.
+To accomplish this, we followed the same procedure as in previous studies, but here augmented the model with a node representing media exposure as a child of the *vaccine intentions* node.
 
@@
 For instance, networks with richer parameterizations could capture how intuitive theories differ across individuals, opening up the possibility of fine-tuning predictions and perhaps even crafting tailored educational interventions for specific individuals or groups.
+
+[talk about magnitude of the effects. tailoring could strengthen. timing also matters, in context of physician visit]
 
@@
 
+## Broader implications and applications
+
+[discuss broader implications / applications as requested]
+
 ## Conclusions

### 2022-06-06 supplement/supplement-main.Rmd
may-june revisions

@@
 
+# Theory of intuitive theories
+
+Quine argued that all of one’s beliefs are intertwined in a “web of belief” [@quine1951; @quine.ullian1978]---an apt metaphor for intuitive theories.
+Intuitive theories consist of relations between beliefs that specify how states of affairs causally, logically, or otherwise interconnect with one another.
+Specifically, we consider intuitive theories to be generative mental models that entail probabilistic dependencies among possible states of affairs.
+
+Given this definition, we argue that any pair of beliefs related by a intuitive theory can be expected to exhibit several qualitative features:
+
+1.
+When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g.
+evidence for B will increase credence in A, and vice versa).
+This is a clear and direct consequence of the laws of probability and Bayes' rule.
+2.
+Where beliefs about two states of affairs, A and B, are related through an intuitive theory (e.g., A causes B), those beliefs will be systematically correlated across individuals in proportion to the average conditional probabilities (e.g.
+people who believe A will also tend to believe B);
+
+In the case of beliefs about binary states of affairs, this can be seen through an application of the law of total probability and some algebra, which reveals a linear relationship between the two beliefs across individuals.
+To derive this result, we assume each individual i holds a specific degree of belief in x and y, $p_i(x)$ and $p_i(y)$.
+Moreover, these degrees of belief are determined by an intuitive theory: a generative mental model encoding a conditional dependency between the two, i.e.
+$p_i(y|x)$ and $p_i(y|\neg x)$.
+
+From the law of total probability, we can write:
+
+$p_i(y) = p_i(y|x)p_i(x) + p_i(y|\neg x)(1-p_i(x))$
+
+With some algebra, we can rearrange these terms:
+
+$p_i(y) = p_i(y|\neg x) + (p_i(y|x)p_i(x) - p_i(y|\neg x))p_i(x)$
+
+This equation has a familiar form $y  = \alpha + \beta x$.
+We know that a least-squares solution for $\beta$ will return $\frac{1}{n}\sum_i p_i(y|x)p_i(x) - p_i(y|\neg x) = \overline{p_i(y|x) - p_i(y|\neg x)}$, and that such an estimate for $\beta \propto corr(p_i(x),p_i(y))$.
+
+3.
+Thus we can often reasonably expect there will be some systematic relationship between the average change in each belief following evidence and the correlation among those beliefs across individuals.
+More specifically, if we assume that the changes in beliefs A following evidence are uncorrelated with the conditional probabilties connecting A and B in people's intuitive theories, then the average change in belief A and B following evidence affecting A will be proportional to the correlation of those beliefs across individuals.
+
+Again we consider this in the case of beliefs about binary states of affairs.
+We define $p_i(x)$ to be the prior probability of $x$ before observing some evidence, and $p_i(x|e)$ to be the posterior probability of $x$ after observing the evidence, $e$.
+
+We define the change in $p_i(x)$ as $\Delta p_i(x) = p_i(x|e) -p_i(x)$.
+
+We can write $\Delta p_i(y)$ in terms of $\Delta p_i(x)$.
+We assume that the evidence has a direct impact on the probability of $x$, but that the evidence only affects $p_i(y)$ through its impact on $p_i(x)$, i.e.
+$y \perp e |x$.
+This implies that $p_i(y|e) = p(y|x)p(x|e)$.
+
+First, we expand $\Delta p_i(y)$ via the law of total probability and rearrange terms
+$$
+\begin{align*}
+\Delta p_i(y)  &= p_i(y|e) - p_i(y)\\
+ &= p_i(y|x)p_i(x|e) + p_i(y|\neg x)(1-p_i(x|e)) - p_i(y|x)p_i(x) + p_i(y|\neg x)(1-p_i(x)) \\
+&= \big(p_i(x|e) - p_i(x)\big)\cdot \big(p_i(y|x) - p_i(y|\neg x)\big)
+\end{align*}
+$$
+Taking the average, we have
+$$
+\overline{\Delta p_i(y)} = \overline{p(y|e) - p(y)} = \frac{1}{n}\sum_i\big(p_i(x|e) - p_i(x)\big)\big(p_i(y|x) - p_i(y|\neg x)\big)
+$$
+From the definition of covariance we have
+$$
+cov(X,Y) = E(XY) - E(X)E(Y)
+$$
+If we assume that the change in belief in x following the evidence, $\Delta p_i(x)$ is uncorrelated with the conditional probabilities encoded in the intuitive theory $p_i(y|x)p_i(x) - p_i(y|\neg x)$ (i.e.
+covariance equals zero) and apply this definition, we can then rewrite the average change as
+$$
+\overline{\Delta p_i(y)} = \overline{p(y|e) - p(y)} = \frac{1}{n}\sum_ip_i(x|e) - p_i(x) \frac{1}{n}\sum_ip_i(y|x) - p_i(y|\neg x)
+$$
+And we have thus shown that $\overline{\Delta p_i(y)} \propto \overline{p_i(y|x)p_i(x) - p_i(y|\neg x)} \propto corr(p_i(x),p_i(y))$
+
+In practice we did not measure probabilistic credences directly, but rather asked participants to report on a agree/disagree scale.
+We assume these actual measurements are some monotonic function of these credences, $f(p_i(x))$.
+Allowing that $f$ could be non-linear, the proportionality conclusions are no longer guaranteed.
+
 # Modeling
@@
 We also estimate $w_0$, the “leak probability” which is assumed to be generative, and $k$, a measure of dispersion in the responses $y$.
+
+One way to satisfy the assumption that changes in some belief following evidence are uncorrelated with the conditional probabilties connecting that belief to others in people's intuitive theories is to assume that all people hold the same conditional probabilities in their intuitive theory.
+This is essentially the assumption that we are making by assuming a single network structure where parents are parameterized as independent generative and preventive forces on their children.
+Thus, the resulting network we develop can be expected to make predictions in accord with point #3 above: the average predicted change in each belief following evidence directly impacting another belief will be proportional to the correlation between those beliefs across people.
 
@@
 Ultimately, this model should be understood as offering a plausible, but not definitive, account for a cognitive model connecting these different beliefs.
-
-What does the resulting model reveal about the intuitive theory undergirding vaccination decisions?
-
-The three nodes with direct connections to _vaccine intentions_ are beliefs about _vaccine effectiveness_, _vaccine danger_, and the severity of childhood diseases (_disease severity_)--concrete beliefs that are, at face value, especially closely related to vaccination decisions.
-The directionality of these edges is informed by the constraints we applied via the generative model principle, but the identification of these three factors as the most proximal to vaccine intentions is a product of the structure learning approach.
-This gives us some confidence that the model is capturing important relationships.
-
-Other parts of the model shed new light on the role of lay theories in vaccine decisions.
-For example, _naturalism_—the general view that natural things are better than artificial things—appears to be strongly related to _medical skepticism_ and _parental expertise_; all three of these abstract beliefs are related to concrete beliefs that, in turn, feed into participants’ vaccination intentions.
-This hierarchical structure is at least partly a product of our constraints that sorted these beliefs into “tiers” of abstractness.
-However, the fact that a model with these constraints provides similarly strong fits as those without these constraints demonstrates that this hierarchical structure is plausible.
-
-Finally, this model structure also helps explain some initially surprising findings.
-For example, before collecting these data we speculated that dispelling the misconceptions about the capacity of the infant immune system could promote positive attitudes toward vaccination.
-We were disappointed to observe the weak first-order correlation between this belief and vaccine intentions in our behavioral data (r = -.097 in our training split).
-The model sheds light on this surprising (lack of) relationship: Although the belief that the infant immune system is limited in capacity is positively related to the belief that vaccines strain the immune system—discouraging vaccination, as we had assumed—it also seems to promote the belief that childhood diseases have severe consequences for young children (_disease severity_), which might, in turn, encourage vaccination.
-These countervailing forces—which, on average, seem to have cancelled each other out in this sample—dissuaded us from our plans to develop an intervention aimed at dispelling misconceptions about limited capacity in order to encourage childhood vaccination.
 
@@
 ```{r fig7-s2_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiment 2.
-Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in gray.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
+Belief scales are ordered by model-predicted changes based on the observed effect on disease severity.
+Our primary outcome of interest, vaccination intentions, is highlighted in gray.
 Right, mean observed and model predicted change scores for the disease risk intervention condition.
@@
 
-s2_scale_order <- s2_scored %>%
-  drop_na(scale) %>%
-  spread(phase, mean) %>%
-  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>%
-  mutate(diff = post-pre) %>%
+obs_pred <- make_pred_df(s2_mdf, base_model, "diseaseSevere")
+
+cor_val_s2 <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
+
+s2_scale_order <- obs_pred %>%
   mutate(scale = recode_nodes2(scale)) %>%
-  group_by(condition, scale) %>%
-  summarize(M = mean(diff, na.rm=TRUE)) %>%
-  ungroup() %>%
-  group_by(scale) %>%
-  summarize(diff_diff = mean(M, na.rm = T)) %>%
-  ungroup() %>%
-  arrange(desc(diff_diff)) %>% # descending because intervention is expected to increase disease risk beliefs
+  arrange(desc(predicted)) %>% # descending because intervention is expected to increase disease risk beliefs
   mutate(order = 1:nrow(.))
+
+# s2_scale_order <- s2_scored %>%
+#   drop_na(scale) %>%
+#   spread(phase, mean) %>%
+#   mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>%
+#   mutate(diff = post-pre) %>%
+#   mutate(scale = recode_nodes2(scale)) %>%
+#   group_by(condition, scale) %>%
+#   summarize(M = mean(diff, na.rm=TRUE)) %>%
+#   ungroup() %>%
+#   group_by(scale) %>%
+#   summarize(diff_diff = mean(M, na.rm = T)) %>%
+#   ungroup() %>%
+#   arrange(desc(diff_diff)) %>% # descending because intervention is expected to increase disease risk beliefs
+#   mutate(order = 1:nrow(.))
 
@@
   left_join(s2_scale_order) %>%
-  ggplot(aes(x = reorder(scale,order), y = M,
+  ggplot(aes(x = reorder(scale, order), y = M,
              ymin = M-se*2, ymax=M+se*2,
@@
 
-obs_pred <- make_pred_df(s2_mdf, base_model, "diseaseSevere")
-
-cor_val_s2 <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
-
 s2_obs_pred_plot <- obs_pred %>% # a bit of a hack
@@
 Thus the model developed in Study 1 generalizes both across samples and across tasks: The model was developed from the correlations among beliefs in one sample of participants at a single time-point, and was able to accurately predict how a separate sample of participants revised their beliefs following evidence.
+
+```{r, include=F}
+## effect size for study 2
+
+s2_reg %>% 
+  group_by(workerId, condition, phase) %>% 
+  summarize(mresp = mean(response, na.rm=TRUE)) %>% 
+  spread(phase, mresp) %>% 
+  ungroup() %>% 
+  group_by(condition) %>% 
+  mutate(
+    sd_pre = sd(pre),
+    diff = post - pre
+    ) %>% 
+  summarize(
+    m_diff = mean(diff),
+    sd_pre = mean(sd_pre)
+  ) %>% 
+  mutate(
+    cohen_d = m_diff/sd_pre
+  )
+
+effect_size_s2 <- (.124 - -.0292)/sqrt( (1.26^2 + 1.30^2)/2 ) # standardized cond diff = .12
+
+```
 
@@
 ```{r fig9-s3_plot, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b.
-Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
+Belief scales are ordered by model-predicted changes based on the observed effect on disease severity.
+Our primary outcome of interest, vaccination intentions, is highlighted in gray.
 Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition.
@@
 
-s3_scale_order <- s3_scored %>%
-  drop_na(scale) %>%
-  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>%
-  mutate(diff = post-pre) %>%
+obs_pred <- make_pred_df(s3_mdf, base_model, "vaccTox")
+
+cor_val_s3 <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
+
+s3_scale_order <- obs_pred %>%
   mutate(scale = recode_nodes2(scale)) %>%
-  group_by(condition, scale) %>%
-  summarize(M = mean(diff, na.rm=TRUE)) %>%
-  ungroup() %>%
-  group_by(scale) %>%
-  summarize(diff_diff = mean(M, na.rm = T)) %>%
-  ungroup() %>%
-  arrange(diff_diff) %>% # ascending because intervention is expected to decrease vaccine toxicity beliefs
+  arrange(desc(predicted)) %>% # descending because intervention is expected to increase disease risk beliefs
   mutate(order = 1:nrow(.))
+
+# s3_scale_order <- s3_scored %>%
+#   drop_na(scale) %>%
+#   mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>%
+#   mutate(diff = post-pre) %>%
+#   mutate(scale = recode_nodes2(scale)) %>%
+#   group_by(condition, scale) %>%
+#   summarize(M = mean(diff, na.rm=TRUE)) %>%
+#   ungroup() %>%
+#   group_by(scale) %>%
+#   summarize(diff_diff = mean(M, na.rm = T)) %>%
+#   ungroup() %>%
+#   arrange(diff_diff) %>% # ascending because intervention is expected to decrease vaccine toxicity beliefs
+#   mutate(order = 1:nrow(.))
 
@@
 
-obs_pred <- make_pred_df(s3_mdf, base_model, "vaccTox")
-
-cor_val_s3 <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
-
 s3_obs_pred_plot <- obs_pred %>%
@@
 ```{r fig10-s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=10, fig.height=5, fig.cap="Belief changes following the intervention in Experiments 3a and 3b, broken out by experiment.
-Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow.
-Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition.
+Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in grey Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition.
 In both plots, error bars represent 95\\% confidence intervals."}
@@
   left_join(s3_demo %>% distinct(workerId, study)) %>%
-  mutate(study = recode_factor(study, "A" = "Expt. 3A", "B" = "Expt. 3B")) %>%
+  mutate(study = recode_factor(study, "A" = "Expt. 3a", "B" = "Expt. 3b")) %>%
   group_by(study, condition, scale) %>%
@@
 
+```{r}
+## Effect size for study 3
+s3_reg %>% 
+  group_by(workerId, condition, phase) %>% 
+  summarize(mresp = mean(response, na.rm=TRUE)) %>% 
+  spread(phase, mresp) %>% 
+  ungroup() %>% 
+  group_by(condition) %>% 
+  mutate(
+    sd_pre = sd(pre),
+    diff = post - pre
+  ) %>% 
+  summarize(
+    m_diff = mean(diff),
+    sd_pre = mean(sd_pre)
+  ) %>% 
+  mutate(
+    cohen_d = m_diff/sd_pre
+  )
+
+effect_size_s3 <- (.0564 - -.11)/sqrt( (1.35^2 + 1.20^2)/2 ) # standardized cond diff = .13
+```
+
 ## Study 4
@@
 
-s4_scale_order <- combined %>%
-  drop_na(scale) %>%
-  mutate(posttest = rescale_beta(posttest, -3, 3),
-         pretest = rescale_beta(pretest, -3, 3)) %>%
-  mutate(diff = posttest-pretest) %>%
+obs_pred <- make_pred_df(s4_mdf, base_model, "vaccIntent")
+
+cor_val_s4 <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
+
+s4_scale_order <- obs_pred %>%
   mutate(scale = recode_nodes2(scale)) %>%
-  group_by(vacc_news, scale) %>%
-  summarize(M = mean(diff, na.rm=TRUE)) %>%
-  ungroup() %>%
-  group_by(scale) %>%
-  summarize(diff_diff = mean(M, na.rm = T)) %>%
-  ungroup() %>%
-  arrange(desc(diff_diff)) %>% # ascending because news exposure is expected to increase vaccine intentions
+  arrange(desc(predicted)) %>% # descending because intervention is expected to increase disease risk beliefs
   mutate(order = 1:nrow(.))
+
+# s4_scale_order <- combined %>%
+#   drop_na(scale) %>%
+#   mutate(posttest = rescale_beta(posttest, -3, 3),
+#          pretest = rescale_beta(pretest, -3, 3)) %>%
+#   mutate(diff = posttest-pretest) %>%
+#   mutate(scale = recode_nodes2(scale)) %>%
+#   group_by(vacc_news, scale) %>%
+#   summarize(M = mean(diff, na.rm=TRUE)) %>%
+#   ungroup() %>%
+#   group_by(scale) %>%
+#   summarize(diff_diff = mean(M, na.rm = T)) %>%
+#   ungroup() %>%
+#   arrange(desc(diff_diff)) %>% # ascending because news exposure is expected to increase vaccine intentions
+#   mutate(order = 1:nrow(.))
 
@@
   # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
-  left_join(s4_scale_order) %>%
+  left_join(s4_scale_order, by ="scale") %>%
   ggplot(aes(x=reorder(scale, order),
@@
 
-obs_pred <- make_pred_df(s4_mdf, base_model, "vaccIntent")
-
-cor_val_s4 <- format(round(cor(obs_pred$predicted, obs_pred$observed),3), nsmall = 3)
-
 s4_obs_pred_plot <- obs_pred %>% # a bit of a hack

### 2022-07-08 paper/paper-papaja.Rmd
paper revisions

@@
 
-note: |
-  This manuscript has not yet been peer-reviewed (2/15/2022).
+# note: |
 
 authornote: |
-  All data, and analysis code for this project are available at https://osf.io/sdfpj/.
+  Supplementary Materials, including all data and analysis code for this project are available at https://osf.io/sdfpj/.
 Preregistration information for Studies 3a and 3b is available at https://osf.io/csnez/registrations.
@@
 @lewandowsky.etal2012].
-Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence [e.g., @gershman2019; @lewandowsky.etal2012; @jern.etal2014; @cook.lewandowsky2016].
+Part of the challenge in correcting misconceptions is that they are situated within larger, internally coherent belief systems---intuitive theories---that guide how people interpret and respond to evidence [e.g., @cook.lewandowsky2016; @gershman2019; @lewandowsky.etal2012; @jern.etal2014].
+In particular, prior work suggests the "attitude roots" of vaccine skepticism may spread quite wide, with vaccine misconceptions correlated with quite distant beliefs about the world [@hornsey.etal2018].
 
@@
 
-We argue that correcting misconceptions requires presenting evidence in a way that is sensitive to and persuasive within the broader conceptual context in which those misconceptions reside [see @gershman2019; @weisman.markman2017; @cook.lewandowsky2016].
+We argue that correcting misconceptions requires presenting evidence in a way that is sensitive to and persuasive within the broader conceptual context in which those misconceptions reside [see @cook.lewandowsky2016; @hornsey.etal2018; @gershman2019; @weisman.markman2017].
 Understanding the revision of any one specific belief (e.g., a misconception like *vaccines are dangerous*) demands a holistic understanding of the wider set of interrelated beliefs that make up people's intuitive theories.
@@
 Intuitive theories consist of relations between beliefs that specify how states of affairs causally, logically, or otherwise interconnect with one another.
-Given this definition, we argue that any set of beliefs related by an intuitive theory can be expected to exhibit several qualitative features:
+Specifically, we consider intuitive theories to be generative mental models that entail probabilistic dependencies among possible states of affairs.
+Given this definition, we argue that any pair of beliefs related by a intuitive theory can be expected to exhibit several qualitative features:
 
-1) Where beliefs about two states of affairs, A and B, are related through a shared intuitive theory (e.g., A causes B), those beliefs will be systematically correlated across individuals (e.g.
-people who believe A will also tend to believe B);
-
-2) When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g.
+1.
+When two beliefs are related by an intuitive theory, evidence directly affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g.
 evidence for B will increase credence in A, and vice versa).
-
-3) Thus, across individuals, the average change in one belief following evidence affecting another belief will be proportional to the correlation between those beliefs across individuals (e.g.
-evidence for B will increase credence in A in proportion to the correlation between beliefs A and B).
+This is a clear and direct consequence of the laws of probability and Bayes' rule.
+2.
+Where beliefs about two states of affairs, A and B, are related through an intuitive theory (e.g., A causes B), those beliefs will be systematically correlated across individuals in proportion to the average conditional probabilities (e.g.
+people who believe A will also tend to believe B); This can be seen through an application of the law of total probability, which implies a linear relationship between the two beliefs across individuals.
+3.
+Thus, we can often reasonably expect there will be some systematic relationship between the average change in each belief following observation of some evidence and the correlation among those beliefs across individuals.
+We provide a more formal explication of these last two points in Supplementary Materials.
 
@@
 @gopnik.etal2004; @jern.etal2014; @griffiths.tenenbaum2005].
-The heart of a Bayesian network is a graphical structure ---not unlike a "web of belief"---that represents variables as nodes connected by edges, where those edges represent probabilistic or statistical relations.
+The heart of a Bayesian network is a graphical structure---not unlike a "web of belief"---that represents variables as nodes connected by edges, where those edges represent probabilistic or statistical relations.
 
-For example, the graph $\text{FIRE} \rightarrow \text{SMOKE}$ represents a Bayesian network capturing the understanding  that fire causes smoke.
-The example of cause and effect is especially intuitive, but edges in a Bayesian network need not be causal; they are better thought of as representing “influence relations,” which may also include relationships like logical implication and set membership [@williamson2001].
-This influence relationship is represented as a probabilistic function, where the probability of smoke depends on the probability of fire.
+### Bayesian networks
 
-This model captures each of the qualitative features laid out above: First, it captures people’s  reasoning  about these states of affairs given observations: observing smoke would lead someone to infer that there is likely to be a fire, and observing fire would lead someone to predict smoke will soon follow (Feature 1).
-This model can also capture how these beliefs might covary across individuals: if two people hold different degrees of belief in FIRE, this model specifies the degree of belief each should have in SMOKE (Feature 2).
-Because the conditional probability of SMOKE given FIRE determines both the change in beliefs given observations and the correlation of beliefs across individuals, changes in beliefs following evidence will be proportional to their correlations across individuals (Feature 3).
+Figure 1 presents several examples of Bayesian networks.
+Each of the networks is a _directed acyclic graph_ (DAG), a type of graphical model.
+Graphical models represent variables as nodes connected by edges.
+In a DAG, these edges are directed, flowing from parent to child, and are constrained so that they cannot form cycles or loops.
+In a Bayesian network, these directed edges encode conditional dependencies among variables, so that the conditional probability distribution for a given variable is defined only in terms of its direct parents.
+
+(ref:bn-explain-caption) Several examples illustrating different features of Bayesian Networks.
+\newline A) A graphical representation of influence relations: Fire causes smoke.
+This influence is represented by the conditional dependencies captured in a conditional probability table (CPT).
+\newline B) A “parent” node can be linked to multiple “children” and a “child” node can be linked to multiple “parents”: A child and its parents together compose a “family”.
+This graph has three families: {Accidents, lightning, drought, fire}, {fire, smoke}, and {fire, ash}.
+\newline C) Not all influence relations correspond to causation: we could say a storm _consists_ of rain and lightning (marked as dashed arrows), which in turn causes thunder.
+Causes can be generative or preventive, e.g.
+rain prevents drought and fire (red arrows).
+Some nodes may exert countervailing influences on others: A storm consists of rain, which can prevent fires, but a storm also consists of lightning, which can cause fires.
+In addition, parents may influence their children independently or interactively.
+Lightning and accidents could be seen as independent causes of fire—an accident may cause a fire whether or not there is lightning, and vice versa.
+However, drought conditions interact with both of these other parent nodes, making them more likely to produce a fire.
+In the present work, we will consider only the role of independent influence relations.
+
+```{r, out.width='100%', fig.align='center', fig.cap = "(ref:bn-explain-caption)"}
+knitr::include_graphics("fig-bn-examples.png")
+```
+
+In Figure 1a, the edge from $fire \rightarrow smoke$ indicates that the probability of smoke is increased by fire.
+So, conditional on fire, smoke becomes more likely.
+The Bayesian network captures how conditioning on any one node affects the probability of all the other nodes in the network.
+The directed edges in a Bayesian network capture _asymmetric_ relationships: different edge directions imply different conditional dependencies and independencies.
+A criterion called “d-separation” provides a formal means for deciding which nodes in a network conditionally depend on one another [@pearl1988].
+To illustrate, consider some relationships depicted in Figure 1c.
+Intuitively, it should be clear that observing (conditioning on) lightning will affect the probability of fire and all of its descendents.
+Indeed, these nodes are “d-connected” in the network.
+But, observing (conditioning on) lightning should not affect the probability of accidents (these nodes are d-separated in the network).
+
+It can be tempting to interpret the edges in a Bayesian network as representing causal relationships.
+Strictly speaking however, the Bayesian network is simply an encoding of the probabilistic relationships among variables.
+These dependencies can be interpreted most generally as representing “influence relations” [@williamson2001].
+As modelers, we might sometimes give these influence relationships more specific interpretations: causal relationships and logical implications [@williamson2001] are two prominent sorts of influence relations.
+In other cases, influence relations might be interpreted as representing “constituency” (e.g.
+see Figure 1c) or an entity's having a particular property (e.g.
+an edge from "being an apple" to "being red" might represent that redness is a common property of apples).
+However, in all these cases these interpretations are external to the Bayesian network model itself, where the edges signify only probabilistic relationships.
+
+Bayesian networks like those depicted in Figure 1 can be made to capture each of the qualitative features of intuitive theories laid out above.
+First, a Bayesian network captures people’s reasoning about these states of affairs given observations: observing smoke would lead someone to infer that there is likely to be a fire, and observing fire would lead someone to predict smoke will soon follow (Feature 1).
+Using the conditional probability values in Figure 1a, observing smoke would shift someone with a prior probability of fire $p(fire) = .2$ to a posterior probability of fire $p(fire|smoke) = .83$.
+And for this same person, observing fire would shift their credence in smoke from $p(smoke) = .238$ to $p(smoke|fire) = .99$.
+
+This model can also capture how these beliefs might covary across individuals: if two people hold different degrees of belief in _fire_, but share the same understanding of the relationship between _fire_ and _smoke_, this model specifies the degree of belief each should have in _smoke_ (Feature 2).
+If Alice holds that $p(fire) = .4$ and Bob holds that $p(fire) = .1$, then Alice should belief $p(smoke) = (.99)(.4) + (.05)(.6) = .426$ and Bob should believe $p(smoke) = (.99)(.1) + (.05)(.9) = .144$.
+
+We can leverage both of these facts to derive a model of people’s intuitive theory relating these affairs based on the correlations among these beliefs.
+Because the conditional probabilities of _smoke_ given _fire_ and $\neg fire$ crucially determine both the change in beliefs given observations and the correlation of beliefs across individuals, average changes in beliefs following evidence will generally be related to the initial correlation of those beliefs across individuals (Feature 3; see Supplementary Materials for further explanation).
+
 Formulating these features in a formal model, rather than a verbal theory, allows us to specify not just the presence but the quantitative strength of these relations, and to simulate the cumulative influences of many factors in more complex networks (for example, incorporating beliefs about the frequency of wildfires, recent weather conditions, etc.).
+
+Other network-based approaches have also been applied to model systematic relationships among beliefs and attitudes, such as neural network models [e.g.
+see @holyoak.powell2016; @holyoak.simon1999; @simon.etal2004; @thagard1989; @spellman.etal1993].
+In these models, beliefs or attitudes are represented by nodes (neurons) connected by undirected or bi-directed edges—in contrast to the directed edges used in Bayesian Networks.
+One application of neural-network models has been the modeling of “coherence-shifts”: patterns of belief revision wherein the beliefs or attitudes that should putatively serve as inputs to an evaluation are themselves modified during the process of evaluation.
+However, the directed edges of Bayesian networks are similarly capable of capturing these coherent reasoning dynamics: When conditioning on a node within a network, information flows in both directions along the edges.
+To illustrate, consider how observing smoke will lead a reasoner to infer that there is a fire, just as readily as observing fire will lead them to predict there will be smoke.[^1]
+
+[^1]: With this in mind, Bayesian Networks also offer potential models of coherence-based reasoning effects based on rational belief updating mechanisms [@jern.etal2014].
 
@@
 Structure learning algorithms [see @scutari.denis2021] provide a means for searching through the (super-exponentially large) possible space of Bayesian networks to find the structure most likely to have generated some observed data.
-These approaches allow us to scale the Bayesian network modeling framework beyond the smaller models characteristic of early computational work on intuitive theories [e.g., @cook.lewandowsky2016; @griffiths.tenenbaum2005; @jern.etal2012].
+These approaches allow us to scale the Bayesian network modeling framework beyond the smaller models characteristic of early computational work on intuitive theories [e.g., @griffiths.tenenbaum2005].
 
@@
 Across all our studies, our primary outcome of interest was participants’ intentions to vaccinate their children against diseases like measles, mumps, and rubella (which we refer to henceforth as *vaccination intentions*).
-Drawing on a variety of sources, including research on anti-vaccine skepticism [e.g.,  @dube.etal2015; @larson.etal2015; @salmon.etal2015; @williams2014], anti-vaccine websites, and our own qualitative work with vaccine skeptics (see SI), we generated a list of 13 additional beliefs that, though surely not exhaustive, might jointly offer a reasonable means of understanding and predicting vaccine intentions.
+Drawing on a variety of sources, including research on anti-vaccine skepticism [e.g.,  @dube.etal2015; @larson.etal2015; @salmon.etal2015; @williams2014], anti-vaccine websites, and our own qualitative work with vaccine skeptics (see Supplementary Materials), we generated a list of 13 additional beliefs that, though surely not exhaustive, might jointly offer a reasonable means of understanding and predicting vaccine intentions.
 
@@
 We developed 13 of these scales, and included one preexisting scale (the “holistic balance” subscale from [@mcfadden.etal2010].
-See SI for all items included in all scales.
+See Supplementary Materials for all items included in all scales.
 
-In Study 1, we administered these 14 belief scales to participants and in an online survey with `r results$s1$demo$n_include` participants.
+In Study 1, we administered these 14 belief scales to participants in an online survey with `r results$s1$demo$n_include` participants.
 We then used these intercorrelations to build a cognitive model of the relations among these beliefs via Bayesian network structure learning techniques.
@@
 `r results$s1$demo$n_exclude` participants (6%) failed at least one of two attention check questions and were excluded from further analysis, leaving a final sample of n = `r results$s1$demo$n_include`.
-See SI for demographic information about this sample.
+See Supplementary Materials for demographic information about this sample.
 
@@
 The goal of this study was to use these data to conduct a bottom-up search for a Bayesian network that would represent the intuitive theory surrounding vaccination decisions as a network of related beliefs.
-There were strong intercorrelations among these 14 beliefs confirming that these beliefs are, in fact, closely related to each other and to intentions to vaccinate children (see SI).
+There were strong intercorrelations among these 14 beliefs confirming that these beliefs are, in fact, closely related to each other and to intentions to vaccinate children (see SM).
 Based on the observed associations among participants' beliefs about each of theses issues, we sought to infer how these states of affairs (e.g., that vaccines are dangerous, that diseases are severe) are connected in people's intuitive theories---how people understand these states of affairs to cause, imply, or otherwise influence one another.
@@
 A Bayesian network is a directed acyclic graph that represents variables as nodes connected by directed edges.
-Each set of “child” and “parent” nodes in the larger network is a “family”.
+Each set of “child” and “parent” nodes in the larger network is a “family” (for some examples, see Figure 1b).
 The network’s directed edges encode conditional dependencies among variables, and many parameterizations for the individual families are possible.
@@
 
-$$P(y=1) = \Big(1-(1-w_0)\prod_i(1-w_i)^{x_i}\Big)\prod_j(1-w_j)^{x_j}$$
+\begin{equation}
+P(y=1) = \Big(1-(1-w_0)\prod_i(1-w_i)^{x_i}\Big)\prod_j(1-w_j)^{x_j}
+\end{equation}
 
@@
 
+This parameterization is a substantial simplification compared with the full flexibility possible within a Bayesian network.
 A cognitive model composed of these types of relations is capable of capturing a causal system of non-interactive generative and preventive causes.
 But it bears noting that this simplification comes with limitations.
-For instance, returning to the example network in Figure 1d, this parameterization would not permit capturing the relationships between dryness, lightning, and fire.
+For instance, returning to the example network in Figure 1c, this parameterization would not permit capturing the relationships between dryness, lightning, and fire.
 Dryness is an enabling condition that both increases the probability of fire but also increases the probability that lightning would cause a fire.
@@
 
-Finally, having transformed participants’ scores on each belief scale to fall between 0 and 1, we estimated the parameters of this model as a Beta regression using maximum likelihood methods (see SI for details).
+Finally, having transformed participants’ scores on each belief scale to fall between 0 and 1, we estimated the parameters of this model as a Beta regression using maximum likelihood methods (see Supplementary Materials for details).
 
@@
 We aimed to represent not only the relationships among variables in the data but the *cognitive model* that gave rise to these observed relationships, i.e., the relationships among beliefs in the mind.
-We actually estimated two models: First, we estimated a data model assuming that participants possess a shared mental model from which they generate their responses to the belief scales.
-In this model, the $x$ in the equation above corresponded to participants’ continuous responses to the belief scales (e.g.
+We actually estimated two models sharing the same network structure as depicted in Figure 2: First, we estimated a data model assuming that participants possess a shared mental model from which they generate their responses to the belief scales.
+In this model, the values of $p(y=1)$ and $x$ in the equation above corresponded to participants’ continuous responses to the belief scales (e.g.
 a participant's score for the *vaccine danger* scale).
 Then, from the parameters estimated in the data model we created a cognitive model of participants’ reasoning, where the $x$ are binary, indicating whether that state of affairs obtains (e.g., whether “vaccines are dangerous”).
-We used this cognitive model to simulate how beliefs could change following exposure to evidence.
+
+We used this cognitive model to simulate participants' degrees of beliefs given other beliefs, as well as how beliefs would change following exposure to evidence.
 
@@
 
-To conduct an efficient search through the super-exponential space of graphs, we tested several learning algorithms implemented in the “bnlearn” R package [@scutari2010] and evaluated their performance through cross validation in our training split (see SI).
-Following this analysis, we chose to fit our model with the score-based “hill-climbing” algorithm, scoring models via the Bayesian Information Criteria, an asymptotic estimate of the likelihood of the data under a given graph structure.
-This produced the network shown in Figure 1.
-See SI for more detailed explanations of these modeling choices.
-
-#### Structure learning
-
+To conduct an efficient search through the super-exponential space of graphs, we tested several learning algorithms implemented in the “bnlearn” R package [@scutari2010] and evaluated their performance through cross validation.
 To avoid overfitting, we used an 80% split of the data (*n* = 904) for training, and reserved the remaining 20% for evaluating model performance.
 We compared performance of different structure learning algorithms using k-fold cross validation within the training split.
-Based on these results, we chose to apply a hill-climbing learning algorithm using our generative model constraints (see SI for details).
+Graphs were scored by Bayesian Information Criteria, an asymptotic estimate of the likelihood of the data under a given graph structure.
+Based on these results, we chose to apply a score-based "hill-climbing"  algorithm using our generative model constraints (see Supplementary Materials for details).
 Applying these techniques resulted in an estimate of the network shown in Figure 1.
@@
 Edge polarity and weights are indicated by color, with red hues indicating negative or preventive influences, and blue hues indicating positive or generating influences.
-The direction of the edge was not determinable from the data and modeling constraints for two edges: $\\text{Naturalism} \\rightarrow \\text{Holistic Balance}$ and $\\text{Medical Skepticism} \\rightarrow \\text{Parental Expertise}$; see SI."}
+The direction of the edge was not determinable from the data and modeling constraints for two edges: $\\text{Naturalism} \\rightarrow \\text{Holistic Balance}$ and $\\text{Medical Skepticism} \\rightarrow \\text{Parental Expertise}$; see Supplementary Materials."}
 
@@
 We evaluated the resulting cognitive model’s performance by testing its accuracy in predicting responses in the 20% testing split (*n* = 226).
-We generated predictions for held-out participants’ responses for each variable by conditioning the network on the remaining 13 observed variables.
-Figure 2 compares the model’s predictions with participants’ actual responses.
+We generated predictions for held-out participants’ responses for each variable by conditioning the cognitive model network on the remaining 13 observed variables.
+Figure 3 compares the model’s predictions with participants’ actual responses.
 Collapsing across all variables, the average correlation between predicted and observed responses was *r* = `r round(avg_corr, 3)`, accounting for `r round(100*avg_corr^2, 0)`% of the variance in observed responses.
@@
 To address this, we compared the Bayesian network model’s predictions to a suite of 14 naive “maximal” regression models, each using values on all 13 other belief scales as predictors for each belief.
-Our simpler model provided equally strong predictions (see SI).
-And, as will be evidenced in later studies, our model can also be used to generate accurate predictions about how beliefs will change following evidence.
+The model presented in Fig.
+1---which we take to be simpler, more psychologically plausible, and more intelligible---performed as strongly as these "maximal" regression models (see Supplementary Materials).
 
@@
 Correlations between observed and predicted values ranged from .380 to .898 across the different belief scales.
-In general, the model showed greater predictive accuracy for more central beliefs (e.g., \\emph{vaccine danger}) than for more peripheral beliefs (e.g., \\emph{parental protectiveness}; see SI for details)."}
+In general, the model showed greater predictive accuracy for more central beliefs (e.g., \\emph{vaccine danger}) than for more peripheral beliefs (e.g., \\emph{parental protectiveness}; see Supplementary Materials for details)."}
 knitr::include_graphics("../local/valid_plt.png")
@@
 
-What does this cognitive model reveal about the intuitive theory underlying vaccination decisions?
+#### What does this cognitive model reveal about the intuitive theory underlying vaccination decisions?
 
@@
 It is worth pointing out that not all of the relationships represented in the model should be interpreted as _causal_.
-Due to Bayesian networks’ tight connections with structural causal networks, it can be tempting to give the edges this interpretation, but in some cases these relationships are better thought of as probabilistic dependencies or “influence” relations (Williamson, 2001).
-For instance, intuitively we might imagine that vaccines having toxins (_toxic additives in vaccines_) could cause them to be dangerous (_vaccine danger_).
-These nodes are connected in the model, but the edges between them run in the opposite direction, and therefore do not support a clear causal interpretation.
-One interpretation is that this edge instead reflects a set membership relation; that toxins are one type of danger vaccines might present.
+Due to Bayesian networks’ tight connections with structural causal networks, it can be tempting to give the edges this interpretation, but in some cases these relationships are better thought of as probabilistic dependencies or “influence” relations [@williamson2001].
+For instance, the edge running from vaccine danger to toxic additives in vaccines clearly does not represent a causal influence: vaccines being dangerous does not cause them to contain toxins.
+Instead, a more plausible interpretation of this edge is that it reflects something like a set membership relation: that toxins are one type of danger that might be present in vaccines.
 
 In other cases, our data and explicit constraints do not perfectly identify the directions of the edges.
-This is the case for two edges (Naturalism $\rightarrow$  Holistic Balance and Medical Skepticism $\rightarrow$ Parental Expertise; see SI for details).
+This is the case for two edges (Naturalism $\rightarrow$  Holistic Balance and Medical Skepticism $\rightarrow$ Parental Expertise; see Supplementary Materials for details).
 In both cases, we do not feel it is intuitive which direction the edge should flow in, nor even that it should be directed at all.
 Such a counterintuitive result might be taken as indicating a limitation of Bayesian network models, which are composed solely of directed, acyclic relationships.
-Prior work has successfully modeled coherent belief revision by leveraging models with undirected or bidirected relations [e.g.
-@spellman.etal1993].
-Alternatively, we might imagine there is an additional unmeasured variable that connects these beliefs that could more intelligibly account for their association within the context of a directed network.
+We note that prior work has successfully modeled coherent belief revision by leveraging models with undirected or bidirected relations [e.g.
+@holyoak.simon1999; @simon.etal2004; @thagard1989; @spellman.etal1993].
+Alternatively, we might instead hypothesize there is an additional unmeasured variable that connects these beliefs that could more intelligibly account for their association within the context of a directed network.
 For instance, a more abstract epistemic belief might influence both medical skepticism and parental expertise beliefs.
@@
 through direct experience versus science).
+
+More generally, as they operate solely on correlations among variables, structure learning algorithms cannot be guaranteed to correctly identify causal directionality.
+Looking forward to future applications of these methods, researchers might seek other ways to resolve ambiguities left by structure learning algorithms.
+The simplest approach would be to set edges manually based on top-down theorizing, or even to set stronger constraints in advance of fitting models.
+Another potential future direction would be to probe people's mental causal models more directly, either by asking them directly what they think about the causal relationships among variables or by asking them to reason through hypothetical interventions on variables.
+These more direct responses might then be used to constrain or augment the structure learning algorithm's outputs.
 
@@
 One of the few successful educational interventions in this domain was tested by Horne and colleagues [-@horne.etal2015], who found that emphasizing the dangers of preventable diseases like mumps, measles, and rubella improved participants’ attitudes toward vaccines.
-Their intervention included descriptions of the symptoms of mumps, measles, and rubella; vivid photos of children suffering from these diseases; and a brief story from the perspective of a parent whose child was hospitalized with measles (see SI).
+Their intervention included descriptions of the symptoms of mumps, measles, and rubella; vivid photos of children suffering from these diseases; and a brief story from the perspective of a parent whose child was hospitalized with measles (see Supplementary Materials).
 This “disease risk” intervention improved attitudes toward vaccines compared to an irrelevant control essay and compared to an intervention aimed at debunking concerns about vaccines causing autism.
@@
 
-In Study 2, we used the belief network established in Study 1 to predict how Horne and colleagues’ [-@horne.etal2015] intervention would affect the beliefs in this network, including people’s intentions to vaccinate their children.
+In Study 2, we used the cognitive model established in Study 1 to predict how Horne and colleagues’ [-@horne.etal2015] intervention would affect the beliefs in this network, including people’s intentions to vaccinate their children.
 Participants completed the 14 belief scales from Study 1, then returned two days later to complete either the disease risk intervention or a no-intervention control, followed by the same 14 belief scales.
@@
 
-Participants (*n* = `r results$s2$demo$n_complete` passed attention checks in total) in the intervention conditions were presented with a version of Horne and colleagues'  “disease risk” intervention, modified to present subparts in a fixed (rather than randomized) order, with slight changes to wording to improve clarity, and with a final statement summarizing the take-home message of the intervention; see SI.
+Participants (*n* = `r results$s2$demo$n_complete` passed attention checks in total) in the intervention conditions were presented with a version of Horne and colleagues'  “disease risk” intervention, modified to present subparts in a fixed (rather than randomized) order, with slight changes to wording to improve clarity, and with a final statement summarizing the take-home message of the intervention; see Supplementary Materials.
 They then completed the same 14 belief scales and demographic questions that they had completed in Phase 1.
@@
 
-Figure 3 shows the change in participants’ attitudes across all 14 belief scales, from pretest to posttest.
+Figure 4 shows the change in participants’ attitudes across all 14 belief scales, from pretest to posttest.
 As expected, the largest change was observed for *disease severity* beliefs---the belief directly targeted by the intervention.
@@
 We included random intercepts by subject and scale item.
+In the lme4 syntex, the model was:
+
+```
+response ~ phase * condition + (1|subject) + (1|item)
+```
+
 In this model, the unique effect of the intervention on vaccination intention scores is assessed by the interaction term (indicating the unique effect of Phase 2 for intervention versus no-intervention participants).
-The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: $b$ = `r round(s2_reg$fixed[9,1],3)`, 95% Credible Interval (CI): [`r round(s2_reg$fixed[9,3], 3)`, `r round(s2_reg$fixed[9,4], 3)`]).
+The disease risk intervention increased participants’ vaccination intention ratings (interaction effect: $b$ = `r round(s2_reg$fixed[9,1],3)`, 95% Credible Interval (CI): [`r round(s2_reg$fixed[9,3], 3)`, `r round(s2_reg$fixed[9,4], 3)`]; see Figure 4, panel A).
 We consider this to be a full replication of Horne and colleagues' [-@horne.etal2015] results.
-See Figure 3, panel A.
 
-Visual inspection of Figure 3, panel A, further reveals that changes were also observed across the belief network identified in Study 1.
+Visual inspection of Figure 4, panel A, further reveals that changes were also observed across the belief network identified in Study 1.
 Not only did participants exposed to the intervention come to see childhood diseases as more severe, they also came to see vaccines as less dangerous, and demonstrated less medical skepticism as well as less commitment to “holistic balance”.
@@
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
+Scales are arranged in order of their predicted changes according to the cognitive model.
 Right, mean observed and predicted change scores from the cognitive model for the disease risk intervention condition.
@@
 
-To model the effects of the intervention presented in Study 2 on the intuitive theory surfaced in Study 1, we augmented the belief network representing the intuitive theory with an additional node representing the information about measles, mumps, and rubella presented in the intervention.
+To model the effects of the intervention presented in Study 2 on the intuitive theory surfaced in Study 1, we augmented the cognitive model's network representing the intuitive theory with an additional node representing the information about measles, mumps, and rubella presented in the intervention.
 This evidence node was added as a child of the *disease severity* node, allowing the intervention to act as virtual evidence for *disease severity* [following @pearl1988].
@@
 
-$$logit(posttest) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})$$
+\begin{equation}
+logit(posttest) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})
+\end{equation}
 
@@
 
-$$ER_i = \ln\frac{(P(d_i|h=1))}{(P(d_i|h=0))}$$
+\begin{equation}
+ER_i = \ln\frac{(P(d_i|h=1))}{(P(d_i|h=0))}
+\end{equation}
 
-In equation X, $ER_0$ represents whatever background "evidence" participants would see between phases outside  the experimental context, that would be shared by participants in both conditions.
+In equation 3, $ER_0$ represents whatever background "evidence" participants would see between phases outside  the experimental context, that would be shared by participants in both conditions.
 $ER_1$ represents the evidence provided by the intervention information, which is assumed to be independent from $ER_0$.
 These log evidence ratios were both estimated via regression.
-Then, we constructed a conditional probability table consistent with $ER_1$ and augmented the cognitive model with this evidence node (see SI for details).
+Then, we constructed a conditional probability table consistent with $ER_1$ and augmented the cognitive model with this evidence node (see Supplementary Materials for details).
 
 Using this augmented model, we are able to “condition” our cognitive model on this evidence node, and thereby predict how observing evidence will affect all of the beliefs in the network.
-As shown in Figure 3, panel B, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (*r* = `r results$s2$modcorr`).
+As shown in Figure 4, panel B, this simulation is a reasonable approximation of what we observed in Study 2: The model’s predictions correlate strongly with observed changes (*r* = `r results$s2$modcorr`).
 
@@
 
-One advantage of having developed a formal, computational representation of a network of beliefs supporting vaccination decisions is that it can guide our search for effective interventions, allowing us to compare how interventions targeting each of these other beliefs might potentially change people’s vaccination intentions (see Figure 4).
+One advantage of having developed a formal, computational representation of a network of beliefs supporting vaccination decisions is that it can guide our search for effective interventions, allowing us to compare how interventions targeting each of these other beliefs might potentially change people’s vaccination intentions (see Figure 5).
 Countering myths about toxic additives is one approach the cognitive model developed in Study 1 predicts should be effective.
@@
 We conducted two preregistered experiments[^prereg] (Study 3a and Study 3b) testing the effects of this novel intervention aimed at dispelling concerns about toxic additives in vaccines using the same pretest-posttest design as Study 2.
+After analyzing data from the first of these studies, we were surprised to observe that in several cases participants' beliefs changed significantly from pretest to posttest among participants in the no-intervention control condition.
+For this reason, two months later we conducted a direct replication (Study 3b) in the hopes that any transient factors that might have caused these changes in beliefs might have dissipated, but we obtained very similar results (see Supplementary Materials).
+
 These studies followed similar design procedures as Study 2, with Phase 2 conducted 1-2 days after Phase 1.
@@
 This left a final sample of `r results$s3$demo$n_complete` participants.
-See SI for demographic information about this sample.
+see Supplementary Materials for demographic information about this sample.
 
@@
 
-As they shared the same design, we combined data from Studies 3a and 3b for analysis (but see SI for separate analyses by study).
+As they shared the same design, we combined data from Studies 3a and 3b for analysis (but see Supplementary Materials for separate analyses by study).
 As in Study 2, we conducted a mixed-effects Bayesian ordinal regression to assess the effects of the vaccine ingredients intervention on participants’ *vaccination intentions* scores.
-The vaccine ingredients intervention improved participants' vaccination intention scores relative to the control conditions (interaction effect: $b$ = `r round(s3_reg$fixed[9,1],3)`, 95% CI: [`r round(s3_reg$fixed[9,3], 3)`, `r round(s3_reg$fixed[9,4], 3)`]); see Figure 5, panel A.
+
+As in Study 2, Study 3a and 3b used a difference-in-difference design.
+Thus the effect of the vaccine intervention is measured by testing the interaction between condition and phase.
+The vaccine ingredients intervention improved participants' vaccination intention scores relative to the control conditions (interaction effect: $b$ = `r round(s3_reg$fixed[9,1],3)`, 95% CI: [`r round(s3_reg$fixed[9,3], 3)`, `r round(s3_reg$fixed[9,4], 3)`]); see Figure 6, panel A.
 It is worth noting that reliable changes were also observed from pretest to posttest in the control conditions (phase effect: $b$ = `r round(s3_reg$fixed[7,1],3)`, 95% CI: [`r round(s3_reg$fixed[7,3], 3)`, `r round(s3_reg$fixed[7,4], 3)`]), suggesting that these attitudes were also being influenced by other factors during the course of the study.
-We discuss this further below, but given that these studies were randomized controlled trial designs, these findings do not impair our ability to conclude that the intervention was causally efficacious in affecting vaccine intentions.
+Given that these studies were randomized controlled trial designs, these findings do not impair our ability to conclude that the intervention was causally efficacious in affecting vaccine intentions.
+It is important to emphasize that the test of the intervention's effectiveness is a test of an interaction---an interaction demonstrating that the improvements in intentions in the intervention condition were greater than those in the control condition.
 
@@
 
-To model the effect of the vaccine ingredients intervention, we followed the same procedure as in Study 2, but this time augmented the cognitive model with a node representing the vaccine ingredients intervention as a child of the vaccine toxins belief node (for details, see SI).
-This allowed us to predict how other beliefs in the network would change in light of the observed changes in participant’s beliefs about whether vaccines contain dangerous toxins; see Figure 5, panel B.
+To model the effect of the vaccine ingredients intervention, we followed the same procedure as in Study 2, but this time augmented the cognitive model with a node representing the vaccine ingredients intervention as a child of the vaccine toxins belief node (for details, see Supplementary Materials).
+This allowed us to predict how other beliefs in the network would change in light of the observed changes in participant’s beliefs about whether vaccines contain dangerous toxins; see Figure 6, panel B.
 
-Collapsing across these two studies, Figure 5 shows the change in participants’ (*n* = `r results$s3$demo$n_complete`) attitudes across all 14 belief scales from pretest to posttest.
+Collapsing across these two studies, Figure 6 shows the change in participants’ (*n* = `r results$s3$demo$n_complete`) attitudes across all 14 belief scales from pretest to posttest.
 Most importantly, the vaccine ingredients intervention significantly improved participants’ vaccination intentions compared to the no-intervention control condition.
@@
 Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions.
+Scales are arranged in order of their predicted changes according to the cognitive model.
 Right, mean observed and  predicted change scores from the cognitive model for the disease risk intervention condition.
@@
 As in Study 2, we used our model to predict how the 13 other beliefs in the intuitive theory should be expected to change given the average magnitude of the change observed in participants’ vaccine toxicity beliefs following the intervention.
-As shown in Figure 5, the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker (*r* = `r results$s3$modcorr`) than those observed in our other studies.
-
-In Study 3a, we were surprised to observe that beliefs also changed significantly from pretest to posttest among participants in the no-intervention control condition.
-Two months later we conducted a direct replication (Study 3b) in the hopes that any transient factors that might have caused these changes in beliefs might have dissipated, but we obtained very similar results (see SI).
+As shown in Figure 6, the model’s predictions are significantly related to the observed changes, but the correlations are relatively weaker (*r* = `r results$s3$modcorr`) than those observed in our other studies.
 
@@
 Left, mean difference scores comparing beliefs reported in August-September 2017 and May 2019 for the 14 belief scales, across participants who did and did not report exposure to news of the ongoing New York measles outbreak.
+Scales are arranged in order of their predicted changes according to the cognitive model.
 Right, mean observed and  predicted change scores from the cognitive model for those participants who did report exposure to this news.
@@
 Approximately `r round(100*(results$s4$demo$n_news/results$s4$demo$n_complete),0) `% of participants reported recently seeing, hearing, or reading about measles outbreaks.
-See SI for demographic information about this sample.
+See Supplementary Materials for demographic information about this sample.
 
@@
 
-Figure 6, panel A, shows the average change in participants’ beliefs following the outbreaks of 2019.
+Figure 7, panel A, shows the average change in participants’ beliefs following the outbreaks of 2019.
 Among participants who were exposed to relevant news covered, we observed changes in a number of beliefs, with notable increases in intentions to vaccinate, perceptions of vaccine efficacy, and perceptions of disease severity, as well as notable decreases in concern about vaccine danger.
@@
 To assess the effects of recent news exposure on vaccine intentions, we examined the interaction between phase and news exposure.
-Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months earlier (interaction effect: $b$ = `r round(s4_reg$fixed[9,1],3)`, 95% CI: [`r round(s4_reg$fixed[9,3], 3)`, `r round(s4_reg$fixed[9,4], 3)`]); see Figure 6, panel A.
+Participants’ vaccine intentions were increased by recent news exposure compared to their responses 18 months earlier (interaction effect: $b$ = `r round(s4_reg$fixed[9,1],3)`, 95% CI: [`r round(s4_reg$fixed[9,3], 3)`, `r round(s4_reg$fixed[9,4], 3)`]); see Figure 7, panel A.
 
@@
 Unlike in the intervention studies, where a specific belief was quite precisely targeted by the intervention, it is likely that many beliefs were addressed by media coverage of these outbreaks.
-Given that we cannot reasonably measure the exact information that participants were exposed to, it is not feasible to attempt to precisely model the impacts of this total evidence.
-However, we can leverage our model to assess whether the changes in their beliefs were *coherent*.
+Given that we cannot measure the exact information that participants were exposed to, it is not feasible to model the precise locus of its impacts.
+However, we can leverage our model to assess whether the changes in participants' beliefs were *coherent*.
 
@@
 To accomplish this, we followed the same procedure as in previous studies, but here augmented the model with a node representing media exposure as a child of the *vaccine intentions* node.
+This provides an evaluation of coherence similar to prior work on coherence-based reasoning, where the coherence of belief revision is evaluated with respect to some emerging decision, evaluation, or change in one specific belief or attitude [e.g.
+@holyoak.simon1999; @simon.etal2004; @spellman.etal1993].
 
-As shown in Figure 6, panel B, the changes in participants’ beliefs are very similar to the model’s predictions (*r* = `r results$s4$modcorr`), suggesting that the changes in their beliefs were highly coherent with respect to their intuitive theories of the domain.
+As shown in Figure 7, panel B, the changes in participants’ beliefs are very similar to the model’s predictions (*r* = `r results$s4$modcorr`), suggesting that the changes in their beliefs were highly coherent with respect to their intuitive theories of the domain.
 Modeling these beliefs as united by an intuitive theory not only captures how these beliefs are revised immediately in light of evidence, but also how they are changed by real-world events.
@@
 Looking forward, this formal representation ---though simplified and imperfect---lays a foundation for richer and more complex descriptions in the future.
-For instance, networks with richer parameterizations could capture how intuitive theories differ across individuals, opening up the possibility of fine-tuning predictions and perhaps even crafting tailored educational interventions for specific individuals or groups.
 
-[talk about magnitude of the effects. tailoring could strengthen. timing also matters, in context of physician visit]
+We tested two educational interventions: one emphasizing the dangers of childhood diseases and another debunking concerns about toxins in vaccines.
+Both were effective in increasing people’s intentions to vaccinate.
+How might these educational interventions affect vaccine uptake if deployed in the real world?
+We are somewhat cautious in our optimism: In conventional terms of standardized effect sizes, both intervention effects would be considered quite modest and their impacts on actual future decisions remain unknown.
+Still, we nevertheless see both of these interventions as promising foundations for real-world educational efforts.
+First, as they are quite brief, these interventions present a very low cost for delivery.
+In addition, their brevity supports opportunities for deploying them with strategic timing and from trusted sources.
+For instance, these arguments could be deployed in the context of visits with family physicians, including immediately before vaccination decisions are to be made.
+Delivering these messages at the point-of-decision could maximize their impacts.
+And, we predict their efficacy would be improved if they were delivered by a trusted family physician, rather than coming from a relatively anonymous online survey.
 
-Developing this model also had practical benefits.
+We credit our development of a quantitative model of the intuitive theory surrounding vaccination decisions as supporting our work as interventionists.
 By providing a graphical representation of the structure of this intuitive theory, this approach helped us to understand relationships between beliefs that were puzzling when considered only as correlations (e.g., the lack of correlation between beliefs about the infant immune system and vaccine intentions), and allowed us to “spot” opportunities to develop novel interventions.
+One exciting future direction for these and other brief interventions would be to tailor these interventions to an individual’s beliefs: Models with richer parameterizations could simulate belief change for an individual given a certain set of prior beliefs, paving the way for determining which specific intervention or combination of interventions would have the most impact for a particular decision-maker.
 
@@
 @kahan2013; @flynn.etal2017; @kunda1990].
-Yet many of the phenomena traditionally taken as evidence for these theories can also be explained by normative models of belief revision, so long as we are willing to posit that other auxiliary beliefs can affect the relationships between a belief and evidence [e.g.,@gershman2019; @jern.etal2014].
+Yet many of the phenomena traditionally taken as evidence for these theories can also be explained by normative models of belief revision, so long as we are willing to posit that other auxiliary beliefs can affect the relationships between a belief and evidence [e.g., @gershman2019; @jern.etal2014].
 Adjudicating between competing views of belief revision will require us to move beyond minimal models and illustrative simulations by assessing whether people actually do hold these auxiliary beliefs, and whether their broader belief systems behave according to the rules of probabilistic inference.
@@
 Indeed, controlled intervention studies have shown that messages focused on personal risk increase vaccination intentions [@motta.etal2021].
-However, as the pandemic has continued, it has become clear that the severity of COVID-19 is highly variable across individuals and across variants of the virus, potentially rendering the formation, updating, and use of beliefs about severity much more nuanced in the case of COVID-19 than in the case of diseases like measles.
+However, the severity of COVID-19 is highly variable across individuals and across variants of the virus, potentially rendering the formation, updating, and use of beliefs about severity much more nuanced in the case of COVID-19 than in the case of diseases like measles.
 
 Our findings also suggest that beliefs about vaccine efficacy are central to determining vaccination intentions.
-In the case of mumps, measles, and rubella, strong vaccines and robust vaccination campaigns have led to the near eradication of these diseases in the U.S.
-and other developed nations.
-Correspondingly, we observed most participants in our studies believed quite strongly that these vaccines are effective in preventing infection.
-In contrast, the high prevalence of COVID-19 makes the risk of infection substantial even for the vaccinated, although these vaccines remain highly effective at preventing severe illness and death.
+The high prevalence and mutation rate of COVID-19 makes the risk of infection substantial even for the vaccinated, although these vaccines remain highly effective at preventing severe illness and death.
 The rising prevalence of breakthrough infections and the need for boosters relatively soon after initial doses are likely to lead people to doubt the effectiveness of vaccines---but we see promise in educational interventions that clarify the many ways in which a vaccine can be “effective” (e.g., by preventing infection vs.
-by preventing severe illness, preventing death, or lowering transmissibility), or explain the need for booster shots (e.g., addressing the misconception that the need for a booster shot indicates a problem with the vaccine).
+by preventing severe illness, preventing death, or lowering transmissibility).
 
 Looking forward, living through the COVID-19 pandemic is likely to have deepened the public’s understanding of infectious diseases and public health.
-For example, the concept of “herd immunity” has likely never had greater public understanding and appreciation than now.
-This understanding seems like a prime target for future interventions aimed at increasing the uptake of vaccines for both COVID and other diseases—although its impacts are likely to depend on other auxiliary ethical commitments, such as moral beliefs about individuals’ obligations to their wider communities.
-
-Unfortunately, the scale and spread of dis- and misinformation about COVID-19 has far eclipsed the spread of fringe ideas about MMR vaccines: millions of people have come to believe that COVID-19 is caused by 5G telecommunications, that the virus was developed in a lab to be used as a bio-weapon, or even that the virus is not real at all, and instead is a "hoax" perpetrated by a globalist elite.
-As is the case with attempts to debunk the misconception that childhood vaccines cause autism, directly addressing these false conspiracy theories could prove to be extremely difficult.
-However, there is some cause for hope that clear education about COVID-19 vaccines may help to address these misconceptions indirectly.
-Our findings demonstrate that revising beliefs about  specific diseases or vaccines can have “upstream” consequences for more abstract beliefs, such as naturalism and medical skepticism—hinting at a novel approach for addressing the kinds of fringe theories that have emerged during the pandemic.
+For example, the concept of “herd immunity” has likely never had greater public visibility  and appreciation than now.
+This understanding seems like a prime target for future interventions aimed at increasing the uptake of vaccines for both COVID and other diseases.
 
 Finally, like all pandemics, the COVID-19 pandemic is inescapably social.
-For one, in the U.S.
+In the U.S.
 and abroad, COVID-19 vaccines and mitigation measures have become deeply politicized.
@@
 Still, these affiliations are also associated with social commitments and personal values that may behave differently than the beliefs examined here.
-Whereas beliefs about “matters of fact” might be driven by an underlying intuitive theory and thereby sensitive to evidence, these sorts of identity-constituting “beliefs” may operate by different principles [@vanleeuwen2014] or may be entirely socially-motivated [@kahan2016].
+Whereas beliefs about “matters of fact” might be driven by an underlying intuitive theory and thereby sensitive to evidence, these sorts of identity-constituting “beliefs” may operate by different principles [@vanleeuwen2014], such as being driven primarily by people’s affinity toward their social groups rather than by concrete external evidence [@kahan2016].
 
-More broadly, people from different social groups have different experiences and knowledge that are likely to shape their intuitive theories of vaccination and the medical establishment in important ways—something that the approach we have taken in the current studies does not yet account for.
+More broadly, people from different social groups have different experiences and knowledge that are likely to shape their intuitive theories of vaccination and the medical establishment in important ways.
 For example, White vs.
@@
 
-[discuss broader implications / applications as requested]
+The current studies add to a growing body of work demonstrating how leveraging intuitive theories can spur belief revision and behavior change in the domain of physical health [cf.
+@weisman.markman2017].
+It also introduces a new approach to modeling and understanding intuitive theories more broadly.
+In prior work, researchers focused on identifying a small set of beliefs or concepts that were core to the intuitive theory and specific attitudinal or behavioral outcomes.
+For example, in previous work on vaccination attitudes, researchers focused on how people balanced perceptions of the risk of vaccine side effects and the risk of childhood diseases to inform their intentions to vaccinate their children [@horne.etal2015].
+The approach we introduced here expands the set of beliefs considered beyond a small core to a wider set of auxiliary beliefs that may influence decisions.
+This is made feasible by leveraging a bottom-up approach that aims to discover the network structure connecting those wide-ranging beliefs.
+
+Here we speculate about how this kind of approach might be applied to the topics of climate change and racial justice: complex domains in which variability in people’s beliefs leads to serious societal consequences, and in which widespread misconceptions demand intervention.
+In both cases, we hypothesize that people’s behaviors are shaped by a wide-ranging network of interconnected beliefs that might be better understand through approaches similar to those developed here.
+
+Consider first the domain of climate change: Without swift and drastic efforts to reduce CO2 emissions, global climate change threatens to increase extreme weather events, disrupt agriculture, destroy ecosystems, and displace millions of people over the next few decades.
+Climate change is a complex geophysical, economic, political, and social phenomenon.
+Many changes, both individual and structural, are likely needed to effectively reduce CO2 emissions and mitigate the worst effects of climate change.
+Our work suggests that efforts to understand and encourage any of these behaviors might be best-served by seeking to understand the broader web of beliefs that sustain and support them.
+
+Small models of beliefs related to climate change with Bayesian Networks have already yielded some promising results.
+Cook and Lewandowsky (2016) developed a model of how a core free-market "worldview" affects beliefs and belief revision about whether human-caused climate change is really happening.
+Schotsch and Powell (2022) explored people's causal mental models of how CO2 emissions cause global warming and how warming in turn causes different outcomes such as rising sea levels and extreme weather.
+Elaborating on these small models to discover and model a wider network of related beliefs has great potential for crafting effective interventions in this domain.
+
+We might ask: How do people understand the science connecting CO2 emissions to warming and warming to other negative consequences and do they trust this science?
+How do people weigh the efficacy of their own individual behaviors versus government regulations?
+How much do they trust regulators or specific regulations to be effective and how concerned are they about their economic side-effects?
+How do they expect climate-driven extreme weather, crop losses, economic disruptions, and mass migration will affect them personally?
+What obligations do they feel toward future generations or even their own children for the kind of world they leave behind?
+What value do they place on preserving the natural world and its rich ecosystems and biodiversity?
+
+The complexity of this domain will likely present a challenge to cataloging even a wide auxiliary set of beliefs that could fully circumscribe it.
+Thus the goal need not be to identify an authoritative and all-encompassing "intuitive theory" of climate change.
+Rather, interventionists might be better served by developing more constrained models of intuitive theories that bear directly on a specific target behavior of interest.
+
+Intuitive theories may also inform people’s reasoning about social and political issues.
+To highlight one important example, following the police killing of George Floyd in 2020, protests for racial and social justice organized by groups like Black Lives Matter spread across the U.S.
+and elsewhere.
+Across different people and groups of people these events spurred a wide range of reactions: Some called for police departments to be defunded, others for police funding to be increased.
+Some sought to educate themselves by purchasing anti-racist books, others began pressuring school boards to eliminate purported elements of “critical race theory” from K-12 curricula.
+Some were freshly or further awakened to and disquieted by racial injustice in American society, others were persuaded by the white supremacist “great replacement” conspiracy theory.
+
+One way to try to understand these vastly different reactions is to imagine that they were shaped by large, complex networks of beliefs about the nature of race; about American history and politics; about policing; about justice, equity, and other moral principles; and so on.
+The approach outlined in the current studies could provide a useful tool for navigating this complexity, yielding insights into the interrelations among these beliefs.
+
+To draw a few examples from the vast literature on American racism: How does understanding of the historical impacts of slavery, reconstruction, the post reconstruction era and the civil rights era relate to beliefs about the racial inequalities that persist in the present day?
+How does this historical awareness in turn relate to whether people conceptualize racism as residing in beliefs, attitudes, and behaviors of individuals or as embedded in societal structures, institutions, and practices?
+How do construals of race as a biological trait versus as a social construct impact thoughts on these issues?
+And how does the conceptualization of racism as an individual or structural problem encourage people to address racism actively or passively ignore it?
+It is our hope that mapping out connections among these and other beliefs could reveal new avenues for correcting people’s misconceptions and promoting mutual understanding that could spur anti-racist actions and social change.
 
@@
 
+Not all human reasoning need be governed by intuitive theories, but intuitive theories are likely to be crucial wherever people must integrate information to evaluate, explain, or make decisions.
 Intuitive theories are powerful cognitive tools, for better and for worse.
 Coherent networks of beliefs allow people to understand, predict, and navigate the world, but they can also sustain misconceptions and lead to suboptimal---even dangerous---decisions and behaviors.
-As the past two years have made abundantly clear, deciding to opt out of getting vaccinated against diseases like measles or COVID-19 is not only dangerous for the individual, but a serious threat to public health.
-We hope the studies presented here have shed light on how people might come to such decisions, why the misconceptions that support these decisions can be so hard to combat, and how to develop educational interventions that are persuasive and effective in encouraging and sustaining healthier behaviors.
+The present work on understanding vaccine hesitancy suggests a general theoretical approach to understanding belief revision more broadly: by mapping out a set of beliefs relevant to a given domain, researchers and educators might identify optimal avenues for persuasion and education.
+Further, by formalizing intuitive theories into quantitative models, our approach supports the use of bottom-up approaches to discover structure among a wider set of auxiliary beliefs and provide more precise tests of theories of belief revision.
+We hope the studies presented here have shed light on how people might come to form the beliefs and misconceptions that they do, why those misconceptions can be so hard to combat, and how to develop educational interventions that are persuasive and effective in encouraging and sustaining positive behaviors.
 

### 2022-07-08 supplement/supplement-main.Rmd
paper revisions

@@
 ---
-title: "Supporting Information"
+title: "Supplementary Materials"
 subtitle: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
@@
 
-1.
+1\.
 When two beliefs are related by an intuitive theory, evidence affecting one of those beliefs will also affect the other in accordance with their relationship in the intuitive theory (e.g.
@@
 This is a clear and direct consequence of the laws of probability and Bayes' rule.
-2.
+
+2\.
 Where beliefs about two states of affairs, A and B, are related through an intuitive theory (e.g., A causes B), those beliefs will be systematically correlated across individuals in proportion to the average conditional probabilities (e.g.
@@
 
-$p_i(y) = p_i(y|x)p_i(x) + p_i(y|\neg x)(1-p_i(x))$
+\begin{equation}
+p_i(y) = p_i(y|x)p_i(x) + p_i(y|\neg x)(1-p_i(x))
+\end{equation}
 
@@
 
-$p_i(y) = p_i(y|\neg x) + (p_i(y|x)p_i(x) - p_i(y|\neg x))p_i(x)$
+\begin{equation}
+p_i(y) = p_i(y|\neg x) + (p_i(y|x)p_i(x) - p_i(y|\neg x))p_i(x)
+\end{equation}
 
@@
 
-3.
+3\.
 Thus we can often reasonably expect there will be some systematic relationship between the average change in each belief following evidence and the correlation among those beliefs across individuals.
@@
 First, we expand $\Delta p_i(y)$ via the law of total probability and rearrange terms
-$$
-\begin{align*}
+
+\begin{align}
 \Delta p_i(y)  &= p_i(y|e) - p_i(y)\\
@@
 &= \big(p_i(x|e) - p_i(x)\big)\cdot \big(p_i(y|x) - p_i(y|\neg x)\big)
-\end{align*}
-$$
+\end{align}
+
 Taking the average, we have
-$$
+
+\begin{equation}
 \overline{\Delta p_i(y)} = \overline{p(y|e) - p(y)} = \frac{1}{n}\sum_i\big(p_i(x|e) - p_i(x)\big)\big(p_i(y|x) - p_i(y|\neg x)\big)
-$$
+\end{equation}
+
 From the definition of covariance we have
-$$
+
+\begin{equation}
 cov(X,Y) = E(XY) - E(X)E(Y)
-$$
+\end{equation}
+
 If we assume that the change in belief in x following the evidence, $\Delta p_i(x)$ is uncorrelated with the conditional probabilities encoded in the intuitive theory $p_i(y|x)p_i(x) - p_i(y|\neg x)$ (i.e.
 covariance equals zero) and apply this definition, we can then rewrite the average change as
-$$
+
+\begin{equation}
 \overline{\Delta p_i(y)} = \overline{p(y|e) - p(y)} = \frac{1}{n}\sum_ip_i(x|e) - p_i(x) \frac{1}{n}\sum_ip_i(y|x) - p_i(y|\neg x)
-$$
+\end{equation}
+
 And we have thus shown that $\overline{\Delta p_i(y)} \propto \overline{p_i(y|x)p_i(x) - p_i(y|\neg x)} \propto corr(p_i(x),p_i(y))$
@@
 We assume these actual measurements are some monotonic function of these credences, $f(p_i(x))$.
-Allowing that $f$ could be non-linear, the proportionality conclusions are no longer guaranteed.
+Allowing that $f$ could be non-linear, the proportionality conclusions are no longer guaranteed, though a monotonic association would remain.
 
@@
 
-```{r fig1-dag-example, echo=F, message=F, warning=F, fig.align='center', out.width = '40%', fig.cap="Example DAG illustrating some variables related to wildfires."}
-
-library(DiagrammeR)
-library(DiagrammeRsvg)
-library(rsvg)
-
-grViz(
-  diagram = "
-  digraph causal {
-
-	  # Nodes
-	  node [shape = oval]
-	  D [label = 'Dry']
-	  H [label = 'Heat']
-	  F [label = 'Fire']
-	  S [label = 'Smoke']
-
-	  # Edges
-	  edge [color = black,
-	        arrowhead = vee]
-	  rankdir = LR
-	  D->F
-	  H->F
-	  F->S
-
-	  # Graph
-	  graph [overlap = true, fontsize = 8]
-	}"
-)
+```{r, out.width='100%', fig.align='center', fig.cap = 'Several examples illustrating different features of Bayesian Networks.
+\\newline A) A graphical representation of influence relations: Fire causes smoke.
+This influence is represented by the conditional dependencies captured in a conditional probability table (CPT).
+\\newline B) A “parent” node can be linked to multiple “children” and a “child” node can be linked to multiple “parents”: A child and its parents together compose a “family”.
+This graph has three families: {Accidents, lightning, drought, fire}, {fire, smoke}, and {fire, ash} described by a corresponding CPT (not pictured).
+\\newline C) Not all influence relations correspond to causation: A storm consists of rain, thunder, and lightning (marked as dashed arrows).
+Causes can be generative or preventive, e.g.
+rain prevents drought and fire (red arrows).
+Some nodes may exert countervailing influences on others: A storm consists of rain, which can prevent fires, but a storm also consists of lightning, which can cause fires.
+In addition, parents may influence their children independently or interactively.
+Lightning and accidents could be seen as independent causes of fire—an accident may cause a fire whether or not there is lightning, and vice versa.
+However, drought conditions interact with both of these other parent nodes, making them more likely to produce a fire.
+In the present work, we will consider only the role of independent influence relations.'}
+knitr::include_graphics("../paper/fig-bn-examples.png")
 ```
@@
 
-$$P(y) = \Big(1-(1-w_0)\prod_i(1-w_i)^{x_i}\Big)\prod_j(1-w_j)^{x_j}$$
+\begin{equation}
+P(y) = \Big(1-(1-w_0)\prod_i(1-w_i)^{x_i}\Big)\prod_j(1-w_j)^{x_j}
+\end{equation}
 
@@
 
-$$y \sim beta\big(\mu k, (1-\mu)k\big)$$
-$$\mu = \exp\Bigg(\ln\Big(1 - \exp\big(\ln\big(1-w_0) + \sum_i(1-w_i)x_i\big)\big) \Big) + \ln\Big(\sum_i(1-w_i)(1-x_i)\Big)\Bigg)$$
+\begin{align}
+y &\sim beta\big(\mu k, (1-\mu)k\big) \\
+\mu &= \exp\Bigg(\ln\Big(1 - \exp\big(\ln\big(1-w_0) + \sum_i(1-w_i)x_i\big)\big) \Big) + \ln\Big(\sum_i(1-w_i)(1-x_i)\Big)\Bigg)
+\end{align}
 
@@
 Many scoring metrics are possible, but a directly meaningful one is p(d|G), the likelihood of the data given the graph structure.
-Asymptotically, this can be estimated using the Bayesian Information Criterion (BIC) (citation):
-
-$$BIC = k \ln (n) - 2\sum_{i}\hat{\ell}(x_i|x_{va(x_i)})$$
+Asymptotically, this can be estimated using the Bayesian Information Criterion (BIC):
+
+\begin{equation}
+BIC = k \ln (n) - 2\sum_{i}\hat{\ell}(x_i|x_{va(x_i)})
+\end{equation}
 
@@
 library(parallel)
+library(DiagrammeR)
 
@@
 
-$$ log\big(O(h|d)\big) = \ln\big(O(h)\big) + \ln\Big(\frac{P(d|h=1)}{P(d|h=0)}\Big) $$
+\begin{equation}
+log\big(O(h|d)\big) = \ln\big(O(h)\big) + \ln\Big(\frac{P(d|h=1)}{P(d|h=0)}\Big) 
+\end{equation}
 
@@
 
-$$ER = \frac{P(d|h=1)}{P(d|h=0)}$$
+\begin{equation}
+ER = \frac{P(d|h=1)}{P(d|h=0)}
+\end{equation}
 
@@
 
-$$y \sim beta\big(\mu k, (1-\mu)k\big)$$
-$$logit(\mu) = logit(pretest) + \ln(ER_0) + x\ln(ER_{1})$$
+\begin{align}
+y &\sim beta\big(\mu k, (1-\mu)k\big) \\
+logit(\mu) &= logit(pretest) + \ln(ER_0) + x\ln(ER_{1})
+\end{align}
 
@@
 
-$$ p(evidence = 1 | x ) = .50*ER_1$$
-$$ p(evidence = 0 | x) = .50. $$
+\begin{align}
+p(evidence = 1 | x ) &= .50*ER_1 \\
+p(evidence = 0 | x) &= .50. 
+\end{align}
 
@@
 
-```{r}
+```{r, include=F}
 ## Effect size for study 3

### 2022-07-08 install-packages.R

@@ -21,3 +21,5 @@ package_list <- c(
 install.packages(package_list)
 
 devtools::install_github("thomasp85/patchwork", "crsh/papaja")
+
+tinytex::install_tinytex()

### 2022-07-09 install-packages.R
last min resub fixes

@@ -15,7 +15,8 @@ package_list <- c(
   "rsvg",
   "corrplot",
   "cowplot",
-  "caret"
+  "caret",
+  "table1"
 )
 
 install.packages(package_list)

### 2022-09-30 paper/paper-papaja.Rmd
updated osf link
2nd resubmission

@@
   Supplementary Materials, including all data and analysis code for this project are available at https://osf.io/sdfpj/.
-Preregistration information for Studies 3a and 3b is available at https://osf.io/csnez/registrations.
+Preregistration information for Studies 3a and 3b is available at https://osf.io/uemq4.
 Earlier modeling and analyses of data from Study 1 were presented at the 40th Annual Conference of the Cognitive Science Society.
@@
 keywords          : "Intuitive theories; Belief revision; Vaccine attitudes; Cognitive modeling"
-wordcount         : "9161"
+wordcount         : "11853"
 
@@
 Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct [e.g., @betsch.sachse2013; @horne.etal2015; @lewandowsky.etal2012].
-Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @dube.etal2015; @horne.etal2015; @vannice.etal2011; @wallace.etal2006].
+Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @dube.etal2015; @horne.etal2015; @vannice.etal2011; @wallace.etal2006; and for some other effective approaches see e.g.
+@gagneur.etal2018; @opel.etal2013].
 This is especially sobering in the context of the coronavirus pandemic: widespread reluctance to be vaccinated against COVID-19 threatens our ability to end a pandemic that has already claimed more than five million lives around the world.
@@
 see @holyoak.powell2016; @holyoak.simon1999; @simon.etal2004; @thagard1989; @spellman.etal1993].
-In these models, beliefs or attitudes are represented by nodes (neurons) connected by undirected or bi-directed edges—in contrast to the directed edges used in Bayesian Networks.
+In these models, beliefs or attitudes are represented by nodes (neurons) connected by undirected or bi-directed edges---in contrast to the directed edges used in Bayesian Networks.
 One application of neural-network models has been the modeling of “coherence-shifts”: patterns of belief revision wherein the beliefs or attitudes that should putatively serve as inputs to an evaluation are themselves modified during the process of evaluation.
@@
 Based on these results, we chose to apply a score-based "hill-climbing"  algorithm using our generative model constraints (see Supplementary Materials for details).
-Applying these techniques resulted in an estimate of the network shown in Figure 1.
+Applying these techniques resulted in an estimate of the network shown in Figure 2.
 
@@
 To address this, we compared the Bayesian network model’s predictions to a suite of 14 naive “maximal” regression models, each using values on all 13 other belief scales as predictors for each belief.
-The model presented in Fig.
-1---which we take to be simpler, more psychologically plausible, and more intelligible---performed as strongly as these "maximal" regression models (see Supplementary Materials).
+The model presented in Figure 2---which we take to be simpler, more psychologically plausible, and more intelligible---performed as strongly as these "maximal" regression models (see Supplementary Materials).
 
@@
 
-Very few educational interventions have been shown to improve attitudes toward childhood vaccination.
-One of the few successful educational interventions in this domain was tested by Horne and colleagues [-@horne.etal2015], who found that emphasizing the dangers of preventable diseases like mumps, measles, and rubella improved participants’ attitudes toward vaccines.
+Only a handful of educational interventions have been shown to improve attitudes toward childhood vaccination.
+One of the successful educational interventions in this domain was tested by Horne and colleagues [-@horne.etal2015], who found that emphasizing the dangers of preventable diseases like mumps, measles, and rubella improved participants’ attitudes toward vaccines.
 Their intervention included descriptions of the symptoms of mumps, measles, and rubella; vivid photos of children suffering from these diseases; and a brief story from the perspective of a parent whose child was hospitalized with measles (see Supplementary Materials).
